### 2023-08-28 paper.tex
First draft

\documentclass{article}
\pdfpagewidth=8.5in
\pdfpageheight=11in

\usepackage{ijcai23}

\usepackage{times}
\usepackage{soul}
\usepackage{url}
\usepackage[hidelinks]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[small]{caption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage[switch]{lineno}

\usepackage{listings}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage[capitalize,noabbrev]{cleveref}
\usepackage{microtype}

\lstset{breaklines=true}
\lstset{language=C++,
        basicstyle=\ttfamily,
        stringstyle=\color{red},
        commentstyle=\color{green},
        breaklines=true,
        showstringspaces=false}

% Comment out this line in the camera-ready submission
\linenumbers

\urlstyle{same}

% the following package is optional:
%\usepackage{latexsym}

% See https://www.overleaf.com/learn/latex/theorems_and_proofs
% for a nice explanation of how to define new theorems, but keep
% in mind that the amsthm package is already included in this
% template and that you must *not* alter the styling.
\newtheorem{example}{Example}
\newtheorem{theorem}{Theorem}

% PDF Info Is REQUIRED.
% Please **do not** include Title and Author information
\pdfinfo{
/TemplateVersion (IJCAI.2023.0)
}

\title{Towards Practical First-Order Model Counting}

% \author{
% First Author$^1$
% \and
% Second Author$^2$\and
% Third Author$^{2,3}$\And
% Fourth Author$^4$
% \affiliations
% $^1$First Affiliation\\
% $^2$Second Affiliation\\
% $^3$Third Affiliation\\
% $^4$Fourth Affiliation
% \emails
% \{first, second\}@example.com,
% third@other.example.com,
% fourth@example.com
% }

\begin{document}

\maketitle

% <= 200 words
\begin{abstract}
\end{abstract}

\section{Introduction}

\section{Methodology}

\begin{itemize}
  \item Added support for infinite precision integers using the \texttt{gmp}
        library to the numerical evaluation part. Now, all functions take
        arguments (domain sizes) as unsigned integers and return
        \texttt{mpz\_class} objects (defined in the \texttt{gmpxx.h} header).
  \item Added a CLI option \texttt{--sizes} to specify the domain sizes on the
        command line.
  \item Converting the recursive equations into a \texttt{C++} program, which
        can then be compiled and executed to obtain numerical values.
  \item The translation of a set of equations($E$) into \texttt{C++} works as
        follows.
        \begin{enumerate}
          \item First, we create a cache for each function in $E$. For a
                function with name \texttt{func}, this cache is called
                \texttt{func\_cache}. This is implemented as a multi-dimensional
                vector containing objects of \texttt{class cahce\_elem} defined
                as shown in the example code. The default initialization of this
                object is to $-1$ which is useful for recognizing unevaluated
                cases.
          \item Next, we create a function definition for each lhs in $E$,
                including all functions and base cases. The signatures of these
                functions is decided as follows - a function call containing
                only variable arguments is named as the function itself, and
                ones with constants in their arguments are suffixed with a
                string that contains \texttt{'x'} at the $i$th place if the
                $i$th argument is variable and the $i$th argument if that
                argument is a constant. For example, $f(x1, x2, x3)$ is declared
                as \texttt{int f(int x1, int x2, int x3);} and $f(1, x2, x3)$ is
                declared as \texttt{int f\_1xx(int x2, int x3);} (the constant
                arguments are removed from the signature).
          \item The rhs of each equation in $E$ is used to define the body of
                the equation corresponding to the lhs of that equation. The
                function body (for a function \texttt{func} corresponding to
                equation $e$) is formed as follows-
                \begin{enumerate}
                  \item First, we check if the evaluation is already present in
                        the cache. If so, then we return the cache element. The
                        cache accesses are done using the \texttt{get\_elem}
                        function(definition given in the example), which resizes
                        the cache if the accessed index is out of range.
                  \item If the element is absent, then we decide if the
                        arguments corresponding to $e$ or one of the functions
                        corresponding to the base cases, based on the value of
                        the arguments. If it corresponds to the base cases, then
                        we directly call the base case function and return its
                        value. Else, we evaluate the value using the rhs, store
                        the evaluated value in the cache and return the
                        evaluated value. Note that in this step, we only call
                        the base case function with one more constant argument
                        that \texttt{func}. For example, \texttt{f0(x, y)} would
                        call \texttt{f0\_0x(y)} if \texttt{x == 0} and
                        \texttt{f0\_x0(x)} if \texttt{y == 0}.
                  \item In order to translate the rhs, we do the following
                        changes-
                        \begin{itemize}
                          \item \verb|a^b| is converted to \texttt{power(a,b)}.
                          \item \texttt{Sum[exp, x, a, b]} = ($\sum_{x=a}^{b}exp$) is converted to -\\
                                \begin{lstlisting}
([y,z,...](){
    int sum{0};
    for(int x{a}; x <= b; x++)
        sum += exp;
    return sum;
})()
\end{lstlisting}
                                where y, z, ... are the free variables present
                                in \texttt{exp}.
                        \end{itemize}
                \end{enumerate}
        \end{enumerate}
  \item Implemented the evaluation of basecases. The evaluation is done by
        simplifying the clauses and then using CRANE to find the basecases.
        First, in the \texttt{SimplifyUsingWolfram} class, while traversing the
        graph to find the equations, we store 2 \texttt{Map} objects -
        \texttt{clause\_func\_map}(which stores the mapping from the function
        names to the formulae, whose model count they represent) and
        \texttt{var\_domain\_map}(which stores the mapping from the variable
        names to the domains whose sizes they represent). Then, a particular
        domain is selected(using the algorithm described in previous reports)
        and the clauses are simplified. Then, CRANE is called on those clauses
        to evaluate the base cases using \texttt{WeightedCNF.SimplifyInWolfram}.
        After that, we change the function names and variable to make it
        consistent with the previous domain to variable mapping, and append
        these basecases to the set of equations.
  \item Ideas for finding which base cases are needed. The goal is to find the
        sufficient set of base cases. We know that if say, on the rhs of all
        equations, the domain size appears as $m-c_1, m-c_2, \dots, m-c_k$, then
        finding $f(0, x_1, x_2, \dots)$, $f(1, x_1, x_2, \dots)$,
        $\dots f(m_0, x_1, x_2, \dots)$ for every function $f$, where
        $m_0 = \textnormal{max}(c_1, c_2, \dots c_k) - 1$ forms a sufficient set
        of base cases. Hence, in order to do the same efficiently, we can take
        that domain for which $m_0$ is the minimum, i.e.
        $argmin(\textnormal{max}(c_1, c_2, \dots c_k))$.
  \item If a domain is set to $0$, the model count can be found by simplifying
        the universal and existential quantifiers over that domain, and then
        using crane. However, if a domain is set to contain some non-empty
        number of elements, we can apply GDR over that domain and proceed with
        crane, substituting the known values of preveiously calculated model
        counts in the process.
  \item Implemented a function to simplify functions (recursive and
        non-recursive) using the Wolfram Engine. Modified the wolfram
        simplification functions to incorporate binomial and indicator
        functions.
\end{itemize}

\subsection{Foo}

The target is to generate C++ code that can evaluate numerical values of the
model counts based on the equations generated by \textsc{Crane}. There are two
ways to do the same.
\begin{enumerate}
  \item Generate C++ code by traversing the FCG, similar to what is done in
        \texttt{OutputVisitor.scala}.
  \item Parse the equations generated by \textsc{Crane} after simplifying in
        wolfram and then generate C++ code.
\end{enumerate}

The problem with the first approach is that while generating base cases, the
subsequent calls for \textsc{Crane} do not necessarily have the same meanings
for the function arguments and the functions. For example, if \texttt{f1[x0, x1,
  x2]} represents the model count of a constrained formula F, where f1 is an
auxilliary formula and $x0 = |A|, x1 = |B|, x2 = |C|$, ($A,B,C$ are domains) and
we want to evaluate \texttt{f1[0, x1, x2]}($|A| = 0$), then \textsc{Crane} may
return the required model count as \texttt{f0[x0, x1]}, where
$x0 = |B|, x1 = |C|$. We'll need to translate this to \texttt{f1[0,x1,x2]},
which has already been implemented in \texttt{Basecases.scala}. Also, the second
approach can be done in linear time in the length of the formula using
the
\href{https://en.wikipedia.org/wiki/Shunting_yard_algorithm#:~:text=In%20computer%20science%2C%20the%20shunting,abstract%20syntax%20tree%20(AST).}{Shunting
  Yard Algorithm}. Hence, we are implementing the second approach (have already
implemented the parser).

\subsection{Bar}

The previous method of base case evaluation on setting a domain to size 0 or 1
had the following error - in case a domain size was set to 0, it assumed that
those predicates which were deleted from the clauses could take any truth value
over the entire domain and the rest were fully covered by the remaining clauses.

For example, consider the constrained CNF formula -
\begin{align}
  \forall x \in \Delta \forall y, z \in \Gamma &: P(x) \lor Q(y, z) \\
  \forall y \in \Gamma^\top &: Q(y, z)
\end{align}
In this case, if we set $|\Delta|$ to $0$, then based on the previous idea, the
new set of clauses would be
\begin{equation}
  \forall y, z \in \Gamma^\top : Q(y, z)
\end{equation}
and the set of removed predicates is $\phi$, and hence the model count returned
would be $1$. However, the actual model count shoud be
$2^{|\Gamma|^2 - |\Gamma^\top|^2}$.

There are 2 ideas which we could think of to solve this -
\begin{enumerate}
  \item \textit{(Currently, we have implemented this)} Convert the clauses
        having universal quantification over the null domain to tautology
        clauses, hence retaining all the predicates which don't have an argument
        belonging to the null domain. For example, we would convert the above
        mentioned CNF formula to
        \begin{align}
          \forall y, z \in \Gamma &: Q(y, z) \lor \neg Q(y, z) \\
          \forall y, z \in \Gamma^\top &: Q(y, z)
        \end{align}
        The model count returned by this will also consider the truth value of Q
        over $y \not \in \Gamma^\top$ or $z \not \in \Gamma^\top$.
  \item We find the domain size over which the predicate has not been defined by
        the clauses and multiply the required factor. For example, in the above
        example, the multiplier would be $2^{|\Gamma|^2 - |\Gamma^\top|^2}$ and
        the simplified set of clauses would be
        \begin{equation}
          \forall y, z \in \Gamma^\top : Q(y, z)
        \end{equation}
        which has a model count of $1$. Hence, the obtained value of model count
        would be $2^{|\Gamma|^2 - |\Gamma^\top|^2} \times 1$.
\end{enumerate}

\section{Algorithms}

\subsection{Algorithm to Find a Sufficient Set of Base Cases}

\begin{algorithm}[t]
  \caption{Algorithm For Sufficient Base Cases}\label{alg1}
  \KwIn{dependencies}
  \KwOut{base\_cases}

        % Algorithm steps
        base\_cases $\leftarrow$ Set()

        \ForEach{dependency $\in$ dependencies}{
          \ForEach{elem $\in$ dependency.value}{
            \If{dependency.key.func\_name = elem.func\_name}{
              \ForEach{arg $\in$ elem.args}{
                \tcp{eg : lim is 2 for the arg (x-3)}
                lim $\leftarrow$ arg.const\_subtracted - 1 \\
                \For{l $\in$ 0 to lim}{
                  \tcp{eg : for dependency.key = f(x,y), arg = x and l = 0, add f(0, y) to base\_cases}
                  base\_cases += dependency.key.substitute\_arg(arg\_var, l)
                }
              }
            }
            \Else{
              \ForEach{arg $\in$ elem.args}{
                \tcp{eg : lim is 2 for the arg (x-3)}
                lim $\leftarrow$ arg.const\_subtracted - 1 \\
                \For{l $\in$ 0 to lim}{
                  \tcp{eg : for dependency.key = f(x,y), arg = x and l = 0, add f(0, y) to base\_cases}
                  base\_cases += dependency.key.substitute\_arg(arg, l)\\
                  \tcp{signature for f(x-1, y-2) is f(x,y)}
                  base\_cases += elem.signature.substitute\_arg(arg, l)
                }
              }
            }
          }
        }
\end{algorithm}

The pseudo-code of the algorithm is given as \cref{alg1}. Here,
\texttt{dependencies} maps the function call on the lhs of each equation to the
set of function calls on the rhs of the equation. For example, for the equations
\begin{equation*}
  f(m, n) = g(m-1, n) + f(m-2, n-1)
\end{equation*}
\begin{equation*}
  g(m, n) = f(m-1, n-2) + g(m-1, n-1)
\end{equation*}
the dependencies are
\begin{equation*}
  f(m,n) \mapsto \{g(m-1,n), f(m-2, n-1)\}
\end{equation*}
\begin{equation*}
  g(m, n) \mapsto \{f(m-1, n-2), g(m-1, n-1)\}
\end{equation*}

\subsection{Algorithm to Transform CNF Based on Domain Sizes}

\begin{algorithm}[t]
  \caption{Algorithm For Transforming CNF Based on Domain Sizes}\label{alg2}
  \KwIn{cnf, dom, dom\_size}
  \KwOut{transformed\_cnf, multiplier}
  removed\_predicates $\leftarrow$ Set()
  retained\_predicates $\leftarrow$ Set()
  \If{dom\_size = 0}{
    \ForEach{clause $\in$ cnf}{
      \If{dom $\in$ clause.domains}{
        removed\_predicates += clause.predicates
      }
      \Else{
        retained\_predicates += clause.predicates
        transformed\_cnf += clause
      }
    }
    removed\_predicates = removed\_predicates $\setminus$ retained\_predicates
    \ForEach{pred $\in$ removed\_predicates}{
      multiplier *= $2^{(pred.domain\_sizes.join("*"))}$
    }
  }
  \ElseIf{dom\_size = 1}{
    const $\leftarrow$ newConst()
    \ForEach{clause $\in$ cnf}{
      transformed\_clause $\leftarrow$ clause
      \ForEach{v $\in$ clause.vars | v.domain = dom}{
        transformed\_cnf $\leftarrow$ transformed\_clause.substituteVar(v, const)
      }
      transformed\_cnf += transformed\_clause
    }
  }
\end{algorithm}

The pseudo code is given as \cref{alg2}. We use \cref{alg2} to find the
transformed CNF corresponding to each base case obtained using \cref{alg1} and
call \textsc{Crane} on the CNF to obtain the required base cases.

\subsection{Baz}

The following steps were followed while finding the basecases-
\begin{enumerate}
  \item Expand the summations in each equation - Here we expand the summations
        of the form:
        $\sum_{x=0}^{x1}<\textnormal{something}> \cdot [a \le x < b]$, or
        similar inequalities where x is bounded by constants and $a$ and $b$ are
        constants, by substituting the value of x from $a$ to $b-1$. For
        example, we replace
        $\sum_{x=0}^{x_1} {{x_1}\choose{x}} f(x_1-x)\cdot[0 \le x < 2]$ by
        ${{x_1}\choose{0}}f(x_1) + {{x_1}\choose{1}}f(x_1-1)$.
  \item Next, we find the dependencies of those functions that appear on the rhs
        of any equation. Consider, for example the following set of equations-
        \begin{align}
          f0(m, n) &= f1(m-1, n) + f2(m, n-1)\\
          f1(m, n) &= f1(m-1, n-1) \times f2(m-2, n-1)\\
          f2(m, n) &= 2 \times f1(m-3, n-1)
        \end{align}
        In this case, the dependencies computed are
        \begin{align*}
          f1(m, n) &\rightarrow f1(m-1, n-1), f2(m, n-1)\\
          f2(m, n) &\rightarrow f1(m-3, n-1)
        \end{align*}
  \item Now, based on idea II of the previous report, we find a domain that has
        only terms of the form $x-1$ appearing on the rhs of the dependencies.
        The base cases are then calculated by setting this domain size to 0. For
        the above example, $n$ is the selected domain, and not $m$ since there
        are $m-2$ and $m-3$ terms appearing in the arguments.
\end{enumerate}

\paragraph{Limitations of the current implementation.} Ideally, we should
calculate the base cases based on idea II of the previous report by finding the
basecases upto max$(c1, c2, ...) - 1$. However, we are yet to implement code for
finding the basecases for the non-null domain case.

\bibliographystyle{named}
\bibliography{paper}

\end{document}

### 2023-08-28 paper.tex
Editing the algorithms

@@
 \usepackage{microtype}
-
-\lstset{breaklines=true}
-\lstset{language=C++,
-        basicstyle=\ttfamily,
-        stringstyle=\color{red},
-        commentstyle=\color{green},
-        breaklines=true,
-        showstringspaces=false}
+\usepackage{amsfonts}
+\usepackage{mathtools}
 
@@
 }
+
+\lstset{breaklines=true}
+\lstset{language=C++,
+        basicstyle=\ttfamily,
+        stringstyle=\color{red},
+        commentstyle=\color{green},
+        breaklines=true,
+        showstringspaces=false}
+
+\crefname{line}{line}{lines}
+
+\DeclareMathOperator{\Dom}{Dom}
+\DeclareMathOperator{\Doms}{Doms}
+\DeclareMathOperator{\Preds}{Preds}
+\DeclareMathOperator{\Vars}{Vars}
 
@@
         \texttt{mpz\_class} objects (defined in the \texttt{gmpxx.h} header).
-  \item Added a CLI option \texttt{--sizes} to specify the domain sizes on the
-        command line.
   \item Converting the recursive equations into a \texttt{C++} program, which
@@
         number of elements, we can apply GDR over that domain and proceed with
-        crane, substituting the known values of preveiously calculated model
+        crane, substituting the known values of previously calculated model
         counts in the process.
@@
         functions.
+  \item The report has some (long) examples of formulas being transformed into
+        programs perhaps suitable for supplementary material.
 \end{itemize}
@@
 
+For any dependency key, element signature, or clause $P$, argument or variable
+$x$, and number or constant $t$, we shall write $P[t / x]$ for the result of
+substituting $t$ for all occurrences of $x$ in $P$.
+
 \subsection{Algorithm to Find a Sufficient Set of Base Cases}
@@
 
-        % Algorithm steps
-        base\_cases $\leftarrow$ Set()
-
+  base\_cases $\gets \emptyset$\;
   \ForEach{dependency $\in$ dependencies}{
     \ForEach{elem $\in$ dependency.value}{
-            \If{dependency.key.func\_name = elem.func\_name}{
       \ForEach{arg $\in$ elem.args}{
-                \tcp{eg : lim is 2 for the arg (x-3)}
-                lim $\leftarrow$ arg.const\_subtracted - 1 \\
-                \For{l $\in$ 0 to lim}{
-                  \tcp{eg : for dependency.key = f(x,y), arg = x and l = 0, add f(0, y) to base\_cases}
-                  base\_cases += dependency.key.substitute\_arg(arg\_var, l)
-                }
-              }
-            }
-            \Else{
-              \ForEach{arg $\in$ elem.args}{
-                \tcp{eg : lim is 2 for the arg (x-3)}
-                lim $\leftarrow$ arg.const\_subtracted - 1 \\
-                \For{l $\in$ 0 to lim}{
-                  \tcp{eg : for dependency.key = f(x,y), arg = x and l = 0, add f(0, y) to base\_cases}
-                  base\_cases += dependency.key.substitute\_arg(arg, l)\\
-                  \tcp{signature for f(x-1, y-2) is f(x,y)}
-                  base\_cases += elem.signature.substitute\_arg(arg, l)
+        \For{l $\in$ 0 to arg.const\_subtracted - 1}{\label{line:lim}
+          base\_cases += dependency.key[l / arg]\;\label{line:insert}
+          \If{dependency.key.func\_name $\ne$ elem.func\_name}{
+            base\_cases += elem.signature[l / arg]\;\label{line:signature}
           }
@@
 \end{algorithm}
+
+\begin{itemize}
+  \item \cref{line:lim}: eg : the limit is 2 for the arg (x-3)
+  \item \cref{line:insert} eg : for dependency.key = f(x,y), arg = x and l = 0,
+        add f(0, y) to base\_cases
+  \item \cref{line:signature} signature for f(x-1, y-2) is f(x,y)
+\end{itemize}
 
@@
 \begin{algorithm}[t]
-  \caption{Algorithm For Transforming CNF Based on Domain Sizes}\label{alg2}
-  \KwIn{cnf, dom, dom\_size}
-  \KwOut{transformed\_cnf, multiplier}
-  removed\_predicates $\leftarrow$ Set()
-  retained\_predicates $\leftarrow$ Set()
-  \If{dom\_size = 0}{
-    \ForEach{clause $\in$ cnf}{
-      \If{dom $\in$ clause.domains}{
-        removed\_predicates += clause.predicates
+  \caption{Transforming Formulas Based on Domain Sizes}\label{alg2}
+  \KwIn{formula $\phi$, domain $\Delta$, target domain size $n \in \{\, 0, 1 \,\}$, domain size function $|\cdot|$}
+  \KwOut{formula $\phi'$, multiplier $m \in \mathbb{N}$}
+  $P^{-} \gets \emptyset$; $P^{+} \gets \emptyset$; $\phi' \gets \emptyset$; m $\gets 1$\;
+  \uIf{$|\Delta| = 0$}{
+    \ForEach{clause $C \in \phi$}{
+      \uIf{$\Delta \in \Doms(C)$}{
+        $P^{-} \gets P^{-} \cup \Preds(C)$\;
       }
       \Else{
-        retained\_predicates += clause.predicates
-        transformed\_cnf += clause
+        $P^{+} \gets P^{+} \cup \Preds(C)$\;
+        $\phi' \gets \phi' \cup \{\, C \,\}$\;
       }
     }
-    removed\_predicates = removed\_predicates $\setminus$ retained\_predicates
-    \ForEach{pred $\in$ removed\_predicates}{
-      multiplier *= $2^{(pred.domain\_sizes.join("*"))}$
+    $P^{-} \gets P^{-} \setminus P^{+}$\;
+    \ForEach{predicate $P \in P^{-}$}{
+      m *= $2^{(pred.domain\_sizes.join("*"))}$\;
     }
   }
-  \ElseIf{dom\_size = 1}{
-    const $\leftarrow$ newConst()
-    \ForEach{clause $\in$ cnf}{
-      transformed\_clause $\leftarrow$ clause
-      \ForEach{v $\in$ clause.vars | v.domain = dom}{
-        transformed\_cnf $\leftarrow$ transformed\_clause.substituteVar(v, const)
+  \ElseIf{$|\Delta| = 1$}{
+    $c \gets$ a new constant symbol\;
+    \ForEach{clause $C \in \phi$}{
+      $C' \gets C$\;
+      \ForEach{$v \in \Vars(C)$ with $\Dom(v) = \Delta$}{
+        $C' \gets C'[c / v]$\;
       }
-      transformed\_cnf += transformed\_clause
+      $\phi' \gets \phi' \cup \{\, C' \,\}$\;
     }
@@
 \end{algorithm}
+% TODO: either the target domain size or the domain size function needs to go
+
+\begin{itemize}
+  \item Formulas are in CNF. Formulas are (multi) sets of clauses.
+  \item $P^{-}$ --- removed predicates
+  \item $P^{+}$ --- retained predicates
+  \item $\phi'$ --- transformed version of $\phi$
+  \item $C'$ --- transformed version of clause $C$
+  \item For any clause $C$, let $\Doms(C)$, $\Preds(C)$, and $\Vars(C)$ denote
+        respectively the set of domains, predicates, and variables in $C$. For
+        any variable $v$, let $\Dom(v)$ denote its domain. Note that, for any
+        clause $C$, we have that
+        $\Doms(C) = \{\, \Dom(v) \mid v \in \Vars(C) \,\}$. Similarly, for any
+        predicate $P$, let $\Doms(P)$ denote the set of domains associated with
+        $P$.
+\end{itemize}
 

### 2023-08-30 paper.tex
Some writing and editing

@@
 \newtheorem{theorem}{Theorem}
+\newtheorem{definition}{Definition}
+\newtheorem*{remark}{Remark}
 
@@
 \DeclareMathOperator{\Vars}{Vars}
+\DeclareMathOperator*{\argmin}{argmin}
 
@@
 
-\section{Methodology}
+\paragraph{Contributions.}
+\begin{itemize}
+  \item Converting the recursive equations into a C++ program, which can then be
+        compiled and executed to obtain numerical values (see \cref{sec:cpp}).
+  \item Support for infinite precision integers using the GNU Multiple Precision
+        Arithmetic Library.
+\end{itemize}
+
+\section{Snippets}
 
 \begin{itemize}
-  \item Added support for infinite precision integers using the \texttt{gmp}
-        library to the numerical evaluation part. Now, all functions take
-        arguments (domain sizes) as unsigned integers and return
-        \texttt{mpz\_class} objects (defined in the \texttt{gmpxx.h} header).
-  \item Converting the recursive equations into a \texttt{C++} program, which
-        can then be compiled and executed to obtain numerical values.
-  \item The translation of a set of equations($E$) into \texttt{C++} works as
-        follows.
-        \begin{enumerate}
-          \item First, we create a cache for each function in $E$. For a
-                function with name \texttt{func}, this cache is called
-                \texttt{func\_cache}. This is implemented as a multi-dimensional
-                vector containing objects of \texttt{class cahce\_elem} defined
-                as shown in the example code. The default initialization of this
-                object is to $-1$ which is useful for recognizing unevaluated
-                cases.
-          \item Next, we create a function definition for each lhs in $E$,
-                including all functions and base cases. The signatures of these
-                functions is decided as follows - a function call containing
-                only variable arguments is named as the function itself, and
-                ones with constants in their arguments are suffixed with a
-                string that contains \texttt{'x'} at the $i$th place if the
-                $i$th argument is variable and the $i$th argument if that
-                argument is a constant. For example, $f(x1, x2, x3)$ is declared
-                as \texttt{int f(int x1, int x2, int x3);} and $f(1, x2, x3)$ is
-                declared as \texttt{int f\_1xx(int x2, int x3);} (the constant
-                arguments are removed from the signature).
-          \item The rhs of each equation in $E$ is used to define the body of
-                the equation corresponding to the lhs of that equation. The
-                function body (for a function \texttt{func} corresponding to
-                equation $e$) is formed as follows-
-                \begin{enumerate}
-                  \item First, we check if the evaluation is already present in
-                        the cache. If so, then we return the cache element. The
-                        cache accesses are done using the \texttt{get\_elem}
-                        function(definition given in the example), which resizes
-                        the cache if the accessed index is out of range.
-                  \item If the element is absent, then we decide if the
-                        arguments corresponding to $e$ or one of the functions
-                        corresponding to the base cases, based on the value of
-                        the arguments. If it corresponds to the base cases, then
-                        we directly call the base case function and return its
-                        value. Else, we evaluate the value using the rhs, store
-                        the evaluated value in the cache and return the
-                        evaluated value. Note that in this step, we only call
-                        the base case function with one more constant argument
-                        that \texttt{func}. For example, \texttt{f0(x, y)} would
-                        call \texttt{f0\_0x(y)} if \texttt{x == 0} and
-                        \texttt{f0\_x0(x)} if \texttt{y == 0}.
-                  \item In order to translate the rhs, we do the following
-                        changes-
-                        \begin{itemize}
-                          \item \verb|a^b| is converted to \texttt{power(a,b)}.
-                          \item \texttt{Sum[exp, x, a, b]} = ($\sum_{x=a}^{b}exp$) is converted to -\\
-                                \begin{lstlisting}
-([y,z,...](){
-    int sum{0};
-    for(int x{a}; x <= b; x++)
-        sum += exp;
-    return sum;
-})()
-\end{lstlisting}
-                                where y, z, ... are the free variables present
-                                in \texttt{exp}.
+  \item The evaluation of base cases is done by simplifying the clauses and then
+        using \textsc{Crane} to find the base cases. First, while traversing the
+        graph to find the equations, we store two maps objects:
+        \texttt{clause\_func\_map} (which stores the mapping from the function
+        names to the formulae, whose model count they represent) and
+        \texttt{var\_domain\_map} (which stores the mapping from the variable
+        names to the domains whose sizes they represent). Then, a particular
+        domain is selected (using the algorithm described in previous reports),
+        and the clauses are simplified. Then, \textsc{Crane} is called on those
+        clauses to evaluate the base cases. After that, we change the function
+        names and variable to make it consistent with the previous domain to
+        variable mapping, and append these base cases to the set of equations.
+  \item Finding a sufficient set of base cases. We know that if, say, on the RHS
+        of all equations, the domain size appears as
+        $m - c_1, m - c_2, \dots, m - c_k$, then finding
+        $f(0, x_1, x_2, \dots)$, $f(1, x_1, x_2, \dots)$,
+        $\dots f(m_0, x_1, x_2, \dots)$ for every function $f$, where
+        $m_0 = \max(c_1, c_2, \dots c_k) - 1$ forms a sufficient set of base
+        cases. Hence, in order to do the same efficiently, we can take that
+        domain for which $m_0$ is the minimum, i.e.
+        $\argmin(\max(c_1, c_2, \dots c_k))$.
 \end{itemize}
-                \end{enumerate}
-        \end{enumerate}
-  \item Implemented the evaluation of basecases. The evaluation is done by
-        simplifying the clauses and then using CRANE to find the basecases.
-        First, in the \texttt{SimplifyUsingWolfram} class, while traversing the
-        graph to find the equations, we store 2 \texttt{Map} objects -
-        \texttt{clause\_func\_map}(which stores the mapping from the function
-        names to the formulae, whose model count they represent) and
-        \texttt{var\_domain\_map}(which stores the mapping from the variable
-        names to the domains whose sizes they represent). Then, a particular
-        domain is selected(using the algorithm described in previous reports)
-        and the clauses are simplified. Then, CRANE is called on those clauses
-        to evaluate the base cases using \texttt{WeightedCNF.SimplifyInWolfram}.
-        After that, we change the function names and variable to make it
-        consistent with the previous domain to variable mapping, and append
-        these basecases to the set of equations.
-  \item Ideas for finding which base cases are needed. The goal is to find the
-        sufficient set of base cases. We know that if say, on the rhs of all
-        equations, the domain size appears as $m-c_1, m-c_2, \dots, m-c_k$, then
-        finding $f(0, x_1, x_2, \dots)$, $f(1, x_1, x_2, \dots)$,
-        $\dots f(m_0, x_1, x_2, \dots)$ for every function $f$, where
-        $m_0 = \textnormal{max}(c_1, c_2, \dots c_k) - 1$ forms a sufficient set
-        of base cases. Hence, in order to do the same efficiently, we can take
-        that domain for which $m_0$ is the minimum, i.e.
-        $argmin(\textnormal{max}(c_1, c_2, \dots c_k))$.
-  \item If a domain is set to $0$, the model count can be found by simplifying
-        the universal and existential quantifiers over that domain, and then
-        using crane. However, if a domain is set to contain some non-empty
-        number of elements, we can apply GDR over that domain and proceed with
-        crane, substituting the known values of previously calculated model
-        counts in the process.
-  \item Implemented a function to simplify functions (recursive and
-        non-recursive) using the Wolfram Engine. Modified the wolfram
-        simplification functions to incorporate binomial and indicator
-        functions.
-  \item The report has some (long) examples of formulas being transformed into
-        programs perhaps suitable for supplementary material.
-\end{itemize}
-
-\subsection{Foo}
-
-The target is to generate C++ code that can evaluate numerical values of the
-model counts based on the equations generated by \textsc{Crane}. There are two
-ways to do the same.
-\begin{enumerate}
-  \item Generate C++ code by traversing the FCG, similar to what is done in
-        \texttt{OutputVisitor.scala}.
-  \item Parse the equations generated by \textsc{Crane} after simplifying in
-        wolfram and then generate C++ code.
-\end{enumerate}
-
-The problem with the first approach is that while generating base cases, the
-subsequent calls for \textsc{Crane} do not necessarily have the same meanings
-for the function arguments and the functions. For example, if \texttt{f1[x0, x1,
-  x2]} represents the model count of a constrained formula F, where f1 is an
-auxilliary formula and $x0 = |A|, x1 = |B|, x2 = |C|$, ($A,B,C$ are domains) and
-we want to evaluate \texttt{f1[0, x1, x2]}($|A| = 0$), then \textsc{Crane} may
-return the required model count as \texttt{f0[x0, x1]}, where
-$x0 = |B|, x1 = |C|$. We'll need to translate this to \texttt{f1[0,x1,x2]},
-which has already been implemented in \texttt{Basecases.scala}. Also, the second
-approach can be done in linear time in the length of the formula using
-the
-\href{https://en.wikipedia.org/wiki/Shunting_yard_algorithm#:~:text=In%20computer%20science%2C%20the%20shunting,abstract%20syntax%20tree%20(AST).}{Shunting
-  Yard Algorithm}. Hence, we are implementing the second approach (have already
-implemented the parser).
 
@@
 
-The previous method of base case evaluation on setting a domain to size 0 or 1
-had the following error - in case a domain size was set to 0, it assumed that
-those predicates which were deleted from the clauses could take any truth value
-over the entire domain and the rest were fully covered by the remaining clauses.
+The previous method of base case evaluation on setting a domain to size zero or
+one had the following error. In case a domain size was set to zero, it assumed
+that those predicates which were deleted from the clauses could take any truth
+value over the entire domain and the rest were fully covered by the remaining
+clauses.
 
-For example, consider the constrained CNF formula -
-\begin{align}
+For example, consider the formula
+\begin{equation}\label{eq:example}
+  \begin{split}
     \forall x \in \Delta \forall y, z \in \Gamma &: P(x) \lor Q(y, z) \\
-  \forall y \in \Gamma^\top &: Q(y, z)
-\end{align}
-In this case, if we set $|\Delta|$ to $0$, then based on the previous idea, the
-new set of clauses would be
-\begin{equation}
-  \forall y, z \in \Gamma^\top : Q(y, z)
+    \forall y \in \Gamma^\top &: Q(y, z).
+  \end{split}
 \end{equation}
-and the set of removed predicates is $\phi$, and hence the model count returned
-would be $1$. However, the actual model count shoud be
+In this case, if we set $|\Delta|$ to zero, the transformed formula would be
+\[
+  \forall y, z \in \Gamma^\top : Q(y, z),
+\]
+and the set of removed predicates is empty, and hence the model count returned
+would be $1$. However, the actual model count should be
 $2^{|\Gamma|^2 - |\Gamma^\top|^2}$.
 
-There are 2 ideas which we could think of to solve this -
-\begin{enumerate}
-  \item \textit{(Currently, we have implemented this)} Convert the clauses
-        having universal quantification over the null domain to tautology
-        clauses, hence retaining all the predicates which don't have an argument
-        belonging to the null domain. For example, we would convert the above
-        mentioned CNF formula to
-        \begin{align}
+We solve this problem by converting clauses with universal quantifiers over the
+empty domain to tautologies, hence retaining all the predicates that have no
+argument assigned to the empty domain. For example, we would convert the above
+mentioned formula to
+\begin{align*}
   \forall y, z \in \Gamma &: Q(y, z) \lor \neg Q(y, z) \\
   \forall y, z \in \Gamma^\top &: Q(y, z)
-        \end{align}
-        The model count returned by this will also consider the truth value of Q
-        over $y \not \in \Gamma^\top$ or $z \not \in \Gamma^\top$.
-  \item We find the domain size over which the predicate has not been defined by
-        the clauses and multiply the required factor. For example, in the above
-        example, the multiplier would be $2^{|\Gamma|^2 - |\Gamma^\top|^2}$ and
-        the simplified set of clauses would be
-        \begin{equation}
-          \forall y, z \in \Gamma^\top : Q(y, z)
-        \end{equation}
-        which has a model count of $1$. Hence, the obtained value of model count
-        would be $2^{|\Gamma|^2 - |\Gamma^\top|^2} \times 1$.
-\end{enumerate}
+\end{align*}
+The model count returned by this will also consider the truth value of $Q$ over
+$y \not \in \Gamma^\top$ or $z \not \in \Gamma^\top$.
 
-\section{Algorithms}
+\section{Preliminaries}
 
-For any dependency key, element signature, or clause $P$, argument or variable
-$x$, and number or constant $t$, we shall write $P[t / x]$ for the result of
-substituting $t$ for all occurrences of $x$ in $P$.
+TODO: Introduce terms: left-hand side (LHS), right-hand side (RHS).
 
-\subsection{Algorithm to Find a Sufficient Set of Base Cases}
+\begin{definition}
+  A \emph{function call} is a term of the form
+  $f(x_{1} - c_{1}, \dots, x_{n} - c_{n})$ (written $f(\mathbf{x} - \mathbf{c})$
+  for short), where $f$ is an $n$-ary function, each $x_{i}$ is a variable, and
+  each $c_{i}$ is a non-negative constant.
+\end{definition}
+% TODO: do I ever use this term for the case when some of the variables don't
+% exist?
+
+\begin{definition}
+  A \emph{signature} is a term of the form $f(x_{1}, \dots, x_{n})$ (written
+  $f(\mathbf{x})$ for short), where $f$ is an $n$-ary function, and each $x_{i}$
+  is a variable. The signature of a function call $f(\mathbf{x} - \mathbf{c})$
+  is $f(\mathbf{x})$. For example, the signature of $f(x - 1, y - 2)$ is
+  $f(x, y)$.
+\end{definition}
+
+\begin{remark}
+  The LHS of an equation is always a signature.
+\end{remark}
+
+For any signature or clause $C$, argument or variable $x$, and number or
+constant $t$, we shall write $C[t / x]$ for the result of substituting $t$ for
+all occurrences of $x$ in $C$.
+% TODO: check if I'm still using this notation in all these cases
+% TODO: explain how this works for function calls too
+
+\section{Identifying a Sufficient Set of Base Cases}
 
 \begin{algorithm}[t]
-  \caption{Algorithm For Sufficient Base Cases}\label{alg1}
-  \KwIn{dependencies}
-  \KwOut{base\_cases}
+  \caption{Identifying a set of sufficient base cases}\label{alg1}
+  \KwIn{set $D$ of dependencies}
+  \KwOut{set $B$ of base cases}
 
-  base\_cases $\gets \emptyset$\;
-  \ForEach{dependency $\in$ dependencies}{
-    \ForEach{elem $\in$ dependency.value}{
-      \ForEach{arg $\in$ elem.args}{
-        \For{l $\in$ 0 to arg.const\_subtracted - 1}{\label{line:lim}
-          base\_cases += dependency.key[l / arg]\;\label{line:insert}
-          \If{dependency.key.func\_name $\ne$ elem.func\_name}{
-            base\_cases += elem.signature[l / arg]\;\label{line:signature}
-          }
-        }
+  $B \gets \emptyset$\;
+  \ForEach{$(f(\mathbf{x}), g(\mathbf{y} - \mathbf{c})) \in D$}{
+    \ForEach{$c_{i} \in \mathbf{c}$}{
+      \For{$n \gets 0$ \KwTo $c_{i} - 1$}{\label{line:lim}
+        $B \gets B \cup \{\, f(\mathbf{x})[x_{i}/n] \,\}$\;\label{line:insert}
+        \lIf{$f \ne g$}{$B \gets B \cup \{\, g(\mathbf{y})[y_{i}/n] \,\}$}\label{line:signature}
       }
@@
 
+The following steps were followed while finding the base cases:
+\begin{enumerate}
+  \item Expand the summations in each equation. Here we expand the summations of
+        the form:
+        $\sum_{x=0}^{x_{1}}<\textnormal{something}> \cdot [a \le x < b]$, or
+        similar inequalities where x is bounded by constants and $a$ and $b$ are
+        constants, by substituting the value of $x$ from $a$ to $b-1$. For
+        example, we replace
+        $\sum_{x=0}^{x_1} \binom{x_{1}}{x} f(x_1 - x) \cdot [0 \le x < 2]$ by
+        $\binom{x_{1}}{0} f(x_1) + \binom{x_{1}}{1} f(x_1-1)$.
+  \item Next, we find the dependencies of those functions that appear on the
+        RHS of any equation. Consider, for example the following set
+        of equations:
+        \begin{align*}
+          f_{0}(m, n) &= f_{1}(m-1, n) + f_{2}(m, n-1)\\
+          f_{1}(m, n) &= f_{1}(m-1, n-1) \times f_{2}(m-2, n-1)\\
+          f_{2}(m, n) &= 2 \times f_{1}(m-3, n-1)
+        \end{align*}
+        In this case, the dependencies computed are
+        \begin{align*}
+          f_{1}(m, n) &\mapsto \{\, f_{1}(m-1, n-1), f_{2}(m, n-1) \,\}\\
+          f_{2}(m, n) &\mapsto \{\, f_{1}(m-3, n-1) \,\}
+        \end{align*}
+  \item Now, we find a domain that has only terms of the form $x-1$ appearing on
+        the RHS of the dependencies. The base cases are then calculated by
+        setting this domain size to zero. For the above example, $n$ is the
+        selected domain, and not $m$ since there are $m-2$ and $m-3$ terms
+        appearing in the arguments.
+\end{enumerate}
+
+\paragraph{Limitations of the current implementation.} Ideally, we should
+calculate the base cases by finding the base cases up to
+$\max(c_{1}, c_{2}, \dots) - 1$. However, currently only empty and singleton
+domains are supported.
+
 \begin{itemize}
-  \item \cref{line:lim}: eg : the limit is 2 for the arg (x-3)
-  \item \cref{line:insert} eg : for dependency.key = f(x,y), arg = x and l = 0,
-        add f(0, y) to base\_cases
-  \item \cref{line:signature} signature for f(x-1, y-2) is f(x,y)
+  \item \cref{line:lim}: the limit is 2 for the arg $(x-3)$.
+  \item \cref{line:insert} for $f(\mathbf{x}) = f(x_{1}, x_{2})$,
+        $\text{arg} = x$, and $n = 0$, add $f(0, x_{2})$ to $B$.
+  \item note that on \cref{line:signature} it is the signature and not the
+        original function call.
 \end{itemize}
 
-The pseudo-code of the algorithm is given as \cref{alg1}. Here,
-\texttt{dependencies} maps the function call on the lhs of each equation to the
-set of function calls on the rhs of the equation. For example, for the equations
-\begin{equation*}
-  f(m, n) = g(m-1, n) + f(m-2, n-1)
-\end{equation*}
-\begin{equation*}
-  g(m, n) = f(m-1, n-2) + g(m-1, n-1)
-\end{equation*}
+The algorithm is described as \cref{alg1}. Here, a dependency is a pair
+$(a, b)$, where $a$ is the signature on the LHS of each equation and $b$ is each
+function call on the RHS of the equation. For example, for the equations
+\begin{align*}
+  f(m, n) &= g(m-1, n) + f(m-2, n-1)\\
+  g(m, n) &= f(m-1, n-2) + g(m-1, n-1)
+\end{align*}
 the dependencies are
-\begin{equation*}
-  f(m,n) \mapsto \{g(m-1,n), f(m-2, n-1)\}
-\end{equation*}
-\begin{equation*}
-  g(m, n) \mapsto \{f(m-1, n-2), g(m-1, n-1)\}
-\end{equation*}
+\begin{multline*}
+  (f(m, n), g(m - 1, n)), (f(m, n), f(m - 2, n - 1)),\\
+  (g(m, n), f(m - 1, n - 2), g(m - 1, n - 1)).
+\end{multline*}
 
-\subsection{Algorithm to Transform CNF Based on Domain Sizes}
+\section{Algorithm to Transform CNF Based on Domain Sizes}
 
@@
   \KwIn{formula $\phi$, domain $\Delta$, target domain size $n \in \{\, 0, 1 \,\}$, domain size function $|\cdot|$}
-  \KwOut{formula $\phi'$, multiplier $m \in \mathbb{N}$}
-  $P^{-} \gets \emptyset$; $P^{+} \gets \emptyset$; $\phi' \gets \emptyset$; m $\gets 1$\;
+  \KwOut{formula $\phi'$}
+  $P^{-} \gets \emptyset$; $P^{+} \gets \emptyset$; $\phi' \gets \emptyset$\;
   \uIf{$|\Delta| = 0$}{
@@
     $P^{-} \gets P^{-} \setminus P^{+}$\;
-    \ForEach{predicate $P \in P^{-}$}{
-      m *= $2^{(pred.domain\_sizes.join("*"))}$\;
-    }
   }
@@
 \end{algorithm}
+% TODO: the removed empty domains should be replaced by smoothing/tautological
+% constructions
+
 % TODO: either the target domain size or the domain size function needs to go
@@
 
-The pseudo code is given as \cref{alg2}. We use \cref{alg2} to find the
-transformed CNF corresponding to each base case obtained using \cref{alg1} and
-call \textsc{Crane} on the CNF to obtain the required base cases.
+We use \cref{alg2} to find the transformed formula corresponding to each base
+case obtained using \cref{alg1} and call \textsc{Crane} on the formula to obtain
+the required base cases.
 
-\subsection{Baz}
+\section{Generating C++ Code}\label{sec:cpp}
 
-The following steps were followed while finding the basecases-
+% TODO: The report has some (long) examples of formulas being transformed into
+% programs perhaps suitable for supplementary material.
+
+The target is to generate C++ code that can evaluate numerical values of the
+model counts based on the equations generated by \textsc{Crane}. There are two
+ways to do the same.
 \begin{enumerate}
-  \item Expand the summations in each equation - Here we expand the summations
-        of the form:
-        $\sum_{x=0}^{x1}<\textnormal{something}> \cdot [a \le x < b]$, or
-        similar inequalities where x is bounded by constants and $a$ and $b$ are
-        constants, by substituting the value of x from $a$ to $b-1$. For
-        example, we replace
-        $\sum_{x=0}^{x_1} {{x_1}\choose{x}} f(x_1-x)\cdot[0 \le x < 2]$ by
-        ${{x_1}\choose{0}}f(x_1) + {{x_1}\choose{1}}f(x_1-1)$.
-  \item Next, we find the dependencies of those functions that appear on the rhs
-        of any equation. Consider, for example the following set of equations-
-        \begin{align}
-          f0(m, n) &= f1(m-1, n) + f2(m, n-1)\\
-          f1(m, n) &= f1(m-1, n-1) \times f2(m-2, n-1)\\
-          f2(m, n) &= 2 \times f1(m-3, n-1)
-        \end{align}
-        In this case, the dependencies computed are
-        \begin{align*}
-          f1(m, n) &\rightarrow f1(m-1, n-1), f2(m, n-1)\\
-          f2(m, n) &\rightarrow f1(m-3, n-1)
-        \end{align*}
-  \item Now, based on idea II of the previous report, we find a domain that has
-        only terms of the form $x-1$ appearing on the rhs of the dependencies.
-        The base cases are then calculated by setting this domain size to 0. For
-        the above example, $n$ is the selected domain, and not $m$ since there
-        are $m-2$ and $m-3$ terms appearing in the arguments.
+  \item Generate C++ code by traversing the FCG, similar to what is done in
+        \texttt{OutputVisitor.scala}.
+  \item Parse the equations generated by \textsc{Crane} after simplifying in
+        wolfram and then generate C++ code.
 \end{enumerate}
 
-\paragraph{Limitations of the current implementation.} Ideally, we should
-calculate the base cases based on idea II of the previous report by finding the
-basecases upto max$(c1, c2, ...) - 1$. However, we are yet to implement code for
-finding the basecases for the non-null domain case.
+The problem with the first approach is that, while generating base cases, the
+subsequent calls to \textsc{Crane} do not necessarily have the same meanings for
+the function arguments and the functions. For example, if
+$f_{1}(x_{0}, x_{1}, x_{2})$ represents the model count of a constrained formula
+$\phi$, where $f_{1}$ is an auxiliary formula and $x_{0} = |A|$, $x_{1} = |B|$,
+$x_{2} = |C|$, and $A$, $B$, $C$ are domains and we want to evaluate
+$f_{1}(0, x_{1}, x_{2})$ (i.e., set $|A| = 0$), then \textsc{Crane} may return
+the required model count as $f_{0}(x_{0}, x_{1})$, where $x_{0} = |B|$ and
+$x_{1} = |C|$. We will then need to translate this to $f_{1}(0, x_{1}, x_{2})$.
+Also, the second approach can be done in linear time in the length of the
+formula using
+the
+\href{https://en.wikipedia.org/wiki/Shunting_yard_algorithm#:~:text=In%20computer%20science%2C%20the%20shunting,abstract%20syntax%20tree%20(AST).}{Shunting
+  Yard Algorithm}. Hence, we stick to the second approach.
+
+\subsection{Our Approach}
+
+The translation of a set $E$ of equations into a C++ program works as follows.
+
+First, we create a cache for each function in $E$. This is implemented as a
+multi-dimensional vector containing objects of \texttt{class cache\_elem}
+defined as shown in the example code. The default initialization of this object
+is to $-1$ which is useful for recognizing unevaluated cases.
+
+Next, we create a function definition for the LHS of each equation in $E$,
+including all functions and base cases. The signatures of these functions is
+decided as follows. A function call containing only variable arguments is named
+as the function itself, and ones with constants in their arguments are suffixed
+with a string that contains \texttt{'x'} at the $i$th place if the $i$th
+argument is variable and the $i$th argument if that argument is a constant. For
+example, $f(x_{1}, x_{2}, x_{3})$ is declared as \texttt{int f(int x1, int x2,
+  int x3);} and $f(1, x_{2}, x_{3})$ is declared as \texttt{int f\_1xx(int x2,
+  int x3);} (the constant arguments are removed from the signature).
+
+The RHS of each equation in $E$ is used to define the body of the equation
+corresponding to the LHS of that equation. The function body (for a function
+\texttt{func} corresponding to equation $e$) is formed as follows.
+\begin{enumerate}
+  \item First, we check if the evaluation is already present in the cache. If
+        so, then we return the cache element. The cache accesses are done using
+        the \texttt{get\_elem} function (definition given in the example), which
+        resizes the cache if the accessed index is out of range.
+  \item If the element is absent, then we decide if the arguments corresponding
+        to $e$ or one of the functions corresponding to the base cases, based on
+        the value of the arguments. If it corresponds to the base cases, then we
+        directly call the base case function and return its value. Else, we
+        evaluate the value using the RHS, store the evaluated value in the cache
+        and return the evaluated value. Note that in this step, we only call the
+        base case function with one more constant argument that \texttt{func}.
+        For example, \texttt{f0(x, y)} would call \texttt{f0\_0x(y)} if
+        \texttt{x == 0} and \texttt{f0\_x0(x)} if \texttt{y == 0}.
+  \item In order to translate the RHS, we convert $\sum_{x=a}^{b} \texttt{exp}$
+        to
+\begin{lstlisting}
+([y,z,...](){
+    int sum = 0;
+    for(int x = a; x <= b; x++)
+        sum += exp;
+    return sum;
+})()
+\end{lstlisting}
+        where $y, z, \dots$ are the free variables present in \texttt{exp}.
+\end{enumerate}
 

### 2023-10-10 paper.tex
A high-level process overview figure

@@
 \usepackage{mathtools}
+\usepackage{tikz}
 
@@
 \newtheorem*{remark}{Remark}
+\newtheorem{fact}{Fact}
 
@@
 \crefname{line}{line}{lines}
+\crefalias{formula}{equation}
+\crefname{formula}{Clause}{Clauses}
+\creflabelformat{formula}{#2\textup{(#1)}#3}
 
@@
 \DeclareMathOperator*{\argmin}{argmin}
+\newcommand{\expr}{\mathtt{expr}}
+
+\SetKwFunction{Crane}{Crane}
+\SetKwFunction{Propagate}{Propagate}
+\SetKwFunction{FindBaseCases}{FindBaseCases}
+
+\usetikzlibrary{arrows.meta}
+\usetikzlibrary{positioning}
+\usetikzlibrary{shapes}
+\usetikzlibrary{fit}
 
@@
 
+\begin{figure*}[t]
+  \centering
+  \begin{tikzpicture}
+    \node at (0, 0) (formula) {$\phi$};
+    \node[draw,rounded rectangle] at (3, 0) (alg1) {\Cref{alg:main}};
+    \node[draw,rounded rectangle] at (6, 0) (simplification) {Simplification};
+    \node[draw,rounded rectangle] at (9, 0) (compilation) {Compilation};
+
+    \node[draw,rounded rectangle,dashed] at (12, 0) (cpp) {C++ code};
+    \node at (12, -1) (sizes) {Domain sizes};
+
+    \node at (15, 0) (count) {Model count};
+
+    \node[draw,rounded rectangle] at (3, -2) (alg2) {\Cref{alg1}};
+    \node[draw,rounded rectangle,left = 0.1cm of alg2] (crane) {\textsc{Crane}};
+    \node[draw,rounded rectangle,right = 0.1cm of alg2] (alg3) {\Cref{alg2}};
+
+    \node[draw,fit={(alg1) (simplification) (compilation) (crane) (alg2) (alg3)},inner ysep=7pt,yshift=5pt] {};
+    \node at (1.1, 0.5) {\textsc{Crane2}};
+
+    \draw[->] (formula) -- (alg1);
+    \draw[->] (alg1) -- node[above] {$E$} (simplification);
+    \draw[->] (simplification) -- node[above] {$E'$} (compilation);
+    \draw[->] (compilation) -- (cpp);
+    \draw[->] (sizes) -- (cpp);
+    \draw[->] (cpp) -- (count);
+
+    \draw[->,dashed] (alg1) -- node[midway,left] {uses} (crane);
+    \draw[->,dashed] (alg1) -- node[midway] {uses} (alg2);
+    \draw[->,dashed] (alg1) -- node[midway,right] {uses} (alg3);
+  \end{tikzpicture}
+  \caption{Using \textsc{Crane2} to compute the model count of formula $\phi$.\
+    The formula is compiled into a set of equations $E$, which are then
+    algebraically simplified and compiled to a C++ program. This program can
+    then be run with different command line arguments to compute the model count
+    of $\phi$ for various domain sizes.}
+\end{figure*}
+
+The evaluation of base cases is done by simplifying the clauses and then using
+\textsc{Crane} to find the base cases. First, while traversing the graph to find
+the equations, we store two maps: $\mathcal{F}$ (which stores the mapping from
+the function names to the formulae, whose model count they represent) and
+$\mathcal{D}$ (which stores the mapping from the variable names to the domains
+whose sizes they represent). Then, a particular domain is selected (using the
+algorithm described in previous reports), and the clauses are simplified. Then,
+\textsc{Crane} is called on those clauses to evaluate the base cases. After
+that, we change the function names and variable to make it consistent with the
+previous domain to variable mapping, and append these base cases to the set of
+equations.
+
 \paragraph{Contributions.}
 \begin{itemize}
+  \item \Cref{sec:identifying}
+  \item \Cref{sec:simplifying}
   \item Converting the recursive equations into a C++ program, which can then be
@@
         Arithmetic Library.
+  \item The experiments are (going to be) more comprehensive than any other
+        experimental study performed on (W)FOMC algorithms (TODO: references to
+        my previous paper and some of the \textsc{ForcLift} and
+        \textsc{FastWFOMC} papers that contain experimental results).
 \end{itemize}
 
-\section{Snippets}
-
-\begin{itemize}
-  \item The evaluation of base cases is done by simplifying the clauses and then
-        using \textsc{Crane} to find the base cases. First, while traversing the
-        graph to find the equations, we store two maps objects:
-        \texttt{clause\_func\_map} (which stores the mapping from the function
-        names to the formulae, whose model count they represent) and
-        \texttt{var\_domain\_map} (which stores the mapping from the variable
-        names to the domains whose sizes they represent). Then, a particular
-        domain is selected (using the algorithm described in previous reports),
-        and the clauses are simplified. Then, \textsc{Crane} is called on those
-        clauses to evaluate the base cases. After that, we change the function
-        names and variable to make it consistent with the previous domain to
-        variable mapping, and append these base cases to the set of equations.
-  \item Finding a sufficient set of base cases. We know that if, say, on the RHS
-        of all equations, the domain size appears as
-        $m - c_1, m - c_2, \dots, m - c_k$, then finding
-        $f(0, x_1, x_2, \dots)$, $f(1, x_1, x_2, \dots)$,
-        $\dots f(m_0, x_1, x_2, \dots)$ for every function $f$, where
-        $m_0 = \max(c_1, c_2, \dots c_k) - 1$ forms a sufficient set of base
-        cases. Hence, in order to do the same efficiently, we can take that
-        domain for which $m_0$ is the minimum, i.e.
-        $\argmin(\max(c_1, c_2, \dots c_k))$.
-\end{itemize}
-
-\subsection{Bar}
-
-The previous method of base case evaluation on setting a domain to size zero or
-one had the following error. In case a domain size was set to zero, it assumed
-that those predicates which were deleted from the clauses could take any truth
-value over the entire domain and the rest were fully covered by the remaining
-clauses.
-
-For example, consider the formula
-\begin{equation}\label{eq:example}
-  \begin{split}
-    \forall x \in \Delta \forall y, z \in \Gamma &: P(x) \lor Q(y, z) \\
-    \forall y \in \Gamma^\top &: Q(y, z).
-  \end{split}
-\end{equation}
-In this case, if we set $|\Delta|$ to zero, the transformed formula would be
-\[
-  \forall y, z \in \Gamma^\top : Q(y, z),
-\]
-and the set of removed predicates is empty, and hence the model count returned
-would be $1$. However, the actual model count should be
-$2^{|\Gamma|^2 - |\Gamma^\top|^2}$.
-
-We solve this problem by converting clauses with universal quantifiers over the
-empty domain to tautologies, hence retaining all the predicates that have no
-argument assigned to the empty domain. For example, we would convert the above
-mentioned formula to
-\begin{align*}
-  \forall y, z \in \Gamma &: Q(y, z) \lor \neg Q(y, z) \\
-  \forall y, z \in \Gamma^\top &: Q(y, z)
-\end{align*}
-The model count returned by this will also consider the truth value of $Q$ over
-$y \not \in \Gamma^\top$ or $z \not \in \Gamma^\top$.
+\Cref{sec:identifying,sec:cpp} deal with algebraic constructs whereas
+\cref{sec:simplifying} deals with logic.
 
@@
 
-TODO: Introduce terms: left-hand side (LHS), right-hand side (RHS).
+\subsection{Algebra}
+
+\paragraph{Notation.}
+We write $\expr{}$ for an arbitrary algebraic expression. For any signature or
+clause $C$, argument or variable $x$, and number or constant $t$, we shall write
+$C[t / x]$ for the result of substituting $t$ for all occurrences of $x$ in $C$.
+% TODO: check if I'm still using this notation in all these cases
+% TODO: explain how this works for function calls too
 
@@
 
-\begin{remark}
-  The LHS of an equation is always a signature.
-\end{remark}
+\begin{definition}
+  An \emph{equation} is always of the form $f(\mathbf{x}) = \expr{}$, where
+  $f(\mathbf{x})$ is a signature, and $\expr{}$ is an algebraic expression.
+  Henceforth, we call $f(\mathbf{x})$ and $\expr{}$ the left-hand side (LHS) and
+  the right-hand side (RHS) of the equation, respectively.
+\end{definition}
+% TODO: give some examples of formulas that: 1) introduce new variables, 2) call
+% the function itself, 3) call some other function, 4) is more nested than just
+% a sum.
 
-For any signature or clause $C$, argument or variable $x$, and number or
-constant $t$, we shall write $C[t / x]$ for the result of substituting $t$ for
-all occurrences of $x$ in $C$.
-% TODO: check if I'm still using this notation in all these cases
-% TODO: explain how this works for function calls too
+\begin{definition}
+  A \emph{base case} is a function call where all arguments are either variables
+  or constants (i.e., there is no subtraction within any argument), and there is
+  at least one constant.
+\end{definition}
 
-\section{Identifying a Sufficient Set of Base Cases}
+\subsection{Logic}
+
+% TODO: what notation am I using for FOL? Colon after every quantifier?
+
+% TODO: (Similar to CNF, maybe QBF). Incomplete. Need (W)FOMC semantics. What is
+% an interpretation? What is a model?
+
+A \emph{formula} is a set of clauses. A \emph{clause} is of the form
+$\forall x_{1} \in \Delta_{1}\forall x_{2} \in \Delta_{2}\dots\forall x_{n} \in \Delta_{n} \phi(x_{1}, x_{2}, \dots, x_{n})$,
+where $\phi$ is a disjunction of literals that only contain variables
+$x_{1}, \dots, x_{n}$ (and any constants). A \emph{literal} is either an atom or
+its negation. An \emph{atom} is of the form $P(t_{1}, \dots, t_{m})$, where $P$
+is a predicate, and $t_{1}, \dots, t_{m}$ are terms. A \emph{term} is either a
+variable or a constant.
+% TODO: explain set-based notation for a clause (iterating over all literals,
+% maybe I should have a Lits() operator? No!!!)
+
+For any clause $C$, let $\Preds(C)$ denote the set of predicates in $C$. For any
+clause or literal $l$, let $\Vars(l)$ denote the set of variables in $l$.
+
+For any (bound) variable $v$, let $\Dom(v)$ denote the domain over which $v$ is
+quantified. For a literal $l$,
+$\Doms(l) \coloneqq \{\, \Dom(v) \mid v \in \Vars(l) \,\}$. Similarly, for any
+clause $C$, let $\Doms(C) = \{\, \Dom(v) \mid v \in \Vars(C) \,\}$.
+
+\section{The Main Algorithm: Finding the Definitions of the Base Cases}
 
 \begin{algorithm}[t]
-  \caption{Identifying a set of sufficient base cases}\label{alg1}
-  \KwIn{set $D$ of dependencies}
+  \caption{Finding the definitions of the base cases}\label{alg:main}
+  \KwIn{formula $\phi$}
+  \KwOut{a set $E$ of equations that define $B$}
+  $(E, \mathcal{F}, \mathcal{D}) \gets \Crane{$\phi$}$\;
+  \ForEach{base case $f(\mathbf{x}) \in \FindBaseCases{$E$}$}{
+    $\psi \gets \mathcal{F}(f)$\;
+    \ForEach{$i$ such that $x_{i}$ is a constant}{
+      $\psi \gets \Propagate{$\psi$, $\mathcal{D}(f, i)$, $x_i$}$\;
+    }
+    $(E', \textunderscore, \textunderscore) \gets \Crane{$\psi$}$\;
+    $E \gets E \cup E'$\;
+  }
+\end{algorithm}
+
+See \cref{alg:main}
+
+% TODO: extend it to work with base cases that are themselves recursive
+
+% TODO: what does it mean for a set of equations to define a set of base cases?
+
+% TODO: for base cases, we will also use the f(\mathbf{x}) notation
+
+\section{Identifying a Sufficient Set of Base Cases}\label{sec:identifying}
+
+\begin{algorithm}[t]
+  \caption{\protect\FindBaseCases{$E$}}\label{alg1}
+  \KwIn{set $E$ of equations}
   \KwOut{set $B$ of base cases}
@@
   $B \gets \emptyset$\;
-  \ForEach{$(f(\mathbf{x}), g(\mathbf{y} - \mathbf{c})) \in D$}{
+  \ForEach{equation $(f(\mathbf{x}) = \expr{}) \in E$}{
+    \ForEach{function call $g(\mathbf{y} - \mathbf{c}) \in \expr{}$}{\label{line:functioncall}
       \ForEach{$c_{i} \in \mathbf{c}$}{
@@
     }
+  }
 \end{algorithm}
 
+We know that if, say, on the RHS of all equations, the domain size appears as
+$m - c_1, m - c_2, \dots, m - c_k$, then finding $f(0, x_1, x_2, \dots)$,
+$f(1, x_1, x_2, \dots)$, $\dots f(m_0, x_1, x_2, \dots)$ for every function $f$,
+where $m_0 = \max(c_1, c_2, \dots c_k) - 1$ forms a sufficient set of base
+cases. Hence, in order to do the same efficiently, we can take that domain for
+which $m_0$ is the minimum, i.e. $\argmin(\max(c_1, c_2, \dots c_k))$. Ideally,
+we should calculate the base cases by finding the base cases up to
+$\max(c_{1}, c_{2}, \dots) - 1$. However, currently only empty and singleton
+domains are supported.
+
+\begin{itemize}
+  \item \cref{line:functioncall} iterates over all function calls in the
+        algebraic expression.
+  \item note that on \cref{line:signature} it is the signature and not the
+        original function call.
+\end{itemize}
+
+% TODO: remove the 'dependencies' data structure from the description
+
 The following steps were followed while finding the base cases:
-\begin{enumerate}
-  \item Expand the summations in each equation. Here we expand the summations of
-        the form:
-        $\sum_{x=0}^{x_{1}}<\textnormal{something}> \cdot [a \le x < b]$, or
-        similar inequalities where x is bounded by constants and $a$ and $b$ are
-        constants, by substituting the value of $x$ from $a$ to $b-1$. For
-        example, we replace
+
+First, expand the summations in each equation. Here we expand the summations of
+the form: $\sum_{x=0}^{x_{1}} \expr{} \cdot [a \le x < b]$ or similar
+inequalities where $x$ is bounded by constants and $a$ and $b$ are constants, by
+substituting the value of $x$ from $a$ to $b-1$. For example, we replace
 $\sum_{x=0}^{x_1} \binom{x_{1}}{x} f(x_1 - x) \cdot [0 \le x < 2]$ by
 $\binom{x_{1}}{0} f(x_1) + \binom{x_{1}}{1} f(x_1-1)$.
-  \item Next, we find the dependencies of those functions that appear on the
-        RHS of any equation. Consider, for example the following set
-        of equations:
+
+Now, we find a domain that has only terms of the form $x-1$ appearing on the RHS
+of the dependencies. The base cases are then calculated by setting this domain
+size to zero. For the above example, $n$ is the selected domain, and not $m$
+since there are $m-2$ and $m-3$ terms appearing in the arguments.
+
+The algorithm is described as \cref{alg1}.
+
+\begin{example}
+  TODO: add an example where \cref{alg1} runs on either
   \begin{align*}
@@
   \end{align*}
-        In this case, the dependencies computed are
+  or
   \begin{align*}
-          f_{1}(m, n) &\mapsto \{\, f_{1}(m-1, n-1), f_{2}(m, n-1) \,\}\\
-          f_{2}(m, n) &\mapsto \{\, f_{1}(m-3, n-1) \,\}
+    f(m, n) &= g(m-1, n) + f(m-2, n-1)\\
+    g(m, n) &= f(m-1, n-2) + g(m-1, n-1).
   \end{align*}
-  \item Now, we find a domain that has only terms of the form $x-1$ appearing on
-        the RHS of the dependencies. The base cases are then calculated by
-        setting this domain size to zero. For the above example, $n$ is the
-        selected domain, and not $m$ since there are $m-2$ and $m-3$ terms
-        appearing in the arguments.
-\end{enumerate}
-
-\paragraph{Limitations of the current implementation.} Ideally, we should
-calculate the base cases by finding the base cases up to
-$\max(c_{1}, c_{2}, \dots) - 1$. However, currently only empty and singleton
-domains are supported.
 
@@
     \item \cref{line:lim}: the limit is 2 for the arg $(x-3)$.
-  \item \cref{line:insert} for $f(\mathbf{x}) = f(x_{1}, x_{2})$,
-        $\text{arg} = x$, and $n = 0$, add $f(0, x_{2})$ to $B$.
-  \item note that on \cref{line:signature} it is the signature and not the
-        original function call.
+    \item \cref{line:insert} for $f(\mathbf{x}) = f(y, z)$, $x_{i} = y$, and
+          $n = 0$, add $f(y, z)[y/0] = f(0, z)$ to $B$.
   \end{itemize}
+\end{example}
 
-The algorithm is described as \cref{alg1}. Here, a dependency is a pair
-$(a, b)$, where $a$ is the signature on the LHS of each equation and $b$ is each
-function call on the RHS of the equation. For example, for the equations
+\section{Propagating Domain Size Assumptions}\label{sec:simplifying}
+
+\subsection{Motivation: Why Tautologies Are Needed and Simply Removing The
+  Clauses Does Not Work}
+
+\begin{fact}
+  Assuming that domain $\Delta$ is empty, any clause that contains
+  `$\forall x \in \Delta$' (for any variable $x$) is vacuously satisfied by all
+  interpretations.
+\end{fact}
+
+For example, consider the formula
+\begin{align}
+  \forall x \in \Delta \forall y, z \in \Gamma &: P(x) \lor Q(y, z)\label[formula]{eq:example1}\\
+  \forall y, z \in \Gamma' &: Q(y, z)\label[formula]{eq:example2}
+\end{align}
+and assume that $\Gamma' \subseteq \Gamma$. In this case, if we set $|\Delta|$
+to zero and remove clauses with variables quantified over $\Delta$, we get
+\begin{equation}\label[formula]{eq:simplified}
+  \forall y, z \in \Gamma' : Q(y, z),
+\end{equation}
+but the model count of \cref{eq:simplified} is one. However, the actual model
+count should be $2^{|\Gamma|^2 - |\Gamma'|^2}$. That is, $Q$ as a relation is a
+subset of $\Gamma \times \Gamma$. While \cref{eq:example1} becomes vacuously
+true, \cref{eq:example2} fixes the value of $Q$ over
+$\Gamma' \times \Gamma' \subseteq \Gamma \times \Gamma$. Hence, the number of
+different values that $Q$ can take is
+$|(\Gamma \times \Gamma) \setminus (\Gamma' \times \Gamma')| = |\Gamma|^{2} - |\Gamma'|^{2}$.
+
+We address this issue by converting clauses with universal quantifiers over the
+empty domain to tautologies, hence retaining all the predicates that have no
+argument assigned to the empty domain. For example, we would convert
+\cref{eq:example1,eq:example2} to
 \begin{align*}
-  f(m, n) &= g(m-1, n) + f(m-2, n-1)\\
-  g(m, n) &= f(m-1, n-2) + g(m-1, n-1)
+  \forall y, z \in \Gamma &: Q(y, z) \lor \neg Q(y, z) \\
+  \forall y, z \in \Gamma' &: Q(y, z).
 \end{align*}
-the dependencies are
-\begin{multline*}
-  (f(m, n), g(m - 1, n)), (f(m, n), f(m - 2, n - 1)),\\
-  (g(m, n), f(m - 1, n - 2), g(m - 1, n - 1)).
-\end{multline*}
+The model count returned by this will also consider the truth value of $Q$ over
+$y \in \Gamma \setminus \Gamma'$ or $z \in \Gamma \setminus \Gamma'$.
 
-\section{Algorithm to Transform CNF Based on Domain Sizes}
+\subsection{The Solution}
 
 \begin{algorithm}[t]
-  \caption{Transforming Formulas Based on Domain Sizes}\label{alg2}
-  \KwIn{formula $\phi$, domain $\Delta$, target domain size $n \in \{\, 0, 1 \,\}$, domain size function $|\cdot|$}
+  \caption{\protect\Propagate{$\phi$, $\Delta$, $n$}}\label{alg2}
+  \KwIn{formula $\phi$, domain $\Delta$, domain size $n \in \{\, 0, 1 \,\}$}
   \KwOut{formula $\phi'$}
-  $P^{-} \gets \emptyset$; $P^{+} \gets \emptyset$; $\phi' \gets \emptyset$\;
-  \uIf{$|\Delta| = 0$}{
+  $\phi' \gets \emptyset$\;
+  \uIf{$n = 0$}{
     \ForEach{clause $C \in \phi$}{
-      \uIf{$\Delta \in \Doms(C)$}{
-        $P^{-} \gets P^{-} \cup \Preds(C)$\;
+      \lIf{$\Delta \not\in \Doms(C)$}{$\phi' \gets \phi' \cup \{\, C \,\}$}
+      $C' \gets \{\, l \in C \mid \Delta \not\in \Doms(l) \,\}$\;
+      \If{$\Delta \in \Doms(C)$ {\bf and} $C' \ne \emptyset$}{
+        $l \gets \text{an arbitrary literal in } C'$\;
+        $\phi' \gets \phi' \cup \{\, C' \cup \{\, \neg l \,\} \,\} $\;
+      }% TODO: find the source code and check: 1) what we're doing with unit clauses, 2) whether we just randomly pick any literal to negate
+    }
   }
   \Else{
-        $P^{+} \gets P^{+} \cup \Preds(C)$\;
-        $\phi' \gets \phi' \cup \{\, C \,\}$\;
-      }
-    }
-    $P^{-} \gets P^{-} \setminus P^{+}$\;
-  }
-  \ElseIf{$|\Delta| = 1$}{
     $c \gets$ a new constant symbol\;
@@
 \end{algorithm}
-% TODO: the removed empty domains should be replaced by smoothing/tautological
-% constructions
-
-% TODO: either the target domain size or the domain size function needs to go
-
-\begin{itemize}
-  \item Formulas are in CNF. Formulas are (multi) sets of clauses.
-  \item $P^{-}$ --- removed predicates
-  \item $P^{+}$ --- retained predicates
-  \item $\phi'$ --- transformed version of $\phi$
-  \item $C'$ --- transformed version of clause $C$
-  \item For any clause $C$, let $\Doms(C)$, $\Preds(C)$, and $\Vars(C)$ denote
-        respectively the set of domains, predicates, and variables in $C$. For
-        any variable $v$, let $\Dom(v)$ denote its domain. Note that, for any
-        clause $C$, we have that
-        $\Doms(C) = \{\, \Dom(v) \mid v \in \Vars(C) \,\}$. Similarly, for any
-        predicate $P$, let $\Doms(P)$ denote the set of domains associated with
-        $P$.
-\end{itemize}
+% TODO: it would be easy to extend the second part to an arbitrary constant
 
@@
 the required base cases.
+
+\begin{itemize}
+  \item Similar to generalised domain recursion (what's the difference?).
+  \item Clauses where all literals have variables quantified over the empty
+        domain are still removed.
+  \item $C'$ is guaranteed to be non-empty.
+\end{itemize}
 
@@
 The target is to generate C++ code that can evaluate numerical values of the
-model counts based on the equations generated by \textsc{Crane}. There are two
-ways to do the same.
-\begin{enumerate}
-  \item Generate C++ code by traversing the FCG, similar to what is done in
-        \texttt{OutputVisitor.scala}.
-  \item Parse the equations generated by \textsc{Crane} after simplifying in
-        wolfram and then generate C++ code.
-\end{enumerate}
-
-The problem with the first approach is that, while generating base cases, the
-subsequent calls to \textsc{Crane} do not necessarily have the same meanings for
-the function arguments and the functions. For example, if
-$f_{1}(x_{0}, x_{1}, x_{2})$ represents the model count of a constrained formula
-$\phi$, where $f_{1}$ is an auxiliary formula and $x_{0} = |A|$, $x_{1} = |B|$,
-$x_{2} = |C|$, and $A$, $B$, $C$ are domains and we want to evaluate
-$f_{1}(0, x_{1}, x_{2})$ (i.e., set $|A| = 0$), then \textsc{Crane} may return
-the required model count as $f_{0}(x_{0}, x_{1})$, where $x_{0} = |B|$ and
-$x_{1} = |C|$. We will then need to translate this to $f_{1}(0, x_{1}, x_{2})$.
-Also, the second approach can be done in linear time in the length of the
-formula using
+model counts based on the equations generated by \textsc{Crane}. We achieve this
+by parsing the equations generated by \textsc{Crane}, simplifying them, and then
+generating C++ code. This approach can be done in linear time in the length of
+the formula using
 the
 \href{https://en.wikipedia.org/wiki/Shunting_yard_algorithm#:~:text=In%20computer%20science%2C%20the%20shunting,abstract%20syntax%20tree%20(AST).}{Shunting
-  Yard Algorithm}. Hence, we stick to the second approach.
-
-\subsection{Our Approach}
+  Yard Algorithm}.
 
@@
 \texttt{func} corresponding to equation $e$) is formed as follows.
-\begin{enumerate}
-  \item First, we check if the evaluation is already present in the cache. If
-        so, then we return the cache element. The cache accesses are done using
-        the \texttt{get\_elem} function (definition given in the example), which
-        resizes the cache if the accessed index is out of range.
-  \item If the element is absent, then we decide if the arguments corresponding
-        to $e$ or one of the functions corresponding to the base cases, based on
-        the value of the arguments. If it corresponds to the base cases, then we
-        directly call the base case function and return its value. Else, we
-        evaluate the value using the RHS, store the evaluated value in the cache
-        and return the evaluated value. Note that in this step, we only call the
-        base case function with one more constant argument that \texttt{func}.
-        For example, \texttt{f0(x, y)} would call \texttt{f0\_0x(y)} if
-        \texttt{x == 0} and \texttt{f0\_x0(x)} if \texttt{y == 0}.
-  \item In order to translate the RHS, we convert $\sum_{x=a}^{b} \texttt{exp}$
-        to
-\begin{lstlisting}
+
+First, we check if the evaluation is already present in the cache. If so, then
+we return the cache element. The cache accesses are done using the
+\texttt{get\_elem} function (definition given in the example), which resizes the
+cache if the accessed index is out of range.
+
+Second, if the element is absent, then we decide if the arguments corresponding
+to $e$ or one of the functions corresponding to the base cases, based on the
+value of the arguments. If it corresponds to the base cases, then we directly
+call the base case function and return its value. Else, we evaluate the value
+using the RHS, store the evaluated value in the cache and return the evaluated
+value. Note that in this step, we only call the base case function with one more
+constant argument than \texttt{func}. For example, \texttt{f0(x, y)} would call
+\texttt{f0\_0x(y)} if $x = 0$ and \texttt{f0\_x0(x)} if $y = 0$.
+
+Third, to translate the RHS, we convert $\sum_{x=a}^{b} \expr{}$ to
+\begin{lstlisting}[escapeinside={(*}{*)}]
 ([y,z,...](){
@@
     for(int x = a; x <= b; x++)
-        sum += exp;
+        sum += (*$\expr{}$*);
     return sum;
@@
 \end{lstlisting}
-        where $y, z, \dots$ are the free variables present in \texttt{exp}.
-\end{enumerate}
+where $y, z, \dots$ are the free variables present in $\expr{}$.
+
+\section{Experiments}
+
+\section{Conclusion}
 

### 2023-12-27 paper.tex
Some changes

@@
 \section{Introduction}
+
+An important change to the compilation algorithm. We make the FCGs satisfy the
+following property. For every domain $\Delta$, for every directed path $P$
+without Ref nodes, the number of atom counting or (generalised) domain recursion
+operations on $\Delta$ on $P$ is at most one.
 
@@
   \ForEach{equation $(f(\mathbf{x}) = \expr{}) \in E$}{
-    \ForEach{function call $g(\mathbf{y} - \mathbf{c}) \in \expr{}$}{\label{line:functioncall}
+    \ForEach{function call $f(\mathbf{x} - \mathbf{c}) \in \expr{}$}{\label{line:functioncall}
       \ForEach{$c_{i} \in \mathbf{c}$}{
@@
           $B \gets B \cup \{\, f(\mathbf{x})[x_{i}/n] \,\}$\;\label{line:insert}
-          \lIf{$f \ne g$}{$B \gets B \cup \{\, g(\mathbf{y})[y_{i}/n] \,\}$}\label{line:signature}
         }
@@
 \end{example}
+
+TODO: I changed the algorithm
+
+\begin{theorem}
+  Under the following assumptions, \cref{alg1} is guaranteed to return a
+  sufficient set of base cases:
+  \begin{itemize}
+    \item there is no mutual recursion (i.e., cyclic dependencies between
+          functions);
+    \item each function $f$ has exactly one equation with $f$ on the LHS;
+    \item in the recursive definition of function $f(x_{1},\dots,x_{n})$, the
+          $i$-th argument of each call to $f$ on the RHS is of the form
+          $x_{i} - c_{i}$, where:
+          \begin{itemize}
+            \item $c_{i} \ge 0$ for all $i$, and
+            \item $c_{i} > 0$ for at least one $i$.
+          \end{itemize}
+  \end{itemize}
+\end{theorem}
+
+\begin{example}
+  For an equation $f(m, n) = 2 \times f(m-1, n)$, \cref{alg1} returns $f(0, n)$.
+\end{example}
+
+NOTE: function calls such as $f(n-m)$ and $f(n-m-1)$ are ignored.
 

### 2023-12-27 fastwfomc/experiment.py

@@ -1,28 +1,0 @@
-import argparse
-import csv
-import random
-import time
-from collections import defaultdict
-
-from aima3.logic import to_cnf
-from aima3.utils import expr, Expr
-
-from wfomc_cc import WFOMCWithCC
-
-MAX_N = 50
-
-bijections = expr('(S1(x) | ~P(x, y)) & (S3(x) | ~P(y, x))')
-times = []
-ns = list(range(1, MAX_N + 1))
-random.shuffle(ns)
-for n in ns:
-    start_time = time.time()
-    counter = WFOMCWithCC(bijections, n, [('P', n)])
-    counter.get_wfomc({'S1': (1, -1), 'S3': (1, -1), 'P': (1, 1)})
-    entry = {'n': n, 'time': time.time() - start_time}
-    times.append(entry)
-with open('runtimes.csv', 'w') as csv_file:
-    writer = csv.DictWriter(csv_file, fieldnames=['n', 'time'])
-    writer.writeheader()
-    for row in times:
-        writer.writerow(row)

### 2024-01-04 paper.tex
Describe some changes to the compilation process

@@
 
-An important change to the compilation algorithm. We make the FCGs satisfy the
-following property. For every domain $\Delta$, for every directed path $P$
-without Ref nodes, the number of atom counting or (generalised) domain recursion
-operations on $\Delta$ on $P$ is at most one.
+% TODO: (in Fig. 1) Crane2 doesn't use Crane, it uses itself.
+
+\paragraph{Changes to the compilation process.}
+\begin{itemize}
+  \item We make the FCGs satisfy the following property. For every domain
+        $\Delta$, for every directed path $P$ without Ref nodes, the number of
+        atom counting or (generalised) domain recursion or independent partial
+        grounding operations on $\Delta$ on $P$ is at most one.
+  \item when checking whether recursion is possible between a source and a
+        target formula, the target formula (maybe the source formula as well?)
+        must not include a domain as well as its subdomain. This might be
+        equivalent to the formula being `unshattered'. Such formulas could be
+        seen as transitory, and allowing such recursive calls leads to FCGs that
+        I cannot make sense of.
+  \item During smoothing, when unit clauses (a.k.a.\ variables) are propagated
+        in the opposite direction of the FCG arcs (i.e., `upwards'), when
+        visiting a \texttt{Ref} node, these clauses are translated using the
+        domain map of the \texttt{Ref} node. For example, we might have a
+        function $g$ that depends on $m$ (i.e., domain $a^{\top}$), which is
+        called as $g(n)$ (i.e., on domain $a$). When smoothing that function
+        call, we want to translate all mentions of $a^{\top}$ to $a$.
+\end{itemize}
 

### 2024-01-26 doc/paper.tex
Some notes regarding the proof of correctness

--- 2024-01-04 paper.tex
@@
 
+% TODO: mention/describe the arithmetic simplification code
+
 % TODO: (in Fig. 1) Crane2 doesn't use Crane, it uses itself.
+
+% TODO: describe which compilation rules are currently greedy or non-greedy.
 
@@
 \end{itemize}
+
+\paragraph{Proof of Correctness}
+\begin{enumerate}
+  \item Define what it means for a formula to be \emph{consistent}.
+        \begin{itemize}
+          \item The formula (including the mapping of constants to their
+                domains) does not mention a domain together with its subdomain
+                (i.e., all mentioned domains are pairwise disjoint).
+                Specifically, we can't have a subdomain together with its parent
+                domain or a subdomain together with a constant that belongs to
+                its parent domain.
+          \item The target of \texttt{Ref} must also be a consistent formula.
+          \item The initial formula is consistent by definition.
+        \end{itemize}
+  \item Aim to show that Crane works correctly on all consistent formulas.
+  \item Prove that, whenever some compilation rule makes the formula $\phi$
+        inconsistent, greedy compilation rules will make $\phi$ consistent again
+        before $\phi$ encounters non-greedy compilation rules that depend on
+        $\phi$ being consistent.
+        \begin{itemize}
+          \item In particular, prove that shattering and unit propagation will
+                always eliminate the parent domain of the domains introduced by
+                atom counting.
+          \item Constraint removal only applies when it can eliminate the parent
+                domain entirely.
+          \item Prove this for a particular assumption about which compilation
+                rules are set to be greedy. For the greedy algorithm, although
+                all rules are applied in a greedy manner, we still assume that
+                greedy rules will be applied before non-greedy rules.
+        \end{itemize}
+  \end{enumerate}
 

### 2024-01-26 parse.py

@@ -15,6 +15,7 @@ with open('sequences.csv', newline='') as f:
 
 rows = []
 for filename in os.listdir(RESULTS_DIR):
+    print('Parsing', filename)
     data = {}
     data['sequence'], data['algorithm'] = filename.split('.')
     domains = []
@@ -36,16 +37,17 @@ for filename in os.listdir(RESULTS_DIR):
         sequence = sequences[int(data['sequence'][1:])]
         if correct and int(count) != sequence[int(domain)]:
             correct = False
-            print('Sequence {} is incorrect:'.format(data['sequence']))
+            print('Sequence {} (algorithm {}) is incorrect:'.format(data['sequence'], data['algorithm']))
             print('Original:', sequence)
             print('Computed: ', [int(x) for x in counts])
             print()
-
         new_data = data.copy()
         new_data['domain.size'] = domain
         new_data['count'] = count
         new_data['inference.time'] = time
         rows.append(new_data)
+    if correct:
+        print('Sequence {} (algorithm {}) is CORRECT'.format(data['sequence'], data['algorithm']))
 
 with open(RESULTS_FILE, 'w', encoding='UTF8', newline='') as f:
     writer = csv.DictWriter(f, fieldnames=FIELDNAMES)

### 2024-02-01 doc/paper.tex
Minor changes

@@
 \usepackage{tikz}
+\usepackage[backgroundcolor=lightgray]{todonotes}
 
@@
 
-% TODO: mention/describe the arithmetic simplification code
-
-% TODO: (in Fig. 1) Crane2 doesn't use Crane, it uses itself.
-
-% TODO: describe which compilation rules are currently greedy or non-greedy.
+\todo[inline,caption={}]{
+  \begin{itemize}
+    \item mention/describe the arithmetic simplification code
+    \item (in Fig. 1) Crane2 doesn't use Crane, it uses itself
+    \item describe which compilation rules are currently greedy or non-greedy
+  \end{itemize}
+}
 
@@
 
-\paragraph{Proof of Correctness}
+\paragraph{Proof of correctness.}
 \begin{enumerate}
@@
   \item The experiments are (going to be) more comprehensive than any other
-        experimental study performed on (W)FOMC algorithms (TODO: references to
-        my previous paper and some of the \textsc{ForcLift} and
-        \textsc{FastWFOMC} papers that contain experimental results).
+        experimental study performed on (W)FOMC algorithms.
 \end{itemize}
+
+\todo[inline]{references to my previous paper and some of the \textsc{ForcLift}
+  and \textsc{FastWFOMC} papers that contain experimental results}
 
@@
 $C[t / x]$ for the result of substituting $t$ for all occurrences of $x$ in $C$.
-% TODO: check if I'm still using this notation in all these cases
-% TODO: explain how this works for function calls too
+
+\todo[inline,caption={}]{
+  \begin{itemize}
+    \item check if I'm still using this notation in all these cases
+    \item explain how this works for function calls too
+  \end{itemize}
+}
 
@@
 \end{definition}
-% TODO: do I ever use this term for the case when some of the variables don't
-% exist?
+\todo[inline]{do I ever use this term for the case when some of the variables
+  don't exist?}
 
@@
 \end{definition}
-% TODO: give some examples of formulas that: 1) introduce new variables, 2) call
-% the function itself, 3) call some other function, 4) is more nested than just
-% a sum.
+\todo[inline,caption={}]{
+  give some examples of formulas that:
+  \begin{itemize}
+    \item introduce new variables,
+    \item call the function itself,
+    \item call some other function, and
+    \item is more nested than just a sum.
+  \end{itemize}
+}
 
@@
 
-% TODO: what notation am I using for FOL? Colon after every quantifier?
-
-% TODO: (Similar to CNF, maybe QBF). Incomplete. Need (W)FOMC semantics. What is
-% an interpretation? What is a model?
+\todo[inline,caption={}]{
+  \begin{itemize}
+    \item What notation am I using for FOL? Colon after every quantifier?
+    \item (Similar to CNF, maybe QBF). Incomplete. Need (W)FOMC semantics. What
+          is an interpretation? What is a model?
+  \end{itemize}
+}
 
@@
 variable or a constant.
-% TODO: explain set-based notation for a clause (iterating over all literals,
-% maybe I should have a Lits() operator? No!!!)
+
+\todo[inline]{explain set-based notation for a clause (iterating over all
+  literals)}
 
@@
     }
-    $(E', \textunderscore, \textunderscore) \gets \Crane{$\psi$}$\;
+    $(E', \text{\textunderscore}, \text{\textunderscore}) \gets \Crane{$\psi$}$\;
     $E \gets E \cup E'$\;
@@
 
-% TODO: extend it to work with base cases that are themselves recursive
-
-% TODO: what does it mean for a set of equations to define a set of base cases?
-
-% TODO: for base cases, we will also use the f(\mathbf{x}) notation
+\todo[inline,caption={}]{
+  \begin{itemize}
+    \item extend it to work with base cases that are themselves recursive
+    \item what does it mean for a set of equations to define a set of base cases?
+    \item for base cases, we will also use the $f(\mathbf{x})$ notation
+  \end{itemize}
+}
 
@@
 
+\todo[inline,caption={}]{
   \begin{itemize}
-  \item \cref{line:functioncall} iterates over all function calls in the
-        algebraic expression.
-  \item note that on \cref{line:signature} it is the signature and not the
-        original function call.
+    \item NOTE: \cref{line:functioncall} iterates over all function calls in the
+          algebraic expression
+    \item remove the `dependencies' data structure from the description
   \end{itemize}
-
-% TODO: remove the 'dependencies' data structure from the description
+}
 
@@
 
-\begin{example}
-  TODO: add an example where \cref{alg1} runs on either
+\todo[inline,caption={}]{
+  add an example where \cref{alg1} runs on either
   \begin{align*}
@@
   \end{align*}
+}
 
@@
 \end{itemize}
-\end{example}
 
-TODO: I changed the algorithm
+\todo[inline]{I changed the algorithm. Update the description.}
 
@@
 \end{algorithm}
-% TODO: it would be easy to extend the second part to an arbitrary constant
+
+\todo[inline]{it would be easy to extend the second part to an arbitrary constant}
 
@@
 
-% TODO: The report has some (long) examples of formulas being transformed into
-% programs perhaps suitable for supplementary material.
+\todo[inline]{the report has some (long) examples of formulas being transformed
+  into programs perhaps suitable for supplementary material}
 

### 2024-02-01 analyse.R

@@ -1,0 +1,5 @@
+df <- read.csv("results.csv")
+summary(df)
+
+n <- length(df$inference.time)
+sort(df$inference.time, decreasing = TRUE)

### 2024-02-01 parse.py

@@ -6,6 +6,7 @@ import os
 RESULTS_DIR = 'results'
 RESULTS_FILE = 'results.csv'
 FIELDNAMES = ['algorithm', 'sequence', 'domain.size', 'count', 'compilation.time', 'inference.time']
+TIMEOUT = 3600000
 
 sequences = {}
 with open('sequences.csv', newline='') as f:
@@ -28,18 +29,23 @@ for filename in os.listdir(RESULTS_DIR):
             elif line.startswith('The model count'):
                 tokens = line.split()
                 domains.append(tokens[7][:-1])
-                counts.append(tokens[8].translate({ord(','): None}))
-                times.append(tokens[10])
+                if tokens[8] == 'TIMEOUT':
+                    counts.append('')
+                    times.append(TIMEOUT)
+                else:
+                    counts.append(tokens[8].translate({ord(','): None}))
+                    times.append(tokens[10])
     assert len(domains) == len(counts)
     assert len(domains) == len(times)
+
     correct = True
     for (domain, count, time) in zip(domains, counts, times):
         sequence = sequences[int(data['sequence'][1:])]
-        if correct and int(count) != sequence[int(domain)]:
+        if count == '' or correct and int(count) != sequence[int(domain)]:
             correct = False
             print('Sequence {} (algorithm {}) is incorrect:'.format(data['sequence'], data['algorithm']))
             print('Original:', sequence)
-            print('Computed: ', [int(x) for x in counts])
+            print('Computed: ', [int(x) for x in counts if x != ''])
             print()
         new_data = data.copy()
         new_data['domain.size'] = domain

### 2024-02-10 parse.py
Ditto

@@ -15,8 +15,11 @@ with open('sequences.csv', newline='') as f:
         sequences[int(row['id'])] = [int(x) for x in row['sequence'].split(',')]
 
 rows = []
+incorrect_count = 0
+total_count = 0
 for filename in os.listdir(RESULTS_DIR):
-    print('Parsing', filename)
+    total_count += 1
+    # print('Parsing', filename)
     data = {}
     data['sequence'], data['algorithm'] = filename.split('.')
     domains = []
@@ -38,22 +41,23 @@ for filename in os.listdir(RESULTS_DIR):
     assert len(domains) == len(counts)
     assert len(domains) == len(times)
 
-    correct = True
+    sequence = [str(x) for x in sequences[int(data['sequence'][1:])][:len(counts) + 1]]
+    if not (counts == sequence[:-1] or counts == sequence[1:]):
+        incorrect_count += 1
+        print('Sequence {} (algorithm {}) is incorrect:'.format(data['sequence'], data['algorithm']))
+        print('Original:', [int(x) for x in sequence])
+        print('Computed: ', [int(x) for x in counts if x != ''])
+        print()
+
     for (domain, count, time) in zip(domains, counts, times):
-        sequence = sequences[int(data['sequence'][1:])]
-        if count == '' or correct and int(count) != sequence[int(domain)]:
-            correct = False
-            print('Sequence {} (algorithm {}) is incorrect:'.format(data['sequence'], data['algorithm']))
-            print('Original:', sequence)
-            print('Computed: ', [int(x) for x in counts if x != ''])
-            print()
         new_data = data.copy()
         new_data['domain.size'] = domain
         new_data['count'] = count
         new_data['inference.time'] = time
         rows.append(new_data)
-    if correct:
-        print('Sequence {} (algorithm {}) is CORRECT'.format(data['sequence'], data['algorithm']))
+
+print('Correct: {:.0f}% ({} out of {})'.format(100 * (total_count - incorrect_count) / total_count,
+                                               total_count - incorrect_count, total_count))
 
 with open(RESULTS_FILE, 'w', encoding='UTF8', newline='') as f:
     writer = csv.DictWriter(f, fieldnames=FIELDNAMES)

### 2024-02-14 doc/paper.tex
Ditto
Experimental setup for ForcLift (just for a linearly-increasing sequence of domains for now)

@@
     \item describe which compilation rules are currently greedy or non-greedy
+    \item my agenda has a plan for proving completeness for $\mathbf{C}^{2}$
   \end{itemize}
@@
         call, we want to translate all mentions of $a^{\top}$ to $a$.
+  \item Implemented an if-then-else arithmetic operation as the interpretation
+        of the new domain recursion node (i.e., there is one branch for when the
+        domain is empty and another branch for any other domain size).
+  \item Smoothing for domain recursion now works the same way as smoothing for
+        disjunction: both sides must have the same atoms. Almost all of
+        \cref{sec:simplifying} is now outdated because smoothing makes the
+        ``tautology insertion'' unnecessary.
+  \item \Cref{sec:main,sec:identifying} might also be outdated: there is
+        probably no need to search for base cases given the new version of
+        domain recursion.
 \end{itemize}
@@
         \end{itemize}
+  \item In particular, independent partial groundings and atom counting are the
+        two classical rules that require the formula to be shattered.
   \end{enumerate}
@@
 
-\section{The Main Algorithm: Finding the Definitions of the Base Cases}
+\section{The Main Algorithm: Finding the Definitions of the Base
+  Cases}\label{sec:main}
 
@@
 
+\paragraph{Remarks on comparing the model counts of the formulas with their
+  corresponding OEIS sequences.}
+Disregarding differences where the OEIS sequence starts with one or two numbers
+that are not included in model counts (which is somewhat justified since we
+start with domains of size one rather than zero), two differences remain:
+\begin{itemize}
+  \item on A62971, the OEIS sequence starts as $1, 2, 16,\dots$, but the model
+        counts start as $1, 16,\dots$ (with the rest exactly the same);
+  \item similarly, on A62971, the OEIS sequence starts as $32, 290,\dots$, but
+        the model counts start as $2, 32, 290,\dots$ (with the rest exactly the
+        same).
+\end{itemize}
+
 \section{Conclusion}

### 2024-02-14 Forclift/src/main/scala/edu/ucla/cs/starai/forclift/examples/MljSmokersExperiment.scala

@@ -1,0 +1,114 @@
+/*
+ * Copyright 2016 Guy Van den Broeck and Wannes Meert (UCLA and KU Leuven)
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+
+package edu.ucla.cs.starai.forclift.examples
+
+import java.io.File
+import util.Random
+import java.io.PrintWriter
+import edu.ucla.cs.starai.forclift._
+import edu.ucla.cs.starai.forclift.learning.LiftedLearning
+import edu.ucla.cs.starai.forclift.languages.mln.MLNParser
+import java.io.OutputStream
+import java.io.PrintStream
+
+object MljSmokersExperiment extends App {
+
+  val dir = new File("experiments/mlj-smokers")
+  dir.mkdirs()
+
+  val data = new PrintWriter(new File(dir, "timings.dat"))
+  data.printf("%10s %10s %10s %10s %10s %10s\n", "DomSize", "GradCalls",
+      "CountTime", "CompTime", "InfTime", "LearnTime")
+
+
+  for (size <- List(30000,2,2,2,2, 3, 4, 10, 20, 50, 100, 500, 1000, 5000, 10000, 15000, 20000, 25000, 30000)) {
+    println(s"Domain size is $size")
+
+    val structStr =
+s"""
+person = $size {}
+Smokes(person)
+Friends(person,person)
+
+!Friends(x,y) v !Smokes(x) v Smokes(y)
+"""
+
+    val structFile = new PrintWriter(new File(dir, s"struct-$size.mln"))
+    structFile.println(structStr)
+    structFile.close
+
+    val r = new Random
+    val trainingDBStr = {
+      val people = (1 to size)
+      // generate smokers
+      val smokers = r.shuffle(people).take((size*0.4).toInt)
+      val nonsmokers = people diff smokers
+      val smokesDb = smokers.map(s => {s"Smokes(P$s)"}).toSet
+      // generate friends
[…]

### 2024-02-14 Forclift/src/main/scala/edu/ucla/cs/starai/forclift/languages/focnf/FOCNFParser.scala

@@ -1,0 +1,304 @@
+/*
+ * Copyright 2016 Guy Van den Broeck and Wannes Meert (UCLA and KU Leuven)
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+
+package edu.ucla.cs.starai.forclift.languages.focnf
+
+import scala.collection._
+import scala.io._
+import edu.ucla.cs.starai.forclift._
+import edu.ucla.cs.starai.forclift.inference._
+import edu.ucla.cs.starai.forclift.languages.ModelParser
+
+
+class FOCNFParser extends ModelParser {
+
+  val domainMap = new mutable.HashMap[String, (RootDomain, mutable.HashSet[Constant], Int)]
+  // One entry per predicate name because in FOCNF we do not allow predicate overloading
+  val predicateMap = new mutable.HashMap[String, Predicate]
+  val weightMap = new mutable.HashMap[Predicate, Weights]
+  val varMap = new mutable.HashMap[String, Var]
+  val atomWeights = new mutable.ListBuffer[(Atom,Weights)]
+
+  def domainSizes: DomainSizes = {
+    val roots = domainMap.values.map {
+      case (k, v, s) =>
+        (k.asInstanceOf[Domain], DomainSize(s, k.asInstanceOf[Domain], v.toSet))
+    }
+    roots.toMap
+  }
+
+  def parseModel(theoryString: String): FOCNF = parse(theoryString)
+
+  def predicateWeights: PredicateWeights = weightMap.toMap
+  def predicateSet: Set[Predicate] = predicateMap.values.toSet.filterNot(_ == Predicate.eq)
+
+  def parseDomain(tokens:List[String], line_nbr:Int): List[Formula] = {
+    tokens match {
+      case "d" :: r_domain(name) :: r_int(size_str) :: constants_str => {
+        val size = size_str.toInt
+        val constants = constants_str.map{constant_str =>
[…]

### 2024-02-14 Forclift/src/main/scala/edu/ucla/cs/starai/forclift/languages/mln/MLNParser.scala

@@ -1,0 +1,943 @@
+/*
+ * Copyright 2016 Guy Van den Broeck and Wannes Meert (UCLA and KU Leuven)
+ *
+ * Licensed under the Apache License, Version 2.0 (the "License");
+ * you may not use this file except in compliance with the License.
+ * You may obtain a copy of the License at
+ *
+ *     http://www.apache.org/licenses/LICENSE-2.0
+ *
+ * Unless required by applicable law or agreed to in writing, software
+ * distributed under the License is distributed on an "AS IS" BASIS,
+ * WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+ * See the License for the specific language governing permissions and
+ * limitations under the License.
+ */
+
+package edu.ucla.cs.starai.forclift.languages.mln
+
+import java.io.{FileNotFoundException, IOException}
+
+import collection._
+import scala.util.parsing.combinator._
+import scala.io._
+import scala.math._
+import edu.ucla.cs.starai.forclift._
+import edu.ucla.cs.starai.forclift.util._
+import edu.ucla.cs.starai.forclift.inference._
+import edu.ucla.cs.starai.forclift.constraints._
+import edu.ucla.cs.starai.forclift.languages.ModelParser
+import edu.ucla.cs.starai.forclift.languages.StatRelModel
+
+/** Syntax used to output MLNs */
+final object FormulaSyntaxMLN extends FormulaSyntax {
+  final override val kwNegation = "!"
+  final override val kwConjunction = "^"
+  final override val kwDisjunction = "v"
+  final override val kwImplication = "=>"
+  final override val kwImplicationRev = "<="
+  final override val kwEquivalence = "<=>"
+  final override val kwWildcardNegation = "*"
+  final override val kwExistential = "EXIST"
+  final override val kwUniversal = "FORALL"
+}
+
+/**
+ * Parser for MLNs
+ *
+ * Operator precedence:
+ *
+ *  - Atomic operators: `!=`, `==`
+ *  - negation: `!` or wildcard negation: `*`
+ *  - conjunction: `^`
+ *  - disjunction: `v`
+ *  - implication: `=>`
+ *  - equivalence: `<=>`
+ *  - quantifiers: `FORALL`/`Forall`/`forall`, `EXISTS`/`Exists`/`exists`
+ *
+ * Structure of .mln file:
+ * {{{
+ * // Example MLN theory containing all of the syntax.
[…]

### 2024-02-14 forclift_wrapper.sh

@@ -1,0 +1,8 @@
+#!/usr/bin/env sh
+
+cd Forclift
+for ((i=1; i<=$1; i++)); do
+    echo "Domain size: $i"
+    sed -i "s/\.\.\.,[[:digit:]]\+/\.\.\.,$i/g" $2
+    ulimit -t $3 -c 0 && /usr/bin/time -f "Elapsed: %e" java -jar target/scala-2.11/crane-assembly-1.0.jar -z --format-in mln $2 || exit 1
+done

### 2024-02-14 parse.py

@@ -19,17 +19,18 @@ incorrect_count = 0
 total_count = 0
 for filename in os.listdir(RESULTS_DIR):
     total_count += 1
-    # print('Parsing', filename)
+    print('Parsing', filename)
     data = {}
     data['sequence'], data['algorithm'] = filename.split('.')
     domains = []
     counts = []
     times = []
+    total_times = []
     with open(RESULTS_DIR + '/' + filename) as f:
         for line in f.readlines():
-            if line.startswith('Compilation time:'):
+            if line.startswith('Compilation time:'): # Crane
                 data['compilation.time'] = line.split()[2]
-            elif line.startswith('The model count'):
+            elif line.startswith('The model count'): # Crane
                 tokens = line.split()
                 domains.append(tokens[7][:-1])
                 if tokens[8] == 'TIMEOUT':
@@ -38,22 +39,50 @@ for filename in os.listdir(RESULTS_DIR):
                 else:
                     counts.append(tokens[8].translate({ord(','): None}))
                     times.append(tokens[10])
+            elif line.startswith('Domain size:'): # ForcLift
+                domains.append(line.split()[2])
+            elif line.startswith('Z = '): # ForcLift
+                counts.append(int(round(float(line.split()[4]))))
+            elif line.startswith('Inference took'): # ForcLift
+                times.append(line.split()[2])
+            elif line.startswith('Elapsed:'): # ForcLift
+                total_times.append(float(line.split()[1]) * 1000)
+
+    # If the algorithm fails to compile, output no domains
+    if len(domains) == 1:
+        domains = []
+        total_times = []
+
+    print('Domains:', domains)
+    print('Counts:', counts)
+    if len(total_times) > 0:
+        print('Total runtimes:', total_times)
+    print()
+
     assert len(domains) == len(counts)
     assert len(domains) == len(times)
+    assert len(total_times) == 0 or len(total_times) == len(domains)
 
-    sequence = [str(x) for x in sequences[int(data['sequence'][1:])][:len(counts) + 1]]
-    if not (counts == sequence[:-1] or counts == sequence[1:]):
-        incorrect_count += 1
-        print('Sequence {} (algorithm {}) is incorrect:'.format(data['sequence'], data['algorithm']))
-        print('Original:', [int(x) for x in sequence])
-        print('Computed: ', [int(x) for x in counts if x != ''])
-        print()
+    # Check correctness of Crane
[…]

### 2024-02-16 analyse.R
The beginnings of some data-plotting code

@@ -1,5 +1,114 @@
-df <- read.csv("results.csv")
-summary(df)
+library(tidyverse)
+library(scales)
 
-n <- length(df$inference.time)
-sort(df$inference.time, decreasing = TRUE)
+TIMEOUT <- 60
+breaks <- c(0.3, 1, 3, 10, 30, 60) # TODO: update this and TIMEOUT later
+df <- read.csv("results.csv")
+df$algorithm[df$algorithm == "bfs"] <- "Crane-BFS" # TODO: make these \textsc{}
+df$algorithm[df$algorithm == "greedy"] <- "Crane-Greedy"
+df$algorithm[df$algorithm == "forclift"] <- "ForcLift"
+algorithms <- sort(unique(df$algorithm))
+
+# Random stuff
+# summary(df)
+# n <- length(df$inference.time)
+# sort(df$inference.time, decreasing = TRUE)
+
+# Functions
+scatter <- function(data, x_var, y_var) {
+  limits <- c(min(df$compilation.time), TIMEOUT)
+  ggplot(data, aes(.data[[x_var]], .data[[y_var]])) +
+    geom_count() +
+    scale_size_area() +
+    geom_abline(slope = 1, intercept = 0, colour = "#989898") +
+    scale_x_continuous(trans = log10_trans(), breaks = breaks, labels = breaks,
+                       limits = limits) +
+    scale_y_continuous(trans = log10_trans(), breaks = breaks, labels = breaks,
+                       limits = limits) +
+    coord_fixed() +
+    annotation_logticks(colour = "#b3b3b3") +
+    theme_light(base_size = 9) +
+    theme(legend.title=element_blank()) +
+    scale_size_continuous(breaks = round)
+} # TODO (later): have the same legend for all scatter plots
+
+cumulative_plot <- function(df) {
+  times <- vector(mode = "list", length = length(algorithms))
+  names(times) <- algorithms
+  for (algorithm in algorithms) {
+    times[[algorithm]] <- unique(df$time[df$algorithm == algorithm])
+  }
+
+  chunks <- vector(mode = "list", length = length(algorithms))
+  names(chunks) <- algorithms
+  for (algorithm in algorithms) {
+    chunks[[algorithm]] <- cbind(times[[algorithm]], algorithm,
+                             unlist(times[[algorithm]] %>%
+                                      map(function(x)
+                                        sum(df$time[df$algorithm == algorithm]
+                                            <= x))))
+  }
+
[…]

### 2024-03-04 doc/paper.tex
The beginnings of some data-plotting code
Writing about smoothing

@@
         I cannot make sense of.
-  \item During smoothing, when unit clauses (a.k.a.\ variables) are propagated
-        in the opposite direction of the FCG arcs (i.e., `upwards'), when
-        visiting a \texttt{Ref} node, these clauses are translated using the
-        domain map of the \texttt{Ref} node. For example, we might have a
-        function $g$ that depends on $m$ (i.e., domain $a^{\top}$), which is
-        called as $g(n)$ (i.e., on domain $a$). When smoothing that function
-        call, we want to translate all mentions of $a^{\top}$ to $a$.
   \item Implemented an if-then-else arithmetic operation as the interpretation
@@
         domain is empty and another branch for any other domain size).
-  \item Smoothing for domain recursion now works the same way as smoothing for
-        disjunction: both sides must have the same atoms. Almost all of
-        \cref{sec:simplifying} is now outdated because smoothing makes the
-        ``tautology insertion'' unnecessary.
   \item \Cref{sec:main,sec:identifying} might also be outdated: there is
@@
         Arithmetic Library.
-  \item The experiments are (going to be) more comprehensive than any other
-        experimental study performed on (W)FOMC algorithms.
+  \item A new set of benchmarks.
+  \item The experiments for Crane and ForcLift are (going to be) more
+        comprehensive than any other experimental study performed on (W)FOMC
+        algorithms.
+  \item Some experiments vs FastWFOMC
+  \item A proof of correctness
+  \item A proof of completeness
 \end{itemize}
@@
 clause $C$, let $\Doms(C) = \{\, \Dom(v) \mid v \in \Vars(C) \,\}$.
+
+\section{Smoothing}
+
+Goal of smoothing: whenever rules such as unit propagation or
+inclusion-exclusion (maybe just these two?) eliminate the consideration of some
+ground atoms, smoothing nodes should be inserted `at the same level' so that
+these ground atoms are still considered when counting. Note that conjunction
+nodes are irrelevant here because multiplication is associative. `At the same
+level' means that, e.g., if some ground atoms were eliminated from consideration
+before/after performing independent partial grounding, then the smoothing node
+should also appear before/after the independent partial grounding node.
+
+\todo[inline]{ Can I prove that the additions to smoothing outlined in the rest
+  of this section `do the right thing'? }
+
+\subsection{Stage 1: Propagating Unit Clauses `Upwards'}
+
+\begin{description}
+  \item[\texttt{Ref}:] during smoothing, when unit clauses (a.k.a.\ variables)
+        are propagated in the opposite direction of the FCG arcs (i.e.,
+        `upwards'), when visiting a \texttt{Ref} node, these clauses are
+        translated using the domain map of the \texttt{Ref} node. For example,
+        if the domain map include $\Delta \mapsto \Delta'$, and the unit clause
+        mentions $\Delta$, then replace it by $\Delta'$.
+  \item[Constraint removal:] do reverse constraint removal. Assuming that
+        domain $\Delta$ with constraints $X \ne c$ (for some constant
+        $c \in \Delta$) were replaced with domain $\Delta'$, replace each
+        $\forall X \in \Delta'\text{. }\phi(X)$ with
+        $\forall X \in \Delta\text{. }X \ne c \Rightarrow \phi(X)$.
+  \item[Domain recursion:] nothing special needs to be done (just propagate the
+        union of the two sets of unit clauses upwards), assuming that $P(c)$ and
+        $\forall X \in \Delta\text{. }X \ne c \Rightarrow P(X)$ are
+        automatically combined into $\forall X \in \Delta\text{. }P(X)$.
+\end{description}
+
+\subsection{Stage 2: Adding Smoothing Nodes}
+
+\begin{description}
+  \item[\texttt{Ref}:] nothing.
+  \item[Constraint removal:] nothing.
+  \item[Domain recursion:] Smoothing for domain recursion now works the same way
+        as smoothing for disjunction: both sides must have the same atoms EXCEPT
+        the `base case' side need not include unit clauses that mention the
+        constant introduced by this domain recursion node or its domain (since
+        this branch assumes that this domain is empty). NOTE: As a consequence,
+        almost all of \cref{sec:simplifying} is now outdated because smoothing
+        makes the ``tautology insertion'' unnecessary.
+\end{description}
 

### 2024-03-07 doc/paper.tex
Minor changes

@@
     \item my agenda has a plan for proving completeness for $\mathbf{C}^{2}$
+    \item Can I prove that Crane's domain recursion can always simulate
+          ForcLift's domain recursion?
   \end{itemize}
@@
 
-\section{Smoothing}
+\section{Smoothing (only relevant for domain recursion v3)}
 
@@
 
-\todo[inline]{ Can I prove that the additions to smoothing outlined in the rest
-  of this section `do the right thing'? }
+\todo[inline,caption={}]{
+  \begin{itemize}
+    \item Can I prove that the additions to smoothing outlined in the rest of
+          this section `do the right thing'?
+    \item I could include more info about the smoothing algorithm that didn't
+          make it into the previous paper.
+  \end{itemize}
+}
 
@@
         $\forall X \in \Delta\text{. }X \ne c \Rightarrow \phi(X)$.
-  \item[Domain recursion:] nothing special needs to be done (just propagate the
-        union of the two sets of unit clauses upwards), assuming that $P(c)$ and
-        $\forall X \in \Delta\text{. }X \ne c \Rightarrow P(X)$ are
-        automatically combined into $\forall X \in \Delta\text{. }P(X)$.
+  \item[Domain recursion:] we merge $P(c)$ and $\forall X \in \Delta\text{.
+        }X \ne c \Rightarrow P(X)$ into $\forall X \in \Delta\text{. }P(X)$.
+        NOTE: the clauses may have other constraints, variables, etc. I could
+        describe this more formally.
 \end{description}

### 2024-03-07 analyse.R

@@ -80,12 +80,20 @@ df$compilation.time[is.na(df$compilation.time)] <- TIMEOUT
 df$inference.time[is.na(df$inference.time)] <- TIMEOUT
 rm(df2)
 
+# Sanity check: are all combinations in the table?
+nrow(df) == n_distinct(df$algorithm) * n_distinct(df$sequence) *
+  n_distinct(df$domain.size)
+
 # Sanity check: do the counts match (should return an empty tibble)?
+# TODO: require Crane-BFS and Crane-Greedy answers to match and
+# show ForcLift relative error
 df %>% group_by(sequence, domain.size) %>%
   filter(min(count, na.rm = TRUE) != max(count, na.rm = TRUE))
 
 # Part 0: success rates per algorithm
 # TODO: along with 'total', add 'uniquely' and 'fastest' columns
+# NOTE: the first number is the number of benchmarks that were solved by at
+# least one algorithm (out of 155)
 length(unique(df$sequence))
 df[df$compilation.time < TIMEOUT,] %>% group_by(algorithm) %>%
   summarize(total = n_distinct(sequence))
@@ -105,8 +113,9 @@ cumulative_plot(df2)
 # size that all algorithms could handle)
 # TODO: unfinished, but the experimental data is not complete enough to
 # properly test this (do both scatter and cumulative plots like above)
-df[!is.na(df$count),] %>% group_by(sequence) %>%
+df2 <- df[!is.na(df$count),] %>% group_by(sequence) %>%
   filter(domain.size == max(domain.size))
+cumulative_plot(df2)
 
 # TODO Part 3: for each algorithm and instance, find the degree of the
 # polynomial that best matches the increase in inference time (use that

### 2024-03-07 parse.py

@@ -1,5 +1,6 @@
 #!/usr/bin/env python3
 
+from collections import defaultdict
 import csv
 import os
 
@@ -7,6 +8,7 @@ RESULTS_DIR = 'results'
 RESULTS_FILE = 'results.csv'
 FIELDNAMES = ['algorithm', 'sequence', 'domain.size', 'count', 'compilation.time', 'inference.time']
 TIMEOUT = 3600000
+VERBOSE = False
 
 sequences = {}
 with open('sequences.csv', newline='') as f:
@@ -16,10 +18,10 @@ with open('sequences.csv', newline='') as f:
 
 rows = []
 incorrect_count = 0
-total_count = 0
+failed_count = defaultdict(lambda: 0)
 for filename in os.listdir(RESULTS_DIR):
-    total_count += 1
-    print('Parsing', filename)
+    if VERBOSE:
+        print('Parsing', filename)
     data = {}
     data['sequence'], data['algorithm'] = filename.split('.')
     domains = []
@@ -42,7 +44,12 @@ for filename in os.listdir(RESULTS_DIR):
             elif line.startswith('Domain size:'): # ForcLift
                 domains.append(line.split()[2])
             elif line.startswith('Z = '): # ForcLift
-                counts.append(int(round(float(line.split()[4]))))
+                try:
+                    counts.append(int(round(float(line.split()[4]))))
+                except ValueError: # Record 'NaN' as a compilation error
+                    domains = []
+                    total_times = []
+                    break
             elif line.startswith('Inference took'): # ForcLift
                 times.append(line.split()[2])
             elif line.startswith('Elapsed:'): # ForcLift
@@ -52,12 +59,15 @@ for filename in os.listdir(RESULTS_DIR):
     if len(domains) == 1:
         domains = []
         total_times = []
+    if len(domains) == 0:
+        failed_count[data['algorithm']] += 1
 
-    print('Domains:', domains)
-    print('Counts:', counts)
-    if len(total_times) > 0:
-        print('Total runtimes:', total_times)
-    print()
+    if VERBOSE:
+        print('Domains:', domains)
+        print('Counts:', counts)
+        if len(total_times) > 0:
+            print('Total runtimes:', total_times)
+        print()
 
     assert len(domains) == len(counts)
     assert len(domains) == len(times)
@@ -85,8 +95,13 @@ for filename in os.listdir(RESULTS_DIR):
             new_data['compilation.time'] = total_times[i] - float(times[i])
         rows.append(new_data)
 
[…]

### 2024-03-20 doc/paper.tex
Prepare for KR

@@
 
-\usepackage{ijcai23}
+\usepackage{kr}
 
+% Use the postscript times font!
 \usepackage{times}
@@
 \usepackage{booktabs}
-\usepackage[switch]{lineno}
+%\usepackage{algorithm}
+%\usepackage{algorithmic}
+\urlstyle{same}
 
+\usepackage[backgroundcolor=lightgray]{todonotes}
 \usepackage{listings}
@@
 \usepackage{microtype}
-\usepackage{amsfonts}
 \usepackage{mathtools}
-\usepackage{tikz}
-\usepackage[backgroundcolor=lightgray]{todonotes}
+\usepackage{forest}
 
-% Comment out this line in the camera-ready submission
-\linenumbers
-
-\urlstyle{same}
-
-% the following package is optional:
-%\usepackage{latexsym}
+\usetikzlibrary{arrows.meta}
+\usetikzlibrary{positioning}
+\usetikzlibrary{shapes}
+\usetikzlibrary{fit}
 
@@
 \newtheorem{fact}{Fact}
+% TODO: fix styling, check if everything in the header is still needed
+% TODO: make sure forest arrows match non-forest arrows
 
-% PDF Info Is REQUIRED.
-% Please **do not** include Title and Author information
 \pdfinfo{
-/TemplateVersion (IJCAI.2023.0)
+/TemplateVersion (KR.2022.0, KR.2023.0, KR.2024.0)
+}
+
+\forestset{
+sn edges/.style={for tree={edge={-Latex}}}
 }
@@
 \DeclareMathOperator*{\argmin}{argmin}
+\DeclareMathOperator{\GDR}{GDR}
+
 \newcommand{\expr}{\mathtt{expr}}
+\newcommand{\FOtwo}{$\mathsf{FO}^{2}$}
 
@@
 
-\usetikzlibrary{arrows.meta}
-\usetikzlibrary{positioning}
-\usetikzlibrary{shapes}
-\usetikzlibrary{fit}
+\title{TBD}
 
-\title{Towards Practical First-Order Model Counting}
-
-% \author{
-% First Author$^1$
-% \and
+% \author{%
+% First Author$^1$\and
 % Second Author$^2$\and
-% Third Author$^{2,3}$\And
-% Fourth Author$^4$
+% Third Author$^{2,3}$\and
+% Fourth Author$^4$ \\
 % \affiliations
@@
 % $^3$Third Affiliation\\
-% $^4$Fourth Affiliation
+% $^4$Fourth Affiliation \\
 % \emails
@@
 
-% <= 200 words
 \begin{abstract}
@@
 
-\paragraph{Proof of correctness.}
+\paragraph{Proof of correctness (leave for later).}
 \begin{enumerate}
@@
 
-    \draw[->] (formula) -- (alg1);
-    \draw[->] (alg1) -- node[above] {$E$} (simplification);
-    \draw[->] (simplification) -- node[above] {$E'$} (compilation);
-    \draw[->] (compilation) -- (cpp);
-    \draw[->] (sizes) -- (cpp);
-    \draw[->] (cpp) -- (count);
+    \draw[-Latex] (formula) -- (alg1);
+    \draw[-Latex] (alg1) -- node[above] {$E$} (simplification);
+    \draw[-Latex] (simplification) -- node[above] {$E'$} (compilation);
+    \draw[-Latex] (compilation) -- (cpp);
+    \draw[-Latex] (sizes) -- (cpp);
+    \draw[-Latex] (cpp) -- (count);
 
-    \draw[->,dashed] (alg1) -- node[midway,left] {uses} (crane);
-    \draw[->,dashed] (alg1) -- node[midway] {uses} (alg2);
-    \draw[->,dashed] (alg1) -- node[midway,right] {uses} (alg3);
+    \draw[-Latex,dashed] (alg1) -- node[midway,left] {uses} (crane);
+    \draw[-Latex,dashed] (alg1) -- node[midway] {uses} (alg2);
+    \draw[-Latex,dashed] (alg1) -- node[midway,right] {uses} (alg3);
   \end{tikzpicture}
@@
 
-\paragraph{Contributions.}
+\paragraph{Contributions (outdated).}
 \begin{itemize}
@@
 clause $C$, let $\Doms(C) = \{\, \Dom(v) \mid v \in \Vars(C) \,\}$.
+
+\section{Theoretical Results}
+
+\begin{theorem}
+  The domain recursion by Dilkas and Belle~\shortcite{DBLP:conf/kr/DilkasB23}
+  can simulate the domain recursion by Van den
+  Broeck~\shortcite{DBLP:conf/nips/Broeck11}. This proves that Crane can (still)
+  handle \FOtwo.
+\end{theorem}
+
+\begin{figure}
+  \centering
+  \begin{forest}
+    for tree={sn edges}
+    [$\land_{r}$,circle,draw,name=dr
+    [$n_{r}$],
+    [$n_{x}$]
+    ]
+    \draw[-Latex] (dr) to [loop right] node {$\Delta \gets \Delta \setminus \{\,x\,\}$} ();
+  \end{forest}
+  \begin{forest}
+    for tree={sn edges}
+    [$\GDR(x \in \Delta)$,ellipse,draw,
+    [$\land$,circle,draw,
+    [$\bigwedge_{y \in \Delta}$,ellipse,draw]
+    [$\land$,circle,draw]
+    ]
+    ]
+  \end{forest}
+\end{figure}
+
+\begin{proof}
+  `A theory allows for domain recursion when the theory is shattered, the theory
+  contains no independent subtheories, and there exists a root binding class.'
+
+  Stuck on some weird cases. Need to prove that the model count of $n_{x}$ will
+  never depend on $|\Delta|$.
+\end{proof}
 
@@
 
-\bibliographystyle{named}
+\bibliographystyle{kr}
 \bibliography{paper}

### 2024-04-01 doc/paper.tex
Focus on a smaller set of benchmarks

@@
 \begin{description}
-  \item[\texttt{Ref}:] during smoothing, when unit clauses (a.k.a.\ variables)
+  \item[\texttt{Ref}.] During smoothing, when unit clauses (a.k.a.\ variables)
         are propagated in the opposite direction of the FCG arcs (i.e.,
@@
         mentions $\Delta$, then replace it by $\Delta'$.
-  \item[Constraint removal:] do reverse constraint removal. Assuming that
+  \item[Constraint removal.] Do reverse constraint removal. Assuming that
         domain $\Delta$ with constraints $X \ne c$ (for some constant
@@
         $\forall X \in \Delta\text{. }X \ne c \Rightarrow \phi(X)$.
-  \item[Domain recursion:] we merge $P(c)$ and $\forall X \in \Delta\text{.
-        }X \ne c \Rightarrow P(X)$ into $\forall X \in \Delta\text{. }P(X)$.
-        NOTE: the clauses may have other constraints, variables, etc. I could
-        describe this more formally.
+  \item[Domain recursion.] Suppose the domain recursion node introduces constant
+        $x \in \Delta$. For each unit clause received from the child node,
+        replace each occurrence of $\phi(x)$ or $\forall X \in \Delta\text{.
+        } X \ne x \Rightarrow \phi(X)$ with $\forall X \in \Delta\text{.
+        }\phi(X)$. This can be seen as a claim about what ground atoms the
+        domain recursion node \emph{should} cover (or a temporary assumption).
+        If the relevant subgraph indeed covers those ground atoms, Stage~2 will
+        do nothing. Otherwise, smoothing nodes will be added below the domain
+        recursion node to cover the difference between what was propagated from
+        the domain recursion node and what was received from the child node.
 \end{description}
+\todo[inline]{Add examples of both cases, with figures.}
 
 \subsection{Stage 2: Adding Smoothing Nodes}
+
+% TODO
+% \item Whenever the set of unit clauses received from the child node contains two
+% formulas $\phi(x)$ and $\forall X \in \Delta\text{.
+% } X \ne x \Rightarrow \phi(X)$ (i.e., the only difference between the two
+% formulas is that one has the constant $x$ whereas the other one has a variable
+% $X \ne x$), merge them into $\forall X \in \Delta\text{. }\phi(X)$.
 
@@
   \item[Constraint removal:] nothing.
-  \item[Domain recursion:] Smoothing for domain recursion now works the same way
-        as smoothing for disjunction: both sides must have the same atoms EXCEPT
-        the `base case' side need not include unit clauses that mention the
-        constant introduced by this domain recursion node or its domain (since
-        this branch assumes that this domain is empty). NOTE: As a consequence,
-        almost all of \cref{sec:simplifying} is now outdated because smoothing
-        makes the ``tautology insertion'' unnecessary.
+  \item[Domain recursion:]
+        \begin{enumerate}
+          \item Whenever the set of unit clauses of the child node contains two
+                formulas $\phi(x)$ and $\forall X \in \Delta\text{.
+                } X \ne x \Rightarrow \phi(X)$ (i.e., the only difference
+                between the two formulas is that one has the constant $x$
+                whereas the other one has a variable $X \ne x$), merge them into
+                $\forall X \in \Delta\text{. }\phi(X)$.
+          \item Add smoothing nodes below the domain recursion node for the
+                difference between the unit clauses assigned to the domain
+                recursion node during Stage 1 and the unit clauses of the child
+                node post-processed by the step above. For example, if the child
+                node `covers' only $p(x)$, then Stage 1 assigns
+                $\forall X \in \Delta\text{. }p(X)$ to the domain recursion
+                node. The smoothing node below the domain recursion node then
+                has the clause $\forall X \in \Delta\text{.
+                } X \ne x \Rightarrow p(X)$.
+        \end{enumerate}
 \end{description}
+
+\todo[inline]{Can I formally define what is meant by `difference'?}
 

### 2024-04-01 fastwfomc/python-flint-0.5.0/src/flint/types/fmpz_poly.pyx

@@ -1,0 +1,597 @@
+from cpython.int cimport PyInt_AS_LONG
+from cpython.list cimport PyList_GET_SIZE
+from cpython.long cimport PyLong_Check
+from cpython.int cimport PyInt_Check
+
+from flint.flint_base.flint_context cimport getprec
+from flint.flint_base.flint_base cimport flint_poly
+from flint.utils.typecheck cimport typecheck
+from flint.types.fmpz cimport fmpz_set_python
+from flint.types.fmpz cimport any_as_fmpz
+from flint.types.fmpz cimport fmpz
+from flint.types.fmpq cimport any_as_fmpq
+from flint.types.fmpq cimport fmpq
+from flint.types.fmpq_poly cimport fmpq_poly
+from flint.types.fmpq_poly cimport any_as_fmpq_poly
+from flint.types.acb cimport acb
+from flint.types.arb cimport any_as_arb_or_notimplemented
+from flint.types.arb cimport arb
+from flint.types.acb cimport any_as_acb_or_notimplemented
+cimport libc.stdlib
+from flint.flintlib.fmpz cimport fmpz_init, fmpz_clear, fmpz_set
+from flint.flintlib.fmpz cimport fmpz_is_one, fmpz_equal_si, fmpz_equal
+from flint.flintlib.acb_modular cimport *
+from flint.flintlib.ulong_extras cimport n_is_prime
+from flint.flintlib.fmpz_poly cimport *
+from flint.flintlib.fmpz_poly_factor cimport *
+from flint.flintlib.arith cimport *
+from flint.flintlib.acb cimport *
+from flint.flintlib.arb_poly cimport *
+from flint.flintlib.arb_fmpz_poly cimport *
+
+cdef any_as_fmpz_poly(x):
+    cdef fmpz_poly res
+    if typecheck(x, fmpz_poly):
+        return x
+    elif typecheck(x, fmpz):
+        res = fmpz_poly.__new__(fmpz_poly)
+        fmpz_poly_set_fmpz(res.val, (<fmpz>x).val)
+        return res
+    elif PyLong_Check(x):
+        res = fmpz_poly.__new__(fmpz_poly)
+        t = fmpz(x)
+        fmpz_poly_set_fmpz(res.val, (<fmpz>t).val)
+        return res
+    return NotImplemented
+
+cdef fmpz_poly_set_list(fmpz_poly_t poly, list val):
+    cdef long i, n
[…]

### 2024-04-01 fastwfomc/python-flint/bin/build_dependencies_unix.sh

@@ -1,364 +1,0 @@
-#!/usr/bin/env bash
-#
-# Build local installs of python-flint's dependencies. This should be run
-# before attempting to build python-flint itself.
-
-set -o errexit
-
-# ------------------------------------------------------------------------- #
-#                                                                           #
-# Supported options:                                                        #
-#                                                                           #
-# --gmp gmp         - build based on GMP (default)                          #
-# --gmp mpir        - build based on MPIR (no longer works)                 #
-# --host <HOST>     - set the host (target) for GMP build                   #
-# --patch-gmp-arm64 - apply patch to GMP for OSX arm64                      #
-#                                                                           #
-# ------------------------------------------------------------------------- #
-
-SKIP_GMP=no
-SKIP_MPFR=no
-
-USE_GMP=gmp
-PATCH_GMP_ARM64=no
-BUILD_ARB=no
-
-while [[ $# -gt 0 ]]
-do
-  key="$1"
-  case $key in
-    -h|--help)
-      echo "bin/download_dependencies.sh [options]"
-      echo
-      echo "Build local installs of python-flint's dependencies."
-      echo
-      echo "Supported options:"
-      echo "  --help            - show this help message"
-      echo "  --host <HOST>     - set the host (target) for GMP build"
-      echo "  --skip-gmp        - skip building GMP"
-      echo "  --skip-mpfr       - skip building MPFR"
-      echo
-      echo "Legacy options:"
-      echo "  --gmp gmp         - build based on GMP (default)"
-      echo "  --gmp mpir        - build based on MPIR (no longer works)"
-      echo "  --patch-gmp-arm64 - apply patch to GMP 6.2.1 for OSX arm64"
-      echo "  --arb             - build Arb (only needed for flint < 3.0.0)"
-      echo
-      exit
-    ;;
-    --host)
-      # e.g. --host x86_64-unknown-linux-gnu
-      # or   --host x86_64-apple-darwin
-      HOST_ARG="$2"
-      shift
-      shift
-    ;;
-    --gmp)
-      # e.g. --gmp gmp or --gmp mpir
-      # The mpir build no longer works because the download fails.
-      USE_GMP="$2"
-      if [[ "$USE_GMP" != "gmp" && "$USE_GMP" != "mpir" ]]; then
-        echo "--gmp option should be gmp or mpir"
-        exit 1
-      fi
-      shift
-      shift
-    ;;
-    --arb)
-      # With flint >= 3.0.0 Arb is included so we do not need to build it
[…]

### 2024-04-01 fastwfomc/python-flint/bin/build_mingw64_wheel.sh

@@ -1,100 +1,0 @@
-#!/bin/bash
-#
-# make_wheels.sh
-#
-# Build relocatable Windows wheel for python_flint using the mingw-w64
-# toolchain in the MSYS2 enironment.
-#
-# - First install Python
-#
-#       https://www.python.org/ftp/python/3.10.8/python-3.10.8-amd64.exe
-#
-# - Then checkout the code:
-#
-#       $ git clone https://github.com/flintlib/python-flint.git
-#
-# - Then install msys2
-#
-#       https://repo.msys2.org/distrib/x86_64/msys2-x86_64-20221028.exe
-#
-# - Then open msys2, cd into the checked out repo. Make sure setup.py says
-#
-#       libraries = ["arb", "flint", "mpfr", "gmp"]
-#
-# - Set the environment variable to the directory containing the installed
-#   Python that we want to build a wheel for i.e. the one installed from
-#   python.org. If python was on PATH then it would be
-#
-#        PYTHONDIR=`dirname $(which python)`
-#	 PYTHONVER=3.10
-#
-# - Then run this script.
-
-set -o errexit
-
-#
-# In CI this environment variable needs to be set to the directory containing
-# the python.org installation of Python. If Python is installed in msys2 then
-# it is also necesary to set this environment variable so that it picks up the
-# right installation of Python i.e. the one that we want to build a wheel for.
-#
-if [[ -z "$PYTHONDIR" ]]; then
-  PYTHONDIR=`dirname $(which python)`
-fi
-PYTHON=$PYTHONDIR/python
-VER="${PYTHONVER//./}"
-
-WHEELNAME=python_flint-0.5.0-cp$VER-cp$VER-win_amd64.whl
-
-$PYTHON -c 'print("hello world")'
-
-echo $PYTHONDIR
-ls $PYTHONDIR
-ls $PYTHONDIR/libs
-
-# Install the mingw-w64 toolchain
-pacman -S --noconfirm mingw-w64-x86_64-gcc m4 make mingw-w64-x86_64-tools-git
-
-# This takes ~30mins
-#bin/build_dependencies_unix.sh
-
-# Add the libpython$VER.a file to Python installation
-cd $PYTHONDIR
-  gendef python$VER.dll
-  dlltool --dllname python$VER.dll --def python$VER.def --output-lib libpython$VER.a
-  mv libpython$VER.a libs
-cd -
-
[…]

### 2024-04-01 fastwfomc/python-flint/bin/build_variables.sh

@@ -1,24 +1,0 @@
-#!/usr/bin/env bash
-#
-# Create a local directory .local to be used as --prefix when building
-# local installs of python-flint's dependencies. This also sets the PREFIX
-# shell variable and environment variables giving the versions to use for each
-# dependency. This script should be sourced rather than executed e.g.:
-#
-#    $ source bin/build_variables.sh
-#
-# This is used implicitly by the other build scripts and does not need to be
-# executed directly.
-
-PREFIX=$(pwd)/.local
-mkdir -p $PREFIX
-
-ARBVER=2.23.0 # Not needed with flint >= 3.0.0 (Arb is included in flint)
-
-YASMVER=1.3.0 # Only needed for MPIR
-MPIRVER=3.0.0 # MPIR build no longer works (not clear where to download from)
-
-# These are the actual dependencies used (at least by default):
-GMPVER=6.3.0
-MPFRVER=4.1.0
-FLINTVER=3.0.0

### 2024-04-01 fastwfomc/python-flint/bin/cibw.sh

@@ -1,36 +1,0 @@
-#!/usr/bin/env bash
-#
-# This script can be used to test cibuildwheel locally on OSX/Linux
-#
-# It is also worth commenting out the BEFORE_ALL line to build GMP etc after you have
-# built those once because that is by far the slowest step.
-#
-
-rm -f wheelhouse/*
-
-# bin/build_dependencies_unix.sh places headers and shared libraries under .local
-export CIBW_ENVIRONMENT='C_INCLUDE_PATH=$(pwd)/.local/include/ LIBRARY_PATH=$(pwd)/.local/lib/ LD_LIBRARY_PATH=$(pwd)/.local/lib:$LD_LIBRARY_PATH PYTHON_FLINT_MINGW64=true'
-
-export CIBW_BUILD='cp39-* cp310-* cp311-* cp312-*'
-# export CIBW_BUILD='cp311-*'
-export CIBW_SKIP='*-win32 *-manylinux_i686 *-musllinux_*'
-
-# export CIBW_ARCHS_MACOS="x86_64"
-export CIBW_ARCHS_MACOS="arm64"
-
-export CIBW_BEFORE_ALL_LINUX=bin/cibw_before_all_linux.sh
-# export CIBW_BEFORE_ALL_MACOS=bin/cibw_before_all_macosx_x86_64.sh
-export CIBW_BEFORE_ALL_MACOS=bin/cibw_before_all_macosx_arm64.sh
-export CIBW_BEFORE_ALL_WINDOWS='C:\\msys64\\usr\\bin\\bash bin/cibw_before_all_windows.sh'
-
-export CIBW_BEFORE_BUILD='pip install numpy cython delvewheel'
-export CIBW_BEFORE_BUILD_WINDOWS='C:\\msys64\\usr\\bin\\bash bin/cibw_before_build_windows.sh'
-
-export CIBW_REPAIR_WHEEL_COMMAND_WINDOWS='bin\cibw_repair_wheel_command_windows.bat {dest_dir} {wheel}'
-
-# export CIBW_TEST_COMMAND="python -c 'import flint; print(str(flint.fmpz(2)))'"
-export CIBW_TEST_COMMAND="python -m flint.test"
-
-# cibuildwheel --platform linux
-# cibuildwheel --platform windows
-cibuildwheel --platform macos

### 2024-04-01 fastwfomc/python-flint/bin/cibw_before_all_macosx_arm64.sh

@@ -1,11 +1,0 @@
-#!/usr/bin/env bash
-
-export CPPFLAGS=" --target=arm64-apple-macos11"
-export LDFLAGS=" -arch arm64"
-
-brew install automake libtool
-
-bin/build_dependencies_unix.sh\
-  --gmp gmp\
-  --host aarch64-apple-darwin\
-  --use-gmp-github-mirror

### 2024-04-01 fastwfomc/python-flint/bin/cibw_before_all_macosx_x86_64.sh

@@ -1,8 +1,0 @@
-#!/usr/bin/env bash
-
-brew install automake libtool
-
-bin/build_dependencies_unix.sh\
-  --gmp gmp\
-  --host x86_64-apple-darwin\
-  --use-gmp-github-mirror

### 2024-04-01 fastwfomc/python-flint/bin/cibw_before_all_windows.sh

@@ -1,29 +1,0 @@
-#!/bin/bash
-
-set -o errexit
-
-# Uncomment this to run cibuildwheel locally on Windows:
-# export PATH=$PATH:/c/msys64/usr/bin:/c/msys64/mingw64/bin
-
-#
-# Make a setup.cfg to specify compiling with mingw64 (even though it says
-# mingw32...)
-#
-echo '[build]' > setup.cfg
-echo 'compiler = mingw32' >> setup.cfg
-cat setup.cfg
-
-# Install the mingw-w64 toolchain and build tools
-pacman -S --noconfirm \
-    mingw-w64-x86_64-gcc\
-    mingw-w64-x86_64-tools-git\
-    m4\
-    make\
-    base-devel\
-    autoconf-wrapper\
-    automake-wrapper\
-    libtool\
-    #
-
-# This takes ~30mins
-bin/build_dependencies_unix.sh --use-gmp-github-mirror

### 2024-04-01 fastwfomc/python-flint/bin/cibw_before_build_windows.sh

@@ -1,43 +1,0 @@
-#!/bin/bash
-
-set -o errexit
-
-# Uncomment this to run cibuildwheel locally on Windows:
-# export PATH=$PATH:/c/msys64/usr/bin:/c/msys64/mingw64/bin
-
-# VER should be set be e.g. 310 for Python 3.10
-VER=`python -c 'import sys; print("%s%s" % sys.version_info[:2])'`
-echo VER=${VER}
-
-###################################################
-#  Find parent Python installation from the venv  #
-###################################################
-
-which python
-PYTHONBIN=`dirname $(which python)`
-PYTHONDIR=`dirname $PYTHONBIN`
-cfgfile=$PYTHONDIR/pyvenv.cfg
-homeline=`grep home $cfgfile`
-homepath=${homeline#*=}
-
-echo ---------------------------------------------------
-echo $homepath
-echo ---------------------------------------------------
-
-###################################################
-#  Find pythonXX.dll and make a .a library        #
-###################################################
-
-cd $homepath
-gendef python${VER}.dll
-dlltool --dllname python${VER}.dll 	\
-	--def python${VER}.def 		\
-	--output-lib libpython${VER}.a
-
-mv libpython${VER}.a libs
-
-###################################################
-#  Install build dependencies                     #
-###################################################
-
-pip install cython numpy delvewheel

### 2024-04-01 fastwfomc/python-flint/bin/cibw_repair_wheel_command_windows.sh

@@ -1,53 +1,0 @@
-#!/bin/bash
-#
-# Repair Windows wheels. See e.g.:
-#
-# https://github.com/scipy/scipy/blob/main/tools/wheels/repair_windows.sh
-
-set -o errexit
-
-# Uncomment this to run cibuildwheel locally on Windows:
-# export PATH=$PATH:/c/msys64/usr/bin:/c/msys64/mingw64/bin
-
-# We cannot use ordinary command line arguments in CI because msys2 -c mangles
-# them. Instead we have a batch file to receive the arguments and convert them
-# into environment variables before calling this script. When running locally
-# this script could be run directly giving the parameters as command line
-# arguments instead.
-
-if [[ -z "${WHEELHOUSE}" ]]; then
-  WHEELNAME=$1
-fi
-if [[ -z "${WHEELNAME}" ]]; then
-  WHEELHOUSE=$2
-fi
-
-echo WHEELHOUSE=$WHEELHOUSE
-echo WHEELNAME=$WHEELNAME
-
-wheeldir=$(dirname $WHEELNAME)
-echo $wheeldir
-
-# delvewheel requires DLLs created by mingw64 to be stripped. This strips the
-# DLLs for GMP etc that will have been built in the CIBW_BEFORE_ALL step.
-#
-# Previously the Arb DLLs would have been placed in .local/lib, but as of
-# flint 3.0.0 all DLLs aRe in .local/bin.
-strip .local/bin/*.dll
-
-# Make sure to leave the wheel in the same directory
-wheeldir=$(dirname $WHEELNAME)
-pushd $wheeldir
-  # Unpack the wheel and strip any .pyd DLLs inside
-  wheel unpack $WHEELNAME
-  rm $WHEELNAME
-  strip python_flint-*/flint/*.pyd
-  wheel pack python_flint-*
-popd
-
-# Make the wheel relocatable. This will fail with an error message about
-# --no-mangle if strip has not been applied to all mingw64-created .dll and
-# .pyd files that are needed for the wheel.
-delvewheel repair $WHEELNAME 	\
-	-w $WHEELHOUSE		\
-	--add-path .local/bin

### 2024-04-01 fastwfomc/python-flint/bin/coverage.sh

@@ -1,39 +1,0 @@
-#!/bin/bash
-#
-# Note: cython's Cython/Coverage.py fails for pyx files that are included in
-# other pyx files. This gives the following error:
-#
-#   $ coverage report -m
-#   Plugin 'Cython.Coverage.Plugin' did not provide a file reporter for
-#   '.../python-flint/src/flint/fmpz.pyx'.
-#
-# A patch to the file is needed:
-#
-#  --- Coverage.py.backup   2022-12-09 17:36:35.387690467 +0000
-#  +++ Coverage.py 2022-12-09 17:08:06.282516837 +0000
-#  @@ -172,7 +172,9 @@ class Plugin(CoveragePlugin):
-#          else:
-#              c_file, _ = self._find_source_files(filename)
-#              if not c_file:
-# -                return None
-# +                c_file = os.path.join(os.path.dirname(filename), 'pyflint.c')
-# +                if not os.path.exists(c_file):
-# +                    return None
-#              rel_file_path, code = self._read_source_lines(c_file, filename)
-#              if code is None:
-#                  return None  # no source found
-#
-#
-
-set -o errexit
-
-source bin/activate
-
-export PYTHON_FLINT_COVERAGE=true
-
-python setup.py build_ext --inplace
-
-coverage run -m flint.test $@
-
-#coverage report -m
-coverage html

### 2024-04-01 fastwfomc/python-flint/bin/pip_install_ubuntu.sh

@@ -1,56 +1,0 @@
-#!/bin/bash
-
-set -o errexit
-
-# This script should work to install python-flint on Ubuntu from a VCS checkout
-#
-#  $ git checkout https://github.com/flintlib/python-flint.git
-#  $ bin/pip_install_ubuntu.sh .
-#
-# To install an sdist from PyPI, use
-#
-#  $ bin/pip_install_ubuntu.sh python-flint
-#
-
-# Install runtime and build dependencies
-
-# First install their dependencies and build dependencies
-sudo apt-get update
-sudo apt-get install libgmp-dev libmpfr-dev xz-utils
-
-# Only Flint 3 or newer will work.
-FLINTVER=3.0.0
-
-# This will default to installing in /usr/local. If you want to install in a
-# non-standard location then configure flint with
-#    ./configure --disable-static --prefix=$PREFIX
-# If $PREFIX is not in default search paths, then at build time set
-#    export C_INCLUDE_PATH=$PREFIX/include
-# and at runtime set
-#    export LD_LIBRARY_PATH=$PREFIX/lib
-
-curl -O -L https://www.flintlib.org/flint-$FLINTVER.tar.gz
-tar xf flint-$FLINTVER.tar.gz
-cd flint-$FLINTVER
-  ./bootstrap.sh
-  ./configure --disable-static
-  make -j
-  sudo make install
-cd ..
-
-ls -l /usr/local/lib
-sudo ldconfig /usr/local/lib
-
-# Python build requirements. Ideally these would be in pyproject.toml, but
-# first need to migrate from setup.py to pyproject.toml.
-pip install numpy cython setuptools wheel
-
-# Install from checkout (or sdist).
-echo -----------------------------------------------------------
-echo
-echo     Running:
-echo        $ pip install --no-binary :all: --no-build-isolation $1
-echo
-echo -----------------------------------------------------------
-
-pip install --no-binary :all: --no-build-isolation $1

### 2024-04-01 fastwfomc/python-flint/bin/rst_to_pxd.py

@@ -1,184 +1,0 @@
-#!/usr/bin/env python3
-
-from collections import defaultdict
-import re
-import sys
-import os
-import fnmatch
-import argparse
-
-"""
-This is relatively rudimentary, but works for the purpose intended
-
-To use this to parse an arb rst file
-
-python rst_to_pxd basename
-
-or to parse a flint rst file
-
-python rst_to_pxd flint/basename
-
-the pxd file is dumped to stdout
-
-for example
-python rst_to_pxd flint/fmpz_poly
-
-will output a skeleton fmpz_poly.pxd to stdout
-
-
-You will need to configure the location of the flintlib submodule directory and the locations of the flint and
-arb doc source directories.
-
-The other useful configuration is the comment_types and set which are two representations of the types that are
-not implemented and therefore we want to comment functions that reference them
-
-TODO: DRY with comment types, also should be able to add commented types from the command line.
-TODO: don't import self
-
-"""
-
-#  recognize a function definition in rst
-is_func = re.compile(r"\.\.( )+(c:)?function( )*::")
-# rename types to avoid python -- c name collisions
-rename_types = [(re.compile(r"\bfmpz\b"),"fmpz_struct"),(re.compile(r"\bfmpq\b"), "fmpq_struct")]
-# comment out functions which use these types
-comment_types = re.compile(r"(\bFILE\b)|(\bmpz_t\b)|(\bmpq_t\b)")
-comment_set = set(["FILE", "mpz_t", "mpq_t"])
-c_types = set(["char", "short", "long", "int", "float", "double"])
-type_modifers = re.compile(r"\*|(\bconst\b)|(\bunsigned\b)|(\bsigned\b)")
-import_dict = {}
-
-def get_cython_struct_types(file):
-    """
-    Extract cython types from a pxd file.
-    """
-    ret = []
-    for line in file:
-        l = line.strip()
-        if l[:8] == "ctypedef":
-            if l[-1] == ']':
-                l = l[:l.rfind('[')]
-            else:
-                l = l.strip(':')
-            ret.append(l.split()[-1])
-    return ret
-
-def fill_import_dict(pyflintlibdir):
-    """
-    Get a map from cython structs to the pxd that defines them
-    """
-    with os.scandir(pyflintlibdir) as entry:
-        for f in entry:
-            if fnmatch.fnmatch(f.name, "*.pxd"):
-                with open(f.path) as pxd:
-                    for t in get_cython_struct_types(pxd):
-                        import_dict[t] = f.name.split('.')[0]
-
[…]

### 2024-04-01 fastwfomc/python-flint/src/flint/types/fmpz_poly.pyx

@@ -1,597 +1,0 @@
-from cpython.int cimport PyInt_AS_LONG
-from cpython.list cimport PyList_GET_SIZE
-from cpython.long cimport PyLong_Check
-from cpython.int cimport PyInt_Check
-
-from flint.flint_base.flint_context cimport getprec
-from flint.flint_base.flint_base cimport flint_poly
-from flint.utils.typecheck cimport typecheck
-from flint.types.fmpz cimport fmpz_set_python
-from flint.types.fmpz cimport any_as_fmpz
-from flint.types.fmpz cimport fmpz
-from flint.types.fmpq cimport any_as_fmpq
-from flint.types.fmpq cimport fmpq
-from flint.types.fmpq_poly cimport fmpq_poly
-from flint.types.fmpq_poly cimport any_as_fmpq_poly
-from flint.types.acb cimport acb
-from flint.types.arb cimport any_as_arb_or_notimplemented
-from flint.types.arb cimport arb
-from flint.types.acb cimport any_as_acb_or_notimplemented
-cimport libc.stdlib
-from flint.flintlib.fmpz cimport fmpz_init, fmpz_clear, fmpz_set
-from flint.flintlib.fmpz cimport fmpz_is_one, fmpz_equal_si, fmpz_equal
-from flint.flintlib.acb_modular cimport *
-from flint.flintlib.ulong_extras cimport n_is_prime
-from flint.flintlib.fmpz_poly cimport *
-from flint.flintlib.fmpz_poly_factor cimport *
-from flint.flintlib.arith cimport *
-from flint.flintlib.acb cimport *
-from flint.flintlib.arb_poly cimport *
-from flint.flintlib.arb_fmpz_poly cimport *
-
-cdef any_as_fmpz_poly(x):
-    cdef fmpz_poly res
-    if typecheck(x, fmpz_poly):
-        return x
-    elif typecheck(x, fmpz):
-        res = fmpz_poly.__new__(fmpz_poly)
-        fmpz_poly_set_fmpz(res.val, (<fmpz>x).val)
-        return res
-    elif PyLong_Check(x):
-        res = fmpz_poly.__new__(fmpz_poly)
-        t = fmpz(x)
-        fmpz_poly_set_fmpz(res.val, (<fmpz>t).val)
-        return res
-    return NotImplemented
-
-cdef fmpz_poly_set_list(fmpz_poly_t poly, list val):
-    cdef long i, n
[…]

### 2024-04-01 fastwfomc/wrapper.py

@@ -2,8 +2,7 @@ import argparse
 import json
 from collections import defaultdict
 
-from aima3.logic import to_cnf
-from aima3.utils import expr, Expr
+from aima3.utils import expr
 
 from wfomc_cc import WFOMCWithCC
 
@@ -19,10 +18,13 @@ def main():
     args = parser.parse_args()
     with open(args.instance) as f:
         instance = json.load(f)
-    counter = WFOMCWithCC(instance['formula'],
-                          args.domainsize, instance['cardinalities'])
+    cardinalities = [(x, args.domainsize * y)
+                     for (x, y) in instance['cardinalities']]
+    counter = WFOMCWithCC(expr(instance['formula']),
+                          args.domainsize, cardinalities)
     print(counter.get_wfomc(
-        instance['weights'] if instance['weights'] else defaultdict(lambda: (1, 1))))
+        instance['weights'] if instance['weights']
+        else defaultdict(lambda: (1, 1))))
 
 
 if __name__ == "__main__":

### 2024-04-01 fastwfomc_wrapper.sh

@@ -1,0 +1,9 @@
+#!/usr/bin/env sh
+
+cd fastwfomc
+source virtualenvwrapper.sh
+workon fastwfomc
+for ((i=1; i<=$1; i++)); do
+    echo "Domain size: $i"
+    ulimit -t $3 -c 0 && /usr/bin/time -f "Elapsed: %e" python wrapper.py $2 $i || exit 1
+done

### 2024-04-01 parse.py

@@ -41,7 +41,7 @@ for filename in os.listdir(RESULTS_DIR):
                 else:
                     counts.append(tokens[8].translate({ord(','): None}))
                     times.append(tokens[10])
-            elif line.startswith('Domain size:'): # ForcLift
+            elif line.startswith('Domain size:'): # ForcLift and FastWFOMC
                 domains.append(line.split()[2])
             elif line.startswith('Z = '): # ForcLift
                 try:
@@ -52,8 +52,13 @@ for filename in os.listdir(RESULTS_DIR):
                     break
             elif line.startswith('Inference took'): # ForcLift
                 times.append(line.split()[2])
-            elif line.startswith('Elapsed:'): # ForcLift
-                total_times.append(float(line.split()[1]) * 1000)
+            elif line.startswith('Elapsed:'): # ForcLift and FastWFOMC
+                t = float(line.split()[1]) * 1000
+                total_times.append(t)
+                if data['algorithm'] == 'fastwfomc':
+                    times.append(t)
+            elif line.strip().isnumeric():
+                counts.append(line.strip())
 
     # If the algorithm fails to compile, output no domains
     if len(domains) == 1:

### 2024-04-02 doc/paper.tex
Some writing about experiments

@@
 \usepackage{forest}
+\usepackage{siunitx}
+\usepackage{amsfonts}
+\usepackage{pifont}
+\usepackage[inline]{enumitem}
 
@@
 
+\newcommand{\cmark}{\ding{51}}
+\newcommand{\xmark}{\ding{55}}
+
 \newcommand{\expr}{\mathtt{expr}}
+\newcommand{\Ctwo}{$\mathsf{C}^{2}$}
+\newcommand{\FO}{$\mathsf{FO}$}
 \newcommand{\FOtwo}{$\mathsf{FO}^{2}$}
+\newcommand{\UFO}{$\mathsf{UFO}^{2} + \mathsf{EQ}$}
 
@@
 
+\begin{itemize}
+  \item Variables in uppercase
+  \item Domains in uppercase Greek
+  \item Constant and predicate symbols in lowercase
+  \item Clauses written on separate lines are implicitly conjoined
+  \item For weights, for any predicate symbol $p$, we write
+        $w^{+}(p), w^{-}(p) \in \mathbb{R}$ for its positive and negative
+        weights, respectively. All weights not explicitly acknowledged are
+        assumed to be equal to one.
+\end{itemize}
+
 \todo[inline,caption={}]{
@@
     \item explain how this works for function calls too
+    \item introduce WFOMC as a problem
   \end{itemize}
@@
   \begin{itemize}
-    \item What notation am I using for FOL? Colon after every quantifier?
-    \item (Similar to CNF, maybe QBF). Incomplete. Need (W)FOMC semantics. What
-          is an interpretation? What is a model?
+    \item What notation am I using for FOL? Introduce equality cardinality
+          constraints, counting quantifiers, etc.
+    \item Need (W)FOMC semantics. What is an interpretation? What is a model?
+    \item Should table caption go above or below the table?
+    \item Define terms.
+    \item Maybe say ``structure'' instead of interpretation?
+    \item What's the right table heading capitalization for KR?
+    \item Should I say ``sort'' instead of domain everywhere?
   \end{itemize}
 }
+
+\begin{table*}
+  \centering
+  \begin{tabular}{llllll}
+    \toprule
+    Logic & Sorts & Constants & Variables & Quantifiers & Additional atomic constraints\\
+    \midrule
+    \FO & one or more & \cmark & unlimited & $\forall$, $\exists$ & $s = t$\\
+    \Ctwo & one & \xmark & two & $\forall$, $\exists$, $\exists^{= k}$, $\exists^{\le k}$, $\exists^{\ge k}$ & ---\\
+    \UFO & one & \xmark & two & $\forall$ & $|p| = m$\\
+    \bottomrule
+  \end{tabular}
+  \caption[]{A comparison of the three logics used in WFOMC in terms of:
+    \begin{enumerate*}[label=(\roman*)]
+      \item the number of sorts,
+      \item support for constants,
+      \item the maximum number of variables,
+      \item allowed quantifiers, and
+      \item atomic constructions in addition to those of the form $p(t_{1}, \dots, t_{n})$ for some predicate symbol $p$ and terms $t_{1}, \dots, t_{n}$.
+    \end{enumerate*}
+    Here:
+    \begin{enumerate*}[label=(\roman*)]
+      \item $k$ and $m$ are non-negative integers, the latter of which can depend on the domain size,
+      \item $p$ is a predicate symbol, and
+      \item $s$ and $t$ are terms.
+    \end{enumerate*}
+  }\label{tbl:logics}
+\end{table*}
+
+\paragraph{Three types of logics}
+\begin{itemize}
+  \item All three logics are function-free.
+  \item Domains are always assumed to be finite.
+  \item See \cref{tbl:logics} for a detailed comparison. \FO{} is used as the
+        input format for \textsc{Crane} and \textsc{ForcLift}. \Ctwo{} is used
+        in the literature on \textsc{FastWFOMC} and related methods (TODO:
+        citations). \UFO{} is the input format supported by a privately-obtained
+        version of \textsc{FastWFOMC}. Note that the publicly available version
+        does not support any cardinality constraints.
+  \item In the case of \textsc{Crane} and \textsc{ForcLift}, support for a
+        formula as valid input does not imply that the algorithm will be able to
+        compile the formula into a circuit or graph suitable for lifted model
+        counting. However, it is known that \textsc{ForcLift} compilation is
+        guaranteed to succeed on any \FO{} formula without constants and with at
+        most two variables (TODO: citation).
+\end{itemize}
 
@@
 
-\paragraph{Remarks on comparing the model counts of the formulas with their
-  corresponding OEIS sequences.}
-Disregarding differences where the OEIS sequence starts with one or two numbers
-that are not included in model counts (which is somewhat justified since we
-start with domains of size one rather than zero), two differences remain:
+Comparing \textsc{Crane} and \textsc{FastWFOMC} on a larger set of benchmarks is
+challenging because there is no automated way to translate a formula in \FO{} or
+\Ctwo{} into \UFO{} (or even check if such an encoding is possible).
+
+\paragraph{Benchmarks (probably for supplementary material).}
 \begin{itemize}
-  \item on A62971, the OEIS sequence starts as $1, 2, 16,\dots$, but the model
-        counts start as $1, 16,\dots$ (with the rest exactly the same);
-  \item similarly, on A62971, the OEIS sequence starts as $32, 290,\dots$, but
-        the model counts start as $2, 32, 290,\dots$ (with the rest exactly the
-        same).
+  \item Functions
+        \begin{itemize}
+          \item In \Ctwo: $\forall X \in \Delta\text{.
+                }\exists^{=1} Y \in \Delta\text{. }p(X, Y)$
+          \item In \UFO:
+                \begin{gather*}
+                  \forall X, Y \in \Delta\text{. } s(X) \lor \neg p(X, Y)\\
+                  |p| = |\Delta|
+                \end{gather*}
+          \item In \FO:
+                \begin{gather*}
+                  \forall X \in \Delta\text{. }\exists Y \in \Delta\text{. } p(X, Y)\\
+                  \forall X, Y, Z \in \Delta\text{. } p(X, Y) \land p(X, Z) \Rightarrow Y = Z
+                \end{gather*}
         \end{itemize}
+  \item Permutations
+        \begin{itemize}
+          \item In \Ctwo:
+                \begin{gather*}
+                  \forall X \in \Delta\text{. }\exists^{=1} Y \in \Delta\text{. }p(X, Y)\\
+                  \forall Y \in \Delta\text{. }\exists^{=1} X \in \Delta\text{. }p(X, Y)
+                \end{gather*}
+          \item In \UFO:
+                \begin{gather*}
+                  \forall X, Y \in \Delta\text{. } r(X) \lor \neg p(X, Y)\\
+                  \forall X, Y \in \Delta\text{. } s(X) \lor \neg p(Y, X)\\
+                  |p| = |\Delta|
+                \end{gather*}
+                with weights $w^{-}(r) = w^{-}(s) = -1$
+          \item In \FO:
+                \begin{gather*}
+                  \forall X \in \Delta\text{. }\exists Y \in \Delta\text{. } p(X, Y)\\
+                  \forall Y \in \Delta\text{. }\exists X \in \Delta\text{. } p(X, Y)\\
+                  \forall X, Y, Z \in \Delta\text{. } p(X, Y) \land p(X, Z) \Rightarrow Y = Z\\
+                  \forall X, Y, Z \in \Delta\text{. } p(X, Y) \land p(Z, Y) \Rightarrow X = Z
+                \end{gather*}
+        \end{itemize}
+\end{itemize}
+
+\paragraph{Setup.}
+\begin{itemize}
+  \item The experiments were run on an AMD~Ryzen~7~5800H processor with
+        \SI{16}{\gibi\byte} of memory and Arch Linux~6.8.2-arch2-1 operating
+        system. \textsc{FastWFOMC} was run using Python~3.8.19 with
+        Python-FLINT~0.5.0.
+\end{itemize}
+
+\begin{figure}
+  \centering
+  \input{plot}
+  \caption{The runtime data of WFOMC algorithms on bijection- and
+    function-counting problems on domains of sizes
+    $1, 2, \dots, 35$}\label{fig:plot}
+\end{figure}
+
+\paragraph{Results.}
+\begin{itemize}
+  \item the runtime appears constant because compilation time dominates
+        inference time for small domain sizes. Indeed, the maximum inference
+        time of both \textsc{Crane-BFS} and \textsc{Crane-Greedy} is only
+        \SI{4}{\milli\second}.
+  \item describe \cref{fig:plot}
+  \item On bijection counting, \textsc{FastWFOMC} takes about \SI{124}{\second}
+        on a domain of size 35, whereas \textsc{Crane-BFS} scales up to
+        \num{e4} in \SI{34}{\second}
+  \item On function counting, \textsc{FastWFOMC} takes about \SI{78}{\second} on
+        a domain of size 35, whereas both \textsc{Crane-BFS} and
+        \textsc{Crane-Greedy} scale up to \num{3e5} in \SI{41}{\second}.
+  \item Note that, both model counts are huge (TODO: add details)
+\end{itemize}
+% ** bijections max time: 123.870
+% *** Crane-BFS scales up to 10k in 34 s
+% **** answer = 10k! = a number with 35660 digits
+% ** functions max time: 78.330
+% *** both Crane-BFS and Crane-Greedy scale up to 300k in 41 s
+% **** the count of this is 300k^300k is a number with over 1 million digits
+
+\todo[inline,caption={}]{
+  Some reproducibility requirements to keep in mind:
+  \begin{itemize}
+    \item A motivation is given for why the experiments are conducted on the
+          selected datasets.
+    \item All novel datasets introduced in this paper are included in a data
+          appendix.
+    \item All datasets drawn from the existing literature (potentially including
+          authors’ own previously published work) are accompanied by appropriate
+          citations. (mention the counting quantifier paper and my KR paper)
+    \item All source code implementing new methods have comments detailing the
+          implementation, with references to the paper where each step comes
+          from.
+    \item This paper formally describes evaluation metrics used and explains the
+          motivation for choosing these metrics.
+    \item This paper states the number of algorithm runs used to compute each
+          reported result.
+  \end{itemize}
+}
 

### 2024-04-02 doc/plot.tex
Some writing about experiments

% Created by tikzDevice version 0.12.6 on 2024-04-01 09:58:28
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (240.29,135.16);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (240.29,135.16);
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 25.11) rectangle (145.94,130.66);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 29.55, 25.11) rectangle (145.94,130.66);
\definecolor{drawColor}{gray}{0.87}

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 29.55, 36.74) --
	(145.94, 36.74);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 29.55, 71.11) --
	(145.94, 71.11);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 29.55,105.49) --
	(145.94,105.49);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 47.29, 25.11) --
	( 47.29,130.66);

\path[draw=drawColor,line width= 0.1pt,line join=round] ( 78.41, 25.11) --
	( 78.41,130.66);

\path[draw=drawColor,line width= 0.1pt,line join=round] (109.53, 25.11) --
	(109.53,130.66);

\path[draw=drawColor,line width= 0.1pt,line join=round] (140.65, 25.11) --
	(140.65,130.66);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 29.55, 53.93) --
	(145.94, 53.93);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 29.55, 88.30) --
	(145.94, 88.30);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 29.55,122.67) --
	(145.94,122.67);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 31.72, 25.11) --
	( 31.72,130.66);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 62.85, 25.11) --
	( 62.85,130.66);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 93.97, 25.11) --
	( 93.97,130.66);

\path[draw=drawColor,line width= 0.2pt,line join=round] (125.09, 25.11) --
	(125.09,130.66);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.84, 54.53) --
	( 37.95, 54.50) --
	( 41.06, 54.50) --
	( 44.17, 54.49) --
	( 47.29, 54.49) --
	( 50.40, 54.49) --
	( 53.51, 54.49) --
	( 56.62, 54.50) --
	( 59.73, 54.50) --
	( 62.85, 54.49) --
	( 65.96, 54.49) --
	( 69.07, 54.49) --
	( 72.18, 54.49) --
	( 75.30, 54.49) --
	( 78.41, 54.50) --
	( 81.52, 54.50) --
	( 84.63, 54.50) --
	( 87.74, 54.50) --
	( 90.86, 54.49) --
	( 93.97, 54.50) --
	( 97.08, 54.50) --
	(100.19, 54.49) --
	(103.31, 54.50) --
	(106.42, 54.50) --
	(109.53, 54.50) --
	(112.64, 54.50) --
	(115.75, 54.49) --
	(118.87, 54.50) --
	(121.98, 54.50) --
	(125.09, 54.50) --
	(128.20, 54.50) --
	(131.32, 54.50) --
	(134.43, 54.50) --
	(137.54, 54.50) --
	(140.65, 54.50);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.84, 52.07) --
	( 37.95, 52.04) --
	( 41.06, 52.04) --
	( 44.17, 52.04) --
	( 47.29, 52.04) --
	( 50.40, 52.05) --
	( 53.51, 52.04) --
	( 56.62, 52.05) --
	( 59.73, 52.04) --
	( 62.85, 52.04) --
	( 65.96, 52.04) --
	( 69.07, 52.04) --
	( 72.18, 52.04) --
	( 75.30, 52.04) --
	( 78.41, 52.05) --
	( 81.52, 52.05) --
	( 84.63, 52.04) --
	( 87.74, 52.04) --
	( 90.86, 52.09) --
	( 93.97, 52.05) --
	( 97.08, 52.05) --
	(100.19, 52.05) --
	(103.31, 52.05) --
	(106.42, 52.04) --
	(109.53, 52.04) --
	(112.64, 52.04) --
	(115.75, 52.04) --
	(118.87, 52.04) --
	(121.98, 52.04) --
	(125.09, 52.05) --
	(128.20, 52.05) --
	(131.32, 52.05) --
	(134.43, 52.04) --
	(137.54, 52.05) --
	(140.65, 52.04);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.84, 49.39) --
	( 37.95, 49.33) --
	( 41.06, 49.33) --
	( 44.17, 49.33) --
	( 47.29, 49.33) --
	( 50.40, 49.33) --
	( 53.51, 49.33) --
	( 56.62, 49.35) --
	( 59.73, 49.35) --
	( 62.85, 49.33) --
	( 65.96, 49.33) --
	( 69.07, 49.33) --
	( 72.18, 49.33) --
	( 75.30, 49.33) --
	( 78.41, 49.33) --
	( 81.52, 49.35) --
	( 84.63, 49.35) --
	( 87.74, 49.35) --
	( 90.86, 49.33) --
	( 93.97, 49.33) --
	( 97.08, 49.33) --
	(100.19, 49.33) --
	(103.31, 49.33) --
	(106.42, 49.33) --
	(109.53, 49.35) --
	(112.64, 49.35) --
	(115.75, 49.33) --
	(118.87, 49.33) --
	(121.98, 49.33) --
	(125.09, 49.33) --
	(128.20, 49.33) --
	(131.32, 49.33) --
	(134.43, 49.35) --
	(137.54, 49.35) --
	(140.65, 49.33);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.84, 30.63) --
	( 37.95, 30.63) --
	( 41.06, 31.33) --
	( 44.17, 31.33) --
	( 47.29, 32.63) --
	( 50.40, 33.82) --
	( 53.51, 35.96) --
	( 56.62, 37.83) --
	( 59.73, 40.62) --
	( 62.85, 43.28) --
	( 65.96, 46.30) --
	( 69.07, 50.22) --
	( 72.18, 53.16) --
	( 75.30, 57.14) --
	( 78.41, 60.47) --
	( 81.52, 64.05) --
	( 84.63, 72.20) --
	( 87.74, 71.34) --
	( 90.86, 80.12) --
	( 93.97, 80.67) --
	( 97.08, 83.21) --
	(100.19, 89.74) --
	(103.31, 87.61) --
	(106.42, 96.04) --
	(109.53, 98.47) --
	(112.64, 99.99) --
	(115.75,103.72) --
	(118.87,103.27) --
	(121.98,109.92) --
	(125.09,111.85) --
	(128.20,115.67) --
	(131.32,116.78) --
	(134.43,119.28) --
	(137.54,123.20) --
	(140.65,125.87);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.84, 29.90) --
	( 37.95, 30.63) --
	( 41.06, 30.63) --
	( 44.17, 29.90) --
	( 47.29, 30.63) --
	( 50.40, 31.33) --
	( 53.51, 32.63) --
	( 56.62, 33.82) --
	( 59.73, 35.45) --
	( 62.85, 38.26) --
	( 65.96, 40.62) --
	( 69.07, 42.34) --
	( 72.18, 46.05) --
	( 75.30, 49.23) --
	( 78.41, 52.36) --
	( 81.52, 64.35) --
	( 84.63, 58.30) --
	( 87.74, 68.19) --
	( 90.86, 70.67) --
	( 93.97, 72.59) --
	( 97.08, 78.45) --
	(100.19, 78.57) --
	(103.31, 83.81) --
	(106.42, 86.56) --
	(109.53, 85.94) --
	(112.64, 92.57) --
	(115.75, 95.46) --
	(118.87, 98.41) --
	(121.98,102.64) --
	(125.09,102.38) --
	(128.20,106.28) --
	(131.32,110.72) --
	(134.43,112.06) --
	(137.54,116.16) --
	(140.65,119.03);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.84, 34.38) --
	( 37.95, 34.38) --
	( 41.06, 34.93) --
	( 44.17, 35.45) --
	( 47.29, 34.93) --
	( 50.40, 34.93) --
	( 53.51, 34.93) --
	( 56.62, 34.93) --
	( 59.73, 34.93) --
	( 62.85, 36.92) --
	( 65.96, 35.45) --
	( 69.07, 34.93) --
	( 72.18, 35.96) --
	( 75.30, 35.45) --
	( 78.41, 35.45) --
	( 81.52, 34.93) --
	( 84.63, 34.93) --
	( 87.74, 34.93) --
	( 90.86, 35.45) --
	( 93.97, 35.45) --
	( 97.08, 34.93) --
	(100.19, 34.93) --
	(103.31, 35.45) --
	(106.42, 34.93) --
	(109.53, 36.92) --
	(112.64, 34.93) --
	(115.75, 35.45) --
	(118.87, 35.45) --
	(121.98, 34.93) --
	(125.09, 34.93) --
	(128.20, 34.93) --
	(131.32, 34.93) --
	(134.43, 34.93) --
	(137.54, 35.45) --
	(140.65, 34.93);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55, 29.90) -- ( 32.39, 29.90);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55, 35.96) -- ( 32.39, 35.96);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55, 40.25) -- ( 32.39, 40.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55, 43.58) -- ( 35.24, 43.58);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55, 46.30) -- ( 32.39, 46.30);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55, 48.60) -- ( 32.39, 48.60);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55, 50.60) -- ( 32.39, 50.60);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55, 52.36) -- ( 32.39, 52.36);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55, 53.93) -- ( 38.08, 53.93);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55, 64.28) -- ( 32.39, 64.28);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55, 70.33) -- ( 32.39, 70.33);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55, 74.62) -- ( 32.39, 74.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55, 77.95) -- ( 35.24, 77.95);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55, 80.67) -- ( 32.39, 80.67);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55, 82.98) -- ( 32.39, 82.98);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55, 84.97) -- ( 32.39, 84.97);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55, 86.73) -- ( 32.39, 86.73);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55, 88.30) -- ( 38.08, 88.30);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55, 98.65) -- ( 32.39, 98.65);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55,104.70) -- ( 32.39,104.70);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55,108.99) -- ( 32.39,108.99);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55,112.32) -- ( 35.24,112.32);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55,115.05) -- ( 32.39,115.05);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55,117.35) -- ( 32.39,117.35);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55,119.34) -- ( 32.39,119.34);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55,121.10) -- ( 32.39,121.10);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55,122.67) -- ( 38.08,122.67);

\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round] ( 29.55, 25.11) rectangle (145.94,130.66);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 25.50, 51.45) {1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 25.50, 85.82) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 25.50,120.19) {100};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 27.30, 53.93) --
	( 29.55, 53.93);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 27.30, 88.30) --
	( 29.55, 88.30);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 27.30,122.67) --
	( 29.55,122.67);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 31.72, 22.86) --
	( 31.72, 25.11);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 62.85, 22.86) --
	( 62.85, 25.11);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 93.97, 22.86) --
	( 93.97, 25.11);

\path[draw=drawColor,line width= 0.2pt,line join=round] (125.09, 22.86) --
	(125.09, 25.11);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 31.72, 16.10) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 62.85, 16.10) {10};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 93.97, 16.10) {20};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (125.09, 16.10) {30};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 87.74,  6.25) {Domain size};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 10.70, 77.89) {Total runtime (s)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (154.94, 96.84) rectangle (212.73,147.20);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (159.44,115.79) rectangle (173.90,130.25);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,line join=round] (160.89,123.02) -- (172.45,123.02);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (159.44,101.34) rectangle (173.90,115.79);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (160.89,108.57) -- (172.45,108.57);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (178.40,120.54) {bijections};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (178.40,106.09) {functions};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (154.94,  8.58) rectangle (235.79, 87.84);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (159.44, 56.44) rectangle (173.90, 70.89);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (160.89, 63.66) -- (172.45, 63.66);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (159.44, 41.98) rectangle (173.90, 56.44);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round] (160.89, 49.21) -- (172.45, 49.21);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (159.44, 27.53) rectangle (173.90, 41.98);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,line join=round] (160.89, 34.76) -- (172.45, 34.76);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (159.44, 13.08) rectangle (173.90, 27.53);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,line join=round] (160.89, 20.30) -- (172.45, 20.30);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (178.40, 61.18) {\textsc{Crane-BFS}};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (178.40, 46.73) {\textsc{Crane-Greedy}};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (178.40, 32.28) {\textsc{FastWFOMC}};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (178.40, 17.82) {\textsc{ForcLift}};
\end{scope}
\end{tikzpicture}

### 2024-04-02 analyse.R

@@ -1,123 +1,99 @@
 library(tidyverse)
 library(scales)
+library(tikzDevice)
 
-TIMEOUT <- 60
-breaks <- c(0.3, 1, 3, 10, 30, 60) # TODO: update this and TIMEOUT later
+K <- 5
+degree <- 10
+
 df <- read.csv("results.csv")
-df$algorithm[df$algorithm == "bfs"] <- "Crane-BFS" # TODO: make these \textsc{}
-df$algorithm[df$algorithm == "greedy"] <- "Crane-Greedy"
-df$algorithm[df$algorithm == "forclift"] <- "ForcLift"
-algorithms <- sort(unique(df$algorithm))
-
-# Random stuff
-# summary(df)
-# n <- length(df$inference.time)
-# sort(df$inference.time, decreasing = TRUE)
-
-# Functions
-scatter <- function(data, x_var, y_var) {
-  limits <- c(min(df$compilation.time), TIMEOUT)
-  ggplot(data, aes(.data[[x_var]], .data[[y_var]])) +
-    geom_count() +
-    scale_size_area() +
-    geom_abline(slope = 1, intercept = 0, colour = "#989898") +
-    scale_x_continuous(trans = log10_trans(), breaks = breaks, labels = breaks,
-                       limits = limits) +
-    scale_y_continuous(trans = log10_trans(), breaks = breaks, labels = breaks,
-                       limits = limits) +
-    coord_fixed() +
-    annotation_logticks(colour = "#b3b3b3") +
-    theme_light(base_size = 9) +
-    theme(legend.title=element_blank()) +
-    scale_size_continuous(breaks = round)
-} # TODO (later): have the same legend for all scatter plots
-
-cumulative_plot <- function(df) {
-  times <- vector(mode = "list", length = length(algorithms))
-  names(times) <- algorithms
-  for (algorithm in algorithms) {
-    times[[algorithm]] <- unique(df$time[df$algorithm == algorithm])
-  }
-
-  chunks <- vector(mode = "list", length = length(algorithms))
-  names(chunks) <- algorithms
-  for (algorithm in algorithms) {
-    chunks[[algorithm]] <- cbind(times[[algorithm]], algorithm,
-                             unlist(times[[algorithm]] %>%
-                                      map(function(x)
-                                        sum(df$time[df$algorithm == algorithm]
-                                            <= x))))
-  }
-
[…]

### 2024-04-11 doc/paper.tex
Restructure the paper (and other changes)

@@
 
-% Use the postscript times font!
 \usepackage{times}
@@
 \usepackage{booktabs}
-%\usepackage{algorithm}
-%\usepackage{algorithmic}
 \urlstyle{same}
@@
 \usetikzlibrary{arrows.meta}
-\usetikzlibrary{positioning}
-\usetikzlibrary{shapes}
-\usetikzlibrary{fit}
 
-% See https://www.overleaf.com/learn/latex/theorems_and_proofs
-% for a nice explanation of how to define new theorems, but keep
-% in mind that the amsthm package is already included in this
-% template and that you must *not* alter the styling.
+\newtheorem{theorem}{Theorem}
+\newtheorem{fact}{Fact}
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}
 \newtheorem{example}{Example}
-\newtheorem{theorem}{Theorem}
-\newtheorem{definition}{Definition}
-\newtheorem*{remark}{Remark}
-\newtheorem{fact}{Fact}
-% TODO: fix styling, check if everything in the header is still needed
-% TODO: make sure forest arrows match non-forest arrows
+
+% TODO: 9 pages!!!
 
@@
 \DeclareMathOperator{\Doms}{Doms}
-\DeclareMathOperator{\Preds}{Preds}
 \DeclareMathOperator{\Vars}{Vars}
@@
 \newcommand{\FO}{$\mathsf{FO}$}
-\newcommand{\FOtwo}{$\mathsf{FO}^{2}$}
 \newcommand{\UFO}{$\mathsf{UFO}^{2} + \mathsf{EQ}$}
 
-\SetKwFunction{Crane}{Crane}
+\newcommand{\Cranetwo}{\textsc{Crane}~2}
+
+\SetKwFunction{Crane}{Compile}
 \SetKwFunction{Propagate}{Propagate}
@@
 
-\title{TBD}
+\title{Towards Efficient First-Order Model Counting}
 
-% \author{%
-% First Author$^1$\and
-% Second Author$^2$\and
-% Third Author$^{2,3}$\and
-% Fourth Author$^4$ \\
-% \affiliations
-% $^1$First Affiliation\\
-% $^2$Second Affiliation\\
-% $^3$Third Affiliation\\
-% $^4$Fourth Affiliation \\
-% \emails
-% \{first, second\}@example.com,
-% third@other.example.com,
-% fourth@example.com
-% }
+% TODO: check if this follows the formatting guidelines
+\author{%
+Ananth K. Kidambi$^1$\and
+Guramrit Singh$^1$\and
+Paulius Dilkas$^2$\and
+Kuldeep S. Meel$^3$ \\
+\affiliations
+$^1$Indian Institute of Technology Bombay, India\\
+$^2$National University of Singapore, Singapore\\
+$^3$University of Toronto, Canada\\
+\emails
+\{210051002, 210050061\}@iitb.ac.in,
+paulius.dilkas@nus.edu.sg,
+meel@cs.toronto.edu
+}
 
@@
   \begin{itemize}
-    \item mention/describe the arithmetic simplification code
-    \item (in Fig. 1) Crane2 doesn't use Crane, it uses itself
     \item describe which compilation rules are currently greedy or non-greedy
     \item my agenda has a plan for proving completeness for $\mathbf{C}^{2}$
-    \item Can I prove that Crane's domain recursion can always simulate
-          ForcLift's domain recursion?
+    \item Can I prove that my domain recursion can always simulate the domain
+          recursion of \textsc{ForcLift}?
   \end{itemize}
 }
+
+\paragraph{Papers to cite.}
+\begin{itemize}
+  \item original domain recursion~\cite{DBLP:conf/nips/Broeck11}
+  \item recent overview paper~\cite{DBLP:conf/ijcai/Kuzelka23}
+  \item conjecturing recurrence relations~\cite{DBLP:conf/ilp/BarvinekB0ZK21}
+  \item algorithms
+  \begin{itemize}
+    \item \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11}
+    \item \textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23}
+    \item \textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21}
+    \item approximate~\cite{DBLP:conf/ijcai/BremenK20}
+  \end{itemize}
+  \item liftable fragments (TODO: perhaps good sources of benchmarks?)
+  \begin{itemize}
+    \item \Ctwo~\cite{DBLP:journals/jair/Kuzelka21}
+    \item tree axioms~\cite{DBLP:journals/ai/BremenK23}
+    \item linear order axioms~\cite{DBLP:conf/aaai/TothK23}
+  \end{itemize}
+  \item applications
+  \begin{itemize}
+    \item extensions to
+          sampling~\cite{DBLP:conf/aaai/WangB0K22,DBLP:conf/lics/WangP0K23}
+    \item discovery of combinatorial
+          sequences~\cite{DBLP:conf/ijcai/SvatosJT0K23}
+  \end{itemize}
+\end{itemize}
+
+% TODO: make sure to not call \Crane2 \textsc{Crane}
 
@@
         I cannot make sense of.
-  \item Implemented an if-then-else arithmetic operation as the interpretation
-        of the new domain recursion node (i.e., there is one branch for when the
-        domain is empty and another branch for any other domain size).
-  \item \Cref{sec:main,sec:identifying} might also be outdated: there is
-        probably no need to search for base cases given the new version of
-        domain recursion.
 \end{itemize}
@@
         \end{itemize}
-  \item Aim to show that Crane works correctly on all consistent formulas.
+  \item Aim to show that \Cranetwo{} works correctly on all consistent formulas.
   \item Prove that, whenever some compilation rule makes the formula $\phi$
@@
 
+ % TODO: Crane2 uses itself instead of Crane. Not really. By 'Crane', here I
+ % mean the process of turning logical formulas into equations. Later on, I use
+ % 'Crane' to refer to Crane2. Maybe rename this use of 'Crane' to something
+ % else?
 \begin{figure*}[t]
@@
     \node[draw,fit={(alg1) (simplification) (compilation) (crane) (alg2) (alg3)},inner ysep=7pt,yshift=5pt] {};
-    \node at (1.1, 0.5) {\textsc{Crane2}};
+    \node at (1.1, 0.5) {\Cranetwo};
 
     \draw[-Latex] (formula) -- (alg1);
-    \draw[-Latex] (alg1) -- node[above] {$E$} (simplification);
-    \draw[-Latex] (simplification) -- node[above] {$E'$} (compilation);
+    \draw[-Latex] (alg1) -- node[above] {$\mathcal{E}$} (simplification);
+    \draw[-Latex] (simplification) -- node[above] {$\mathcal{E}'$} (compilation);
     \draw[-Latex] (compilation) -- (cpp);
@@
   \end{tikzpicture}
-  \caption{Using \textsc{Crane2} to compute the model count of formula $\phi$.\
-    The formula is compiled into a set of equations $E$, which are then
+  \caption{Using \Cranetwo{} to compute the model count of formula $\phi$.\ The
+    formula is compiled into a set of equations $\mathcal{E}$, which are then
     algebraically simplified and compiled to a C++ program. This program can
@@
 \end{figure*}
-
-The evaluation of base cases is done by simplifying the clauses and then using
-\textsc{Crane} to find the base cases. First, while traversing the graph to find
-the equations, we store two maps: $\mathcal{F}$ (which stores the mapping from
-the function names to the formulae, whose model count they represent) and
-$\mathcal{D}$ (which stores the mapping from the variable names to the domains
-whose sizes they represent). Then, a particular domain is selected (using the
-algorithm described in previous reports), and the clauses are simplified. Then,
-\textsc{Crane} is called on those clauses to evaluate the base cases. After
-that, we change the function names and variable to make it consistent with the
-previous domain to variable mapping, and append these base cases to the set of
-equations.
 
@@
         Arithmetic Library.
-  \item A new set of benchmarks.
-  \item The experiments for Crane and ForcLift are (going to be) more
-        comprehensive than any other experimental study performed on (W)FOMC
-        algorithms.
   \item Some experiments vs FastWFOMC
-  \item A proof of correctness
   \item A proof of completeness
 \end{itemize}
-
-\todo[inline]{references to my previous paper and some of the \textsc{ForcLift}
-  and \textsc{FastWFOMC} papers that contain experimental results}
 
@@
   or constants (i.e., there is no subtraction within any argument), and there is
-  at least one constant.
+  at least one constant. We denote a base case in the same way as a signature,
+  e.g., $f(\mathbf{x})$.
 \end{definition}
@@
   \centering
-  \begin{tabular}{llllll}
+  \begin{tabular}{llclll}
     \toprule
@@
   \item See \cref{tbl:logics} for a detailed comparison. \FO{} is used as the
-        input format for \textsc{Crane} and \textsc{ForcLift}. \Ctwo{} is used
-        in the literature on \textsc{FastWFOMC} and related methods (TODO:
-        citations). \UFO{} is the input format supported by a privately-obtained
-        version of \textsc{FastWFOMC}. Note that the publicly available version
-        does not support any cardinality constraints.
-  \item In the case of \textsc{Crane} and \textsc{ForcLift}, support for a
+        input format for \textsc{ForcLift} and its extensions \textsc{Crane} and
+        \Cranetwo{}. \Ctwo{} is used in the literature on \textsc{FastWFOMC} and
+        related methods (TODO: citations). \UFO{} is the input format supported
+        by a privately-obtained version of \textsc{FastWFOMC}. Note that the
+        publicly available version does not support any cardinality constraints.
+  \item In the case of \textsc{ForcLift} and its extensions, support for a
         formula as valid input does not imply that the algorithm will be able to
@@
 
-For any clause $C$, let $\Preds(C)$ denote the set of predicates in $C$. For any
-clause or literal $l$, let $\Vars(l)$ denote the set of variables in $l$.
+For any clause or literal $l$, let $\Vars(l)$ denote the set of variables in
+$l$.
 
@@
 
-\section{Theoretical Results}
+\section{Completing the Definitions of Recursive Functions}\label{sec:main}
+
+\begin{algorithm}[t]
+  \caption{The core part of \Cranetwo{} that compiles a formula...}\label{alg:main}% TODO: start here
+  \KwIn{formula $\phi$}
+  \KwOut{set $\mathcal{E}$ of equations}
+  $(\mathcal{E}, \mathcal{F}, \mathcal{D}) \gets \Crane{$\phi$}$\;
+  \ForEach{base case $f(\mathbf{x}) \in \FindBaseCases{$\mathcal{E}$}$}{
+    $\psi \gets \mathcal{F}(f)$\;
+    \ForEach{$i$ such that $x_{i}$ is a constant}{
+      $\psi \gets \Propagate{$\psi$, $\mathcal{D}(f, i)$, $x_i$}$\;
+    }
+    $(\mathcal{E}', \text{\textunderscore}, \text{\textunderscore}) \gets \Crane{$\psi$}$\;
+    $\mathcal{E} \gets \mathcal{E} \cup \mathcal{E}'$\;
+  }
+\end{algorithm}
+
+See \cref{alg:main}.
+
+We write \Crane for a slight modification of the original \textsc{Crane} that
+compiles a formula $\phi$ into:
+\begin{itemize}
+  \item a set $\mathcal{E}$ of equations,
+  \item a map $\mathcal{F}$ from function names to formulas, and
+  \item a map $\mathcal{D}$ from function names and parameter indices to
+        domains.
+\end{itemize}
+
+% TODO: update: crane or crane2
+The evaluation of base cases is done by simplifying the clauses and then using
+\textsc{Crane} to find the base cases. A particular domain is selected, and the
+clauses are simplified. Then, \textsc{Crane} is called on those clauses to
+evaluate the base cases. After that, we change the function names and variable
+to make it consistent with the previous domain to variable mapping, and append
+these base cases to the set of equations.
+
+\todo[inline,caption={}]{extend it to work with base cases that are themselves
+  recursive}
+
+\subsection{Identifying a Sufficient Set of Base Cases}\label{sec:identifying}
+
+\begin{algorithm}[t]
+  \caption{\protect\FindBaseCases{$\mathcal{E}$}}\label{alg1}
+  \KwIn{set $\mathcal{E}$ of equations}
+  \KwOut{set $\mathcal{B}$ of base cases}
+
+  $\mathcal{B} \gets \emptyset$\;
+  \ForEach{equation $(f(\mathbf{x}) = \expr{}) \in \mathcal{E}$}{
+    \ForEach{function call $f(\mathbf{x} - \mathbf{c}) \in \expr{}$}{\label{line:functioncall}
+      \ForEach{$c_{i} \in \mathbf{c}$}{
+        \For{$n \gets 0$ \KwTo $c_{i} - 1$}{\label{line:lim}
+          $\mathcal{B} \gets \mathcal{B} \cup \{\, f(\mathbf{x})[x_{i}/n] \,\}$\;\label{line:insert}
+        }
+      }
+    }
+  }
+\end{algorithm}
+
+The algorithm is described as \cref{alg1}. We know that if, say, on the RHS of
+all equations, the domain size appears as $m - c_1, m - c_2, \dots, m - c_k$,
+then finding $f(0, x_1, x_2, \dots)$, $f(1, x_1, x_2, \dots)$,
+$\dots f(m_0, x_1, x_2, \dots)$ for every function $f$, where
+$m_0 = \max(c_1, c_2, \dots c_k) - 1$ forms a sufficient set of base cases.
+Hence, in order to do the same efficiently, we can take that domain for which
+$m_0$ is the minimum, i.e. $\argmin(\max(c_1, c_2, \dots c_k))$. Ideally, we
+should calculate the base cases by finding the base cases up to
+$\max(c_{1}, c_{2}, \dots) - 1$. However, currently only empty and singleton
+domains are supported.
+
+First, expand the summations in each equation. Here we expand the summations of
+the form: $\sum_{x=0}^{x_{1}} \expr{} \cdot [a \le x < b]$ or similar
+inequalities where $x$ is bounded by constants and $a$ and $b$ are constants, by
+substituting the value of $x$ from $a$ to $b-1$. For example, we replace
+$\sum_{x=0}^{x_1} \binom{x_{1}}{x} f(x_1 - x) \cdot [0 \le x < 2]$ by
+$\binom{x_{1}}{0} f(x_1) + \binom{x_{1}}{1} f(x_1-1)$.
+
+\begin{itemize}
+  \item \cref{line:insert} for $f(\mathbf{x}) = f(y, z)$, $x_{i} = y$, and
+        $n = 0$, add $f(y, z)[y/0] = f(0, z)$ to $\mathcal{B}$.
+\end{itemize}
 
 \begin{theorem}
-  The domain recursion by Dilkas and Belle~\shortcite{DBLP:conf/kr/DilkasB23}
-  can simulate the domain recursion by Van den
-  Broeck~\shortcite{DBLP:conf/nips/Broeck11}. This proves that Crane can (still)
-  handle \FOtwo.
+  Under the following assumptions, \cref{alg1} is guaranteed to return a
+  sufficient set of base cases:
+  \begin{itemize}
+    \item there is no mutual recursion
+    \item each function $f$ has exactly one equation with $f$ on the LHS;
+    \item in the recursive definition of function $f(x_{1},\dots,x_{n})$, the
+          $i$-th argument of each call to $f$ on the RHS is of the form
+          $x_{i} - c_{i}$, where:
+          \begin{itemize}
+            \item $c_{i} \ge 0$ for all $i$, and
+            \item $c_{i} > 0$ for at least one $i$.
+          \end{itemize}
+  \end{itemize}
 \end{theorem}
 
-\begin{figure}
-  \centering
-  \begin{forest}
-    for tree={sn edges}
-    [$\land_{r}$,circle,draw,name=dr
-    [$n_{r}$],
-    [$n_{x}$]
-    ]
-    \draw[-Latex] (dr) to [loop right] node {$\Delta \gets \Delta \setminus \{\,x\,\}$} ();
-  \end{forest}
-  \begin{forest}
-    for tree={sn edges}
-    [$\GDR(x \in \Delta)$,ellipse,draw,
-    [$\land$,circle,draw,
-    [$\bigwedge_{y \in \Delta}$,ellipse,draw]
-    [$\land$,circle,draw]
-    ]
-    ]
-  \end{forest}
-\end{figure}
+\begin{example}
+  For an equation $f(m, n) = 2 \times f(m-1, n)$, \cref{alg1} returns $f(0, n)$.
+\end{example}
 
-\begin{proof}
-  `A theory allows for domain recursion when the theory is shattered, the theory
-  contains no independent subtheories, and there exists a root binding class.'
+NOTE: function calls such as $f(n-m)$ and $f(n-m-1)$ are ignored.
 
-  Stuck on some weird cases. Need to prove that the model count of $n_{x}$ will
-  never depend on $|\Delta|$.
-\end{proof}
+\subsection{Propagating Domain Size Assumptions}\label{sec:simplifying}
 
-\section{Smoothing (only relevant for domain recursion v3)}
+\begin{algorithm}[t]
+  \caption{\protect\Propagate{$\phi$, $\Delta$, $n$} TODO: find the source code and check: (1) what we're doing with unit clauses, (2) whether we just randomly pick any literal to negate}\label{alg2}
+  \KwIn{formula $\phi$, domain $\Delta$, domain size $n \in \{\, 0, 1 \,\}$}
+  \KwOut{formula $\phi'$}
+  $\phi' \gets \emptyset$\;
+  \uIf{$n = 0$}{
+    \ForEach{clause $C \in \phi$}{
+      \lIf{$\Delta \not\in \Doms(C)$}{$\phi' \gets \phi' \cup \{\, C \,\}$}
+      $C' \gets \{\, l \in C \mid \Delta \not\in \Doms(l) \,\}$\;
+      \If{$\Delta \in \Doms(C)$ {\bf and} $C' \ne \emptyset$}{
+        $l \gets \text{an arbitrary literal in } C'$\;\label{line:smoothing1}
+        $\phi' \gets \phi' \cup \{\, C' \cup \{\, \neg l \,\} \,\} $\;\label{line:smoothing2}
+      }
+    }
+  }
+  \Else{
+    $c \gets$ a new constant symbol\;
+    \ForEach{clause $C \in \phi$}{
+      $C' \gets C$\;
+      \ForEach{$v \in \Vars(C)$ with $\Dom(v) = \Delta$}{
+        $C' \gets C'[c / v]$\;
+      }
+      $\phi' \gets \phi' \cup \{\, C' \,\}$\;
+    }
+  }
+\end{algorithm}
+
+We use \cref{alg2} to find the transformed formula corresponding to each base
+case obtained using \cref{alg1} and call \textsc{Crane} on the formula to obtain
+the required base cases.
+% TODO: or crane 2?
+
+\begin{itemize}
+  \item Clauses where all literals have variables quantified over the empty
+        domain are still removed.
+  \item $C'$ is guaranteed to be non-empty.
+  \item \Cref{line:smoothing1,line:smoothing2} are explained in
+        \cref{sec:smoothingbase}.
+\end{itemize}
+
+\section{Smoothing}
 
@@
 }
+
+\subsection{Smoothing for Base Cases}\label{sec:smoothingbase}
+
+\paragraph{Key point.}
+If there is a predicate $p$ that has nothing to do with domain $\Delta$, make
+sure that $p$ remains as part of the formula even if all clauses with $p$ can be
+removed. Which literal is picked on \cref{line:smoothing1} of \cref{alg2} is not
+important because any choice achieves the same goal: constructing a clause that
+mentions the same predicates as $C'$ and is satisfied by any interpretation.
+
+\begin{fact}
+  Assuming that domain $\Delta$ is empty, any clause that contains
+  `$\forall x \in \Delta$' (for any variable $x$) is vacuously satisfied by all
+  interpretations.
+\end{fact}
+
+For example, consider the formula
+\begin{align}
+  \forall x \in \Delta \forall y, z \in \Gamma &: P(x) \lor Q(y, z)\label[formula]{eq:example1}\\
+  \forall y, z \in \Gamma' &: Q(y, z)\label[formula]{eq:example2}
+\end{align}
+and assume that $\Gamma' \subseteq \Gamma$. In this case, if we set $|\Delta|$
+to zero and remove clauses with variables quantified over $\Delta$, we get
+\begin{equation}\label[formula]{eq:simplified}
+  \forall y, z \in \Gamma' : Q(y, z),
+\end{equation}
+but the model count of \cref{eq:simplified} is one. However, the actual model
+count should be $2^{|\Gamma|^2 - |\Gamma'|^2}$. That is, $Q$ as a relation is a
+subset of $\Gamma \times \Gamma$. While \cref{eq:example1} becomes vacuously
+true, \cref{eq:example2} fixes the value of $Q$ over
+$\Gamma' \times \Gamma' \subseteq \Gamma \times \Gamma$. Hence, the number of
+different values that $Q$ can take is
+$|(\Gamma \times \Gamma) \setminus (\Gamma' \times \Gamma')| = |\Gamma|^{2} - |\Gamma'|^{2}$.
+
+We address this issue by converting clauses with universal quantifiers over the
+empty domain to tautologies, hence retaining all the predicates that have no
+argument assigned to the empty domain. For example, we would convert
+\cref{eq:example1,eq:example2} to
+\begin{align*}
+  \forall y, z \in \Gamma &: Q(y, z) \lor \neg Q(y, z) \\
+  \forall y, z \in \Gamma' &: Q(y, z).
+\end{align*}
+The model count returned by this will also consider the truth value of $Q$ over
+$y \in \Gamma \setminus \Gamma'$ or $z \in \Gamma \setminus \Gamma'$.
 
@@
 
-\section{The Main Algorithm: Finding the Definitions of the Base
-  Cases}\label{sec:main}
-
-\begin{algorithm}[t]
-  \caption{Finding the definitions of the base cases}\label{alg:main}
-  \KwIn{formula $\phi$}
-  \KwOut{a set $E$ of equations that define $B$}
-  $(E, \mathcal{F}, \mathcal{D}) \gets \Crane{$\phi$}$\;
-  \ForEach{base case $f(\mathbf{x}) \in \FindBaseCases{$E$}$}{
-    $\psi \gets \mathcal{F}(f)$\;
-    \ForEach{$i$ such that $x_{i}$ is a constant}{
-      $\psi \gets \Propagate{$\psi$, $\mathcal{D}(f, i)$, $x_i$}$\;
-    }
-    $(E', \text{\textunderscore}, \text{\textunderscore}) \gets \Crane{$\psi$}$\;
-    $E \gets E \cup E'$\;
-  }
-\end{algorithm}
-
-See \cref{alg:main}
-
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item extend it to work with base cases that are themselves recursive
-    \item what does it mean for a set of equations to define a set of base cases?
-    \item for base cases, we will also use the $f(\mathbf{x})$ notation
-  \end{itemize}
-}
-
-\section{Identifying a Sufficient Set of Base Cases}\label{sec:identifying}
-
-\begin{algorithm}[t]
-  \caption{\protect\FindBaseCases{$E$}}\label{alg1}
-  \KwIn{set $E$ of equations}
-  \KwOut{set $B$ of base cases}
-
-  $B \gets \emptyset$\;
-  \ForEach{equation $(f(\mathbf{x}) = \expr{}) \in E$}{
-    \ForEach{function call $f(\mathbf{x} - \mathbf{c}) \in \expr{}$}{\label{line:functioncall}
-      \ForEach{$c_{i} \in \mathbf{c}$}{
-        \For{$n \gets 0$ \KwTo $c_{i} - 1$}{\label{line:lim}
-          $B \gets B \cup \{\, f(\mathbf{x})[x_{i}/n] \,\}$\;\label{line:insert}
-        }
-      }
-    }
-  }
-\end{algorithm}
-
-We know that if, say, on the RHS of all equations, the domain size appears as
-$m - c_1, m - c_2, \dots, m - c_k$, then finding $f(0, x_1, x_2, \dots)$,
-$f(1, x_1, x_2, \dots)$, $\dots f(m_0, x_1, x_2, \dots)$ for every function $f$,
-where $m_0 = \max(c_1, c_2, \dots c_k) - 1$ forms a sufficient set of base
-cases. Hence, in order to do the same efficiently, we can take that domain for
-which $m_0$ is the minimum, i.e. $\argmin(\max(c_1, c_2, \dots c_k))$. Ideally,
-we should calculate the base cases by finding the base cases up to
-$\max(c_{1}, c_{2}, \dots) - 1$. However, currently only empty and singleton
-domains are supported.
-
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item NOTE: \cref{line:functioncall} iterates over all function calls in the
-          algebraic expression
-    \item remove the `dependencies' data structure from the description
-  \end{itemize}
-}
-
-The following steps were followed while finding the base cases:
-
-First, expand the summations in each equation. Here we expand the summations of
-the form: $\sum_{x=0}^{x_{1}} \expr{} \cdot [a \le x < b]$ or similar
-inequalities where $x$ is bounded by constants and $a$ and $b$ are constants, by
-substituting the value of $x$ from $a$ to $b-1$. For example, we replace
-$\sum_{x=0}^{x_1} \binom{x_{1}}{x} f(x_1 - x) \cdot [0 \le x < 2]$ by
-$\binom{x_{1}}{0} f(x_1) + \binom{x_{1}}{1} f(x_1-1)$.
-
-Now, we find a domain that has only terms of the form $x-1$ appearing on the RHS
-of the dependencies. The base cases are then calculated by setting this domain
-size to zero. For the above example, $n$ is the selected domain, and not $m$
-since there are $m-2$ and $m-3$ terms appearing in the arguments.
-
-The algorithm is described as \cref{alg1}.
-
-\todo[inline,caption={}]{
-  add an example where \cref{alg1} runs on either
-  \begin{align*}
-    f_{0}(m, n) &= f_{1}(m-1, n) + f_{2}(m, n-1)\\
-    f_{1}(m, n) &= f_{1}(m-1, n-1) \times f_{2}(m-2, n-1)\\
-    f_{2}(m, n) &= 2 \times f_{1}(m-3, n-1)
-  \end{align*}
-  or
-  \begin{align*}
-    f(m, n) &= g(m-1, n) + f(m-2, n-1)\\
-    g(m, n) &= f(m-1, n-2) + g(m-1, n-1).
-  \end{align*}
-}
-
-\begin{itemize}
-  \item \cref{line:lim}: the limit is 2 for the arg $(x-3)$.
-  \item \cref{line:insert} for $f(\mathbf{x}) = f(y, z)$, $x_{i} = y$, and
-        $n = 0$, add $f(y, z)[y/0] = f(0, z)$ to $B$.
-\end{itemize}
-
-\todo[inline]{I changed the algorithm. Update the description.}
-
-\begin{theorem}
-  Under the following assumptions, \cref{alg1} is guaranteed to return a
-  sufficient set of base cases:
-  \begin{itemize}
-    \item there is no mutual recursion (i.e., cyclic dependencies between
-          functions);
-    \item each function $f$ has exactly one equation with $f$ on the LHS;
-    \item in the recursive definition of function $f(x_{1},\dots,x_{n})$, the
-          $i$-th argument of each call to $f$ on the RHS is of the form
-          $x_{i} - c_{i}$, where:
-          \begin{itemize}
-            \item $c_{i} \ge 0$ for all $i$, and
-            \item $c_{i} > 0$ for at least one $i$.
-          \end{itemize}
-  \end{itemize}
-\end{theorem}
-
-\begin{example}
-  For an equation $f(m, n) = 2 \times f(m-1, n)$, \cref{alg1} returns $f(0, n)$.
-\end{example}
-
-NOTE: function calls such as $f(n-m)$ and $f(n-m-1)$ are ignored.
-
-\section{Propagating Domain Size Assumptions}\label{sec:simplifying}
-
-\subsection{Motivation: Why Tautologies Are Needed and Simply Removing The
-  Clauses Does Not Work}
-
-\begin{fact}
-  Assuming that domain $\Delta$ is empty, any clause that contains
-  `$\forall x \in \Delta$' (for any variable $x$) is vacuously satisfied by all
-  interpretations.
-\end{fact}
-
-For example, consider the formula
-\begin{align}
-  \forall x \in \Delta \forall y, z \in \Gamma &: P(x) \lor Q(y, z)\label[formula]{eq:example1}\\
-  \forall y, z \in \Gamma' &: Q(y, z)\label[formula]{eq:example2}
-\end{align}
-and assume that $\Gamma' \subseteq \Gamma$. In this case, if we set $|\Delta|$
-to zero and remove clauses with variables quantified over $\Delta$, we get
-\begin{equation}\label[formula]{eq:simplified}
-  \forall y, z \in \Gamma' : Q(y, z),
-\end{equation}
-but the model count of \cref{eq:simplified} is one. However, the actual model
-count should be $2^{|\Gamma|^2 - |\Gamma'|^2}$. That is, $Q$ as a relation is a
-subset of $\Gamma \times \Gamma$. While \cref{eq:example1} becomes vacuously
-true, \cref{eq:example2} fixes the value of $Q$ over
-$\Gamma' \times \Gamma' \subseteq \Gamma \times \Gamma$. Hence, the number of
-different values that $Q$ can take is
-$|(\Gamma \times \Gamma) \setminus (\Gamma' \times \Gamma')| = |\Gamma|^{2} - |\Gamma'|^{2}$.
-
-We address this issue by converting clauses with universal quantifiers over the
-empty domain to tautologies, hence retaining all the predicates that have no
-argument assigned to the empty domain. For example, we would convert
-\cref{eq:example1,eq:example2} to
-\begin{align*}
-  \forall y, z \in \Gamma &: Q(y, z) \lor \neg Q(y, z) \\
-  \forall y, z \in \Gamma' &: Q(y, z).
-\end{align*}
-The model count returned by this will also consider the truth value of $Q$ over
-$y \in \Gamma \setminus \Gamma'$ or $z \in \Gamma \setminus \Gamma'$.
-
-\subsection{The Solution}
-
-\begin{algorithm}[t]
-  \caption{\protect\Propagate{$\phi$, $\Delta$, $n$}}\label{alg2}
-  \KwIn{formula $\phi$, domain $\Delta$, domain size $n \in \{\, 0, 1 \,\}$}
-  \KwOut{formula $\phi'$}
-  $\phi' \gets \emptyset$\;
-  \uIf{$n = 0$}{
-    \ForEach{clause $C \in \phi$}{
-      \lIf{$\Delta \not\in \Doms(C)$}{$\phi' \gets \phi' \cup \{\, C \,\}$}
-      $C' \gets \{\, l \in C \mid \Delta \not\in \Doms(l) \,\}$\;
-      \If{$\Delta \in \Doms(C)$ {\bf and} $C' \ne \emptyset$}{
-        $l \gets \text{an arbitrary literal in } C'$\;
-        $\phi' \gets \phi' \cup \{\, C' \cup \{\, \neg l \,\} \,\} $\;
-      }% TODO: find the source code and check: 1) what we're doing with unit clauses, 2) whether we just randomly pick any literal to negate
-    }
-  }
-  \Else{
-    $c \gets$ a new constant symbol\;
-    \ForEach{clause $C \in \phi$}{
-      $C' \gets C$\;
-      \ForEach{$v \in \Vars(C)$ with $\Dom(v) = \Delta$}{
-        $C' \gets C'[c / v]$\;
-      }
-      $\phi' \gets \phi' \cup \{\, C' \,\}$\;
-    }
-  }
-\end{algorithm}
-
-\todo[inline]{it would be easy to extend the second part to an arbitrary constant}
-
-We use \cref{alg2} to find the transformed formula corresponding to each base
-case obtained using \cref{alg1} and call \textsc{Crane} on the formula to obtain
-the required base cases.
-
-\begin{itemize}
-  \item Similar to generalised domain recursion (what's the difference?).
-  \item Clauses where all literals have variables quantified over the empty
-        domain are still removed.
-  \item $C'$ is guaranteed to be non-empty.
-\end{itemize}
-
 \section{Generating C++ Code}\label{sec:cpp}
-
-\todo[inline]{the report has some (long) examples of formulas being transformed
-  into programs perhaps suitable for supplementary material}
 
@@
 
-The translation of a set $E$ of equations into a C++ program works as follows.
+The translation of a set $\mathcal{E}$ of equations into a C++ program works as
+follows.
 
-First, we create a cache for each function in $E$. This is implemented as a
-multi-dimensional vector containing objects of \texttt{class cache\_elem}
+First, we create a cache for each function in $\mathcal{E}$. This is implemented
+as a multi-dimensional vector containing objects of \texttt{class cache\_elem}
 defined as shown in the example code. The default initialization of this object
@@
 
-Next, we create a function definition for the LHS of each equation in $E$,
-including all functions and base cases. The signatures of these functions is
-decided as follows. A function call containing only variable arguments is named
-as the function itself, and ones with constants in their arguments are suffixed
-with a string that contains \texttt{'x'} at the $i$th place if the $i$th
-argument is variable and the $i$th argument if that argument is a constant. For
-example, $f(x_{1}, x_{2}, x_{3})$ is declared as \texttt{int f(int x1, int x2,
-  int x3);} and $f(1, x_{2}, x_{3})$ is declared as \texttt{int f\_1xx(int x2,
-  int x3);} (the constant arguments are removed from the signature).
+Next, we create a function definition for the LHS of each equation in
+$\mathcal{E}$, including all functions and base cases. The signatures of these
+functions is decided as follows. A function call containing only variable
+arguments is named as the function itself, and ones with constants in their
+arguments are suffixed with a string that contains \texttt{'x'} at the $i$th
+place if the $i$th argument is variable and the $i$th argument if that argument
+is a constant. For example, $f(x_{1}, x_{2}, x_{3})$ is declared as \texttt{int
+  f(int x1, int x2, int x3);} and $f(1, x_{2}, x_{3})$ is declared as
+\texttt{int f\_1xx(int x2, int x3);} (the constant arguments are removed from
+the signature).
 
-The RHS of each equation in $E$ is used to define the body of the equation
-corresponding to the LHS of that equation. The function body (for a function
-\texttt{func} corresponding to equation $e$) is formed as follows.
+The RHS of each equation in $\mathcal{E}$ is used to define the body of the
+equation corresponding to the LHS of that equation. The function body (for a
+function \texttt{func} corresponding to equation $e$) is formed as follows.
 
@@
   \input{plot}
-  \caption{The runtime data of WFOMC algorithms on bijection- and
-    function-counting problems on domains of sizes
-    $1, 2, \dots, 35$}\label{fig:plot}
+  \caption{The runtime data of WFOMC algorithms on permutation- and
+    function-counting problems on domains of sizes $1, 2, \dots, 35$. Note that
+    the $y$ axis is on a logarithmic scale.}\label{fig:plot}
 \end{figure}
@@
 \begin{itemize}
-  \item the runtime appears constant because compilation time dominates
-        inference time for small domain sizes. Indeed, the maximum inference
-        time of both \textsc{Crane-BFS} and \textsc{Crane-Greedy} is only
-        \SI{4}{\milli\second}.
-  \item describe \cref{fig:plot}
-  \item On bijection counting, \textsc{FastWFOMC} takes about \SI{124}{\second}
-        on a domain of size 35, whereas \textsc{Crane-BFS} scales up to
-        \num{e4} in \SI{34}{\second}
-  \item On function counting, \textsc{FastWFOMC} takes about \SI{78}{\second} on
-        a domain of size 35, whereas both \textsc{Crane-BFS} and
-        \textsc{Crane-Greedy} scale up to \num{3e5} in \SI{41}{\second}.
-  \item Note that, both model counts are huge (TODO: add details)
+  \item As shown in \cref{fig:plot}, the runtimes of all compilation-based
+        algorithms remain practically constant in contrast to the rapidly
+        increasing runtimes of \textsc{FastWFOMC}.
+  \item Note that \textsc{Crane-BFS} is able to handle more instances than
+        \textsc{ForcLift} (e.g., the permutation-counting problem in our
+        experiments and other problems in my previous work).
+  \item Although the search/compilation part is slower in \textsc{Crane} than in
+        \textsc{ForcLift}, the difference is negligible.
+  \item The runtimes of three out of four WFOMC algorithms appear constant
+        because---for these counting problems and domain sizes---compilation
+        time dominates inference time (recall that compilation time is
+        independent of domain sizes). Indeed, the maximum inference time of both
+        \textsc{Crane-BFS} and \textsc{Crane-Greedy} across these experiments is
+        only \SI{4}{\milli\second}.
+  \item The runtimes of \textsc{Crane} have lower variation than those of
+        \textsc{ForcLift} because with \textsc{ForcLift} we compile the formula
+        anew for each domain size whereas with \textsc{Crane} we compile it once
+        and reuse the resulting C++ program for all domain sizes.
+  \item As another point of comparison,---in at most
+        \SI{41}{\second}---\textsc{Crane} scales up to domains of sizes \num{e4}
+        and \num{3e5} in permutation- and function-counting problems,
+        respectively (whereas \textsc{FastWFOMC} already takes longer with
+        domains of sizes\dots)
 \end{itemize}
-% ** bijections max time: 123.870
-% *** Crane-BFS scales up to 10k in 34 s
-% **** answer = 10k! = a number with 35660 digits
-% ** functions max time: 78.330
-% *** both Crane-BFS and Crane-Greedy scale up to 300k in 41 s
-% **** the count of this is 300k^300k is a number with over 1 million digits
 
@@
 
+% TODO: for references, maybe fix the spelling of Kuzelka's name
+
+% TODO: the report has some (long) examples of formulas being transformed into
+% programs perhaps suitable for supplementary material
+
 \end{document}

### 2024-04-11 doc/plot.tex
Restructure the paper (and other changes)

@@
-% Created by tikzDevice version 0.12.6 on 2024-04-01 09:58:28
+% Created by tikzDevice version 0.12.6 on 2024-04-04 08:49:14
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.84, 54.53) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.84, 52.07) --
+	( 37.95, 52.04) --
+	( 41.06, 52.04) --
+	( 44.17, 52.04) --
+	( 47.29, 52.04) --
+	( 50.40, 52.05) --
+	( 53.51, 52.04) --
+	( 56.62, 52.05) --
+	( 59.73, 52.04) --
+	( 62.85, 52.04) --
+	( 65.96, 52.04) --
+	( 69.07, 52.04) --
+	( 72.18, 52.04) --
+	( 75.30, 52.04) --
+	( 78.41, 52.05) --
+	( 81.52, 52.05) --
+	( 84.63, 52.04) --
+	( 87.74, 52.04) --
+	( 90.86, 52.09) --
+	( 93.97, 52.05) --
+	( 97.08, 52.05) --
+	(100.19, 52.05) --
+	(103.31, 52.05) --
+	(106.42, 52.04) --
+	(109.53, 52.04) --
+	(112.64, 52.04) --
+	(115.75, 52.04) --
+	(118.87, 52.04) --
+	(121.98, 52.04) --
+	(125.09, 52.05) --
+	(128.20, 52.05) --
+	(131.32, 52.05) --
+	(134.43, 52.04) --
+	(137.54, 52.05) --
+	(140.65, 52.04);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.84, 54.53) --
 	( 37.95, 54.50) --
@@
 	(140.65, 54.50);
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.84, 52.07) --
-	( 37.95, 52.04) --
-	( 41.06, 52.04) --
-	( 44.17, 52.04) --
-	( 47.29, 52.04) --
-	( 50.40, 52.05) --
-	( 53.51, 52.04) --
-	( 56.62, 52.05) --
-	( 59.73, 52.04) --
-	( 62.85, 52.04) --
-	( 65.96, 52.04) --
-	( 69.07, 52.04) --
-	( 72.18, 52.04) --
-	( 75.30, 52.04) --
-	( 78.41, 52.05) --
-	( 81.52, 52.05) --
-	( 84.63, 52.04) --
-	( 87.74, 52.04) --
-	( 90.86, 52.09) --
-	( 93.97, 52.05) --
-	( 97.08, 52.05) --
-	(100.19, 52.05) --
-	(103.31, 52.05) --
-	(106.42, 52.04) --
-	(109.53, 52.04) --
-	(112.64, 52.04) --
-	(115.75, 52.04) --
-	(118.87, 52.04) --
-	(121.98, 52.04) --
-	(125.09, 52.05) --
-	(128.20, 52.05) --
-	(131.32, 52.05) --
-	(134.43, 52.04) --
-	(137.54, 52.05) --
-	(140.65, 52.04);
 \definecolor{drawColor}{RGB}{217,95,2}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.84, 49.39) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.84, 49.39) --
 	( 37.95, 49.33) --
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.84, 30.63) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.84, 29.90) --
+	( 37.95, 30.63) --
+	( 41.06, 30.63) --
+	( 44.17, 29.90) --
+	( 47.29, 30.63) --
+	( 50.40, 31.33) --
+	( 53.51, 32.63) --
+	( 56.62, 33.82) --
+	( 59.73, 35.45) --
+	( 62.85, 38.26) --
+	( 65.96, 40.62) --
+	( 69.07, 42.34) --
+	( 72.18, 46.05) --
+	( 75.30, 49.23) --
+	( 78.41, 52.36) --
+	( 81.52, 64.35) --
+	( 84.63, 58.30) --
+	( 87.74, 68.19) --
+	( 90.86, 70.67) --
+	( 93.97, 72.59) --
+	( 97.08, 78.45) --
+	(100.19, 78.57) --
+	(103.31, 83.81) --
+	(106.42, 86.56) --
+	(109.53, 85.94) --
+	(112.64, 92.57) --
+	(115.75, 95.46) --
+	(118.87, 98.41) --
+	(121.98,102.64) --
+	(125.09,102.38) --
+	(128.20,106.28) --
+	(131.32,110.72) --
+	(134.43,112.06) --
+	(137.54,116.16) --
+	(140.65,119.03);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.84, 30.63) --
 	( 37.95, 30.63) --
@@
 	(140.65,125.87);
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.84, 29.90) --
-	( 37.95, 30.63) --
-	( 41.06, 30.63) --
-	( 44.17, 29.90) --
-	( 47.29, 30.63) --
-	( 50.40, 31.33) --
-	( 53.51, 32.63) --
-	( 56.62, 33.82) --
-	( 59.73, 35.45) --
-	( 62.85, 38.26) --
-	( 65.96, 40.62) --
-	( 69.07, 42.34) --
-	( 72.18, 46.05) --
-	( 75.30, 49.23) --
-	( 78.41, 52.36) --
-	( 81.52, 64.35) --
-	( 84.63, 58.30) --
-	( 87.74, 68.19) --
-	( 90.86, 70.67) --
-	( 93.97, 72.59) --
-	( 97.08, 78.45) --
-	(100.19, 78.57) --
-	(103.31, 83.81) --
-	(106.42, 86.56) --
-	(109.53, 85.94) --
-	(112.64, 92.57) --
-	(115.75, 95.46) --
-	(118.87, 98.41) --
-	(121.98,102.64) --
-	(125.09,102.38) --
-	(128.20,106.28) --
-	(131.32,110.72) --
-	(134.43,112.06) --
-	(137.54,116.16) --
-	(140.65,119.03);
 \definecolor{drawColor}{RGB}{231,41,138}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.84, 34.38) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.84, 34.38) --
 	( 37.95, 34.38) --
@@
 
-\path[fill=fillColor] (154.94, 96.84) rectangle (212.73,147.20);
+\path[fill=fillColor] (154.94, 96.84) rectangle (224.55,147.20);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (178.40,120.54) {bijections};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (178.40,120.54) {functions};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (178.40,106.09) {functions};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (178.40,106.09) {permutations};
 \end{scope}

### 2024-04-11 analysis/analyse.R

@@ -2,10 +2,7 @@ library(tidyverse)
 library(scales)
 library(tikzDevice)
 
-K <- 5
-degree <- 10
-
-df <- read.csv("results.csv")
+df <- read.csv("../results/processed/results.csv")
 df$compilation.time <- df$compilation.time / 1000
 df$inference.time <- df$inference.time / 1000
 df$time <- df$compilation.time + df$inference.time
@@ -13,13 +10,14 @@ df$algorithm[df$algorithm == "bfs"] <- "\\textsc{Crane-BFS}"
 df$algorithm[df$algorithm == "greedy"] <- "\\textsc{Crane-Greedy}"
 df$algorithm[df$algorithm == "forclift"] <- "\\textsc{ForcLift}"
 df$algorithm[df$algorithm == "fastwfomc"] <- "\\textsc{FastWFOMC}"
+df$sequence[df$sequence == "bijections"] <- "permutations"
 
 # Sanity check: differences between max and min counts as a percentage of the
 # min count
 #differences <- df %>% group_by(sequence, domain.size) %>%
 #  summarise(diff = 100 * (max(count) - min(count)) / min(count))
 
-tikz(file = "doc/plot.tex", width = 3.32492194445, height = 1.8702685937531252)
+tikz(file = "../doc/plot.tex", width = 3.32492194445, height = 1.8702685937531252)
 ggplot(df, aes(domain.size, time, colour = algorithm, linetype = sequence)) +
   geom_line() +
   scale_y_continuous(trans = log10_trans()) +
@@ -32,6 +30,9 @@ ggplot(df, aes(domain.size, time, colour = algorithm, linetype = sequence)) +
 dev.off()
 
 # ============== DEGREE FINDING (not doing this right now) ================
+
+K <- 5
+degree <- 10
 
 df1 <- df[df$algorithm == "\\textsc{FastWFOMC}" & df$sequence == "bijections",]
 df1 <- df[df$algorithm == "\\textsc{FastWFOMC}" & df$sequence == "functions",]

### 2024-04-12 doc/paper.tex
Writing

@@
 \newtheorem{example}{Example}
-
-% TODO: 9 pages!!!
 
@@
 
-\title{Towards Efficient First-Order Model Counting}
+\title{Towards Practical First-Order Model Counting}
 
@@
 \begin{abstract}
+  TODO: 9 pages!!!
 \end{abstract}
@@
 
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item describe which compilation rules are currently greedy or non-greedy
-    \item my agenda has a plan for proving completeness for $\mathbf{C}^{2}$
-    \item Can I prove that my domain recursion can always simulate the domain
-          recursion of \textsc{ForcLift}?
-  \end{itemize}
-}
-
 \paragraph{Papers to cite.}
 \begin{itemize}
+  \item relevant theoretical work~\cite{DBLP:conf/aaai/MalhotraS22} (there is
+        more, e.g., the LICS 2018 paper)
   \item original domain recursion~\cite{DBLP:conf/nips/Broeck11}
@@
   \end{itemize}
-  \item liftable fragments (TODO: perhaps good sources of benchmarks?)
+  \item liftable fragments
   \begin{itemize}
@@
 
-% TODO: make sure to not call \Crane2 \textsc{Crane}
+\todo[inline]{Disambiguate between \protect\Crane, \textsc{Crane}, and
+  \Cranetwo}
 
@@
 
-\paragraph{Proof of correctness (leave for later).}
-\begin{enumerate}
-  \item Define what it means for a formula to be \emph{consistent}.
-        \begin{itemize}
-          \item The formula (including the mapping of constants to their
-                domains) does not mention a domain together with its subdomain
-                (i.e., all mentioned domains are pairwise disjoint).
-                Specifically, we can't have a subdomain together with its parent
-                domain or a subdomain together with a constant that belongs to
-                its parent domain.
-          \item The target of \texttt{Ref} must also be a consistent formula.
-          \item The initial formula is consistent by definition.
-        \end{itemize}
-  \item Aim to show that \Cranetwo{} works correctly on all consistent formulas.
-  \item Prove that, whenever some compilation rule makes the formula $\phi$
-        inconsistent, greedy compilation rules will make $\phi$ consistent again
-        before $\phi$ encounters non-greedy compilation rules that depend on
-        $\phi$ being consistent.
-        \begin{itemize}
-          \item In particular, prove that shattering and unit propagation will
-                always eliminate the parent domain of the domains introduced by
-                atom counting.
-          \item Constraint removal only applies when it can eliminate the parent
-                domain entirely.
-          \item Prove this for a particular assumption about which compilation
-                rules are set to be greedy. For the greedy algorithm, although
-                all rules are applied in a greedy manner, we still assume that
-                greedy rules will be applied before non-greedy rules.
-        \end{itemize}
-  \item In particular, independent partial groundings and atom counting are the
-        two classical rules that require the formula to be shattered.
-  \end{enumerate}
-
- % TODO: Crane2 uses itself instead of Crane. Not really. By 'Crane', here I
- % mean the process of turning logical formulas into equations. Later on, I use
- % 'Crane' to refer to Crane2. Maybe rename this use of 'Crane' to something
- % else?
 \begin{figure*}[t]
@@
   \item Some experiments vs FastWFOMC
-  \item A proof of completeness
 \end{itemize}
@@
 \section{Preliminaries}
+
+\subsection{Logic}
+
+\todo[inline,caption={}]{
+  \begin{itemize}
+    \item What notation am I using for FOL? Introduce equality cardinality
+          constraints, counting quantifiers, etc.
+    \item Maybe say ``structure'' instead of interpretation?
+    \item Should I say ``sort'' instead of domain everywhere?
+  \end{itemize}
+}
+
+\begin{table*}
+  \centering
+  \begin{tabular}{llclll}
+    \toprule
+    Logic & Sorts & Constants & Variables & Quantifiers & Additional atomic constraints\\
+    \midrule
+    \FO & one or more & \cmark & unlimited & $\forall$, $\exists$ & $s = t$\\
+    \Ctwo & one & \xmark & two & $\forall$, $\exists$, $\exists^{= k}$, $\exists^{\le k}$, $\exists^{\ge k}$ & ---\\
+    \UFO & one & \xmark & two & $\forall$ & $|p| = m$\\
+    \bottomrule
+  \end{tabular}
+  \caption[]{A comparison of the three logics used in WFOMC in terms of:
+    \begin{enumerate*}[label=(\roman*)]
+      \item the number of sorts,
+      \item support for constants,
+      \item the maximum number of variables,
+      \item allowed quantifiers, and
+      \item atomic constructions in addition to those of the form $p(t_{1}, \dots, t_{n})$ for some predicate symbol $p$ and terms $t_{1}, \dots, t_{n}$.
+    \end{enumerate*}
+    Here:
+    \begin{enumerate*}[label=(\roman*)]
+      \item $k$ and $m$ are non-negative integers, the latter of which can depend on the domain size,
+      \item $p$ is a predicate symbol, and
+      \item $s$ and $t$ are terms.
+    \end{enumerate*}
+  }\label{tbl:logics}
+\end{table*}
+
+\paragraph{Three types of logics}
+\begin{itemize}
+  \item See \cref{tbl:logics} for a detailed comparison. The notation introduced
+        in the table is standard for \Ctwo{}, new for \UFO{}, and redefined to
+        be more specific for \FO{}.
+  \item All three logics are function-free.
+  \item Domains are always assumed to be finite.
+  \item
+        \begin{itemize}
+          \item \FO{} is used as the input format for
+                \textsc{ForcLift}\footnote{\url{https://github.com/UCLA-StarAI/Forclift}}~\cite{DBLP:conf/ijcai/BroeckTMDR11}
+                and its extensions
+                \textsc{Crane}\footnote{\url{https://doi.org/10.5281/zenodo.8004077}}~\cite{DBLP:conf/kr/DilkasB23}
+                and \Cranetwo{}.
+          \item \Ctwo{} is discussed in the literature on
+                \textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21} and related
+                methods~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}
+          \item \UFO{} is the input format supported by a version of
+                \textsc{FastWFOMC} obtained directly from the authors. Note that
+                the publicly available
+                version\footnote{\url{https://www.comp.nus.edu.sg/~tvanbr/software/fastwfomc.tar.gz}}
+                does not support any cardinality constraints.
+        \end{itemize}
+  \item Note that, in the case of \textsc{ForcLift} and its extensions, support
+        for a formula as valid input does not imply that the algorithm will be
+        able to compile the formula into a circuit or graph suitable for lifted
+        model counting. However, it is known that \textsc{ForcLift} compilation
+        is guaranteed to succeed on any \FO{} formula without constants and with
+        at most two variables~\cite{DBLP:conf/nips/Broeck11}.
+\end{itemize}
+
+\todo[inline]{Explain arity and its notation. Define `ground'?}
+
+A \emph{formula} is a set of clauses. A \emph{clause} is of the form
+$\forall x_{1} \in \Delta_{1}\text{. }\forall x_{2} \in \Delta_{2}\dots\text{
+}\forall x_{n} \in \Delta_{n}\text{. }\phi(x_{1}, x_{2}, \dots, x_{n})$, where
+$\phi$ is a disjunction of literals that only contain variables
+$x_{1}, \dots, x_{n}$ (and any constants). A \emph{literal} is either an atom or
+its negation. An \emph{atom} is of the form $p(t_{1}, \dots, t_{m})$, where $p$
+is a predicate, and $t_{1}, \dots, t_{m}$ are terms. A \emph{term} is either a
+variable or a constant. Throughout the paper, we use set-theoretic notation,
+interpreting a formula as a set of clauses and a clause as a set of literals.
+
+For any clause or literal $l$, let $\Vars(l)$ denote the set of variables in
+$l$. For any (bound) variable $v$, let $\Dom(v)$ denote the domain over which
+$v$ is quantified. For a literal $l$,
+$\Doms(l) \coloneqq \{\, \Dom(v) \mid v \in \Vars(l) \,\}$. Similarly, for any
+clause $C$, let $\Doms(C) = \{\, \Dom(v) \mid v \in \Vars(C) \,\}$.
+
+\begin{definition}[Model]\label{def:model}
+  Let $\phi$ be a formula in \FO{}. For every predicate $p/n$ in $\phi$, let
+  ${(\Delta_{i}^{p})}_{i=1}^{n}$ be a list of the corresponding domains (not
+  necessarily distinct). Let $\sigma$ be a map from the domains of $\phi$ to
+  their interpretations as sets such that:
+  \begin{itemize}
+    \item the sets are pairwise disjoint, and
+    \item the constants in $\phi$ are included in the corresponding domains.
+  \end{itemize}
+  Then an \emph{interpretation} of $\phi$ (with respect to $\sigma$) is a set
+  $M$ of ground literals defined by adding either $p(\mathbf{t})$ or
+  $\neg p(\mathbf{t})$ for every predicate $p/n$ in $\phi$ and $n$-tuple
+  $\mathbf{t} \in \prod_{i=1}^{n} \sigma(\Delta_{i}^{p})$. An interpretation is
+  a \emph{model} if it satisfies $\phi$ (see Appendix~A of~Dilkas and
+  Belle~\shortcite{DBLP:journals/corr/abs-2306-04189} for more details).
+\end{definition}
+
+\begin{definition}[WFOMC]
+  Continuing from \cref{def:model}, for every predicate $p/n$ in $\phi$, let
+  $w^{+}(p), w^{-}(p) \in \mathbb{R}$ be its (positive and negative)
+  \emph{weights}. Unless explicitly specified otherwise, we assume weights to be
+  equal to one. The \emph{(symmetric) weighted first-order model count} (WFOMC)
+  of $\phi$ (with respect to $\sigma$, $w^{+}$, and $w^{-}$) is the quantity
+  \[
+    \sum_{M \models \phi} \prod_{p(\mathbf{t}) \in M} w^{+}(p) \prod_{\neg p(\mathbf{t}) \in M} w^{-}(p),
+  \]
+  where the sum is over all models of $\phi$.
+\end{definition}
 
@@
   \item Clauses written on separate lines are implicitly conjoined
-  \item For weights, for any predicate symbol $p$, we write
-        $w^{+}(p), w^{-}(p) \in \mathbb{R}$ for its positive and negative
-        weights, respectively. All weights not explicitly acknowledged are
-        assumed to be equal to one.
 \end{itemize}
@@
     \item explain how this works for function calls too
-    \item introduce WFOMC as a problem
   \end{itemize}
@@
 \end{definition}
-
-\subsection{Logic}
-
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item What notation am I using for FOL? Introduce equality cardinality
-          constraints, counting quantifiers, etc.
-    \item Need (W)FOMC semantics. What is an interpretation? What is a model?
-    \item Should table caption go above or below the table?
-    \item Define terms.
-    \item Maybe say ``structure'' instead of interpretation?
-    \item What's the right table heading capitalization for KR?
-    \item Should I say ``sort'' instead of domain everywhere?
-  \end{itemize}
-}
-
-\begin{table*}
-  \centering
-  \begin{tabular}{llclll}
-    \toprule
-    Logic & Sorts & Constants & Variables & Quantifiers & Additional atomic constraints\\
-    \midrule
-    \FO & one or more & \cmark & unlimited & $\forall$, $\exists$ & $s = t$\\
-    \Ctwo & one & \xmark & two & $\forall$, $\exists$, $\exists^{= k}$, $\exists^{\le k}$, $\exists^{\ge k}$ & ---\\
-    \UFO & one & \xmark & two & $\forall$ & $|p| = m$\\
-    \bottomrule
-  \end{tabular}
-  \caption[]{A comparison of the three logics used in WFOMC in terms of:
-    \begin{enumerate*}[label=(\roman*)]
-      \item the number of sorts,
-      \item support for constants,
-      \item the maximum number of variables,
-      \item allowed quantifiers, and
-      \item atomic constructions in addition to those of the form $p(t_{1}, \dots, t_{n})$ for some predicate symbol $p$ and terms $t_{1}, \dots, t_{n}$.
-    \end{enumerate*}
-    Here:
-    \begin{enumerate*}[label=(\roman*)]
-      \item $k$ and $m$ are non-negative integers, the latter of which can depend on the domain size,
-      \item $p$ is a predicate symbol, and
-      \item $s$ and $t$ are terms.
-    \end{enumerate*}
-  }\label{tbl:logics}
-\end{table*}
-
-\paragraph{Three types of logics}
-\begin{itemize}
-  \item All three logics are function-free.
-  \item Domains are always assumed to be finite.
-  \item See \cref{tbl:logics} for a detailed comparison. \FO{} is used as the
-        input format for \textsc{ForcLift} and its extensions \textsc{Crane} and
-        \Cranetwo{}. \Ctwo{} is used in the literature on \textsc{FastWFOMC} and
-        related methods (TODO: citations). \UFO{} is the input format supported
-        by a privately-obtained version of \textsc{FastWFOMC}. Note that the
-        publicly available version does not support any cardinality constraints.
-  \item In the case of \textsc{ForcLift} and its extensions, support for a
-        formula as valid input does not imply that the algorithm will be able to
-        compile the formula into a circuit or graph suitable for lifted model
-        counting. However, it is known that \textsc{ForcLift} compilation is
-        guaranteed to succeed on any \FO{} formula without constants and with at
-        most two variables (TODO: citation).
-\end{itemize}
-
-A \emph{formula} is a set of clauses. A \emph{clause} is of the form
-$\forall x_{1} \in \Delta_{1}\forall x_{2} \in \Delta_{2}\dots\forall x_{n} \in \Delta_{n} \phi(x_{1}, x_{2}, \dots, x_{n})$,
-where $\phi$ is a disjunction of literals that only contain variables
-$x_{1}, \dots, x_{n}$ (and any constants). A \emph{literal} is either an atom or
-its negation. An \emph{atom} is of the form $P(t_{1}, \dots, t_{m})$, where $P$
-is a predicate, and $t_{1}, \dots, t_{m}$ are terms. A \emph{term} is either a
-variable or a constant.
-
-\todo[inline]{explain set-based notation for a clause (iterating over all
-  literals)}
-
-For any clause or literal $l$, let $\Vars(l)$ denote the set of variables in
-$l$.
-
-For any (bound) variable $v$, let $\Dom(v)$ denote the domain over which $v$ is
-quantified. For a literal $l$,
-$\Doms(l) \coloneqq \{\, \Dom(v) \mid v \in \Vars(l) \,\}$. Similarly, for any
-clause $C$, let $\Doms(C) = \{\, \Dom(v) \mid v \in \Vars(C) \,\}$.
 
@@
 
-NOTE: function calls such as $f(n-m)$ and $f(n-m-1)$ are ignored.
-
 \subsection{Propagating Domain Size Assumptions}\label{sec:simplifying}
@@
 \begin{algorithm}[t]
-  \caption{\protect\Propagate{$\phi$, $\Delta$, $n$} TODO: find the source code and check: (1) what we're doing with unit clauses, (2) whether we just randomly pick any literal to negate}\label{alg2}
+  \caption{\protect\Propagate{$\phi$, $\Delta$, $n$}}\label{alg2}
   \KwIn{formula $\phi$, domain $\Delta$, domain size $n \in \{\, 0, 1 \,\}$}
@@
 
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item Can I prove that the additions to smoothing outlined in the rest of
-          this section `do the right thing'?
-    \item I could include more info about the smoothing algorithm that didn't
-          make it into the previous paper.
-  \end{itemize}
-}
+\todo[inline]{Can I prove that the additions to smoothing outlined in the rest
+  of this section `do the right thing'?}
 
@@
 
+\subsection{Smoothing the FCG}
+
+\begin{algorithm}
+  \caption{Propagate atoms for smoothing across the FCG}\label{alg:smoothing}
+  \SetKwData{changed}{changed}
+  \KwIn{FCG $(V, s, N^+, \tau)$}
+  \KwIn{function $\iota$ that maps vertex types in $\mathcal{T}$ to sets of atoms}
+  \KwIn{functions $\{\,f_t\,\}_{t \in \mathcal{T}}$ that map a list of sets of atoms to a set of atoms}
+  \KwOut{function $S$ that maps vertices in $V$ to sets of atoms}
+  $S \gets \{\, v \mapsto \iota(\tau(v)) \mid v \in V \,\}$\;
+  $\changed \gets \texttt{true}$\;
+  \While{\changed}{
+    $\changed \gets \texttt{false}$\;
+    \ForEach{vertex $v \in V$}{
+      $S' \gets f_{\tau(v)}(\langle S(w) \mid w \in N^+(v) \rangle)$\;
+      \If{$S' \ne S(v)$}{
+        $\changed \gets \texttt{true}$\;
+        $S(v) \gets S'$\;
+      }
+    }
+  }
+\end{algorithm}
+
+\todo[inline]{Insert motivation for smoothing from Section 3.4.\ of the ForcLift
+  paper.}
+
+Originally, smoothing was (and still is) a two-step process. First, atoms that
+are still accounted for in the circuit are propagated upwards. Then, at vertices
+of certain types, missing atoms are detected and additional sinks are created to
+account for them. If left unchanged, the first step of this process would result
+in an infinite loop whenever a cycle is encountered. \Cref{alg:smoothing}
+outlines how the first step can be adapted to an arbitrary directed graph.
+
 \subsection{Stage 1: Propagating Unit Clauses `Upwards'}
@@
 
-% TODO
-% \item Whenever the set of unit clauses received from the child node contains two
-% formulas $\phi(x)$ and $\forall X \in \Delta\text{.
-% } X \ne x \Rightarrow \phi(X)$ (i.e., the only difference between the two
-% formulas is that one has the constant $x$ whereas the other one has a variable
-% $X \ne x$), merge them into $\forall X \in \Delta\text{. }\phi(X)$.
+We never need to add smoothing nodes after \texttt{Ref} or constraint removal
+nodes. However, for domain recursion we must do the following.
 
-\begin{description}
-  \item[\texttt{Ref}:] nothing.
-  \item[Constraint removal:] nothing.
-  \item[Domain recursion:]
 \begin{enumerate}
-          \item Whenever the set of unit clauses of the child node contains two
-                formulas $\phi(x)$ and $\forall X \in \Delta\text{.
-                } X \ne x \Rightarrow \phi(X)$ (i.e., the only difference
-                between the two formulas is that one has the constant $x$
-                whereas the other one has a variable $X \ne x$), merge them into
-                $\forall X \in \Delta\text{. }\phi(X)$.
-          \item Add smoothing nodes below the domain recursion node for the
-                difference between the unit clauses assigned to the domain
-                recursion node during Stage 1 and the unit clauses of the child
-                node post-processed by the step above. For example, if the child
-                node `covers' only $p(x)$, then Stage 1 assigns
-                $\forall X \in \Delta\text{. }p(X)$ to the domain recursion
-                node. The smoothing node below the domain recursion node then
-                has the clause $\forall X \in \Delta\text{.
-                } X \ne x \Rightarrow p(X)$.
+  \item Whenever the set of unit clauses of the child node contains two formulas
+        $\phi(x)$ and $\forall X \in \Delta\text{.
+        } X \ne x \Rightarrow \phi(X)$ (i.e., the only difference between the
+        two formulas is that one has the constant $x$ whereas the other one has
+        a variable $X \ne x$), merge them into $\forall X \in \Delta\text{.
+        }\phi(X)$.
+  \item Add smoothing nodes below the domain recursion node for the difference
+        between the unit clauses assigned to the domain recursion node during
+        Stage 1 and the unit clauses of the child node post-processed by the
+        step above. For example, if the child node `covers' only $p(x)$, then
+        Stage 1 assigns $\forall X \in \Delta\text{. }p(X)$ to the domain
+        recursion node. The smoothing node below the domain recursion node then
+        has the clause $\forall X \in \Delta\text{. } X \ne x \Rightarrow p(X)$.
 \end{enumerate}
-\end{description}
 
@@
 
-\section{Experiments}
+\section{Experimental Evaluation}
 

### 2024-04-12 doc/paper.tex
Add lots of references (and some other changes)

@@
 
-\newcommand{\Cranetwo}{\textsc{Crane}~2}
+\newcommand{\Cranetwo}{\textsc{Crane2}}
+\newcommand{\Cranebfs}{\textsc{Crane2-BFS}}
+\newcommand{\Cranegreedy}{\textsc{Crane2-Greedy}}
 
@@
 
-% TODO: check if this follows the formatting guidelines
 \author{%
@@
 \affiliations
-$^1$Indian Institute of Technology Bombay, India\\
-$^2$National University of Singapore, Singapore\\
-$^3$University of Toronto, Canada\\
+$^1$Indian Institute of Technology Bombay, Mumbai, India\\
+$^2$National University of Singapore, Singapore, Singapore\\
+$^3$University of Toronto, Toronto, Canada\\
 \emails
@@
 
+\todo[inline,caption={}]{
+  Add some papers mentioned in:
+  \begin{itemize}
+    \item very recent work
+    \item my previous paper, including:
+    \begin{itemize}
+      \item other liftable fragments
+      \item some more theory papers, e.g., LICS 2018
+    \end{itemize}
+  \end{itemize}
+}
+
 \paragraph{Papers to cite.}
 \begin{itemize}
-  \item relevant theoretical work~\cite{DBLP:conf/aaai/MalhotraS22} (there is
-        more, e.g., the LICS 2018 paper)
+  \item overviews
+        \begin{itemize}
+          \item lifted probabilistic inference~\cite{DBLP:conf/ecai/Kersting12}
+          \item recent overview paper~\cite{DBLP:conf/ijcai/Kuzelka23}
+        \end{itemize}
+  \item Alternative definition~\cite{DBLP:journals/cacm/GogateD16}
+  \item relevant theoretical work~\cite{DBLP:conf/aaai/MalhotraS22}
   \item original domain recursion~\cite{DBLP:conf/nips/Broeck11}
-  \item recent overview paper~\cite{DBLP:conf/ijcai/Kuzelka23}
-  \item conjecturing recurrence relations~\cite{DBLP:conf/ilp/BarvinekB0ZK21}
   \item algorithms
@@
           \item \textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21}
+          \item \textsc{L2C}~\cite{DBLP:conf/kr/KazemiP16} (similarly to us
+                compiles to C++ code, but (probably) doesn't work on as many
+                formulas)
           \item approximate~\cite{DBLP:conf/ijcai/BremenK20}
+          \item for Markov logic networks~\cite{DBLP:journals/ml/RichardsonD06}
+                \begin{itemize}
+                  \item \textsc{Magician}~\cite{DBLP:conf/aaai/VenugopalSG15}
+                  \item \textsc{Tuffy}~\cite{DBLP:journals/pvldb/NiuRDS11}
+                  \item \textsc{Alchemy}~\cite{DBLP:journals/cacm/GogateD16}
+                        (same as the alternative definition)
                 \end{itemize}
+        \end{itemize}
+  \item complexity
+        \begin{itemize}
+          \item liftability~\cite{DBLP:conf/starai/JaegerB12}
+          \item hardness for three variables~\cite{DBLP:conf/pods/BeameBGS15}
           \item liftable fragments
@@
                   \item linear order axioms~\cite{DBLP:conf/aaai/TothK23}
+                  \item some liftable fragments~\cite{DBLP:conf/nips/KazemiKBP16}
+                \end{itemize}
         \end{itemize}
@@
                 sequences~\cite{DBLP:conf/ijcai/SvatosJT0K23}
+          \item conjecturing recurrence
+                relations~\cite{DBLP:conf/ilp/BarvinekB0ZK21}
+          \item probabilistic logic
+                programming~\cite{DBLP:journals/ijar/RiguzziBZCL17} (WFOMC was
+                shown to be supreme)
+          \item probabilistic databases~\cite{DBLP:journals/debu/GribkoffSB14}
+        \end{itemize}
+  \item lifted inference in other domains
+        \begin{itemize}
+          \item constraint satisfaction~\cite{DBLP:journals/jair/TotisDRK23}
+          \item answer set programming~\cite{DBLP:journals/ijar/AzzoliniR23}
         \end{itemize}
@@
 
-\todo[inline]{Disambiguate between \protect\Crane, \textsc{Crane}, and
-  \Cranetwo}
-
+\todo[inline,caption={}]{
+  Where to put this?
   \paragraph{Changes to the compilation process.}
@@
           grounding operations on $\Delta$ on $P$ is at most one.
-  \item when checking whether recursion is possible between a source and a
+    \item When checking whether recursion is possible between a source and a
           target formula, the target formula (maybe the source formula as well?)
@@
           equivalent to the formula being `unshattered'. Such formulas could be
-        seen as transitory, and allowing such recursive calls leads to FCGs that
-        I cannot make sense of.
+          seen as transitory, and allowing such recursive calls leads to FCGs
+          that I cannot make sense of.
   \end{itemize}
+}
 
@@
                 the publicly available
-                version\footnote{\url{https://www.comp.nus.edu.sg/~tvanbr/software/fastwfomc.tar.gz}}
+                version\footnote{\url{https://comp.nus.edu.sg/~tvanbr/software/fastwfomc.tar.gz}}
                 does not support any cardinality constraints.
@@
 \begin{algorithm}[t]
-  \caption{The core part of \Cranetwo{} that compiles a formula...}\label{alg:main}% TODO: start here
+  \caption{The main part of \Cranetwo{} that compiles a formula into a set of
+    equations, including the base cases of recursive functions}\label{alg:main}
   \KwIn{formula $\phi$}
@@
 
-See \cref{alg:main}.
-
-We write \Crane for a slight modification of the original \textsc{Crane} that
-compiles a formula $\phi$ into:
+We write \Crane for the first-order knowledge compilation algorithm of the
+original \textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23} that compiles a formula
+$\phi$ into:
 \begin{itemize}
@@
 
-% TODO: update: crane or crane2
-The evaluation of base cases is done by simplifying the clauses and then using
-\textsc{Crane} to find the base cases. A particular domain is selected, and the
-clauses are simplified. Then, \textsc{Crane} is called on those clauses to
-evaluate the base cases. After that, we change the function names and variable
-to make it consistent with the previous domain to variable mapping, and append
-these base cases to the set of equations.
+\todo[inline,caption={}]{
+  \begin{itemize}
+    \item extend it to work with base cases that are themselves recursive
+    \item \textsc{Crane}, \Cranetwo{}, or \Crane (here and elsewhere)?
+  \end{itemize}
+}
 
-\todo[inline,caption={}]{extend it to work with base cases that are themselves
-  recursive}
+See \cref{alg:main}. The evaluation of base cases is done by simplifying the
+clauses and then using \textsc{Crane} to find the base cases. A particular
+domain is selected, and the clauses are simplified. Then, \textsc{Crane} is
+called on those clauses to evaluate the base cases. After that, we change the
+function names and variable to make it consistent with the previous domain to
+variable mapping, and append these base cases to the set of equations.
 
@@
 
-Comparing \textsc{Crane} and \textsc{FastWFOMC} on a larger set of benchmarks is
+Comparing \Cranetwo{} and \textsc{FastWFOMC} on a larger set of benchmarks is
 challenging because there is no automated way to translate a formula in \FO{} or
@@
         Python-FLINT~0.5.0.
+  \item The knowledge compilation part of both \textsc{Crane} and \Cranetwo{}
+        can be executed using either greedy (similar to \textsc{ForcLift}) or
+        breadth-first search. We use both in our experiments, denoting them as
+        \Cranegreedy{} and \Cranebfs{}, respectively.
 \end{itemize}
@@
         increasing runtimes of \textsc{FastWFOMC}.
-  \item Note that \textsc{Crane-BFS} is able to handle more instances than
+  \item Note that \Cranebfs{} is able to handle more instances than
         \textsc{ForcLift} (e.g., the permutation-counting problem in our
         experiments and other problems in my previous work).
-  \item Although the search/compilation part is slower in \textsc{Crane} than in
+  \item Although the search/compilation part is slower in \Cranetwo{} than in
         \textsc{ForcLift}, the difference is negligible.
@@
         independent of domain sizes). Indeed, the maximum inference time of both
-        \textsc{Crane-BFS} and \textsc{Crane-Greedy} across these experiments is
+        \Cranebfs{} and \Cranegreedy{} across these experiments is
         only \SI{4}{\milli\second}.
-  \item The runtimes of \textsc{Crane} have lower variation than those of
+  \item The runtimes of \Cranetwo{} have lower variation than those of
         \textsc{ForcLift} because with \textsc{ForcLift} we compile the formula
-        anew for each domain size whereas with \textsc{Crane} we compile it once
+        anew for each domain size whereas with \Cranetwo{} we compile it once
         and reuse the resulting C++ program for all domain sizes.
   \item As another point of comparison,---in at most
-        \SI{41}{\second}---\textsc{Crane} scales up to domains of sizes \num{e4}
+        \SI{41}{\second}---\Cranetwo{} scales up to domains of sizes \num{e4}
         and \num{3e5} in permutation- and function-counting problems,
@@
 
-% TODO: for references, maybe fix the spelling of Kuzelka's name
-
 % TODO: the report has some (long) examples of formulas being transformed into

### 2024-04-12 doc/plot.tex
Add lots of references (and some other changes)

@@
-% Created by tikzDevice version 0.12.6 on 2024-04-04 08:49:14
+% Created by tikzDevice version 0.12.6 on 2024-04-12 11:27:55
 % !TEX encoding = UTF-8 Unicode
@@
 \begin{scope}
-\path[clip] ( 29.55, 25.11) rectangle (145.94,130.66);
+\path[clip] ( 29.55, 25.11) rectangle (141.96,130.66);
 \definecolor{fillColor}{RGB}{255,255,255}
 
-\path[fill=fillColor] ( 29.55, 25.11) rectangle (145.94,130.66);
+\path[fill=fillColor] ( 29.55, 25.11) rectangle (141.96,130.66);
 \definecolor{drawColor}{gray}{0.87}
@@
 \path[draw=drawColor,line width= 0.1pt,line join=round] ( 29.55, 36.74) --
-	(145.94, 36.74);
+	(141.96, 36.74);
 
 \path[draw=drawColor,line width= 0.1pt,line join=round] ( 29.55, 71.11) --
-	(145.94, 71.11);
+	(141.96, 71.11);
 
 \path[draw=drawColor,line width= 0.1pt,line join=round] ( 29.55,105.49) --
-	(145.94,105.49);
+	(141.96,105.49);
 
-\path[draw=drawColor,line width= 0.1pt,line join=round] ( 47.29, 25.11) --
-	( 47.29,130.66);
+\path[draw=drawColor,line width= 0.1pt,line join=round] ( 46.68, 25.11) --
+	( 46.68,130.66);
 
-\path[draw=drawColor,line width= 0.1pt,line join=round] ( 78.41, 25.11) --
-	( 78.41,130.66);
+\path[draw=drawColor,line width= 0.1pt,line join=round] ( 76.74, 25.11) --
+	( 76.74,130.66);
 
-\path[draw=drawColor,line width= 0.1pt,line join=round] (109.53, 25.11) --
-	(109.53,130.66);
+\path[draw=drawColor,line width= 0.1pt,line join=round] (106.80, 25.11) --
+	(106.80,130.66);
 
-\path[draw=drawColor,line width= 0.1pt,line join=round] (140.65, 25.11) --
-	(140.65,130.66);
+\path[draw=drawColor,line width= 0.1pt,line join=round] (136.85, 25.11) --
+	(136.85,130.66);
 
 \path[draw=drawColor,line width= 0.2pt,line join=round] ( 29.55, 53.93) --
-	(145.94, 53.93);
+	(141.96, 53.93);
 
 \path[draw=drawColor,line width= 0.2pt,line join=round] ( 29.55, 88.30) --
-	(145.94, 88.30);
+	(141.96, 88.30);
 
 \path[draw=drawColor,line width= 0.2pt,line join=round] ( 29.55,122.67) --
-	(145.94,122.67);
+	(141.96,122.67);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] ( 31.72, 25.11) --
-	( 31.72,130.66);
+\path[draw=drawColor,line width= 0.2pt,line join=round] ( 31.65, 25.11) --
+	( 31.65,130.66);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] ( 62.85, 25.11) --
-	( 62.85,130.66);
+\path[draw=drawColor,line width= 0.2pt,line join=round] ( 61.71, 25.11) --
+	( 61.71,130.66);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] ( 93.97, 25.11) --
-	( 93.97,130.66);
+\path[draw=drawColor,line width= 0.2pt,line join=round] ( 91.77, 25.11) --
+	( 91.77,130.66);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] (125.09, 25.11) --
-	(125.09,130.66);
+\path[draw=drawColor,line width= 0.2pt,line join=round] (121.82, 25.11) --
+	(121.82,130.66);
 \definecolor{drawColor}{RGB}{27,158,119}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.84, 52.07) --
-	( 37.95, 52.04) --
-	( 41.06, 52.04) --
-	( 44.17, 52.04) --
-	( 47.29, 52.04) --
-	( 50.40, 52.05) --
-	( 53.51, 52.04) --
-	( 56.62, 52.05) --
-	( 59.73, 52.04) --
-	( 62.85, 52.04) --
-	( 65.96, 52.04) --
-	( 69.07, 52.04) --
-	( 72.18, 52.04) --
-	( 75.30, 52.04) --
-	( 78.41, 52.05) --
-	( 81.52, 52.05) --
-	( 84.63, 52.04) --
-	( 87.74, 52.04) --
-	( 90.86, 52.09) --
-	( 93.97, 52.05) --
-	( 97.08, 52.05) --
-	(100.19, 52.05) --
-	(103.31, 52.05) --
-	(106.42, 52.04) --
-	(109.53, 52.04) --
-	(112.64, 52.04) --
-	(115.75, 52.04) --
-	(118.87, 52.04) --
-	(121.98, 52.04) --
-	(125.09, 52.05) --
-	(128.20, 52.05) --
-	(131.32, 52.05) --
-	(134.43, 52.04) --
-	(137.54, 52.05) --
-	(140.65, 52.04);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.66, 52.07) --
+	( 37.66, 52.04) --
+	( 40.67, 52.04) --
+	( 43.67, 52.04) --
+	( 46.68, 52.04) --
+	( 49.68, 52.05) --
+	( 52.69, 52.04) --
+	( 55.70, 52.05) --
+	( 58.70, 52.04) --
+	( 61.71, 52.04) --
+	( 64.71, 52.04) --
+	( 67.72, 52.04) --
+	( 70.73, 52.04) --
+	( 73.73, 52.04) --
+	( 76.74, 52.05) --
+	( 79.74, 52.05) --
+	( 82.75, 52.04) --
+	( 85.75, 52.04) --
+	( 88.76, 52.09) --
+	( 91.77, 52.05) --
+	( 94.77, 52.05) --
+	( 97.78, 52.05) --
+	(100.78, 52.05) --
+	(103.79, 52.04) --
+	(106.80, 52.04) --
+	(109.80, 52.04) --
+	(112.81, 52.04) --
+	(115.81, 52.04) --
+	(118.82, 52.04) --
+	(121.82, 52.05) --
+	(124.83, 52.05) --
+	(127.84, 52.05) --
+	(130.84, 52.04) --
+	(133.85, 52.05) --
+	(136.85, 52.04);
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.84, 54.53) --
-	( 37.95, 54.50) --
-	( 41.06, 54.50) --
-	( 44.17, 54.49) --
-	( 47.29, 54.49) --
-	( 50.40, 54.49) --
-	( 53.51, 54.49) --
-	( 56.62, 54.50) --
-	( 59.73, 54.50) --
-	( 62.85, 54.49) --
-	( 65.96, 54.49) --
-	( 69.07, 54.49) --
-	( 72.18, 54.49) --
-	( 75.30, 54.49) --
-	( 78.41, 54.50) --
-	( 81.52, 54.50) --
-	( 84.63, 54.50) --
-	( 87.74, 54.50) --
-	( 90.86, 54.49) --
-	( 93.97, 54.50) --
-	( 97.08, 54.50) --
-	(100.19, 54.49) --
-	(103.31, 54.50) --
-	(106.42, 54.50) --
-	(109.53, 54.50) --
-	(112.64, 54.50) --
-	(115.75, 54.49) --
-	(118.87, 54.50) --
-	(121.98, 54.50) --
-	(125.09, 54.50) --
-	(128.20, 54.50) --
-	(131.32, 54.50) --
-	(134.43, 54.50) --
-	(137.54, 54.50) --
-	(140.65, 54.50);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.66, 54.53) --
+	( 37.66, 54.50) --
+	( 40.67, 54.50) --
+	( 43.67, 54.49) --
+	( 46.68, 54.49) --
+	( 49.68, 54.49) --
+	( 52.69, 54.49) --
+	( 55.70, 54.50) --
+	( 58.70, 54.50) --
+	( 61.71, 54.49) --
+	( 64.71, 54.49) --
+	( 67.72, 54.49) --
+	( 70.73, 54.49) --
+	( 73.73, 54.49) --
+	( 76.74, 54.50) --
+	( 79.74, 54.50) --
+	( 82.75, 54.50) --
+	( 85.75, 54.50) --
+	( 88.76, 54.49) --
+	( 91.77, 54.50) --
+	( 94.77, 54.50) --
+	( 97.78, 54.49) --
+	(100.78, 54.50) --
+	(103.79, 54.50) --
+	(106.80, 54.50) --
+	(109.80, 54.50) --
+	(112.81, 54.49) --
+	(115.81, 54.50) --
+	(118.82, 54.50) --
+	(121.82, 54.50) --
+	(124.83, 54.50) --
+	(127.84, 54.50) --
+	(130.84, 54.50) --
+	(133.85, 54.50) --
+	(136.85, 54.50);
 \definecolor{drawColor}{RGB}{217,95,2}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.84, 49.39) --
-	( 37.95, 49.33) --
-	( 41.06, 49.33) --
-	( 44.17, 49.33) --
-	( 47.29, 49.33) --
-	( 50.40, 49.33) --
-	( 53.51, 49.33) --
-	( 56.62, 49.35) --
-	( 59.73, 49.35) --
-	( 62.85, 49.33) --
-	( 65.96, 49.33) --
-	( 69.07, 49.33) --
-	( 72.18, 49.33) --
-	( 75.30, 49.33) --
-	( 78.41, 49.33) --
-	( 81.52, 49.35) --
-	( 84.63, 49.35) --
-	( 87.74, 49.35) --
-	( 90.86, 49.33) --
-	( 93.97, 49.33) --
-	( 97.08, 49.33) --
-	(100.19, 49.33) --
-	(103.31, 49.33) --
-	(106.42, 49.33) --
-	(109.53, 49.35) --
-	(112.64, 49.35) --
-	(115.75, 49.33) --
-	(118.87, 49.33) --
-	(121.98, 49.33) --
-	(125.09, 49.33) --
-	(128.20, 49.33) --
-	(131.32, 49.33) --
-	(134.43, 49.35) --
-	(137.54, 49.35) --
-	(140.65, 49.33);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.66, 49.39) --
+	( 37.66, 49.33) --
+	( 40.67, 49.33) --
+	( 43.67, 49.33) --
+	( 46.68, 49.33) --
+	( 49.68, 49.33) --
+	( 52.69, 49.33) --
+	( 55.70, 49.35) --
+	( 58.70, 49.35) --
+	( 61.71, 49.33) --
+	( 64.71, 49.33) --
+	( 67.72, 49.33) --
+	( 70.73, 49.33) --
+	( 73.73, 49.33) --
+	( 76.74, 49.33) --
+	( 79.74, 49.35) --
+	( 82.75, 49.35) --
+	( 85.75, 49.35) --
+	( 88.76, 49.33) --
+	( 91.77, 49.33) --
+	( 94.77, 49.33) --
+	( 97.78, 49.33) --
+	(100.78, 49.33) --
+	(103.79, 49.33) --
+	(106.80, 49.35) --
+	(109.80, 49.35) --
+	(112.81, 49.33) --
+	(115.81, 49.33) --
+	(118.82, 49.33) --
+	(121.82, 49.33) --
+	(124.83, 49.33) --
+	(127.84, 49.33) --
+	(130.84, 49.35) --
+	(133.85, 49.35) --
+	(136.85, 49.33);
 \definecolor{drawColor}{RGB}{117,112,179}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.84, 29.90) --
-	( 37.95, 30.63) --
-	( 41.06, 30.63) --
-	( 44.17, 29.90) --
-	( 47.29, 30.63) --
-	( 50.40, 31.33) --
-	( 53.51, 32.63) --
-	( 56.62, 33.82) --
-	( 59.73, 35.45) --
-	( 62.85, 38.26) --
-	( 65.96, 40.62) --
-	( 69.07, 42.34) --
-	( 72.18, 46.05) --
-	( 75.30, 49.23) --
-	( 78.41, 52.36) --
-	( 81.52, 64.35) --
-	( 84.63, 58.30) --
-	( 87.74, 68.19) --
-	( 90.86, 70.67) --
-	( 93.97, 72.59) --
-	( 97.08, 78.45) --
-	(100.19, 78.57) --
-	(103.31, 83.81) --
-	(106.42, 86.56) --
-	(109.53, 85.94) --
-	(112.64, 92.57) --
-	(115.75, 95.46) --
-	(118.87, 98.41) --
-	(121.98,102.64) --
-	(125.09,102.38) --
-	(128.20,106.28) --
-	(131.32,110.72) --
-	(134.43,112.06) --
-	(137.54,116.16) --
-	(140.65,119.03);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.66, 29.90) --
+	( 37.66, 30.63) --
+	( 40.67, 30.63) --
+	( 43.67, 29.90) --
+	( 46.68, 30.63) --
+	( 49.68, 31.33) --
+	( 52.69, 32.63) --
+	( 55.70, 33.82) --
+	( 58.70, 35.45) --
+	( 61.71, 38.26) --
+	( 64.71, 40.62) --
+	( 67.72, 42.34) --
+	( 70.73, 46.05) --
+	( 73.73, 49.23) --
+	( 76.74, 52.36) --
+	( 79.74, 64.35) --
+	( 82.75, 58.30) --
+	( 85.75, 68.19) --
+	( 88.76, 70.67) --
+	( 91.77, 72.59) --
+	( 94.77, 78.45) --
+	( 97.78, 78.57) --
+	(100.78, 83.81) --
+	(103.79, 86.56) --
+	(106.80, 85.94) --
+	(109.80, 92.57) --
+	(112.81, 95.46) --
+	(115.81, 98.41) --
+	(118.82,102.64) --
+	(121.82,102.38) --
+	(124.83,106.28) --
+	(127.84,110.72) --
+	(130.84,112.06) --
+	(133.85,116.16) --
+	(136.85,119.03);
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.84, 30.63) --
-	( 37.95, 30.63) --
-	( 41.06, 31.33) --
-	( 44.17, 31.33) --
-	( 47.29, 32.63) --
-	( 50.40, 33.82) --
-	( 53.51, 35.96) --
-	( 56.62, 37.83) --
-	( 59.73, 40.62) --
-	( 62.85, 43.28) --
-	( 65.96, 46.30) --
-	( 69.07, 50.22) --
-	( 72.18, 53.16) --
-	( 75.30, 57.14) --
-	( 78.41, 60.47) --
-	( 81.52, 64.05) --
-	( 84.63, 72.20) --
-	( 87.74, 71.34) --
-	( 90.86, 80.12) --
-	( 93.97, 80.67) --
-	( 97.08, 83.21) --
-	(100.19, 89.74) --
-	(103.31, 87.61) --
-	(106.42, 96.04) --
-	(109.53, 98.47) --
-	(112.64, 99.99) --
-	(115.75,103.72) --
-	(118.87,103.27) --
-	(121.98,109.92) --
-	(125.09,111.85) --
-	(128.20,115.67) --
-	(131.32,116.78) --
-	(134.43,119.28) --
-	(137.54,123.20) --
-	(140.65,125.87);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.66, 30.63) --
+	( 37.66, 30.63) --
+	( 40.67, 31.33) --
+	( 43.67, 31.33) --
+	( 46.68, 32.63) --
+	( 49.68, 33.82) --
+	( 52.69, 35.96) --
+	( 55.70, 37.83) --
+	( 58.70, 40.62) --
+	( 61.71, 43.28) --
+	( 64.71, 46.30) --
+	( 67.72, 50.22) --
+	( 70.73, 53.16) --
+	( 73.73, 57.14) --
+	( 76.74, 60.47) --
+	( 79.74, 64.05) --
+	( 82.75, 72.20) --
+	( 85.75, 71.34) --
+	( 88.76, 80.12) --
+	( 91.77, 80.67) --
+	( 94.77, 83.21) --
+	( 97.78, 89.74) --
+	(100.78, 87.61) --
+	(103.79, 96.04) --
+	(106.80, 98.47) --
+	(109.80, 99.99) --
+	(112.81,103.72) --
+	(115.81,103.27) --
+	(118.82,109.92) --
+	(121.82,111.85) --
+	(124.83,115.67) --
+	(127.84,116.78) --
+	(130.84,119.28) --
+	(133.85,123.20) --
+	(136.85,125.87);
 \definecolor{drawColor}{RGB}{231,41,138}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.84, 34.38) --
-	( 37.95, 34.38) --
-	( 41.06, 34.93) --
-	( 44.17, 35.45) --
-	( 47.29, 34.93) --
-	( 50.40, 34.93) --
-	( 53.51, 34.93) --
-	( 56.62, 34.93) --
-	( 59.73, 34.93) --
-	( 62.85, 36.92) --
-	( 65.96, 35.45) --
-	( 69.07, 34.93) --
-	( 72.18, 35.96) --
-	( 75.30, 35.45) --
-	( 78.41, 35.45) --
-	( 81.52, 34.93) --
-	( 84.63, 34.93) --
-	( 87.74, 34.93) --
-	( 90.86, 35.45) --
-	( 93.97, 35.45) --
-	( 97.08, 34.93) --
-	(100.19, 34.93) --
-	(103.31, 35.45) --
-	(106.42, 34.93) --
-	(109.53, 36.92) --
-	(112.64, 34.93) --
-	(115.75, 35.45) --
-	(118.87, 35.45) --
-	(121.98, 34.93) --
-	(125.09, 34.93) --
-	(128.20, 34.93) --
-	(131.32, 34.93) --
-	(134.43, 34.93) --
-	(137.54, 35.45) --
-	(140.65, 34.93);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.66, 34.38) --
+	( 37.66, 34.38) --
+	( 40.67, 34.93) --
+	( 43.67, 35.45) --
+	( 46.68, 34.93) --
+	( 49.68, 34.93) --
+	( 52.69, 34.93) --
+	( 55.70, 34.93) --
+	( 58.70, 34.93) --
+	( 61.71, 36.92) --
+	( 64.71, 35.45) --
+	( 67.72, 34.93) --
+	( 70.73, 35.96) --
+	( 73.73, 35.45) --
+	( 76.74, 35.45) --
+	( 79.74, 34.93) --
+	( 82.75, 34.93) --
+	( 85.75, 34.93) --
+	( 88.76, 35.45) --
+	( 91.77, 35.45) --
+	( 94.77, 34.93) --
+	( 97.78, 34.93) --
+	(100.78, 35.45) --
+	(103.79, 34.93) --
+	(106.80, 36.92) --
+	(109.80, 34.93) --
+	(112.81, 35.45) --
+	(115.81, 35.45) --
+	(118.82, 34.93) --
+	(121.82, 34.93) --
+	(124.83, 34.93) --
+	(127.84, 34.93) --
+	(130.84, 34.93) --
+	(133.85, 35.45) --
+	(136.85, 34.93);
 \definecolor{drawColor}{gray}{0.70}
@@
 
-\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round] ( 29.55, 25.11) rectangle (145.94,130.66);
+\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round] ( 29.55, 25.11) rectangle (141.96,130.66);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] ( 31.72, 22.86) --
-	( 31.72, 25.11);
+\path[draw=drawColor,line width= 0.2pt,line join=round] ( 31.65, 22.86) --
+	( 31.65, 25.11);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] ( 62.85, 22.86) --
-	( 62.85, 25.11);
+\path[draw=drawColor,line width= 0.2pt,line join=round] ( 61.71, 22.86) --
+	( 61.71, 25.11);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] ( 93.97, 22.86) --
-	( 93.97, 25.11);
+\path[draw=drawColor,line width= 0.2pt,line join=round] ( 91.77, 22.86) --
+	( 91.77, 25.11);
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] (125.09, 22.86) --
-	(125.09, 25.11);
+\path[draw=drawColor,line width= 0.2pt,line join=round] (121.82, 22.86) --
+	(121.82, 25.11);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 31.72, 16.10) {0};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 31.65, 16.10) {0};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 62.85, 16.10) {10};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 61.71, 16.10) {10};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 93.97, 16.10) {20};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 91.77, 16.10) {20};
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (125.09, 16.10) {30};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (121.82, 16.10) {30};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 87.74,  6.25) {Domain size};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 85.75,  6.25) {Domain size};
 \end{scope}
@@
 
-\path[fill=fillColor] (154.94, 96.84) rectangle (224.55,147.20);
+\path[fill=fillColor] (150.96, 67.93) rectangle (235.79,147.20);
 \end{scope}
@@
 
-\path[fill=fillColor] (159.44,115.79) rectangle (173.90,130.25);
+\path[fill=fillColor] (155.46,115.79) rectangle (169.92,130.25);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
+\definecolor{drawColor}{RGB}{27,158,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (156.91,123.02) -- (168.47,123.02);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (155.46,101.34) rectangle (169.92,115.79);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
+\definecolor{drawColor}{RGB}{217,95,2}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (156.91,108.57) -- (168.47,108.57);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (155.46, 86.89) rectangle (169.92,101.34);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
+\definecolor{drawColor}{RGB}{117,112,179}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (156.91, 94.11) -- (168.47, 94.11);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (155.46, 72.43) rectangle (169.92, 86.89);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
+\definecolor{drawColor}{RGB}{231,41,138}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (156.91, 79.66) -- (168.47, 79.66);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (160.89,123.02) -- (172.45,123.02);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (174.42,120.54) {\textsc{Crane2-BFS}};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (174.42,106.09) {\textsc{Crane2-Greedy}};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (174.42, 91.63) {\textsc{FastWFOMC}};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (174.42, 77.18) {\textsc{ForcLift}};
 \end{scope}
@@
 
-\path[fill=fillColor] (159.44,101.34) rectangle (173.90,115.79);
+\path[fill=fillColor] (150.96,  8.58) rectangle (220.57, 58.93);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (155.46, 27.53) rectangle (169.92, 41.98);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (160.89,108.57) -- (172.45,108.57);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (156.91, 34.76) -- (168.47, 34.76);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] (155.46, 13.08) rectangle (169.92, 27.53);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (178.40,120.54) {functions};
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (156.91, 20.30) -- (168.47, 20.30);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (178.40,106.09) {permutations};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (154.94,  8.58) rectangle (235.79, 87.84);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (159.44, 56.44) rectangle (173.90, 70.89);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
-\definecolor{drawColor}{RGB}{27,158,119}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (160.89, 63.66) -- (172.45, 63.66);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (159.44, 41.98) rectangle (173.90, 56.44);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
-\definecolor{drawColor}{RGB}{217,95,2}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (160.89, 49.21) -- (172.45, 49.21);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (159.44, 27.53) rectangle (173.90, 41.98);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
-\definecolor{drawColor}{RGB}{117,112,179}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (160.89, 34.76) -- (172.45, 34.76);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (159.44, 13.08) rectangle (173.90, 27.53);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
-\definecolor{drawColor}{RGB}{231,41,138}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (160.89, 20.30) -- (172.45, 20.30);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (174.42, 32.28) {functions};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (178.40, 61.18) {\textsc{Crane-BFS}};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (178.40, 46.73) {\textsc{Crane-Greedy}};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (178.40, 32.28) {\textsc{FastWFOMC}};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (178.40, 17.82) {\textsc{ForcLift}};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (174.42, 17.82) {permutations};
 \end{scope}

### 2024-04-12 analysis/analyse.R

@@ -6,8 +6,8 @@ df <- read.csv("../results/processed/results.csv")
 df$compilation.time <- df$compilation.time / 1000
 df$inference.time <- df$inference.time / 1000
 df$time <- df$compilation.time + df$inference.time
-df$algorithm[df$algorithm == "bfs"] <- "\\textsc{Crane-BFS}"
-df$algorithm[df$algorithm == "greedy"] <- "\\textsc{Crane-Greedy}"
+df$algorithm[df$algorithm == "bfs"] <- "\\textsc{Crane2-BFS}"
+df$algorithm[df$algorithm == "greedy"] <- "\\textsc{Crane2-Greedy}"
 df$algorithm[df$algorithm == "forclift"] <- "\\textsc{ForcLift}"
 df$algorithm[df$algorithm == "fastwfomc"] <- "\\textsc{FastWFOMC}"
 df$sequence[df$sequence == "bijections"] <- "permutations"

### 2024-04-15 doc/paper.tex
Syntax improvements (and other minor changes)

@@
 \begin{abstract}
-  TODO: 9 pages!!!
 \end{abstract}
@@
 \todo[inline,caption={}]{
-  Add some papers mentioned in:
+  \begin{itemize}
+    \item 9 pages!!!
+    \item Add some papers mentioned in:
           \begin{itemize}
@@
                     \item some more theory papers, e.g., LICS 2018
+                  \end{itemize}
           \end{itemize}
@@
         \end{itemize}
-  \item lifted inference in other domains
+  \item lifted inference elsewhere
         \begin{itemize}
@@
 \end{itemize}
-
-\todo[inline,caption={}]{
-  Where to put this?
-  \paragraph{Changes to the compilation process.}
-  \begin{itemize}
-    \item We make the FCGs satisfy the following property. For every domain
-          $\Delta$, for every directed path $P$ without Ref nodes, the number of
-          atom counting or (generalised) domain recursion or independent partial
-          grounding operations on $\Delta$ on $P$ is at most one.
-    \item When checking whether recursion is possible between a source and a
-          target formula, the target formula (maybe the source formula as well?)
-          must not include a domain as well as its subdomain. This might be
-          equivalent to the formula being `unshattered'. Such formulas could be
-          seen as transitory, and allowing such recursive calls leads to FCGs
-          that I cannot make sense of.
-  \end{itemize}
-}
 
@@
 \begin{itemize}
-  \item \Cref{sec:identifying}
-  \item \Cref{sec:simplifying}
-  \item Converting the recursive equations into a C++ program, which can then be
-        compiled and executed to obtain numerical values (see \cref{sec:cpp}).
-  \item Support for infinite precision integers using the GNU Multiple Precision
-        Arithmetic Library.
-  \item Some experiments vs FastWFOMC
+  \item Completing the definitions of recursive functions by:
+  \begin{itemize}
+    \item identifying a sufficient set of base cases (\cref{sec:identifying})
+    \item constructing formulas that correspond to these base cases
+          (\cref{sec:simplifying})
+    \item and recursing on these subproblems
+  \end{itemize}
+  \item Compiling these function definitions into a C++ program that can be
+        executed independently for any domain size values \cref{sec:cpp}
+        \begin{itemize}
+          \item including support for infinite precision arithmetic via GNU
+                Multiple Precision Arithmetic Library
+        \end{itemize}
+  \item Experiments comparing \Cranetwo{} with the main alternative approach
+        demonstrate the ability of \Cranetwo{} to scale to domain sizes\dots
 \end{itemize}
@@
 
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item What notation am I using for FOL? Introduce equality cardinality
-          constraints, counting quantifiers, etc.
-    \item Maybe say ``structure'' instead of interpretation?
-    \item Should I say ``sort'' instead of domain everywhere?
-  \end{itemize}
-}
-
 \begin{table*}
@@
     \toprule
-    Logic & Sorts & Constants & Variables & Quantifiers & Additional atomic constraints\\
+    Logic & Sorts & Constants & Variables & Quantifiers & Additional atoms\\
     \midrule
-    \FO & one or more & \cmark & unlimited & $\forall$, $\exists$ & $s = t$\\
+    \FO & one or more & \cmark & unlimited & $\forall$, $\exists$ & $x = y$\\
     \Ctwo & one & \xmark & two & $\forall$, $\exists$, $\exists^{= k}$, $\exists^{\le k}$, $\exists^{\ge k}$ & ---\\
-    \UFO & one & \xmark & two & $\forall$ & $|p| = m$\\
+    \UFO & one & \xmark & two & $\forall$ & $|P| = m$\\
     \bottomrule
@@
       \item allowed quantifiers, and
-      \item atomic constructions in addition to those of the form $p(t_{1}, \dots, t_{n})$ for some predicate symbol $p$ and terms $t_{1}, \dots, t_{n}$.
+      \item supported atoms in addition to those of the form $P(\mathbf{t})$ for some predicate $P/n$ and $n$-tuple of terms $\mathbf{t}$.
     \end{enumerate*}
@@
     \begin{enumerate*}[label=(\roman*)]
-      \item $k$ and $m$ are non-negative integers, the latter of which can depend on the domain size,
-      \item $p$ is a predicate symbol, and
-      \item $s$ and $t$ are terms.
+      \item $k, m \in \mathbb{N}_{0}$, the latter of which can depend on the domain size,
+      \item $P$ is a predicate, and
+      \item $x$ and $y$ are terms.
     \end{enumerate*}
@@
   \item Domains are always assumed to be finite.
+  \item In many-sorted logic, each term is assigned to a \emph{sort}, and each
+        predicate $p/n$ is assigned to a sequence of $n$ sorts. Each sort has
+        its corresponding domain. In the input formula, all domains are assumed
+        to be pairwise disjoin.t Most of these assignments are typically left
+        implicit and can be reconstructed from the quantifiers. For instance,
+        $\forall x,y \in \Delta\text{. }P(x, y)$ implies that variables $x$ and
+        $y$ have the same sort. On the other hand, $\forall x \in \Delta\text{.
+        }\forall y \in \Gamma\text{. } P(x, y)$ implies that $x$ and $y$ have
+        different sorts, and it would be improper to have $x = y$ as part of a
+        formula.
   \item
@@
 
-\todo[inline]{Explain arity and its notation. Define `ground'?}
+\todo[inline,caption={}]{
+  \begin{itemize}
+    \item Add examples of cardinality constraints and counting quantifiers
+    \item Mention the role of Skolemization (with a citation)
+  \end{itemize}
+}
 
-A \emph{formula} is a set of clauses. A \emph{clause} is of the form
-$\forall x_{1} \in \Delta_{1}\text{. }\forall x_{2} \in \Delta_{2}\dots\text{
-}\forall x_{n} \in \Delta_{n}\text{. }\phi(x_{1}, x_{2}, \dots, x_{n})$, where
-$\phi$ is a disjunction of literals that only contain variables
-$x_{1}, \dots, x_{n}$ (and any constants). A \emph{literal} is either an atom or
-its negation. An \emph{atom} is of the form $p(t_{1}, \dots, t_{m})$, where $p$
-is a predicate, and $t_{1}, \dots, t_{m}$ are terms. A \emph{term} is either a
-variable or a constant. Throughout the paper, we use set-theoretic notation,
-interpreting a formula as a set of clauses and a clause as a set of literals.
+\paragraph{The \FO{} logic (after Skolemization).}
+\begin{itemize}
+  \item In the spirit of keeping sorts implicit, we always assume formulas `type
+        check' with respect to sorts. For example, if $P(x)$, $P(y)$, and
+        $x \ne c$ are all part of the formula (for some predicate $P$, variables
+        $x$ and $y$, and constant $c$), then $x$, $y$, and $c$ all have the same
+        sort.
+  \item A \emph{formula} is a conjunction of clauses.
+  \item A \emph{clause} is of the form $\forall x_{1} \in \Delta_{1}\text{.
+        }\forall x_{2} \in \Delta_{2}\dots\text{
+        }\forall x_{n} \in \Delta_{n}\text{. }\phi(x_{1}, x_{2}, \dots, x_{n})$,
+        where $\phi$ is a disjunction of literals that only contain variables
+        $x_{1}, \dots, x_{n}$ (and any constants).
+  \item A \emph{literal} is either an atom or its negation.
+  \item An \emph{atom} is either:
+  \begin{itemize}
+    \item $P(t_{1}, \dots, t_{m})$ for some predicate $P/m$ and terms
+          $t_{1}, \dots, t_{m}$ or
+    \item $x=y$ for some terms $x$ and $y$
+  \end{itemize}
+  \item An atom is \emph{ground} if it contains no variables (i.e., only
+        constants).
+  \item The \emph{arity} of a predicate is the number of arguments it takes,
+        i.e., $m$ in the case of predicate $P$.
+  \item When we want to denote a predicate together with its arity, we write
+        $P/m$.
+  \item A \emph{term} is either a variable or a constant.
+  \item Throughout the paper, we use set-theoretic notation, interpreting a
+        formula as a set of clauses and a clause as a set of literals. Moreover,
+        for readability, clauses written on separate lines are implicitly
+        conjoined.
+\end{itemize}
 
-For any clause or literal $l$, let $\Vars(l)$ denote the set of variables in
-$l$. For any (bound) variable $v$, let $\Dom(v)$ denote the domain over which
-$v$ is quantified. For a literal $l$,
-$\Doms(l) \coloneqq \{\, \Dom(v) \mid v \in \Vars(l) \,\}$. Similarly, for any
-clause $C$, let $\Doms(C) = \{\, \Dom(v) \mid v \in \Vars(C) \,\}$.
+For any variable $v$, let $\Dom(v)$ denote the domain over which $v$ is
+quantified. For any clause or literal $l$, let $\Vars(l)$ denote the set of
+variables in $l$, and, similarly, let
+$\Doms(l) \coloneqq \{\, \Dom(v) \mid v \in \Vars(l) \,\}$.
 
@@
   \end{itemize}
-  Then an \emph{interpretation} of $\phi$ (with respect to $\sigma$) is a set
-  $M$ of ground literals defined by adding either $p(\mathbf{t})$ or
+  Then a \emph{structure} of $\phi$ (with respect to $\sigma$) is a set $M$ of
+  ground literals defined by adding either $p(\mathbf{t})$ or
   $\neg p(\mathbf{t})$ for every predicate $p/n$ in $\phi$ and $n$-tuple
-  $\mathbf{t} \in \prod_{i=1}^{n} \sigma(\Delta_{i}^{p})$. An interpretation is
-  a \emph{model} if it satisfies $\phi$ (see Appendix~A of~Dilkas and
+  $\mathbf{t} \in \prod_{i=1}^{n} \sigma(\Delta_{i}^{p})$. A structure is a
+  \emph{model} if it satisfies $\phi$ (see Appendix~A of~Dilkas and
   Belle~\shortcite{DBLP:journals/corr/abs-2306-04189} for more details).
@@
 
-\paragraph{Notation.}
-We write $\expr{}$ for an arbitrary algebraic expression. For any signature or
-clause $C$, argument or variable $x$, and number or constant $t$, we shall write
-$C[t / x]$ for the result of substituting $t$ for all occurrences of $x$ in $C$.
-
-\begin{itemize}
-  \item Variables in uppercase
-  \item Domains in uppercase Greek
-  \item Constant and predicate symbols in lowercase
-  \item Clauses written on separate lines are implicitly conjoined
-\end{itemize}
-
 \todo[inline,caption={}]{
@@
     \item explain how this works for function calls too
+    \item introduce the Iverson bracket (somewhere)
+    \item reorder the Logic subsection to cover \FO before comparing it to other
+          logics (and clarify the differences between the input format and the
+          internal format)
   \end{itemize}
@@
 \begin{definition}
-  A \emph{function call} is a term of the form
-  $f(x_{1} - c_{1}, \dots, x_{n} - c_{n})$ (written $f(\mathbf{x} - \mathbf{c})$
-  for short), where $f$ is an $n$-ary function, each $x_{i}$ is a variable, and
-  each $c_{i}$ is a non-negative constant.
+  A \emph{function call} is $f(x_{1} - c_{1}, \dots, x_{n} - c_{n})$ (written
+  $f(\mathbf{x} - \mathbf{c})$ for short), where $f$ is an $n$-ary function,
+  each $x_{i}$ is a variable, and each $c_{i}$ is a non-negative constant.
 \end{definition}
-\todo[inline]{do I ever use this term for the case when some of the variables
-  don't exist?}
+\todo[inline]{do I ever use this notation for the case when some of the
+  variables don't exist?}
 
 \begin{definition}
-  A \emph{signature} is a term of the form $f(x_{1}, \dots, x_{n})$ (written
-  $f(\mathbf{x})$ for short), where $f$ is an $n$-ary function, and each $x_{i}$
-  is a variable. The signature of a function call $f(\mathbf{x} - \mathbf{c})$
-  is $f(\mathbf{x})$. For example, the signature of $f(x - 1, y - 2)$ is
-  $f(x, y)$.
+  A \emph{signature} is $f(x_{1}, \dots, x_{n})$ (written $f(\mathbf{x})$ for
+  short), where $f$ is an $n$-ary function, and each $x_{i}$ is a variable. The
+  signature of a function call $f(\mathbf{x} - \mathbf{c})$ is $f(\mathbf{x})$.
+  For example, the signature of $f(x - 1, y - 2)$ is $f(x, y)$.
 \end{definition}
@@
 \end{definition}
+
 \todo[inline,caption={}]{
-  give some examples of formulas that:
+  an example of a formula that:
   \begin{itemize}
-    \item introduce new variables,
-    \item call the function itself,
-    \item call some other function, and
-    \item is more nested than just a sum.
+    \item introduces a new variable,
+    \item calls itself.
   \end{itemize}
@@
 \end{definition}
+
+\paragraph{Notation.}
+We write $\expr{}$ for an arbitrary algebraic expression. In the context of both
+algebra and logic, we write $C[x \mapsto y]$ for $C$ with all occurrences of $x$
+replaced with $y$.
 
@@
         \For{$n \gets 0$ \KwTo $c_{i} - 1$}{\label{line:lim}
-          $\mathcal{B} \gets \mathcal{B} \cup \{\, f(\mathbf{x})[x_{i}/n] \,\}$\;\label{line:insert}
+          $\mathcal{B} \gets \mathcal{B} \cup \{\, f(\mathbf{x})[x_{i} \mapsto n] \,\}$\;\label{line:insert}
         }
@@
   \item \cref{line:insert} for $f(\mathbf{x}) = f(y, z)$, $x_{i} = y$, and
-        $n = 0$, add $f(y, z)[y/0] = f(0, z)$ to $\mathcal{B}$.
+        $n = 0$, add $f(y, z)[y \mapsto 0] = f(0, z)$ to $\mathcal{B}$.
 \end{itemize}
@@
   \Else{
-    $c \gets$ a new constant symbol\;
+    $c \gets$ a new constant in $\Delta$\;
     \ForEach{clause $C \in \phi$}{
@@
       \ForEach{$v \in \Vars(C)$ with $\Dom(v) = \Delta$}{
-        $C' \gets C'[c / v]$\;
+        $C' \gets C'[v \mapsto c]$\;
       }
@@
 \paragraph{Key point.}
-If there is a predicate $p$ that has nothing to do with domain $\Delta$, make
-sure that $p$ remains as part of the formula even if all clauses with $p$ can be
+If there is a predicate $P$ that has nothing to do with domain $\Delta$, make
+sure that $P$ remains as part of the formula even if all clauses with $P$ can be
 removed. Which literal is picked on \cref{line:smoothing1} of \cref{alg2} is not
 important because any choice achieves the same goal: constructing a clause that
-mentions the same predicates as $C'$ and is satisfied by any interpretation.
+mentions the same predicates as $C'$ and is satisfied by any structure.
 
@@
   `$\forall x \in \Delta$' (for any variable $x$) is vacuously satisfied by all
-  interpretations.
+  structures.
 \end{fact}
@@
 For example, consider the formula
-\begin{align}
-  \forall x \in \Delta \forall y, z \in \Gamma &: P(x) \lor Q(y, z)\label[formula]{eq:example1}\\
-  \forall y, z \in \Gamma' &: Q(y, z)\label[formula]{eq:example2}
-\end{align}
-and assume that $\Gamma' \subseteq \Gamma$. In this case, if we set $|\Delta|$
+\begin{gather}
+  \forall x \in \Delta\text{. }\forall y, z \in \Gamma\text{. }P(x) \lor Q(y, z)\label[formula]{eq:example1}\\
+  \forall y, z \in \Gamma'\text{. }Q(y, z)\label[formula]{eq:example2}
+\end{gather}
+and assume that $\Gamma' \subseteq \Gamma$. If we set $|\Delta|$
 to zero and remove clauses with variables quantified over $\Delta$, we get
 \begin{equation}\label[formula]{eq:simplified}
-  \forall y, z \in \Gamma' : Q(y, z),
+  \forall y, z \in \Gamma'\text{. }Q(y, z),
 \end{equation}
@@
 \cref{eq:example1,eq:example2} to
-\begin{align*}
-  \forall y, z \in \Gamma &: Q(y, z) \lor \neg Q(y, z) \\
-  \forall y, z \in \Gamma' &: Q(y, z).
-\end{align*}
+\begin{gather*}
+  \forall y, z \in \Gamma\text{. }Q(y, z) \lor \neg Q(y, z)\\
+  \forall y, z \in \Gamma'\text{. }Q(y, z).
+\end{gather*}
 The model count returned by this will also consider the truth value of $Q$ over
@@
   \item[Constraint removal.] Do reverse constraint removal. Assuming that
-        domain $\Delta$ with constraints $X \ne c$ (for some constant
+        domain $\Delta$ with constraints $x \ne c$ (for some constant
         $c \in \Delta$) were replaced with domain $\Delta'$, replace each
-        $\forall X \in \Delta'\text{. }\phi(X)$ with
-        $\forall X \in \Delta\text{. }X \ne c \Rightarrow \phi(X)$.
+        $\forall x \in \Delta'\text{. }\phi(x)$ with
+        $\forall x \in \Delta\text{. }X \ne c \Rightarrow \phi(x)$.
   \item[Domain recursion.] Suppose the domain recursion node introduces constant
-        $x \in \Delta$. For each unit clause received from the child node,
-        replace each occurrence of $\phi(x)$ or $\forall X \in \Delta\text{.
-        } X \ne x \Rightarrow \phi(X)$ with $\forall X \in \Delta\text{.
-        }\phi(X)$. This can be seen as a claim about what ground atoms the
+        $c \in \Delta$. For each unit clause received from the child node,
+        replace each occurrence of $\phi(x)$ or $\forall x \in \Delta\text{.
+        } x \ne c \Rightarrow \phi(x)$ with $\forall x \in \Delta\text{.
+        }\phi(x)$. This can be seen as a claim about what ground atoms the
         domain recursion node \emph{should} cover (or a temporary assumption).
@@
   \item Whenever the set of unit clauses of the child node contains two formulas
-        $\phi(x)$ and $\forall X \in \Delta\text{.
-        } X \ne x \Rightarrow \phi(X)$ (i.e., the only difference between the
-        two formulas is that one has the constant $x$ whereas the other one has
-        a variable $X \ne x$), merge them into $\forall X \in \Delta\text{.
-        }\phi(X)$.
+        $\phi(c)$ and $\forall x \in \Delta\text{.
+        } x \ne c \Rightarrow \phi(x)$ (i.e., the only difference between the
+        two formulas is that one has the constant $c$ whereas the other one has
+        a variable $x \ne c$), merge them into $\forall x \in \Delta\text{.
+        }\phi(x)$.
   \item Add smoothing nodes below the domain recursion node for the difference
@@
         Stage 1 and the unit clauses of the child node post-processed by the
-        step above. For example, if the child node `covers' only $p(x)$, then
-        Stage 1 assigns $\forall X \in \Delta\text{. }p(X)$ to the domain
+        step above. For example, if the child node `covers' only $P(c)$, then
+        Stage 1 assigns $\forall x \in \Delta\text{. }P(x)$ to the domain
         recursion node. The smoothing node below the domain recursion node then
-        has the clause $\forall X \in \Delta\text{. } X \ne x \Rightarrow p(X)$.
+        has the clause $\forall x \in \Delta\text{. } x \ne c \Rightarrow P(x)$.
 \end{enumerate}
@@
         \begin{itemize}
-          \item In \Ctwo: $\forall X \in \Delta\text{.
-                }\exists^{=1} Y \in \Delta\text{. }p(X, Y)$
+          \item In \Ctwo: $\forall x \in \Delta\text{.
+                }\exists^{=1} y \in \Delta\text{. }P(x, y)$
           \item In \UFO:
                 \begin{gather*}
-                  \forall X, Y \in \Delta\text{. } s(X) \lor \neg p(X, Y)\\
-                  |p| = |\Delta|
+                  \forall x, y \in \Delta\text{. }S(x) \lor \neg P(x, y)\\
+                  |P| = |\Delta|
                 \end{gather*}
@@
                 \begin{gather*}
-                  \forall X \in \Delta\text{. }\exists Y \in \Delta\text{. } p(X, Y)\\
-                  \forall X, Y, Z \in \Delta\text{. } p(X, Y) \land p(X, Z) \Rightarrow Y = Z
+                  \forall x \in \Delta\text{. }\exists y \in \Delta\text{. }P(x, y)\\
+                  \forall x, y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z
                 \end{gather*}
@@
                 \begin{gather*}
-                  \forall X \in \Delta\text{. }\exists^{=1} Y \in \Delta\text{. }p(X, Y)\\
-                  \forall Y \in \Delta\text{. }\exists^{=1} X \in \Delta\text{. }p(X, Y)
+                  \forall x \in \Delta\text{. }\exists^{=1} y \in \Delta\text{. }P(x, y)\\
+                  \forall y \in \Delta\text{. }\exists^{=1} x \in \Delta\text{. }P(x, y)
                 \end{gather*}
@@
                 \begin{gather*}
-                  \forall X, Y \in \Delta\text{. } r(X) \lor \neg p(X, Y)\\
-                  \forall X, Y \in \Delta\text{. } s(X) \lor \neg p(Y, X)\\
-                  |p| = |\Delta|
+                  \forall x, y \in \Delta\text{. }R(x) \lor \neg P(x, y)\\
+                  \forall x, y \in \Delta\text{. }S(x) \lor \neg P(y, x)\\
+                  |P| = |\Delta|
                 \end{gather*}
-                with weights $w^{-}(r) = w^{-}(s) = -1$
+                with weights $w^{-}(R) = w^{-}(S) = -1$
           \item In \FO:
                 \begin{gather*}
-                  \forall X \in \Delta\text{. }\exists Y \in \Delta\text{. } p(X, Y)\\
-                  \forall Y \in \Delta\text{. }\exists X \in \Delta\text{. } p(X, Y)\\
-                  \forall X, Y, Z \in \Delta\text{. } p(X, Y) \land p(X, Z) \Rightarrow Y = Z\\
-                  \forall X, Y, Z \in \Delta\text{. } p(X, Y) \land p(Z, Y) \Rightarrow X = Z
+                  \forall x \in \Delta\text{. }\exists y \in \Delta\text{. }P(x, y)\\
+                  \forall y \in \Delta\text{. }\exists x \in \Delta\text{. }P(x, y)\\
+                  \forall x, y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z\\
+                  \forall x, y, z \in \Delta\text{. }P(x, y) \land P(z, y) \Rightarrow x = z
                 \end{gather*}
@@
 
+\todo[inline]{maybe examine \textsc{ForcLift}'s scalability as well}
+
 \todo[inline,caption={}]{

### 2024-04-16 doc/paper.tex
Writing and stuff (+ some figures to describe smoothing)

@@
 
+\DeclareMathOperator{\CR}{CR}
+\DeclareMathOperator{\DR}{DR}
+\DeclareMathOperator{\Reff}{Ref}
+
 \DeclareMathOperator{\Dom}{Dom}
@@
 \DeclareMathOperator*{\argmin}{argmin}
-\DeclareMathOperator{\GDR}{GDR}
 
@@
 \author{%
-Ananth K. Kidambi$^1$\and
+  Ananth K. Kidambi$^1$\footnote{The first and second authors contributed equally and were affiliated with the National University of Singapore during the completion of this work.}\and
 Guramrit Singh$^1$\and
@@
 \begin{abstract}
+  TODO: at most 200 words
 \end{abstract}
@@
 
-\paragraph{Papers to cite.}
+\paragraph{Papers To Cite}
 \begin{itemize}
@@
 
-\paragraph{Contributions (outdated).}
+\paragraph{Contributions}
 \begin{itemize}
@@
 
-\subsection{Logic}
+\Cref{sec:logic} introduces the fundamental ideas of first-order logic and
+WFOMC, and discusses the different logics used in the latter.\@
+\Cref{sec:algebra} introduces the terminology we use to describe the output of
+the original \textsc{Crane} algorithm~\cite{DBLP:conf/kr/DilkasB23}, i.e.,
+functions and equations that define them.
+
+\subsection{Logic}\label{sec:logic}
+
+\begin{example}\label{example:functions}
+  Functions
+  \begin{itemize}
+    \item In \Ctwo: $\forall x \in \Delta\text{.
+          }\exists^{=1} y \in \Delta\text{. }P(x, y)$
+    \item In \UFO:
+          \begin{gather*}
+            \forall x, y \in \Delta\text{. }S(x) \lor \neg P(x, y)\\
+            |P| = |\Delta|
+          \end{gather*}
+    \item In \FO:
+          \begin{gather*}
+            \forall x \in \Delta\text{. }\exists y \in \Delta\text{. }P(x, y)\\
+            \forall x, y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z
+          \end{gather*}
+  \end{itemize}
+\end{example}
 
@@
 
-\paragraph{Three types of logics}
+\paragraph{Three Types of Logics}
 \begin{itemize}
@@
 
-\todo[inline,caption={}]{
+\paragraph{The \FO{} Logic (After Skolemization)}
 \begin{itemize}
-    \item Add examples of cardinality constraints and counting quantifiers
-    \item Mention the role of Skolemization (with a citation)
-  \end{itemize}
-}
-
-\paragraph{The \FO{} logic (after Skolemization).}
-\begin{itemize}
+  \item Although existential quantifiers are supported, here we describe the
+        format used internally. During preprocessing, all existential
+        quantifiers are eliminated using
+        Skolemization~\cite{DBLP:conf/kr/BroeckMD14}, and the formula is
+        rewritten into a conjunction of clauses, each of which is in
+        \emph{prenex normal form}~\cite{hinman2018fundamentals}.
   \item In the spirit of keeping sorts implicit, we always assume formulas `type
@@
 
-\subsection{Algebra}
+\subsection{Algebra}\label{sec:algebra}
 
@@
   \begin{itemize}
-    \item check if I'm still using this notation in all these cases
     \item explain how this works for function calls too
     \item introduce the Iverson bracket (somewhere)
-    \item reorder the Logic subsection to cover \FO before comparing it to other
-          logics (and clarify the differences between the input format and the
-          internal format)
+    \item reorder the Logic subsection to cover \FO{} before comparing it to
+          other logics (and clarify the differences between the input format and
+          the internal format)
+    \item (somewhere) mention the trick about increasing the number of sorts
   \end{itemize}
@@
 
+\paragraph{Additional notation}
+We write $\expr{}$ for an arbitrary algebraic expression. In the context of both
+algebra and logic, we write $C[x \mapsto y]$ for $C$ with all occurrences of $x$
+replaced with $y$.
+
 \begin{definition}
-  An \emph{equation} is always of the form $f(\mathbf{x}) = \expr{}$, where
-  $f(\mathbf{x})$ is a signature, and $\expr{}$ is an algebraic expression.
-  Henceforth, we call $f(\mathbf{x})$ and $\expr{}$ the left-hand side (LHS) and
-  the right-hand side (RHS) of the equation, respectively.
+  An \emph{equation} is $f(\mathbf{x}) = \expr{}$, where $f(\mathbf{x})$ is a
+  signature, and $\expr{}$ is an algebraic expression. Henceforth, we call
+  $f(\mathbf{x})$ and $\expr{}$ the left-hand side (LHS) and the right-hand side
+  (RHS) of the equation, respectively.
+\end{definition}
+
+\begin{definition}
+  A \emph{base case} is a function call where all arguments are either variables
+  or constants (i.e., there is no subtraction within any argument), and there is
+  at least one constant. We denote a base case in the same way as a signature,
+  e.g., $f(\mathbf{x})$.
 \end{definition}
@@
 }
-
-\begin{definition}
-  A \emph{base case} is a function call where all arguments are either variables
-  or constants (i.e., there is no subtraction within any argument), and there is
-  at least one constant. We denote a base case in the same way as a signature,
-  e.g., $f(\mathbf{x})$.
-\end{definition}
-
-\paragraph{Notation.}
-We write $\expr{}$ for an arbitrary algebraic expression. In the context of both
-algebra and logic, we write $C[x \mapsto y]$ for $C$ with all occurrences of $x$
-replaced with $y$.
 
@@
 
+\todo[inline]{Can I use an example based on permutations or something similar?}
+
 \paragraph{Key point.}
@@
 
+\todo[inline,caption={}]{
+  \begin{itemize}
+    \item It seems like I'll need to introduce:
+          \begin{itemize}
+            \item FCGs
+            \item node types (be consistent w.r.t.\ node vs vertex)
+            \item their notation
+          \end{itemize}
+    \item Describe \cref{fig:smoothing1,fig:smoothing2}
+  \end{itemize}
+}
+
+\begin{figure}
+  \centering
+  \begin{forest}
+    for tree={sn edges}
+    [$\DR(c \in \Delta)$,name=dr,ellipse,draw,label={right:\textcolor{blue}{3. $\{\, \forall x \in \Delta\text{. }P(x) \,\}$}}
+    [$\land$,ellipse,draw,label={left:\textcolor{blue}{2. $\{\, P(c) \,\}$}},label={right:\textcolor{blue}{6. $\{\, P(c), \forall x \in \Delta\text{. }x \ne c \Rightarrow P(x) \,\}$}},
+    [$P(c)$,rectangle,draw,fill=green!20,label={272:\textcolor{blue}{1. $\{\, P(c) \,\}$}}],
+    [$\CR(\Delta' \gets \Delta \setminus \{\, c \,\})$,ellipse,draw,label={87:\textcolor{blue}{5. $\{\, \forall x \in \Delta\text{. }x \ne c \Rightarrow P(x) \,\}$}}
+    [$\Reff(\Delta \mapsto \Delta')$,name=ref,ellipse,draw,label={below:\textcolor{blue}{4. $\{\, \forall x \in \Delta'\text{. }P(x) \,\}$}}]
+    ]
+    ]
+    ]
+  \end{forest}
+  \caption{An example based on permutation counting (but simplified a lot). The
+    arc from the $\Reff$ node to the $\DR$ node is omitted.}\label{fig:smoothing1}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \begin{forest}
+    for tree={sn edges}
+    [$\DR(c \in \Delta)$,name=dr,ellipse,draw,
+    [$P(c)$,rectangle,draw,fill=green!20],
+    [$\forall x \in \Delta\text{. }x \ne c \Rightarrow P(x) \lor \neg P(x)$,rectangle,dashed,edge=dashed,draw,fill=blue!20]
+    ]
+  \end{forest}
+  \caption{An artificial example of a situation when smoothing nodes need to be
+    added below a $\DR$ node}\label{fig:smoothing2}
+\end{figure}
+
 \begin{algorithm}
@@
 
-\todo[inline]{Insert motivation for smoothing from Section 3.4.\ of the ForcLift
-  paper.}
-
-Originally, smoothing was (and still is) a two-step process. First, atoms that
-are still accounted for in the circuit are propagated upwards. Then, at vertices
-of certain types, missing atoms are detected and additional sinks are created to
-account for them. If left unchanged, the first step of this process would result
-in an infinite loop whenever a cycle is encountered. \Cref{alg:smoothing}
-outlines how the first step can be adapted to an arbitrary directed graph.
+Smoothing is a two-step process. First, atoms that are still accounted for in
+the circuit are propagated upwards. Then, at vertices of certain types, missing
+atoms are detected and additional sinks are created to account for them. If left
+unchanged, the first step of this process would result in an infinite loop
+whenever a cycle is encountered. \Cref{alg:smoothing} outlines how the first
+step can be adapted to an arbitrary directed graph.
 
@@
 \begin{itemize}
-  \item Functions
-        \begin{itemize}
-          \item In \Ctwo: $\forall x \in \Delta\text{.
-                }\exists^{=1} y \in \Delta\text{. }P(x, y)$
-          \item In \UFO:
-                \begin{gather*}
-                  \forall x, y \in \Delta\text{. }S(x) \lor \neg P(x, y)\\
-                  |P| = |\Delta|
-                \end{gather*}
-          \item In \FO:
-                \begin{gather*}
-                  \forall x \in \Delta\text{. }\exists y \in \Delta\text{. }P(x, y)\\
-                  \forall x, y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z
-                \end{gather*}
-        \end{itemize}
+  \item Functions (\cref{example:functions})
   \item Permutations
@@
                 \end{gather*}
+          \item NOTE: when it's the same domain, counting bijections,
+                injections, surjections, and partial surjections all boil down
+                to the same integer sequence.
         \end{itemize}
 \end{itemize}
+
+\todo[inline]{ If it is possible to rewrite a formula to have more sorts, we do
+  that. Explain in more detail and with an example. Mention that this has been
+  observed previously by my previous work (i.e., linear vs cubic complexity). }
 
@@
 
+\todo[inline,caption={}]{
+  \begin{itemize}
+    \item Maybe add some complete examples of C++ programs in the supplementary
+          material.
+          \item Later on:
+          \begin{itemize}
+            \item Eliminate (e.g., Emacs) warnings.
+            \item must run it by A\&G
+            \item re-check submission instructions and formatting guidelines
+            \item Full stop at the end of a single-sentence caption?
+          \end{itemize}
+  \end{itemize}
+}
+
+\clearpage % TODO: temporarary
+
 \bibliographystyle{kr}
@@
 
-% TODO: the report has some (long) examples of formulas being transformed into
-% programs perhaps suitable for supplementary material
-
 \end{document}

### 2024-04-17 doc/paper.tex
Modify the overview diagram (and lots of other changes)

@@
 
+\SetKwFunction{CompileWithBaseCases}{CompileWithBaseCases}
 \SetKwFunction{Crane}{Compile}
@@
 \SetKwFunction{FindBaseCases}{FindBaseCases}
+\SetKwFunction{Simplify}{Simplify}
 
@@
   \begin{tikzpicture}
-    \node at (0, 0) (formula) {$\phi$};
-    \node[draw,rounded rectangle] at (3, 0) (alg1) {\Cref{alg:main}};
-    \node[draw,rounded rectangle] at (6, 0) (simplification) {Simplification};
-    \node[draw,rounded rectangle] at (9, 0) (compilation) {Compilation};
+    \node at (-1, 0) (formula) {$\phi$};
+    \node[draw,rounded rectangle] at (3, 0) (alg1) {\CompileWithBaseCases};
+    \node[draw,rounded rectangle] at (9, 0) (compilation) {Compile to C++};
 
@@
 
-    \node[draw,rounded rectangle] at (3, -2) (alg2) {\Cref{alg1}};
-    \node[draw,rounded rectangle,left = 0.1cm of alg2] (crane) {\textsc{Crane}};
-    \node[draw,rounded rectangle,right = 0.1cm of alg2] (alg3) {\Cref{alg2}};
-
-    \node[draw,fit={(alg1) (simplification) (compilation) (crane) (alg2) (alg3)},inner ysep=7pt,yshift=5pt] {};
-    \node at (1.1, 0.5) {\Cranetwo};
+    \node[draw,rounded rectangle] at (3, -2) (alg2) {\FindBaseCases};
+    \node[draw,rounded rectangle,left = 0.1cm of alg2] (crane) {\Crane};
+    \node[draw,rounded rectangle,right = 0.1cm of alg2] (alg3) {\Propagate};
+    \node[draw,rounded rectangle,right = 0.1cm of alg3] (simplify) {\Simplify};
+
+    \node[draw,fit={(alg1) (compilation) (crane) (alg2) (alg3)},inner ysep=7pt,yshift=5pt] {};
+    \node at (0.2, 0.5) {\Cranetwo};
 
     \draw[-Latex] (formula) -- (alg1);
-    \draw[-Latex] (alg1) -- node[above] {$\mathcal{E}$} (simplification);
-    \draw[-Latex] (simplification) -- node[above] {$\mathcal{E}'$} (compilation);
+    \draw[-Latex] (alg1) -- node[above] {$\mathcal{E}$} (compilation);
     \draw[-Latex] (compilation) -- (cpp);
@@
     \draw[-Latex,dashed] (alg1) -- node[midway,left] {uses} (crane);
-    \draw[-Latex,dashed] (alg1) -- node[midway] {uses} (alg2);
-    \draw[-Latex,dashed] (alg1) -- node[midway,right] {uses} (alg3);
+    \draw[-Latex,dashed] (alg1) -- node[midway,left] {uses} (alg2);
+    \draw[-Latex,dashed] (alg1) -- node[midway,left] {uses} (alg3);
+    \draw[-Latex,dashed] (alg1) -- node[midway,right] {uses} (simplify);
   \end{tikzpicture}
-  \caption{Using \Cranetwo{} to compute the model count of formula $\phi$.\ The
-    formula is compiled into a set of equations $\mathcal{E}$, which are then
-    algebraically simplified and compiled to a C++ program. This program can
-    then be run with different command line arguments to compute the model count
-    of $\phi$ for various domain sizes.}
+  \caption[]{The outline of using \Cranetwo{} to compute the model count of a
+    formula $\phi$. The formula is compiled into a set of equations
+    $\mathcal{E}$ that are then compiled to a C++ program. This program can then
+    be run with different command line arguments to compute the model count of
+    $\phi$ for various domain sizes. \CompileWithBaseCases makes use
+    of: \begin{enumerate*}[label=(\roman*)]
+      \item the knowledge compilation algorithm of \textsc{Crane} (denoted by \Crane),
+      \item a procedure for identifying a sufficient set of base cases (denoted by \FindBaseCases),
+      \item a procedure for constructing a formula that corresponds to a given base case (denoted by \Propagate), and
+      \item algebraic simplification techniques (denoted by \Simplify).
+    \end{enumerate*}
+  }\label{fig:overview}
 \end{figure*}
+
+\todo[inline]{By pointing to the outline in \cref{fig:overview}, make forward
+  references to the sections of the paper.}
 
@@
 
+We write $\mathbb{N}_{0}$ for the set of non-negative integers. In the context
+of both algebra and logic, we write $C[x \mapsto y]$ for $C$ with all
+occurrences of $x$ replaced with $y$.
+
 \subsection{Logic}\label{sec:logic}
+
+\todo[inline]{Reorder the Logic subsection to cover \FO{} before comparing it to
+  other logics (and clarify the differences between the input format and the
+  internal format)}
 
@@
         $x_{1}, \dots, x_{n}$ (and any constants).
-  \item A \emph{literal} is either an atom or its negation.
+  \item We say that a clause is a \emph{(positive) unit clause} if:
+        \begin{itemize}
+          \item there is only one literal with a predicate, and
+          \item it is a positive literal.
+        \end{itemize}
+  \item A \emph{literal} is either an atom (i.e., a \emph{positive} literal) or
+        its negation (i.e., a \emph{negative} literal).
   \item An \emph{atom} is either:
@@
   \begin{itemize}
-    \item explain how this works for function calls too
-    \item introduce the Iverson bracket (somewhere)
-    \item reorder the Logic subsection to cover \FO{} before comparing it to
-          other logics (and clarify the differences between the input format and
-          the internal format)
-    \item (somewhere) mention the trick about increasing the number of sorts
-  \end{itemize}
-}
+    \item the definition of a function is a strong assumption
+    \item the notation for a function call is now outdated
+  \end{itemize}
+}
+
+\begin{itemize}
+  \item We write $\expr{}$ for an arbitrary algebraic expression.
+  \item A few terms have different meanings in the context of algebra as
+        compared to logic:
+        \begin{itemize}
+          \item a \emph{variable} is either:
+                \begin{itemize}
+                  \item a parameter of a function or
+                  \item a variable introduced by a summation, e.g., $i$ in
+                        $\sum_{i=1}^{n} \expr$.
+                \end{itemize}
+          \item A \emph{constant} is a non-negative integer.
+        \end{itemize}
+\end{itemize}
 
 \begin{definition}
-  A \emph{function call} is $f(x_{1} - c_{1}, \dots, x_{n} - c_{n})$ (written
-  $f(\mathbf{x} - \mathbf{c})$ for short), where $f$ is an $n$-ary function,
-  each $x_{i}$ is a variable, and each $c_{i}$ is a non-negative constant.
+  A (function) \emph{signature} is $f(x_{1}, \dots, x_{n})$ (written
+  $f(\mathbf{x})$ for short), where $f$ is an $n$-ary function, and each $x_{i}$
+  is a variable.
 \end{definition}
-\todo[inline]{do I ever use this notation for the case when some of the
-  variables don't exist?}
 
 \begin{definition}
-  A \emph{signature} is $f(x_{1}, \dots, x_{n})$ (written $f(\mathbf{x})$ for
-  short), where $f$ is an $n$-ary function, and each $x_{i}$ is a variable. The
-  signature of a function call $f(\mathbf{x} - \mathbf{c})$ is $f(\mathbf{x})$.
-  For example, the signature of $f(x - 1, y - 2)$ is $f(x, y)$.
+  Given a function $f$ with signature $f(\mathbf{x})$, a \emph{function call} of
+  $f$ is $f(\mathbf{y})$, where each $y_{i}$ is either $x_{i} - c_{i}$ or
+  $c_{i}$ for some constant $c_{i} \in \mathbb{N}_{0}$.
 \end{definition}
-
-\paragraph{Additional notation}
-We write $\expr{}$ for an arbitrary algebraic expression. In the context of both
-algebra and logic, we write $C[x \mapsto y]$ for $C$ with all occurrences of $x$
-replaced with $y$.
 
@@
   An \emph{equation} is $f(\mathbf{x}) = \expr{}$, where $f(\mathbf{x})$ is a
-  signature, and $\expr{}$ is an algebraic expression. Henceforth, we call
-  $f(\mathbf{x})$ and $\expr{}$ the left-hand side (LHS) and the right-hand side
-  (RHS) of the equation, respectively.
+  signature. We refer to $f(\mathbf{x})$ and $\expr{}$ as the \emph{left-hand
+    side} (LHS) and the \emph{right-hand side} (RHS) of the equation,
+  respectively.
 \end{definition}
 
-\begin{definition}
-  A \emph{base case} is a function call where all arguments are either variables
-  or constants (i.e., there is no subtraction within any argument), and there is
-  at least one constant. We denote a base case in the same way as a signature,
-  e.g., $f(\mathbf{x})$.
+\begin{definition}\label{def:basecase}
+  Let $f$ be a function with signature $f(\mathbf{x})$. Then a \emph{base case}
+  of $f$ is a function call $f(\mathbf{y})$ such that either $y_{i} = x_{i}$ or
+  $y_{i} \in \mathbb{N}_{0}$ for all $i$, and the latter case applies at least
+  once.
 \end{definition}
 
-\todo[inline,caption={}]{
-  an example of a formula that:
-  \begin{itemize}
-    \item introduces a new variable,
-    \item calls itself.
-  \end{itemize}
-}
-
 \section{Completing the Definitions of Recursive Functions}\label{sec:main}
@@
 \begin{algorithm}[t]
-  \caption{The main part of \Cranetwo{} that compiles a formula into a set of
-    equations, including the base cases of recursive functions}\label{alg:main}
+  \caption{\protect\CompileWithBaseCases{$\phi$}}\label{alg:main}
   \KwIn{formula $\phi$}
@@
   $(\mathcal{E}, \mathcal{F}, \mathcal{D}) \gets \Crane{$\phi$}$\;
+  $\mathcal{E} \gets \Simplify{$\mathcal{E}$}$\;
   \ForEach{base case $f(\mathbf{x}) \in \FindBaseCases{$\mathcal{E}$}$}{
     $\psi \gets \mathcal{F}(f)$\;
-    \ForEach{$i$ such that $x_{i}$ is a constant}{
+    \ForEach{$i$ such that $x_{i} \in \mathbb{N}_{0}$}{
       $\psi \gets \Propagate{$\psi$, $\mathcal{D}(f, i)$, $x_i$}$\;
     }
-    $(\mathcal{E}', \text{\textunderscore}, \text{\textunderscore}) \gets \Crane{$\psi$}$\;
-    $\mathcal{E} \gets \mathcal{E} \cup \mathcal{E}'$\;
+    $\mathcal{E} \gets \mathcal{E} \cup \CompileWithBaseCases{$\psi$}$\;
   }
 \end{algorithm}
+
+\todo[inline]{In \cref{alg:main}, some kind of translation also needs to take
+  place, right?}
 
@@
   \begin{itemize}
-    \item extend it to work with base cases that are themselves recursive
-    \item \textsc{Crane}, \Cranetwo{}, or \Crane (here and elsewhere)?
+    \item \textsc{Crane}, \Cranetwo{}, or \Crane in the paragraph below
   \end{itemize}
@@
   $\mathcal{B} \gets \emptyset$\;
-  \ForEach{equation $(f(\mathbf{x}) = \expr{}) \in \mathcal{E}$}{
-    \ForEach{function call $f(\mathbf{x} - \mathbf{c}) \in \expr{}$}{\label{line:functioncall}
-      \ForEach{$c_{i} \in \mathbf{c}$}{
-        \For{$n \gets 0$ \KwTo $c_{i} - 1$}{\label{line:lim}
-          $\mathcal{B} \gets \mathcal{B} \cup \{\, f(\mathbf{x})[x_{i} \mapsto n] \,\}$\;\label{line:insert}
+  \ForEach{equation $(\ldots = \expr{}) \in \mathcal{E}$}{
+    \ForEach{function call $f(\mathbf{y}) \in \expr{}$}{\label{line:functioncall}
+      let $f(\mathbf{x})$ be the signature of $f$\;
+      \ForEach{$y_{i} \in \mathbf{y}$} {
+        \uIf{$y_{i} \in \mathbb{N}_{0}$}{
+          $\mathcal{B} \gets \mathcal{B} \cup \{\, f(\mathbf{x})[x_{i} \mapsto y_{i}] \,\}$\;
+        }
+        \ElseIf{$y_{i} = x_{i} - c_{i}$}{
+          \For{$j \gets 0$ \KwTo $c_{i} - 1$}{\label{line:lim}
+            $\mathcal{B} \gets \mathcal{B} \cup \{\, f(\mathbf{x})[x_{i} \mapsto j] \,\}$\;\label{line:insert}
+          }
         }
@@
 \end{algorithm}
+
+\todo[inline,caption={}]{
+  \begin{itemize}
+    \item introduce the Iverson bracket (it's only used in this subsection)
+    \item \Cref{alg1} is now fixed and supersedes the description below (and the
+          code!)
+    \item NOTE: exactly one of the if and else-if branches always applies
+  \end{itemize}
+}
 
@@
 
+\todo[inline,caption={}]{
+  \begin{itemize}
+    \item later check if I'm still using the syntax for $\Vars$, $\Dom$, etc.
+    \item align the last line to be a bit neater
+    \item \Cref{alg2} now supports any base case domain sizes
+    \item NOTE: if $C' = \emptyset$, then the clause becomes irrelevant and
+          doesn't need smoothing, so can be skipped
+  \end{itemize}
+}
+
 \begin{algorithm}[t]
   \caption{\protect\Propagate{$\phi$, $\Delta$, $n$}}\label{alg2}
-  \KwIn{formula $\phi$, domain $\Delta$, domain size $n \in \{\, 0, 1 \,\}$}
+  \KwIn{formula $\phi$, domain $\Delta$, $n \in \mathbb{N}_{0}$}
   \KwOut{formula $\phi'$}
@@
       \lIf{$\Delta \not\in \Doms(C)$}{$\phi' \gets \phi' \cup \{\, C \,\}$}
+      \Else{
         $C' \gets \{\, l \in C \mid \Delta \not\in \Doms(l) \,\}$\;
-      \If{$\Delta \in \Doms(C)$ {\bf and} $C' \ne \emptyset$}{
+        \If{$C' \ne \emptyset$}{
           $l \gets \text{an arbitrary literal in } C'$\;\label{line:smoothing1}
@@
     }
+  }
   \Else{
-    $c \gets$ a new constant in $\Delta$\;
+    $D \gets \text{a set of $n$ new constants in $\Delta$}$\;
     \ForEach{clause $C \in \phi$}{
-      $C' \gets C$\;
-      \ForEach{$v \in \Vars(C)$ with $\Dom(v) = \Delta$}{
-        $C' \gets C'[v \mapsto c]$\;
-      }
-      $\phi' \gets \phi' \cup \{\, C' \,\}$\;
+      ${(x_{i})}_{i=1}^{m} \gets \text{the variables in $C$ with domain $\Delta$}$\;
+      \lIf{$m = 0$}{$\phi' \gets \phi' \cup \{\, C \,\}$}
+      \Else{
+        $\phi' \gets \phi' \cup \{\, C[x_{1} \mapsto c_{1}, \dots, x_{m} \mapsto c_{m}] \mid {(c_{i})}_{i=1}^{m} \in D^{m} \,\}$\;
+      }
     }
@@
 
-We use \cref{alg2} to find the transformed formula corresponding to each base
-case obtained using \cref{alg1} and call \textsc{Crane} on the formula to obtain
-the required base cases.
-% TODO: or crane 2?
-
-\begin{itemize}
+\todo[inline,caption={}]{ Turn these notes into a coherent description (that
+  doesn't mention \textsc{Crane}):
+  \begin{itemize}
+    \item Each base case identified by \FindBaseCases can be interpreted as
+          assuming some domain...
+    \item \Propagate (\cref{alg2}) to find the transformed formula corresponding
+          to each base case identified by \FindBaseCases and call \textsc{Crane}
+          on the formula to obtain the required base cases.
     \item Clauses where all literals have variables quantified over the empty
@@
   \end{itemize}
+}
+\todo[inline]{Maybe prove consistency: if two base case overlap, their numerical
+  answers also overlap.}
 
@@
 \begin{description}
-  \item[\texttt{Ref}.] During smoothing, when unit clauses (a.k.a.\ variables)
-        are propagated in the opposite direction of the FCG arcs (i.e.,
-        `upwards'), when visiting a \texttt{Ref} node, these clauses are
-        translated using the domain map of the \texttt{Ref} node. For example,
-        if the domain map include $\Delta \mapsto \Delta'$, and the unit clause
-        mentions $\Delta$, then replace it by $\Delta'$.
+  \item[\texttt{Ref}.] During smoothing, when unit clauses are propagated in the
+        opposite direction of the FCG arcs (i.e., `upwards'), when visiting a
+        \texttt{Ref} node, these clauses are translated using the domain map of
+        the \texttt{Ref} node. For example, if the domain map include
+        $\Delta \mapsto \Delta'$, and the unit clause mentions $\Delta$, then
+        replace it by $\Delta'$.
   \item[Constraint removal.] Do reverse constraint removal. Assuming that
@@
 \end{description}
-\todo[inline]{Add examples of both cases, with figures.}
 
@@
 The target is to generate C++ code that can evaluate numerical values of the
-model counts based on the equations generated by \textsc{Crane}. We achieve this
-by parsing the equations generated by \textsc{Crane}, simplifying them, and then
-generating C++ code. This approach can be done in linear time in the length of
-the formula using
-the
-\href{https://en.wikipedia.org/wiki/Shunting_yard_algorithm#:~:text=In%20computer%20science%2C%20the%20shunting,abstract%20syntax%20tree%20(AST).}{Shunting
-  Yard Algorithm}.
-
-The translation of a set $\mathcal{E}$ of equations into a C++ program works as
+model counts based on the equations generated by \CompileWithBaseCases. The
+translation of a set $\mathcal{E}$ of equations into a C++ program works as
 follows.
@@
             \item Full stop at the end of a single-sentence caption?
+            \item cite the \textsc{Crane} paper (and other algorithms' papers)
+                  where necessary
           \end{itemize}

### 2024-04-18 doc/paper.tex
First draft of the beginning of Section 3

@@
 \crefname{line}{line}{lines}
+
+\crefalias{clause}{equation}
+\crefname{clause}{Clause}{Clauses}
+\creflabelformat{clause}{#2\textup{(#1)}#3}
+
 \crefalias{formula}{equation}
-\crefname{formula}{Clause}{Clauses}
+\crefname{formula}{Formula}{Formulas}
 \creflabelformat{formula}{#2\textup{(#1)}#3}
@@
 
-\DeclareMathOperator{\Dom}{Dom}
 \DeclareMathOperator{\Doms}{Doms}
-\DeclareMathOperator{\Vars}{Vars}
-\DeclareMathOperator*{\argmin}{argmin}
+\DeclareMathOperator*{\argmin}{argmin} % TODO: soon to be removed
 
@@
 
-\todo[inline]{Reorder the Logic subsection to cover \FO{} before comparing it to
-  other logics (and clarify the differences between the input format and the
-  internal format)}
-
-\begin{example}\label{example:functions}
-  Functions
-  \begin{itemize}
-    \item In \Ctwo: $\forall x \in \Delta\text{.
-          }\exists^{=1} y \in \Delta\text{. }P(x, y)$
-    \item In \UFO:
-          \begin{gather*}
-            \forall x, y \in \Delta\text{. }S(x) \lor \neg P(x, y)\\
-            |P| = |\Delta|
-          \end{gather*}
-    \item In \FO:
-          \begin{gather*}
-            \forall x \in \Delta\text{. }\exists y \in \Delta\text{. }P(x, y)\\
-            \forall x, y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z
-          \end{gather*}
-  \end{itemize}
-\end{example}
+\todo[inline]{Clarify the differences between the input format and the internal
+  format}
+
+\paragraph{The \FO{} Logic (After Skolemization and in a special (prenex, CNF)
+  form)}
+\begin{itemize}
+  \item Although existential quantifiers are supported, here we describe the
+        format used internally. During preprocessing, all existential
+        quantifiers are eliminated using
+        Skolemization~\cite{DBLP:conf/kr/BroeckMD14}, and the formula is
+        rewritten into a conjunction of clauses, each of which is in
+        \emph{prenex normal form}~\cite{hinman2018fundamentals}.
+  \item In the spirit of keeping sorts implicit, we always assume formulas `type
+        check' with respect to sorts. For example, if $P(x)$, $P(y)$, and
+        $x \ne c$ are all part of the formula (for some predicate $P$, variables
+        $x$ and $y$, and constant $c$), then $x$, $y$, and $c$ all have the same
+        sort.
+  \item A \emph{formula} is a conjunction of clauses.
+  \item A \emph{clause} is of the form $\forall x_{1} \in \Delta_{1}\text{.
+        }\forall x_{2} \in \Delta_{2}\dots\text{
+        }\forall x_{n} \in \Delta_{n}\text{. }\phi(x_{1}, x_{2}, \dots, x_{n})$,
+        where $\phi$ is a disjunction of literals that only contain variables
+        $x_{1}, \dots, x_{n}$ (and any constants).
+  \item We say that a clause is a \emph{(positive) unit clause} if:
+        \begin{itemize}
+          \item there is only one literal with a predicate, and
+          \item it is a positive literal.
+        \end{itemize}
+  \item A \emph{literal} is either an atom (i.e., a \emph{positive} literal) or
+        its negation (i.e., a \emph{negative} literal).
+  \item An \emph{atom} is either:
+  \begin{itemize}
+    \item $P(t_{1}, \dots, t_{m})$ for some predicate $P/m$ and terms
+          $t_{1}, \dots, t_{m}$ or
+    \item $x=y$ for some terms $x$ and $y$
+  \end{itemize}
+  \item An atom is \emph{ground} if it contains no variables (i.e., only
+        constants).
+  \item The \emph{arity} of a predicate is the number of arguments it takes,
+        i.e., $m$ in the case of predicate $P$.
+  \item When we want to denote a predicate together with its arity, we write
+        $P/m$.
+  \item A \emph{term} is either a variable or a constant.
+  \item Throughout the paper, we use set-theoretic notation, interpreting a
+        formula as a set of clauses and a clause as a set of literals. Moreover,
+        for readability, clauses written on separate lines are implicitly
+        conjoined.
+\end{itemize}
+
+\begin{definition}[Model]\label{def:model}
+  Let $\phi$ be a formula in \FO{}. For every predicate $p/n$ in $\phi$, let
+  ${(\Delta_{i}^{p})}_{i=1}^{n}$ be a list of the corresponding domains (not
+  necessarily distinct). Let $\sigma$ be a map from the domains of $\phi$ to
+  their interpretations as sets such that:
+  \begin{itemize}
+    \item the sets are pairwise disjoint, and
+    \item the constants in $\phi$ are included in the corresponding domains.
+  \end{itemize}
+  Then a \emph{structure} of $\phi$ (with respect to $\sigma$) is a set $M$ of
+  ground literals defined by adding either $p(\mathbf{t})$ or
+  $\neg p(\mathbf{t})$ for every predicate $p/n$ in $\phi$ and $n$-tuple
+  $\mathbf{t} \in \prod_{i=1}^{n} \sigma(\Delta_{i}^{p})$. A structure is a
+  \emph{model} if it satisfies $\phi$ (see Appendix~A of~Dilkas and
+  Belle~\shortcite{DBLP:journals/corr/abs-2306-04189} for more details).
+\end{definition}
+
+\begin{definition}[WFOMC]
+  Continuing from \cref{def:model}, for every predicate $p/n$ in $\phi$, let
+  $w^{+}(p), w^{-}(p) \in \mathbb{R}$ be its (positive and negative)
+  \emph{weights}. Unless explicitly specified otherwise, we assume weights to be
+  equal to one. The \emph{(symmetric) weighted first-order model count} (WFOMC)
+  of $\phi$ (with respect to $\sigma$, $w^{+}$, and $w^{-}$) is the quantity
+  \[
+    \sum_{M \models \phi} \prod_{p(\mathbf{t}) \in M} w^{+}(p) \prod_{\neg p(\mathbf{t}) \in M} w^{-}(p),
+  \]
+  where the sum is over all models of $\phi$.
+\end{definition}
 
@@
         its corresponding domain. In the input formula, all domains are assumed
-        to be pairwise disjoin.t Most of these assignments are typically left
+        to be pairwise disjoint Most of these assignments are typically left
         implicit and can be reconstructed from the quantifiers. For instance,
@@
 
-\paragraph{The \FO{} Logic (After Skolemization)}
-\begin{itemize}
-  \item Although existential quantifiers are supported, here we describe the
-        format used internally. During preprocessing, all existential
-        quantifiers are eliminated using
-        Skolemization~\cite{DBLP:conf/kr/BroeckMD14}, and the formula is
-        rewritten into a conjunction of clauses, each of which is in
-        \emph{prenex normal form}~\cite{hinman2018fundamentals}.
-  \item In the spirit of keeping sorts implicit, we always assume formulas `type
-        check' with respect to sorts. For example, if $P(x)$, $P(y)$, and
-        $x \ne c$ are all part of the formula (for some predicate $P$, variables
-        $x$ and $y$, and constant $c$), then $x$, $y$, and $c$ all have the same
-        sort.
-  \item A \emph{formula} is a conjunction of clauses.
-  \item A \emph{clause} is of the form $\forall x_{1} \in \Delta_{1}\text{.
-        }\forall x_{2} \in \Delta_{2}\dots\text{
-        }\forall x_{n} \in \Delta_{n}\text{. }\phi(x_{1}, x_{2}, \dots, x_{n})$,
-        where $\phi$ is a disjunction of literals that only contain variables
-        $x_{1}, \dots, x_{n}$ (and any constants).
-  \item We say that a clause is a \emph{(positive) unit clause} if:
-        \begin{itemize}
-          \item there is only one literal with a predicate, and
-          \item it is a positive literal.
-        \end{itemize}
-  \item A \emph{literal} is either an atom (i.e., a \emph{positive} literal) or
-        its negation (i.e., a \emph{negative} literal).
-  \item An \emph{atom} is either:
-  \begin{itemize}
-    \item $P(t_{1}, \dots, t_{m})$ for some predicate $P/m$ and terms
-          $t_{1}, \dots, t_{m}$ or
-    \item $x=y$ for some terms $x$ and $y$
-  \end{itemize}
-  \item An atom is \emph{ground} if it contains no variables (i.e., only
-        constants).
-  \item The \emph{arity} of a predicate is the number of arguments it takes,
-        i.e., $m$ in the case of predicate $P$.
-  \item When we want to denote a predicate together with its arity, we write
-        $P/m$.
-  \item A \emph{term} is either a variable or a constant.
-  \item Throughout the paper, we use set-theoretic notation, interpreting a
-        formula as a set of clauses and a clause as a set of literals. Moreover,
-        for readability, clauses written on separate lines are implicitly
-        conjoined.
-\end{itemize}
-
-For any variable $v$, let $\Dom(v)$ denote the domain over which $v$ is
-quantified. For any clause or literal $l$, let $\Vars(l)$ denote the set of
-variables in $l$, and, similarly, let
-$\Doms(l) \coloneqq \{\, \Dom(v) \mid v \in \Vars(l) \,\}$.
-
-\begin{definition}[Model]\label{def:model}
-  Let $\phi$ be a formula in \FO{}. For every predicate $p/n$ in $\phi$, let
-  ${(\Delta_{i}^{p})}_{i=1}^{n}$ be a list of the corresponding domains (not
-  necessarily distinct). Let $\sigma$ be a map from the domains of $\phi$ to
-  their interpretations as sets such that:
-  \begin{itemize}
-    \item the sets are pairwise disjoint, and
-    \item the constants in $\phi$ are included in the corresponding domains.
-  \end{itemize}
-  Then a \emph{structure} of $\phi$ (with respect to $\sigma$) is a set $M$ of
-  ground literals defined by adding either $p(\mathbf{t})$ or
-  $\neg p(\mathbf{t})$ for every predicate $p/n$ in $\phi$ and $n$-tuple
-  $\mathbf{t} \in \prod_{i=1}^{n} \sigma(\Delta_{i}^{p})$. A structure is a
-  \emph{model} if it satisfies $\phi$ (see Appendix~A of~Dilkas and
-  Belle~\shortcite{DBLP:journals/corr/abs-2306-04189} for more details).
-\end{definition}
-
-\begin{definition}[WFOMC]
-  Continuing from \cref{def:model}, for every predicate $p/n$ in $\phi$, let
-  $w^{+}(p), w^{-}(p) \in \mathbb{R}$ be its (positive and negative)
-  \emph{weights}. Unless explicitly specified otherwise, we assume weights to be
-  equal to one. The \emph{(symmetric) weighted first-order model count} (WFOMC)
-  of $\phi$ (with respect to $\sigma$, $w^{+}$, and $w^{-}$) is the quantity
-  \[
-    \sum_{M \models \phi} \prod_{p(\mathbf{t}) \in M} w^{+}(p) \prod_{\neg p(\mathbf{t}) \in M} w^{-}(p),
-  \]
-  where the sum is over all models of $\phi$.
-\end{definition}
+\begin{example}\label{example:functions}
+  Functions
+  \begin{itemize}
+    \item In \Ctwo: $\forall x \in \Delta\text{.
+          }\exists^{=1} y \in \Delta\text{. }P(x, y)$
+    \item In \UFO:
+          \begin{gather*}
+            \forall x, y \in \Delta\text{. }S(x) \lor \neg P(x, y)\\
+            |P| = |\Delta|
+          \end{gather*}
+    \item In \FO:
+          \begin{gather*}
+            \forall x \in \Delta\text{. }\exists y \in \Delta\text{. }P(x, y)\\
+            \forall x, y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z
+          \end{gather*}
+  \end{itemize}
+\end{example}
 
@@
   \begin{itemize}
-    \item the definition of a function is a strong assumption
-    \item the notation for a function call is now outdated
+    \item say something about what $\expr{}$ can contain (function calls,
+          various arithmetic operations, summations, non-negative integer
+          constants, variables introduces by the function signature or
+          summations)
   \end{itemize}
@@
   \item We write $\expr{}$ for an arbitrary algebraic expression.
-  \item A few terms have different meanings in the context of algebra as
-        compared to logic:
-        \begin{itemize}
-          \item a \emph{variable} is either:
-                \begin{itemize}
-                  \item a parameter of a function or
-                  \item a variable introduced by a summation, e.g., $i$ in
-                        $\sum_{i=1}^{n} \expr$.
-                \end{itemize}
-          \item A \emph{constant} is a non-negative integer.
-        \end{itemize}
+  \item Some terms have different meanings in the context of algebra as compared
+        to logic. Here, a \emph{constant} is a non-negative integer. Similarly,
+        a \emph{variable} is either a parameter of a function or a variable
+        introduced by a summation, e.g., $i$ in $\sum_{i=1}^{n} \expr$.
 \end{itemize}
@@
   \KwOut{set $\mathcal{E}$ of equations}
-  $(\mathcal{E}, \mathcal{F}, \mathcal{D}) \gets \Crane{$\phi$}$\;
-  $\mathcal{E} \gets \Simplify{$\mathcal{E}$}$\;
+  $(\mathcal{E}, \mathcal{F}, \mathcal{D}) \gets \Crane{$\phi$}$\;\label{line:first}
+  $\mathcal{E} \gets \Simplify{$\mathcal{E}$}$\;\label{line:second}
   \ForEach{base case $f(\mathbf{x}) \in \FindBaseCases{$\mathcal{E}$}$}{
@@
 
-\todo[inline]{In \cref{alg:main}, some kind of translation also needs to take
-  place, right?}
-
-We write \Crane for the first-order knowledge compilation algorithm of the
-original \textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23} that compiles a formula
-$\phi$ into:
-\begin{itemize}
-  \item a set $\mathcal{E}$ of equations,
-  \item a map $\mathcal{F}$ from function names to formulas, and
-  \item a map $\mathcal{D}$ from function names and parameter indices to
-        domains.
-\end{itemize}
-
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item \textsc{Crane}, \Cranetwo{}, or \Crane in the paragraph below
-  \end{itemize}
-}
-
-See \cref{alg:main}. The evaluation of base cases is done by simplifying the
-clauses and then using \textsc{Crane} to find the base cases. A particular
-domain is selected, and the clauses are simplified. Then, \textsc{Crane} is
-called on those clauses to evaluate the base cases. After that, we change the
-function names and variable to make it consistent with the previous domain to
-variable mapping, and append these base cases to the set of equations.
+\Cref{alg:main} outlines our overall approach for compiling a formula into a set
+of equation that include the required base cases. In short, we first use the
+knowledge compilation algorithm of the original
+\textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23} to compile the formula into:
+\begin{enumerate*}[label=(\roman*)]
+  \item set $\mathcal{E}$ of equations,
+  \item map $\mathcal{F}$ from function names to formulas, and
+  \item map $\mathcal{D}$ from function names and argument indices to domains.
+\end{enumerate*}
+After some algebraic simplification, $\mathcal{E}$ is passed to the
+\FindBaseCases procedure that returns a set of base cases that we need to find
+solutions for (described in \cref{sec:identifying}). For each base case
+$f(\mathbf{x})$, we identify the formula associated with $f$ and simplify it
+using the \Propagate procedure (described in \cref{sec:simplifying}). The
+algorithm then recurses on these simplified formulas and adds the resulting base
+case equations to $\mathcal{E}$. \Cref{example:overall} explains \cref{alg:main}
+in more detail.
+
+\begin{example}\label{example:overall}
+  Let us consider the following formula (previously examined by Dilkas and
+  Belle~\shortcite{DBLP:conf/kr/DilkasB23}) that defines predicate $P$ to be a
+  bijection between two sets $\Gamma$ and $\Delta$:
+  \[
+    \begin{gathered}
+      \forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }P(x, y)\\
+      \forall y \in \Delta\text{. }\exists x \in \Gamma\text{. }P(x, y)\\
+      \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z\\
+      \forall x, z \in \Gamma\text{. }\forall y \in \Delta\text{. }P(x, y) \land P(z, y) \Rightarrow x = z.
+    \end{gathered}
+  \]
+  In particular, we examine the first solution that \Cranebfs{} returns for this
+  formula.
+
+  After \cref{line:first,line:second}, we have
+  \begin{align*}
+    \mathcal{E} &= \left\{\,\begin{aligned}f(m, n) &= \sum_{l=0}^{n} \binom{n}{l}{(-1)}^{n-l}g(l, m),\\ g(l, m) &= g(l-1, m) + mg(l-1, m-1)\end{aligned}\,\right\};\\
+    \mathcal{D} &= \{\, (f, 1) \mapsto \Gamma, (f, 2) \mapsto \Delta, (g, 1) \mapsto \Delta^{\top}, (g, 2) \mapsto \Gamma \,\},
+  \end{align*}
+  where $\Delta^{\top}$ is a new domain introduced by \Crane. Then
+  \FindBaseCases identifies two base cases: $g(0, m)$ and $g(l, 0)$. In both
+  cases, \CompileWithBaseCases recurses on the formula $\mathcal{F}(g)$
+  simplified by assuming that one of the domains is empty. In the first case, we
+  recurse on the formula $\forall x \in \Gamma\text{. }S(x) \lor \neg S(x)$,
+  where $S$ is a predicate introduced by Skolemization with weights
+  $w^{+}(S) = 1$ and $w^{-}(S) = -1$. Hence, we get the base case
+  $g(0, m) = 0^{m}$. In the case of $g(l, 0)$, \Propagate{$\psi$, $\Gamma$, $0$}
+  returns an empty formula, giving us $g(l, 0) = 1$.
+\end{example}
 
@@
   \begin{itemize}
-    \item later check if I'm still using the syntax for $\Vars$, $\Dom$, etc.
-    \item align the last line to be a bit neater
     \item \Cref{alg2} now supports any base case domain sizes
@@
           \cref{sec:smoothingbase}.
+    \item For a literal or a clause $C$, let $\Doms(C)$ denote the set of the
+          corresponding domains. Make sure an example illustrates this.
   \end{itemize}
@@
 \begin{gather}
-  \forall x \in \Delta\text{. }\forall y, z \in \Gamma\text{. }P(x) \lor Q(y, z)\label[formula]{eq:example1}\\
-  \forall y, z \in \Gamma'\text{. }Q(y, z)\label[formula]{eq:example2}
+  \forall x \in \Delta\text{. }\forall y, z \in \Gamma\text{. }P(x) \lor Q(y, z)\label[clause]{eq:example1}\\
+  \forall y, z \in \Gamma'\text{. }Q(y, z)\label[clause]{eq:example2}
 \end{gather}
@@
 to zero and remove clauses with variables quantified over $\Delta$, we get
-\begin{equation}\label[formula]{eq:simplified}
+\begin{equation}\label[clause]{eq:simplified}
   \forall y, z \in \Gamma'\text{. }Q(y, z),
@@
 
+\todo[inline]{\Cranebfs{} must be introduced earlier (in the introduction?)}
+
 \begin{figure}
@@
             \item Eliminate (e.g., Emacs) warnings.
-            \item must run it by A\&G
+            \item must run it by all 3 other coauthors
             \item re-check submission instructions and formatting guidelines

### 2024-04-18 doc/paper.tex
Section 3.2

@@
 \crefname{line}{line}{lines}
+
+\crefalias{enumi}{type}
+\crefname{type}{Type}{Types}
+\creflabelformat{type}{#2\textup{#1}#3}
 
@@
           summations)
+    \item The definition of a function call contradicts the base case finding
+          algorithm. Maybe rephrase it to only look at function calls from $f$
+          to itself and assume:
+          \begin{itemize}
+            \item no mutual recursion,
+            \item these calls in particular have this form
+          \end{itemize}
   \end{itemize}
@@
   returns an empty formula, giving us $g(l, 0) = 1$.
+
+  Note that these base cases overlap when $l = m = 0$ but are consistent with
+  each other since $0^{0} = 1$. More generally, let $\phi$ be a formula with two
+  domains $\Gamma$ and $\Delta$, and let $n, m \in \mathbb{N}_{0}$. Then the
+  model count of \Propagate{$\phi$, $\Delta$, $n$} assuming $|\Gamma| = m$ is
+  the same as the model count of \Propagate{$\phi$, $\Gamma$, $m$} assuming
+  $|\Delta| = n$.
 \end{example}
+
+\todo[inline]{This last claim sounds like something that should be proven.}
 
@@
 \subsection{Propagating Domain Size Assumptions}\label{sec:simplifying}
-
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item \Cref{alg2} now supports any base case domain sizes
-    \item NOTE: if $C' = \emptyset$, then the clause becomes irrelevant and
-          doesn't need smoothing, so can be skipped
-  \end{itemize}
-}
 
@@
 
-\todo[inline,caption={}]{ Turn these notes into a coherent description (that
-  doesn't mention \textsc{Crane}):
-  \begin{itemize}
-    \item Each base case identified by \FindBaseCases can be interpreted as
-          assuming some domain...
-    \item \Propagate (\cref{alg2}) to find the transformed formula corresponding
-          to each base case identified by \FindBaseCases and call \textsc{Crane}
-          on the formula to obtain the required base cases.
-    \item Clauses where all literals have variables quantified over the empty
-          domain are still removed.
-    \item $C'$ is guaranteed to be non-empty.
-    \item \Cref{line:smoothing1,line:smoothing2} are explained in
-          \cref{sec:smoothingbase}.
-    \item For a literal or a clause $C$, let $\Doms(C)$ denote the set of the
-          corresponding domains. Make sure an example illustrates this.
-  \end{itemize}
-}
-\todo[inline]{Maybe prove consistency: if two base case overlap, their numerical
-  answers also overlap.}
+\Propagate (\cref{alg2}) modifies formula $\phi$ with the assumption that domain
+$\Delta$ has size $n \in \mathbb{N}_{0}$. In the case of $n=0$, many clauses
+become vacuously satisfied and can be removed. In the case of
+$n > 0$\footnote{None of the formulas considered in this work had $n > 1$.}, we
+perform partial grounding, using constants to replace all variables quantified
+over $\Delta$. \Cref{alg2} considers these two cases separately. For a literal
+or a clause $C$, we write $\Doms(C)$ to denote the set of corresponding domains.
+
+In the case of $n = 0$, consider three types of clauses:
+\begin{enumerate*}[label=(\roman*)]
+  \item those that do not mention $\Delta$,\label{type1}
+  \item those in which every literal contains variables quantified over
+  $\Delta$, and\label{type2}
+  \item those that have some literals with variables quantified over $\Delta$
+  and some without.\label{type3}
+\end{enumerate*}
+\Cref{type1} clauses are transferred to the new formula $\phi'$ unchanged. For
+\cref{type2} clauses, $C' = \emptyset$, so these clauses are filtered out. One
+might think that the same should be done with \cref{type3} clauses, however,
+\cref{line:smoothing1,line:smoothing2} perform a new kind of smoothing, the
+explanation of which we defer to \cref{sec:smoothingbase}.
+
+In the case of $n>0$, we introduce $n$ new constants. Consider an arbitrary
+clause $C \in \phi$ and let $m \in \mathbb{N}_{0}$ be the number of variables in
+$C$ quantified over $\Delta$. If $m=0$, then, similarly to the previous case, we
+add $C$ directly to $\phi'$. Otherwise, we add a clause to $\phi'$ with every
+possible way of replacing the $m$ variables in $C$ with some combination of the
+$n$ new constants.
+
+\begin{example}
+  Let us consider the clause $C \equiv \forall x \in \Gamma\text{.
+  }\forall y, z \in \Delta\text{. } \neg P(x, y) \lor \neg P(x, z) \lor y=z$.
+  Then
+  $\Doms(C) = \Doms(\neg P(x, y)) = \Doms(\neg P(x, z)) = \{\, \Gamma, \Delta \,\}$,
+  and $\Doms(y=z) = \{\, \Delta \,\}$. A call to \Propagate{$\{\, C \,\}$,
+    $\Delta$, $3$} would produce the following formula with nine clauses:
+  \begin{align*}
+    \forall x \in \Gamma\text{. }\neg P(x, c_{1}) \lor& \neg P(x, c_{1}) \lor c_{1}=c_{1}\\
+    \forall x \in \Gamma\text{. }\neg P(x, c_{1}) \lor& \neg P(x, c_{2}) \lor c_{1}=c_{2}\\
+    \vdots&\\
+    \forall x \in \Gamma\text{. }\neg P(x, c_{3}) \lor& \neg P(x, c_{3}) \lor c_{3}=c_{3},\\
+  \end{align*}
+  where $c_{1}$, $c_{2}$, and $c_{3}$ are the new constants.
+\end{example}
 
@@
 
-\todo[inline]{Can I prove that the additions to smoothing outlined in the rest
-  of this section `do the right thing'?}
+\todo[inline,caption={}]{
+\begin{itemize}
+  \item Cite something when introducing the idea of smoothing. Maybe both
+        propositional and first-order sources.
+  \item Can I prove that the additions to smoothing outlined in the rest of this
+        section `do the right thing'?
+\end{itemize}
+}
 
@@
 
-\todo[inline]{Can I use an example based on permutations or something similar?}
+\todo[inline]{Must include an example of propagating the empty-domain
+  assumption (ideally based on previous examples).}
 
@@
                   where necessary
+            \item Something to think about that could inspire some kind of
+                  theorems: how can I assume that a domain is empty if there are
+                  constants associated with it?
           \end{itemize}

### 2024-04-19 doc/paper.tex
Section 3.1 (except for the proof)

@@
 
-\section{Introduction}
+\section{Introduction (TODO)}
 
@@
 
-\section{Preliminaries}
+\section{Preliminaries (TODO)}
 
@@
 
-\subsection{Logic}\label{sec:logic}
+\subsection{Logic (TODO)}\label{sec:logic}
 
@@
 
-\subsection{Algebra}\label{sec:algebra}
-
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item say something about what $\expr{}$ can contain (function calls,
-          various arithmetic operations, summations, non-negative integer
-          constants, variables introduces by the function signature or
-          summations)
-    \item The definition of a function call contradicts the base case finding
-          algorithm. Maybe rephrase it to only look at function calls from $f$
-          to itself and assume:
-          \begin{itemize}
-            \item no mutual recursion,
-            \item these calls in particular have this form
-          \end{itemize}
-  \end{itemize}
-}
+\subsection{Algebra (TODO)}\label{sec:algebra}
 
@@
   is a variable.
-\end{definition}
-
-\begin{definition}
-  Given a function $f$ with signature $f(\mathbf{x})$, a \emph{function call} of
-  $f$ is $f(\mathbf{y})$, where each $y_{i}$ is either $x_{i} - c_{i}$ or
-  $c_{i}$ for some constant $c_{i} \in \mathbb{N}_{0}$.
 \end{definition}
@@
 After some algebraic simplification, $\mathcal{E}$ is passed to the
-\FindBaseCases procedure that returns a set of base cases that we need to find
-solutions for (described in \cref{sec:identifying}). For each base case
+\FindBaseCases procedure (described in \cref{sec:identifying}) that returns a
+set of base cases that we need to find solutions for. For each base case
 $f(\mathbf{x})$, we identify the formula associated with $f$ and simplify it
@@
   returns an empty formula, giving us $g(l, 0) = 1$.
-
-  Note that these base cases overlap when $l = m = 0$ but are consistent with
-  each other since $0^{0} = 1$. More generally, let $\phi$ be a formula with two
-  domains $\Gamma$ and $\Delta$, and let $n, m \in \mathbb{N}_{0}$. Then the
-  model count of \Propagate{$\phi$, $\Delta$, $n$} assuming $|\Gamma| = m$ is
-  the same as the model count of \Propagate{$\phi$, $\Gamma$, $m$} assuming
-  $|\Delta| = n$.
 \end{example}
 
-\todo[inline]{This last claim sounds like something that should be proven.}
+Note that these base cases overlap when $l = m = 0$ but are consistent with each
+other since $0^{0} = 1$. More generally, let $\phi$ be a formula with two
+domains $\Gamma$ and $\Delta$, and let $n, m \in \mathbb{N}_{0}$. Then the model
+count of \Propagate{$\phi$, $\Delta$, $n$} assuming $|\Gamma| = m$ is the same
+as the model count of \Propagate{$\phi$, $\Gamma$, $m$} assuming $|\Delta| = n$.
+
+\todo[inline]{Can I turn the above into a theorem?}
+
+Finally, we note that the \Simplify procedure plays a crucial role in
+simplifying a common algebraic pattern $\sum_{m=0}^{n}[a \le m \le b] f(m)$.
+Here:
+\begin{enumerate*}[label=(\roman*)]
+  \item $n$ is a variable,
+  \item $a, b \in \mathbb{N}_{0}$ are constants,
+  \item $f$ is an expression that may depend on $m$, and
+  \item $[a \le m \le b] =
+  \begin{cases}
+    1 & \text{if $a \le m \le b$} \\
+    0 & \text{otherwise}
+  \end{cases}$ is the Iverson bracket.
+\end{enumerate*}
+\Simplify transforms this pattern into
+$f(a) + f(a+1) + \cdots + f(\min\{\, n, b \,\})$. For instance, in the case of
+\cref{example:overall}, \Simplify transforms
+$g(l, m) = \sum_{k=0}^{m}[0 \le k \le 1]\binom{m}{k}g(l-1, m-k)$ into the
+simpler form above.
+
+\todo[inline]{A concluding sentence that introduces the remaining subsections?}
 
@@
   $\mathcal{B} \gets \emptyset$\;
-  \ForEach{equation $(\ldots = \expr{}) \in \mathcal{E}$}{
+  \ForEach{equation $(f(\mathbf{x}) = \expr{}) \in \mathcal{E}$}{
     \ForEach{function call $f(\mathbf{y}) \in \expr{}$}{\label{line:functioncall}
-      let $f(\mathbf{x})$ be the signature of $f$\;
       \ForEach{$y_{i} \in \mathbf{y}$} {
@@
         }
-        \ElseIf{$y_{i} = x_{i} - c_{i}$}{
+        \ElseIf{$y_{i} = x_{i} - c_{i}$ for some $c_{i} \in \mathbb{N}_{0}$}{
           \For{$j \gets 0$ \KwTo $c_{i} - 1$}{\label{line:lim}
@@
 
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item introduce the Iverson bracket (it's only used in this subsection)
-    \item \Cref{alg1} is now fixed and supersedes the description below (and the
-          code!)
-    \item NOTE: exactly one of the if and else-if branches always applies
-  \end{itemize}
-}
-
-The algorithm is described as \cref{alg1}. We know that if, say, on the RHS of
-all equations, the domain size appears as $m - c_1, m - c_2, \dots, m - c_k$,
-then finding $f(0, x_1, x_2, \dots)$, $f(1, x_1, x_2, \dots)$,
-$\dots f(m_0, x_1, x_2, \dots)$ for every function $f$, where
-$m_0 = \max(c_1, c_2, \dots c_k) - 1$ forms a sufficient set of base cases.
-Hence, in order to do the same efficiently, we can take that domain for which
-$m_0$ is the minimum, i.e. $\argmin(\max(c_1, c_2, \dots c_k))$. Ideally, we
-should calculate the base cases by finding the base cases up to
-$\max(c_{1}, c_{2}, \dots) - 1$. However, currently only empty and singleton
-domains are supported.
-
-First, expand the summations in each equation. Here we expand the summations of
-the form: $\sum_{x=0}^{x_{1}} \expr{} \cdot [a \le x < b]$ or similar
-inequalities where $x$ is bounded by constants and $a$ and $b$ are constants, by
-substituting the value of $x$ from $a$ to $b-1$. For example, we replace
-$\sum_{x=0}^{x_1} \binom{x_{1}}{x} f(x_1 - x) \cdot [0 \le x < 2]$ by
-$\binom{x_{1}}{0} f(x_1) + \binom{x_{1}}{1} f(x_1-1)$.
-
-\begin{itemize}
-  \item \cref{line:insert} for $f(\mathbf{x}) = f(y, z)$, $x_{i} = y$, and
-        $n = 0$, add $f(y, z)[y \mapsto 0] = f(0, z)$ to $\mathcal{B}$.
-\end{itemize}
-
-\begin{theorem}
-  Under the following assumptions, \cref{alg1} is guaranteed to return a
-  sufficient set of base cases:
-  \begin{itemize}
-    \item there is no mutual recursion
-    \item each function $f$ has exactly one equation with $f$ on the LHS;
-    \item in the recursive definition of function $f(x_{1},\dots,x_{n})$, the
-          $i$-th argument of each call to $f$ on the RHS is of the form
-          $x_{i} - c_{i}$, where:
-          \begin{itemize}
-            \item $c_{i} \ge 0$ for all $i$, and
-            \item $c_{i} > 0$ for at least one $i$.
-          \end{itemize}
-  \end{itemize}
+\Cref{alg1} summarises the implementation of \FindBaseCases. For each recursive
+call from a function $f$ to itself, we consider two types of arguments:
+\begin{enumerate*}[label=(\roman*)]
+  \item constants and
+  \item arguments of the form $x_{i} - c_{i}$, where $c_{i} \in \mathbb{N}_{0}$
+  is a constant, and $x_{i}$ is the $i$-th argument of the signature of $f$.
+\end{enumerate*}
+In the former case, we consider a base case specifically for that constant. In
+the latter case, we consider a base case for constants from zero up to (but not
+including) $c_{i}$. \Cref{thm:halting} below motivates this approach.
+
+\begin{example}
+  Consider the recursive function $g$ from \cref{example:overall}.
+  \FindBaseCases{$\mathcal{E}$} iterates over two function calls: $g(l-1, m)$
+  and $g(l-1, m-1)$. The former produces the base case $g(0, m)$, while the
+  latter produces both $g(0, m)$ and $g(l, 0)$.
+\end{example}
+
+\todo[inline]{Prove (lots of notes, handwritten and elsewhere)}
+
+\begin{theorem}[Halting]\label{thm:halting}
+  Let us assume the following about the input set of equations $\mathcal{E}$:
+  \begin{enumerate}
+    \item Each function $f$ has exactly one equation with $f$ on the LHS.\@ We
+          call this equation the \emph{definition} of $f$.
+    \item There exists a topological ordering of all functions ${(f_{i})}_{i}$
+          such that the definition of $f_{i}$ does not contain function calls to
+          $f_{j}$ with $j > i$.\footnote{This condition excludes the possibility
+          of mutual recursion and similar cyclic scenarios and is akin to
+          stratified logic programs~\cite{DBLP:books/sp/Lloyd87}.}
+    \item For every equation $(f(\mathbf{x}) = \expr) \in \mathcal{E}$, every
+          recursive function call $f(\mathbf{y}) \in \expr$ satisfies the
+          following:
+          \begin{itemize}
+            \item each $y_{i}$ is either $x_{i} - c_{i}$ or $c_{i}$ for some
+                  constant $c_{i} \in \mathbb{N}_{0}$;
+            \item there exists $i$ such that $y_{i} = x_{i} - c_{i}$ for some
+                  $c_{i} > 0$.
+          \end{itemize}
+  \end{enumerate}
+  Then the set of base cases $\mathcal{B}$ returned by
+  \FindBaseCases{$\mathcal{E}$} is \emph{sufficient} for $\mathcal{E}$ in the
+  following sense. The evaluation of any function call with non-negative
+  arguments halts as long as the evaluation of base cases is prioritised over
+  the corresponding recursive definitions.\footnote{Recall that, as previously
+    discussed, the order in which base cases are considered is immaterial.}
 \end{theorem}
-
-\begin{example}
-  For an equation $f(m, n) = 2 \times f(m-1, n)$, \cref{alg1} returns $f(0, n)$.
-\end{example}
 
@@
 
-\section{Smoothing}
+\section{Smoothing (TODO)}
 
@@
 
-\subsection{Smoothing for Base Cases}\label{sec:smoothingbase}
+\subsection{Smoothing for Base Cases (TODO)}\label{sec:smoothingbase}
 
@@
 
-\subsection{Smoothing the FCG}
+\subsection{Smoothing the FCG (TODO)}
 
@@
 
-\subsection{Stage 1: Propagating Unit Clauses `Upwards'}
+\subsection{Stage 1: Propagating Unit Clauses `Upwards' (TODO)}
 
@@
 
-\subsection{Stage 2: Adding Smoothing Nodes}
+\subsection{Stage 2: Adding Smoothing Nodes (TODO)}
 
@@
 
-\section{Generating C++ Code}\label{sec:cpp}
+\section{Generating C++ Code (TODO)}\label{sec:cpp}
 
@@
 
-\section{Experimental Evaluation}
+\section{Experimental Evaluation (TODO)}
 
@@
 
-\section{Conclusion}
+\section{Conclusion (TODO)}
 

### 2024-04-19 doc/paper.tex
Section 2.2

@@
 
-\subsection{Algebra (TODO)}\label{sec:algebra}
-
-\begin{itemize}
-  \item We write $\expr{}$ for an arbitrary algebraic expression.
-  \item Some terms have different meanings in the context of algebra as compared
-        to logic. Here, a \emph{constant} is a non-negative integer. Similarly,
-        a \emph{variable} is either a parameter of a function or a variable
-        introduced by a summation, e.g., $i$ in $\sum_{i=1}^{n} \expr$.
-\end{itemize}
+\subsection{Algebra}\label{sec:algebra}
+
+We write $\expr{}$ for an arbitrary algebraic expression. Note that some terms
+have different meanings in the context of algebra as compared to logic. Here, a
+\emph{constant} is a non-negative integer. Similarly, a \emph{variable} is
+either a parameter of a function or a variable introduced by a summation, e.g.,
+$i$ in $\sum_{i=1}^{n} \expr$. A (function) \emph{signature} is
+$f(x_{1}, \dots, x_{n})$ (written $f(\mathbf{x})$ for short), where $f$ is an
+$n$-ary function, and each $x_{i}$ is a variable. An \emph{equation} is
+$f(\mathbf{x}) = \expr{}$, where $f(\mathbf{x})$ is a signature.
 
 \begin{definition}
-  A (function) \emph{signature} is $f(x_{1}, \dots, x_{n})$ (written
-  $f(\mathbf{x})$ for short), where $f$ is an $n$-ary function, and each $x_{i}$
-  is a variable.
-\end{definition}
-
-\begin{definition}
-  An \emph{equation} is $f(\mathbf{x}) = \expr{}$, where $f(\mathbf{x})$ is a
-  signature. We refer to $f(\mathbf{x})$ and $\expr{}$ as the \emph{left-hand
-    side} (LHS) and the \emph{right-hand side} (RHS) of the equation,
-  respectively.
-\end{definition}
-
-\begin{definition}\label{def:basecase}
   Let $f$ be a function with signature $f(\mathbf{x})$. Then a \emph{base case}
@@
   \begin{enumerate}
-    \item Each function $f$ has exactly one equation with $f$ on the LHS.\@ We
-          call this equation the \emph{definition} of $f$.
+    \item Each function $f$ has exactly one equation with $f$ on the left-hand
+          side.\@ We call this equation the \emph{definition} of $f$.
     \item There exists a topological ordering of all functions ${(f_{i})}_{i}$
@@
 
+\todo[inline]{Remove mentions of LHS and RHS.}
+
 The target is to generate C++ code that can evaluate numerical values of the

### 2024-04-19 doc/paper.tex
Section 5

@@
 We write $\mathbb{N}_{0}$ for the set of non-negative integers. In the context
-of both algebra and logic, we write $C[x \mapsto y]$ for $C$ with all
-occurrences of $x$ replaced with $y$.
+of both algebra and logic, we write $S\sigma$ for a \emph{substitution} $\sigma$
+applied to an expression $S$, where
+$\sigma = [x_{1} \mapsto y_{1}, x_{2} \mapsto y_{2}, \dots, x_{n} \mapsto y_{n}]$
+denotes the replacement of all occurrences of $x_{i}$ with $y_{i}$ for all
+$i = 1, \dots, n$.
 
@@
 
-\begin{definition}
-  Let $f$ be a function with signature $f(\mathbf{x})$. Then a \emph{base case}
-  of $f$ is a function call $f(\mathbf{y})$ such that either $y_{i} = x_{i}$ or
-  $y_{i} \in \mathbb{N}_{0}$ for all $i$, and the latter case applies at least
-  once.
+\begin{definition}\label{def:basecase}
+  Let $f(\mathbf{x})$ be a function call where each $x_{i}$ is either a constant
+  or a variable (note that signatures are included in this definition). Then a
+  function call $f(\mathbf{y})$ is a \emph{base case} of $f(\mathbf{x})$ if
+  $f(\mathbf{y}) = f(\mathbf{x})\sigma$, where $\sigma$ is a substitution that
+  replaces one or more $x_{i}$ with a constant.
 \end{definition}
@@
 
-\section{Generating C++ Code (TODO)}\label{sec:cpp}
-
-\todo[inline]{Remove mentions of LHS and RHS.}
-
-The target is to generate C++ code that can evaluate numerical values of the
-model counts based on the equations generated by \CompileWithBaseCases. The
-translation of a set $\mathcal{E}$ of equations into a C++ program works as
-follows.
-
-First, we create a cache for each function in $\mathcal{E}$. This is implemented
-as a multi-dimensional vector containing objects of \texttt{class cache\_elem}
-defined as shown in the example code. The default initialization of this object
-is to $-1$ which is useful for recognizing unevaluated cases.
-
-Next, we create a function definition for the LHS of each equation in
-$\mathcal{E}$, including all functions and base cases. The signatures of these
-functions is decided as follows. A function call containing only variable
-arguments is named as the function itself, and ones with constants in their
-arguments are suffixed with a string that contains \texttt{'x'} at the $i$th
-place if the $i$th argument is variable and the $i$th argument if that argument
-is a constant. For example, $f(x_{1}, x_{2}, x_{3})$ is declared as \texttt{int
-  f(int x1, int x2, int x3);} and $f(1, x_{2}, x_{3})$ is declared as
-\texttt{int f\_1xx(int x2, int x3);} (the constant arguments are removed from
-the signature).
-
-The RHS of each equation in $\mathcal{E}$ is used to define the body of the
-equation corresponding to the LHS of that equation. The function body (for a
-function \texttt{func} corresponding to equation $e$) is formed as follows.
-
-First, we check if the evaluation is already present in the cache. If so, then
-we return the cache element. The cache accesses are done using the
-\texttt{get\_elem} function (definition given in the example), which resizes the
-cache if the accessed index is out of range.
-
-Second, if the element is absent, then we decide if the arguments corresponding
-to $e$ or one of the functions corresponding to the base cases, based on the
-value of the arguments. If it corresponds to the base cases, then we directly
-call the base case function and return its value. Else, we evaluate the value
-using the RHS, store the evaluated value in the cache and return the evaluated
-value. Note that in this step, we only call the base case function with one more
-constant argument than \texttt{func}. For example, \texttt{f0(x, y)} would call
-\texttt{f0\_0x(y)} if $x = 0$ and \texttt{f0\_x0(x)} if $y = 0$.
-
-Third, to translate the RHS, we convert $\sum_{x=a}^{b} \expr{}$ to
-\begin{lstlisting}[escapeinside={(*}{*)}]
-([y,z,...](){
-    int sum = 0;
-    for(int x = a; x <= b; x++)
-        sum += (*$\expr{}$*);
-    return sum;
-})()
-\end{lstlisting}
-where $y, z, \dots$ are the free variables present in $\expr{}$.
+\todo[inline]{Somewhere: mention that we're primarily concerned with computing
+  unweighted model counts, but everything trivially extends to the weighted
+  setting as well.}
+
+\section{Generating C++ Code}\label{sec:cpp}
+
+In this section, we describe the last step of \Cranetwo{} outlined in
+\cref{fig:overview}: translating the set of equations $\mathcal{E}$ produced by
+\CompileWithBaseCases into C++ code. The produced C++ program can then be
+compiled and executed with different command-line arguments to compute the model
+count of the formula for different (combinations of) domain sizes.
+
+Each equation in $\mathcal{E}$ is compiled into a C++ function, together with
+its own cache for memoisation. Let
+$e = (f(\mathbf{x}) = \expr{}) \in \mathcal{E}$ be an arbitrary equation, and
+let $\mathbf{c} \in \mathbb{N}_{0}^{n}$ represent the arguments of the
+corresponding C++ function. The implementation of $e$ consists of three parts.
+First, we check whether $\mathbf{c}$ is already in the cache of $e$ (in which
+case the cached value is returned). Second, for each base case $f(\mathbf{y})$
+of $f(\mathbf{x})$ (as in \cref{def:basecase}), we check whether $\mathbf{c}$
+\emph{matches} $\mathbf{y}$, i.e., $c_{i} = y_{i}$ whenever
+$y_{i} \in \mathbb{N}_{0}$. In this case, $\mathbf{c}$ is redirected to the C++
+function that corresponds to the definition of base case $f(\mathbf{y})$.
+Finally, if the above cases fail, we evaluate $\mathbf{c}$ according to
+$\expr{}$, store the result in the cache, and return it.
 
@@
                   constants associated with it?
+            \item consider turning small sections (e.g., Section 5) into
+                  subsections of even paragraphs.
           \end{itemize}

### 2024-04-22 doc/paper.tex
Section 4.1

@@
   \begin{itemize}
-    \item 9 pages!!!
+    \item 9 pages including appendices but not acknowledgements
     \item Add some papers mentioned in:
@@
     \node at (-1, 0) (formula) {$\phi$};
-    \node[draw,rounded rectangle] at (3, 0) (alg1) {\CompileWithBaseCases};
+    \node[draw,rounded rectangle] at (3, 0) (compilewithbasecases) {\CompileWithBaseCases};
     \node[draw,rounded rectangle] at (9, 0) (compilation) {Compile to C++};
@@
 
-    \node[draw,rounded rectangle] at (3, -2) (alg2) {\FindBaseCases};
-    \node[draw,rounded rectangle,left = 0.1cm of alg2] (crane) {\Crane};
-    \node[draw,rounded rectangle,right = 0.1cm of alg2] (alg3) {\Propagate};
-    \node[draw,rounded rectangle,right = 0.1cm of alg3] (simplify) {\Simplify};
-
-    \node[draw,fit={(alg1) (compilation) (crane) (alg2) (alg3)},inner ysep=7pt,yshift=5pt] {};
+    \node[draw,rounded rectangle] at (3, -2) (findbasecases) {\FindBaseCases};
+    \node[draw,rounded rectangle,left = 0.1cm of findbasecases] (crane) {\Crane};
+    \node[draw,rounded rectangle,right = 0.1cm of findbasecases] (propagate) {\Propagate};
+    \node[draw,rounded rectangle,right = 0.1cm of propagate] (simplify) {\Simplify};
+
+    \node[draw,fit={(compilewithbasecases) (compilation) (crane) (findbasecases) (propagate)},inner ysep=7pt,yshift=5pt] {};
     \node at (0.2, 0.5) {\Cranetwo};
 
-    \draw[-Latex] (formula) -- (alg1);
-    \draw[-Latex] (alg1) -- node[above] {$\mathcal{E}$} (compilation);
+    \draw[-Latex] (formula) -- (compilewithbasecases);
+    \draw[-Latex] (compilewithbasecases) -- node[above] {$\mathcal{E}$} (compilation);
     \draw[-Latex] (compilation) -- (cpp);
@@
 
-    \draw[-Latex,dashed] (alg1) -- node[midway,left] {uses} (crane);
-    \draw[-Latex,dashed] (alg1) -- node[midway,left] {uses} (alg2);
-    \draw[-Latex,dashed] (alg1) -- node[midway,left] {uses} (alg3);
-    \draw[-Latex,dashed] (alg1) -- node[midway,right] {uses} (simplify);
+    \draw[-Latex,dashed] (compilewithbasecases) -- node[midway,left] {uses} (crane);
+    \draw[-Latex,dashed] (compilewithbasecases) -- node[midway,left] {uses} (findbasecases);
+    \draw[-Latex,dashed] (compilewithbasecases) -- node[midway,left] {uses} (propagate);
+    \draw[-Latex,dashed] (compilewithbasecases) -- node[midway,right] {uses} (simplify);
   \end{tikzpicture}
@@
 
-\todo[inline]{By pointing to the outline in \cref{fig:overview}, make forward
-  references to the sections of the paper.}
+\todo[inline,caption={}]{
+  \begin{itemize}
+    \item By pointing to the outline in \cref{fig:overview}, make forward
+          references to the sections of the paper.
+    \item Somewhere: mention that we're primarily concerned with computing
+          unweighted model counts, but everything trivially extends to the
+          weighted setting as well.
+    \item Introduce greedy search and breadth-first search (BFS), together with
+          \Cranegreedy{} and \Cranebfs{}. The knowledge compilation part of both
+          \textsc{Crane} and \Cranetwo{} can be executed using either greedy
+          (similar to \textsc{ForcLift}) or breadth-first search. We use both in
+          our experiments, denoting them as \Cranegreedy{} and \Cranebfs{},
+          respectively.
+    \item Introduce the WFOMC acronym.
+    \item Introduce first-order knowledge compilation as a class of WFOMC
+          algorithms, defining/mentioning compilation rules, FCG, etc.
+  \end{itemize}
+}
 
@@
     \item In \FO:
-          \begin{gather*}
-            \forall x \in \Delta\text{. }\exists y \in \Delta\text{. }P(x, y)\\
-            \forall x, y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z
-          \end{gather*}
-  \end{itemize}
+    \begin{equation}\label[formula]{eq:fo}
+      \begin{gathered}
+        \forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }P(x, y)\\
+        \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z
+      \end{gathered}
+    \end{equation}
+  \end{itemize}
+
+  Note that \cref{eq:fo} is written with two domains instead of one. Clearly,
+  the model count does not change whenever $|\Gamma| = |\Delta|$. As was
+  previously observed by Dilkas and Belle~\shortcite{DBLP:conf/kr/DilkasB23},
+  such a reformulation can help first-order knowledge compilation algorithms
+  find efficient solutions.
 \end{example}
@@
 \begin{algorithm}[t]
-  \caption{\protect\CompileWithBaseCases{$\phi$}}\label{alg:main}
+  \caption{\protect\CompileWithBaseCases{$\phi$}}\label{alg:compilewithbasecases}
   \KwIn{formula $\phi$}
@@
 
-\Cref{alg:main} outlines our overall approach for compiling a formula into a set
-of equation that include the required base cases. In short, we first use the
-knowledge compilation algorithm of the original
+\Cref{alg:compilewithbasecases} outlines our overall approach for compiling a
+formula into a set of equation that include the required base cases. In short,
+we first use the knowledge compilation algorithm of the original
 \textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23} to compile the formula into:
@@
 algorithm then recurses on these simplified formulas and adds the resulting base
-case equations to $\mathcal{E}$. \Cref{example:overall} explains \cref{alg:main}
-in more detail.
+case equations to $\mathcal{E}$. \Cref{example:overall} explains
+\cref{alg:compilewithbasecases} in more detail.
 
@@
 \begin{algorithm}[t]
-  \caption{\protect\FindBaseCases{$\mathcal{E}$}}\label{alg1}
+  \caption{\protect\FindBaseCases{$\mathcal{E}$}}\label{alg:findbasecases}
   \KwIn{set $\mathcal{E}$ of equations}
@@
 
-\Cref{alg1} summarises the implementation of \FindBaseCases. For each recursive
-call from a function $f$ to itself, we consider two types of arguments:
+\Cref{alg:findbasecases} summarises the implementation of \FindBaseCases. For
+each recursive call from a function $f$ to itself, we consider two types of
+arguments:
 \begin{enumerate*}[label=(\roman*)]
@@
 
-\begin{theorem}[Halting]\label{thm:halting}
+\begin{theorem}[Termination]\label{thm:halting}
   Let us assume the following about the input set of equations $\mathcal{E}$:
@@
   following sense. The evaluation of any function call with non-negative
-  arguments halts as long as the evaluation of base cases is prioritised over
-  the corresponding recursive definitions.\footnote{Recall that, as previously
-    discussed, the order in which base cases are considered is immaterial.}
+  arguments terminates as long as the evaluation of base cases is prioritised
+  over the corresponding recursive definitions.\footnote{Recall that, as
+    previously discussed, the order in which base cases are considered is
+    immaterial.}
 \end{theorem}
@@
 \begin{algorithm}[t]
-  \caption{\protect\Propagate{$\phi$, $\Delta$, $n$}}\label{alg2}
+  \caption{\protect\Propagate{$\phi$, $\Delta$, $n$}}\label{alg:propagate}
   \KwIn{formula $\phi$, domain $\Delta$, $n \in \mathbb{N}_{0}$}
@@
 
-\Propagate (\cref{alg2}) modifies formula $\phi$ with the assumption that domain
-$\Delta$ has size $n \in \mathbb{N}_{0}$. In the case of $n=0$, many clauses
-become vacuously satisfied and can be removed. In the case of
+\Propagate (\cref{alg:propagate}) modifies formula $\phi$ with the assumption
+that domain $\Delta$ has size $n \in \mathbb{N}_{0}$. In the case of $n=0$, many
+clauses become vacuously satisfied and can be removed. In the case of
 $n > 0$\footnote{None of the formulas considered in this work had $n > 1$.}, we
 perform partial grounding, using constants to replace all variables quantified
-over $\Delta$. \Cref{alg2} considers these two cases separately. For a literal
-or a clause $C$, we write $\Doms(C)$ to denote the set of corresponding domains.
+over $\Delta$. \Cref{alg:propagate} considers these two cases separately. For a
+literal or a clause $C$, we write $\Doms(C)$ to denote the set of corresponding
+domains.
 
@@
 
-\subsection{Smoothing for Base Cases (TODO)}\label{sec:smoothingbase}
-
-\todo[inline]{Must include an example of propagating the empty-domain
-  assumption (ideally based on previous examples).}
-
-\paragraph{Key point.}
-If there is a predicate $P$ that has nothing to do with domain $\Delta$, make
-sure that $P$ remains as part of the formula even if all clauses with $P$ can be
-removed. Which literal is picked on \cref{line:smoothing1} of \cref{alg2} is not
-important because any choice achieves the same goal: constructing a clause that
-mentions the same predicates as $C'$ and is satisfied by any structure.
-
-\begin{fact}
-  Assuming that domain $\Delta$ is empty, any clause that contains
-  `$\forall x \in \Delta$' (for any variable $x$) is vacuously satisfied by all
-  structures.
-\end{fact}
-
-For example, consider the formula
-\begin{gather}
-  \forall x \in \Delta\text{. }\forall y, z \in \Gamma\text{. }P(x) \lor Q(y, z)\label[clause]{eq:example1}\\
-  \forall y, z \in \Gamma'\text{. }Q(y, z)\label[clause]{eq:example2}
-\end{gather}
-and assume that $\Gamma' \subseteq \Gamma$. If we set $|\Delta|$
-to zero and remove clauses with variables quantified over $\Delta$, we get
-\begin{equation}\label[clause]{eq:simplified}
-  \forall y, z \in \Gamma'\text{. }Q(y, z),
-\end{equation}
-but the model count of \cref{eq:simplified} is one. However, the actual model
-count should be $2^{|\Gamma|^2 - |\Gamma'|^2}$. That is, $Q$ as a relation is a
-subset of $\Gamma \times \Gamma$. While \cref{eq:example1} becomes vacuously
-true, \cref{eq:example2} fixes the value of $Q$ over
-$\Gamma' \times \Gamma' \subseteq \Gamma \times \Gamma$. Hence, the number of
-different values that $Q$ can take is
-$|(\Gamma \times \Gamma) \setminus (\Gamma' \times \Gamma')| = |\Gamma|^{2} - |\Gamma'|^{2}$.
-
-We address this issue by converting clauses with universal quantifiers over the
-empty domain to tautologies, hence retaining all the predicates that have no
-argument assigned to the empty domain. For example, we would convert
-\cref{eq:example1,eq:example2} to
+\subsection{Smoothing for Base Cases}\label{sec:smoothingbase}
+
+In this section, we motivate and describe \cref{line:smoothing1,line:smoothing2}
+of \cref{alg:propagate}. Suppose that \Propagate is called with arguments
+$(\phi, \Delta, 0)$, i.e., we are simplifying formula $\phi$ by assuming that
+domain $\Delta$ is empty. Informally, if there is a predicate $P$ in $\phi$ that
+has nothing to do with domain $\Delta$, the role of smoothing is to preserve all
+occurrences of $P$ even if all clauses with $P$ become vacuously satisfied. We
+note that the approach presented in this section is far from unique and explain
+it via an example below.
+
+\begin{example}\label{example:basecasesmoothing}
+  Let $\phi$ be
+  \begin{align}
+    \forall x \in \Delta\text{. }\forall y, z \in \Gamma&\text{. }Q(x) \lor P(y, z)\label[clause]{eq:example1}\\
+    \forall y, z \in \Gamma'&\text{. }P(y, z)\label[clause]{eq:example2},
+  \end{align}
+  where $\Gamma' \subseteq \Gamma$ is a domain introduced by a compilation rule.
+  Note that, as a relation, $P \subseteq \Gamma \times \Gamma$.
+
+  Let us reason by hand about the model count of $\phi$ when
+  $\Delta = \emptyset$. Predicate $Q$ can only take one value, i.e.,
+  $Q = \emptyset$. The value of $P$ is fixed over $\Gamma' \times \Gamma'$ by
+  \cref{eq:example2} but is allowed to vary freely over
+  $(\Gamma \times \Gamma) \setminus (\Gamma' \times \Gamma')$ since
+  \cref{eq:example1} is vacuously satisfied by all structures. Hence, the right
+  model count should be $2^{|\Gamma|^2 - |\Gamma'|^2}$.
+
+  However, without \cref{line:smoothing2}, \Propagate would simplify $\phi$ to
+  $\forall y, z \in \Gamma'\text{. }P(y, z)$. Here, $P$ is defined as a subset
+  of $\Gamma' \times \Gamma'$. Clearly, this simplified formula has only one
+  model: $\{\, P(y, z) \mid y, z \in \Gamma' \,\}$.
+
+  With \cref{line:smoothing2} included, $\phi$ is transformed to
   \begin{gather*}
-  \forall y, z \in \Gamma\text{. }Q(y, z) \lor \neg Q(y, z)\\
-  \forall y, z \in \Gamma'\text{. }Q(y, z).
+    \forall y, z \in \Gamma\text{. }P(y, z) \lor \neg P(y, z)\\
+    \forall y, z \in \Gamma'\text{. }P(y, z),
   \end{gather*}
-The model count returned by this will also consider the truth value of $Q$ over
-$y \in \Gamma \setminus \Gamma'$ or $z \in \Gamma \setminus \Gamma'$.
+  which retains the correct model count.
+\end{example}
+
+Note that the choice of $l$ on \cref{line:smoothing1} of \cref{alg:propagate} is
+inconsequential because any choice achieves the same goal: constructing a
+tautological clause that retains the literals in $C'$.
 
@@
     \item Describe \cref{fig:smoothing1,fig:smoothing2}
+    \item Introduce the compilation rules
   \end{itemize}
@@
     [$\DR(c \in \Delta)$,name=dr,ellipse,draw,label={right:\textcolor{blue}{3. $\{\, \forall x \in \Delta\text{. }P(x) \,\}$}}
-    [$\land$,ellipse,draw,label={left:\textcolor{blue}{2. $\{\, P(c) \,\}$}},label={right:\textcolor{blue}{6. $\{\, P(c), \forall x \in \Delta\text{. }x \ne c \Rightarrow P(x) \,\}$}},
-    [$P(c)$,rectangle,draw,fill=green!20,label={272:\textcolor{blue}{1. $\{\, P(c) \,\}$}}],
+    [$\land$,ellipse,draw,label={left:\textcolor{blue}{2. $\{\, P(c) \,\}$}},label={right:\textcolor{blue}{6. $\{\, P(c), \forall x \in \Delta\text{. }x \ne c \Rightarrow P(x) \,\}$}}
+    [$P(c)$,rectangle,draw,fill=green!20,label={272:\textcolor{blue}{1. $\{\, P(c) \,\}$}}]
     [$\CR(\Delta' \gets \Delta \setminus \{\, c \,\})$,ellipse,draw,label={87:\textcolor{blue}{5. $\{\, \forall x \in \Delta\text{. }x \ne c \Rightarrow P(x) \,\}$}}
@@
   \end{forest}
-  \caption{An example based on permutation counting (but simplified a lot). The
-    arc from the $\Reff$ node to the $\DR$ node is omitted.}\label{fig:smoothing1}
+  \caption{An example based on bijection counting (but simplified a lot). The
+    arc from the $\Reff$ node to the $\DR$ node is
+    omitted.}\label{fig:smoothing1}
 \end{figure}
@@
     for tree={sn edges}
-    [$\DR(c \in \Delta)$,name=dr,ellipse,draw,
-    [$P(c)$,rectangle,draw,fill=green!20],
+    [$\DR(c \in \Delta)$,name=dr,ellipse,draw
+    [$\land$,ellipse,draw,dashed,edge=dashed
+    [$P(c)$,rectangle,draw,fill=green!20]
     [$\forall x \in \Delta\text{. }x \ne c \Rightarrow P(x) \lor \neg P(x)$,rectangle,dashed,edge=dashed,draw,fill=blue!20]
+    ]
     ]
@@
   \caption{An artificial example of a situation when smoothing nodes need to be
-    added below a $\DR$ node}\label{fig:smoothing2}
+    added below a $\DR$ node. The dashed part is added during
+    smoothing}\label{fig:smoothing2}
 \end{figure}
-
-\begin{algorithm}
-  \caption{Propagate atoms for smoothing across the FCG}\label{alg:smoothing}
-  \SetKwData{changed}{changed}
-  \KwIn{FCG $(V, s, N^+, \tau)$}
-  \KwIn{function $\iota$ that maps vertex types in $\mathcal{T}$ to sets of atoms}
-  \KwIn{functions $\{\,f_t\,\}_{t \in \mathcal{T}}$ that map a list of sets of atoms to a set of atoms}
-  \KwOut{function $S$ that maps vertices in $V$ to sets of atoms}
-  $S \gets \{\, v \mapsto \iota(\tau(v)) \mid v \in V \,\}$\;
-  $\changed \gets \texttt{true}$\;
-  \While{\changed}{
-    $\changed \gets \texttt{false}$\;
-    \ForEach{vertex $v \in V$}{
-      $S' \gets f_{\tau(v)}(\langle S(w) \mid w \in N^+(v) \rangle)$\;
-      \If{$S' \ne S(v)$}{
-        $\changed \gets \texttt{true}$\;
-        $S(v) \gets S'$\;
-      }
-    }
-  }
-\end{algorithm}
 
@@
 unchanged, the first step of this process would result in an infinite loop
-whenever a cycle is encountered. \Cref{alg:smoothing} outlines how the first
-step can be adapted to an arbitrary directed graph.
+whenever a cycle is encountered.
 
@@
         $c \in \Delta$. For each unit clause received from the child node,
-        replace each occurrence of $\phi(x)$ or $\forall x \in \Delta\text{.
+        replace each occurrence of $\phi(c)$ or $\forall x \in \Delta\text{.
         } x \ne c \Rightarrow \phi(x)$ with $\forall x \in \Delta\text{.
@@
 
-\todo[inline]{Somewhere: mention that we're primarily concerned with computing
-  unweighted model counts, but everything trivially extends to the weighted
-  setting as well.}
-
 \section{Generating C++ Code}\label{sec:cpp}
@@
 
-Comparing \Cranetwo{} and \textsc{FastWFOMC} on a larger set of benchmarks is
-challenging because there is no automated way to translate a formula in \FO{} or
-\Ctwo{} into \UFO{} (or even check if such an encoding is possible).
+We compare \Cranetwo{} (in both BFS and greedy modes) with \textsc{FastWFOMC}
+and \textsc{ForcLift} on two problems previously considered by Dilkas and
+Belle~\shortcite{DBLP:conf/kr/DilkasB23}: the function-counting problem from
+\cref{example:functions} and the bijection-counting problem described below.
+Note that comparing \Cranetwo{} and \textsc{FastWFOMC} on a larger set of
+benchmarks is challenging because there is no automated way to translate a
+formula in \FO{} or \Ctwo{} into \UFO{} (or even check if such an encoding is
+possible). The experiments were run on an AMD~Ryzen~7~5800H processor with
+\SI{16}{\gibi\byte} of memory and Arch Linux~6.8.2-arch2-1 operating system.
+\textsc{FastWFOMC} was executed using Python~3.8.19 with Python-FLINT~0.5.0.
 
@@
 \begin{itemize}
-  \item Functions (\cref{example:functions})
-  \item Permutations
+  \item Bijections
         \begin{itemize}
@@
                 with weights $w^{-}(R) = w^{-}(S) = -1$
-          \item In \FO:
-                \begin{gather*}
-                  \forall x \in \Delta\text{. }\exists y \in \Delta\text{. }P(x, y)\\
-                  \forall y \in \Delta\text{. }\exists x \in \Delta\text{. }P(x, y)\\
-                  \forall x, y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z\\
-                  \forall x, y, z \in \Delta\text{. }P(x, y) \land P(z, y) \Rightarrow x = z
-                \end{gather*}
-          \item NOTE: when it's the same domain, counting bijections,
-                injections, surjections, and partial surjections all boil down
-                to the same integer sequence.
-        \end{itemize}
-\end{itemize}
-
-\todo[inline]{ If it is possible to rewrite a formula to have more sorts, we do
-  that. Explain in more detail and with an example. Mention that this has been
-  observed previously by my previous work (i.e., linear vs cubic complexity). }
-
-\paragraph{Setup.}
-\begin{itemize}
-  \item The experiments were run on an AMD~Ryzen~7~5800H processor with
-        \SI{16}{\gibi\byte} of memory and Arch Linux~6.8.2-arch2-1 operating
-        system. \textsc{FastWFOMC} was run using Python~3.8.19 with
-        Python-FLINT~0.5.0.
-  \item The knowledge compilation part of both \textsc{Crane} and \Cranetwo{}
-        can be executed using either greedy (similar to \textsc{ForcLift}) or
-        breadth-first search. We use both in our experiments, denoting them as
-        \Cranegreedy{} and \Cranebfs{}, respectively.
-\end{itemize}
-
-\todo[inline]{\Cranebfs{} must be introduced earlier (in the introduction?)}
+          \item In \FO: see \cref{example:overall}
+        \end{itemize}
+\end{itemize}
 
@@
   \input{plot}
-  \caption{The runtime data of WFOMC algorithms on permutation- and
-    function-counting problems on domains of sizes $1, 2, \dots, 35$. Note that
-    the $y$ axis is on a logarithmic scale.}\label{fig:plot}
+  \caption{The runtime data of WFOMC algorithms on domains of sizes
+    $1, 2, \dots, 35$. Note that the $y$ axis is on a logarithmic
+    scale.}\label{fig:plot}
 \end{figure}
+% TODO: rename permutations to bijections in the plot
 
@@
   \item Note that \Cranebfs{} is able to handle more instances than
-        \textsc{ForcLift} (e.g., the permutation-counting problem in our
+        \textsc{ForcLift} (e.g., the bijection-counting problem in our
         experiments and other problems in my previous work).
@@
         \SI{41}{\second}---\Cranetwo{} scales up to domains of sizes \num{e4}
-        and \num{3e5} in permutation- and function-counting problems,
-        respectively (whereas \textsc{FastWFOMC} already takes longer with
-        domains of sizes\dots)
+        and \num{3e5} in bijection- and function-counting problems, respectively
+        (whereas \textsc{FastWFOMC} already takes longer with domains of
+        sizes\dots)
 \end{itemize}
@@
                   subsections of even paragraphs.
+            \item Authors may submit a separate PDF with additional information
+                  supporting their claims (such as proof details, additional
+                  experimental results, further details on experimental design,
+                  etc).
           \end{itemize}

### 2024-04-23 doc/paper.tex
The introductory part of Section 4

@@
         showstringspaces=false}
+
+\newcommand{\crefrangeconjunction}{--}
 
@@
 
-\section{Smoothing (TODO)}
-
-Goal of smoothing: whenever rules such as unit propagation or
-inclusion-exclusion (maybe just these two?) eliminate the consideration of some
-ground atoms, smoothing nodes should be inserted `at the same level' so that
-these ground atoms are still considered when counting. Note that conjunction
-nodes are irrelevant here because multiplication is associative. `At the same
-level' means that, e.g., if some ground atoms were eliminated from consideration
-before/after performing independent partial grounding, then the smoothing node
-should also appear before/after the independent partial grounding node.
-
-\todo[inline,caption={}]{
-\begin{itemize}
-  \item Cite something when introducing the idea of smoothing. Maybe both
-        propositional and first-order sources.
-  \item Can I prove that the additions to smoothing outlined in the rest of this
-        section `do the right thing'?
-\end{itemize}
-}
+\section{Smoothing}
+
+Smoothness originates in propositional knowledge compilation where it is defined
+as the property that, for every disjunction node, all disjuncts (as subtrees of
+the circuit) contain the same atoms~\cite{darwiche2001tractable}. Van den Broeck
+et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11} generalise smoothness to
+first-order logic, adding set-disjunction and inclusion-exclusion nodes
+alongside disjunction.
+
+The motivation for smoothing is as follows. Whenever compilation rules such as
+unit propagation and inclusion-exclusion simplify the formula, some ground atoms
+might be eliminated from consideration (see \cref{example:basecasesmoothing}
+below). To account for them during counting, smoothing nodes (i.e., tautological
+clauses such as $P(c) \lor \neg P(c)$) are added to the FCG at an appropriate
+location.
+
+In the rest of this section, we extend the smoothing algorithm of Van den Broeck
+et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11} even further.
+\Cref{sec:smoothingbase} describes the role smoothing plays in the
+base-case-finding algorithm from \cref{sec:main}. Then,
+\cref{sec:smoothingfcg1,sec:smoothingfcg2,sec:smoothingfcg3} show how to adapt
+smoothing to the compilation rules introduced by Dilkas and
+Belle~\shortcite{DBLP:conf/kr/DilkasB23}.
 
@@
 
-\subsection{Smoothing the FCG (TODO)}
+\subsection{Smoothing the FCG (TODO)}\label{sec:smoothingfcg1}
 
@@
   \begin{itemize}
-    \item It seems like I'll need to introduce:
-          \begin{itemize}
-            \item FCGs
-            \item node types (be consistent w.r.t.\ node vs vertex)
-            \item their notation
-          \end{itemize}
+    \item introduce the relevant node types and their notation
     \item Describe \cref{fig:smoothing1,fig:smoothing2}
-    \item Introduce the compilation rules
   \end{itemize}
@@
 Smoothing is a two-step process. First, atoms that are still accounted for in
-the circuit are propagated upwards. Then, at vertices of certain types, missing
+the circuit are propagated upwards. Then, at nodes of certain types, missing
 atoms are detected and additional sinks are created to account for them. If left
@@
 
-\subsection{Stage 1: Propagating Unit Clauses `Upwards' (TODO)}
+\todo[inline]{Don't say `upwards'}
+
+\subsection{Stage 1: Propagating Unit Clauses (TODO)}\label{sec:smoothingfcg2}
 
@@
 
-\subsection{Stage 2: Adding Smoothing Nodes (TODO)}
+\subsection{Stage 2: Adding Smoothing Nodes (TODO)}\label{sec:smoothingfcg3}
 

### 2024-04-23 doc/paper.tex
The rest of Section 4

@@
 
-\section{Preliminaries (TODO)}
+\section{Preliminaries}
 
 \Cref{sec:logic} introduces the fundamental ideas of first-order logic and
-WFOMC, and discusses the different logics used in the latter.\@
-\Cref{sec:algebra} introduces the terminology we use to describe the output of
+WFOMC, and discusses the different logics used in the latter.\@ Then,
+\cref{sec:algebra} introduces the terminology we use to describe the output of
 the original \textsc{Crane} algorithm~\cite{DBLP:conf/kr/DilkasB23}, i.e.,
@@
 \begin{example}\label{example:overall}
-  Let us consider the following formula (previously examined by Dilkas and
+  Consider the following formula (previously examined by Dilkas and
   Belle~\shortcite{DBLP:conf/kr/DilkasB23}) that defines predicate $P$ to be a
@@
 \Cref{sec:smoothingbase} describes the role smoothing plays in the
-base-case-finding algorithm from \cref{sec:main}. Then,
-\cref{sec:smoothingfcg1,sec:smoothingfcg2,sec:smoothingfcg3} show how to adapt
-smoothing to the compilation rules introduced by Dilkas and
+base-case-finding algorithm from \cref{sec:main}. Then, \cref{sec:smoothingfcg1}
+shows how to adapt smoothing to the compilation rules introduced by Dilkas and
 Belle~\shortcite{DBLP:conf/kr/DilkasB23}.
@@
 
-\subsection{Smoothing the FCG (TODO)}\label{sec:smoothingfcg1}
-
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item introduce the relevant node types and their notation
-    \item Describe \cref{fig:smoothing1,fig:smoothing2}
-  \end{itemize}
-}
+\subsection{Smoothing the FCG}\label{sec:smoothingfcg1}
+
+Smoothing is a two-step process. First, positive unit clauses (denoting sets of
+ground atoms that are accounted for in the FCG) are propagated `upwards', i.e.,
+in the opposite direction of FCG arcs. Then, at nodes of certain types, missing
+atoms are detected and additional nodes are added to account for them. In this
+section, we:
+\begin{enumerate*}[label=(\roman*)]
+  \item describe the relevant node types from previous work,
+  \item show how smoothing ought to work for these node types, and
+  \item illustrate how the new smoothing techniques work on two example FCGs.
+\end{enumerate*}
+
+Before describing the proposed changes to smoothing, we briefly review the
+compilation rules (and their corresponding node types) introduced by Dilkas and
+Belle~\shortcite{DBLP:conf/kr/DilkasB23} while referring to the aforementioned
+paper for precise definitions. \emph{Domain recursion} selects a domain
+$\Delta$, introduces a new constant $c \in \Delta$, and, for each variable $x$
+quantified over $\Delta$, considers two possibilities: $x = c$ or $x \ne c$,
+modifying the formula accordingly. We denote the resulting node as
+$\DR(c \in \Delta)$. \emph{Constraint removal} applies to formulas such that,
+for some domain $\Delta$, each variable $x$ quantified over $\Delta$ is followed
+by the inequality constraint $x \ne c$. In other words, the relevant clauses can
+be rewritten to begin with $\forall x \in \Delta\text{.
+}x \ne c \Rightarrow \ldots$ For such formulas, constraint removal replaces
+$\Delta$ with a new domain $\Delta'$ and removes the $x \ne c$ constraints. We
+denote the resulting node as $\CR(\Delta' \gets \Delta \setminus \{\,c\,\})$.
+Finally, \emph{caching} detects when the input formula $\phi$ is equal to a
+previously-encountered formula $\psi$ except for having different domains. We
+denote the resulting node as $\Reff(\sigma)$, where $\sigma$ is the substitution
+mapping the domains of $\psi$ to their corresponding domains in $\phi$.
+
+\paragraph{Stage~1 for domain recursion.}
+When visiting a $\DR(c \in \Delta)$ node, for each unit clause received from the
+child node, we replace each occurrence of $\phi(c)$ or
+$\forall x \in \Delta\text{. } x \ne c \Rightarrow \phi(x)$ with
+$\forall x \in \Delta\text{. }\phi(x)$. In other words, if the subgraph below
+the domain recursion node covers some of the ground atoms that are affected by
+domain recursion, then it should cover all of them. If the relevant subgraph
+indeed covers those ground atoms, Stage~2 will do nothing. Otherwise, smoothing
+nodes will be added below the domain recursion node to cover the difference
+between the sets of ground atoms assigned to the domain recursion node and its
+child node.
+
+\paragraph{Stage~1 for constraint removal and caching.}
+When visiting a $\CR(\Delta' \gets \Delta \setminus \{\,c\,\})$ node, we reverse
+constraint removal. In other words, we replace each
+$\forall x \in \Delta'\text{. }\phi(x)$ with $\forall x \in \Delta\text{.
+}x \ne c \Rightarrow \phi(x)$. When visiting a $\Reff(\sigma)$ node, we apply
+substitution $\sigma$ to the unit clauses coming from the child node.
+
+\paragraph{Stage~2 for domain recursion.}
+We need not add smoothing nodes immediately below constraint removal or caching
+nodes. However, for domain recursion we do the following.
+\begin{enumerate}
+  \item Suppose the set of unit clauses assigned to the child node during
+        Stage~1 contains both $\phi(c)$ and $\forall x \in \Delta\text{.
+        } x \ne c \Rightarrow \phi(x)$. In other words, the only difference
+        between the two clauses is that one has the constant $c$ whereas the
+        other one has a variable $x \ne c$. In such a case, we merge the two
+        clauses into $\forall x \in \Delta\text{. }\phi(x)$.
+  \item If necessary, we add smoothing nodes below the domain recursion node to
+        cover the difference between the unit clauses assigned to the domain
+        recursion node during Stage~1 and the unit clauses of the child node
+        post-processed by the step above.
+\end{enumerate}
+
+\begin{figure}
+  \centering
+  \begin{forest}
+    for tree={sn edges}
+    [$\DR(c \in \Delta)$,name=dr,ellipse,draw
+    [$\land$,ellipse,draw,dashed,edge=dashed
+    [$P(c)$,rectangle,draw,fill=green!20]
+    [$\forall x \in \Delta\text{. }x \ne c \Rightarrow P(x) \lor \neg P(x)$,rectangle,dashed,edge=dashed,draw,fill=blue!20]
+    ]
+    ]
+  \end{forest}
+  \caption{An artificial example of an FCG where a smoothing node must be added
+    below a domain recursion node. The dashed nodes and arcs are added during
+    Stage~2 of smoothing.}\label{fig:smoothing2}
+\end{figure}
+
+\begin{example}[An FCG that needs smoothing]
+  \Cref{fig:smoothing2} shows an FCG with a domain recursion node
+  $\DR(c \in \Delta)$ immediately followed by a single $P(c)$ node. In this
+  case, Stage~1 of smoothing assigns $\{\, \forall x \in \Delta\text{.
+  }P(x) \,\}$ to the former node and $\{\, P(c) \,\}$ to the latter. Since these
+  two sets of unit clauses cover different ground atoms, Stage~2 adds a
+  smoothing node to cover $P(x)$ for all $x \in \Delta \setminus \{\, c \,\}$.
+\end{example}
 
@@
   \end{forest}
-  \caption{An example based on bijection counting (but simplified a lot). The
-    arc from the $\Reff$ node to the $\DR$ node is
-    omitted.}\label{fig:smoothing1}
+  \caption{A smooth FCG loosely based on \cref{example:overall}. The arc from
+    the caching node to the domain recursion node is omitted for compactness.
+    The labels next to nodes show the sets of unit clauses assigned to each node
+    during Stage~1 and the order of these assignments, omitting empty
+    assignments that replace a set $S$ with $S$ itself.}\label{fig:smoothing1}
 \end{figure}
 
-\begin{figure}
-  \centering
-  \begin{forest}
-    for tree={sn edges}
-    [$\DR(c \in \Delta)$,name=dr,ellipse,draw
-    [$\land$,ellipse,draw,dashed,edge=dashed
-    [$P(c)$,rectangle,draw,fill=green!20]
-    [$\forall x \in \Delta\text{. }x \ne c \Rightarrow P(x) \lor \neg P(x)$,rectangle,dashed,edge=dashed,draw,fill=blue!20]
-    ]
-    ]
-  \end{forest}
-  \caption{An artificial example of a situation when smoothing nodes need to be
-    added below a $\DR$ node. The dashed part is added during
-    smoothing}\label{fig:smoothing2}
-\end{figure}
-
-Smoothing is a two-step process. First, atoms that are still accounted for in
-the circuit are propagated upwards. Then, at nodes of certain types, missing
-atoms are detected and additional sinks are created to account for them. If left
-unchanged, the first step of this process would result in an infinite loop
-whenever a cycle is encountered.
-
-\todo[inline]{Don't say `upwards'}
-
-\subsection{Stage 1: Propagating Unit Clauses (TODO)}\label{sec:smoothingfcg2}
-
-\begin{description}
-  \item[\texttt{Ref}.] During smoothing, when unit clauses are propagated in the
-        opposite direction of the FCG arcs (i.e., `upwards'), when visiting a
-        \texttt{Ref} node, these clauses are translated using the domain map of
-        the \texttt{Ref} node. For example, if the domain map include
-        $\Delta \mapsto \Delta'$, and the unit clause mentions $\Delta$, then
-        replace it by $\Delta'$.
-  \item[Constraint removal.] Do reverse constraint removal. Assuming that
-        domain $\Delta$ with constraints $x \ne c$ (for some constant
-        $c \in \Delta$) were replaced with domain $\Delta'$, replace each
-        $\forall x \in \Delta'\text{. }\phi(x)$ with
-        $\forall x \in \Delta\text{. }X \ne c \Rightarrow \phi(x)$.
-  \item[Domain recursion.] Suppose the domain recursion node introduces constant
-        $c \in \Delta$. For each unit clause received from the child node,
-        replace each occurrence of $\phi(c)$ or $\forall x \in \Delta\text{.
-        } x \ne c \Rightarrow \phi(x)$ with $\forall x \in \Delta\text{.
-        }\phi(x)$. This can be seen as a claim about what ground atoms the
-        domain recursion node \emph{should} cover (or a temporary assumption).
-        If the relevant subgraph indeed covers those ground atoms, Stage~2 will
-        do nothing. Otherwise, smoothing nodes will be added below the domain
-        recursion node to cover the difference between what was propagated from
-        the domain recursion node and what was received from the child node.
-\end{description}
-
-\subsection{Stage 2: Adding Smoothing Nodes (TODO)}\label{sec:smoothingfcg3}
-
-We never need to add smoothing nodes after \texttt{Ref} or constraint removal
-nodes. However, for domain recursion we must do the following.
-
-\begin{enumerate}
-  \item Whenever the set of unit clauses of the child node contains two formulas
-        $\phi(c)$ and $\forall x \in \Delta\text{.
-        } x \ne c \Rightarrow \phi(x)$ (i.e., the only difference between the
-        two formulas is that one has the constant $c$ whereas the other one has
-        a variable $x \ne c$), merge them into $\forall x \in \Delta\text{.
-        }\phi(x)$.
-  \item Add smoothing nodes below the domain recursion node for the difference
-        between the unit clauses assigned to the domain recursion node during
-        Stage 1 and the unit clauses of the child node post-processed by the
-        step above. For example, if the child node `covers' only $P(c)$, then
-        Stage 1 assigns $\forall x \in \Delta\text{. }P(x)$ to the domain
-        recursion node. The smoothing node below the domain recursion node then
-        has the clause $\forall x \in \Delta\text{. } x \ne c \Rightarrow P(x)$.
-\end{enumerate}
-
-\todo[inline]{Can I formally define what is meant by `difference'?}
+\begin{example}[A smooth FCG]\label{example:smooth}
+  Stage~1 of smoothing is more involved in the case of the FCG in
+  \cref{fig:smoothing1}. The unit clause $P(c)$ propagates to the conjunction
+  node and is then generalised to $\forall x \in \Delta\text{. }P(x)$ by the
+  domain recursion node. It then propagates to the caching node, changing form
+  to $(\forall x \in \Delta\text{.
+  }P(x))[\Delta \mapsto \Delta'] \equiv \forall x \in \Delta'\text{. }P(x)$. The
+  constraint removal node re-introduces the constraints, transforming the clause
+  to $\forall x \in \Delta\text{. }x \ne c \Rightarrow P(x)$, which is then
+  propagated to the conjunction node, joining $P(c)$.
+
+  In Stage~2, $P(c)$ and $\forall x \in \Delta\text{. }x \ne c \Rightarrow P(x)$
+  are merged into $\forall x \in \Delta\text{. }P(x)$. Since the resulting
+  clause matches the clause assigned to the domain recursion node, the FCG is
+  already smooth.
+\end{example}
+
+The algebraic interpretation of \cref{fig:smoothing1} is an equation $e$ that
+defines a recursive function. The right-hand side of $e$ already covers $P(c)$,
+and the smoothing algorithm correctly recognises that the recursive call also
+covers $P(x)$ for all $x \in \Delta \setminus \{\, c \,\}$.
 

### 2024-04-24 doc/paper.tex
The abstract

@@
 
-\usepackage[backgroundcolor=lightgray]{todonotes}
+\usepackage[backgroundcolor=lightgray]{todonotes} % TODO: remove
 \usepackage{listings}
@@
 \DeclareMathOperator{\Doms}{Doms}
-\DeclareMathOperator*{\argmin}{argmin} % TODO: soon to be removed
 
@@
 \begin{abstract}
-  TODO: at most 200 words
+  First-order model counting (FOMC) is the problem of counting the number of
+  models of a sentence in first-order logic. Recently, a new algorithm for FOMC
+  was proposed that, instead of simply providing the final count, generates
+  definitions of (possibly recursive) functions, which can be evaluated with
+  different arguments to compute the model count for any domain size. However,
+  the algorithm did not include base cases in the recursive definitions. This
+  work makes three contributions. Firstly, we demonstrate how to construct
+  function definitions that include base cases by modifying the logical formulas
+  used in the FOMC algorithm. Secondly, we extend the well-known circuit
+  modification technique in knowledge compilation, known as smoothing, to work
+  with the formulas corresponding to base cases and the recently proposed node
+  types, such as domain recursion and constraint removal. Thirdly, we introduce
+  a compilation algorithm that transforms the function definitions into C++
+  code, equipped with arbitrary-precision arithmetic. These additions allow the
+  new FOMC algorithm to scale to domain sizes over \num{9000} times larger than
+  the current state of the art, as demonstrated through experimental results.
 \end{abstract}
@@
 formula in \FO{} or \Ctwo{} into \UFO{} (or even check if such an encoding is
-possible). The experiments were run on an AMD~Ryzen~7~5800H processor with
-\SI{16}{\gibi\byte} of memory and Arch Linux~6.8.2-arch2-1 operating system.
-\textsc{FastWFOMC} was executed using Python~3.8.19 with Python-FLINT~0.5.0.
-
-\paragraph{Benchmarks (probably for supplementary material).}
-\begin{itemize}
-  \item Bijections
-        \begin{itemize}
-          \item In \Ctwo:
+possible).
+
+The \FO{} formula for bijections is described in \cref{example:overall}. The
+equivalent formula in \Ctwo{} is
 \begin{gather*}
   \forall x \in \Delta\text{. }\exists^{=1} y \in \Delta\text{. }P(x, y)\\
-                  \forall y \in \Delta\text{. }\exists^{=1} x \in \Delta\text{. }P(x, y)
+  \forall y \in \Delta\text{. }\exists^{=1} x \in \Delta\text{. }P(x, y).
 \end{gather*}
-          \item In \UFO:
+Similarly, in \UFO{} the same formula can be written as
 \begin{gather*}
@@
   \forall x, y \in \Delta\text{. }S(x) \lor \neg P(y, x)\\
-                  |P| = |\Delta|
+  |P| = |\Delta|,
 \end{gather*}
-                with weights $w^{-}(R) = w^{-}(S) = -1$
-          \item In \FO: see \cref{example:overall}
-        \end{itemize}
-\end{itemize}
+where $w^{-}(R) = w^{-}(S) = -1$.
+
+We run each of the four algorithms once on each combination of formula and
+domain size, the latter ranging from one up to and including 35. The experiments
+were run on an AMD~Ryzen~7~5800H processor with \SI{16}{\gibi\byte} of memory
+and Arch Linux~6.8.2-arch2-1 operating system. \textsc{FastWFOMC} was executed
+using Python~3.8.19 with Python-FLINT~0.5.0.
 
@@
   \input{plot}
-  \caption{The runtime data of WFOMC algorithms on domains of sizes
-    $1, 2, \dots, 35$. Note that the $y$ axis is on a logarithmic
-    scale.}\label{fig:plot}
+  \caption{The runtime of WFOMC algorithms. Note that the $y$ axis is on a
+    logarithmic scale.}\label{fig:plot}
 \end{figure}
-% TODO: rename permutations to bijections in the plot
-
-\paragraph{Results.}
-\begin{itemize}
-  \item As shown in \cref{fig:plot}, the runtimes of all compilation-based
-        algorithms remain practically constant in contrast to the rapidly
-        increasing runtimes of \textsc{FastWFOMC}.
-  \item Note that \Cranebfs{} is able to handle more instances than
-        \textsc{ForcLift} (e.g., the bijection-counting problem in our
-        experiments and other problems in my previous work).
-  \item Although the search/compilation part is slower in \Cranetwo{} than in
-        \textsc{ForcLift}, the difference is negligible.
-  \item The runtimes of three out of four WFOMC algorithms appear constant
-        because---for these counting problems and domain sizes---compilation
-        time dominates inference time (recall that compilation time is
-        independent of domain sizes). Indeed, the maximum inference time of both
-        \Cranebfs{} and \Cranegreedy{} across these experiments is
-        only \SI{4}{\milli\second}.
-  \item The runtimes of \Cranetwo{} have lower variation than those of
-        \textsc{ForcLift} because with \textsc{ForcLift} we compile the formula
-        anew for each domain size whereas with \Cranetwo{} we compile it once
-        and reuse the resulting C++ program for all domain sizes.
-  \item As another point of comparison,---in at most
-        \SI{41}{\second}---\Cranetwo{} scales up to domains of sizes \num{e4}
-        and \num{3e5} in bijection- and function-counting problems, respectively
-        (whereas \textsc{FastWFOMC} already takes longer with domains of
-        sizes\dots)
-\end{itemize}
-
-\todo[inline]{maybe examine \textsc{ForcLift}'s scalability as well}
+
+\Cref{fig:plot} shows total runtime values as a measure of the overall
+performance of each algorithm. For the three knowledge compilation algorithms,
+we also separately track compilation and inference times and comment on them
+where relevant. Note that \Cranebfs{} is able to handle more instances than
+either \textsc{ForcLift} or \Cranegreedy{}, i.e., the bijection-counting problem
+in our experiments as well as similar formulas examined
+previously~\cite{DBLP:conf/kr/DilkasB23}.
+
+As shown in the figure, the runtimes of all compilation-based algorithms remain
+practically constant in contrast to the rapidly increasing runtimes of
+\textsc{FastWFOMC}. Although the search/compilation part is slower in
+\Cranetwo{} than in \textsc{ForcLift}, the difference is negligible. The
+runtimes of the knowledge compilation algorithms appear constant because---for
+these counting problems and domain sizes---compilation time dominates inference
+time (recall that compilation time is independent of domain sizes). Indeed, the
+maximum inference time of both \Cranebfs{} and \Cranegreedy{} across these
+experiments is only \SI{4}{\milli\second}. The runtimes of \Cranetwo{} have
+lower variation than those of \textsc{ForcLift} because with \textsc{ForcLift}
+we compile the formula anew for each domain size whereas with \Cranetwo{} we
+compile it once and reuse the resulting C++ program for all domain sizes.
+
+As another point of comparison, we examine the maximum domain size that the
+algorithms can handle in at most \SI{45}{\second} of total runtime. For
+bijection-counting, \textsc{FastWFOMC} scales up to domains of size 28, whereas
+\Cranebfs{} can handle domains of size \num{e4}. In the case of
+function-counting, \textsc{FastWFOMC} can handle domains of size 32, whereas
+\Cranebfs{} can handle \num{3e5}. On function-counting, \textsc{ForcLift} can
+handle domains sizes up to about 100, but then the finite-precision arithmetic
+declares higher model as infinite.
 
 \todo[inline,caption={}]{
-  Some reproducibility requirements to keep in mind:
-  \begin{itemize}
-    \item A motivation is given for why the experiments are conducted on the
-          selected datasets.
-    \item All novel datasets introduced in this paper are included in a data
-          appendix.
-    \item All datasets drawn from the existing literature (potentially including
-          authors’ own previously published work) are accompanied by appropriate
-          citations. (mention the counting quantifier paper and my KR paper)
-    \item All source code implementing new methods have comments detailing the
-          implementation, with references to the paper where each step comes
-          from.
-    \item This paper formally describes evaluation metrics used and explains the
-          motivation for choosing these metrics.
-    \item This paper states the number of algorithm runs used to compute each
-          reported result.
+  \begin{itemize}
+    \item Add info about \textsc{ForcLift} (taking care of infinities)
+    \item Turn the above paragraph into a table.
+    \item Mention two types of experiments earlier in the section.
   \end{itemize}
@@
   \begin{itemize}
-    \item Maybe add some complete examples of C++ programs in the supplementary
-          material.
     \item Later on:

### 2024-04-24 doc/plot.tex
The abstract

@@
-% Created by tikzDevice version 0.12.6 on 2024-04-12 11:27:55
+% Created by tikzDevice version 0.12.6 on 2024-04-23 11:24:49
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.66, 52.07) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.66, 54.53) --
+	( 37.66, 54.50) --
+	( 40.67, 54.50) --
+	( 43.67, 54.49) --
+	( 46.68, 54.49) --
+	( 49.68, 54.49) --
+	( 52.69, 54.49) --
+	( 55.70, 54.50) --
+	( 58.70, 54.50) --
+	( 61.71, 54.49) --
+	( 64.71, 54.49) --
+	( 67.72, 54.49) --
+	( 70.73, 54.49) --
+	( 73.73, 54.49) --
+	( 76.74, 54.50) --
+	( 79.74, 54.50) --
+	( 82.75, 54.50) --
+	( 85.75, 54.50) --
+	( 88.76, 54.49) --
+	( 91.77, 54.50) --
+	( 94.77, 54.50) --
+	( 97.78, 54.49) --
+	(100.78, 54.50) --
+	(103.79, 54.50) --
+	(106.80, 54.50) --
+	(109.80, 54.50) --
+	(112.81, 54.49) --
+	(115.81, 54.50) --
+	(118.82, 54.50) --
+	(121.82, 54.50) --
+	(124.83, 54.50) --
+	(127.84, 54.50) --
+	(130.84, 54.50) --
+	(133.85, 54.50) --
+	(136.85, 54.50);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.66, 52.07) --
 	( 37.66, 52.04) --
@@
 	(136.85, 52.04);
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.66, 54.53) --
-	( 37.66, 54.50) --
-	( 40.67, 54.50) --
-	( 43.67, 54.49) --
-	( 46.68, 54.49) --
-	( 49.68, 54.49) --
-	( 52.69, 54.49) --
-	( 55.70, 54.50) --
-	( 58.70, 54.50) --
-	( 61.71, 54.49) --
-	( 64.71, 54.49) --
-	( 67.72, 54.49) --
-	( 70.73, 54.49) --
-	( 73.73, 54.49) --
-	( 76.74, 54.50) --
-	( 79.74, 54.50) --
-	( 82.75, 54.50) --
-	( 85.75, 54.50) --
-	( 88.76, 54.49) --
-	( 91.77, 54.50) --
-	( 94.77, 54.50) --
-	( 97.78, 54.49) --
-	(100.78, 54.50) --
-	(103.79, 54.50) --
-	(106.80, 54.50) --
-	(109.80, 54.50) --
-	(112.81, 54.49) --
-	(115.81, 54.50) --
-	(118.82, 54.50) --
-	(121.82, 54.50) --
-	(124.83, 54.50) --
-	(127.84, 54.50) --
-	(130.84, 54.50) --
-	(133.85, 54.50) --
-	(136.85, 54.50);
 \definecolor{drawColor}{RGB}{217,95,2}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.66, 49.39) --
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.66, 49.39) --
 	( 37.66, 49.33) --
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.66, 29.90) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.66, 30.63) --
+	( 37.66, 30.63) --
+	( 40.67, 31.33) --
+	( 43.67, 31.33) --
+	( 46.68, 32.63) --
+	( 49.68, 33.82) --
+	( 52.69, 35.96) --
+	( 55.70, 37.83) --
+	( 58.70, 40.62) --
+	( 61.71, 43.28) --
+	( 64.71, 46.30) --
+	( 67.72, 50.22) --
+	( 70.73, 53.16) --
+	( 73.73, 57.14) --
+	( 76.74, 60.47) --
+	( 79.74, 64.05) --
+	( 82.75, 72.20) --
+	( 85.75, 71.34) --
+	( 88.76, 80.12) --
+	( 91.77, 80.67) --
+	( 94.77, 83.21) --
+	( 97.78, 89.74) --
+	(100.78, 87.61) --
+	(103.79, 96.04) --
+	(106.80, 98.47) --
+	(109.80, 99.99) --
+	(112.81,103.72) --
+	(115.81,103.27) --
+	(118.82,109.92) --
+	(121.82,111.85) --
+	(124.83,115.67) --
+	(127.84,116.78) --
+	(130.84,119.28) --
+	(133.85,123.20) --
+	(136.85,125.87);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.66, 29.90) --
 	( 37.66, 30.63) --
@@
 	(136.85,119.03);
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.66, 30.63) --
-	( 37.66, 30.63) --
-	( 40.67, 31.33) --
-	( 43.67, 31.33) --
-	( 46.68, 32.63) --
-	( 49.68, 33.82) --
-	( 52.69, 35.96) --
-	( 55.70, 37.83) --
-	( 58.70, 40.62) --
-	( 61.71, 43.28) --
-	( 64.71, 46.30) --
-	( 67.72, 50.22) --
-	( 70.73, 53.16) --
-	( 73.73, 57.14) --
-	( 76.74, 60.47) --
-	( 79.74, 64.05) --
-	( 82.75, 72.20) --
-	( 85.75, 71.34) --
-	( 88.76, 80.12) --
-	( 91.77, 80.67) --
-	( 94.77, 83.21) --
-	( 97.78, 89.74) --
-	(100.78, 87.61) --
-	(103.79, 96.04) --
-	(106.80, 98.47) --
-	(109.80, 99.99) --
-	(112.81,103.72) --
-	(115.81,103.27) --
-	(118.82,109.92) --
-	(121.82,111.85) --
-	(124.83,115.67) --
-	(127.84,116.78) --
-	(130.84,119.28) --
-	(133.85,123.20) --
-	(136.85,125.87);
 \definecolor{drawColor}{RGB}{231,41,138}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.66, 34.38) --
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.66, 34.38) --
 	( 37.66, 34.38) --
@@
 
-\path[fill=fillColor] (150.96,  8.58) rectangle (220.57, 58.93);
+\path[fill=fillColor] (150.96,  8.58) rectangle (208.75, 58.93);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (174.42, 32.28) {functions};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (174.42, 32.28) {bijections};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (174.42, 17.82) {permutations};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (174.42, 17.82) {functions};
 \end{scope}

### 2024-04-24 analysis/analyse.R

@@ -2,7 +2,7 @@ library(tidyverse)
 library(scales)
 library(tikzDevice)
 
-df <- read.csv("../results/processed/results.csv")
+df <- read.csv("../results/processed/results1.csv")
 df$compilation.time <- df$compilation.time / 1000
 df$inference.time <- df$inference.time / 1000
 df$time <- df$compilation.time + df$inference.time
@@ -10,7 +10,6 @@ df$algorithm[df$algorithm == "bfs"] <- "\\textsc{Crane2-BFS}"
 df$algorithm[df$algorithm == "greedy"] <- "\\textsc{Crane2-Greedy}"
 df$algorithm[df$algorithm == "forclift"] <- "\\textsc{ForcLift}"
 df$algorithm[df$algorithm == "fastwfomc"] <- "\\textsc{FastWFOMC}"
-df$sequence[df$sequence == "bijections"] <- "permutations"
 
 # Sanity check: differences between max and min counts as a percentage of the
 # min count

### 2024-04-24 build/forclift_wrapper.sh

@@ -1,6 +1,6 @@
 #!/usr/bin/env sh
 
-cd Forclift
+cd ../lib/Forclift
 for ((i=1; i<=$1; i++)); do
     echo "Domain size: $i"
     sed -i "s/\.\.\.,[[:digit:]]\+/\.\.\.,$i/g" $2

### 2024-04-24 doc/paper.tex
Section 6

@@
 
-\section{Experimental Evaluation (TODO)}
+\section{Experimental Evaluation}
 
@@
 formula in \FO{} or \Ctwo{} into \UFO{} (or even check if such an encoding is
-possible).
+possible). The experiments were run on an AMD~Ryzen~7~5800H processor with
+\SI{16}{\gibi\byte} of memory and Arch Linux~6.8.2-arch2-1 operating system.
+\textsc{FastWFOMC} was executed using Python~3.8.19 with Python-FLINT~0.5.0.
 
@@
 
-We run each of the four algorithms once on each combination of formula and
-domain size, the latter ranging from one up to and including 35. The experiments
-were run on an AMD~Ryzen~7~5800H processor with \SI{16}{\gibi\byte} of memory
-and Arch Linux~6.8.2-arch2-1 operating system. \textsc{FastWFOMC} was executed
-using Python~3.8.19 with Python-FLINT~0.5.0.
-
 \begin{figure}
@@
 
-\Cref{fig:plot} shows total runtime values as a measure of the overall
-performance of each algorithm. For the three knowledge compilation algorithms,
-we also separately track compilation and inference times and comment on them
-where relevant. Note that \Cranebfs{} is able to handle more instances than
-either \textsc{ForcLift} or \Cranegreedy{}, i.e., the bijection-counting problem
-in our experiments as well as similar formulas examined
+In the first experiment, we run each of the four algorithms once on each
+combination of benchmark and domain size, the latter ranging from one up to and
+including 35. \Cref{fig:plot} shows total runtime values as a measure of the
+overall performance of each algorithm. For the three knowledge compilation
+algorithms, we also separately track compilation and inference times and comment
+on them where relevant. Note that \Cranebfs{} is able to handle more instances
+than either \textsc{ForcLift} or \Cranegreedy{}, i.e., the bijection-counting
+problem in our experiments as well as similar formulas examined
 previously~\cite{DBLP:conf/kr/DilkasB23}.
 
-As shown in the figure, the runtimes of all compilation-based algorithms remain
-practically constant in contrast to the rapidly increasing runtimes of
+As shown in \cref{fig:plot}, the runtimes of all compilation-based algorithms
+remain practically constant in contrast to the rapidly increasing runtimes of
 \textsc{FastWFOMC}. Although the search/compilation part is slower in
@@
 
-As another point of comparison, we examine the maximum domain size that the
-algorithms can handle in at most \SI{45}{\second} of total runtime. For
-bijection-counting, \textsc{FastWFOMC} scales up to domains of size 28, whereas
-\Cranebfs{} can handle domains of size \num{e4}. In the case of
-function-counting, \textsc{FastWFOMC} can handle domains of size 32, whereas
-\Cranebfs{} can handle \num{3e5}. On function-counting, \textsc{ForcLift} can
-handle domains sizes up to about 100, but then the finite-precision arithmetic
-declares higher model as infinite.
-
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item Add info about \textsc{ForcLift} (taking care of infinities)
-    \item Turn the above paragraph into a table.
-    \item Mention two types of experiments earlier in the section.
-  \end{itemize}
-}
+\begin{table}
+  \centering
+  \begin{tabular}{lrr}
+    \toprule
+    Algorithm & Bijections & Functions \\
+    \midrule
+    \Cranebfs{} & \num{e4} & \num{3e5} \\
+    \Cranegreedy{} & --- & \num{3e5} \\
+    \textsc{FastWFOMC} & 28 & 32 \\
+    \textsc{ForcLift} & --- & 143 \\
+    \bottomrule
+  \end{tabular}
+  \caption{The maximum domain sizes that can be handled by each algorithm in at
+    most \SI{45}{\second}. `---' indicates that the algorithm is unable to find
+    a solution. The domain sizes for \Cranetwo{} are accurate up to the first
+    digit while other domain sizes are exact.}\label{table:results}
+\end{table}
+
+For the second experiment, we examine the maximum domain size that the
+algorithms can handle in at most \SI{45}{\second} of total runtime. As shown in
+\cref{table:results}, \Cranebfs{} is able to scale to domain sizes \num{357} and
+\num{9375} times larger than \textsc{FastWFOMC} for bijection-counting and
+function-counting problems, respectively. Note that, while \textsc{ForcLift} may
+have runtime performance comparable to \Cranetwo{}, its finite-precision
+arithmetic cannot represent model counts for domain sizes higher than 143 and
+returns $\infty$ instead.
 
@@
             \item re-check submission instructions and formatting guidelines
-            \item Full stop at the end of a single-sentence caption?
             \item cite the \textsc{Crane} paper (and other algorithms' papers)
                   where necessary
-            \item Something to think about that could inspire some kind of
-                  theorems: how can I assume that a domain is empty if there are
-                  constants associated with it?
-            \item consider turning small sections (e.g., Section 5) into
-                  subsections of even paragraphs.
-            \item Authors may submit a separate PDF with additional information
-                  supporting their claims (such as proof details, additional
-                  experimental results, further details on experimental design,
-                  etc).
           \end{itemize}

### 2024-04-25 doc/paper.tex
Section 2.2

@@
 \newtheorem{example}{Example}
+\theoremstyle{remark}
+\newtheorem*{remark}{Remark}
 
@@
   the algorithm did not include base cases in the recursive definitions. This
-  work makes three contributions. Firstly, we demonstrate how to construct
+  work makes three contributions. First, we demonstrate how to construct
   function definitions that include base cases by modifying the logical formulas
-  used in the FOMC algorithm. Secondly, we extend the well-known circuit
+  used in the FOMC algorithm. Second, we extend the well-known circuit
   modification technique in knowledge compilation, known as smoothing, to work
   with the formulas corresponding to base cases and the recently proposed node
-  types, such as domain recursion and constraint removal. Thirdly, we introduce
-  a compilation algorithm that transforms the function definitions into C++
-  code, equipped with arbitrary-precision arithmetic. These additions allow the
-  new FOMC algorithm to scale to domain sizes over \num{9000} times larger than
-  the current state of the art, as demonstrated through experimental results.
+  types, such as domain recursion and constraint removal. Third, we introduce a
+  compilation algorithm that transforms the function definitions into C++ code,
+  equipped with arbitrary-precision arithmetic. These additions allow the new
+  FOMC algorithm to scale to domain sizes over \num{9000} times larger than the
+  current state of the art, as demonstrated through experimental results.
 \end{abstract}
@@
           \end{itemize}
+    \item introduce \Cranetwo{}
+    \item (maybe) introduce lifted/liftable
   \end{itemize}
@@
 
-\subsection{Logic (TODO)}\label{sec:logic}
+\todo[inline]{There are three subsections now, not two.}
+
+\subsection{First-Order Logic and WFOMC (TODO)}\label{sec:logic}
 
@@
 \begin{definition}[Model]\label{def:model}
-  Let $\phi$ be a formula in \FO{}. For every predicate $p/n$ in $\phi$, let
-  ${(\Delta_{i}^{p})}_{i=1}^{n}$ be a list of the corresponding domains (not
+  Let $\phi$ be a formula in \FO{}. For every predicate $P/n$ in $\phi$, let
+  ${(\Delta_{i}^{P})}_{i=1}^{n}$ be a list of the corresponding domains (not
   necessarily distinct). Let $\sigma$ be a map from the domains of $\phi$ to
   their interpretations as sets such that:
-  \begin{itemize}
+  \begin{enumerate*}[label=(\roman*)]
     \item the sets are pairwise disjoint, and
     \item the constants in $\phi$ are included in the corresponding domains.
-  \end{itemize}
+  \end{enumerate*}
   Then a \emph{structure} of $\phi$ (with respect to $\sigma$) is a set $M$ of
-  ground literals defined by adding either $p(\mathbf{t})$ or
-  $\neg p(\mathbf{t})$ for every predicate $p/n$ in $\phi$ and $n$-tuple
-  $\mathbf{t} \in \prod_{i=1}^{n} \sigma(\Delta_{i}^{p})$. A structure is a
+  ground literals defined by adding either $P(\mathbf{t})$ or
+  $\neg P(\mathbf{t})$ for every predicate $P/n$ in $\phi$ and $n$-tuple
+  $\mathbf{t} \in \prod_{i=1}^{n} \sigma(\Delta_{i}^{P})$. A structure is a
   \emph{model} if it satisfies $\phi$ (see Appendix~A of~Dilkas and
@@
 \begin{definition}[WFOMC]
-  Continuing from \cref{def:model}, for every predicate $p/n$ in $\phi$, let
-  $w^{+}(p), w^{-}(p) \in \mathbb{R}$ be its (positive and negative)
-  \emph{weights}. Unless explicitly specified otherwise, we assume weights to be
-  equal to one. The \emph{(symmetric) weighted first-order model count} (WFOMC)
-  of $\phi$ (with respect to $\sigma$, $w^{+}$, and $w^{-}$) is the quantity
+  Continuing from \cref{def:model}, for every predicate $P/n$ in $\phi$, let
+  $w^{+}(P), w^{-}(P) \in \mathbb{R}$ be its (positive and negative)
+  \emph{weights}. Unless specified otherwise, we assume weights to be equal to
+  one. The \emph{(symmetric) weighted first-order model count} (WFOMC) of $\phi$
+  (with respect to $\sigma$, $w^{+}$, and $w^{-}$) is the quantity
   \[
-    \sum_{M \models \phi} \prod_{p(\mathbf{t}) \in M} w^{+}(p) \prod_{\neg p(\mathbf{t}) \in M} w^{-}(p),
+    \sum_{M \models \phi} \prod_{P(\mathbf{t}) \in M} w^{+}(P) \prod_{\neg P(\mathbf{t}) \in M} w^{-}(P),
   \]
@@
 \end{definition}
+
+\subsection{WFOMC Algorithms and Their Logics}\label{sec:threelogics}
 
@@
 
-\paragraph{Three Types of Logics}
-\begin{itemize}
-  \item See \cref{tbl:logics} for a detailed comparison. The notation introduced
-        in the table is standard for \Ctwo{}, new for \UFO{}, and redefined to
-        be more specific for \FO{}.
-  \item All three logics are function-free.
-  \item Domains are always assumed to be finite.
-  \item In many-sorted logic, each term is assigned to a \emph{sort}, and each
-        predicate $p/n$ is assigned to a sequence of $n$ sorts. Each sort has
-        its corresponding domain. In the input formula, all domains are assumed
-        to be pairwise disjoint Most of these assignments are typically left
-        implicit and can be reconstructed from the quantifiers. For instance,
-        $\forall x,y \in \Delta\text{. }P(x, y)$ implies that variables $x$ and
-        $y$ have the same sort. On the other hand, $\forall x \in \Delta\text{.
-        }\forall y \in \Gamma\text{. } P(x, y)$ implies that $x$ and $y$ have
-        different sorts, and it would be improper to have $x = y$ as part of a
-        formula.
-  \item
-        \begin{itemize}
-          \item \FO{} is used as the input format for
-                \textsc{ForcLift}\footnote{\url{https://github.com/UCLA-StarAI/Forclift}}~\cite{DBLP:conf/ijcai/BroeckTMDR11}
-                and its extensions
-                \textsc{Crane}\footnote{\url{https://doi.org/10.5281/zenodo.8004077}}~\cite{DBLP:conf/kr/DilkasB23}
-                and \Cranetwo{}.
-          \item \Ctwo{} is discussed in the literature on
-                \textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21} and related
-                methods~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}
-          \item \UFO{} is the input format supported by a version of
-                \textsc{FastWFOMC} obtained directly from the authors. Note that
-                the publicly available
+In \cref{tbl:logics}, we outline the differences among three first-order logics
+commonly used in WFOMC:
+\begin{enumerate*}[label=(\roman*)]
+  \item \FO{} is the input format for
+  \textsc{ForcLift}\footnote{\url{https://github.com/UCLA-StarAI/Forclift}} and
+  its extensions
+  \textsc{Crane}\footnote{\url{https://doi.org/10.5281/zenodo.8004077}} and
+  \Cranetwo{},
+  \item \Ctwo{} is often used in the literature on \textsc{FastWFOMC} and
+  related
+  methods~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}, and
+  \item \UFO{} is the input format supported by a private version of
+  \textsc{FastWFOMC} obtained directly from the authors.
+\end{enumerate*}
+Note that the publicly available
 version\footnote{\url{https://comp.nus.edu.sg/~tvanbr/software/fastwfomc.tar.gz}}
-                does not support any cardinality constraints.
-        \end{itemize}
-  \item Note that, in the case of \textsc{ForcLift} and its extensions, support
-        for a formula as valid input does not imply that the algorithm will be
-        able to compile the formula into a circuit or graph suitable for lifted
-        model counting. However, it is known that \textsc{ForcLift} compilation
-        is guaranteed to succeed on any \FO{} formula without constants and with
-        at most two variables~\cite{DBLP:conf/nips/Broeck11}.
-\end{itemize}
-
-\begin{example}\label{example:functions}
-  Functions
-  \begin{itemize}
-    \item In \Ctwo: $\forall x \in \Delta\text{.
-          }\exists^{=1} y \in \Delta\text{. }P(x, y)$
-    \item In \UFO:
-          \begin{gather*}
+does not support any cardinality constraints. The notation we use to refer to
+each logic is standard in the case of \Ctwo{}, new in the case of \UFO{}, and
+redefined to be more specific in the case of \FO{}. All three logics are
+function-free, and domains are always assumed to be finite.
+
+In \FO{}, each term is assigned to a \emph{sort}, and each predicate $P/n$ is
+assigned to a sequence of $n$ sorts. Each sort has its corresponding domain.
+Most of these assignments to sorts are typically left implicit and can be
+reconstructed from the quantifiers. For example, $\forall x,y \in \Delta\text{.
+}P(x, y)$ implies that variables $x$ and $y$ have the same sort. On the other
+hand, $\forall x \in \Delta\text{. }\forall y \in \Gamma\text{. } P(x, y)$
+implies that $x$ and $y$ have different sorts, and it would be improper to
+write, e.g., $\forall x \in \Delta\text{. }\forall y \in \Gamma\text{.
+} P(x, y) \lor x = y$. \FO{} is also the only logic to support constants,
+clauses with more than two variables, and the equality predicate.
+
+\begin{remark}
+  In the case of \textsc{ForcLift} and its extensions, support for a formula as
+  valid input does not imply that the algorithm will be able to compile the
+  formula into a circuit or graph suitable for lifted model counting. However,
+  it is known that \textsc{ForcLift} compilation is guaranteed to succeed on any
+  \FO{} formula without constants and with at most two
+  variables~\cite{DBLP:conf/nips/Broeck11}.
+\end{remark}
+
+Both \Ctwo{} and \UFO{} are single-sorted (i.e., variables are always quantified
+over the same domain) and only include formulas with at most two variables and
+no constants. Unlike \UFO{}, \Ctwo{} supports existential quantifiers, including
+\emph{counting quantifiers}. For example, $\exists^{=1} x\text{. }\phi(x)$ means
+that there exists \emph{exactly one} $x$ such that $\phi(x)$, and
+$\exists^{\le 2} x\text{. }\phi(x)$ means that there exist \emph{at most two}
+such $x$. The advantage \UFO{} brings over \Ctwo{} is the support for
+\emph{(equality) cardinality constraints}. For example, $|P| = 3$ constrains all
+models to have \emph{exactly three positive literals with predicate $P$}. We
+further illustrate the differences among the three logics with the example
+below.
+
+\begin{example}[Functions]\label{example:functions}
+  To define predicate $P$ to be an endofunction on $\Delta$, in \Ctwo{} one
+  could write $\forall x \in \Delta\text{. }\exists^{=1} y \in \Delta\text{.
+  }P(x, y)$. In \UFO{}, the same could be written as
+  \begin{equation}\label[formula]{eq:functions1}
+    \begin{gathered}
       \forall x, y \in \Delta\text{. }S(x) \lor \neg P(x, y)\\
-            |P| = |\Delta|
-          \end{gather*}
-    \item In \FO:
+      |P| = |\Delta|.
+    \end{gathered}
+  \end{equation}
+  Although \cref{eq:functions1} has some additional models, the negative weight
+  $w^{-}(S) = -1$ makes some of the counts cancel out so that the WFOMC of
+  \cref{eq:functions1} is still equal to the number of endofunctions on
+  $\Delta$.
+
+  In \FO{}, we would write
   \begin{equation}\label[formula]{eq:fo}
@@
       \forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }P(x, y)\\
-        \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z
+      \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z,
     \end{gathered}
   \end{equation}
-  \end{itemize}
-
-  Note that \cref{eq:fo} is written with two domains instead of one. Clearly,
-  the model count does not change whenever $|\Gamma| = |\Delta|$. As was
-  previously observed by Dilkas and Belle~\shortcite{DBLP:conf/kr/DilkasB23},
-  such a reformulation can help first-order knowledge compilation algorithms
-  find efficient solutions.
+  first stating that each $x$ must be mapped to at least one $y$ and then adding
+  that if $x$ is mapped to both $y$ and $z$, then $y=z$. Note that \cref{eq:fo}
+  is written with two domains instead of one. Clearly, one can still count the
+  number of endofunctions by setting $|\Gamma| = |\Delta|$. As was previously
+  observed by Dilkas and Belle~\shortcite{DBLP:conf/kr/DilkasB23}, such a
+  reformulation can help first-order knowledge compilation algorithms find
+  efficient solutions.
 \end{example}
@@
 
-\clearpage % TODO: temporarary
-
 \bibliographystyle{kr}

### 2024-04-25 doc/paper.tex
The rest of Section 2

@@
 
-\Cref{sec:logic} introduces the fundamental ideas of first-order logic and
-WFOMC, and discusses the different logics used in the latter.\@ Then,
-\cref{sec:algebra} introduces the terminology we use to describe the output of
-the original \textsc{Crane} algorithm~\cite{DBLP:conf/kr/DilkasB23}, i.e.,
-functions and equations that define them.
+In \cref{sec:logic}, we summarise the fundamentals of first-order logic. Then,
+in \cref{sec:threelogics}, we formally define WFOMC and discuss the differences
+among three variants of first-order logic used for WFOMC.\@ Finally, in
+\cref{sec:algebra}, we introduce the terminology used to describe the output of
+the original \textsc{Crane} algorithm, i.e., functions and equations that define
+them.
 
@@
 
-\todo[inline]{There are three subsections now, not two.}
-
-\subsection{First-Order Logic and WFOMC (TODO)}\label{sec:logic}
-
-\todo[inline]{Clarify the differences between the input format and the internal
-  format}
-
-\paragraph{The \FO{} Logic (After Skolemization and in a special (prenex, CNF)
-  form)}
-\begin{itemize}
-  \item Although existential quantifiers are supported, here we describe the
-        format used internally. During preprocessing, all existential
-        quantifiers are eliminated using
-        Skolemization~\cite{DBLP:conf/kr/BroeckMD14}, and the formula is
-        rewritten into a conjunction of clauses, each of which is in
-        \emph{prenex normal form}~\cite{hinman2018fundamentals}.
-  \item In the spirit of keeping sorts implicit, we always assume formulas `type
-        check' with respect to sorts. For example, if $P(x)$, $P(y)$, and
-        $x \ne c$ are all part of the formula (for some predicate $P$, variables
-        $x$ and $y$, and constant $c$), then $x$, $y$, and $c$ all have the same
-        sort.
-  \item A \emph{formula} is a conjunction of clauses.
-  \item A \emph{clause} is of the form $\forall x_{1} \in \Delta_{1}\text{.
-        }\forall x_{2} \in \Delta_{2}\dots\text{
-        }\forall x_{n} \in \Delta_{n}\text{. }\phi(x_{1}, x_{2}, \dots, x_{n})$,
-        where $\phi$ is a disjunction of literals that only contain variables
-        $x_{1}, \dots, x_{n}$ (and any constants).
-  \item We say that a clause is a \emph{(positive) unit clause} if:
-        \begin{itemize}
+\subsection{First-Order Logic}\label{sec:logic}
+
+In this section, we review the basic concepts of first-order logic as they are
+used in first-order knowledge compilation algorithms. There are two key
+differences between the logic used within such algorithms and the logic
+supported as input. First, Skolemization~\cite{DBLP:conf/kr/BroeckMD14} is used
+to eliminate existential quantifiers by introducing additional predicates (some
+of which have negative weights). Second, the input formula is rewritten as a
+conjunction of clauses, each of which is in \emph{prenex normal
+  form}~\cite{hinman2018fundamentals}.
+
+A \emph{formula} is a conjunction of clauses. A \emph{clause} is of the form
+$\forall x_{1} \in \Delta_{1}\text{.}\forall x_{2} \in \Delta_{2}\dots\text{
+}\forall x_{n} \in \Delta_{n}\text{.}\phi(x_{1}, x_{2}, \dots, x_{n})$, where
+$\phi$ is a disjunction of literals that only contain variables
+$x_{1}, \dots, x_{n}$ (and any constants). We say that a clause is a
+\emph{(positive) unit clause} if
+\begin{enumerate*}[label=(\roman*)]
   \item there is only one literal with a predicate, and
   \item it is a positive literal.
-        \end{itemize}
-  \item A \emph{literal} is either an atom (i.e., a \emph{positive} literal) or
-        its negation (i.e., a \emph{negative} literal).
-  \item An \emph{atom} is either:
-  \begin{itemize}
-    \item $P(t_{1}, \dots, t_{m})$ for some predicate $P/m$ and terms
-          $t_{1}, \dots, t_{m}$ or
-    \item $x=y$ for some terms $x$ and $y$
-  \end{itemize}
-  \item An atom is \emph{ground} if it contains no variables (i.e., only
-        constants).
-  \item The \emph{arity} of a predicate is the number of arguments it takes,
-        i.e., $m$ in the case of predicate $P$.
-  \item When we want to denote a predicate together with its arity, we write
-        $P/m$.
-  \item A \emph{term} is either a variable or a constant.
-  \item Throughout the paper, we use set-theoretic notation, interpreting a
-        formula as a set of clauses and a clause as a set of literals. Moreover,
-        for readability, clauses written on separate lines are implicitly
-        conjoined.
-\end{itemize}
-
-\begin{definition}[Model]\label{def:model}
-  Let $\phi$ be a formula in \FO{}. For every predicate $P/n$ in $\phi$, let
-  ${(\Delta_{i}^{P})}_{i=1}^{n}$ be a list of the corresponding domains (not
-  necessarily distinct). Let $\sigma$ be a map from the domains of $\phi$ to
-  their interpretations as sets such that:
+\end{enumerate*}
+A \emph{literal} is either an atom (i.e., a \emph{positive} literal) or its
+negation (i.e., a \emph{negative} literal). An \emph{atom} is either
 \begin{enumerate*}[label=(\roman*)]
-    \item the sets are pairwise disjoint, and
-    \item the constants in $\phi$ are included in the corresponding domains.
-  \end{enumerate*}
-  Then a \emph{structure} of $\phi$ (with respect to $\sigma$) is a set $M$ of
-  ground literals defined by adding either $P(\mathbf{t})$ or
-  $\neg P(\mathbf{t})$ for every predicate $P/n$ in $\phi$ and $n$-tuple
-  $\mathbf{t} \in \prod_{i=1}^{n} \sigma(\Delta_{i}^{P})$. A structure is a
-  \emph{model} if it satisfies $\phi$ (see Appendix~A of~Dilkas and
-  Belle~\shortcite{DBLP:journals/corr/abs-2306-04189} for more details).
-\end{definition}
-
-\begin{definition}[WFOMC]
-  Continuing from \cref{def:model}, for every predicate $P/n$ in $\phi$, let
-  $w^{+}(P), w^{-}(P) \in \mathbb{R}$ be its (positive and negative)
-  \emph{weights}. Unless specified otherwise, we assume weights to be equal to
-  one. The \emph{(symmetric) weighted first-order model count} (WFOMC) of $\phi$
-  (with respect to $\sigma$, $w^{+}$, and $w^{-}$) is the quantity
-  \[
-    \sum_{M \models \phi} \prod_{P(\mathbf{t}) \in M} w^{+}(P) \prod_{\neg P(\mathbf{t}) \in M} w^{-}(P),
-  \]
-  where the sum is over all models of $\phi$.
-\end{definition}
+  \item $P(t_{1}, \dots, t_{m})$ for some predicate $P$ and terms
+  $t_{1}, \dots, t_{m}$ (written $P(\mathbf{t})$ for short) or
+  \item $x=y$ for some terms $x$ and $y$.
+\end{enumerate*}
+An atom is \emph{ground} if it contains no variables, i.e., only constants. The
+\emph{arity} of a predicate is the number of arguments it takes, i.e., $m$ in
+the case of predicate $P$ above. When we want to denote a predicate together
+with its arity, we write $P/m$. A \emph{term} is either a variable or a
+constant. Throughout the paper, we use set-theoretic notation, interpreting a
+formula as a set of clauses and a clause as a set of literals. Moreover, for
+readability, clauses written on separate lines are implicitly conjoined.
 
@@
       \item the maximum number of variables,
-      \item allowed quantifiers, and
+      \item supported quantifiers, and
       \item supported atoms in addition to those of the form $P(\mathbf{t})$ for some predicate $P/n$ and $n$-tuple of terms $\mathbf{t}$.
@@
 } P(x, y) \lor x = y$. \FO{} is also the only logic to support constants,
-clauses with more than two variables, and the equality predicate.
+formulas with more than two variables, and the equality predicate.
 
@@
   In the case of \textsc{ForcLift} and its extensions, support for a formula as
-  valid input does not imply that the algorithm will be able to compile the
-  formula into a circuit or graph suitable for lifted model counting. However,
-  it is known that \textsc{ForcLift} compilation is guaranteed to succeed on any
-  \FO{} formula without constants and with at most two
+  valid input does not imply that the algorithm can compile the formula into a
+  circuit or graph suitable for lifted model counting. However, it is known that
+  \textsc{ForcLift} compilation is guaranteed to succeed on any \FO{} formula
+  without constants and with at most two
   variables~\cite{DBLP:conf/nips/Broeck11}.
@@
 \emph{(equality) cardinality constraints}. For example, $|P| = 3$ constrains all
-models to have \emph{exactly three positive literals with predicate $P$}. We
-further illustrate the differences among the three logics with the example
-below.
-
-\begin{example}[Functions]\label{example:functions}
-  To define predicate $P$ to be an endofunction on $\Delta$, in \Ctwo{} one
-  could write $\forall x \in \Delta\text{. }\exists^{=1} y \in \Delta\text{.
+models to have \emph{exactly three positive literals with predicate $P$}.
+
+\begin{definition}[Model]\label{def:model}
+  Let $\phi$ be a formula in \FO{}. For every predicate $P/n$ in $\phi$, let
+  ${(\Delta_{i}^{P})}_{i=1}^{n}$ be a list of the corresponding domains (not
+  necessarily distinct). Let $\sigma$ be a map from the domains of $\phi$ to
+  their interpretations as sets such that:
+  \begin{enumerate*}[label=(\roman*)]
+    \item the sets are pairwise disjoint, and
+    \item the constants in $\phi$ are included in the corresponding domains.
+  \end{enumerate*}
+  Then a \emph{structure} of $\phi$ (with respect to $\sigma$) is a set $M$ of
+  ground literals defined by adding either $P(\mathbf{t})$ or
+  $\neg P(\mathbf{t})$ for every predicate $P/n$ in $\phi$ and $n$-tuple
+  $\mathbf{t} \in \prod_{i=1}^{n} \sigma(\Delta_{i}^{P})$. A structure is a
+  \emph{model} if it satisfies $\phi$ (see Appendix~A of~Dilkas and
+  Belle~\shortcite{DBLP:journals/corr/abs-2306-04189} for more details).
+\end{definition}
+
+\begin{definition}[WFOMC~\cite{DBLP:conf/ijcai/BroeckTMDR11}]
+  Continuing from \cref{def:model}, for every predicate $P$ in $\phi$, let
+  $w^{+}(P), w^{-}(P) \in \mathbb{Q}$ be its \emph{weights}. Unless specified
+  otherwise, we assume weights to be equal to one. The \emph{(symmetric)
+    weighted first-order model count} (WFOMC) of $\phi$ (with respect to
+  $\sigma$, $w^{+}$, and $w^{-}$) is
+  \[
+    \sum_{M \models \phi} \prod_{P(\mathbf{t}) \in M} w^{+}(P) \prod_{\neg P(\mathbf{t}) \in M} w^{-}(P),
+  \]
+  where the sum is over all models of $\phi$.
+\end{definition}
+
+\begin{example}[Counting functions]\label{example:functions}
+  To define predicate $P$ as an endofunction on $\Delta$, in \Ctwo{} one would
+  write $\forall x \in \Delta\text{. }\exists^{=1} y \in \Delta\text{.
   }P(x, y)$. In \UFO{}, the same could be written as
@@
       \forall x, y \in \Delta\text{. }S(x) \lor \neg P(x, y)\\
-      |P| = |\Delta|.
+      |P| = |\Delta|,
     \end{gathered}
   \end{equation}
-  Although \cref{eq:functions1} has some additional models, the negative weight
-  $w^{-}(S) = -1$ makes some of the counts cancel out so that the WFOMC of
-  \cref{eq:functions1} is still equal to the number of endofunctions on
-  $\Delta$.
-
-  In \FO{}, we would write
+  where $w^{-}(S) = -1$. Although \cref{eq:functions1} has more models compared
+  to its counterpart in \Ctwo{}, the weight function makes it so the
+  \emph{weighted} model count of \cref{eq:functions1} is still equal to the
+  number of endofunctions on $\Delta$.
+
+  Equivalently, in \FO{} we would write
   \begin{equation}\label[formula]{eq:fo}
@@
 
-We write $\expr{}$ for an arbitrary algebraic expression. Note that some terms
-have different meanings in the context of algebra as compared to logic. Here, a
+We write $\expr{}$ for an arbitrary algebraic expression. Some terms have
+different meanings in the context of algebra compared to logic. Here, a
 \emph{constant} is a non-negative integer. Similarly, a \emph{variable} is

### 2024-04-26 doc/paper.tex
Most of the introduction

@@
 \creflabelformat{type}{#2\textup{#1}#3}
+
+\crefalias{enumi}{step}
+\crefname{step}{Step}{Steps}
+\creflabelformat{step}{#2\textup{#1}#3}
 
@@
 
+% 1. What is the problem?
+
+\emph{First-order model counting} is the problem of counting the number of
+models of a sentence in first-order logic over some given domain(s). The
+(symmetric) weighted variant of the problem (WFOMC) asks for the sum of model
+weights instead, where the weight of a model is a product over predicate
+weights~\cite{DBLP:conf/ijcai/BroeckTMDR11}. WFOMC is a prominent approach to
+the broader problem known as \emph{lifted (probabilistic) inference} that aims
+to compute probabilities more efficiently by utlilising symmetries inherent in
+the description of the problem~\cite{DBLP:conf/ecai/Kersting12}.
+
+% 2. Why is it interesting and important?
+
+Lifted inference is an active area of research with recent work in domains such
+as constraint satisfaction problems~\cite{DBLP:journals/jair/TotisDRK23} and
+probabilistic answer set programming~\cite{DBLP:journals/ijar/AzzoliniR23}.
+WFOMC itself has been used to perform inference on probabilistic
+databases~\cite{DBLP:journals/debu/GribkoffSB14} and probabilistic logic
+programs~\cite{DBLP:journals/ijar/RiguzziBZCL17}. By iteratively considering
+domains of increasing sizes, the model count of a formula can be interpreted as
+an (integer) sequence. WFOMC algorithms have been used to discover new
+sequences~\cite{DBLP:conf/ijcai/SvatosJT0K23} and
+conjecture~\cite{DBLP:conf/ilp/BarvinekB0ZK21} and
+construct~\cite{DBLP:conf/kr/DilkasB23} recurrence relations and other recursive
+constructs that describe these sequences. Recently, WFOMC algorithms have also
+been extended and applied to perform
+\emph{sampling}~\cite{DBLP:conf/aaai/WangB0K22,DBLP:conf/lics/WangP0K23}.
+
+% 3. Why is it hard? (E.g., why do naive approaches fail?)
+
+The complexity of WFOMC is typically characterised in terms of \emph{data
+  complexity}, i.e., fixing the formula and asking whether there exists an
+algorithm that can compute the WFOMC in time polynomial in the domain size(s).
+If such an algorithm exists, the formula is called
+\emph{liftable}~\cite{DBLP:conf/starai/JaegerB12}. Beame et
+al.~\shortcite{DBLP:conf/pods/BeameBGS15} showed that there exists an unliftable
+formula with three variables. It is also known that all formulas with up to two
+variables are liftable~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/kr/BroeckMD14}.
+This liftable fragment of formulas with two variables has been extended with
+various axioms~\cite{DBLP:conf/aaai/TothK23,DBLP:journals/ai/BremenK23},
+counting quantifiers~\cite{DBLP:journals/jair/Kuzelka21}, and in other
+ways~\cite{DBLP:conf/nips/KazemiKBP16}.
+
+% 4. Why hasn't it been solved before? (Or, what's wrong with previous proposed
+% solutions? How does mine differ?)
+
+There is a variety of WFOMC algorithms with different underlying principles.
+Perhaps the most prominent class of WFOMC algorithms is based on
+\emph{first-order knowledge compilation}. Here, by iteratively applying
+\emph{compilation rules}, the formula is compiled to a representation (such as a
+circuit of graph), which can then be used to compute the WFOMC for any
+combination of domain sizes (or weights). Algorithms in this class include
+\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} and its recent extension
+\textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23}. The former compiles formulas into
+circuits whereas the latter compiles them first to \emph{first-order
+  computational graphs} (FCGs) and then to (algebraic) equations. Another major
+WFOMC algorithm \textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21} is based on
+cell enumeration. Other algorithms employ local
+search~\cite{DBLP:journals/pvldb/NiuRDS11}, junction
+trees~\cite{DBLP:conf/aaai/VenugopalSG15}, Monte Carlo
+sampling~\cite{DBLP:journals/cacm/GogateD16}, and anytime approximation via
+upper/lower bound construction~\cite{DBLP:conf/ijcai/BremenK20}.
+
+% 5. What are the key components of my approach and results? Also include any
+% specific limitations.
+
+The recently-proposed \textsc{Crane} algorithm, while able to handle formulas
+beyond the reach of \textsc{ForcLift}, was somewhat incomplete in that it could
+only construct functions definitions, which would then need to be evaluated to
+compute the WFOMC.\@ Moreover, recursive functions were presented without base
+cases. In this work, we present \Cranetwo{}---an extension of \textsc{Crane}
+that fixes these two weaknesses.
+
 \todo[inline,caption={}]{
   \begin{itemize}
-    \item 9 pages including appendices but not acknowledgements
-    \item Add some papers mentioned in:
-          \begin{itemize}
-            \item very recent work
-            \item my previous paper, including:
-                  \begin{itemize}
-                    \item other liftable fragments
-                    \item some more theory papers, e.g., LICS 2018
+  \item Finish the paragraph above.
+  \item mention that \textsc{L2C}~\cite{DBLP:conf/kr/KazemiP16} compiles to C++
   \end{itemize}
-          \end{itemize}
-    \item introduce \Cranetwo{}
-    \item (maybe) introduce lifted/liftable
-  \end{itemize}
-}
-
-\paragraph{Papers To Cite}
-\begin{itemize}
-  \item overviews
-        \begin{itemize}
-          \item lifted probabilistic inference~\cite{DBLP:conf/ecai/Kersting12}
-          \item recent overview paper~\cite{DBLP:conf/ijcai/Kuzelka23}
-        \end{itemize}
-  \item Alternative definition~\cite{DBLP:journals/cacm/GogateD16}
-  \item relevant theoretical work~\cite{DBLP:conf/aaai/MalhotraS22}
-  \item original domain recursion~\cite{DBLP:conf/nips/Broeck11}
-  \item algorithms
-        \begin{itemize}
-          \item \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11}
-          \item \textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23}
-          \item \textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21}
-          \item \textsc{L2C}~\cite{DBLP:conf/kr/KazemiP16} (similarly to us
-                compiles to C++ code, but (probably) doesn't work on as many
-                formulas)
-          \item approximate~\cite{DBLP:conf/ijcai/BremenK20}
-          \item for Markov logic networks~\cite{DBLP:journals/ml/RichardsonD06}
-                \begin{itemize}
-                  \item \textsc{Magician}~\cite{DBLP:conf/aaai/VenugopalSG15}
-                  \item \textsc{Tuffy}~\cite{DBLP:journals/pvldb/NiuRDS11}
-                  \item \textsc{Alchemy}~\cite{DBLP:journals/cacm/GogateD16}
-                        (same as the alternative definition)
-                \end{itemize}
-        \end{itemize}
-  \item complexity
-        \begin{itemize}
-          \item liftability~\cite{DBLP:conf/starai/JaegerB12}
-          \item hardness for three variables~\cite{DBLP:conf/pods/BeameBGS15}
-          \item liftable fragments
-                \begin{itemize}
-                  \item \Ctwo~\cite{DBLP:journals/jair/Kuzelka21}
-                  \item tree axioms~\cite{DBLP:journals/ai/BremenK23}
-                  \item linear order axioms~\cite{DBLP:conf/aaai/TothK23}
-                  \item some liftable fragments~\cite{DBLP:conf/nips/KazemiKBP16}
-                \end{itemize}
-        \end{itemize}
-  \item applications
-        \begin{itemize}
-          \item extensions to
-                sampling~\cite{DBLP:conf/aaai/WangB0K22,DBLP:conf/lics/WangP0K23}
-          \item discovery of combinatorial
-                sequences~\cite{DBLP:conf/ijcai/SvatosJT0K23}
-          \item conjecturing recurrence
-                relations~\cite{DBLP:conf/ilp/BarvinekB0ZK21}
-          \item probabilistic logic
-                programming~\cite{DBLP:journals/ijar/RiguzziBZCL17} (WFOMC was
-                shown to be supreme)
-          \item probabilistic databases~\cite{DBLP:journals/debu/GribkoffSB14}
-        \end{itemize}
-  \item lifted inference elsewhere
-        \begin{itemize}
-          \item constraint satisfaction~\cite{DBLP:journals/jair/TotisDRK23}
-          \item answer set programming~\cite{DBLP:journals/ijar/AzzoliniR23}
-        \end{itemize}
-\end{itemize}
+}
 
@@
 
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item By pointing to the outline in \cref{fig:overview}, make forward
-          references to the sections of the paper.
-    \item Somewhere: mention that we're primarily concerned with computing
-          unweighted model counts, but everything trivially extends to the
-          weighted setting as well.
-    \item Introduce greedy search and breadth-first search (BFS), together with
-          \Cranegreedy{} and \Cranebfs{}. The knowledge compilation part of both
-          \textsc{Crane} and \Cranetwo{} can be executed using either greedy
-          (similar to \textsc{ForcLift}) or breadth-first search. We use both in
-          our experiments, denoting them as \Cranegreedy{} and \Cranebfs{},
-          respectively.
-    \item Introduce the WFOMC acronym.
-    \item Introduce first-order knowledge compilation as a class of WFOMC
-          algorithms, defining/mentioning compilation rules, FCG, etc.
-  \end{itemize}
-}
-
-\paragraph{Contributions}
-\begin{itemize}
-  \item Completing the definitions of recursive functions by:
-  \begin{itemize}
-    \item identifying a sufficient set of base cases (\cref{sec:identifying})
-    \item constructing formulas that correspond to these base cases
-          (\cref{sec:simplifying})
-    \item and recursing on these subproblems
-  \end{itemize}
-  \item Compiling these function definitions into a C++ program that can be
-        executed independently for any domain size values \cref{sec:cpp}
-        \begin{itemize}
-          \item including support for infinite precision arithmetic via GNU
-                Multiple Precision Arithmetic Library
-        \end{itemize}
-  \item Experiments comparing \Cranetwo{} with the main alternative approach
-        demonstrate the ability of \Cranetwo{} to scale to domain sizes\dots
-\end{itemize}
-
-\Cref{sec:identifying,sec:cpp} deal with algebraic constructs whereas
-\cref{sec:simplifying} deals with logic.
+\Cref{fig:overview} outlines the workflow of the new algorithm \Cranetwo{}. In
+\cref{sec:main}, we describe how \CompileWithBaseCases finds the base cases for
+recursive functions by:
+\begin{enumerate*}[label=(\roman*)]
+  \item identifying a sufficient set of base cases for each function,
+  \item constructing formulas that correspond to these base cases,
+  and\label[step]{step2}
+  \item recursing on these new formulas.
+\end{enumerate*}
+Then, \cref{sec:smoothing} describes post-processing techniques for FCGs and the
+formulas from \cref{step2} above necessary to preserve the correct model count.
+Next, \cref{sec:cpp} explains how function definitions that encode a solution to
+a WFOMC problem are then compiled to a C++ program. Finally,
+\cref{sec:experiments} reports on two experiments that compare \Cranetwo{} with
+other state-of-the-art WFOMC algorithms.
 
@@
   without constants and with at most two
-  variables~\cite{DBLP:conf/nips/Broeck11}.
+  variables~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/kr/BroeckMD14}.
 \end{remark}
@@
 formula into a set of equation that include the required base cases. In short,
-we first use the knowledge compilation algorithm of the original
-\textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23} to compile the formula into:
+we first use the knowledge compilation algorithm of the original \textsc{Crane}
+to compile the formula into:
 \begin{enumerate*}[label=(\roman*)]
@@
   \]
-  In particular, we examine the first solution that \Cranebfs{} returns for this
+  In particular, we examine the first solution that \Cranetwo{} returns for this
   formula.
@@
 
-\todo[inline]{Can I turn the above into a theorem?}
-
 Finally, we note that the \Simplify procedure plays a crucial role in
@@
 simpler form above.
-
-\todo[inline]{A concluding sentence that introduces the remaining subsections?}
 
@@
 
-\section{Smoothing}
-
-Smoothness originates in propositional knowledge compilation where it is defined
-as the property that, for every disjunction node, all disjuncts (as subtrees of
-the circuit) contain the same atoms~\cite{darwiche2001tractable}. Van den Broeck
-et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11} generalise smoothness to
-first-order logic, adding set-disjunction and inclusion-exclusion nodes
-alongside disjunction.
+\section{Smoothing}\label{sec:smoothing}
+
+\emph{Smoothness} originates in propositional knowledge compilation where it is
+defined as the property that, for every disjunction node, all disjuncts (as
+subtrees of the circuit) contain the same atoms~\cite{darwiche2001tractable}.
+Van den Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11} generalise
+smoothness to first-order logic, adding set-disjunction and inclusion-exclusion
+nodes alongside disjunction.
 
@@
 
-In the rest of this section, we extend the smoothing algorithm of Van den Broeck
-et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11} even further.
+The rest of this section presents an extension to the smoothing algorithm of Van
+den Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}.
 \Cref{sec:smoothingbase} describes the role smoothing plays in the
@@
 
-\section{Experimental Evaluation}
+\section{Experimental Evaluation}\label{sec:experiments}
+
+\todo[inline]{Introduce greedy search and breadth-first search (BFS), together
+  with \Cranegreedy{} and \Cranebfs{}. The knowledge compilation part of both
+  \textsc{Crane} and \Cranetwo{} can be executed using either greedy (similar to
+  \textsc{ForcLift}) or breadth-first search. We use both in our experiments,
+  denoting them as \Cranegreedy{} and \Cranebfs{}, respectively.}
 
@@
             \item re-check submission instructions and formatting guidelines
-            \item cite the \textsc{Crane} paper (and other algorithms' papers)
-                  where necessary
           \end{itemize}

### 2024-04-27 doc/paper.tex
Section 1

@@
 
-\usepackage[backgroundcolor=lightgray]{todonotes} % TODO: remove
-\usepackage{listings}
 \usepackage[linesnumbered,ruled,vlined]{algorithm2e}
@@
 \usetikzlibrary{arrows.meta}
+\usetikzlibrary{positioning}
 
 \newtheorem{theorem}{Theorem}
-\newtheorem{fact}{Fact}
-\theoremstyle{definition}
 \newtheorem{definition}{Definition}
@@
 
-\lstset{breaklines=true}
-\lstset{language=C++,
-        basicstyle=\ttfamily,
-        stringstyle=\color{red},
-        commentstyle=\color{green},
-        breaklines=true,
-        showstringspaces=false}
-
 \newcommand{\crefrangeconjunction}{--}
@@
 \SetKwFunction{CompileWithBaseCases}{CompileWithBaseCases}
-\SetKwFunction{Crane}{Compile}
+\SetKwFunction{Compile}{Compile}
 \SetKwFunction{Propagate}{Propagate}
@@
 
-\section{Introduction (TODO)}
+\section{Introduction}
 
@@
 construct~\cite{DBLP:conf/kr/DilkasB23} recurrence relations and other recursive
-constructs that describe these sequences. Recently, WFOMC algorithms have also
+structures that describe these sequences. Recently, WFOMC algorithms have also
 been extended and applied to perform
@@
 The recently-proposed \textsc{Crane} algorithm, while able to handle formulas
-beyond the reach of \textsc{ForcLift}, was somewhat incomplete in that it could
-only construct functions definitions, which would then need to be evaluated to
+beyond the reach of \textsc{ForcLift}, was incomplete in that it could only
+construct functions definitions, which would then need to be evaluated to
 compute the WFOMC.\@ Moreover, recursive functions were presented without base
@@
 that fixes these two weaknesses.
-
-\todo[inline,caption={}]{
-  \begin{itemize}
-  \item Finish the paragraph above.
-  \item mention that \textsc{L2C}~\cite{DBLP:conf/kr/KazemiP16} compiles to C++
-  \end{itemize}
-}
 
@@
     \node[draw,rounded rectangle] at (3, -2) (findbasecases) {\FindBaseCases};
-    \node[draw,rounded rectangle,left = 0.1cm of findbasecases] (crane) {\Crane};
+    \node[draw,rounded rectangle,left = 0.1cm of findbasecases] (crane) {\Compile};
     \node[draw,rounded rectangle,right = 0.1cm of findbasecases] (propagate) {\Propagate};
@@
   \end{tikzpicture}
-  \caption[]{The outline of using \Cranetwo{} to compute the model count of a
-    formula $\phi$. The formula is compiled into a set of equations
-    $\mathcal{E}$ that are then compiled to a C++ program. This program can then
-    be run with different command line arguments to compute the model count of
-    $\phi$ for various domain sizes. \CompileWithBaseCases makes use
-    of: \begin{enumerate*}[label=(\roman*)]
-      \item the knowledge compilation algorithm of \textsc{Crane} (denoted by \Crane),
-      \item a procedure for identifying a sufficient set of base cases (denoted by \FindBaseCases),
-      \item a procedure for constructing a formula that corresponds to a given base case (denoted by \Propagate), and
-      \item algebraic simplification techniques (denoted by \Simplify).
+  \caption[]{The outline of using \Cranetwo{} to compute the model count of a formula $\phi$.
+First, the formula is compiled into a set of equations, which are then used to create a C++ program.
+This program can be executed with different command line arguments to calculate the model count of $\phi$ for different domain sizes.
+To accomplish this, the \CompileWithBaseCases function employs several components:
+    \begin{enumerate*}[label=(\roman*)]
+      \item the knowledge compilation algorithm of \textsc{Crane}, referred to as \Compile,
+      \item a procedure called \FindBaseCases, which identifies a sufficient set of base cases,
+      \item a procedure called \Propagate, which constructs a formula corresponding to a given base case, and
+      \item algebraic simplification techniques (denoted as \Simplify).
     \end{enumerate*}
@@
 
-\Cref{fig:overview} outlines the workflow of the new algorithm \Cranetwo{}. In
+\Cref{fig:overview} outlines the workflow of the new algorithm. In
 \cref{sec:main}, we describe how \CompileWithBaseCases finds the base cases for
@@
 Next, \cref{sec:cpp} explains how function definitions that encode a solution to
-a WFOMC problem are then compiled to a C++ program. Finally,
-\cref{sec:experiments} reports on two experiments that compare \Cranetwo{} with
-other state-of-the-art WFOMC algorithms.
+a WFOMC problem are then compiled to C++ programs.\footnote{Compilation to C++
+  has been explored before~\cite{DBLP:conf/kr/KazemiP16}, although with limited
+  capabilities in terms of what formulas can be handled in a lifted manner.}
+Finally, \cref{sec:experiments} reports on two experiments that compare
+\Cranetwo{} with other state-of-the-art WFOMC algorithms.
 
@@
 
-In \cref{sec:logic}, we summarise the fundamentals of first-order logic. Then,
-in \cref{sec:threelogics}, we formally define WFOMC and discuss the differences
-among three variants of first-order logic used for WFOMC.\@ Finally, in
-\cref{sec:algebra}, we introduce the terminology used to describe the output of
-the original \textsc{Crane} algorithm, i.e., functions and equations that define
-them.
-
-We write $\mathbb{N}_{0}$ for the set of non-negative integers. In the context
-of both algebra and logic, we write $S\sigma$ for a \emph{substitution} $\sigma$
-applied to an expression $S$, where
+In \cref{sec:logic}, we provide a summary of the basic principles of first-order
+logic. Then, in \cref{sec:threelogics}, we formally define WFOMC and discuss the
+distinctions between three variations of first-order logic that are utilised for
+WFOMC.\@ Finally, in \cref{sec:algebra}, we introduce the terminology used to
+describe the output of the original \textsc{Crane} algorithm, i.e., functions
+and equations that define them.
+
+We use $\mathbb{N}_{0}$ to represent the set of non-negative integers. In both
+algebra and logic, we write $S\sigma$ to denote the application of a
+\emph{substitution} $\sigma$ to an expression $S$, where
 $\sigma = [x_{1} \mapsto y_{1}, x_{2} \mapsto y_{2}, \dots, x_{n} \mapsto y_{n}]$
-denotes the replacement of all occurrences of $x_{i}$ with $y_{i}$ for all
+signifies the replacement of all instances of $x_{i}$ with $y_{i}$ for all
 $i = 1, \dots, n$.
@@
 
-In this section, we review the basic concepts of first-order logic as they are
-used in first-order knowledge compilation algorithms. There are two key
+In this section, we will review the basic concepts of first-order logic as they
+are used in first-order knowledge compilation algorithms. There are two key
 differences between the logic used within such algorithms and the logic
-supported as input. First, Skolemization~\cite{DBLP:conf/kr/BroeckMD14} is used
-to eliminate existential quantifiers by introducing additional predicates (some
-of which have negative weights). Second, the input formula is rewritten as a
-conjunction of clauses, each of which is in \emph{prenex normal
-  form}~\cite{hinman2018fundamentals}.
+supported as input. First, Skolemization~\cite{DBLP:conf/kr/BroeckMD14} is
+employed to eliminate existential quantifiers by introducing additional
+predicates. Second, the input formula is rewritten as a conjunction of clauses,
+each of which is in \emph{prenex normal form}~\cite{hinman2018fundamentals}.
 
@@
   \item $P(t_{1}, \dots, t_{m})$ for some predicate $P$ and terms
-  $t_{1}, \dots, t_{m}$ (written $P(\mathbf{t})$ for short) or
+  $t_{1}, \dots, t_{m}$ (written as $P(\mathbf{t})$ for short) or
   \item $x=y$ for some terms $x$ and $y$.
@@
 \emph{arity} of a predicate is the number of arguments it takes, i.e., $m$ in
-the case of predicate $P$ above. When we want to denote a predicate together
-with its arity, we write $P/m$. A \emph{term} is either a variable or a
-constant. Throughout the paper, we use set-theoretic notation, interpreting a
-formula as a set of clauses and a clause as a set of literals. Moreover, for
+the case of predicate $P$ mentioned above. When we want to denote a predicate
+together with its arity, we write $P/m$. A \emph{term} is either a variable or a
+constant. Throughout the paper, we will use set-theoretic notation, interpreting
+a formula as a set of clauses and a clause as a set of literals. Moreover, for
 readability, clauses written on separate lines are implicitly conjoined.
@@
 
-\begin{table*}
+\begin{table*}[t]
   \centering
@@
   \end{tabular}
-  \caption[]{A comparison of the three logics used in WFOMC in terms of:
-    \begin{enumerate*}[label=(\roman*)]
-      \item the number of sorts,
+  \caption[]{Comparison of three logics used in WFOMC based on the following aspects:
+    \begin{enumerate*}[label=(\roman*)]
+      \item number of sorts,
       \item support for constants,
-      \item the maximum number of variables,
+      \item maximum number of variables,
       \item supported quantifiers, and
-      \item supported atoms in addition to those of the form $P(\mathbf{t})$ for some predicate $P/n$ and $n$-tuple of terms $\mathbf{t}$.
-    \end{enumerate*}
-    Here:
-    \begin{enumerate*}[label=(\roman*)]
-      \item $k, m \in \mathbb{N}_{0}$, the latter of which can depend on the domain size,
-      \item $P$ is a predicate, and
+      \item supported atoms in addition to those of the form $P(\mathbf{t})$ for a predicate $P/n$ and $n$-tuple of terms $\mathbf{t}$.
+    \end{enumerate*}
+    In this context:
+    \begin{enumerate*}[label=(\roman*)]
+      \item $k$ and $m$ are non-negative integers, with the latter depending on the domain size,
+      \item $P$ represents a predicate, and
       \item $x$ and $y$ are terms.
@@
   \textsc{Crane}\footnote{\url{https://doi.org/10.5281/zenodo.8004077}} and
-  \Cranetwo{},
+  \Cranetwo{};
   \item \Ctwo{} is often used in the literature on \textsc{FastWFOMC} and
   related
-  methods~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}, and
+  methods~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22};
   \item \UFO{} is the input format supported by a private version of
@@
 version\footnote{\url{https://comp.nus.edu.sg/~tvanbr/software/fastwfomc.tar.gz}}
-does not support any cardinality constraints. The notation we use to refer to
-each logic is standard in the case of \Ctwo{}, new in the case of \UFO{}, and
-redefined to be more specific in the case of \FO{}. All three logics are
-function-free, and domains are always assumed to be finite.
+of \textsc{FastWFOMC} does not support any cardinality constraints. The notation
+we use to refer to each logic is standard in the case of \Ctwo{}, new in the
+case of \UFO{}, and redefined to be more specific in the case of \FO{}. All
+three logics are function-free, and domains are always assumed to be finite.
 
@@
 implies that $x$ and $y$ have different sorts, and it would be improper to
-write, e.g., $\forall x \in \Delta\text{. }\forall y \in \Gamma\text{.
+write, for example, $\forall x \in \Delta\text{. }\forall y \in \Gamma\text{.
 } P(x, y) \lor x = y$. \FO{} is also the only logic to support constants,
@@
 \begin{definition}[Model]\label{def:model}
-  Let $\phi$ be a formula in \FO{}. For every predicate $P/n$ in $\phi$, let
-  ${(\Delta_{i}^{P})}_{i=1}^{n}$ be a list of the corresponding domains (not
-  necessarily distinct). Let $\sigma$ be a map from the domains of $\phi$ to
-  their interpretations as sets such that:
+  Let $\phi$ be a formula in \FO{}. For each predicate $P/n$ in $\phi$, let
+  ${(\Delta_{i}^{P})}_{i=1}^{n}$ be a list of the corresponding domains (which
+  may not be distinct). Let $\sigma$ be a map from the domains of $\phi$ to
+  their interpretations as sets that, satisfying the following conditions:
   \begin{enumerate*}[label=(\roman*)]
@@
   $\neg P(\mathbf{t})$ for every predicate $P/n$ in $\phi$ and $n$-tuple
-  $\mathbf{t} \in \prod_{i=1}^{n} \sigma(\Delta_{i}^{P})$. A structure is a
-  \emph{model} if it satisfies $\phi$ (see Appendix~A of~Dilkas and
-  Belle~\shortcite{DBLP:journals/corr/abs-2306-04189} for more details).
+  $\mathbf{t} \in \prod_{i=1}^{n} \sigma(\Delta_{i}^{P})$. A structure is
+  considered a \emph{model} if it satisfies $\phi$.
 \end{definition}
@@
 \begin{definition}[WFOMC~\cite{DBLP:conf/ijcai/BroeckTMDR11}]
-  Continuing from \cref{def:model}, for every predicate $P$ in $\phi$, let
-  $w^{+}(P), w^{-}(P) \in \mathbb{Q}$ be its \emph{weights}. Unless specified
-  otherwise, we assume weights to be equal to one. The \emph{(symmetric)
-    weighted first-order model count} (WFOMC) of $\phi$ (with respect to
-  $\sigma$, $w^{+}$, and $w^{-}$) is
+  Continuing from \cref{def:model}, for each predicate $P$ in $\phi$, let
+  $w^{+}(P)$ and $w^{-}(P)$ be its \emph{weights} in $\mathbb{Q}$. Unless
+  specified otherwise, we assume weights to be equal to one. The
+  \emph{(symmetric) weighted first-order model count} (WFOMC) of $\phi$ (with
+  respect to $\sigma$, $w^{+}$, and $w^{-}$) is calculated as follows:
   \[
@@
   \]
-  where the sum is over all models of $\phi$.
+  where the sum is taken over all models of $\phi$.
 \end{definition}
@@
   where $w^{-}(S) = -1$. Although \cref{eq:functions1} has more models compared
-  to its counterpart in \Ctwo{}, the weight function makes it so the
-  \emph{weighted} model count of \cref{eq:functions1} is still equal to the
-  number of endofunctions on $\Delta$.
+  to its counterpart in \Ctwo{}, the weight function makes the \emph{weighted}
+  model count of \cref{eq:functions1} equal to the number of endofunctions on
+  $\Delta$.
 
@@
       \forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }P(x, y)\\
-      \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z,
+      \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z.
     \end{gathered}
   \end{equation}
-  first stating that each $x$ must be mapped to at least one $y$ and then adding
-  that if $x$ is mapped to both $y$ and $z$, then $y=z$. Note that \cref{eq:fo}
-  is written with two domains instead of one. Clearly, one can still count the
-  number of endofunctions by setting $|\Gamma| = |\Delta|$. As was previously
-  observed by Dilkas and Belle~\shortcite{DBLP:conf/kr/DilkasB23}, such a
-  reformulation can help first-order knowledge compilation algorithms find
-  efficient solutions.
+  The first clause asserts that each $x$ must have at least one corresponding
+  $y$, while the second statement adds the condition that if $x$ is mapped to
+  both $y$ and $z$, then $y$ must equal $z$. It is important to note that
+  \cref{eq:fo} is written with two domains instead of just one. However, we can
+  still determine the number of endofunctions by assuming that the sizes of
+  $\Gamma$ and $\Delta$ are equal. This formulation, as observed by Dilkas and
+  Belle~\shortcite{DBLP:conf/kr/DilkasB23}, can prove beneficial in enabling
+  first-order knowledge compilation algorithms to find efficient solutions.
 \end{example}
@@
 
-We write $\expr{}$ for an arbitrary algebraic expression. Some terms have
-different meanings in the context of algebra compared to logic. Here, a
-\emph{constant} is a non-negative integer. Similarly, a \emph{variable} is
-either a parameter of a function or a variable introduced by a summation, e.g.,
-$i$ in $\sum_{i=1}^{n} \expr$. A (function) \emph{signature} is
-$f(x_{1}, \dots, x_{n})$ (written $f(\mathbf{x})$ for short), where $f$ is an
-$n$-ary function, and each $x_{i}$ is a variable. An \emph{equation} is
-$f(\mathbf{x}) = \expr{}$, where $f(\mathbf{x})$ is a signature.
-
-\begin{definition}\label{def:basecase}
+We write $\expr{}$ to represent an arbitrary algebraic expression. It is
+important to note that certain terms have different meanings in the context of
+algebra compared to logic. In algebra, a \emph{constant} refers to a
+non-negative integer. Likewise, a \emph{variable} can either be a parameter of a
+function or a variable introduced through summation, such as $i$ in the
+expression $\sum_{i=1}^{n} \expr$. A (function) \emph{signature} is denoted as
+$f(x_{1}, \dots, x_{n})$ (or $f(\mathbf{x})$ for short), where $f$ represents an
+$n$-ary function, and each $x_{i}$ represents a variable. An \emph{equation} is
+written as $f(\mathbf{x}) = \expr{}$, with $f(\mathbf{x})$ representing a
+signature.
+
+\begin{definition}[Base case]\label{def:basecase}
   Let $f(\mathbf{x})$ be a function call where each $x_{i}$ is either a constant
   or a variable (note that signatures are included in this definition). Then a
-  function call $f(\mathbf{y})$ is a \emph{base case} of $f(\mathbf{x})$ if
-  $f(\mathbf{y}) = f(\mathbf{x})\sigma$, where $\sigma$ is a substitution that
-  replaces one or more $x_{i}$ with a constant.
+  function call $f(\mathbf{y})$ is considered a \emph{base case} of
+  $f(\mathbf{x})$ if $f(\mathbf{y}) = f(\mathbf{x})\sigma$, where $\sigma$ is a
+  substitution that replaces one or more $x_{i}$ with a constant.
 \end{definition}
@@
   \KwOut{set $\mathcal{E}$ of equations}
-  $(\mathcal{E}, \mathcal{F}, \mathcal{D}) \gets \Crane{$\phi$}$\;\label{line:first}
+  $(\mathcal{E}, \mathcal{F}, \mathcal{D}) \gets \Compile{$\phi$}$\;\label{line:first}
   $\mathcal{E} \gets \Simplify{$\mathcal{E}$}$\;\label{line:second}
@@
 
-\begin{example}\label{example:overall}
+\begin{example}[Counting bijections]\label{example:overall}
   Consider the following formula (previously examined by Dilkas and
@@
   \end{align*}
-  where $\Delta^{\top}$ is a new domain introduced by \Crane. Then
+  where $\Delta^{\top}$ is a new domain introduced by \Compile. Then
   \FindBaseCases identifies two base cases: $g(0, m)$ and $g(l, 0)$. In both
@@
 
-\todo[inline]{Prove (lots of notes, handwritten and elsewhere)}
+TODO: Prove (lots of notes, handwritten and elsewhere)
 
@@
 \begin{example}
-  Let us consider the clause $C \equiv \forall x \in \Gamma\text{.
+  Consider the clause $C \equiv \forall x \in \Gamma\text{.
   }\forall y, z \in \Delta\text{. } \neg P(x, y) \lor \neg P(x, z) \lor y=z$.
@@
 
-\paragraph{Stage~1 for domain recursion.}
+\paragraph{Stage~1 for Domain Recursion}
 When visiting a $\DR(c \in \Delta)$ node, for each unit clause received from the
@@
 
-\paragraph{Stage~1 for constraint removal and caching.}
+\paragraph{Stage~1 for Constraint Removal and Caching}
 When visiting a $\CR(\Delta' \gets \Delta \setminus \{\,c\,\})$ node, we reverse
@@
 
-\paragraph{Stage~2 for domain recursion.}
+\paragraph{Stage~2 for Domain Recursion}
 We need not add smoothing nodes immediately below constraint removal or caching
@@
 
-\begin{figure}
+\begin{figure}[t]
   \centering
@@
   \end{forest}
-  \caption{A smooth FCG loosely based on \cref{example:overall}. The arc from
-    the caching node to the domain recursion node is omitted for compactness.
-    The labels next to nodes show the sets of unit clauses assigned to each node
+  \caption{A smooth FCG based on \cref{example:overall}. The arc from the
+    caching node to the domain recursion node is omitted for compactness. The
+    labels next to nodes show the sets of unit clauses assigned to each node
     during Stage~1 and the order of these assignments, omitting empty
@@
 
-\todo[inline]{Introduce greedy search and breadth-first search (BFS), together
-  with \Cranegreedy{} and \Cranebfs{}. The knowledge compilation part of both
+TODO: Introduce greedy search and breadth-first search (BFS), together with
+\Cranegreedy{} and \Cranebfs{}. The knowledge compilation part of both
 \textsc{Crane} and \Cranetwo{} can be executed using either greedy (similar to
 \textsc{ForcLift}) or breadth-first search. We use both in our experiments,
-  denoting them as \Cranegreedy{} and \Cranebfs{}, respectively.}
+denoting them as \Cranegreedy{} and \Cranebfs{}, respectively.
 
@@
 
-\begin{table}
+\begin{table}[t]
   \centering
@@
 
-\section{Conclusion (TODO)}
-
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item Later on:
-          \begin{itemize}
-            \item Eliminate (e.g., Emacs) warnings.
-            \item must run it by all 3 other coauthors
-            \item re-check submission instructions and formatting guidelines
-          \end{itemize}
-  \end{itemize}
-}
+\section{Conclusion}
+
+TODO
 

### 2024-04-27 doc/paper.tex
Conclusion (& the first complete draft)

@@
 \end{example}
-
-TODO: Prove (lots of notes, handwritten and elsewhere)
 
@@
 
-TODO: Introduce greedy search and breadth-first search (BFS), together with
-\Cranegreedy{} and \Cranebfs{}. The knowledge compilation part of both
-\textsc{Crane} and \Cranetwo{} can be executed using either greedy (similar to
-\textsc{ForcLift}) or breadth-first search. We use both in our experiments,
-denoting them as \Cranegreedy{} and \Cranebfs{}, respectively.
-
-We compare \Cranetwo{} (in both BFS and greedy modes) with \textsc{FastWFOMC}
-and \textsc{ForcLift} on two problems previously considered by Dilkas and
-Belle~\shortcite{DBLP:conf/kr/DilkasB23}: the function-counting problem from
-\cref{example:functions} and the bijection-counting problem described below.
-Note that comparing \Cranetwo{} and \textsc{FastWFOMC} on a larger set of
-benchmarks is challenging because there is no automated way to translate a
-formula in \FO{} or \Ctwo{} into \UFO{} (or even check if such an encoding is
-possible). The experiments were run on an AMD~Ryzen~7~5800H processor with
-\SI{16}{\gibi\byte} of memory and Arch Linux~6.8.2-arch2-1 operating system.
-\textsc{FastWFOMC} was executed using Python~3.8.19 with Python-FLINT~0.5.0.
+We compare \Cranetwo{}\footnote{\textsc{Crane} has two modes that decide how
+  compilation rules are applied to formulas: one based on greedy search and one
+  that combines greedy and breadth-first search. We include both modes in our
+  experiments, referring to them as \Cranegreedy{} and \Cranebfs{},
+  respectively.} with \textsc{FastWFOMC} and \textsc{ForcLift} on two problems
+previously considered by Dilkas and Belle~\shortcite{DBLP:conf/kr/DilkasB23}:
+the function-counting problem from \cref{example:functions} and the
+bijection-counting problem described below. Note that comparing \Cranetwo{} and
+\textsc{FastWFOMC} on a larger set of benchmarks is challenging because there is
+no automated way to translate a formula in \FO{} or \Ctwo{} into \UFO{} (or even
+check if such an encoding is possible). The experiments were run on an
+AMD~Ryzen~7~5800H processor with \SI{16}{\gibi\byte} of memory and Arch
+Linux~6.8.2-arch2-1 operating system. \textsc{FastWFOMC} was executed using
+Python~3.8.19 with Python-FLINT~0.5.0.
 
@@
 
-\section{Conclusion}
-
-TODO
+\section{Conclusion and Future Work}
+
+In this work, we presented:
+\begin{enumerate*}[label=(\roman*)]
+  \item algorithmic techniques for finding the base cases of recursive functions
+  produced by the original \textsc{Crane} algorithm,
+  \item an extension to the smoothing procedure of \textsc{ForcLift} and
+  \textsc{Crane} that supports base case formulas and the compilation rules
+  introduced by Dilkas and Belle~\shortcite{DBLP:conf/kr/DilkasB23}.
+  \item an approach for compiling function definitions to C++ programs with
+  support for arbitrary-precision arithmetic, and
+  \item experimental evidence showing that \Cranetwo{} can scale to domain sizes
+  orders of magnitude higher than \textsc{FastWFOMC} while being able to handle
+  more formulas than \textsc{ForcLift}.
+\end{enumerate*}
+
+Many avenues for future work remain. In particular, a more extensive
+experimental study is warranted to better understand how WFOMC algorithms
+compare in terms of
+\begin{enumerate*}[label=(\roman*)]
+  \item what formulas they can handle and
+  \item their scalability with respect to domain size.
+\end{enumerate*}
+The capabilities of \Cranetwo{} could be further characterised in other ways.
+For instance, one could prove \emph{completeness} for a fragment of first-order
+logic such as \Ctwo{} (via a suitable encoding of counting quantifiers).
+Moreover, the efficiency with which a WFOMC algorithm is able to handle a
+particular formula can be assessed using \emph{fine-grained complexity}. In the
+case of \textsc{Crane} and \Cranetwo{}, one can do so simply by analysing the
+equations~\cite{DBLP:conf/kr/DilkasB23}. This way, one can reason about
+efficiency in a more implementation-independent manner by making claims about
+the maximum degree of the polynomial that characterises any particular solution.
 

### 2024-04-29 doc/paper.tex
Proof of Theorem 1

--- 2024-04-27 doc/paper.tex
@@
 \newtheorem{theorem}{Theorem}
+\newtheorem{lemma}{Lemma}
+\newtheorem{fact}{Observation}
+\newtheorem{corollary}{Corollary}
+\newtheorem{assumption}{Assumption}
 \newtheorem{definition}{Definition}
@@
 \crefname{line}{line}{lines}
+
+\crefname{fact}{Observation}{Observations}
+\crefname{assumption}{Assumption}{Assumptions}
 
@@
 \emails
-\{210051002, 210050061\}@iitb.ac.in,
+210051002@iitb.ac.in,
+guramrit@iitb.ac.in,
 paulius.dilkas@nus.edu.sg,
@@
 
-\emph{First-order model counting} is the problem of counting the number of
-models of a sentence in first-order logic over some given domain(s). The
-(symmetric) weighted variant of the problem (WFOMC) asks for the sum of model
-weights instead, where the weight of a model is a product over predicate
-weights~\cite{DBLP:conf/ijcai/BroeckTMDR11}. WFOMC is a prominent approach to
-the broader problem known as \emph{lifted (probabilistic) inference} that aims
-to compute probabilities more efficiently by utlilising symmetries inherent in
-the description of the problem~\cite{DBLP:conf/ecai/Kersting12}.
+\emph{First-order model counting} is the task of counting the number of models
+of a sentence in first-order logic over some given domain(s). The (symmetric)
+weighted variant of this problem, known as WFOMC, seeks to calculate the sum of
+model weights. In WFOMC, the weight of a model is determined by predicate
+weights~\cite{DBLP:conf/ijcai/BroeckTMDR11}. WFOMC is a key approach to
+\emph{lifted (probabilistic) inference}, which aims to compute probabilities
+more efficiently by leveraging symmetries inherent in the problem
+description~\cite{DBLP:conf/ecai/Kersting12}.
 
@@
 
-Lifted inference is an active area of research with recent work in domains such
+Lifted inference is an active area of research, with recent work in domains such
 as constraint satisfaction problems~\cite{DBLP:journals/jair/TotisDRK23} and
 probabilistic answer set programming~\cite{DBLP:journals/ijar/AzzoliniR23}.
-WFOMC itself has been used to perform inference on probabilistic
+WFOMC has been used for inference on probabilistic
 databases~\cite{DBLP:journals/debu/GribkoffSB14} and probabilistic logic
-programs~\cite{DBLP:journals/ijar/RiguzziBZCL17}. By iteratively considering
-domains of increasing sizes, the model count of a formula can be interpreted as
-an (integer) sequence. WFOMC algorithms have been used to discover new
-sequences~\cite{DBLP:conf/ijcai/SvatosJT0K23} and
-conjecture~\cite{DBLP:conf/ilp/BarvinekB0ZK21} and
-construct~\cite{DBLP:conf/kr/DilkasB23} recurrence relations and other recursive
-structures that describe these sequences. Recently, WFOMC algorithms have also
-been extended and applied to perform
+programs~\cite{DBLP:journals/ijar/RiguzziBZCL17}. By considering domains of
+increasing sizes, the model count of a formula can be seen as an integer
+sequence. WFOMC algorithms have been utilised for discovering new
+sequences~\cite{DBLP:conf/ijcai/SvatosJT0K23} as well as
+conjecturing~\cite{DBLP:conf/ilp/BarvinekB0ZK21} and
+constructing~\cite{DBLP:conf/kr/DilkasB23} recurrence relations and other
+recursive structures that describe these sequences. Additionally, WFOMC
+algorithms have been extended to perform
 \emph{sampling}~\cite{DBLP:conf/aaai/WangB0K22,DBLP:conf/lics/WangP0K23}.
@@
 The complexity of WFOMC is typically characterised in terms of \emph{data
-  complexity}, i.e., fixing the formula and asking whether there exists an
-algorithm that can compute the WFOMC in time polynomial in the domain size(s).
-If such an algorithm exists, the formula is called
+  complexity}. This involves fixing the formula and determining whether an
+algorithm exists that can compute the WFOMC in time polynomial with respect to
+the domain size(s). If such an algorithm exists, the formula is called
 \emph{liftable}~\cite{DBLP:conf/starai/JaegerB12}. Beame et
-al.~\shortcite{DBLP:conf/pods/BeameBGS15} showed that there exists an unliftable
-formula with three variables. It is also known that all formulas with up to two
-variables are liftable~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/kr/BroeckMD14}.
-This liftable fragment of formulas with two variables has been extended with
-various axioms~\cite{DBLP:conf/aaai/TothK23,DBLP:journals/ai/BremenK23},
-counting quantifiers~\cite{DBLP:journals/jair/Kuzelka21}, and in other
+al.~\shortcite{DBLP:conf/pods/BeameBGS15} demonstrated the existence of an
+unliftable formula with three variables. It is also known that all formulas with
+up to two variables are
+liftable~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/kr/BroeckMD14}. The liftable
+fragment of formulas with two variables has been expanded with various
+axioms~\cite{DBLP:conf/aaai/TothK23,DBLP:journals/ai/BremenK23}, counting
+quantifiers~\cite{DBLP:journals/jair/Kuzelka21} and in other
 ways~\cite{DBLP:conf/nips/KazemiKBP16}.
@@
 
-There is a variety of WFOMC algorithms with different underlying principles.
-Perhaps the most prominent class of WFOMC algorithms is based on
-\emph{first-order knowledge compilation}. Here, by iteratively applying
-\emph{compilation rules}, the formula is compiled to a representation (such as a
-circuit of graph), which can then be used to compute the WFOMC for any
-combination of domain sizes (or weights). Algorithms in this class include
-\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} and its recent extension
-\textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23}. The former compiles formulas into
-circuits whereas the latter compiles them first to \emph{first-order
-  computational graphs} (FCGs) and then to (algebraic) equations. Another major
-WFOMC algorithm \textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21} is based on
-cell enumeration. Other algorithms employ local
-search~\cite{DBLP:journals/pvldb/NiuRDS11}, junction
-trees~\cite{DBLP:conf/aaai/VenugopalSG15}, Monte Carlo
+There are various WFOMC algorithms with different underlying principles. Perhaps
+the most prominent class of WFOMC algorithms is based on \emph{first-order
+  knowledge compilation}. In this approach, the formula is compiled into a
+representation (such as a circuit or graph) by iteratively applying
+\emph{compilation rules}. This representation can then be used to compute the
+WFOMC for any combination of domain sizes (or weights). Algorithms in this class
+include \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} and its recent
+extension \textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23}. The former compiles
+formulas into circuits, while the latter compiles them first to
+\emph{first-order computational graphs} (FCGs) and then to (algebraic)
+equations. Another WFOMC algorithm,
+\textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21}, is based on cell enumeration.
+Other algorithms utilise local search~\cite{DBLP:journals/pvldb/NiuRDS11},
+junction trees~\cite{DBLP:conf/aaai/VenugopalSG15}, Monte Carlo
 sampling~\cite{DBLP:journals/cacm/GogateD16}, and anytime approximation via
@@
 
-The recently-proposed \textsc{Crane} algorithm, while able to handle formulas
-beyond the reach of \textsc{ForcLift}, was incomplete in that it could only
-construct functions definitions, which would then need to be evaluated to
-compute the WFOMC.\@ Moreover, recursive functions were presented without base
-cases. In this work, we present \Cranetwo{}---an extension of \textsc{Crane}
-that fixes these two weaknesses.
+The recently proposed \textsc{Crane} algorithm, while capable of handling
+formulas beyond the reach of \textsc{ForcLift}, was incomplete as it could only
+construct function definitions, which would then need to be evaluated to compute
+the WFOMC.\@ Additionally, recursive functions were presented without base
+cases. In this work, we introduce \Cranetwo{}, an extension of \textsc{Crane}
+that addresses these two weaknesses.
 
@@
   \item identifying a sufficient set of base cases for each function,
-  \item constructing formulas that correspond to these base cases,
+  \item constructing formulas corresponding to these base cases,
   and\label[step]{step2}
@@
 \end{enumerate*}
-Then, \cref{sec:smoothing} describes post-processing techniques for FCGs and the
-formulas from \cref{step2} above necessary to preserve the correct model count.
-Next, \cref{sec:cpp} explains how function definitions that encode a solution to
-a WFOMC problem are then compiled to C++ programs.\footnote{Compilation to C++
-  has been explored before~\cite{DBLP:conf/kr/KazemiP16}, although with limited
-  capabilities in terms of what formulas can be handled in a lifted manner.}
-Finally, \cref{sec:experiments} reports on two experiments that compare
-\Cranetwo{} with other state-of-the-art WFOMC algorithms.
+Then, \cref{sec:smoothing} explains post-processing techniques for FCGs and the
+formulas from \cref{step2} above required to preserve the correct model count.
+Next, \cref{sec:cpp} elucidates how function definitions encoding a solution to
+a WFOMC problem are compiled into C++ programs.\footnote{The possibility of
+  compiling WFOMC solutions to C++ programs has been previously
+  considered~\cite{DBLP:conf/kr/KazemiP16}. However, the extent of formulas that
+  could be handled was limited.} Finally, \cref{sec:experiments} presents two
+experiments comparing \Cranetwo{} with other state-of-the-art WFOMC algorithms.
 
@@
     \end{enumerate*}
-    In this context:
+    Here:
     \begin{enumerate*}[label=(\roman*)]
@@
 
-Both \Ctwo{} and \UFO{} are single-sorted (i.e., variables are always quantified
-over the same domain) and only include formulas with at most two variables and
-no constants. Unlike \UFO{}, \Ctwo{} supports existential quantifiers, including
+\Ctwo{} and \UFO{} are single-sorted (i.e., all variables are quantified over
+the same domain) and only include formulas with at most two variables and no
+constants. Unlike \UFO{}, \Ctwo{} supports existential quantifiers, including
 \emph{counting quantifiers}. For example, $\exists^{=1} x\text{. }\phi(x)$ means
@@
 \emph{(equality) cardinality constraints}. For example, $|P| = 3$ constrains all
-models to have \emph{exactly three positive literals with predicate $P$}.
+models to have \emph{precisely three positive literals with the predicate $P$}.
 
@@
   may not be distinct). Let $\sigma$ be a map from the domains of $\phi$ to
-  their interpretations as sets that, satisfying the following conditions:
+  their interpretations as sets, satisfying the following conditions:
   \begin{enumerate*}[label=(\roman*)]
@@
   $\neg P(\mathbf{t})$ for every predicate $P/n$ in $\phi$ and $n$-tuple
-  $\mathbf{t} \in \prod_{i=1}^{n} \sigma(\Delta_{i}^{P})$. A structure is
-  considered a \emph{model} if it satisfies $\phi$.
+  $\mathbf{t} \in \prod_{i=1}^{n} \sigma(\Delta_{i}^{P})$. A structure is a
+  \emph{model} if it satisfies $\phi$.
 \end{definition}
@@
   $w^{+}(P)$ and $w^{-}(P)$ be its \emph{weights} in $\mathbb{Q}$. Unless
-  specified otherwise, we assume weights to be equal to one. The
+  specified otherwise, we assume all weights are equal to one. The
   \emph{(symmetric) weighted first-order model count} (WFOMC) of $\phi$ (with
-  respect to $\sigma$, $w^{+}$, and $w^{-}$) is calculated as follows:
+  respect to $\sigma$, $w^{+}$, and $w^{-}$) is:
   \[
@@
   \]
-  where the sum is taken over all models of $\phi$.
+  where the sum is over all models of $\phi$.
 \end{definition}
@@
 We write $\expr{}$ to represent an arbitrary algebraic expression. It is
-important to note that certain terms have different meanings in the context of
-algebra compared to logic. In algebra, a \emph{constant} refers to a
-non-negative integer. Likewise, a \emph{variable} can either be a parameter of a
-function or a variable introduced through summation, such as $i$ in the
-expression $\sum_{i=1}^{n} \expr$. A (function) \emph{signature} is denoted as
+important to note that some terms have different meanings in algebra compared to
+logic. In algebra, a \emph{constant} refers to a non-negative integer. Likewise,
+a \emph{variable} can either be a parameter of a function or a variable
+introduced through summation, such as $i$ in the expression
+$\sum_{i=1}^{n} \expr$. A (function) \emph{signature} is
 $f(x_{1}, \dots, x_{n})$ (or $f(\mathbf{x})$ for short), where $f$ represents an
 $n$-ary function, and each $x_{i}$ represents a variable. An \emph{equation} is
-written as $f(\mathbf{x}) = \expr{}$, with $f(\mathbf{x})$ representing a
-signature.
+$f(\mathbf{x}) = \expr{}$, with $f(\mathbf{x})$ representing a signature.
 
@@
   Let $f(\mathbf{x})$ be a function call where each $x_{i}$ is either a constant
-  or a variable (note that signatures are included in this definition). Then a
+  or a variable (note that signatures are included in this definition). Then
   function call $f(\mathbf{y})$ is considered a \emph{base case} of
@@
 
-\Cref{alg:compilewithbasecases} outlines our overall approach for compiling a
-formula into a set of equation that include the required base cases. In short,
-we first use the knowledge compilation algorithm of the original \textsc{Crane}
-to compile the formula into:
+\Cref{alg:compilewithbasecases} presents our overall approach for compiling a
+formula into equations that include the necessary base cases. To begin, we
+utilise the knowledge compilation algorithm from the original \textsc{Crane} to
+compile the formula into three components:
 \begin{enumerate*}[label=(\roman*)]
@@
 \end{enumerate*}
-After some algebraic simplification, $\mathcal{E}$ is passed to the
-\FindBaseCases procedure (described in \cref{sec:identifying}) that returns a
-set of base cases that we need to find solutions for. For each base case
-$f(\mathbf{x})$, we identify the formula associated with $f$ and simplify it
-using the \Propagate procedure (described in \cref{sec:simplifying}). The
-algorithm then recurses on these simplified formulas and adds the resulting base
-case equations to $\mathcal{E}$. \Cref{example:overall} explains
-\cref{alg:compilewithbasecases} in more detail.
+After some algebraic simplification, $\mathcal{E}$ is then passed to the
+\FindBaseCases procedure (explained in \cref{sec:identifying}), which identifies
+the base cases that need to be defined. For each base case $f(\mathbf{x})$, we
+determine the formula associated with the function name $f$ and simplify it
+using the \Propagate procedure (explained in \cref{sec:simplifying}). The
+algorithm then calls itself on these simplified formulas and adds the resulting
+base case equations to $\mathcal{E}$. \Cref{example:overall} provides a more
+detailed explanation of \cref{alg:compilewithbasecases}.
 
@@
   Consider the following formula (previously examined by Dilkas and
-  Belle~\shortcite{DBLP:conf/kr/DilkasB23}) that defines predicate $P$ to be a
+  Belle~\shortcite{DBLP:conf/kr/DilkasB23}) that defines predicate $P$ as a
   bijection between two sets $\Gamma$ and $\Delta$:
@@
   \]
-  In particular, we examine the first solution that \Cranetwo{} returns for this
+  We specifically examine the first solution returned by \Cranetwo{} for this
   formula.
@@
   where $S$ is a predicate introduced by Skolemization with weights
-  $w^{+}(S) = 1$ and $w^{-}(S) = -1$. Hence, we get the base case
+  $w^{+}(S) = 1$ and $w^{-}(S) = -1$. Hence, we obtain the base case
   $g(0, m) = 0^{m}$. In the case of $g(l, 0)$, \Propagate{$\psi$, $\Gamma$, $0$}
-  returns an empty formula, giving us $g(l, 0) = 1$.
+  returns an empty formula, resulting in $g(l, 0) = 1$.
 \end{example}
 
-Note that these base cases overlap when $l = m = 0$ but are consistent with each
-other since $0^{0} = 1$. More generally, let $\phi$ be a formula with two
-domains $\Gamma$ and $\Delta$, and let $n, m \in \mathbb{N}_{0}$. Then the model
-count of \Propagate{$\phi$, $\Delta$, $n$} assuming $|\Gamma| = m$ is the same
-as the model count of \Propagate{$\phi$, $\Gamma$, $m$} assuming $|\Delta| = n$.
-
-Finally, we note that the \Simplify procedure plays a crucial role in
-simplifying a common algebraic pattern $\sum_{m=0}^{n}[a \le m \le b] f(m)$.
-Here:
+It is worth noting that these base cases overlap when $l = m = 0$ but remain
+consistent since $0^{0} = 1$. Generally, let $\phi$ be a formula with two
+domains $\Gamma$ and $\Delta$, and let $n, m \in \mathbb{N}_{0}$. Then the WFOMC
+of \Propagate{$\phi$, $\Delta$, $n$} assuming $|\Gamma| = m$ is the same as the
+WFOMC of \Propagate{$\phi$, $\Gamma$, $m$} assuming $|\Delta| = n$.
+
+Finally, we highlight the crucial role of the \Simplify procedure in simplifying
+the algebraic pattern $\sum_{m=0}^{n}[a \le m \le b] f(m)$. Here:
 \begin{enumerate*}[label=(\roman*)]
@@
     0 & \text{otherwise}
-  \end{cases}$ is the Iverson bracket.
+  \end{cases}$ represents the Iverson bracket.
 \end{enumerate*}
@@
 $g(l, m) = \sum_{k=0}^{m}[0 \le k \le 1]\binom{m}{k}g(l-1, m-k)$ into the
-simpler form above.
+simplified form mentioned above.
 
@@
 
-\Cref{alg:findbasecases} summarises the implementation of \FindBaseCases. For
-each recursive call from a function $f$ to itself, we consider two types of
-arguments:
+\Cref{alg:findbasecases} summarises the implementation of the \FindBaseCases
+function. When a function $f$ calls itself recursively, \FindBaseCases considers
+two types of arguments:
 \begin{enumerate*}[label=(\roman*)]
   \item constants and
-  \item arguments of the form $x_{i} - c_{i}$, where $c_{i} \in \mathbb{N}_{0}$
-  is a constant, and $x_{i}$ is the $i$-th argument of the signature of $f$.
-\end{enumerate*}
-In the former case, we consider a base case specifically for that constant. In
-the latter case, we consider a base case for constants from zero up to (but not
-including) $c_{i}$. \Cref{thm:halting} below motivates this approach.
+  \item arguments of the form $x_{i} - c_{i}$, where $c_{i}$ is a constant and
+  $x_{i}$ is the $i$-th argument of the signature of $f$.
+\end{enumerate*}
+If the argument is a constant $c_{i}$, a base case with $c_{i}$ is added. In the
+second case, a base case is added for each constant from zero up to (but not
+including) $c_{i}$. The following discussion explains the reasoning behind this
+approach.
 
 \begin{example}
-  Consider the recursive function $g$ from \cref{example:overall}.
-  \FindBaseCases{$\mathcal{E}$} iterates over two function calls: $g(l-1, m)$
-  and $g(l-1, m-1)$. The former produces the base case $g(0, m)$, while the
-  latter produces both $g(0, m)$ and $g(l, 0)$.
+  Let us consider the recursive function $g$ from \cref{example:overall}. In
+  this case, \FindBaseCases iterates over two function calls: $g(l-1, m)$ and
+  $g(l-1, m-1)$. The former produces the base case $g(0, m)$, while the latter
+  produces both $g(0, m)$ and $g(l, 0)$.
 \end{example}
 
-TODO: Prove (lots of notes, handwritten and elsewhere)
-
-\begin{theorem}[Termination]\label{thm:halting}
-  Let us assume the following about the input set of equations $\mathcal{E}$:
-  \begin{enumerate}
-    \item Each function $f$ has exactly one equation with $f$ on the left-hand
-          side.\@ We call this equation the \emph{definition} of $f$.
-    \item There exists a topological ordering of all functions ${(f_{i})}_{i}$
-          such that the definition of $f_{i}$ does not contain function calls to
-          $f_{j}$ with $j > i$.\footnote{This condition excludes the possibility
-          of mutual recursion and similar cyclic scenarios and is akin to
-          stratified logic programs~\cite{DBLP:books/sp/Lloyd87}.}
-    \item For every equation $(f(\mathbf{x}) = \expr) \in \mathcal{E}$, every
-          recursive function call $f(\mathbf{y}) \in \expr$ satisfies the
+For the rest of this section, let $\mathcal{E}$ represent the equations returned
+by \CompileWithBaseCases. To demonstrate that the base cases identified by
+\FindBaseCases are sufficient, we begin with a few observations that stem from
+the details of previous
+work~\cite{DBLP:conf/ijcai/BroeckTMDR11,DBLP:conf/kr/DilkasB23} and this work.
+
+\begin{fact}\label{assumption1}
+  For each function $f$, there is precisely one equation $e \in \mathcal{E}$
+  with $f(\mathbf{x})$ on the left-hand side where all $x_{i}$'s are variables
+  (i.e., $e$ is not a base case). We refer to $e$ as the \emph{definition} of
+  $f$.
+\end{fact}
+
+\begin{fact}\label{assumption2}
+  There is a \emph{topological ordering} of all functions ${(f_{i})}_{i}$ in
+  $\mathcal{E}$ such that equations in $\mathcal{E}$ with $f_{i}$ on the
+  left-hand side do not contain function calls to $f_{j}$ with $j > i$. This
+  condition prevents mutual recursion and other cyclic scenarios.
+\end{fact}
+
+\begin{fact}\label{assumption3}
+  For every equation $(f(\mathbf{x}) = \expr) \in \mathcal{E}$, the evaluation
+  of $\expr$ terminates when provided with the values of all relevant function
+  calls.
+\end{fact}
+
+\begin{corollary}\label{fact}
+  If $f$ is a non-recursive function with no function calls on the right-hand
+  side of its definition, then the evaluation of any function call
+  $f(\mathbf{x})$ terminates.
+\end{corollary}
+
+\begin{fact}\label{fact2}
+  For any equation $f(\mathbf{x}) = \expr{}$, if $\mathbf{x}$ contains only
+  constants, then $\expr{}$ cannot include any function calls to $f$.
+\end{fact}
+
+Additionally, we introduce an assumption about the structure of recursion.
+
+\begin{assumption}\label{assumption4}
+  For every equation $(f(\mathbf{x}) = \expr) \in \mathcal{E}$, every recursive
+  function call $f(\mathbf{y}) \in \expr$ satisfies the
   following:
   \begin{itemize}
-            \item each $y_{i}$ is either $x_{i} - c_{i}$ or $c_{i}$ for some
-                  constant $c_{i} \in \mathbb{N}_{0}$;
-            \item there exists $i$ such that $y_{i} = x_{i} - c_{i}$ for some
+    \item Each $y_{i}$ is either $x_{i} - c_{i}$ or $c_{i}$ for some constant
+          $c_{i}$.
+    \item There exists $i$ such that $y_{i} = x_{i} - c_{i}$ for some
           $c_{i} > 0$.
   \end{itemize}
-  \end{enumerate}
-  Then the set of base cases $\mathcal{B}$ returned by
-  \FindBaseCases{$\mathcal{E}$} is \emph{sufficient} for $\mathcal{E}$ in the
-  following sense. The evaluation of any function call with non-negative
-  arguments terminates as long as the evaluation of base cases is prioritised
-  over the corresponding recursive definitions.\footnote{Recall that, as
-    previously discussed, the order in which base cases are considered is
-    immaterial.}
+\end{assumption}
+
+Finally, we assume a particular order of evaluation for function calls using the
+equations in $\mathcal{E}$. Specifically, we assume that base cases are
+considered before the recursive definition. The exact order in which base cases
+are considered is not relevant.
+
+\begin{assumption}
+  When multiple equations in $\mathcal{E}$ match a function call
+  $f(\mathbf{x})$, preference is given to an equation with the most constants on
+  its left-hand side.
+\end{assumption}
+
+With the facts and assumptions mentioned above, we prove the following theorem.
+
+\begin{theorem}[Termination]\label{thm:halting}
+  Let $f$ be an $n$-ary function in $\mathcal{E}$ and
+  $\mathbf{x} \in \mathbf{N}_{0}^{n}$. Then the evaluation of $f(\mathbf{x})$
+  terminates.
 \end{theorem}
+
+We prove \cref{thm:halting} using double induction. First, we apply induction on
+the number of functions in $\mathcal{E}$. Then, we use induction on the arity of
+the `last' function in $\mathcal{E}$ according to some topological ordering (as
+defined in \cref{assumption2}). For readability, we divide the proof into
+several lemmas of increasing generality.
+
+\begin{lemma}\label{lemma:oneunary}
+  Assume that $\mathcal{E}$ consists of just \emph{one unary} function $f$. Then
+  the evaluation of a function call $f(x)$ terminates for any
+  $x \in \mathbb{N}_{0}$.
+\end{lemma}
+\begin{proof}
+  If $f(x)$ is captured by a base case, then its evaluation terminates by
+  \cref{fact,fact2}. If $f$ is not recursive, the evaluation of
+  $f(x)$ terminates by \cref{fact}.
+
+  Otherwise, let $f(y)$ be an arbitrary function call on the right-hand side of
+  the definition of $f(x)$. If $y$ is a constant, there is a base case for
+  $f(y)$. Otherwise, let $y = x - c$ for some $c > 0$. Then there exists
+  $k \in \mathbb{N}_{0}$ such that $0 \le x - kc \le c-1$. So, after $k$
+  iterations, the sequence of function calls $f(x), f(x-c), f(x-2c),\dots$ will
+  be captured by the base case $f(x \mod c)$.
+\end{proof}
+
+\begin{lemma}\label{lemma:onefunction}
+  Generalising \cref{lemma:oneunary}, let $\mathcal{E}$ be a set of equations
+  for \emph{one} $n$-ary function $f$ for some $n \ge 1$. Then the evaluation of
+  $f(\mathbf{x})$ terminates for any $\mathbf{x} \in \mathbb{N}_{0}^{n}$.
+\end{lemma}
+\begin{proof}
+  If $f$ is non-recursive, the evaluation of $f(\mathbf{x})$ terminates by
+  previous arguments. We proceed by induction on $n$, with the base case of
+  $n=1$ handled by \cref{lemma:oneunary}. Assume that $n > 1$. Any base case of
+  $f$ can be seen as a function of arity $n-1$, since one of the parameters is
+  fixed. Thus, the evaluation of any base case terminates by the inductive
+  hypothesis. It remains to show that the evaluation of the recursive equation
+  for $f$ terminates, but that follows from \cref{assumption3}.
+\end{proof}
+
+\begin{proof}[Proof of \cref{thm:halting}]
+  We proceed by induction on the number of functions $n$. The base case of $n=1$
+  is handled by \cref{lemma:onefunction}. Let ${(f_{i})}_{i=1}^{n}$ be some
+  topological ordering of these $n > 1$ functions. If $f = f_{j}$ for $j < n$,
+  then the evaluation of $f(\mathbf{x})$ terminates by the inductive hypothesis
+  since $f_{j}$ cannot call $f_{n}$ by \cref{assumption2}. Using the inductive
+  hypothesis that all function calls to $f_{j}$ (with $j < n$) terminate, the
+  proof proceeds similarly to the Proof of \cref{lemma:onefunction}.
+\end{proof}
 
@@
 
-\Propagate (\cref{alg:propagate}) modifies formula $\phi$ with the assumption
-that domain $\Delta$ has size $n \in \mathbb{N}_{0}$. In the case of $n=0$, many
-clauses become vacuously satisfied and can be removed. In the case of
-$n > 0$\footnote{None of the formulas considered in this work had $n > 1$.}, we
-perform partial grounding, using constants to replace all variables quantified
-over $\Delta$. \Cref{alg:propagate} considers these two cases separately. For a
-literal or a clause $C$, we write $\Doms(C)$ to denote the set of corresponding
-domains.
-
-In the case of $n = 0$, consider three types of clauses:
-\begin{enumerate*}[label=(\roman*)]
-  \item those that do not mention $\Delta$,\label{type1}
+\Cref{alg:propagate}, called \Propagate, modifies the formula $\phi$ based on
+the assumption that $|\Delta| = n$. When $n=0$, some clauses become vacuously
+satisfied and can be removed. When $n > 0$\footnote{None of the formulas
+  examined in this study had $n > 1$.}, partial grounding is performed by
+replacing all variables quantified over $\Delta$ with constants.
+\Cref{alg:propagate} handles these two cases separately. For a literal or a
+clause $C$, the set of corresponding domains is denoted as $\Doms(C)$.
+
+In the case of $n = 0$, there are three types of clauses to consider:
+\begin{enumerate*}[label=(\roman*)]
+  \item those that do not mention $\Delta$,\label[type]{type1}
   \item those in which every literal contains variables quantified over
-  $\Delta$, and\label{type2}
+  $\Delta$, and\label[type]{type2}
   \item those that have some literals with variables quantified over $\Delta$
-  and some without.\label{type3}
-\end{enumerate*}
-\Cref{type1} clauses are transferred to the new formula $\phi'$ unchanged. For
-\cref{type2} clauses, $C' = \emptyset$, so these clauses are filtered out. One
-might think that the same should be done with \cref{type3} clauses, however,
-\cref{line:smoothing1,line:smoothing2} perform a new kind of smoothing, the
-explanation of which we defer to \cref{sec:smoothingbase}.
-
-In the case of $n>0$, we introduce $n$ new constants. Consider an arbitrary
-clause $C \in \phi$ and let $m \in \mathbb{N}_{0}$ be the number of variables in
-$C$ quantified over $\Delta$. If $m=0$, then, similarly to the previous case, we
-add $C$ directly to $\phi'$. Otherwise, we add a clause to $\phi'$ with every
-possible way of replacing the $m$ variables in $C$ with some combination of the
-$n$ new constants.
+  and some without.\label[type]{type3}
+\end{enumerate*}
+Clauses of \cref{type1} are transferred to the new formula $\phi'$ without any
+changes. For clauses of \cref{type2}, $C'$ is empty, so these clauses are
+filtered out. As for clauses of \cref{type3}, a new kind of smoothing is
+performed, which will be explained in \cref{sec:smoothingbase}.
+
+In the case of $n>0$, $n$ new constants are introduced. Let $C$ be an arbitrary
+clause in $\phi$, and let $m \in \mathbb{N}_{0}$ be the number of variables in
+$C$ quantified over $\Delta$. If $m=0$, $C$ is added directly to $\phi'$.
+Otherwise, a clause is added to $\phi'$ for every possible combination of
+replacing the $m$ variables in $C$ with the $n$ new constants.
 
 \begin{example}
-  Consider the clause $C \equiv \forall x \in \Gamma\text{.
-  }\forall y, z \in \Delta\text{. } \neg P(x, y) \lor \neg P(x, z) \lor y=z$.
-  Then
+  Let $C \equiv \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{.
+  } \neg P(x, y) \lor \neg P(x, z) \lor y=z$. Then
   $\Doms(C) = \Doms(\neg P(x, y)) = \Doms(\neg P(x, z)) = \{\, \Gamma, \Delta \,\}$,
   and $\Doms(y=z) = \{\, \Delta \,\}$. A call to \Propagate{$\{\, C \,\}$,
-    $\Delta$, $3$} would produce the following formula with nine clauses:
+    $\Delta$, $3$} would result in the following formula with nine clauses:
   \begin{align*}
@@
     \vdots&\\
-    \forall x \in \Gamma\text{. }\neg P(x, c_{3}) \lor& \neg P(x, c_{3}) \lor c_{3}=c_{3},\\
+    \forall x \in \Gamma\text{. }\neg P(x, c_{3}) \lor& \neg P(x, c_{3}) \lor c_{3}=c_{3}.\\
   \end{align*}
-  where $c_{1}$, $c_{2}$, and $c_{3}$ are the new constants.
+  Here, $c_{1}$, $c_{2}$, and $c_{3}$ are the new constants.
 \end{example}
@@
 
-\emph{Smoothness} originates in propositional knowledge compilation where it is
-defined as the property that, for every disjunction node, all disjuncts (as
-subtrees of the circuit) contain the same atoms~\cite{darwiche2001tractable}.
-Van den Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11} generalise
-smoothness to first-order logic, adding set-disjunction and inclusion-exclusion
-nodes alongside disjunction.
-
-The motivation for smoothing is as follows. Whenever compilation rules such as
-unit propagation and inclusion-exclusion simplify the formula, some ground atoms
-might be eliminated from consideration (see \cref{example:basecasesmoothing}
-below). To account for them during counting, smoothing nodes (i.e., tautological
-clauses such as $P(c) \lor \neg P(c)$) are added to the FCG at an appropriate
-location.
-
-The rest of this section presents an extension to the smoothing algorithm of Van
-den Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}.
-\Cref{sec:smoothingbase} describes the role smoothing plays in the
-base-case-finding algorithm from \cref{sec:main}. Then, \cref{sec:smoothingfcg1}
-shows how to adapt smoothing to the compilation rules introduced by Dilkas and
+\emph{Smoothness} is a property originating in propositional knowledge
+compilation, where it refers to the situation where all disjuncts in a
+disjunction node contain the same atoms~\cite{darwiche2001tractable}. Van den
+Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11} extend this concept to
+first-order logic, introducing set-disjunction and inclusion-exclusion nodes in
+addition to disjunction.
+
+The purpose of smoothing is as follows. When compilation rules such as unit
+propagation and inclusion-exclusion simplify a formula, certain ground atoms may
+be eliminated (see \cref{example:basecasesmoothing} below). To properly account
+for these atoms during counting, smoothing nodes (i.e., tautological clauses
+such as $P(c) \lor \neg P(c)$) are added to the FCG in the appropriate location.
+
+The remainder of this section presents an extension to the smoothing algorithm
+of Van den Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}.
+\Cref{sec:smoothingbase} explains the role of smoothing in the base-case-finding
+algorithm described in \cref{sec:main}. \Cref{sec:smoothingfcg1} demonstrates
+how to adapt smoothing to the compilation rules introduced by Dilkas and
 Belle~\shortcite{DBLP:conf/kr/DilkasB23}.
@@
 of \cref{alg:propagate}. Suppose that \Propagate is called with arguments
-$(\phi, \Delta, 0)$, i.e., we are simplifying formula $\phi$ by assuming that
-domain $\Delta$ is empty. Informally, if there is a predicate $P$ in $\phi$ that
-has nothing to do with domain $\Delta$, the role of smoothing is to preserve all
-occurrences of $P$ even if all clauses with $P$ become vacuously satisfied. We
-note that the approach presented in this section is far from unique and explain
-it via an example below.
+$(\phi, \Delta, 0)$, which means we are simplifying the formula $\phi$ by
+assuming that the domain $\Delta$ is empty. Informally, if there is a predicate
+$P$ in $\phi$ that has nothing to do with the domain $\Delta$, smoothing
+preserves all occurrences of $P$ even if all clauses with $P$ become vacuously
+satisfied. It is important to note that the approach presented in this section
+is not unique. We explain it via the example below.
 
 \begin{example}\label{example:basecasesmoothing}
-  Let $\phi$ be
+  Let $\phi$ be:
   \begin{align}
@@
   where $\Gamma' \subseteq \Gamma$ is a domain introduced by a compilation rule.
-  Note that, as a relation, $P \subseteq \Gamma \times \Gamma$.
-
-  Let us reason by hand about the model count of $\phi$ when
-  $\Delta = \emptyset$. Predicate $Q$ can only take one value, i.e.,
-  $Q = \emptyset$. The value of $P$ is fixed over $\Gamma' \times \Gamma'$ by
-  \cref{eq:example2} but is allowed to vary freely over
+  It should be noted that $P$, as a relation, is a subset of
+  $\Gamma \times \Gamma$.
+
+  Now, let us reason manually about the model count of $\phi$ when
+  $\Delta = \emptyset$. Predicate $Q$ can only take one value, $Q = \emptyset$.
+  The value of $P$ is fixed over $\Gamma' \times \Gamma'$ by \cref{eq:example2},
+  but it is allowed to vary freely over
   $(\Gamma \times \Gamma) \setminus (\Gamma' \times \Gamma')$ since
-  \cref{eq:example1} is vacuously satisfied by all structures. Hence, the right
-  model count should be $2^{|\Gamma|^2 - |\Gamma'|^2}$.
+  \cref{eq:example1} is vacuously satisfied by all structures. Therefore, the
+  correct WFOMC should be $2^{|\Gamma|^2 - |\Gamma'|^2}$.
 
   However, without \cref{line:smoothing2}, \Propagate would simplify $\phi$ to
-  $\forall y, z \in \Gamma'\text{. }P(y, z)$. Here, $P$ is defined as a subset
-  of $\Gamma' \times \Gamma'$. Clearly, this simplified formula has only one
-  model: $\{\, P(y, z) \mid y, z \in \Gamma' \,\}$.
-
-  With \cref{line:smoothing2} included, $\phi$ is transformed to
+  $\forall y, z \in \Gamma'\text{. }P(y, z)$. In this case, $P$ is a subset of
+  $\Gamma' \times \Gamma'$. This simplified formula has only one model:
+  $\{\, P(y, z) \mid y, z \in \Gamma' \,\}$.
+
+  By including \cref{line:smoothing2}, \Propagate transforms $\phi$ to:
   \begin{gather*}
@@
 
-Note that the choice of $l$ on \cref{line:smoothing1} of \cref{alg:propagate} is
-inconsequential because any choice achieves the same goal: constructing a
-tautological clause that retains the literals in $C'$.
+It is worth mentioning that the choice of $l$ on \cref{line:smoothing1} of
+\cref{alg:propagate} is inconsequential because any choice achieves the same
+goal: constructing a tautological clause that retains the literals in $C'$.
 
@@
 
-Smoothing is a two-step process. First, positive unit clauses (denoting sets of
-ground atoms that are accounted for in the FCG) are propagated `upwards', i.e.,
-in the opposite direction of FCG arcs. Then, at nodes of certain types, missing
-atoms are detected and additional nodes are added to account for them. In this
-section, we:
+Smoothing is a two-step process that involves propagating unit clauses upwards
+(i.e., in the opposite direction of FCG arcs) and adding smoothing nodes to
+account for missing atoms. In this section, we will
 \begin{enumerate*}[label=(\roman*)]
   \item describe the relevant node types from previous work,
-  \item show how smoothing ought to work for these node types, and
-  \item illustrate how the new smoothing techniques work on two example FCGs.
-\end{enumerate*}
-
-Before describing the proposed changes to smoothing, we briefly review the
-compilation rules (and their corresponding node types) introduced by Dilkas and
-Belle~\shortcite{DBLP:conf/kr/DilkasB23} while referring to the aforementioned
-paper for precise definitions. \emph{Domain recursion} selects a domain
-$\Delta$, introduces a new constant $c \in \Delta$, and, for each variable $x$
-quantified over $\Delta$, considers two possibilities: $x = c$ or $x \ne c$,
-modifying the formula accordingly. We denote the resulting node as
-$\DR(c \in \Delta)$. \emph{Constraint removal} applies to formulas such that,
-for some domain $\Delta$, each variable $x$ quantified over $\Delta$ is followed
-by the inequality constraint $x \ne c$. In other words, the relevant clauses can
-be rewritten to begin with $\forall x \in \Delta\text{.
-}x \ne c \Rightarrow \ldots$ For such formulas, constraint removal replaces
-$\Delta$ with a new domain $\Delta'$ and removes the $x \ne c$ constraints. We
-denote the resulting node as $\CR(\Delta' \gets \Delta \setminus \{\,c\,\})$.
-Finally, \emph{caching} detects when the input formula $\phi$ is equal to a
-previously-encountered formula $\psi$ except for having different domains. We
-denote the resulting node as $\Reff(\sigma)$, where $\sigma$ is the substitution
-mapping the domains of $\psi$ to their corresponding domains in $\phi$.
+  \item explain how smoothing should work for these node types, and
+  \item demonstrate the new smoothing techniques using two example FCGs.
+\end{enumerate*}
+
+Before discussing the proposed changes to smoothing, let us briefly review the
+compilation rules and their corresponding node types introduced by Dilkas and
+Belle~\shortcite{DBLP:conf/kr/DilkasB23}. \emph{Domain recursion} involves
+selecting a domain $\Delta$, introducing a new constant $c \in \Delta$, and
+modifying the formula based on two possibilities for each variable $x$
+quantified over $\Delta$: $x = c$ or $x \ne c$. The resulting node is denoted as
+$\DR(c \in \Delta)$. \emph{Constraint removal} applies to formulas where each
+variable $x$ quantified over a domain $\Delta$ is followed by the inequality
+constraint $x \ne c$. These formulas can be rewritten so that each clause begins
+with $\forall x \in \Delta\text{. }x \ne c \Rightarrow \ldots$ Constraint
+removal replaces $\Delta$ with a new domain $\Delta'$ and removes the $x \ne c$
+constraints. The resulting node is denoted as
+$\CR(\Delta' \gets \Delta \setminus \{\,c\,\})$. Finally, \emph{caching} detects
+when the input formula $\phi$ is equal to a previously encountered formula
+$\psi$ except for having different domains. The resulting node is denoted as
+$\Reff(\sigma)$, with $\sigma$ representing the substitution mapping the domains
+of $\psi$ to their corresponding domains in $\phi$.
 
 \paragraph{Stage~1 for Domain Recursion}
-When visiting a $\DR(c \in \Delta)$ node, for each unit clause received from the
-child node, we replace each occurrence of $\phi(c)$ or
-$\forall x \in \Delta\text{. } x \ne c \Rightarrow \phi(x)$ with
-$\forall x \in \Delta\text{. }\phi(x)$. In other words, if the subgraph below
-the domain recursion node covers some of the ground atoms that are affected by
-domain recursion, then it should cover all of them. If the relevant subgraph
-indeed covers those ground atoms, Stage~2 will do nothing. Otherwise, smoothing
-nodes will be added below the domain recursion node to cover the difference
-between the sets of ground atoms assigned to the domain recursion node and its
-child node.
+When visiting a $\DR(c \in \Delta)$ node, we replace each occurrence of
+$\phi(c)$ or $\forall x \in \Delta\text{. } x \ne c \Rightarrow \phi(x)$ with
+$\forall x \in \Delta\text{. }\phi(x)$ for each unit clause received from the
+child node. This way, we ensure that if the subgraph below the domain recursion
+node covers some of the ground atoms affected by domain recursion, it covers all
+of them. If the relevant subgraph already covers those ground atoms, Stage~2
+will not make any changes. Otherwise, smoothing nodes will be added below the
+domain recursion node to account for the difference in the sets of ground atoms
+assigned to the domain recursion node and its child node.
 
@@
 When visiting a $\CR(\Delta' \gets \Delta \setminus \{\,c\,\})$ node, we reverse
-constraint removal. In other words, we replace each
-$\forall x \in \Delta'\text{. }\phi(x)$ with $\forall x \in \Delta\text{.
-}x \ne c \Rightarrow \phi(x)$. When visiting a $\Reff(\sigma)$ node, we apply
-substitution $\sigma$ to the unit clauses coming from the child node.
+constraint removal by replacing each $\forall x \in \Delta'\text{. }\phi(x)$
+with $\forall x \in \Delta\text{. }x \ne c \Rightarrow \phi(x)$. When visiting a
+$\Reff(\sigma)$ node, we apply the substitution $\sigma$ to the unit clauses
+from the child node.
 
 \paragraph{Stage~2 for Domain Recursion}
-We need not add smoothing nodes immediately below constraint removal or caching
-nodes. However, for domain recursion we do the following.
+We do not need to add smoothing nodes immediately below constraint removal or
+caching nodes. However, for domain recursion, we follow a specific process.
 \begin{enumerate}
-  \item Suppose the set of unit clauses assigned to the child node during
-        Stage~1 contains both $\phi(c)$ and $\forall x \in \Delta\text{.
-        } x \ne c \Rightarrow \phi(x)$. In other words, the only difference
-        between the two clauses is that one has the constant $c$ whereas the
-        other one has a variable $x \ne c$. In such a case, we merge the two
-        clauses into $\forall x \in \Delta\text{. }\phi(x)$.
+  \item If the set of unit clauses assigned to the child node during Stage~1
+        contains both $\phi(c)$ and $\forall x \in \Delta\text{.
+        } x \ne c \Rightarrow \phi(x)$, we merge the two clauses into
+        $\forall x \in \Delta\text{. }\phi(x)$. The only difference between
+        these two clauses is that one has the constant $c$ while the other has a
+        variable $x \ne c$.
   \item If necessary, we add smoothing nodes below the domain recursion node to
-        cover the difference between the unit clauses assigned to the domain
-        recursion node during Stage~1 and the unit clauses of the child node
-        post-processed by the step above.
+        account for the difference between the unit clauses assigned to the
+        domain recursion node during Stage~1 and the unit clauses of the child
+        node post-processed by the step above.
 \end{enumerate}
@@
   \end{forest}
-  \caption{An artificial example of an FCG where a smoothing node must be added
-    below a domain recursion node. The dashed nodes and arcs are added during
-    Stage~2 of smoothing.}\label{fig:smoothing2}
+  \caption{An artificial example of an FCG where a smoothing node needs to be
+    added below a domain recursion node. The dashed nodes and arcs are added
+    during Stage~2 of smoothing.}\label{fig:smoothing2}
 \end{figure}
 
-\begin{example}[An FCG that needs smoothing]
-  \Cref{fig:smoothing2} shows an FCG with a domain recursion node
-  $\DR(c \in \Delta)$ immediately followed by a single $P(c)$ node. In this
-  case, Stage~1 of smoothing assigns $\{\, \forall x \in \Delta\text{.
-  }P(x) \,\}$ to the former node and $\{\, P(c) \,\}$ to the latter. Since these
-  two sets of unit clauses cover different ground atoms, Stage~2 adds a
-  smoothing node to cover $P(x)$ for all $x \in \Delta \setminus \{\, c \,\}$.
+\begin{example}[An FCG that requires smoothing]
+  \Cref{fig:smoothing2} depicts an FCG with a domain recursion node
+  $\DR(c \in \Delta)$ followed directly by a single $P(c)$ node. In this
+  scenario, Stage~1 assigns $\{\, \forall x \in \Delta\text{. }P(x) \,\}$ to the
+  former node and $\{\, P(c) \,\}$ to the latter. As these two sets of unit
+  clauses cover different ground atoms, Stage~2 adds a smoothing node to address
+  $P(x)$ for all $x \in \Delta \setminus \{\, c \,\}$.
 \end{example}
@@
   \end{forest}
-  \caption{A smooth FCG based on \cref{example:overall}. The arc from the
-    caching node to the domain recursion node is omitted for compactness. The
-    labels next to nodes show the sets of unit clauses assigned to each node
-    during Stage~1 and the order of these assignments, omitting empty
-    assignments that replace a set $S$ with $S$ itself.}\label{fig:smoothing1}
+  \caption{A smooth FCG based on \cref{example:overall}. For compactness, the
+    arc between the caching node and the domain recursion node is not shown. The
+    labels next to the nodes indicate the sets of unit clauses assigned to each
+    node during Stage~1 and the order in which these assignments were made.
+    Empty assignments that replace a set $S$ with $S$ itself are not
+    included.}\label{fig:smoothing1}
 \end{figure}
@@
 \begin{example}[A smooth FCG]\label{example:smooth}
-  Stage~1 of smoothing is more involved in the case of the FCG in
-  \cref{fig:smoothing1}. The unit clause $P(c)$ propagates to the conjunction
+  Stage~1 of the smoothing process is more complex in the case of the FCG shown
+  in \cref{fig:smoothing1}. The unit clause $P(c)$ propagates to the conjunction
   node and is then generalised to $\forall x \in \Delta\text{. }P(x)$ by the
-  domain recursion node. It then propagates to the caching node, changing form
-  to $(\forall x \in \Delta\text{.
+  domain recursion node. It continues to propagate to the caching node, changing
+  its form to $(\forall x \in \Delta\text{.
   }P(x))[\Delta \mapsto \Delta'] \equiv \forall x \in \Delta'\text{. }P(x)$. The
   constraint removal node re-introduces the constraints, transforming the clause
-  to $\forall x \in \Delta\text{. }x \ne c \Rightarrow P(x)$, which is then
-  propagated to the conjunction node, joining $P(c)$.
-
-  In Stage~2, $P(c)$ and $\forall x \in \Delta\text{. }x \ne c \Rightarrow P(x)$
-  are merged into $\forall x \in \Delta\text{. }P(x)$. Since the resulting
-  clause matches the clause assigned to the domain recursion node, the FCG is
-  already smooth.
+  to $\forall x \in \Delta\text{. }x \ne c \Rightarrow P(x)$, which then
+  propagates to the conjunction node, joining $P(c)$.
+
+  During Stage~2, $P(c)$ and $\forall x \in \Delta\text{.
+  }x \ne c \Rightarrow P(x)$ are combined into $\forall x \in \Delta\text{.
+  }P(x)$. Since the resulting clause matches the clause assigned to the domain
+  recursion node, the FCG is already smooth.
 \end{example}
@@
 The algebraic interpretation of \cref{fig:smoothing1} is an equation $e$ that
-defines a recursive function. The right-hand side of $e$ already covers $P(c)$,
-and the smoothing algorithm correctly recognises that the recursive call also
-covers $P(x)$ for all $x \in \Delta \setminus \{\, c \,\}$.
+defines a recursive function. The right-hand side of $e$ already encompasses
+$P(c)$, and the smoothing algorithm correctly recognises that the recursive call
+also encompasses $P(x)$ for all $x \in \Delta \setminus \{\, c \,\}$.
 
@@
 
-In this section, we describe the last step of \Cranetwo{} outlined in
-\cref{fig:overview}: translating the set of equations $\mathcal{E}$ produced by
-\CompileWithBaseCases into C++ code. The produced C++ program can then be
-compiled and executed with different command-line arguments to compute the model
-count of the formula for different (combinations of) domain sizes.
-
-Each equation in $\mathcal{E}$ is compiled into a C++ function, together with
-its own cache for memoisation. Let
-$e = (f(\mathbf{x}) = \expr{}) \in \mathcal{E}$ be an arbitrary equation, and
-let $\mathbf{c} \in \mathbb{N}_{0}^{n}$ represent the arguments of the
-corresponding C++ function. The implementation of $e$ consists of three parts.
-First, we check whether $\mathbf{c}$ is already in the cache of $e$ (in which
-case the cached value is returned). Second, for each base case $f(\mathbf{y})$
-of $f(\mathbf{x})$ (as in \cref{def:basecase}), we check whether $\mathbf{c}$
+In this section, we will describe the final step of \Cranetwo{} as outlined in
+\cref{fig:overview}. This step involves translating the set of equations
+$\mathcal{E}$ into C++ code. The resulting C++ program can then be compiled and
+executed with different command-line arguments to compute the model count of the
+formula for various domain sizes.
+
+Each equation in $\mathcal{E}$ is compiled into a C++ function, along with a
+separate cache for memoisation. Let us consider an arbitrary equation
+$e = (f(\mathbf{x}) = \expr{}) \in \mathcal{E}$, and let
+$\mathbf{c} \in \mathbb{N}_{0}^{n}$ represent the arguments of the corresponding
+C++ function. The implementation of $e$ consists of three parts. First, we check
+if $\mathbf{c}$ is already present in the cache of $e$. If it is, we simply
+return the cached value. Second, for each base case $f(\mathbf{y})$ of
+$f(\mathbf{x})$ (as defined in \cref{def:basecase}), we check if $\mathbf{c}$
 \emph{matches} $\mathbf{y}$, i.e., $c_{i} = y_{i}$ whenever
-$y_{i} \in \mathbb{N}_{0}$. In this case, $\mathbf{c}$ is redirected to the C++
-function that corresponds to the definition of base case $f(\mathbf{y})$.
-Finally, if the above cases fail, we evaluate $\mathbf{c}$ according to
-$\expr{}$, store the result in the cache, and return it.
+$y_{i} \in \mathbb{N}_{0}$. If this condition is satisfied, $\mathbf{c}$ is
+redirected to the C++ function that corresponds to the definition of the base
+case $f(\mathbf{y})$. Finally, if none of the above cases apply, we evaluate
+$\mathbf{c}$ based on the expression $\expr{}$, store the result in the cache,
+and return it.
 
@@
 
-TODO: Introduce greedy search and breadth-first search (BFS), together with
-\Cranegreedy{} and \Cranebfs{}. The knowledge compilation part of both
-\textsc{Crane} and \Cranetwo{} can be executed using either greedy (similar to
-\textsc{ForcLift}) or breadth-first search. We use both in our experiments,
-denoting them as \Cranegreedy{} and \Cranebfs{}, respectively.
-
-We compare \Cranetwo{} (in both BFS and greedy modes) with \textsc{FastWFOMC}
-and \textsc{ForcLift} on two problems previously considered by Dilkas and
-Belle~\shortcite{DBLP:conf/kr/DilkasB23}: the function-counting problem from
-\cref{example:functions} and the bijection-counting problem described below.
-Note that comparing \Cranetwo{} and \textsc{FastWFOMC} on a larger set of
+We compared \Cranetwo{}\footnote{\textsc{Crane} has two modes that decide how
+  compilation rules are applied to formulas: one that uses greedy search and
+  another that combines greedy and breadth-first search. In our experiments, we
+  refer to these modes as \Cranegreedy{} and \Cranebfs{}, respectively.} with
+\textsc{FastWFOMC} and \textsc{ForcLift} on two problems previously considered
+by Dilkas and Belle~\shortcite{DBLP:conf/kr/DilkasB23}. The first problem is the
+function-counting problem from \cref{example:functions}, and the second problem
+is the bijection-counting problem described below. It is important to note that
+comparing \Cranetwo{} and \textsc{FastWFOMC} on a more substantial set of
 benchmarks is challenging because there is no automated way to translate a
-formula in \FO{} or \Ctwo{} into \UFO{} (or even check if such an encoding is
-possible). The experiments were run on an AMD~Ryzen~7~5800H processor with
+formula in \FO{} or \Ctwo{} into \UFO{}, or even check if such an encoding is
+possible. We ran the experiments on an AMD~Ryzen~7~5800H processor with
 \SI{16}{\gibi\byte} of memory and Arch Linux~6.8.2-arch2-1 operating system.
@@
   \input{plot}
-  \caption{The runtime of WFOMC algorithms. Note that the $y$ axis is on a
+  \caption{The running time of WFOMC algorithms. Note that the $y$-axis is on a
     logarithmic scale.}\label{fig:plot}
@@
 
-In the first experiment, we run each of the four algorithms once on each
-combination of benchmark and domain size, the latter ranging from one up to and
-including 35. \Cref{fig:plot} shows total runtime values as a measure of the
-overall performance of each algorithm. For the three knowledge compilation
-algorithms, we also separately track compilation and inference times and comment
-on them where relevant. Note that \Cranebfs{} is able to handle more instances
-than either \textsc{ForcLift} or \Cranegreedy{}, i.e., the bijection-counting
-problem in our experiments as well as similar formulas examined
-previously~\cite{DBLP:conf/kr/DilkasB23}.
+In the first experiment, we ran each of the four algorithms once on each
+combination of benchmark and domain size, ranging from one up to and including
+35. \Cref{fig:plot} shows the total runtime values as a measure of the overall
+performance of each algorithm. We also separately tracked compilation and
+inference times and commented on them where relevant. It is worth noting that
+\Cranebfs{} can handle more instances than either \textsc{ForcLift} or
+\Cranegreedy{}, including the bijection-counting problem in our experiments as
+well as similar formulas examined previously~\cite{DBLP:conf/kr/DilkasB23}.
 
 As shown in \cref{fig:plot}, the runtimes of all compilation-based algorithms
-remain practically constant in contrast to the rapidly increasing runtimes of
+remained practically constant, in contrast to the rapidly increasing runtimes of
 \textsc{FastWFOMC}. Although the search/compilation part is slower in
 \Cranetwo{} than in \textsc{ForcLift}, the difference is negligible. The
-runtimes of the knowledge compilation algorithms appear constant because---for
-these counting problems and domain sizes---compilation time dominates inference
-time (recall that compilation time is independent of domain sizes). Indeed, the
-maximum inference time of both \Cranebfs{} and \Cranegreedy{} across these
+runtimes of the knowledge compilation algorithms appear constant because, for
+these counting problems and domain sizes, compilation time dominates inference
+time (remember that compilation time is independent of domain sizes). Indeed,
+the maximum inference time of \Cranebfs{} and \Cranegreedy{} across these
 experiments is only \SI{4}{\milli\second}. The runtimes of \Cranetwo{} have
-lower variation than those of \textsc{ForcLift} because with \textsc{ForcLift}
-we compile the formula anew for each domain size whereas with \Cranetwo{} we
+lower variation than those of \textsc{ForcLift} because we compile the formula
+anew for each domain size with \textsc{ForcLift}, whereas with \Cranetwo{}, we
 compile it once and reuse the resulting C++ program for all domain sizes.
@@
   \end{tabular}
-  \caption{The maximum domain sizes that can be handled by each algorithm in at
-    most \SI{45}{\second}. `---' indicates that the algorithm is unable to find
-    a solution. The domain sizes for \Cranetwo{} are accurate up to the first
-    digit while other domain sizes are exact.}\label{table:results}
+  \caption{The maximum domain sizes that each algorithm can handle within
+    \SI{45}{\second}. A dash symbol `---' indicates that the algorithm was
+    unable to find a solution. The domain sizes for \Cranetwo{} are accurate up
+    to the first digit, while the domain sizes for the other domain sizes are
+    exact.}\label{table:results}
 \end{table}
 
-For the second experiment, we examine the maximum domain size that the
-algorithms can handle in at most \SI{45}{\second} of total runtime. As shown in
-\cref{table:results}, \Cranebfs{} is able to scale to domain sizes \num{357} and
-\num{9375} times larger than \textsc{FastWFOMC} for bijection-counting and
-function-counting problems, respectively. Note that, while \textsc{ForcLift} may
-have runtime performance comparable to \Cranetwo{}, its finite-precision
-arithmetic cannot represent model counts for domain sizes higher than 143 and
-returns $\infty$ instead.
-
-\section{Conclusion}
-
-TODO
+For the second experiment, we examined the maximum domain size the algorithms
+can handle in at most \SI{45}{\second} of total runtime. As shown in
+\cref{table:results}, \Cranebfs{} can scale to domain sizes \num{357} and
+\num{9375} times larger than \textsc{FastWFOMC} for the bijection-counting and
+function-counting problems, respectively. It is important to note that while
+\textsc{ForcLift} may have runtime performance comparable to \Cranetwo{}, its
+finite-precision arithmetic cannot represent model counts for domain sizes
+greater than 143 and returns $\infty$ instead.
+
+\section{Conclusion and Future Work}
+
+In this work, we have presented several contributions. First, we have developed
+algorithmic techniques to find the base cases of recursive functions generated
+by the original \textsc{Crane} algorithm. Second, we have extended the smoothing
+procedure of \textsc{ForcLift} and \textsc{Crane} to support base case formulas
+and the compilation rules introduced by Dilkas and
+Belle~\shortcite{DBLP:conf/kr/DilkasB23}. Third, we have proposed an approach to
+compile function definitions into C++ programs with support for
+arbitrary-precision arithmetic. Lastly, we have provided experimental evidence
+demonstrating that \Cranetwo{} can scale to much larger domain sizes than
+\textsc{FastWFOMC} while handling more formulas than \textsc{ForcLift}.
+
+There are many potential avenues for future work. Specifically, a more thorough
+experimental study is needed to understand how WFOMC algorithms compare in terms
+of their ability to handle different formulas and their scalability with respect
+to domain size. Additionally, further characterisation of the capabilities of
+\Cranetwo{} can be explored. For example, \emph{completeness} could be proven
+for a fragment of first-order logic such as \Ctwo{} (using a suitable encoding
+of counting quantifiers). Moreover, the efficiency of a WFOMC algorithm in
+handling a particular formula can be assessed using \emph{fine-grained
+  complexity}. In the case of \textsc{Crane} and \Cranetwo{}, this can be done
+by analysing the equations~\cite{DBLP:conf/kr/DilkasB23}. By doing so,
+efficiency can be reasoned about in a more implementation-independent manner by
+making claims about the maximum degree of the polynomial that characterises any
+given solution.
 

### 2024-04-30 lib/FastWFOMC.jl/snippets/sample.jl
New version of FastWFOMC

@@ -1,0 +1,33 @@
+# using Pkg
+
+# # Use current folder as a Julia project
+# Pkg.activate("."; io=devnull)
+
+# # Add FastWFOMC.jl dependency to the current Julia project
+# Pkg.add(PackageSpec(url="https://github.com/jan-toth/FastWFOMC.jl"))
+
+# # Install all dependencies that might be missing
+# Pkg.instantiate()
+
+# using FastWFOMC
+
+# open(ARGS[1]) do fr
+#     for line in readlines(fr)
+#         startswith(line, '#') && continue
+#         cell_graph = get_cell_graph(line)
+#         println(cell_graph)
+#     end
+# end
+
+
+
+
+# Command to run Julia with the new sysimage
+# $ julia --sysimage "bin/FWFOMC_$(VERSION).so"
+
+using .FastWFOMC
+
+# "~B0(x, y) | S0(x)"
+sentence = ARGS[1]
+cell_graph = get_cell_graph(sentence)
+println(cell_graph)

### 2024-04-30 lib/FastWFOMC.jl/snippets/sample_multithreaded_unskolemized.jl

@@ -1,0 +1,30 @@
+using Pkg
+using Base.Threads
+
+Pkg.activate("."; io=devnull)
+using FastWFOMC
+
+function process_sentences(file=ARGS[1])
+    lines = String[]
+    open(file) do fr
+        append!(lines, readlines(fr))
+    end
+
+    sentences = fill("#", length(lines))
+
+    Threads.@threads for i in eachindex(lines)
+        line = lines[i]
+        startswith(line, '#') && continue
+        sentences[i] = get_condensed_cell_graph_unskolemized(line)
+    end
+
+    for sentence in sentences
+        startswith(sentence, '#') && continue
+        println(sentence)
+    end
+end
+
+process_sentences()
+
+
+

### 2024-04-30 lib/FastWFOMC.jl/src/FastWFOMC.jl

@@ -1,0 +1,31 @@
+module FastWFOMC
+
+using LightGraphs
+using Nemo
+using Pkg
+using TOML 
+
+
+import LinearAlgebra
+
+include("utils/utils.jl")
+using .utils
+
+export compute_wfomc, compute_wfomc_unskolemized, WFOMCWeights, CardinalityConstraint
+export NoOptFastWFOMCAlgorithm, FastWFOMCAlgorithm
+export fill_missing_weights!
+export Formula, parse_formula, is_satisfiable
+export get_cell_graph, get_cell_graph_unskolemized, get_condensed_cell_graph_unskolemized, get_skolemized_formula
+
+include("logic/logic.jl")
+include("logic/reductions.jl")
+include("types/types.jl")
+include("cells.jl")
+include("wmc.jl")
+include("algorithm.jl")
+
+function get_version()
+    return TOML.parsefile(joinpath(dirname(@__DIR__), "Project.toml"))["version"]
+end
+
+end # module

### 2024-04-30 lib/FastWFOMC.jl/src/algorithm.jl

@@ -1,0 +1,284 @@
+"""All algorithms for WFOMC should subtype this."""
+abstract type WFOMCAlgorithm end
+
+"""Algorithm for WFOMC computation that sets I₁ = I₂ = ∅."""
+struct NoOptFastWFOMCAlgorithm <: WFOMCAlgorithm end
+
+"""Algorithm for WFOMC computation using all optimizations."""
+struct FastWFOMCAlgorithm <: WFOMCAlgorithm end
+
+
+
+function compute_wfomc_unskolemized(ψ::AbstractString, domainsize::Integer, weights=WFOMCWeights(); ccs=CardinalityConstraint[])
+    Γ, weights, cc_templates, denom_templates, ks = skolemize_theory(ψ, weights)
+
+    for k in ks
+        k > domainsize && return zero(weights)
+    end
+    weights = WFOMCWeights{Rational{BigInt}}(weights)
+
+    for cct in cc_templates
+        push!(ccs, cct(domainsize))
+    end
+
+    denominator = big"1"//1
+    for divt in denom_templates
+        denominator *= divt(domainsize)
+    end
+
+    ψ = reduce(&, Γ)
+    fill_missing_weights!(weights, ψ)
+
+    wfomc = compute_wfomc(ψ, domainsize, weights; ccs)
+    return wfomc // denominator
+end
+
+"""
+    compute_wfomc(ψ::Formula, domainsize::Integer [, weights::WFOMCWeights]; kwargs...)
+
+Compute weighted first order model count (WFOMC).
+
+If `weights` are not provided, they are all set to `1`.
+`kwargs` may specify special predicates or change the computation's behavior in some way:
+1. `algo` - algorithm to be used.
+2. `ccs` - list of cardinality constraints for some of the predicates in the formula `ψ`.
+"""
+function compute_wfomc(ψ::Formula, domainsize::Integer, weights::WFOMCWeights; kwargs...)
+    props = filter(x -> x[2] == 0, predicate_symbols(ψ))
+    length(props) == 0 && return _compute_wfomc_once(ψ, domainsize, weights; kwargs...)
+
+    total = zero(weights)
+    # TODO multithreading
+    for valuation in Iterators.product(ntuple(i -> (TRUE, FALSE), length(props))...)
+        subs = Dict(pred => val for (pred, val) in zip(props, valuation))
+        
[…]

### 2024-04-30 lib/FastWFOMC.jl/src/cells.jl

@@ -1,0 +1,645 @@
+"""
+    Cell
+
+A maximally consistent conjunction of unary and binary reflexive predicates.
+"""
+struct Cell
+    interpretation::BitVector
+    atoms::Vector{Formula}
+
+    function Cell(interpretation::BitVector, atoms::Vector{Formula})
+        length(interpretation) == length(atoms) || throw(ArgumentError("The lifted interpretation and the atom list must be of the same length."))
+        new(interpretation, atoms)
+    end
+end
+
+Cell(interpretation::Vector{Integer}, atoms::Vector{Formula}) = Cell(convert(BitVector, interpretation), atoms)
+
+Base.convert(::Type{Cell}, cell::Cell) = cell
+Base.convert(::Type{Formula}, cell::Cell) = reduce(&, _generate_literals(cell))
+Base.promote_rule(::Type{Formula}, ::Type{Cell}) = Formula
+Base.show(io::IO, cell::Cell) = print(io, join(_generate_literals(cell), " ∧ "))
+
+Base.:&(lhs::Formula, rhs::Cell) = Formula("&", lhs, convert(Formula, rhs))
+Base.:&(lhs::Cell, rhs::Formula) = Formula("&", convert(Formula, lhs), rhs)
+
+function _generate_literals(cell::Cell)
+    return (truthvalue ? atom : ~atom for (truthvalue, atom) in zip(cell.interpretation, cell.atoms))
+end
+
+"""
+    build_cells(ψ::Formula)
+
+Naively build all cells of the formula `ψ` for variable `x`.
+
+If there are `p` distict predicate symbols in `ψ`, there are `2ᵖ` cells.
+"""
+function build_cells(ψ::Formula)
+    atoms = substitute(Dict(Variable("y") => Variable("x")), ψ) |> proposition_symbols |> collect
+    p = length(atoms)
+
+    n = 2^p
+    cells = Vector{Cell}(undef, n)
+    
+    for (i, rank) in enumerate(0:n-1)
+        interpretation = BitVector(undef, p)
+        for j in 1:p
+            interpretation[j] = (rank & (1 << (j - 1))) > 0
+        end
+
+        cells[i] = Cell(interpretation, atoms)
+    end
+
+    return cells
+end
+
+
+"""
+    build_valid_cells(ψ::Formula)
+
+Build valid cells (1-types) of the formula `ψ` for variable `x`.
+
[…]

### 2024-04-30 lib/FastWFOMC.jl/test/aimalogic.jl

@@ -1,0 +1,313 @@
+using FastWFOMC.aimalogic
+import FastWFOMC.aimalogic: wumpus_world_inference, horn_clauses_kb, test_fol_kb, crime_kb
+
+x = Expression("x");
+
+y = Expression("y");
+
+z = Expression("z");
+
+@test variables(expr("F(x, x) & G(x, y) & H(y, z) & R(A, z, z)")) == Set([x, y, z]);
+
+@test variables(expr("F(x, A, y)")) == Set([x, y]);
+
+@test variables(expr("F(G(x), z)")) == Set([x, z]);
+
+@test show(expr("P & Q ==> Q")) == "((P & Q) ==> Q)";
+
+@test show(expr("P ==> Q(1)")) == "(P ==> Q(1))";
+
+@test show(expr("P & Q | ~R(x, F(x))")) == "((P & Q) | ~(R(x, F(x))))";
+
+@test show(expr("P & Q ==> R & S")) == "(((P & Q) ==> R) & S)";
+
+@test tt_entails(expr("P & Q"), expr("Q")) == true;
+
+@test tt_entails(expr("P | Q"), expr("Q")) == false;
+
+@test tt_entails(expr("A & (B | C) & E & F & ~(P | Q)"), expr("A & E & F & ~P & ~Q")) == true;
+
+@test proposition_symbols(expr("x & y & z | A")) == Set([Expression("A")]);
+
+@test proposition_symbols(expr("(x & B(z)) ==> Farmer(y) | A")) == Set([Expression("A"), expr("Farmer(y)"), expr("B(z)")]);
+
+@test tt_true("(P ==> Q) <=> (~P | Q)") == true;
+
+@test typeof(pl_true(Expression("P"))) <: Nothing;
+
+@test typeof(pl_true(expr("P | P"))) <: Nothing;
+
+@test pl_true(expr("P | Q"), model = Dict([Pair(Expression("P"), true)])) == true;
+
+@test pl_true(expr("(A | B) & (C | D)"),
+    model = Dict([Pair(Expression("A"), false),
+        Pair(Expression("B"), true),
+        Pair(Expression("C"), true)])) == true;
+
+@test pl_true(expr("(A & B) & (C | D)"),
+    model = Dict([Pair(Expression("A"), false),
+        Pair(Expression("B"), true),
+        Pair(Expression("C"), true)])) == false;
+
+@test pl_true(expr("(A & B) | (A & C)"),
+    model = Dict([Pair(Expression("A"), false),
[…]

### 2024-04-30 lib/FastWFOMC.jl/test/ccs/three_regular_graphs.jl

@@ -1,0 +1,69 @@
+ψ = parse_formula(
+    "~E(x, x) & " *
+    "(~E(x, y) | E(y, x)) & " *
+    "(~F(x, y) | E(x, y)) & " *
+    "(F(x, y) | ~E(x, y)) & " *
+    "(S1(x) | ~F1(x, y)) & " *
+    "(S2(x) | ~F2(x, y)) & " *
+    "(S3(x) | ~F3(x, y)) & " *
+    "(~F(x, y) | F1(x, y) | F2(x, y) | F3(x, y)) & " *
+    "(F(x, y) | ~F1(x, y)) & " *
+    "(F(x, y) | ~F2(x, y)) & " *
+    "(F(x, y) | ~F3(x, y)) & " *
+    "(~F1(x, y) | ~F2(x, y)) & " *
+    "(~F1(x, y) | ~F3(x, y)) & " *
+    "(~F2(x, y) | ~F3(x, y))"
+)
+
+weights = WFOMCWeights{Rational{BigInt}}(("S1", 1) => (1, -1), ("S2", 1) => (1, -1), ("S3", 1) => (1, -1))
+fill_missing_weights!(weights, ψ)
+
+
+for n = 1:2:20
+    cc = CardinalityConstraint(("F", 2), 3 * n)
+    @test compute_wfomc(ψ, n, weights; ccs=[cc]) // big(6)^n == 0
+end
+
+n = 0
+cc = CardinalityConstraint(("F", 2), 3 * n)
+@test compute_wfomc(ψ, n, weights; ccs=[cc]) // big(6)^n == 1
+
+n = 2
+cc = CardinalityConstraint(("F", 2), 3 * n)
+@test compute_wfomc(ψ, n, weights; ccs=[cc]) // big(6)^n == 0
+
+n = 4
+cc = CardinalityConstraint(("F", 2), 3 * n)
+@test compute_wfomc(ψ, n, weights; ccs=[cc]) // big(6)^n == 1
+
+n = 6
+cc = CardinalityConstraint(("F", 2), 3 * n)
+@test compute_wfomc(ψ, n, weights; ccs=[cc]) // big(6)^n == 70
+
+n = 8
+cc = CardinalityConstraint(("F", 2), 3 * n)
+@test compute_wfomc(ψ, n, weights; ccs=[cc]) // big(6)^n == 19355
+
+n = 10
+cc = CardinalityConstraint(("F", 2), 3 * n)
[…]

### 2024-04-30 lib/FastWFOMC.jl/test/fast_wfomc/undirected_connected_graphs.jl

@@ -1,0 +1,161 @@
+# Γ = {
+#     ∀x ¬E(x, x),
+#     ∀x∀y E(x, y) ⟹ E(y, x),
+#     ∀x∃!y E(x, y)
+# }
+
+# ψ = expr(
+#     "~E(x, x) & " *
+#     "(~E(x, y) | E(y, x)) &" *
+#     "Z(x) &" *
+#     "(Z(x) | ~E(x, y)) &" *
+#     "(Z(x) | S(x)) &" *
+#     "(S(x) | ~E(x, y))"
+# )
+
+# eliminated Z(x) by unit propagation
+ψ = parse_formula(
+    "~E(x, x) & " *
+    "(~E(x, y) | E(y, x)) &" *
+    "(S(x) | ~E(x, y))"
+)
+
+# Results taken from https://oeis.org/A006129
+@testset "$(typeof(algo))" for algo in [NoOptFastWFOMCAlgorithm(), FastWFOMCAlgorithm()]
+    weights = WFOMCWeights{BigInt}(("S", 1) => (1, -1))
+    fill_missing_weights!(weights, ψ)
+    @test compute_wfomc(ψ, 0, weights; algo) == 1
+    @test compute_wfomc(ψ, 1, weights; algo) == 0
+    @test compute_wfomc(ψ, 2, weights; algo) == 1
+    @test compute_wfomc(ψ, 3, weights; algo) == 4
+    @test compute_wfomc(ψ, 4, weights; algo) == 41
+    @test compute_wfomc(ψ, 5, weights; algo) == 768
+    @test compute_wfomc(ψ, 6, weights; algo) == 27449
+    @test compute_wfomc(ψ, 7, weights; algo) == 1887284
+    @test compute_wfomc(ψ, 8, weights; algo) == 252522481
+    @test compute_wfomc(ψ, 9, weights; algo) == 66376424160
+    @test compute_wfomc(ψ, 10, weights; algo) == 34509011894545
+    @test compute_wfomc(ψ, 11, weights; algo) == 35645504882731588
+    @test compute_wfomc(ψ, 12, weights; algo) == 73356937912127722841
+    @test compute_wfomc(ψ, 13, weights; algo) == 301275024444053951967648
+    @test compute_wfomc(ψ, 14, weights; algo) == 2471655539737552842139838345
+    @test compute_wfomc(ψ, 15, weights; algo) == 40527712706903544101000417059892
+
[…]

### 2024-04-30 lib/FastWFOMC.jl/test/fast_wfomc/undirected_graphs.jl

@@ -1,0 +1,125 @@
+ψ = parse_formula(
+    "~E(x, x) & " *
+    "(~E(x, y) | E(y, x))"
+)
+
+# Results taken from https://oeis.org/A006125
+@testset "$(typeof(algo))" for algo in [NoOptFastWFOMCAlgorithm(), FastWFOMCAlgorithm()]
+    w = WFOMCWeights{Float64}()
+    fill_missing_weights!(w, ψ)
+    @test compute_wfomc(ψ, 0, w; algo) ≈ 1
+    @test compute_wfomc(ψ, 1, w; algo) ≈ 1
+    @test compute_wfomc(ψ, 2, w; algo) ≈ 2
+    @test compute_wfomc(ψ, 3, w; algo) ≈ 8
+    @test compute_wfomc(ψ, 4, w; algo) ≈ 64
+    @test compute_wfomc(ψ, 5, w; algo) ≈ 1024
+    @test compute_wfomc(ψ, 6, w; algo) ≈ 32768
+    @test compute_wfomc(ψ, 7, w; algo) ≈ 2097152
+    @test compute_wfomc(ψ, 8, w; algo) ≈ 268435456
+
+    w = WFOMCWeights{BigFloat}()
+    fill_missing_weights!(w, ψ)
+    @test compute_wfomc(ψ, 0, w; algo) ≈ 1
+    @test compute_wfomc(ψ, 1, w; algo) ≈ 1
+    @test compute_wfomc(ψ, 2, w; algo) ≈ 2
+    @test compute_wfomc(ψ, 3, w; algo) ≈ 8
+    @test compute_wfomc(ψ, 4, w; algo) ≈ 64
+    @test compute_wfomc(ψ, 5, w; algo) ≈ 1024
+    @test compute_wfomc(ψ, 6, w; algo) ≈ 32768
+    @test compute_wfomc(ψ, 7, w; algo) ≈ 2097152
+    @test compute_wfomc(ψ, 8, w; algo) ≈ 268435456
+    @test compute_wfomc(ψ, 9, w; algo) ≈ 68719476736
+    @test compute_wfomc(ψ, 10, w; algo) ≈ 35184372088832
+    @test compute_wfomc(ψ, 11, w; algo) ≈ 36028797018963968
+    @test compute_wfomc(ψ, 12, w; algo) ≈ 73786976294838206464
+    @test compute_wfomc(ψ, 13, w; algo) ≈ 302231454903657293676544
[…]

### 2024-04-30 lib/FastWFOMC.jl/test/runtests.jl

@@ -1,0 +1,38 @@
+using Test
+using FastWFOMC
+using Nemo
+
+@testset "FastWFOMC Tests" begin
+    @testset "AIMA logic" begin
+        include("aimalogic.jl")
+    end
+
+    @testset "Combinatorics" begin
+        include("combinatorics.jl")
+    end
+
+    @testset "Fast WFOMC" begin
+        @testset "Number of undirected graphs" begin
+            include("fast_wfomc/undirected_graphs.jl")
+        end
+    
+        @testset "Number of 4-colored graphs" begin
+            include("fast_wfomc/four_colored_graphs.jl")
+        end
+    
+        @testset "Number of connected undirected graphs" begin
+            include("fast_wfomc/undirected_connected_graphs.jl")
+        end
+
+        @testset "Miscellaneous" begin
+            include("fast_wfomc/misc.jl")
+        end
+    end
+
+    @testset "WFOMC with CCs" begin
+        # @testset "Number of three-regular graphs" begin
+        #     include("ccs/three_regular_graphs.jl")
+        # end
+        include("ccs/counting.jl")
+    end
+end

### 2024-06-30 doc/paper.tex
New version of FastWFOMC
Notes for improvement

@@
 meel@cs.toronto.edu
-}
+}% TODO: update affiliation and email
 
@@
 
+% TODO: No proper runtime consideration (other than the termination). (address
+% this criticism in some way)
+
+% TODO: Having an algorithm that can efficiently handle large domain sizes is
+% crucial in the weighted setting. For example, consider the well-known "friends
+% and smokers" Markov logic network [1]. The utility of such a model would be
+% significantly limited if exact probabilities could only be efficiently
+% computed for social networks of at most 30 people.
+% [1] Richardson, M., & Domingos, P. (2006). Markov logic networks. Machine learning, 62, 107-136.
+
+% TODO: somehow indicate that source code will be available (a redacted link?)
+
+% TODO: Updates to the algorithm
+% 1) replace x_i-c_i on Line 7 of Algorithm 2 with a generalisation of x_i that can be an arbitrary summation/subtraction of domain sizes
+% 2) a function call with a constant should always mean that that function should have a base case, not just when it's in the same function
+
 \section{Introduction}
+% TODO: improvements to the introduction (must):
+% * make it extra clear what the gap is that this work is trying to fill
+% * mention Crane earlier and describe its importance
+% * the last two paragraphs should make more of a BOOM (e.g., include the over 9k claim)
+% * (here and elsewhere) clarify the distinction between the weighted and unweighted variants of the problem in the final version of the paper.
+We focus on the unweighted variant in our implementation and experiments, however, Crane2 can handle WFOMC instances as well simply by switching the main data type from integers to rational numbers.
+Maybe add some weighted experiments as well.
 
@@
 upper/lower bound construction~\cite{DBLP:conf/ijcai/BremenK20}.
+% TODO: FCGs were never defined. Maybe avoid referring to them altogether?
+% Smoothing nodes are also undefined.
 
@@
 
+% TODO: first sentence: elaborate a bit more for a general audience
 The recently proposed \textsc{Crane} algorithm, while capable of handling
@@
 that addresses these two weaknesses.
+% TODO: We called the previous version of Crane "incomplete" because it cannot
+% be used as a black box that takes Markov logic networks (or weighted formulas
+% in some other format) and outputs numbers (i.e., model counts or
+% probabilities).
 
@@
 each of which is in \emph{prenex normal form}~\cite{hinman2018fundamentals}.
-
+% TODO: explain that "Skolemization" here is NOT standard Skolemization of
+% first-order logic, which would replace existential quantifiers by function
+% terms.
+
+% TODO: reorder the definitions in the opposite direction
 A \emph{formula} is a conjunction of clauses. A \emph{clause} is of the form
@@
 \subsection{WFOMC Algorithms and Their Logics}\label{sec:threelogics}
+
+% TODO: mention the Unique Name Assumption and that, hence, s = t holds iff s
+% and t are the same constant.
 
@@
 
+% TODO:
+% 1. Rename \UFO{} to what that new paper uses
+% 2. Use FastWFOMC.jl instead, removing the mention of 'privately-obtained'
+% 3. use symbols instead of numbers for the footnotes
 In \cref{tbl:logics}, we outline the differences among three first-order logics
@@
 formulas with more than two variables, and the equality predicate.
+% TODO: the discussion about sorts isn't featured in the rest of the paper
 
@@
 
+% TODO: The distinctness of domains is important in two ways. First, in terms of
+% expressiveness, writing clause such as "\forall x, P(x, x)" is valid if
+% predicate P is defined over two copies of the same domain and invalid
+% otherwise. Second, having more distinct domains makes the problem more
+% decomposable for the knowledge compilation algorithm. With more distinct
+% domains, it can make assumptions or deductions about, e.g., the first domain
+% of predicate P without worrying how (or if) they apply to the second domain.
 \begin{definition}[Model]\label{def:model}
@@
 \end{definition}
-
+% TODO: adding to what
+
+% TODO: “Weights in Q” undefined, C2 undefined (and also far from well explained
+% before), endofunction undefined (also endomorphisms missing), weight function
+% undefined, weighted model count imprecise (above it’s called weighted
+% first-order model count/wfmoc),
 \begin{definition}[WFOMC~\cite{DBLP:conf/ijcai/BroeckTMDR11}]
@@
   $w^{+}(P)$ and $w^{-}(P)$ be its \emph{weights} in $\mathbb{Q}$. Unless
-  specified otherwise, we assume all weights are equal to one. The
+  specified otherwise, we assume all weights are equal to 1. The
   \emph{(symmetric) weighted first-order model count} (WFOMC) of $\phi$ (with
@@
 
+  % TODO: Yes, as mentioned at the end of Section 2.1, clauses c and d written
+  % on separate lines are to be interpreted as the conjunction of c and d (maybe
+  % move that sentence here?).
   Equivalently, in \FO{} we would write
@@
 \section{Completing the Definitions of Recursive Functions}\label{sec:main}
-
+% TODO: As mentioned in the caption of Figure 1, "Compile" refers to the
+% knowledge compilation algorithm of Dilkas and Belle (2023). Its three return
+% values are explained at the beginning of page 4. We do not elaborate on the
+% details of "Simplify" as it primarily consists of elementary algebraic
+% simplifications such as "1x = x" and "0x = 0". However, we highlight one
+% non-trivial aspect of "Simplify" right before Section 3.1. We will improve the
+% structure of Section 3 to make this information more readily available. Maybe
+% write Crane instead of Compile?
+
+% TODO: It would not be entirely accurate to call the algorithms presented in
+% this work a "post-processing step" because Algorithm 1 is recursive. In other
+% words, this "post-processing step" to first-order knowledge compilation can
+% lead to more compilation that then updates/completes the original set of
+% equations.
 \begin{algorithm}[t]
@@
 \end{algorithm}
+% TODO: >> Alg 1, line 5: Why is this not an infinite loop? On line 5 of
+% Algorithm 1, the loop iterates over the indices of \mathbf{x}. The arity of a
+% function is always a finite number, typically equal to 1 or 2.
 
@@
 
+% TODO: F missing (also not explained that it’s not needed below).
+E is not explained other than that we take the example from X.
+Would not be a problem if it is motivated differently and the focus is on post-processing (defining inputs properly) and not on the entire algorithm.
+% TODO: include a high-level overview of first-order knowledge compilation and the meaning of the resulting functions.
+For the most part, the compilation process that constructs these function definitions can be treated as a black box for the purposes of this work.
+However, a few high-level details still ought to be mentioned:
+% 1. Each algebraic variable ("m", "n", and "l" in the example) corresponds to a domain size.
+% 2. \mathcal{D} indicates that "m" denotes the size of \Gamma, "n" denotes the size of \Delta, etc.
+% 3. \mathcal{E} can contain any (positive) number of functions.
+% 4. Function denoted by "f" represents the solution to the model counting problem.
+% 3. The model count of the original formula is computed by evaluating f on the desired domain sizes. For example, f(3, 2) is the model count when |\Gamma| = 3, and |\Delta| = 2.
 \begin{example}[Counting bijections]\label{example:overall}
@@
 
+% TODO: maybe omit the word 'iverson'...
 Finally, we highlight the crucial role of the \Simplify procedure in simplifying
@@
   Let $f$ be an $n$-ary function in $\mathcal{E}$ and
-  $\mathbf{x} \in \mathbf{N}_{0}^{n}$. Then the evaluation of $f(\mathbf{x})$
+  $\mathbf{x} \in \mathbb{N}_{0}^{n}$. Then the evaluation of $f(\mathbf{x})$
   terminates.
@@
 \subsection{Smoothing for Base Cases}\label{sec:smoothingbase}
+% TODO: To be precise, line 7 of Algorithm 3 checks whether smoothing is
+% necessary, and lines 8-9 execute it. If the condition on line 7 is not
+% satisfied, the clause is not smoothed but rather completely omitted.
 
@@
 is not unique. We explain it via the example below.
+% TODO: In this context, "not unique" means that there are many different ways
+% to adjust/rewrite the formula to achieve the goal of smoothing. This section
+% (and Algorithm 3) presents one such approach.
 
@@
 \section{Experimental Evaluation}\label{sec:experiments}
+% TODO: A WFOMC instance comprises of a formula in first-order logic, a pair of
+% weights for each predicate, and a domain size (i.e., a non-negative integer)
+% for each domain. We provide the full details of all of these, including how
+% the formulas ought to be rewritten to fit the format of each WFOMC algorithm.
+
+% TODO: must rerun on an HPC
+
+% TODO: "hard to follow", pointing to the DPMC paper as a good example
+
+% TODO: Compilation time is included in the experimental results, and the
+% differences between compilation and inference time are delineated in the
+% second-to-last paragraph of Section 6.
+
+% TODO: It would not have been feasible to increase domain sizes by 1 all the
+% way up to 300000. Thus, the experimental results are presented in two parts,
+% where the first part examines scalability with small domain sizes, and the
+% second part tests the limits of each algorithm within a given timeout.
+
+% TODO: maybe instead of a table I should have an experiment where:
+% 1) Crane scales exponentially (with a base of sqrt(2))
+% 2) other algorithm scale linearly
+% 3) Then I can just draw the usual cumulative plot
+% 4) Stop each algorithm when they reach the timeout value
+
+% TODO: (here or in the introduction) C++ code generation is necessary for any
+% runtime experiments because without it the algorithm is "incomplete" as
+% explained above.
+
+% TODO: I'm claiming that C++ code generation is not the main contribution, but
+% the experiments are mainly about it...
+
+% TODO: The asymptotic analysis of the total number of arithmetic operations
+% required to compute the FOMC of these formulas was already performed in
+% previous work [1].
+
+% TODO: Since FastWFOMC does not support many-sorted logic, our experiments were restricted to formulas with a single domain.
+However, many of the counting problems examined in [1] become equivalent (in the sense that they generate the same integer sequences) when restricted to a single domain.
+Moreover, it is challenging to compare Crane2 and FastWFOMC on a larger set of problems because each problem has to be represented in two (fairly different) logics: FO and UFO^2+EQ.
 
@@
 \end{figure}
+% TODO: turn this into two separate plots for clarity. Maybe also attach labels
+% to their corresponding lines
 
@@
 compile it once and reuse the resulting C++ program for all domain sizes.
+% TODO: The lines for Crane2 in Figure 4 appear to be completely flat whereas
+% the line for ForcLift has some slight fluctuations. We refer to these
+% fluctuations as variance.
 

### 2024-07-11 doc/paper/paper.tex
AAAI Author Kit

--- 2024-06-30 doc/paper.tex
@@
-\documentclass{article}
-\pdfpagewidth=8.5in
-\pdfpageheight=11in
-
-\usepackage{kr}
-
-\usepackage{times}
-\usepackage{soul}
-\usepackage{url}
-\usepackage[hidelinks]{hyperref}
-\usepackage[utf8]{inputenc}
-\usepackage[small]{caption}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{booktabs}
-\urlstyle{same}
+\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
+\usepackage[submission]{aaai25}  % DO NOT CHANGE THIS
+\usepackage{times}  % DO NOT CHANGE THIS
+\usepackage{helvet}  % DO NOT CHANGE THIS
+\usepackage{courier}  % DO NOT CHANGE THIS
+\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
+\usepackage{graphicx} % DO NOT CHANGE THIS
+\urlstyle{rm} % DO NOT CHANGE THIS
+\def\UrlFont{\rm}  % DO NOT CHANGE THIS
+\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
+\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
+\frenchspacing  % DO NOT CHANGE THIS
+\setlength{\pdfpagewidth}{8.5in} % DO NOT CHANGE THIS
+\setlength{\pdfpageheight}{11in} % DO NOT CHANGE THIS
 
 \usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-\usepackage[capitalize,noabbrev]{cleveref}
 \usepackage{microtype}
@@
 \usepackage[inline]{enumitem}
+\usepackage[capitalize,noabbrev]{cleveref}
+\usepackage{booktabs}
+\usepackage{amsthm}
+
+\newtheorem{theorem}{Theorem}
+\newtheorem{assumption}{Assumption}
+\newtheorem{corollary}{Corollary}
+\newtheorem{fact}{Observation}
+\newtheorem{lemma}{Lemma}
+\theoremstyle{remark}
+\newtheorem*{remark}{Remark}
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}
+\newtheorem{example}{Example}
 
@@
 
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}{Lemma}
-\newtheorem{fact}{Observation}
-\newtheorem{corollary}{Corollary}
-\newtheorem{assumption}{Assumption}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
-\theoremstyle{remark}
-\newtheorem*{remark}{Remark}
-
-\pdfinfo{
-/TemplateVersion (KR.2022.0, KR.2023.0, KR.2024.0)
-}
-
 \forestset{
@@
 
-\newcommand{\crefrangeconjunction}{--}
-
-\crefname{line}{line}{lines}
-
-\crefname{fact}{Observation}{Observations}
-\crefname{assumption}{Assumption}{Assumptions}
-
-\crefalias{enumi}{type}
-\crefname{type}{Type}{Types}
-\creflabelformat{type}{#2\textup{#1}#3}
-
-\crefalias{enumi}{step}
-\crefname{step}{Step}{Steps}
-\creflabelformat{step}{#2\textup{#1}#3}
-
-\crefalias{clause}{equation}
-\crefname{clause}{Clause}{Clauses}
-\creflabelformat{clause}{#2\textup{(#1)}#3}
-
-\crefalias{formula}{equation}
-\crefname{formula}{Formula}{Formulas}
-\creflabelformat{formula}{#2\textup{(#1)}#3}
-
-\DeclareMathOperator{\CR}{CR}
-\DeclareMathOperator{\DR}{DR}
-\DeclareMathOperator{\Reff}{Ref}
-
-\DeclareMathOperator{\Doms}{Doms}
-
 \newcommand{\cmark}{\ding{51}}
 \newcommand{\xmark}{\ding{55}}
-
 \newcommand{\expr}{\mathtt{expr}}
@@
 \newcommand{\UFO}{$\mathsf{UFO}^{2} + \mathsf{EQ}$}
-
 \newcommand{\Cranetwo}{\textsc{Crane2}}
@@
 \newcommand{\Cranegreedy}{\textsc{Crane2-Greedy}}
+
+\newcommand{\crefrangeconjunction}{--}
+\crefname{line}{line}{lines}
+\crefname{fact}{Observation}{Observations}
+\crefname{assumption}{Assumption}{Assumptions}
+\crefalias{enumi}{type}
+\crefname{type}{Type}{Types}
+\creflabelformat{type}{#2\textup{#1}#3}
+\crefalias{enumi}{step}
+\crefname{step}{Step}{Steps}
+\creflabelformat{step}{#2\textup{#1}#3}
+\crefalias{clause}{equation}
+\crefname{clause}{Clause}{Clauses}
+\creflabelformat{clause}{#2\textup{(#1)}#3}
+\crefalias{formula}{equation}
+\crefname{formula}{Formula}{Formulas}
+\creflabelformat{formula}{#2\textup{(#1)}#3}
+
+\DeclareMathOperator{\CR}{CR}
+\DeclareMathOperator{\DR}{DR}
+\DeclareMathOperator{\Reff}{Ref}
+\DeclareMathOperator{\Doms}{Doms}
 
@@
 
+\pdfinfo{
+/TemplateVersion (2025.1)
+}
+
+\setcounter{secnumdepth}{2} %May be changed to 1 or 2 if section numbers are desired.
+
 \title{Towards Practical First-Order Model Counting}
-
-\author{%
-  Ananth K. Kidambi$^1$\footnote{The first and second authors contributed equally and were affiliated with the National University of Singapore during the completion of this work.}\and
-Guramrit Singh$^1$\and
-Paulius Dilkas$^2$\and
-Kuldeep S. Meel$^3$ \\
-\affiliations
-$^1$Indian Institute of Technology Bombay, Mumbai, India\\
-$^2$National University of Singapore, Singapore, Singapore\\
-$^3$University of Toronto, Toronto, Canada\\
-\emails
-210051002@iitb.ac.in,
-guramrit@iitb.ac.in,
-paulius.dilkas@nus.edu.sg,
-meel@cs.toronto.edu
-}% TODO: update affiliation and email
+\author{Anonymous Submission}
+\affiliations{}
 
@@
 
+% TODO: must find a way to include the implementation in the submission
+
+% TODO: consider restructuring the paper to make it easier to understand
+
 \section{Introduction}
@@
 Maybe add some weighted experiments as well.
+% * (must) more related work, situating my contributions in the broader context
+% * (concerning related work) the topic is intimately related to "graded logics", largely investigated in DL, mu-calculus and temporal logics
 
@@
 the domain size(s). If such an algorithm exists, the formula is called
-\emph{liftable}~\cite{DBLP:conf/starai/JaegerB12}. Beame et
-al.~\shortcite{DBLP:conf/pods/BeameBGS15} demonstrated the existence of an
-unliftable formula with three variables. It is also known that all formulas with
-up to two variables are
+\emph{liftable}~\cite{DBLP:conf/starai/JaegerB12}.
+\citeauthor{DBLP:conf/pods/BeameBGS15}~\shortcite{DBLP:conf/pods/BeameBGS15}
+demonstrated the existence of an unliftable formula with three variables. It is
+also known that all formulas with up to two variables are
 liftable~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/kr/BroeckMD14}. The liftable
@@
   still determine the number of endofunctions by assuming that the sizes of
-  $\Gamma$ and $\Delta$ are equal. This formulation, as observed by Dilkas and
-  Belle~\shortcite{DBLP:conf/kr/DilkasB23}, can prove beneficial in enabling
-  first-order knowledge compilation algorithms to find efficient solutions.
+  $\Gamma$ and $\Delta$ are equal. This formulation, as observed by
+  \citeauthor{DBLP:conf/kr/DilkasB23}~\shortcite{DBLP:conf/kr/DilkasB23}, can
+  prove beneficial in enabling first-order knowledge compilation algorithms to
+  find efficient solutions.
 \end{example}
@@
 \begin{example}[Counting bijections]\label{example:overall}
-  Consider the following formula (previously examined by Dilkas and
-  Belle~\shortcite{DBLP:conf/kr/DilkasB23}) that defines predicate $P$ as a
-  bijection between two sets $\Gamma$ and $\Delta$:
+  Consider the following formula (previously examined by
+  \citeauthor{DBLP:conf/kr/DilkasB23}~\shortcite{DBLP:conf/kr/DilkasB23}) that
+  defines predicate $P$ as a bijection between two sets $\Gamma$ and $\Delta$:
   \[
@@
 compilation, where it refers to the situation where all disjuncts in a
-disjunction node contain the same atoms~\cite{darwiche2001tractable}. Van den
-Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11} extend this concept to
-first-order logic, introducing set-disjunction and inclusion-exclusion nodes in
-addition to disjunction.
+disjunction node contain the same atoms~\cite{darwiche2001tractable}.
+\citeauthor{DBLP:conf/ijcai/BroeckTMDR11}~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}
+extend this concept to first-order logic, introducing set-disjunction and
+inclusion-exclusion nodes in addition to disjunction.
 
@@
 The remainder of this section presents an extension to the smoothing algorithm
-of Van den Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}.
+of
+\citeauthor{DBLP:conf/ijcai/BroeckTMDR11}~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}.
 \Cref{sec:smoothingbase} explains the role of smoothing in the base-case-finding
 algorithm described in \cref{sec:main}. \Cref{sec:smoothingfcg1} demonstrates
-how to adapt smoothing to the compilation rules introduced by Dilkas and
-Belle~\shortcite{DBLP:conf/kr/DilkasB23}.
+how to adapt smoothing to the compilation rules introduced by
+\citeauthor{DBLP:conf/kr/DilkasB23}~\shortcite{DBLP:conf/kr/DilkasB23}.
 
@@
 Before discussing the proposed changes to smoothing, let us briefly review the
-compilation rules and their corresponding node types introduced by Dilkas and
-Belle~\shortcite{DBLP:conf/kr/DilkasB23}. \emph{Domain recursion} involves
-selecting a domain $\Delta$, introducing a new constant $c \in \Delta$, and
-modifying the formula based on two possibilities for each variable $x$
-quantified over $\Delta$: $x = c$ or $x \ne c$. The resulting node is denoted as
-$\DR(c \in \Delta)$. \emph{Constraint removal} applies to formulas where each
-variable $x$ quantified over a domain $\Delta$ is followed by the inequality
-constraint $x \ne c$. These formulas can be rewritten so that each clause begins
-with $\forall x \in \Delta\text{. }x \ne c \Rightarrow \ldots$ Constraint
-removal replaces $\Delta$ with a new domain $\Delta'$ and removes the $x \ne c$
-constraints. The resulting node is denoted as
-$\CR(\Delta' \gets \Delta \setminus \{\,c\,\})$. Finally, \emph{caching} detects
-when the input formula $\phi$ is equal to a previously encountered formula
-$\psi$ except for having different domains. The resulting node is denoted as
-$\Reff(\sigma)$, with $\sigma$ representing the substitution mapping the domains
-of $\psi$ to their corresponding domains in $\phi$.
+compilation rules and their corresponding node types introduced by
+\citeauthor{DBLP:conf/kr/DilkasB23}~\shortcite{DBLP:conf/kr/DilkasB23}.
+\emph{Domain recursion} involves selecting a domain $\Delta$, introducing a new
+constant $c \in \Delta$, and modifying the formula based on two possibilities
+for each variable $x$ quantified over $\Delta$: $x = c$ or $x \ne c$. The
+resulting node is denoted as $\DR(c \in \Delta)$. \emph{Constraint removal}
+applies to formulas where each variable $x$ quantified over a domain $\Delta$ is
+followed by the inequality constraint $x \ne c$. These formulas can be rewritten
+so that each clause begins with $\forall x \in \Delta\text{.
+}x \ne c \Rightarrow \ldots$ Constraint removal replaces $\Delta$ with a new
+domain $\Delta'$ and removes the $x \ne c$ constraints. The resulting node is
+denoted as $\CR(\Delta' \gets \Delta \setminus \{\,c\,\})$. Finally,
+\emph{caching} detects when the input formula $\phi$ is equal to a previously
+encountered formula $\psi$ except for having different domains. The resulting
+node is denoted as $\Reff(\sigma)$, with $\sigma$ representing the substitution
+mapping the domains of $\psi$ to their corresponding domains in $\phi$.
 
@@
 
-% TODO: must rerun on an HPC
+% TODO: must rerun on an HPC and include more instances
 
@@
 
-% TODO: Since FastWFOMC does not support many-sorted logic, our experiments were restricted to formulas with a single domain.
-However, many of the counting problems examined in [1] become equivalent (in the sense that they generate the same integer sequences) when restricted to a single domain.
-Moreover, it is challenging to compare Crane2 and FastWFOMC on a larger set of problems because each problem has to be represented in two (fairly different) logics: FO and UFO^2+EQ.
+% TODO: Since FastWFOMC does not support many-sorted logic, our experiments were
+% restricted to formulas with a single domain. However, many of the counting
+% problems examined in [1] become equivalent (in the sense that they generate
+% the same integer sequences) when restricted to a single domain. Moreover, it
+% is challenging to compare Crane2 and FastWFOMC on a larger set of problems
+% because each problem has to be represented in two (fairly different) logics:
+% FO and UFO^2+EQ.
+
+% TODO: position some of the experiments as 'practical'
 
@@
 \textsc{FastWFOMC} and \textsc{ForcLift} on two problems previously considered
-by Dilkas and Belle~\shortcite{DBLP:conf/kr/DilkasB23}. The first problem is the
-function-counting problem from \cref{example:functions}, and the second problem
-is the bijection-counting problem described below. It is important to note that
-comparing \Cranetwo{} and \textsc{FastWFOMC} on a more substantial set of
-benchmarks is challenging because there is no automated way to translate a
-formula in \FO{} or \Ctwo{} into \UFO{}, or even check if such an encoding is
-possible. We ran the experiments on an AMD~Ryzen~7~5800H processor with
-\SI{16}{\gibi\byte} of memory and Arch Linux~6.8.2-arch2-1 operating system.
-\textsc{FastWFOMC} was executed using Python~3.8.19 with Python-FLINT~0.5.0.
+by \citeauthor{DBLP:conf/kr/DilkasB23}~\shortcite{DBLP:conf/kr/DilkasB23}. The
+first problem is the function-counting problem from \cref{example:functions},
+and the second problem is the bijection-counting problem described below. It is
+important to note that comparing \Cranetwo{} and \textsc{FastWFOMC} on a more
+substantial set of benchmarks is challenging because there is no automated way
+to translate a formula in \FO{} or \Ctwo{} into \UFO{}, or even check if such an
+encoding is possible. We ran the experiments on an AMD~Ryzen~7~5800H processor
+with \SI{16}{\gibi\byte} of memory and Arch Linux~6.8.2-arch2-1 operating
+system. \textsc{FastWFOMC} was executed using Python~3.8.19 with
+Python-FLINT~0.5.0.
 
@@
 procedure of \textsc{ForcLift} and \textsc{Crane} to support base case formulas
-and the compilation rules introduced by Dilkas and
-Belle~\shortcite{DBLP:conf/kr/DilkasB23}. Third, we have proposed an approach to
-compile function definitions into C++ programs with support for
-arbitrary-precision arithmetic. Lastly, we have provided experimental evidence
-demonstrating that \Cranetwo{} can scale to much larger domain sizes than
-\textsc{FastWFOMC} while handling more formulas than \textsc{ForcLift}.
+and the compilation rules introduced by
+\citeauthor{DBLP:conf/kr/DilkasB23}~\shortcite{DBLP:conf/kr/DilkasB23}. Third,
+we have proposed an approach to compile function definitions into C++ programs
+with support for arbitrary-precision arithmetic. Lastly, we have provided
+experimental evidence demonstrating that \Cranetwo{} can scale to much larger
+domain sizes than \textsc{FastWFOMC} while handling more formulas than
+\textsc{ForcLift}.
 
@@
 
-\bibliographystyle{kr}
 \bibliography{paper}

### 2024-07-11 doc/paper/paper.tex
Remove unnecessary mentions of FCGs and (traditional) smoothing

@@
   modification technique in knowledge compilation, known as smoothing, to work
-  with the formulas corresponding to base cases and the recently proposed node
-  types, such as domain recursion and constraint removal. Third, we introduce a
+  with the formulas corresponding to base cases. Third, we introduce a
   compilation algorithm that transforms the function definitions into C++ code,
@@
 
-% TODO: somehow indicate that source code will be available (a redacted link?)
-
 % TODO: Updates to the algorithm
@@
 % 2) a function call with a constant should always mean that that function should have a base case, not just when it's in the same function
-
-% TODO: must find a way to include the implementation in the submission
 
@@
 \end{enumerate*}
-Then, \cref{sec:smoothing} explains post-processing techniques for FCGs and the
-formulas from \cref{step2} above required to preserve the correct model count.
-Next, \cref{sec:cpp} elucidates how function definitions encoding a solution to
-a WFOMC problem are compiled into C++ programs.\footnote{The possibility of
+Then, \cref{sec:smoothing} explains post-processing techniques for the formulas
+from \cref{step2} above required to preserve the correct model count. Next,
+\cref{sec:cpp} elucidates how function definitions encoding a solution to a
+WFOMC problem are compiled into C++ programs.\footnote{The possibility of
   compiling WFOMC solutions to C++ programs has been previously
@@
 filtered out. As for clauses of \cref{type3}, a new kind of smoothing is
-performed, which will be explained in \cref{sec:smoothingbase}.
+performed, which will be explained in \cref{sec:smoothing}.
 
@@
 
-\section{Smoothing}\label{sec:smoothing}
-
-\emph{Smoothness} is a property originating in propositional knowledge
-compilation, where it refers to the situation where all disjuncts in a
-disjunction node contain the same atoms~\cite{darwiche2001tractable}.
-\citeauthor{DBLP:conf/ijcai/BroeckTMDR11}~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}
-extend this concept to first-order logic, introducing set-disjunction and
-inclusion-exclusion nodes in addition to disjunction.
-
-The purpose of smoothing is as follows. When compilation rules such as unit
-propagation and inclusion-exclusion simplify a formula, certain ground atoms may
-be eliminated (see \cref{example:basecasesmoothing} below). To properly account
-for these atoms during counting, smoothing nodes (i.e., tautological clauses
-such as $P(c) \lor \neg P(c)$) are added to the FCG in the appropriate location.
-
-The remainder of this section presents an extension to the smoothing algorithm
-of
-\citeauthor{DBLP:conf/ijcai/BroeckTMDR11}~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}.
-\Cref{sec:smoothingbase} explains the role of smoothing in the base-case-finding
-algorithm described in \cref{sec:main}. \Cref{sec:smoothingfcg1} demonstrates
-how to adapt smoothing to the compilation rules introduced by
-\citeauthor{DBLP:conf/kr/DilkasB23}~\shortcite{DBLP:conf/kr/DilkasB23}.
-
-\subsection{Smoothing for Base Cases}\label{sec:smoothingbase}
+\section{Smoothing the Base Cases}\label{sec:smoothing}
+
+\emph{Smoothing} is the process of modifying a circuit to re-introduce atoms
+that might have been eliminated, thus ensuring that the circuit preserves the
+correct (weighted) model
+count~\cite{darwiche2001tractable,DBLP:conf/ijcai/BroeckTMDR11}. In this
+section, we motivate and describe a similar process performed on
+\cref{line:smoothing1,line:smoothing2} of \cref{alg:propagate}.
+
 % TODO: To be precise, line 7 of Algorithm 3 checks whether smoothing is
@@
 
-In this section, we motivate and describe \cref{line:smoothing1,line:smoothing2}
-of \cref{alg:propagate}. Suppose that \Propagate is called with arguments
-$(\phi, \Delta, 0)$, which means we are simplifying the formula $\phi$ by
-assuming that the domain $\Delta$ is empty. Informally, if there is a predicate
-$P$ in $\phi$ that has nothing to do with the domain $\Delta$, smoothing
-preserves all occurrences of $P$ even if all clauses with $P$ become vacuously
-satisfied. It is important to note that the approach presented in this section
-is not unique. We explain it via the example below.
+Suppose that \Propagate is called with arguments $(\phi, \Delta, 0)$, which
+means we are simplifying the formula $\phi$ by assuming that the domain $\Delta$
+is empty. Informally, if there is a predicate $P$ in $\phi$ that has nothing to
+do with the domain $\Delta$, smoothing preserves all occurrences of $P$ even if
+all clauses with $P$ become vacuously satisfied. It is important to note that
+the approach presented in this section is not unique. We explain it via the
+example below.
 % TODO: In this context, "not unique" means that there are many different ways
@@
 goal: constructing a tautological clause that retains the literals in $C'$.
-
-\subsection{Smoothing the FCG}\label{sec:smoothingfcg1}
-
-Smoothing is a two-step process that involves propagating unit clauses upwards
-(i.e., in the opposite direction of FCG arcs) and adding smoothing nodes to
-account for missing atoms. In this section, we will
-\begin{enumerate*}[label=(\roman*)]
-  \item describe the relevant node types from previous work,
-  \item explain how smoothing should work for these node types, and
-  \item demonstrate the new smoothing techniques using two example FCGs.
-\end{enumerate*}
-
-Before discussing the proposed changes to smoothing, let us briefly review the
-compilation rules and their corresponding node types introduced by
-\citeauthor{DBLP:conf/kr/DilkasB23}~\shortcite{DBLP:conf/kr/DilkasB23}.
-\emph{Domain recursion} involves selecting a domain $\Delta$, introducing a new
-constant $c \in \Delta$, and modifying the formula based on two possibilities
-for each variable $x$ quantified over $\Delta$: $x = c$ or $x \ne c$. The
-resulting node is denoted as $\DR(c \in \Delta)$. \emph{Constraint removal}
-applies to formulas where each variable $x$ quantified over a domain $\Delta$ is
-followed by the inequality constraint $x \ne c$. These formulas can be rewritten
-so that each clause begins with $\forall x \in \Delta\text{.
-}x \ne c \Rightarrow \ldots$ Constraint removal replaces $\Delta$ with a new
-domain $\Delta'$ and removes the $x \ne c$ constraints. The resulting node is
-denoted as $\CR(\Delta' \gets \Delta \setminus \{\,c\,\})$. Finally,
-\emph{caching} detects when the input formula $\phi$ is equal to a previously
-encountered formula $\psi$ except for having different domains. The resulting
-node is denoted as $\Reff(\sigma)$, with $\sigma$ representing the substitution
-mapping the domains of $\psi$ to their corresponding domains in $\phi$.
-
-\paragraph{Stage~1 for Domain Recursion}
-When visiting a $\DR(c \in \Delta)$ node, we replace each occurrence of
-$\phi(c)$ or $\forall x \in \Delta\text{. } x \ne c \Rightarrow \phi(x)$ with
-$\forall x \in \Delta\text{. }\phi(x)$ for each unit clause received from the
-child node. This way, we ensure that if the subgraph below the domain recursion
-node covers some of the ground atoms affected by domain recursion, it covers all
-of them. If the relevant subgraph already covers those ground atoms, Stage~2
-will not make any changes. Otherwise, smoothing nodes will be added below the
-domain recursion node to account for the difference in the sets of ground atoms
-assigned to the domain recursion node and its child node.
-
-\paragraph{Stage~1 for Constraint Removal and Caching}
-When visiting a $\CR(\Delta' \gets \Delta \setminus \{\,c\,\})$ node, we reverse
-constraint removal by replacing each $\forall x \in \Delta'\text{. }\phi(x)$
-with $\forall x \in \Delta\text{. }x \ne c \Rightarrow \phi(x)$. When visiting a
-$\Reff(\sigma)$ node, we apply the substitution $\sigma$ to the unit clauses
-from the child node.
-
-\paragraph{Stage~2 for Domain Recursion}
-We do not need to add smoothing nodes immediately below constraint removal or
-caching nodes. However, for domain recursion, we follow a specific process.
-\begin{enumerate}
-  \item If the set of unit clauses assigned to the child node during Stage~1
-        contains both $\phi(c)$ and $\forall x \in \Delta\text{.
-        } x \ne c \Rightarrow \phi(x)$, we merge the two clauses into
-        $\forall x \in \Delta\text{. }\phi(x)$. The only difference between
-        these two clauses is that one has the constant $c$ while the other has a
-        variable $x \ne c$.
-  \item If necessary, we add smoothing nodes below the domain recursion node to
-        account for the difference between the unit clauses assigned to the
-        domain recursion node during Stage~1 and the unit clauses of the child
-        node post-processed by the step above.
-\end{enumerate}
-
-\begin{figure}[t]
-  \centering
-  \begin{forest}
-    for tree={sn edges}
-    [$\DR(c \in \Delta)$,name=dr,ellipse,draw
-    [$\land$,ellipse,draw,dashed,edge=dashed
-    [$P(c)$,rectangle,draw,fill=green!20]
-    [$\forall x \in \Delta\text{. }x \ne c \Rightarrow P(x) \lor \neg P(x)$,rectangle,dashed,edge=dashed,draw,fill=blue!20]
-    ]
-    ]
-  \end{forest}
-  \caption{An artificial example of an FCG where a smoothing node needs to be
-    added below a domain recursion node. The dashed nodes and arcs are added
-    during Stage~2 of smoothing.}\label{fig:smoothing2}
-\end{figure}
-
-\begin{example}[An FCG that requires smoothing]
-  \Cref{fig:smoothing2} depicts an FCG with a domain recursion node
-  $\DR(c \in \Delta)$ followed directly by a single $P(c)$ node. In this
-  scenario, Stage~1 assigns $\{\, \forall x \in \Delta\text{. }P(x) \,\}$ to the
-  former node and $\{\, P(c) \,\}$ to the latter. As these two sets of unit
-  clauses cover different ground atoms, Stage~2 adds a smoothing node to address
-  $P(x)$ for all $x \in \Delta \setminus \{\, c \,\}$.
-\end{example}
-
-\begin{figure}[t]
-  \centering
-  \begin{forest}
-    for tree={sn edges}
-    [$\DR(c \in \Delta)$,name=dr,ellipse,draw,label={right:\textcolor{blue}{3. $\{\, \forall x \in \Delta\text{. }P(x) \,\}$}}
-    [$\land$,ellipse,draw,label={left:\textcolor{blue}{2. $\{\, P(c) \,\}$}},label={right:\textcolor{blue}{6. $\{\, P(c), \forall x \in \Delta\text{. }x \ne c \Rightarrow P(x) \,\}$}}
-    [$P(c)$,rectangle,draw,fill=green!20,label={272:\textcolor{blue}{1. $\{\, P(c) \,\}$}}]
-    [$\CR(\Delta' \gets \Delta \setminus \{\, c \,\})$,ellipse,draw,label={87:\textcolor{blue}{5. $\{\, \forall x \in \Delta\text{. }x \ne c \Rightarrow P(x) \,\}$}}
-    [$\Reff(\Delta \mapsto \Delta')$,name=ref,ellipse,draw,label={below:\textcolor{blue}{4. $\{\, \forall x \in \Delta'\text{. }P(x) \,\}$}}]
-    ]
-    ]
-    ]
-  \end{forest}
-  \caption{A smooth FCG based on \cref{example:overall}. For compactness, the
-    arc between the caching node and the domain recursion node is not shown. The
-    labels next to the nodes indicate the sets of unit clauses assigned to each
-    node during Stage~1 and the order in which these assignments were made.
-    Empty assignments that replace a set $S$ with $S$ itself are not
-    included.}\label{fig:smoothing1}
-\end{figure}
-
-\begin{example}[A smooth FCG]\label{example:smooth}
-  Stage~1 of the smoothing process is more complex in the case of the FCG shown
-  in \cref{fig:smoothing1}. The unit clause $P(c)$ propagates to the conjunction
-  node and is then generalised to $\forall x \in \Delta\text{. }P(x)$ by the
-  domain recursion node. It continues to propagate to the caching node, changing
-  its form to $(\forall x \in \Delta\text{.
-  }P(x))[\Delta \mapsto \Delta'] \equiv \forall x \in \Delta'\text{. }P(x)$. The
-  constraint removal node re-introduces the constraints, transforming the clause
-  to $\forall x \in \Delta\text{. }x \ne c \Rightarrow P(x)$, which then
-  propagates to the conjunction node, joining $P(c)$.
-
-  During Stage~2, $P(c)$ and $\forall x \in \Delta\text{.
-  }x \ne c \Rightarrow P(x)$ are combined into $\forall x \in \Delta\text{.
-  }P(x)$. Since the resulting clause matches the clause assigned to the domain
-  recursion node, the FCG is already smooth.
-\end{example}
-
-The algebraic interpretation of \cref{fig:smoothing1} is an equation $e$ that
-defines a recursive function. The right-hand side of $e$ already encompasses
-$P(c)$, and the smoothing algorithm correctly recognises that the recursive call
-also encompasses $P(x)$ for all $x \in \Delta \setminus \{\, c \,\}$.
 
@@
 by the original \textsc{Crane} algorithm. Second, we have extended the smoothing
-procedure of \textsc{ForcLift} and \textsc{Crane} to support base case formulas
-and the compilation rules introduced by
-\citeauthor{DBLP:conf/kr/DilkasB23}~\shortcite{DBLP:conf/kr/DilkasB23}. Third,
-we have proposed an approach to compile function definitions into C++ programs
-with support for arbitrary-precision arithmetic. Lastly, we have provided
-experimental evidence demonstrating that \Cranetwo{} can scale to much larger
-domain sizes than \textsc{FastWFOMC} while handling more formulas than
+procedure of \textsc{ForcLift} and \textsc{Crane} to support base case formulas.
+Third, we have proposed an approach to compile function definitions into C++
+programs with support for arbitrary-precision arithmetic. Lastly, we have
+provided experimental evidence demonstrating that \Cranetwo{} can scale to much
+larger domain sizes than \textsc{FastWFOMC} while handling more formulas than
 \textsc{ForcLift}.
@@
 \end{document}
+
+% TODO:
+% must clean pdf metadata before submitting
+% make sure that it's not automatically deducible that I'm the author of Crane
+% no type 3 fonts (including in the PDFs of figures)
+% no overfull boxes (might be the figure)
+% no embedded links (but URLs are fine as long as they're not clickable?)
+% must not use 'input' command. instead, compile to a pdf
+% figures should appear on the page where they are discussed or on the next page
+% colors in figures must be cmyk, not rgb
+% references must not have missing fields

### 2024-07-15 doc/paper/paper.tex
Some editing

@@
 \newcommand{\FO}{$\mathsf{FO}$}
-\newcommand{\UFO}{$\mathsf{UFO}^{2} + \mathsf{EQ}$}
+\newcommand{\UFO}{$\mathsf{UFO}^{2} + \mathsf{CC}$}
 \newcommand{\Cranetwo}{\textsc{Crane2}}
@@
 \SetKwFunction{CompileWithBaseCases}{CompileWithBaseCases}
-\SetKwFunction{Compile}{Compile}
+\SetKwFunction{Compile}{{\normalfont \textsc{Crane}}}
 \SetKwFunction{Propagate}{Propagate}
@@
 
-% TODO: No proper runtime consideration (other than the termination). (address
-% this criticism in some way)
-
 % TODO: Having an algorithm that can efficiently handle large domain sizes is
@@
 
-% TODO: Updates to the algorithm
-% 1) replace x_i-c_i on Line 7 of Algorithm 2 with a generalisation of x_i that can be an arbitrary summation/subtraction of domain sizes
-% 2) a function call with a constant should always mean that that function should have a base case, not just when it's in the same function
-
-% TODO: consider restructuring the paper to make it easier to understand
+% TODO: consider restructuring the paper (how?)
 
 \section{Introduction}
-% TODO: improvements to the introduction (must):
-% * make it extra clear what the gap is that this work is trying to fill
-% * mention Crane earlier and describe its importance
-% * the last two paragraphs should make more of a BOOM (e.g., include the over 9k claim)
-% * (here and elsewhere) clarify the distinction between the weighted and unweighted variants of the problem in the final version of the paper.
-We focus on the unweighted variant in our implementation and experiments, however, Crane2 can handle WFOMC instances as well simply by switching the main data type from integers to rational numbers.
-Maybe add some weighted experiments as well.
-% * (must) more related work, situating my contributions in the broader context
-% * (concerning related work) the topic is intimately related to "graded logics", largely investigated in DL, mu-calculus and temporal logics
+% TODO: make it extra clear what the gap is that this work is trying to fill
+
+% TODO: mention Crane earlier and describe its importance
+
+% TODO: the last two paragraphs should make more of a BOOM (e.g., include the
+% over 9k claim)
+
+% TODO (here and elsewhere): clarify the distinction between the weighted and
+% unweighted variants of the problem in the final version of the paper. We focus
+% on the unweighted variant in our implementation and experiments, however,
+% Crane2 can handle WFOMC instances as well simply by switching the main data
+% type from integers to rational numbers. Maybe add some weighted experiments as
+% well.
+
+% TODO: (must) more related work, situating my contributions in the broader
+% context
+
+% TODO: (concerning related work) the topic is intimately related to "graded
+% logics", largely investigated in DL, mu-calculus and temporal logics
 
@@
 the most prominent class of WFOMC algorithms is based on \emph{first-order
-  knowledge compilation}. In this approach, the formula is compiled into a
-representation (such as a circuit or graph) by iteratively applying
+  knowledge compilation} (FOKC). In this approach, the formula is compiled into
+a representation (such as a circuit or graph) by iteratively applying
 \emph{compilation rules}. This representation can then be used to compute the
@@
 extension \textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23}. The former compiles
-formulas into circuits, while the latter compiles them first to
-\emph{first-order computational graphs} (FCGs) and then to (algebraic)
-equations. Another WFOMC algorithm,
+formulas into circuits, while the latter compiles them first to graphs and then
+to (algebraic) equations. Another WFOMC algorithm,
 \textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21}, is based on cell enumeration.
@@
 upper/lower bound construction~\cite{DBLP:conf/ijcai/BremenK20}.
-% TODO: FCGs were never defined. Maybe avoid referring to them altogether?
-% Smoothing nodes are also undefined.
 
@@
 
-% TODO: first sentence: elaborate a bit more for a general audience
+% TODO: introduce MLNs somewhere? maybe use an acronym?
 The recently proposed \textsc{Crane} algorithm, while capable of handling
-formulas beyond the reach of \textsc{ForcLift}, was incomplete as it could only
-construct function definitions, which would then need to be evaluated to compute
-the WFOMC.\@ Additionally, recursive functions were presented without base
-cases. In this work, we introduce \Cranetwo{}, an extension of \textsc{Crane}
-that addresses these two weaknesses.
-% TODO: We called the previous version of Crane "incomplete" because it cannot
-% be used as a black box that takes Markov logic networks (or weighted formulas
-% in some other format) and outputs numbers (i.e., model counts or
-% probabilities).
+formulas beyond the reach of \textsc{ForcLift}, was `incomplete' as it could
+only construct function definitions, which would then need to be evaluated to
+compute the WFOMC.\@ In other words, it could not be used as a black box that
+takes Markov logic networks (or weighted formulas in some other format) and
+outputs numbers (i.e., model counts or probabilities). Additionally, recursive
+functions were presented without base cases. In this work, we introduce
+\Cranetwo{}, an extension of \textsc{Crane} that addresses these two weaknesses.
 
@@
     \node[draw,fit={(compilewithbasecases) (compilation) (crane) (findbasecases) (propagate)},inner ysep=7pt,yshift=5pt] {};
-    \node at (0.2, 0.5) {\Cranetwo};
+    \node at (0.6, 0.5) {\Cranetwo};
 
@@
     \begin{enumerate*}[label=(\roman*)]
-      \item the knowledge compilation algorithm of \textsc{Crane}, referred to as \Compile,
+      \item the FOKC algorithm of \textsc{Crane},
       \item a procedure called \FindBaseCases, which identifies a sufficient set of base cases,
@@
 \cref{sec:cpp} elucidates how function definitions encoding a solution to a
-WFOMC problem are compiled into C++ programs.\footnote{The possibility of
-  compiling WFOMC solutions to C++ programs has been previously
-  considered~\cite{DBLP:conf/kr/KazemiP16}. However, the extent of formulas that
-  could be handled was limited.} Finally, \cref{sec:experiments} presents two
-experiments comparing \Cranetwo{} with other state-of-the-art WFOMC algorithms.
+WFOMC problem are compiled into C++ programs. Note that a solution to WFOMC that
+uses compilation to C++ has been considered
+before~\cite{DBLP:conf/kr/KazemiP16}, however, the extent of formulas that could
+be handled was limited. Finally, \cref{sec:experiments} presents experiments
+results comparing \Cranetwo{} with other state-of-the-art WFOMC algorithms.
 
@@
 
-In this section, we will review the basic concepts of first-order logic as they
-are used in first-order knowledge compilation algorithms. There are two key
-differences between the logic used within such algorithms and the logic
-supported as input. First, Skolemization~\cite{DBLP:conf/kr/BroeckMD14} is
-employed to eliminate existential quantifiers by introducing additional
-predicates. Second, the input formula is rewritten as a conjunction of clauses,
-each of which is in \emph{prenex normal form}~\cite{hinman2018fundamentals}.
-% TODO: explain that "Skolemization" here is NOT standard Skolemization of
-% first-order logic, which would replace existential quantifiers by function
-% terms.
-
-% TODO: reorder the definitions in the opposite direction
-A \emph{formula} is a conjunction of clauses. A \emph{clause} is of the form
-$\forall x_{1} \in \Delta_{1}\text{.}\forall x_{2} \in \Delta_{2}\dots\text{
-}\forall x_{n} \in \Delta_{n}\text{.}\phi(x_{1}, x_{2}, \dots, x_{n})$, where
-$\phi$ is a disjunction of literals that only contain variables
-$x_{1}, \dots, x_{n}$ (and any constants). We say that a clause is a
-\emph{(positive) unit clause} if
-\begin{enumerate*}[label=(\roman*)]
-  \item there is only one literal with a predicate, and
-  \item it is a positive literal.
-\end{enumerate*}
-A \emph{literal} is either an atom (i.e., a \emph{positive} literal) or its
-negation (i.e., a \emph{negative} literal). An \emph{atom} is either
+In this section, we review the basic concepts of first-order logic as they are
+used in FOKC algorithms. There are two key differences between the logic used by
+such algorithms and the logic supported as input. First,
+Skolemization~\cite{DBLP:conf/kr/BroeckMD14} is employed to eliminate
+existential quantifiers by introducing additional predicates. Note that
+Skolemization here is different from the standard Skolemization procedure that
+introduces function symbols~\cite{DBLP:books/daglib/0030198}. Second, the input
+formula is rewritten as a conjunction of clauses, each of which is in
+\emph{prenex normal form}~\cite{hinman2018fundamentals}.
+
+A \emph{term} is either a variable or a constant. An \emph{atom} is either
 \begin{enumerate*}[label=(\roman*)]
@@
 \end{enumerate*}
-An atom is \emph{ground} if it contains no variables, i.e., only constants. The
-\emph{arity} of a predicate is the number of arguments it takes, i.e., $m$ in
-the case of predicate $P$ mentioned above. When we want to denote a predicate
-together with its arity, we write $P/m$. A \emph{term} is either a variable or a
-constant. Throughout the paper, we will use set-theoretic notation, interpreting
-a formula as a set of clauses and a clause as a set of literals. Moreover, for
-readability, clauses written on separate lines are implicitly conjoined.
+The \emph{arity} of a predicate is the number of arguments it takes, i.e., $m$
+in the case of predicate $P$ above. We write $P/m$ to denote a predicate
+together with its arity. A \emph{literal} is either an atom (i.e., a
+\emph{positive} literal) or its negation (i.e., a \emph{negative} literal). An
+atom is \emph{ground} if it contains no variables, i.e., only constants. A
+\emph{clause} is of the form
+$\forall x_{1} \in \Delta_{1}\text{.}\forall x_{2} \in \Delta_{2}\dots\text{}\forall x_{n} \in \Delta_{n}\text{.}\phi(x_{1}, x_{2}, \dots, x_{n})$,
+where $\phi$ is a disjunction of literals that only contain variables
+$x_{1}, \dots, x_{n}$ (and any constants). We say that a clause is a
+\emph{(positive) unit clause} if
+\begin{enumerate*}[label=(\roman*)]
+  \item there is only one literal with a predicate, and
+  \item it is a positive literal.
+\end{enumerate*}
+Finally, a \emph{formula} is a conjunction of clauses. Throughout the paper, we
+use set-theoretic notation, interpreting a formula as a set of clauses and a
+clause as a set of literals.
 
 \subsection{WFOMC Algorithms and Their Logics}\label{sec:threelogics}
-
-% TODO: mention the Unique Name Assumption and that, hence, s = t holds iff s
-% and t are the same constant.
 
@@
   \end{tabular}
-  \caption[]{Comparison of three logics used in WFOMC based on the following aspects:
-    \begin{enumerate*}[label=(\roman*)]
-      \item number of sorts,
+  \caption[]{A comparison of the three logics used in WFOMC based on the following aspects:
+    \begin{enumerate*}[label=(\roman*)]
+      \item the number of sorts,
       \item support for constants,
-      \item maximum number of variables,
+      \item the maximum number of variables,
       \item supported quantifiers, and
@@
 
-% TODO:
-% 1. Rename \UFO{} to what that new paper uses
-% 2. Use FastWFOMC.jl instead, removing the mention of 'privately-obtained'
-% 3. use symbols instead of numbers for the footnotes
+% TODO: Use FastWFOMC.jl instead, removing the mention of 'privately-obtained'
+
+\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
+
 In \cref{tbl:logics}, we outline the differences among three first-order logics
@@
 of \textsc{FastWFOMC} does not support any cardinality constraints. The notation
-we use to refer to each logic is standard in the case of \Ctwo{}, new in the
-case of \UFO{}, and redefined to be more specific in the case of \FO{}. All
-three logics are function-free, and domains are always assumed to be finite.
+we use to refer to each logic is standard in the case of \Ctwo{} and redefined
+to be more specific in the case of the other two logics. All three logics are
+function-free, and domains are always assumed to be finite. As usual, we
+presuppose the \emph{unique name assumption}, which states that two constants
+are equal if and only if they are the same constant~\cite{DBLP:books/aw/RN2020}.
+
+\renewcommand*{\thefootnote}{\arabic{footnote}}
 
@@
 assigned to a sequence of $n$ sorts. Each sort has its corresponding domain.
-Most of these assignments to sorts are typically left implicit and can be
-reconstructed from the quantifiers. For example, $\forall x,y \in \Delta\text{.
-}P(x, y)$ implies that variables $x$ and $y$ have the same sort. On the other
-hand, $\forall x \in \Delta\text{. }\forall y \in \Gamma\text{. } P(x, y)$
-implies that $x$ and $y$ have different sorts, and it would be improper to
-write, for example, $\forall x \in \Delta\text{. }\forall y \in \Gamma\text{.
+These assignments to sorts are typically left implicit and can be reconstructed
+from the quantifiers. For example, $\forall x,y \in \Delta\text{. }P(x, y)$
+implies that variables $x$ and $y$ have the same sort. On the other hand,
+$\forall x \in \Delta\text{. }\forall y \in \Gamma\text{. } P(x, y)$ implies
+that $x$ and $y$ have different sorts, and it would be improper to write, for
+example, $\forall x \in \Delta\text{. }\forall y \in \Gamma\text{.
 } P(x, y) \lor x = y$. \FO{} is also the only logic to support constants,
-formulas with more than two variables, and the equality predicate.
-% TODO: the discussion about sorts isn't featured in the rest of the paper
+formulas with more than two variables, and the equality predicate. While we do
+not explicitly refer to sorts in subsequent sections of this paper, the
+many-sorted nature of \FO{} is paramount to the algorithms presented therein.
 
@@
 
-\Ctwo{} and \UFO{} are single-sorted (i.e., all variables are quantified over
-the same domain) and only include formulas with at most two variables and no
-constants. Unlike \UFO{}, \Ctwo{} supports existential quantifiers, including
-\emph{counting quantifiers}. For example, $\exists^{=1} x\text{. }\phi(x)$ means
-that there exists \emph{exactly one} $x$ such that $\phi(x)$, and
-$\exists^{\le 2} x\text{. }\phi(x)$ means that there exist \emph{at most two}
-such $x$. The advantage \UFO{} brings over \Ctwo{} is the support for
-\emph{(equality) cardinality constraints}. For example, $|P| = 3$ constrains all
-models to have \emph{precisely three positive literals with the predicate $P$}.
-
-% TODO: The distinctness of domains is important in two ways. First, in terms of
-% expressiveness, writing clause such as "\forall x, P(x, x)" is valid if
-% predicate P is defined over two copies of the same domain and invalid
-% otherwise. Second, having more distinct domains makes the problem more
-% decomposable for the knowledge compilation algorithm. With more distinct
-% domains, it can make assumptions or deductions about, e.g., the first domain
-% of predicate P without worrying how (or if) they apply to the second domain.
+Compared to \FO{}, \Ctwo{} and \UFO{} lack support for:
+\begin{enumerate*}[label=(\roman*)]
+  \item constants,
+  \item the equality predicate,
+  \item multiple domains, and
+  \item formulas with more than two variables.
+\end{enumerate*}
+The advantage that \Ctwo{} brings over \FO{} is the inclusion of \emph{counting
+  quantifiers}. That is, alongside $\forall$ and $\exists$, \Ctwo{} supports
+$\exists^{=k}$, $\exists^{\le k}$, and $\exists^{\ge k}$ for any positive
+integer $k$. For example, $\exists^{=1} x\text{. }\phi(x)$ means that there
+exists \emph{exactly one} $x$ such that $\phi(x)$, and $\exists^{\le 2} x\text{.
+}\phi(x)$ means that there exist \emph{at most two} such $x$. \UFO{}, on the
+other hand, does not support any existential quantifiers but instead
+incorporates \emph{(equality) cardinality constraints}. For example, $|P| = 3$
+constrains all models to have \emph{precisely three positive literals with the
+  predicate $P$}.
+
 \begin{definition}[Model]\label{def:model}
@@
   \end{enumerate*}
-  Then a \emph{structure} of $\phi$ (with respect to $\sigma$) is a set $M$ of
-  ground literals defined by adding either $P(\mathbf{t})$ or
+  (In practice, we typically only specify the size of each domain.) A
+  \emph{structure} of $\phi$ (with respect to $\sigma$) is a set $M$ of ground
+  literals defined by adding to $M$ either $P(\mathbf{t})$ or
   $\neg P(\mathbf{t})$ for every predicate $P/n$ in $\phi$ and $n$-tuple
@@
 \end{definition}
-% TODO: adding to what
-
-% TODO: “Weights in Q” undefined, C2 undefined (and also far from well explained
-% before), endofunction undefined (also endomorphisms missing), weight function
-% undefined, weighted model count imprecise (above it’s called weighted
-% first-order model count/wfmoc),
+
+\begin{remark}
+  The distinctness of domains is important in two ways. First, in terms of
+  expressiveness, clauses such as $\forall x \in \Delta\text{. }P(x, x)$ are
+  valid if predicate $P$ is defined over two copies of the same domain and
+  invalid otherwise. Second, having more distinct domains makes the problem more
+  decomposable for the FOKC algorithm. With more distinct domains, the algorithm
+  can make assumptions or deductions about, e.g., the first domain of predicate
+  $P$ without worrying how (or if) they apply to the second domain.
+\end{remark}
+
+\begin{definition}[WFOMC Instance]\label{def:instance}
+  A \emph{WFOMC instance} comprises of:
+  \begin{enumerate*}[label=(\roman*)]
+    \item a formula $\phi$ in \FO{},
+    \item two (rational) \emph{weights} $w^{+}(P)$ and $w^{-}(P)$ assigned to
+    each predicate $P$ in $\phi$, and
+    \item $\sigma$ as described in \cref{def:model}.
+  \end{enumerate*}
+  Unless specified otherwise, we assume all weights to be equal to 1.
+\end{definition}
+
 \begin{definition}[WFOMC~\cite{DBLP:conf/ijcai/BroeckTMDR11}]
-  Continuing from \cref{def:model}, for each predicate $P$ in $\phi$, let
-  $w^{+}(P)$ and $w^{-}(P)$ be its \emph{weights} in $\mathbb{Q}$. Unless
-  specified otherwise, we assume all weights are equal to 1. The
-  \emph{(symmetric) weighted first-order model count} (WFOMC) of $\phi$ (with
-  respect to $\sigma$, $w^{+}$, and $w^{-}$) is:
-  \[
+  Given a WFOMC instance $(\phi, w^{+}, w^{-}, \sigma)$ as in
+  \cref{def:instance}, the \emph{(symmetric) weighted first-order model count}
+  (WFOMC) of $\phi$ (with respect to $\sigma$, $w^{+}$, and $w^{-}$) is
+  \begin{equation}\label{eq:wfomc}
     \sum_{M \models \phi} \prod_{P(\mathbf{t}) \in M} w^{+}(P) \prod_{\neg P(\mathbf{t}) \in M} w^{-}(P),
-  \]
+  \end{equation}
   where the sum is over all models of $\phi$.
@@
 \begin{example}[Counting functions]\label{example:functions}
-  To define predicate $P$ as an endofunction on $\Delta$, in \Ctwo{} one would
-  write $\forall x \in \Delta\text{. }\exists^{=1} y \in \Delta\text{.
-  }P(x, y)$. In \UFO{}, the same could be written as
+  To define predicate $P$ as a function from a domain $\Delta$ to itself, in
+  \Ctwo{} one would write $\forall x \in \Delta\text{.
+  }\exists^{=1} y \in \Delta\text{. }P(x, y)$. In \UFO{}, the same could be
+  written as
   \begin{equation}\label[formula]{eq:functions1}
     \begin{gathered}
-      \forall x, y \in \Delta\text{. }S(x) \lor \neg P(x, y)\\
-      |P| = |\Delta|,
+      (\forall x, y \in \Delta\text{. }S(x) \lor \neg P(x, y)) \land{}\\
+      (|P| = |\Delta|),
     \end{gathered}
@@
   where $w^{-}(S) = -1$. Although \cref{eq:functions1} has more models compared
-  to its counterpart in \Ctwo{}, the weight function makes the \emph{weighted}
-  model count of \cref{eq:functions1} equal to the number of endofunctions on
-  $\Delta$.
-
-  % TODO: Yes, as mentioned at the end of Section 2.1, clauses c and d written
-  % on separate lines are to be interpreted as the conjunction of c and d (maybe
-  % move that sentence here?).
+  to its counterpart in \Ctwo{}, the negative weight $w^{-}(S) = -1$ makes some
+  of the terms in \cref{eq:wfomc} cancel out.
+
   Equivalently, in \FO{} we would write
@@
     \begin{gathered}
-      \forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }P(x, y)\\
-      \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z.
+      (\forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }P(x, y)) \land{}\\
+      (\forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z).
     \end{gathered}
@@
   \cref{eq:fo} is written with two domains instead of just one. However, we can
-  still determine the number of endofunctions by assuming that the sizes of
+  still determine the correct number of functions by assuming that the sizes of
   $\Gamma$ and $\Delta$ are equal. This formulation, as observed by
   \citeauthor{DBLP:conf/kr/DilkasB23}~\shortcite{DBLP:conf/kr/DilkasB23}, can
-  prove beneficial in enabling first-order knowledge compilation algorithms to
-  find efficient solutions.
+  prove beneficial in enabling FOKC algorithms to find efficient solutions.
 \end{example}
@@
 
-\section{Completing the Definitions of Recursive Functions}\label{sec:main}
-% TODO: As mentioned in the caption of Figure 1, "Compile" refers to the
-% knowledge compilation algorithm of Dilkas and Belle (2023). Its three return
-% values are explained at the beginning of page 4. We do not elaborate on the
-% details of "Simplify" as it primarily consists of elementary algebraic
-% simplifications such as "1x = x" and "0x = 0". However, we highlight one
-% non-trivial aspect of "Simplify" right before Section 3.1. We will improve the
-% structure of Section 3 to make this information more readily available. Maybe
-% write Crane instead of Compile?
-
-% TODO: It would not be entirely accurate to call the algorithms presented in
-% this work a "post-processing step" because Algorithm 1 is recursive. In other
-% words, this "post-processing step" to first-order knowledge compilation can
-% lead to more compilation that then updates/completes the original set of
-% equations.
+\section{Completing the Definitions of Functions}\label{sec:main}
+
 \begin{algorithm}[t]
@@
     $\psi \gets \mathcal{F}(f)$\;
-    \ForEach{$i$ such that $x_{i} \in \mathbb{N}_{0}$}{
+    \ForEach{index $i$ such that $x_{i} \in \mathbb{N}_{0}$}{\label{line:loop}
       $\psi \gets \Propagate{$\psi$, $\mathcal{D}(f, i)$, $x_i$}$\;
     }
-    $\mathcal{E} \gets \mathcal{E} \cup \CompileWithBaseCases{$\psi$}$\;
+    $\mathcal{E} \gets \mathcal{E} \cup \CompileWithBaseCases{$\psi$}$\;\label{line:final}
   }
 \end{algorithm}
-% TODO: >> Alg 1, line 5: Why is this not an infinite loop? On line 5 of
-% Algorithm 1, the loop iterates over the indices of \mathbf{x}. The arity of a
-% function is always a finite number, typically equal to 1 or 2.
 
 \Cref{alg:compilewithbasecases} presents our overall approach for compiling a
-formula into equations that include the necessary base cases. To begin, we
-utilise the knowledge compilation algorithm from the original \textsc{Crane} to
-compile the formula into three components:
+formula into equations that include the necessary base cases. To begin, we use
+the FOKC algorithm of the original \textsc{Crane} to compile the formula into
+three components:
 \begin{enumerate*}[label=(\roman*)]
@@
 \end{enumerate*}
-After some algebraic simplification, $\mathcal{E}$ is then passed to the
-\FindBaseCases procedure (explained in \cref{sec:identifying}), which identifies
-the base cases that need to be defined. For each base case $f(\mathbf{x})$, we
-determine the formula associated with the function name $f$ and simplify it
-using the \Propagate procedure (explained in \cref{sec:simplifying}). The
-algorithm then calls itself on these simplified formulas and adds the resulting
-base case equations to $\mathcal{E}$. \Cref{example:overall} provides a more
-detailed explanation of \cref{alg:compilewithbasecases}.
-
-% TODO: F missing (also not explained that it’s not needed below).
-E is not explained other than that we take the example from X.
-Would not be a problem if it is motivated differently and the focus is on post-processing (defining inputs properly) and not on the entire algorithm.
+After some algebraic simplification (explained at the end of this section),
+$\mathcal{E}$ is passed to the \FindBaseCases procedure (explained in
+\cref{sec:identifying}), which identifies the base cases that need to be
+defined.
+
+For each base case $f(\mathbf{x})$, we retrieve the logical formula
+$\mathcal{F}(f)$ associated with the function name $f$ and simplify it using the
+\Propagate procedure (explained in detail in \cref{sec:simplifying}). We do this
+by iterating over all indices of $\mathbf{x}$, where $x_{i}$ is a constant, and
+using \Propagate to simplify $\psi$ by assuming that domain $\mathcal{D}(f, i)$
+has size $x_{i}$. Finally, on \cref{line:final}, \CompileWithBaseCases recurses
+on these simplified formulas and adds the resulting base case equations to
+$\mathcal{E}$. \Cref{example:overall} below provides more detail.
+
+\begin{remark}
+  Although \CompileWithBaseCases starts with a call to \textsc{Crane}, the
+  proposed algorithm is not just a post-processing step for FOKC because
+  \cref{alg:compilewithbasecases} is recursive and can issue more calls to
+  \textsc{Crane} on various derived formulas.
+\end{remark}
+
+% TODO: F missing
+
+% TODO: E is not explained other than that we take the example from X
+
 % TODO: include a high-level overview of first-order knowledge compilation and the meaning of the resulting functions.
@@
     \begin{gathered}
-      \forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }P(x, y)\\
-      \forall y \in \Delta\text{. }\exists x \in \Gamma\text{. }P(x, y)\\
-      \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z\\
-      \forall x, z \in \Gamma\text{. }\forall y \in \Delta\text{. }P(x, y) \land P(z, y) \Rightarrow x = z.
+      (\forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }P(x, y))\land{}\\
+      (\forall y \in \Delta\text{. }\exists x \in \Gamma\text{. }P(x, y))\land{}\\
+      (\forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z)\land{}\\
+      (\forall x, z \in \Gamma\text{. }\forall y \in \Delta\text{. }P(x, y) \land P(z, y) \Rightarrow x = z).
     \end{gathered}
@@
 
-% TODO: maybe omit the word 'iverson'...
-Finally, we highlight the crucial role of the \Simplify procedure in simplifying
-the algebraic pattern $\sum_{m=0}^{n}[a \le m \le b] f(m)$. Here:
+Finally, we main responsibility of the \Simplify procedure is in handling the
+algebraic pattern $\sum_{m=0}^{n}[a \le m \le b] f(m)$. Here:
 \begin{enumerate*}[label=(\roman*)]
@@
     0 & \text{otherwise}
-  \end{cases}$ represents the Iverson bracket.
+  \end{cases}$.
 \end{enumerate*}
@@
 \cref{example:overall}, \Simplify transforms
-$g(l, m) = \sum_{k=0}^{m}[0 \le k \le 1]\binom{m}{k}g(l-1, m-k)$ into the
-simplified form mentioned above.
+$g(l, m) = \sum_{k=0}^{m}[0 \le k \le 1]\binom{m}{k}g(l-1, m-k)$ into
+$g(l, m) = g(l-1, m) + mg(l-1, m-1)$.
 
@@
 \end{algorithm}
+% TODO: replace x_i-c_i on Line 7 of Algorithm 2 with a generalisation of x_i
+% that can be an arbitrary summation/subtraction of domain sizes (propagating
+% this change to the rest of the paper)
+
+% TODO: a function call with a constant should always mean that that function
+% should have a base case, not just when it's in the same function
 
@@
         $C' \gets \{\, l \in C \mid \Delta \not\in \Doms(l) \,\}$\;
-        \If{$C' \ne \emptyset$}{
+        \If{$C' \ne \emptyset$}{\label{line:presmoothing}
           $l \gets \text{an arbitrary literal in } C'$\;\label{line:smoothing1}
@@
 the assumption that $|\Delta| = n$. When $n=0$, some clauses become vacuously
-satisfied and can be removed. When $n > 0$\footnote{None of the formulas
-  examined in this study had $n > 1$.}, partial grounding is performed by
-replacing all variables quantified over $\Delta$ with constants.
-\Cref{alg:propagate} handles these two cases separately. For a literal or a
-clause $C$, the set of corresponding domains is denoted as $\Doms(C)$.
+satisfied and can be removed. When $n > 0$, partial grounding is performed by
+replacing all variables quantified over $\Delta$ with constants. (None of the
+formulas examined in this work had $n > 1$.) \Cref{alg:propagate} handles these
+two cases separately. For a literal or a clause $C$, the set of corresponding
+domains is denoted as $\Doms(C)$.
 
@@
   \begin{align*}
-    \forall x \in \Gamma\text{. }\neg P(x, c_{1}) \lor& \neg P(x, c_{1}) \lor c_{1}=c_{1}\\
-    \forall x \in \Gamma\text{. }\neg P(x, c_{1}) \lor& \neg P(x, c_{2}) \lor c_{1}=c_{2}\\
+    (\forall x \in \Gamma\text{. }\neg P(x, c_{1}) \lor& \neg P(x, c_{1}) \lor c_{1}=c_{1})\land{}\\
+    (\forall x \in \Gamma\text{. }\neg P(x, c_{1}) \lor& \neg P(x, c_{2}) \lor c_{1}=c_{2})\land{}\\
     \vdots&\\
-    \forall x \in \Gamma\text{. }\neg P(x, c_{3}) \lor& \neg P(x, c_{3}) \lor c_{3}=c_{3}.\\
+    (\forall x \in \Gamma\text{. }\neg P(x, c_{3}) \lor& \neg P(x, c_{3}) \lor c_{3}=c_{3}).\\
   \end{align*}
@@
 \cref{line:smoothing1,line:smoothing2} of \cref{alg:propagate}.
-
-% TODO: To be precise, line 7 of Algorithm 3 checks whether smoothing is
-% necessary, and lines 8-9 execute it. If the condition on line 7 is not
-% satisfied, the clause is not smoothed but rather completely omitted.
+\Cref{line:presmoothing} checks whether smoothing is necessary, and
+\cref{line:smoothing1,line:smoothing2} execute it. If the condition on
+\cref{line:presmoothing} is not satisfied, the clause is not smoothed but rather
+completely omitted.
 
@@
 means we are simplifying the formula $\phi$ by assuming that the domain $\Delta$
-is empty. Informally, if there is a predicate $P$ in $\phi$ that has nothing to
-do with the domain $\Delta$, smoothing preserves all occurrences of $P$ even if
-all clauses with $P$ become vacuously satisfied. It is important to note that
-the approach presented in this section is not unique. We explain it via the
-example below.
-% TODO: In this context, "not unique" means that there are many different ways
-% to adjust/rewrite the formula to achieve the goal of smoothing. This section
-% (and Algorithm 3) presents one such approach.
+is empty. Informally, if there is a predicate $P$ in $\phi$ unrelated to
+$\Delta$, smoothing preserves all occurrences of $P$ even if all clauses with
+$P$ become vacuously satisfied.
 
@@
   \begin{align}
-    \forall x \in \Delta\text{. }\forall y, z \in \Gamma&\text{. }Q(x) \lor P(y, z)\label[clause]{eq:example1}\\
-    \forall y, z \in \Gamma'&\text{. }P(y, z)\label[clause]{eq:example2},
+    (\forall x \in \Delta\text{. }\forall y, z \in \Gamma&\text{. }Q(x) \lor P(y, z))\land{}\label[clause]{eq:example1}\\
+    (\forall y, z \in \Gamma'&\text{. }P(y, z))\label[clause]{eq:example2},
   \end{align}
@@
   \begin{gather*}
-    \forall y, z \in \Gamma\text{. }P(y, z) \lor \neg P(y, z)\\
-    \forall y, z \in \Gamma'\text{. }P(y, z),
+    (\forall y, z \in \Gamma\text{. }P(y, z) \lor \neg P(y, z))\land{}\\
+    (\forall y, z \in \Gamma'\text{. }P(y, z)),
   \end{gather*}
@@
 \section{Experimental Evaluation}\label{sec:experiments}
-% TODO: A WFOMC instance comprises of a formula in first-order logic, a pair of
-% weights for each predicate, and a domain size (i.e., a non-negative integer)
-% for each domain. We provide the full details of all of these, including how
-% the formulas ought to be rewritten to fit the format of each WFOMC algorithm.
-
 % TODO: must rerun on an HPC and include more instances
 
-% TODO: "hard to follow", pointing to the DPMC paper as a good example
+% TODO: this section is apparently "hard to follow"
 
@@
 equivalent formula in \Ctwo{} is
-\begin{gather*}
-  \forall x \in \Delta\text{. }\exists^{=1} y \in \Delta\text{. }P(x, y)\\
-  \forall y \in \Delta\text{. }\exists^{=1} x \in \Delta\text{. }P(x, y).
-\end{gather*}
+\begin{align*}
+  (\forall x \in \Delta\text{. }\exists^{=1} y \in \Delta&\text{. }P(x, y))\land{}\\
+  (\forall y \in \Delta\text{. }\exists^{=1} x \in \Delta&\text{. }P(x, y)).
+\end{align*}
 Similarly, in \UFO{} the same formula can be written as
 \begin{gather*}
-  \forall x, y \in \Delta\text{. }R(x) \lor \neg P(x, y)\\
-  \forall x, y \in \Delta\text{. }S(x) \lor \neg P(y, x)\\
-  |P| = |\Delta|,
+  (\forall x, y \in \Delta\text{. }R(x) \lor \neg P(x, y))\land{}\\
+  (\forall x, y \in \Delta\text{. }S(x) \lor \neg P(y, x))\land{}\\
+  (|P| = |\Delta|),
 \end{gather*}
@@
 
+% TODO: no overfull boxes (might be the fault of the figure)
+
+% TODO: must not use 'input' command. instead, compile to a pdf
+
 In the first experiment, we ran each of the four algorithms once on each
@@
 \Cranetwo{} than in \textsc{ForcLift}, the difference is negligible. The
-runtimes of the knowledge compilation algorithms appear constant because, for
-these counting problems and domain sizes, compilation time dominates inference
-time (remember that compilation time is independent of domain sizes). Indeed,
-the maximum inference time of \Cranebfs{} and \Cranegreedy{} across these
-experiments is only \SI{4}{\milli\second}. The runtimes of \Cranetwo{} have
-lower variation than those of \textsc{ForcLift} because we compile the formula
-anew for each domain size with \textsc{ForcLift}, whereas with \Cranetwo{}, we
-compile it once and reuse the resulting C++ program for all domain sizes.
+runtimes of the FOKC algorithms appear constant because, for these counting
+problems and domain sizes, compilation time dominates inference time (remember
+that compilation time is independent of domain sizes). Indeed, the maximum
+inference time of \Cranebfs{} and \Cranegreedy{} across these experiments is
+only \SI{4}{\milli\second}. The runtimes of \Cranetwo{} have lower variation
+than those of \textsc{ForcLift} because we compile the formula anew for each
+domain size with \textsc{ForcLift}, whereas with \Cranetwo{}, we compile it once
+and reuse the resulting C++ program for all domain sizes.
 % TODO: The lines for Crane2 in Figure 4 appear to be completely flat whereas
@@
 \end{document}
-
-% TODO:
-% must clean pdf metadata before submitting
-% make sure that it's not automatically deducible that I'm the author of Crane
-% no type 3 fonts (including in the PDFs of figures)
-% no overfull boxes (might be the figure)
-% no embedded links (but URLs are fine as long as they're not clickable?)
-% must not use 'input' command. instead, compile to a pdf
-% figures should appear on the page where they are discussed or on the next page
-% colors in figures must be cmyk, not rgb
-% references must not have missing fields

### 2024-07-17 doc/paper/paper.tex
A wrapper for FastWFOMC.jl

@@
 % [1] Richardson, M., & Domingos, P. (2006). Markov logic networks. Machine learning, 62, 107-136.
+
+% TODO: (somewhere) The implementation is only for unweighted (but the
+% definition of WFOMC is still necessary because of Skolemization).
 
@@
   $\mathcal{B} \gets \emptyset$\;
-  \ForEach{equation $(f(\mathbf{x}) = \expr{}) \in \mathcal{E}$}{
-    \ForEach{function call $f(\mathbf{y}) \in \expr{}$}{\label{line:functioncall}
+  \ForEach{function call $f(\mathbf{y})$ on the right-hand side of an equation in $\mathcal{E}$}{\label{line:functioncall}
+    $\mathbf{x} \gets \text{the parameters of $f$ in its definition}$\;
     \ForEach{$y_{i} \in \mathbf{y}$} {
@@
   }
-  }
 \end{algorithm}
-% TODO: replace x_i-c_i on Line 7 of Algorithm 2 with a generalisation of x_i
-% that can be an arbitrary summation/subtraction of domain sizes (propagating
-% this change to the rest of the paper)
-
-% TODO: a function call with a constant should always mean that that function
-% should have a base case, not just when it's in the same function
+% TODO (later, let's not bother yet): replace x_i-c_i on Line 7 of Algorithm 2
+% with a generalisation of x_i that can be an arbitrary summation/subtraction of
+% domain sizes (propagating this change to the rest of the paper, particularly
+% Assumption 1, the proof of Lemma 1)
 
@@
 \begin{example}
-  Let us consider the recursive function $g$ from \cref{example:overall}. In
-  this case, \FindBaseCases iterates over two function calls: $g(l-1, m)$ and
+  Consider the recursive function $g$ from \cref{example:overall}. Then
+  \FindBaseCases iterates over two function calls: $g(l-1, m)$ and
   $g(l-1, m-1)$. The former produces the base case $g(0, m)$, while the latter
@@
 considered before the recursive definition. The exact order in which base cases
-are considered is not relevant.
+are considered is immaterial.
 
@@
 
-With the facts and assumptions mentioned above, we prove the following theorem.
+With the observations and assumptions mentioned above, we prove the following
+theorem.
 
@@
   Otherwise, let $f(y)$ be an arbitrary function call on the right-hand side of
-  the definition of $f(x)$. If $y$ is a constant, there is a base case for
+  the definition of $f(x)$. If $y$ is a constant, then there is a base case for
   $f(y)$. Otherwise, let $y = x - c$ for some $c > 0$. Then there exists
@@
 \section{Experimental Evaluation}\label{sec:experiments}
-% TODO: must rerun on an HPC and include more instances
-
 % TODO: this section is apparently "hard to follow"
@@
 
-% TODO: maybe instead of a table I should have an experiment where:
-% 1) Crane scales exponentially (with a base of sqrt(2))
-% 2) other algorithm scale linearly
-% 3) Then I can just draw the usual cumulative plot
-% 4) Stop each algorithm when they reach the timeout value
-
 % TODO: (here or in the introduction) C++ code generation is necessary for any
@@
 
-% TODO: I'm claiming that C++ code generation is not the main contribution, but
-% the experiments are mainly about it...
-
 % TODO: The asymptotic analysis of the total number of arithmetic operations
 % required to compute the FOMC of these formulas was already performed in
-% previous work [1].
+% previous work.
 
@@
 % because each problem has to be represented in two (fairly different) logics:
-% FO and UFO^2+EQ.
-
-% TODO: position some of the experiments as 'practical'
+% \FO{} and \UFO{}.
 

### 2024-07-17 FastWFOMC_example.jl

@@ -1,25 +1,0 @@
-using FastWFOMC
-
-formula = parse_formula(
-    "~E(x, x) & " *
-    "(~E(x, y) | E(y, x)) & " *
-    "(~F(x, y) | E(x, y)) & " *
-    "(F(x, y) | ~E(x, y)) & " *
-    "(S1(x) | ~F1(x, y)) & " *
-    "(S2(x) | ~F2(x, y)) & " *
-    "(S3(x) | ~F3(x, y)) & " *
-    "(~F(x, y) | F1(x, y) | F2(x, y) | F3(x, y)) & " *
-    "(F(x, y) | ~F1(x, y)) & " *
-    "(F(x, y) | ~F2(x, y)) & " *
-    "(F(x, y) | ~F3(x, y)) & " *
-    "(~F1(x, y) | ~F2(x, y)) & " *
-    "(~F1(x, y) | ~F3(x, y)) & " *
-    "(~F2(x, y) | ~F3(x, y))"
-);
-
-n = 6
-weights = WFOMCWeights{Rational{BigInt}}(("S1", 1) => (1, -1), ("S2", 1) => (1, -1), ("S3", 1) => (1, -1))
-fill_missing_weights!(weights, formula)
-
-count = compute_wfomc(formula, n, weights; ccs=[CardinalityConstraint(("F", 2), 3n)])
-@show(count)

### 2024-07-17 FastWFOMC_wrapper.jl

@@ -1,0 +1,50 @@
+using ArgParse
+using JSON
+using FastWFOMC
+
+function main()
+    parser = ArgParseSettings()
+    @add_arg_table parser begin
+        "instance"
+        help = "WFOMC instance (in a custom JSON format)"
+        required = true
+
+        "domainsize"
+        help = "domain size"
+        required = true
+        arg_type = Int
+    end
+
+    args = parse_args(parser)
+    instance_file = args["instance"]
+    domainsize = args["domainsize"]
+
+    # Load JSON instance
+    instance = JSON.parsefile(instance_file)
+
+    # Parse the formula
+    formula = parse_formula(instance["formula"])
+
+    # Parse arities
+    arities = Dict{String, Int}([(k, v) for (k, v) in instance["arities"]])
+
+    # Parse cardinalities and weights
+    cardinalities = [(x, domainsize * y) for (x, y) in instance["cardinalities"]]
+    weights_data = instance["weights"]
+    weights = if !isempty(weights_data)
+        WFOMCWeights{Rational{BigInt}}([(k, arities[k]) => (v[1], v[2]) for (k, v) in weights_data])
+    else
+        WFOMCWeights{Rational{BigInt}}()
+    end
+    fill_missing_weights!(weights, formula)
+
+    # Create cardinality constraints with arities
+    ccs = [CardinalityConstraint((x, arities[x]), y) for (x, y) in cardinalities]
+
+    # Compute WFOMC
+    count = compute_wfomc(formula, domainsize, weights; ccs=ccs)
+    println("WFOMC: ", count)
+end
+
+# Run the script
+main()

### 2024-07-18 build/fastwfomc_wrapper.sh
Preparing for a new round of experiments

@@ -1,9 +1,6 @@
 #!/usr/bin/env sh
 
-cd fastwfomc
-source virtualenvwrapper.sh
-workon fastwfomc
-for ((i=1; i<=$1; i++)); do
+for ((i=1; ; i++)); do
     echo "Domain size: $i"
-    ulimit -t $3 -c 0 && /usr/bin/time -f "Elapsed: %e" python wrapper.py $2 $i || exit 1
+    ulimit -t $2 -c 0 && /usr/bin/time -f "Elapsed: %e" julia --project=../deps/FastWFOMC.jl fastwfomc_wrapper.jl $1 $i || exit 1
 done

### 2024-07-18 build/forclift_wrapper.sh

@@ -1,8 +1,8 @@
 #!/usr/bin/env sh
 
-cd ../lib/Forclift
-for ((i=1; i<=$1; i++)); do
+cd ../deps/Forclift
+for ((i=1; ; i++)); do
     echo "Domain size: $i"
-    sed -i "s/\.\.\.,[[:digit:]]\+/\.\.\.,$i/g" $2
-    ulimit -t $3 -c 0 && /usr/bin/time -f "Elapsed: %e" java -jar target/scala-2.11/crane-assembly-1.0.jar -z --format-in mln $2 || exit 1
+    sed -i "s/\.\.\.,[[:digit:]]\+/\.\.\.,$i/g" $1
+    ulimit -t $2 -c 0 && /usr/bin/time -f "Elapsed: %e" java -jar target/scala-2.11/crane-assembly-1.0.jar -z --format-in mln $2 || exit 1
 done

### 2024-07-25 analysis/parse.py
Some of the preparations for a new set of experiments (including scaling FastWFOMC domains exponentially, since it's faster now)

@@ -1,20 +1,28 @@
 #!/usr/bin/env python3
 
 from collections import defaultdict
+from datetime import datetime
 import csv
 import os
 
-RESULTS_DIR = 'results'
-RESULTS_FILE = 'results.csv'
-FIELDNAMES = ['algorithm', 'sequence', 'domain.size', 'count', 'compilation.time', 'inference.time']
-TIMEOUT = 3600000
+RESULTS_DIR = '../results/raw'
+RESULTS_FILE = '../results/processed/{}.csv'.format(
+    datetime.now().strftime('%Y%m%d%H%M%S'))
+FIELDNAMES = [
+    'algorithm',
+    'sequence',
+    'domain.size',
+    'count',
+    'compilation.time',
+    'inference.time']
+TIMEOUT = 15
 VERBOSE = False
 
-sequences = {}
-with open('sequences.csv', newline='') as f:
-    reader = csv.DictReader(f, delimiter=';')
-    for row in reader:
-        sequences[int(row['id'])] = [int(x) for x in row['sequence'].split(',')]
+# sequences = {}
+# with open('sequences.csv', newline='') as f:
+#     reader = csv.DictReader(f, delimiter=';')
+#     for row in reader:
+#         sequences[int(row['id'])] = [int(x) for x in row['sequence'].split(',')]
 
 rows = []
 incorrect_count = 0
@@ -30,9 +38,9 @@ for filename in os.listdir(RESULTS_DIR):
     total_times = []
     with open(RESULTS_DIR + '/' + filename) as f:
         for line in f.readlines():
-            if line.startswith('Compilation time:'): # Crane
+            if line.startswith('Compilation time:'):  # Crane
                 data['compilation.time'] = line.split()[2]
-            elif line.startswith('The model count'): # Crane
+            elif line.startswith('The model count'):  # Crane
                 tokens = line.split()
                 domains.append(tokens[7][:-1])
                 if tokens[8] == 'TIMEOUT':
@@ -41,24 +49,24 @@ for filename in os.listdir(RESULTS_DIR):
                 else:
                     counts.append(tokens[8].translate({ord(','): None}))
                     times.append(tokens[10])
-            elif line.startswith('Domain size:'): # ForcLift and FastWFOMC
+            elif line.startswith('Domain size:'):  # ForcLift and FastWFOMC
                 domains.append(line.split()[2])
-            elif line.startswith('Z = '): # ForcLift
+            elif line.startswith('Z = '):  # ForcLift
[…]

### 2024-07-25 build/fastwfomc_wrapper.sh

@@ -1,6 +1,7 @@
 #!/usr/bin/env sh
 
 for ((i=1; ; i++)); do
-    echo "Domain size: $i"
-    ulimit -t $2 -c 0 && /usr/bin/time -f "Elapsed: %e" julia --project=../deps/FastWFOMC.jl fastwfomc_wrapper.jl $1 $i || exit 1
+    j=$((2 ** $i))
+    echo "Domain size: $j"
+    ulimit -t $2 -c 0 && /usr/bin/time -f "Elapsed: %e" julia --project=../deps/FastWFOMC.jl fastwfomc_wrapper.jl $1 $j || exit 1
 done

### 2024-07-25 build/forclift_wrapper.sh

@@ -4,5 +4,9 @@ cd ../deps/Forclift
 for ((i=1; ; i++)); do
     echo "Domain size: $i"
     sed -i "s/\.\.\.,[[:digit:]]\+/\.\.\.,$i/g" $1
-    ulimit -t $2 -c 0 && /usr/bin/time -f "Elapsed: %e" java -jar target/scala-2.11/crane-assembly-1.0.jar -z --format-in mln $2 || exit 1
+    output=$(ulimit -t $2 -c 0 && /usr/bin/time -f "Elapsed: %e" java -jar target/scala-2.11/crane-assembly-1.0.jar -z --format-in mln $1 2>&1)
+    echo $output
+    if [[ $output == *"Infinity"* ]] || [[ $output == *"Cannot"* ]] || [[ $output == *"Exception"* ]]; then
+        exit 0
+    fi
 done

### 2024-07-26 analysis/analyse.R
Misc improvements to the experimental setup, parsing, etc.

@@ -2,7 +2,7 @@ library(tidyverse)
 library(scales)
 library(tikzDevice)
 
-df <- read.csv("../results/processed/results1.csv")
+df <- read.csv("../results/processed/results.csv")
 df$compilation.time <- df$compilation.time / 1000
 df$inference.time <- df$inference.time / 1000
 df$time <- df$compilation.time + df$inference.time
@@ -17,13 +17,17 @@ df$algorithm[df$algorithm == "fastwfomc"] <- "\\textsc{FastWFOMC}"
 #  summarise(diff = 100 * (max(count) - min(count)) / min(count))
 
 tikz(file = "../doc/plot.tex", width = 3.32492194445, height = 1.8702685937531252)
-ggplot(df, aes(domain.size, time, colour = algorithm, linetype = sequence)) +
+ggplot(df[df$sequence == "friends",],
+       aes(domain.size, time, colour = algorithm, linetype = algorithm,
+           shape = algorithm)) +
   geom_line() +
-  scale_y_continuous(trans = log10_trans()) +
+  geom_point() +
+  scale_x_continuous(trans = log2_trans()) +
+  scale_y_continuous(trans = log2_trans()) +
   annotation_logticks(sides = "l", colour = "#b3b3b3") +
   ylab("Total runtime (s)") +
   xlab("Domain size") +
-  labs(color = "", linetype = "") +
+  labs(color = "", linetype = "", shape = "") +
   scale_color_brewer(palette = "Dark2") +
   theme_light(base_size = 9)
 dev.off()

### 2024-07-26 analysis/parse.py

@@ -1,13 +1,11 @@
 #!/usr/bin/env python3
 
 from collections import defaultdict
-from datetime import datetime
 import csv
 import os
 
 RESULTS_DIR = '../results/raw'
-RESULTS_FILE = '../results/processed/{}.csv'.format(
-    datetime.now().strftime('%Y%m%d%H%M%S'))
+RESULTS_FILE = '../results/processed/results.csv'
 FIELDNAMES = [
     'algorithm',
     'sequence',
@@ -15,8 +13,17 @@ FIELDNAMES = [
     'count',
     'compilation.time',
     'inference.time']
-TIMEOUT = 15
-VERBOSE = False
+TIMEOUT = 15 * 1000  # in ms
+
+def chop_trailing_empty_strings(lst):
+    # Iterate from the end to find the first non-empty string
+    last_non_empty_index = len(lst)
+    for i in range(len(lst) - 1, -1, -1):
+        if lst[i] != '':
+            last_non_empty_index = i + 1
+            break
+    # Slice the list to remove trailing empty strings
+    return lst[:last_non_empty_index]
 
 # sequences = {}
 # with open('sequences.csv', newline='') as f:
@@ -28,8 +35,7 @@ rows = []
 incorrect_count = 0
 failed_count = defaultdict(lambda: 0)
 for filename in os.listdir(RESULTS_DIR):
-    if VERBOSE:
-        print('Parsing', filename)
+    print('Parsing', filename)
     data = {}
     data['sequence'], data['algorithm'] = filename.split('.')
     domains = []
@@ -54,7 +60,10 @@ for filename in os.listdir(RESULTS_DIR):
             elif line.startswith('Z = '):  # ForcLift
                 try:
                     counts.append(int(round(float(line.split()[4]))))
-                except ValueError:  # Record 'NaN' as a compilation error
+                except OverflowError:  # Record 'Infinity' as a timeout
+                    counts.append('')
+                except ValueError:
+                    # Record 'NaN' as a compilation error
                     domains = []
                     total_times = []
                     break
@@ -68,29 +77,25 @@ for filename in os.listdir(RESULTS_DIR):
             elif line.startswith('WFOMC:'):  # FastWFOMC
                 counts.append(line.split()[1][:-3])
 
+    # Ignore the timeouts at the end
+    counts = chop_trailing_empty_strings(counts)
+    domains = domains[:len(counts)]
+    times = times[:len(counts)]
+    if len(total_times) != 0:
+        total_times = total_times[:len(counts)]
+
[…]

### 2024-07-26 build/forclift_wrapper.sh

@@ -1,12 +1,18 @@
 #!/usr/bin/env sh
 
-cd ../deps/Forclift
-for ((i=1; ; i++)); do
+cd ../deps/Forclift || exit 1
+for ((k=1; ; k++)); do
+    i=$((2 ** $k))
     echo "Domain size: $i"
-    sed -i "s/\.\.\.,[[:digit:]]\+/\.\.\.,$i/g" $1
-    output=$(ulimit -t $2 -c 0 && /usr/bin/time -f "Elapsed: %e" java -jar target/scala-2.11/crane-assembly-1.0.jar -z --format-in mln $1 2>&1)
-    echo $output
-    if [[ $output == *"Infinity"* ]] || [[ $output == *"Cannot"* ]] || [[ $output == *"Exception"* ]]; then
+    sed -i "s/\.\.\.,[[:digit:]]\+/\.\.\.,$i/g" "$1"
+    error_found=false
+    while IFS= read -r line; do
+        echo "$line"
+        if echo "$line" | grep -qE "Infinity|Cannot|Exception|Error"; then
+            error_found=true
+        fi
+    done < <(ulimit -t "$2" -c 0 -Sv "$3" && /usr/bin/time -f "Elapsed: %e" java -jar target/scala-2.11/crane-assembly-1.0.jar -z --format-in mln "$1" 2>&1)
+    if $error_found; then
         exit 0
     fi
 done

### 2024-07-26 build/job.sh

@@ -1,0 +1,15 @@
+#!/bin/bash
+#SBATCH --nodes=1
+#SBATCH --cpus-per-task=40
+#SBATCH --time=00:05:00
+#SBATCH --job-name wfomc
+#SBATCH --output=output_%j.txt
+#SBATCH --mail-type=FAIL
+
+cd $SLURM_SUBMIT_DIR
+
+# TODO: module load intel/2018.2
+
+ulimit -c 0
+lscpu > cpuinfo.txt
+make -j 1

### 2024-07-30 doc/paper/plot.tex
Everything related to the new set of experiments (except for the results, which are too big to be stored here)

% Created by tikzDevice version 0.12.6 on 2024-07-30 13:11:15
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (505.89,216.81);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (505.89,216.81);
\end{scope}
\begin{scope}
\path[clip] ( 33.14, 57.56) rectangle (186.23,198.75);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] ( 33.14, 57.56) rectangle (186.23,198.75);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14, 70.17) --
	(186.23, 70.17);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14,101.68) --
	(186.23,101.68);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14,133.19) --
	(186.23,133.19);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14,164.70) --
	(186.23,164.70);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14,196.21) --
	(186.23,196.21);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 48.13, 57.56) --
	( 48.13,198.75);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 85.60, 57.56) --
	( 85.60,198.75);

\path[draw=drawColor,line width= 0.2pt,line join=round] (123.07, 57.56) --
	(123.07,198.75);

\path[draw=drawColor,line width= 0.2pt,line join=round] (160.53, 57.56) --
	(160.53,198.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 33.14, 85.92) --
	(186.23, 85.92);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 33.14,117.43) --
	(186.23,117.43);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 33.14,148.95) --
	(186.23,148.95);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 33.14,180.46) --
	(186.23,180.46);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 66.87, 57.56) --
	( 66.87,198.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (104.33, 57.56) --
	(104.33,198.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (141.80, 57.56) --
	(141.80,198.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (179.27, 57.56) --
	(179.27,198.75);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.10,106.36) --
	( 45.46,106.36) --
	( 50.81,106.36) --
	( 56.16,106.36) --
	( 61.51,106.36) --
	( 66.87,106.36) --
	( 72.22,106.37) --
	( 77.57,106.38) --
	( 82.92,106.42) --
	( 88.28,106.58) --
	( 93.63,107.23) --
	( 98.98,109.99) --
	(104.33,117.90);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 45.46,123.48) --
	( 50.81,112.22) --
	( 56.16,112.22) --
	( 61.51,112.42) --
	( 66.87,119.02) --
	( 72.22,162.96);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] ( 40.10,106.36) circle (  1.96);

\path[fill=fillColor] ( 45.46,106.36) circle (  1.96);

\path[fill=fillColor] ( 50.81,106.36) circle (  1.96);

\path[fill=fillColor] ( 56.16,106.36) circle (  1.96);

\path[fill=fillColor] ( 61.51,106.36) circle (  1.96);

\path[fill=fillColor] ( 66.87,106.36) circle (  1.96);

\path[fill=fillColor] ( 72.22,106.37) circle (  1.96);

\path[fill=fillColor] ( 77.57,106.38) circle (  1.96);

\path[fill=fillColor] ( 82.92,106.42) circle (  1.96);

\path[fill=fillColor] ( 88.28,106.58) circle (  1.96);

\path[fill=fillColor] ( 93.63,107.23) circle (  1.96);

\path[fill=fillColor] ( 98.98,109.99) circle (  1.96);

\path[fill=fillColor] (104.33,117.90) circle (  1.96);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] ( 43.49,121.52) --
	( 47.42,121.52) --
	( 47.42,125.44) --
	( 43.49,125.44) --
	cycle;

\path[fill=fillColor] ( 48.85,110.26) --
	( 52.77,110.26) --
	( 52.77,114.18) --
	( 48.85,114.18) --
	cycle;

\path[fill=fillColor] ( 54.20,110.26) --
	( 58.12,110.26) --
	( 58.12,114.18) --
	( 54.20,114.18) --
	cycle;

\path[fill=fillColor] ( 59.55,110.46) --
	( 63.47,110.46) --
	( 63.47,114.38) --
	( 59.55,114.38) --
	cycle;

\path[fill=fillColor] ( 64.90,117.06) --
	( 68.83,117.06) --
	( 68.83,120.99) --
	( 64.90,120.99) --
	cycle;

\path[fill=fillColor] ( 70.26,161.00) --
	( 74.18,161.00) --
	( 74.18,164.92) --
	( 70.26,164.92) --
	cycle;
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 34.75, 57.56) -- ( 34.75, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.10, 57.56) -- ( 40.10, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 45.46, 57.56) -- ( 45.46, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 50.81, 57.56) -- ( 50.81, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 56.16, 57.56) -- ( 56.16, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 61.51, 57.56) -- ( 61.51, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 66.87, 57.56) -- ( 66.87, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 72.22, 57.56) -- ( 72.22, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 77.57, 57.56) -- ( 77.57, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 82.92, 57.56) -- ( 82.92, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 88.28, 57.56) -- ( 88.28, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 93.63, 57.56) -- ( 93.63, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 98.98, 57.56) -- ( 98.98, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (104.33, 57.56) -- (104.33, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (109.69, 57.56) -- (109.69, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (115.04, 57.56) -- (115.04, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (120.39, 57.56) -- (120.39, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (125.74, 57.56) -- (125.74, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (131.10, 57.56) -- (131.10, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (136.45, 57.56) -- (136.45, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (141.80, 57.56) -- (141.80, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (147.15, 57.56) -- (147.15, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (152.51, 57.56) -- (152.51, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (157.86, 57.56) -- (157.86, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (163.21, 57.56) -- (163.21, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (168.56, 57.56) -- (168.56, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (173.92, 57.56) -- (173.92, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (179.27, 57.56) -- (179.27, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (184.62, 57.56) -- (184.62, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 64.92) -- ( 38.84, 64.92);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 75.42) -- ( 38.84, 75.42);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 85.92) -- ( 38.84, 85.92);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 96.43) -- ( 38.84, 96.43);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,106.93) -- ( 38.84,106.93);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,117.43) -- ( 38.84,117.43);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,127.94) -- ( 38.84,127.94);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,138.44) -- ( 38.84,138.44);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,148.95) -- ( 38.84,148.95);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,159.45) -- ( 38.84,159.45);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,169.95) -- ( 38.84,169.95);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,180.46) -- ( 38.84,180.46);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,190.96) -- ( 38.84,190.96);
\end{scope}
\begin{scope}
\path[clip] (190.73, 57.56) rectangle (343.81,198.75);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] (190.73, 57.56) rectangle (343.81,198.75);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.2pt,line join=round] (190.73, 70.17) --
	(343.81, 70.17);

\path[draw=drawColor,line width= 0.2pt,line join=round] (190.73,101.68) --
	(343.81,101.68);

\path[draw=drawColor,line width= 0.2pt,line join=round] (190.73,133.19) --
	(343.81,133.19);

\path[draw=drawColor,line width= 0.2pt,line join=round] (190.73,164.70) --
	(343.81,164.70);

\path[draw=drawColor,line width= 0.2pt,line join=round] (190.73,196.21) --
	(343.81,196.21);

\path[draw=drawColor,line width= 0.2pt,line join=round] (205.71, 57.56) --
	(205.71,198.75);

\path[draw=drawColor,line width= 0.2pt,line join=round] (243.18, 57.56) --
	(243.18,198.75);

\path[draw=drawColor,line width= 0.2pt,line join=round] (280.65, 57.56) --
	(280.65,198.75);

\path[draw=drawColor,line width= 0.2pt,line join=round] (318.12, 57.56) --
	(318.12,198.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (190.73, 85.92) --
	(343.81, 85.92);

\path[draw=drawColor,line width= 0.5pt,line join=round] (190.73,117.43) --
	(343.81,117.43);

\path[draw=drawColor,line width= 0.5pt,line join=round] (190.73,148.95) --
	(343.81,148.95);

\path[draw=drawColor,line width= 0.5pt,line join=round] (190.73,180.46) --
	(343.81,180.46);

\path[draw=drawColor,line width= 0.5pt,line join=round] (224.45, 57.56) --
	(224.45,198.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (261.91, 57.56) --
	(261.91,198.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (299.38, 57.56) --
	(299.38,198.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (336.85, 57.56) --
	(336.85,198.75);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (197.68, 87.62) --
	(203.04, 87.62) --
	(208.39, 87.61) --
	(213.74, 87.61) --
	(219.09, 87.61) --
	(224.45, 87.61) --
	(229.80, 87.61) --
	(235.15, 87.62) --
	(240.50, 87.69) --
	(245.86, 88.58) --
	(251.21, 97.29) --
	(256.56,123.32) --
	(261.91,157.55) --
	(267.27,192.33);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (197.68, 87.37) --
	(203.04, 87.37) --
	(208.39, 87.36) --
	(213.74, 87.36) --
	(219.09, 87.36) --
	(224.45, 87.36) --
	(229.80, 87.36) --
	(235.15, 87.37) --
	(240.50, 87.44) --
	(245.86, 88.34) --
	(251.21, 97.16) --
	(256.56,123.35) --
	(261.91,157.54) --
	(267.27,192.33);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (203.04,113.24) --
	(208.39,111.85) --
	(213.74,111.59) --
	(219.09,111.66) --
	(224.45,112.12) --
	(229.80,112.27) --
	(235.15,112.50) --
	(240.50,116.23) --
	(245.86,130.94) --
	(251.21,168.51);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (203.04, 68.42) --
	(208.39, 63.98) --
	(213.74, 63.98) --
	(219.09, 63.98);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] (201.07,111.28) --
	(205.00,111.28) --
	(205.00,115.20) --
	(201.07,115.20) --
	cycle;

\path[fill=fillColor] (206.43,109.89) --
	(210.35,109.89) --
	(210.35,113.82) --
	(206.43,113.82) --
	cycle;

\path[fill=fillColor] (211.78,109.63) --
	(215.70,109.63) --
	(215.70,113.55) --
	(211.78,113.55) --
	cycle;

\path[fill=fillColor] (217.13,109.70) --
	(221.06,109.70) --
	(221.06,113.62) --
	(217.13,113.62) --
	cycle;

\path[fill=fillColor] (222.49,110.16) --
	(226.41,110.16) --
	(226.41,114.09) --
	(222.49,114.09) --
	cycle;

\path[fill=fillColor] (227.84,110.31) --
	(231.76,110.31) --
	(231.76,114.23) --
	(227.84,114.23) --
	cycle;

\path[fill=fillColor] (233.19,110.53) --
	(237.11,110.53) --
	(237.11,114.46) --
	(233.19,114.46) --
	cycle;

\path[fill=fillColor] (238.54,114.27) --
	(242.47,114.27) --
	(242.47,118.20) --
	(238.54,118.20) --
	cycle;

\path[fill=fillColor] (243.90,128.97) --
	(247.82,128.97) --
	(247.82,132.90) --
	(243.90,132.90) --
	cycle;

\path[fill=fillColor] (249.25,166.55) --
	(253.17,166.55) --
	(253.17,170.47) --
	(249.25,170.47) --
	cycle;
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor] (197.68, 90.42) --
	(200.33, 85.84) --
	(195.04, 85.84) --
	cycle;

\path[fill=fillColor] (203.04, 90.42) --
	(205.68, 85.84) --
	(200.39, 85.84) --
	cycle;

\path[fill=fillColor] (208.39, 90.41) --
	(211.03, 85.84) --
	(205.75, 85.84) --
	cycle;

\path[fill=fillColor] (213.74, 90.41) --
	(216.38, 85.84) --
	(211.10, 85.84) --
	cycle;

\path[fill=fillColor] (219.09, 90.41) --
	(221.74, 85.84) --
	(216.45, 85.84) --
	cycle;

\path[fill=fillColor] (224.45, 90.41) --
	(227.09, 85.84) --
	(221.80, 85.84) --
	cycle;

\path[fill=fillColor] (229.80, 90.41) --
	(232.44, 85.84) --
	(227.16, 85.84) --
	cycle;

\path[fill=fillColor] (235.15, 90.42) --
	(237.79, 85.84) --
	(232.51, 85.84) --
	cycle;

\path[fill=fillColor] (240.50, 90.49) --
	(243.15, 85.92) --
	(237.86, 85.92) --
	cycle;

\path[fill=fillColor] (245.86, 91.39) --
	(248.50, 86.82) --
	(243.21, 86.82) --
	cycle;

\path[fill=fillColor] (251.21,100.21) --
	(253.85, 95.64) --
	(248.57, 95.64) --
	cycle;

\path[fill=fillColor] (256.56,126.40) --
	(259.20,121.82) --
	(253.92,121.82) --
	cycle;

\path[fill=fillColor] (261.91,160.59) --
	(264.56,156.02) --
	(259.27,156.02) --
	cycle;

\path[fill=fillColor] (267.27,195.39) --
	(269.91,190.81) --
	(264.62,190.81) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.26, 68.42) -- (205.81, 68.42);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.04, 65.64) -- (203.04, 71.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.61, 63.98) -- (211.16, 63.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.39, 61.20) -- (208.39, 66.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.97, 63.98) -- (216.52, 63.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (213.74, 61.20) -- (213.74, 66.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (216.32, 63.98) -- (221.87, 63.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (219.09, 61.20) -- (219.09, 66.75);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] (197.68, 87.62) circle (  1.96);

\path[fill=fillColor] (203.04, 87.62) circle (  1.96);

\path[fill=fillColor] (208.39, 87.61) circle (  1.96);

\path[fill=fillColor] (213.74, 87.61) circle (  1.96);

\path[fill=fillColor] (219.09, 87.61) circle (  1.96);

\path[fill=fillColor] (224.45, 87.61) circle (  1.96);

\path[fill=fillColor] (229.80, 87.61) circle (  1.96);

\path[fill=fillColor] (235.15, 87.62) circle (  1.96);

\path[fill=fillColor] (240.50, 87.69) circle (  1.96);

\path[fill=fillColor] (245.86, 88.58) circle (  1.96);

\path[fill=fillColor] (251.21, 97.29) circle (  1.96);

\path[fill=fillColor] (256.56,123.32) circle (  1.96);

\path[fill=fillColor] (261.91,157.55) circle (  1.96);

\path[fill=fillColor] (267.27,192.33) circle (  1.96);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (192.33, 57.56) -- (192.33, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (197.68, 57.56) -- (197.68, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (203.04, 57.56) -- (203.04, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (208.39, 57.56) -- (208.39, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (213.74, 57.56) -- (213.74, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (219.09, 57.56) -- (219.09, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (224.45, 57.56) -- (224.45, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (229.80, 57.56) -- (229.80, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (235.15, 57.56) -- (235.15, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (240.50, 57.56) -- (240.50, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (245.86, 57.56) -- (245.86, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (251.21, 57.56) -- (251.21, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (256.56, 57.56) -- (256.56, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (261.91, 57.56) -- (261.91, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (267.27, 57.56) -- (267.27, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (272.62, 57.56) -- (272.62, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (277.97, 57.56) -- (277.97, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (283.32, 57.56) -- (283.32, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (288.68, 57.56) -- (288.68, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (294.03, 57.56) -- (294.03, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (299.38, 57.56) -- (299.38, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (304.73, 57.56) -- (304.73, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (310.09, 57.56) -- (310.09, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (315.44, 57.56) -- (315.44, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (320.79, 57.56) -- (320.79, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (326.14, 57.56) -- (326.14, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (331.50, 57.56) -- (331.50, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (336.85, 57.56) -- (336.85, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (342.20, 57.56) -- (342.20, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73, 64.92) -- (196.42, 64.92);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73, 75.42) -- (196.42, 75.42);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73, 85.92) -- (196.42, 85.92);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73, 96.43) -- (196.42, 96.43);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73,106.93) -- (196.42,106.93);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73,117.43) -- (196.42,117.43);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73,127.94) -- (196.42,127.94);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73,138.44) -- (196.42,138.44);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73,148.95) -- (196.42,148.95);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73,159.45) -- (196.42,159.45);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73,169.95) -- (196.42,169.95);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73,180.46) -- (196.42,180.46);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73,190.96) -- (196.42,190.96);
\end{scope}
\begin{scope}
\path[clip] (348.31, 57.56) rectangle (501.39,198.75);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] (348.31, 57.56) rectangle (501.39,198.75);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.2pt,line join=round] (348.31, 70.17) --
	(501.39, 70.17);

\path[draw=drawColor,line width= 0.2pt,line join=round] (348.31,101.68) --
	(501.39,101.68);

\path[draw=drawColor,line width= 0.2pt,line join=round] (348.31,133.19) --
	(501.39,133.19);

\path[draw=drawColor,line width= 0.2pt,line join=round] (348.31,164.70) --
	(501.39,164.70);

\path[draw=drawColor,line width= 0.2pt,line join=round] (348.31,196.21) --
	(501.39,196.21);

\path[draw=drawColor,line width= 0.2pt,line join=round] (363.30, 57.56) --
	(363.30,198.75);

\path[draw=drawColor,line width= 0.2pt,line join=round] (400.76, 57.56) --
	(400.76,198.75);

\path[draw=drawColor,line width= 0.2pt,line join=round] (438.23, 57.56) --
	(438.23,198.75);

\path[draw=drawColor,line width= 0.2pt,line join=round] (475.70, 57.56) --
	(475.70,198.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (348.31, 85.92) --
	(501.39, 85.92);

\path[draw=drawColor,line width= 0.5pt,line join=round] (348.31,117.43) --
	(501.39,117.43);

\path[draw=drawColor,line width= 0.5pt,line join=round] (348.31,148.95) --
	(501.39,148.95);

\path[draw=drawColor,line width= 0.5pt,line join=round] (348.31,180.46) --
	(501.39,180.46);

\path[draw=drawColor,line width= 0.5pt,line join=round] (382.03, 57.56) --
	(382.03,198.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (419.50, 57.56) --
	(419.50,198.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (456.96, 57.56) --
	(456.96,198.75);

\path[draw=drawColor,line width= 0.5pt,line join=round] (494.43, 57.56) --
	(494.43,198.75);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (355.27, 89.52) --
	(360.62, 89.52) --
	(365.97, 89.52) --
	(371.32, 89.52) --
	(376.68, 89.52) --
	(382.03, 89.52) --
	(387.38, 89.52) --
	(392.73, 89.52) --
	(398.09, 89.52) --
	(403.44, 89.52) --
	(408.79, 89.52) --
	(414.14, 89.52) --
	(419.50, 89.52) --
	(424.85, 89.53) --
	(430.20, 89.55) --
	(435.55, 89.61) --
	(440.91, 89.71) --
	(446.26, 89.97) --
	(451.61, 90.65) --
	(456.96, 92.11) --
	(462.32, 95.47) --
	(467.67,101.07) --
	(473.02,108.80) --
	(478.37,119.46) --
	(483.73,132.70) --
	(489.08,144.57) --
	(494.43,157.31);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (355.27, 88.43) --
	(360.62, 88.43) --
	(365.97, 88.43) --
	(371.32, 88.43) --
	(376.68, 88.43) --
	(382.03, 88.43) --
	(387.38, 88.43) --
	(392.73, 88.43) --
	(398.09, 88.43) --
	(403.44, 88.43) --
	(408.79, 88.43) --
	(414.14, 88.43) --
	(419.50, 88.43) --
	(424.85, 88.44) --
	(430.20, 88.46) --
	(435.55, 88.51) --
	(440.91, 88.64) --
	(446.26, 88.92) --
	(451.61, 89.63) --
	(456.96, 91.16) --
	(462.32, 94.48) --
	(467.67,100.45) --
	(473.02,108.29) --
	(478.37,119.14) --
	(483.73,132.38) --
	(489.08,144.46) --
	(494.43,157.43);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (360.62,114.65) --
	(365.97,111.15) --
	(371.32,111.49) --
	(376.68,111.10) --
	(382.03,115.68) --
	(387.38,162.17);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (360.62, 66.36) --
	(365.97, 64.61) --
	(371.32, 64.61) --
	(376.68, 64.61) --
	(382.03, 64.61) --
	(387.38, 64.92) --
	(392.73, 64.92);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] (355.27, 89.52) circle (  1.96);

\path[fill=fillColor] (360.62, 89.52) circle (  1.96);

\path[fill=fillColor] (365.97, 89.52) circle (  1.96);

\path[fill=fillColor] (371.32, 89.52) circle (  1.96);

\path[fill=fillColor] (376.68, 89.52) circle (  1.96);

\path[fill=fillColor] (382.03, 89.52) circle (  1.96);

\path[fill=fillColor] (387.38, 89.52) circle (  1.96);

\path[fill=fillColor] (392.73, 89.52) circle (  1.96);

\path[fill=fillColor] (398.09, 89.52) circle (  1.96);

\path[fill=fillColor] (403.44, 89.52) circle (  1.96);

\path[fill=fillColor] (408.79, 89.52) circle (  1.96);

\path[fill=fillColor] (414.14, 89.52) circle (  1.96);

\path[fill=fillColor] (419.50, 89.52) circle (  1.96);

\path[fill=fillColor] (424.85, 89.53) circle (  1.96);

\path[fill=fillColor] (430.20, 89.55) circle (  1.96);

\path[fill=fillColor] (435.55, 89.61) circle (  1.96);

\path[fill=fillColor] (440.91, 89.71) circle (  1.96);

\path[fill=fillColor] (446.26, 89.97) circle (  1.96);

\path[fill=fillColor] (451.61, 90.65) circle (  1.96);

\path[fill=fillColor] (456.96, 92.11) circle (  1.96);

\path[fill=fillColor] (462.32, 95.47) circle (  1.96);

\path[fill=fillColor] (467.67,101.07) circle (  1.96);

\path[fill=fillColor] (473.02,108.80) circle (  1.96);

\path[fill=fillColor] (478.37,119.46) circle (  1.96);

\path[fill=fillColor] (483.73,132.70) circle (  1.96);

\path[fill=fillColor] (489.08,144.57) circle (  1.96);

\path[fill=fillColor] (494.43,157.31) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (357.84, 66.36) -- (363.39, 66.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (360.62, 63.59) -- (360.62, 69.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (363.20, 64.61) -- (368.75, 64.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.97, 61.83) -- (365.97, 67.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (368.55, 64.61) -- (374.10, 64.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (371.32, 61.83) -- (371.32, 67.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (373.90, 64.61) -- (379.45, 64.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (376.68, 61.83) -- (376.68, 67.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.25, 64.61) -- (384.80, 64.61);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (382.03, 61.83) -- (382.03, 67.38);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.61, 64.92) -- (390.16, 64.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.38, 62.14) -- (387.38, 67.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.96, 64.92) -- (395.51, 64.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (392.73, 62.14) -- (392.73, 67.69);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] (358.66,112.68) --
	(362.58,112.68) --
	(362.58,116.61) --
	(358.66,116.61) --
	cycle;

\path[fill=fillColor] (364.01,109.19) --
	(367.93,109.19) --
	(367.93,113.11) --
	(364.01,113.11) --
	cycle;

\path[fill=fillColor] (369.36,109.53) --
	(373.29,109.53) --
	(373.29,113.45) --
	(369.36,113.45) --
	cycle;

\path[fill=fillColor] (374.71,109.13) --
	(378.64,109.13) --
	(378.64,113.06) --
	(374.71,113.06) --
	cycle;

\path[fill=fillColor] (380.07,113.72) --
	(383.99,113.72) --
	(383.99,117.64) --
	(380.07,117.64) --
	cycle;

\path[fill=fillColor] (385.42,160.21) --
	(389.34,160.21) --
	(389.34,164.13) --
	(385.42,164.13) --
	cycle;
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor] (355.27, 91.48) --
	(357.91, 86.91) --
	(352.62, 86.91) --
	cycle;

\path[fill=fillColor] (360.62, 91.48) --
	(363.26, 86.90) --
	(357.98, 86.90) --
	cycle;

\path[fill=fillColor] (365.97, 91.48) --
	(368.61, 86.90) --
	(363.33, 86.90) --
	cycle;

\path[fill=fillColor] (371.32, 91.48) --
	(373.97, 86.90) --
	(368.68, 86.90) --
	cycle;

\path[fill=fillColor] (376.68, 91.48) --
	(379.32, 86.90) --
	(374.03, 86.90) --
	cycle;

\path[fill=fillColor] (382.03, 91.48) --
	(384.67, 86.90) --
	(379.39, 86.90) --
	cycle;

\path[fill=fillColor] (387.38, 91.48) --
	(390.02, 86.90) --
	(384.74, 86.90) --
	cycle;

\path[fill=fillColor] (392.73, 91.48) --
	(395.38, 86.91) --
	(390.09, 86.91) --
	cycle;

\path[fill=fillColor] (398.09, 91.48) --
	(400.73, 86.90) --
	(395.44, 86.90) --
	cycle;

\path[fill=fillColor] (403.44, 91.48) --
	(406.08, 86.90) --
	(400.80, 86.90) --
	cycle;

\path[fill=fillColor] (408.79, 91.48) --
	(411.43, 86.91) --
	(406.15, 86.91) --
	cycle;

\path[fill=fillColor] (414.14, 91.48) --
	(416.79, 86.91) --
	(411.50, 86.91) --
	cycle;

\path[fill=fillColor] (419.50, 91.48) --
	(422.14, 86.91) --
	(416.85, 86.91) --
	cycle;

\path[fill=fillColor] (424.85, 91.50) --
	(427.49, 86.92) --
	(422.21, 86.92) --
	cycle;

\path[fill=fillColor] (430.20, 91.51) --
	(432.84, 86.93) --
	(427.56, 86.93) --
	cycle;

\path[fill=fillColor] (435.55, 91.57) --
	(438.20, 86.99) --
	(432.91, 86.99) --
	cycle;

\path[fill=fillColor] (440.91, 91.69) --
	(443.55, 87.11) --
	(438.26, 87.11) --
	cycle;

\path[fill=fillColor] (446.26, 91.97) --
	(448.90, 87.39) --
	(443.62, 87.39) --
	cycle;

\path[fill=fillColor] (451.61, 92.68) --
	(454.25, 88.10) --
	(448.97, 88.10) --
	cycle;

\path[fill=fillColor] (456.96, 94.21) --
	(459.61, 89.64) --
	(454.32, 89.64) --
	cycle;

\path[fill=fillColor] (462.32, 97.53) --
	(464.96, 92.95) --
	(459.67, 92.95) --
	cycle;

\path[fill=fillColor] (467.67,103.50) --
	(470.31, 98.92) --
	(465.03, 98.92) --
	cycle;

\path[fill=fillColor] (473.02,111.34) --
	(475.66,106.76) --
	(470.38,106.76) --
	cycle;

\path[fill=fillColor] (478.37,122.19) --
	(481.02,117.61) --
	(475.73,117.61) --
	cycle;

\path[fill=fillColor] (483.73,135.43) --
	(486.37,130.86) --
	(481.08,130.86) --
	cycle;

\path[fill=fillColor] (489.08,147.51) --
	(491.72,142.93) --
	(486.44,142.93) --
	cycle;

\path[fill=fillColor] (494.43,160.48) --
	(497.07,155.91) --
	(491.79,155.91) --
	cycle;
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (349.91, 57.56) -- (349.91, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (355.27, 57.56) -- (355.27, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (360.62, 57.56) -- (360.62, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (365.97, 57.56) -- (365.97, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (371.32, 57.56) -- (371.32, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (376.68, 57.56) -- (376.68, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (382.03, 57.56) -- (382.03, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (387.38, 57.56) -- (387.38, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (392.73, 57.56) -- (392.73, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (398.09, 57.56) -- (398.09, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (403.44, 57.56) -- (403.44, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (408.79, 57.56) -- (408.79, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (414.14, 57.56) -- (414.14, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (419.50, 57.56) -- (419.50, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (424.85, 57.56) -- (424.85, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (430.20, 57.56) -- (430.20, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (435.55, 57.56) -- (435.55, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (440.91, 57.56) -- (440.91, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (446.26, 57.56) -- (446.26, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (451.61, 57.56) -- (451.61, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (456.96, 57.56) -- (456.96, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (462.32, 57.56) -- (462.32, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (467.67, 57.56) -- (467.67, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (473.02, 57.56) -- (473.02, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (478.37, 57.56) -- (478.37, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (483.73, 57.56) -- (483.73, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (489.08, 57.56) -- (489.08, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (494.43, 57.56) -- (494.43, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (499.78, 57.56) -- (499.78, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31, 64.92) -- (354.00, 64.92);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31, 75.42) -- (354.00, 75.42);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31, 85.92) -- (354.00, 85.92);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31, 96.43) -- (354.00, 96.43);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31,106.93) -- (354.00,106.93);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31,117.43) -- (354.00,117.43);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31,127.94) -- (354.00,127.94);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31,138.44) -- (354.00,138.44);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31,148.95) -- (354.00,148.95);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31,159.45) -- (354.00,159.45);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31,169.95) -- (354.00,169.95);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31,180.46) -- (354.00,180.46);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31,190.96) -- (354.00,190.96);
\end{scope}
\begin{scope}
\path[clip] ( 33.14,198.75) rectangle (186.23,212.31);
\definecolor{fillColor}{gray}{0.85}

\path[fill=fillColor] ( 33.14,198.75) rectangle (186.23,212.31);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (109.69,203.05) {Bijections};
\end{scope}
\begin{scope}
\path[clip] (190.73,198.75) rectangle (343.81,212.31);
\definecolor{fillColor}{gray}{0.85}

\path[fill=fillColor] (190.73,198.75) rectangle (343.81,212.31);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (267.27,203.05) {Friends};
\end{scope}
\begin{scope}
\path[clip] (348.31,198.75) rectangle (501.39,212.31);
\definecolor{fillColor}{gray}{0.85}

\path[fill=fillColor] (348.31,198.75) rectangle (501.39,212.31);
\definecolor{drawColor}{gray}{0.10}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (424.85,203.05) {Functions};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 66.87, 55.31) --
	( 66.87, 57.56);

\path[draw=drawColor,line width= 0.5pt,line join=round] (104.33, 55.31) --
	(104.33, 57.56);

\path[draw=drawColor,line width= 0.5pt,line join=round] (141.80, 55.31) --
	(141.80, 57.56);

\path[draw=drawColor,line width= 0.5pt,line join=round] (179.27, 55.31) --
	(179.27, 57.56);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 66.87, 48.55) {$2^{5}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (104.33, 48.55) {$2^{12}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (141.80, 48.55) {$2^{19}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (179.27, 48.55) {$2^{26}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.5pt,line join=round] (224.45, 55.31) --
	(224.45, 57.56);

\path[draw=drawColor,line width= 0.5pt,line join=round] (261.91, 55.31) --
	(261.91, 57.56);

\path[draw=drawColor,line width= 0.5pt,line join=round] (299.38, 55.31) --
	(299.38, 57.56);

\path[draw=drawColor,line width= 0.5pt,line join=round] (336.85, 55.31) --
	(336.85, 57.56);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (224.45, 48.55) {$2^{5}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (261.91, 48.55) {$2^{12}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (299.38, 48.55) {$2^{19}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (336.85, 48.55) {$2^{26}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.5pt,line join=round] (382.03, 55.31) --
	(382.03, 57.56);

\path[draw=drawColor,line width= 0.5pt,line join=round] (419.50, 55.31) --
	(419.50, 57.56);

\path[draw=drawColor,line width= 0.5pt,line join=round] (456.96, 55.31) --
	(456.96, 57.56);

\path[draw=drawColor,line width= 0.5pt,line join=round] (494.43, 55.31) --
	(494.43, 57.56);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (382.03, 48.55) {$2^{5}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (419.50, 48.55) {$2^{12}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (456.96, 48.55) {$2^{19}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (494.43, 48.55) {$2^{26}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 29.09, 83.44) {2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 29.09,114.96) {16};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 29.09,146.47) {128};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 29.09,177.98) {1024};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 30.89, 85.92) --
	( 33.14, 85.92);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 30.89,117.43) --
	( 33.14,117.43);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 30.89,148.95) --
	( 33.14,148.95);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 30.89,180.46) --
	( 33.14,180.46);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (267.27, 38.70) {Domain size};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 10.70,128.16) {Total runtime (s)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (124.58,  4.50) rectangle (409.95, 27.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] (133.58,  9.00) rectangle (148.04, 23.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (135.03, 16.23) -- (146.59, 16.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] (140.81, 16.23) circle (  1.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] (201.65,  9.00) rectangle (216.10, 23.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (203.10, 16.23) -- (214.66, 16.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor] (208.88, 19.28) --
	(211.52, 14.70) --
	(206.24, 14.70) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] (281.98,  9.00) rectangle (296.43, 23.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (283.42, 16.23) -- (294.99, 16.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] (287.24, 14.26) --
	(291.17, 14.26) --
	(291.17, 18.19) --
	(287.24, 18.19) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] (353.42,  9.00) rectangle (367.87, 23.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (354.86, 16.23) -- (366.43, 16.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (357.87, 16.23) -- (363.42, 16.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (360.65, 13.45) -- (360.65, 19.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (152.54, 13.75) {\textsc{Crane2-BFS}};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (220.60, 13.75) {\textsc{Crane2-Greedy}};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (300.93, 13.75) {\textsc{FastWFOMC}};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (372.37, 13.75) {\textsc{ForcLift}};
\end{scope}
\end{tikzpicture}

\end{document}

### 2024-07-30 analysis/analyse.R

@@ -1,6 +1,7 @@
 library(tidyverse)
 library(scales)
 library(tikzDevice)
+library(ggpubr)
 
 df <- read.csv("../results/processed/results.csv")
 df$compilation.time <- df$compilation.time / 1000
@@ -8,28 +9,36 @@ df$inference.time <- df$inference.time / 1000
 df$time <- df$compilation.time + df$inference.time
 df$algorithm[df$algorithm == "bfs"] <- "\\textsc{Crane2-BFS}"
 df$algorithm[df$algorithm == "greedy"] <- "\\textsc{Crane2-Greedy}"
-df$algorithm[df$algorithm == "forclift"] <- "\\textsc{ForcLift}"
 df$algorithm[df$algorithm == "fastwfomc"] <- "\\textsc{FastWFOMC}"
+df$algorithm[df$algorithm == "forclift"] <- "\\textsc{ForcLift}"
+df$sequence[df$sequence == "bijections"] <- "Bijections"
+df$sequence[df$sequence == "friends"] <- "Friends"
+df$sequence[df$sequence == "functions"] <- "Functions"
 
 # Sanity check: differences between max and min counts as a percentage of the
 # min count
-#differences <- df %>% group_by(sequence, domain.size) %>%
-#  summarise(diff = 100 * (max(count) - min(count)) / min(count))
+# differences <- df %>% group_by(sequence, domain.size) %>%
+#   summarise(diff = 100 * (max(count) - min(count)) / min(count))
 
-tikz(file = "../doc/plot.tex", width = 3.32492194445, height = 1.8702685937531252)
-ggplot(df[df$sequence == "friends",],
-       aes(domain.size, time, colour = algorithm, linetype = algorithm,
-           shape = algorithm)) +
+tikz(file = "../doc/paper/plot.tex", width = 7, height = 3,
+     standAlone = TRUE)
+ggplot(df, aes(domain.size, time, color = algorithm, linetype = algorithm,
+               shape = algorithm)) +
   geom_line() +
   geom_point() +
-  scale_x_continuous(trans = log2_trans()) +
+  scale_x_continuous(trans = log2_trans(),
+                     breaks = c(32, 4096, 524288, 67108864),
+                     labels = c("$2^{5}$", "$2^{12}$", "$2^{19}$",
+                                "$2^{26}$")) +
   scale_y_continuous(trans = log2_trans()) +
-  annotation_logticks(sides = "l", colour = "#b3b3b3") +
[…]

### 2024-07-30 build/fastwfomc_wrapper.sh

@@ -1,4 +1,4 @@
-#!/usr/bin/env sh
+#!/bin/bash
 
 for ((i=1; ; i++)); do
     j=$((2 ** $i))

### 2024-07-30 build/forclift_wrapper.sh

@@ -1,4 +1,4 @@
-#!/usr/bin/env sh
+#!/bin/bash
 
 cd ../deps/Forclift || exit 1
 for ((k=1; ; k++)); do
@@ -8,7 +8,7 @@ for ((k=1; ; k++)); do
     error_found=false
     while IFS= read -r line; do
         echo "$line"
-        if echo "$line" | grep -qE "Infinity|Cannot|Exception|Error"; then
+        if echo "$line" | grep -qE "Infinity|Cannot|cannot|Exception|Error"; then
             error_found=true
         fi
     done < <(ulimit -t "$2" -c 0 -Sv "$3" && /usr/bin/time -f "Elapsed: %e" java -jar target/scala-2.11/crane-assembly-1.0.jar -z --format-in mln "$1" 2>&1)

### 2024-07-30 build/job.sh

@@ -8,7 +8,9 @@
 
 cd $SLURM_SUBMIT_DIR
 
-# TODO: module load intel/2018.2
+module load java/1.8.0_201
+module load julia/1.10.4
+module load intel/2020u4
 
 ulimit -c 0
 lscpu > cpuinfo.txt

### 2024-08-02 doc/paper/paper.tex
Preparing for a new round of experiments
Some of the preparations for a new set of experiments (including scaling FastWFOMC domains exponentially, since it's faster now)
Everything related to the new set of experiments (except for the results, which are too big to be stored here)
The full experimental results are too big to fit into a repo

@@
 \section{Experimental Evaluation}\label{sec:experiments}
-% TODO: this section is apparently "hard to follow"
-
-% TODO: Compilation time is included in the experimental results, and the
-% differences between compilation and inference time are delineated in the
-% second-to-last paragraph of Section 6.
-
-% TODO: It would not have been feasible to increase domain sizes by 1 all the
-% way up to 300000. Thus, the experimental results are presented in two parts,
-% where the first part examines scalability with small domain sizes, and the
-% second part tests the limits of each algorithm within a given timeout.
-
-% TODO: (here or in the introduction) C++ code generation is necessary for any
-% runtime experiments because without it the algorithm is "incomplete" as
-% explained above.
-
-% TODO: The asymptotic analysis of the total number of arithmetic operations
-% required to compute the FOMC of these formulas was already performed in
-% previous work.
-
-% TODO: Since FastWFOMC does not support many-sorted logic, our experiments were
-% restricted to formulas with a single domain. However, many of the counting
-% problems examined in [1] become equivalent (in the sense that they generate
-% the same integer sequences) when restricted to a single domain. Moreover, it
-% is challenging to compare Crane2 and FastWFOMC on a larger set of problems
-% because each problem has to be represented in two (fairly different) logics:
-% \FO{} and \UFO{}.
-
-We compared \Cranetwo{}\footnote{\textsc{Crane} has two modes that decide how
-  compilation rules are applied to formulas: one that uses greedy search and
-  another that combines greedy and breadth-first search. In our experiments, we
-  refer to these modes as \Cranegreedy{} and \Cranebfs{}, respectively.} with
-\textsc{FastWFOMC} and \textsc{ForcLift} on two problems previously considered
-by \citeauthor{DBLP:conf/kr/DilkasB23}~\shortcite{DBLP:conf/kr/DilkasB23}. The
+
+% TODO: 1. Introduction
+% Objective: Briefly state the goals of the experiments.
+% Overview: Summarize the structure of the section.
+
+\begin{itemize}
+  \item Note that it would not make sense to experimentally evaluate \Cranetwo{}
+        without the C++ code generation described in \cref{sec:cpp} because the
+        algorithm would only produce mathematical definitions of functions.
+\end{itemize}
+
+% TODO: 2. Experimental Setup
+
+% Environment: Describe the hardware and software environment (e.g.,
+% specifications of the computer, operating system, libraries, and tools used).
+
+\begin{itemize}
+  \item The experiments were run on an Intel Skylake \SI{2.4}{\giga\hertz} CPU
+        with \SI{188}{\gibi\byte} of memory and CentOS~7 operating system. C++
+        programs were compiled using the Intel C++ Compiler 2020u4.
+        \textsc{FastWFOMC} was run on Julia~1.10.4, while all other algorithms
+        were run on the Java Virtual Machine 1.8.0\_201.
+\end{itemize}
+
+% Datasets: Provide details about the datasets used in the experiments,
+% including size, source, and any preprocessing steps.
+
+\begin{itemize}
+  \item The asymptotic analysis of the total number of arithmetic operations
+        required to compute the FOMC of some of these formulas was already
+        performed in previous work~\cite{DBLP:conf/kr/DilkasB23}.
+  \item Since FastWFOMC does not support many-sorted logic, our experiments were
+        restricted to formulas with a single domain. However, many of the
+        counting problems examined in [1] become equivalent (in the sense that
+        they generate the same integer sequences) when restricted to a single
+        domain. Moreover, it is challenging to compare Crane2 and FastWFOMC on a
+        larger set of problems because each problem has to be represented in two
+        (fairly different) logics: \FO{} and \UFO{}.
+  \item It is important to note that comparing \Cranetwo{} and
+        \textsc{FastWFOMC} on a more substantial set of benchmarks is
+        challenging because there is no automated way to translate a formula in
+        \FO{} or \Ctwo{} into \UFO{}, or even check if such an encoding is
+        possible.
+\end{itemize}
+
+% Baselines: List and describe the baseline methods or systems used for
+% comparison.
+
+\begin{itemize}
+  \item \textsc{Crane} has two modes that decide how compilation rules are
+        applied to formulas: one that uses greedy search and another that
+        combines greedy and breadth-first search. In our experiments, we refer
+        to these modes as \Cranegreedy{} and \Cranebfs{}, respectively.
+\end{itemize}
+
+% Metrics: Define the performance metrics used to evaluate the results (e.g.,
+% accuracy, precision, recall, F1-score, runtime).
+
+\begin{itemize}
+  \item Compilation time is included in the experimental results, and the
+        differences between compilation and inference time are delineated in the
+        second-to-last paragraph of Section 6.
+  \item We run each algorithm on each benchmark on domains of size
+        $2^{0}, 2^{1}, 2^{2},\dots$ until the algorithm times out after
+        \SI{1}{\hour}, runs out of memory, or (in the case of \textsc{ForcLift})
+        returns $\infty$.
+\end{itemize}
+
+% TODO: 3. Results and Analysis
+% Presentation of Results: Use tables, graphs, and charts to present the experimental results clearly.
+% Comparison with Baselines: Compare your method’s results with the baselines.
+% Discussion: Analyze and interpret the results, highlighting the strengths and potential weaknesses of your approach.
+% Insights: Provide insights or patterns observed from the results.
+% Challenges: Discuss any challenges or unexpected outcomes.
+% Acknowledgement: Honestly acknowledge any limitations of your experiments or method.
+
+\begin{itemize}
+  \item It is important to note that while \textsc{ForcLift} may have runtime
+        performance comparable to \Cranetwo{}, its finite-precision arithmetic
+        cannot represent model counts for domain sizes greater than 143 and
+        returns $\infty$ instead.
+\end{itemize}
+
+% TODO: 8. Conclusion
+% Summary: Briefly summarize the key findings from the experimental results.
+% Future Work: Suggest directions for future research based on your findings.
+
+We compare \Cranetwo{} with \textsc{FastWFOMC} and \textsc{ForcLift} on two
+problems previously considered by
+\citeauthor{DBLP:conf/kr/DilkasB23}~\shortcite{DBLP:conf/kr/DilkasB23}. The
 first problem is the function-counting problem from \cref{example:functions},
-and the second problem is the bijection-counting problem described below. It is
-important to note that comparing \Cranetwo{} and \textsc{FastWFOMC} on a more
-substantial set of benchmarks is challenging because there is no automated way
-to translate a formula in \FO{} or \Ctwo{} into \UFO{}, or even check if such an
-encoding is possible. We ran the experiments on an AMD~Ryzen~7~5800H processor
-with \SI{16}{\gibi\byte} of memory and Arch Linux~6.8.2-arch2-1 operating
-system. \textsc{FastWFOMC} was executed using Python~3.8.19 with
-Python-FLINT~0.5.0.
+and the second problem is the bijection-counting problem described below.
 
@@
 
-\begin{figure}[t]
+\begin{figure*}[t]
   \centering
-  \input{plot}
-  \caption{The running time of WFOMC algorithms. Note that the $y$-axis is on a
-    logarithmic scale.}\label{fig:plot}
-\end{figure}
-% TODO: turn this into two separate plots for clarity. Maybe also attach labels
-% to their corresponding lines
-
-% TODO: no overfull boxes (might be the fault of the figure)
-
-% TODO: must not use 'input' command. instead, compile to a pdf
-
-In the first experiment, we ran each of the four algorithms once on each
-combination of benchmark and domain size, ranging from one up to and including
-35. \Cref{fig:plot} shows the total runtime values as a measure of the overall
+  \includegraphics{plot.pdf}
+  \caption{The runtime of the algorithms as a function of the domain size. Note
+    that both axes are on a logarithmic scale.}\label{fig:plot}
+\end{figure*}
+
+\Cref{fig:plot} shows the total runtime values as a measure of the overall
 performance of each algorithm. We also separately tracked compilation and
@@
 and reuse the resulting C++ program for all domain sizes.
-% TODO: The lines for Crane2 in Figure 4 appear to be completely flat whereas
-% the line for ForcLift has some slight fluctuations. We refer to these
-% fluctuations as variance.
-
-\begin{table}[t]
-  \centering
-  \begin{tabular}{lrr}
-    \toprule
-    Algorithm & Bijections & Functions \\
-    \midrule
-    \Cranebfs{} & \num{e4} & \num{3e5} \\
-    \Cranegreedy{} & --- & \num{3e5} \\
-    \textsc{FastWFOMC} & 28 & 32 \\
-    \textsc{ForcLift} & --- & 143 \\
-    \bottomrule
-  \end{tabular}
-  \caption{The maximum domain sizes that each algorithm can handle within
-    \SI{45}{\second}. A dash symbol `---' indicates that the algorithm was
-    unable to find a solution. The domain sizes for \Cranetwo{} are accurate up
-    to the first digit, while the domain sizes for the other domain sizes are
-    exact.}\label{table:results}
-\end{table}
-
-For the second experiment, we examined the maximum domain size the algorithms
-can handle in at most \SI{45}{\second} of total runtime. As shown in
-\cref{table:results}, \Cranebfs{} can scale to domain sizes \num{357} and
-\num{9375} times larger than \textsc{FastWFOMC} for the bijection-counting and
-function-counting problems, respectively. It is important to note that while
-\textsc{ForcLift} may have runtime performance comparable to \Cranetwo{}, its
-finite-precision arithmetic cannot represent model counts for domain sizes
-greater than 143 and returns $\infty$ instead.
 

### 2024-08-02 analysis/analyse.R

@@ -3,6 +3,10 @@ library(scales)
 library(tikzDevice)
 library(ggpubr)
 
+df <- read.csv("../results/processed/results_with_counts.csv")
+df$count <- NULL
+write.csv(df, "../results/processed/results.csv")
+
 df <- read.csv("../results/processed/results.csv")
 df$compilation.time <- df$compilation.time / 1000
 df$inference.time <- df$inference.time / 1000

### 2024-08-02 analysis/parse.py

@@ -5,7 +5,7 @@ import csv
 import os
 
 RESULTS_DIR = '../results/raw'
-RESULTS_FILE = '../results/processed/results.csv'
+RESULTS_FILE = '../results/processed/results_with_counts.csv'
 FIELDNAMES = [
     'algorithm',
     'sequence',

### 2024-08-09 doc/paper/paper.tex
First (second?) draft of the 'experiments' section

@@
   equipped with arbitrary-precision arithmetic. These additions allow the new
-  FOMC algorithm to scale to domain sizes over \num{9000} times larger than the
-  current state of the art, as demonstrated through experimental results.
+  FOMC algorithm to scale to domain sizes over \num{500000} times larger than
+  the current state of the art, as demonstrated through experimental results.
 \end{abstract}
@@
 
+% TODO: The asymptotic analysis of the total number of arithmetic operations
+% required to compute the FOMC of some of these formulas was already performed
+% in previous work~\cite{DBLP:conf/kr/DilkasB23}.
+
 \begin{algorithm}[t]
@@
 
-% TODO: 1. Introduction
+% 1. Introduction
 % Objective: Briefly state the goals of the experiments.
@@
 
-\begin{itemize}
-  \item Note that it would not make sense to experimentally evaluate \Cranetwo{}
-        without the C++ code generation described in \cref{sec:cpp} because the
-        algorithm would only produce mathematical definitions of functions.
-\end{itemize}
-
-% TODO: 2. Experimental Setup
-
-% Environment: Describe the hardware and software environment (e.g.,
-% specifications of the computer, operating system, libraries, and tools used).
-
-\begin{itemize}
-  \item The experiments were run on an Intel Skylake \SI{2.4}{\giga\hertz} CPU
-        with \SI{188}{\gibi\byte} of memory and CentOS~7 operating system. C++
-        programs were compiled using the Intel C++ Compiler 2020u4.
-        \textsc{FastWFOMC} was run on Julia~1.10.4, while all other algorithms
-        were run on the Java Virtual Machine 1.8.0\_201.
-\end{itemize}
+% 2. Experimental Setup
+
+% Baselines: List and describe the baseline methods or systems used for
+% comparison.
+
+In this section, we present experimental results examining the scalability of
+\Cranetwo{} compared to two other notable FOMC algorithms: \textsc{FastWFOMC}
+and \textsc{ForcLift}. Note that it would not make sense to include the original
+\textsc{Crane} algorithm in the experiments or to evaluate \Cranetwo{} without
+the C++ code generation described in \cref{sec:cpp}. Indeed, these algorithms
+can only produce mathematical definitions of functions without evaluating them.
+
+In our experiments, we include two versions of \Cranetwo{}: \Cranegreedy{} and
+\Cranebfs{}. Like its predecessor, \Cranetwo{} has two modes that decide how
+compilation rules are applied to formulas: one that uses greedy search similarly
+to \textsc{ForcLift} and another that combines greedy and breadth-first search.
+While greedy search is more efficient (in terms of being able to handle larger
+formulas), it is a heuristic that can miss some solutions.
 
@@
 
-\begin{itemize}
-  \item The asymptotic analysis of the total number of arithmetic operations
-        required to compute the FOMC of some of these formulas was already
-        performed in previous work~\cite{DBLP:conf/kr/DilkasB23}.
-  \item Since FastWFOMC does not support many-sorted logic, our experiments were
-        restricted to formulas with a single domain. However, many of the
-        counting problems examined in [1] become equivalent (in the sense that
-        they generate the same integer sequences) when restricted to a single
-        domain. Moreover, it is challenging to compare Crane2 and FastWFOMC on a
-        larger set of problems because each problem has to be represented in two
-        (fairly different) logics: \FO{} and \UFO{}.
-  \item It is important to note that comparing \Cranetwo{} and
-        \textsc{FastWFOMC} on a more substantial set of benchmarks is
-        challenging because there is no automated way to translate a formula in
-        \FO{} or \Ctwo{} into \UFO{}, or even check if such an encoding is
-        possible.
-\end{itemize}
-
-% Baselines: List and describe the baseline methods or systems used for
-% comparison.
-
-\begin{itemize}
-  \item \textsc{Crane} has two modes that decide how compilation rules are
-        applied to formulas: one that uses greedy search and another that
-        combines greedy and breadth-first search. In our experiments, we refer
-        to these modes as \Cranegreedy{} and \Cranebfs{}, respectively.
-\end{itemize}
-
-% Metrics: Define the performance metrics used to evaluate the results (e.g.,
-% accuracy, precision, recall, F1-score, runtime).
-
-\begin{itemize}
-  \item Compilation time is included in the experimental results, and the
-        differences between compilation and inference time are delineated in the
-        second-to-last paragraph of Section 6.
-  \item We run each algorithm on each benchmark on domains of size
-        $2^{0}, 2^{1}, 2^{2},\dots$ until the algorithm times out after
-        \SI{1}{\hour}, runs out of memory, or (in the case of \textsc{ForcLift})
-        returns $\infty$.
-\end{itemize}
-
-% TODO: 3. Results and Analysis
-% Presentation of Results: Use tables, graphs, and charts to present the experimental results clearly.
-% Comparison with Baselines: Compare your method’s results with the baselines.
-% Discussion: Analyze and interpret the results, highlighting the strengths and potential weaknesses of your approach.
-% Insights: Provide insights or patterns observed from the results.
-% Challenges: Discuss any challenges or unexpected outcomes.
-% Acknowledgement: Honestly acknowledge any limitations of your experiments or method.
-
-\begin{itemize}
-  \item It is important to note that while \textsc{ForcLift} may have runtime
-        performance comparable to \Cranetwo{}, its finite-precision arithmetic
-        cannot represent model counts for domain sizes greater than 143 and
-        returns $\infty$ instead.
-\end{itemize}
-
-% TODO: 8. Conclusion
-% Summary: Briefly summarize the key findings from the experimental results.
-% Future Work: Suggest directions for future research based on your findings.
-
-We compare \Cranetwo{} with \textsc{FastWFOMC} and \textsc{ForcLift} on two
-problems previously considered by
-\citeauthor{DBLP:conf/kr/DilkasB23}~\shortcite{DBLP:conf/kr/DilkasB23}. The
-first problem is the function-counting problem from \cref{example:functions},
-and the second problem is the bijection-counting problem described below.
-
-The \FO{} formula for bijections is described in \cref{example:overall}. The
-equivalent formula in \Ctwo{} is
+We compare the algorithms on three benchmarks from previous work. The first is
+the function-counting problem from \cref{example:functions}, previously examined
+by \citeauthor{DBLP:conf/kr/DilkasB23}~\shortcite{DBLP:conf/kr/DilkasB23}. The
+second is a variant of the well-known `Friends \& Smokers' Markov logic
+network~\cite{DBLP:conf/aaai/SinglaD08,DBLP:conf/uai/BroeckCD12}. In \Ctwo{},
+\FO{}, and \UFO{}, it can be formulated as
+\begin{gather*}
+  (\forall x,y \in \Delta\text{. } S(x) \land F(x, y) \Rightarrow S(y)) \land{}\\
+  (\forall x \in \Delta\text{. }S(x) \Rightarrow C(x))
+\end{gather*}
+or, equivalently, in conjunctive normal form as
+\begin{gather*}
+  (\forall x,y \in \Delta\text{. }S(y) \lor \neg S(x) \lor \neg F(x, y)) \land{}\\
+  (\forall x \in \Delta\text{. } C(x) \lor \neg S(x)).
+\end{gather*}
+Finally, we include the bijection-counting problem previously used by
+\citeauthor{DBLP:conf/kr/DilkasB23}~\shortcite{DBLP:conf/kr/DilkasB23}. Its
+formulation in \FO{} is described in \cref{example:overall}. The equivalent
+formula in \Ctwo{} is
 \begin{align*}
@@
 
+Since \textsc{FastWFOMC} does not support many-sorted logic, our experiments are
+restricted to formulas with a single domain. However, many of the counting
+problems examined in the experimental evaluation of
+\textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23} become equivalent (in the sense
+that they generate the same integer sequences) when restricted to a single
+domain. Moreover, it is challenging to compare \Cranetwo{} and
+\textsc{FastWFOMC} on a larger set of problems because each problem has to be
+represented in two (fairly different) logics: \FO{} and \UFO{}. Nonetheless, the
+three benchmarks cover a diverse range of possibilities. Unlike the other two,
+the `friends' benchmark uses multiple predicates and can be written in \FO{}
+using only two variables and no cardinality constraints or counting quantifiers.
+Next, the `functions' benchmark, while still liftable by all of the algorithms,
+requires either the use of cardinality constraints, counting quantifiers, or
+more than two variables. Finally, the `bijections' benchmark is an example of a
+formula that can be handled by \textsc{FastWFOMC} but not \textsc{ForcLift}.
+
+% Metrics: Define the performance metrics used to evaluate the results (e.g.,
+% accuracy, precision, recall, F1-score, runtime).
+
+A major difference between \textsc{ForcLift} and the other two algorithms is
+that \textsc{ForcLift} does not support arbitrary-precision arithmetic whereas
+the other two algorithms both use the GNU Multiple Precision Arithmetic Library.
+Instead, when the numerical value of the count becomes too big to be accurately
+presented using finite precision, \textsc{ForcLift} returns $\infty$. We run
+each algorithm on each benchmark on domains of size $2^{1}, 2^{2}, 2^{3},\dots$
+until the algorithm times out after \SI{1}{\hour}, runs out of memory, or (in
+the case of \textsc{ForcLift}) returns $\infty$. We measure compilation and
+inference time separately, but primarily focus on total runtime (i.e., the sum
+of both), which is dominated by the latter.
+
+% Environment: Describe the hardware and software environment (e.g.,
+% specifications of the computer, operating system, libraries, and tools used).
+
+The experiments were run on an Intel Skylake \SI{2.4}{\giga\hertz} CPU with
+\SI{188}{\gibi\byte} of memory and CentOS~7 operating system. C++ programs were
+compiled using the Intel C++ Compiler 2020u4. \textsc{FastWFOMC} was run on
+Julia~1.10.4, while all other algorithms were run on the Java Virtual Machine
+1.8.0\_201.
+
+% 3. Results and Analysis
+% Presentation of Results: Use tables, graphs, and charts to present the experimental results clearly.
+% Comparison with Baselines: Compare your method’s results with the baselines.
+% Discussion: Analyze and interpret the results, highlighting the strengths and potential weaknesses of your approach.
+% Insights: Provide insights or patterns observed from the results.
+% Challenges: Discuss any challenges or unexpected outcomes.
+% Acknowledgement: Honestly acknowledge any limitations of your experiments or method.
+
 \begin{figure*}[t]
@@
 
-\Cref{fig:plot} shows the total runtime values as a measure of the overall
-performance of each algorithm. We also separately tracked compilation and
-inference times and commented on them where relevant. It is worth noting that
-\Cranebfs{} can handle more instances than either \textsc{ForcLift} or
-\Cranegreedy{}, including the bijection-counting problem in our experiments as
-well as similar formulas examined previously~\cite{DBLP:conf/kr/DilkasB23}.
-
-As shown in \cref{fig:plot}, the runtimes of all compilation-based algorithms
-remained practically constant, in contrast to the rapidly increasing runtimes of
-\textsc{FastWFOMC}. Although the search/compilation part is slower in
-\Cranetwo{} than in \textsc{ForcLift}, the difference is negligible. The
-runtimes of the FOKC algorithms appear constant because, for these counting
-problems and domain sizes, compilation time dominates inference time (remember
-that compilation time is independent of domain sizes). Indeed, the maximum
-inference time of \Cranebfs{} and \Cranegreedy{} across these experiments is
-only \SI{4}{\milli\second}. The runtimes of \Cranetwo{} have lower variation
-than those of \textsc{ForcLift} because we compile the formula anew for each
-domain size with \textsc{ForcLift}, whereas with \Cranetwo{}, we compile it once
-and reuse the resulting C++ program for all domain sizes.
+\Cref{fig:plot} summarises the experimental results. Only \textsc{FastWFOMC} and
+\Cranebfs{} could lift the bijection-counting problem. On this benchmark, the
+largest domain sizes that these algorithms could handle were \num{64} and
+\num{4096}, respectively. On the other two benchmarks, \textsc{ForcLift} has the
+lowest runtime, but, as it is finite-precision, only scales up to domain sizes
+of \num{16} and \num{128} in the case of `friends' and `functions',
+respectively. Next, \textsc{FastWFOMC} outperforms \textsc{ForcLift} in the case
+of `friends' but not `functions': it scales up to domains of size \num{1024} and
+\num{64}, respectively. Finally, both \Cranebfs{} and \Cranegreedy{} perform
+nearly identically on both of these benchmarks. Similarly to the `bijections'
+benchmark, \Cranetwo{} significantly surpasses the other two algorithms, scaling
+up to domains of size \num{8192} and \num{67108864}, respectively.
+
+Another aspect of the experimental results worth discussing separately is that
+of compilation. As both Julia and Scala use just-in-time (JIT) compilation, both
+\textsc{FastWFOMC} and \textsc{ForcLift} take longer when run on the smallest
+domain size, as that is when most JIT compilation happens. As \Cranetwo{} is run
+only once per benchmark, JIT compilation time is incorporated into its runtime
+across all domain sizes. Moreover, while \textsc{ForcLift} compilation is
+generally faster than that of \Cranetwo{}, neither is significant in comparison
+to inference time. Indeed, typically, \textsc{ForcLift} compilation took around
+\SI{0.5}{\second}, while \Cranetwo{} compilation took around \SI{2.3}{\second}.
+
+% 8. Conclusion
+% Summary: Briefly summarize the key findings from the experimental results.
+% Future Work: Suggest directions for future research based on your findings.
+
+So what do our experiments reveal about which algorithm should one use in
+practice? If the formula can be handled by \textsc{ForcLift} and the domain
+sizes are reasonably small, it is likely to be the fastest algorithm. In other
+cases, \Cranetwo{} is likely to be significantly faster than \textsc{FastWFOMC}
+across all domain sizes (but especially with higher domain sizes), assuming the
+formula can be handled by both algorithms.
+
+% TODO: run this section through editgpt and grammarly
 

### 2024-08-09 doc/paper/plot.tex
First (second?) draft of the 'experiments' section

@@
-% Created by tikzDevice version 0.12.6 on 2024-07-30 13:11:15
+% Created by tikzDevice version 0.12.6 on 2024-08-07 14:16:35
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] ( 48.13, 57.56) --
-	( 48.13,198.75);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] ( 85.60, 57.56) --
-	( 85.60,198.75);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (123.07, 57.56) --
-	(123.07,198.75);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (160.53, 57.56) --
-	(160.53,198.75);
+\path[draw=drawColor,line width= 0.2pt,line join=round] ( 42.89, 57.56) --
+	( 42.89,198.75);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] ( 81.85, 57.56) --
+	( 81.85,198.75);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (120.82, 57.56) --
+	(120.82,198.75);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (159.78, 57.56) --
+	(159.78,198.75);
 
@@
 
-\path[draw=drawColor,line width= 0.5pt,line join=round] ( 66.87, 57.56) --
-	( 66.87,198.75);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (104.33, 57.56) --
-	(104.33,198.75);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (141.80, 57.56) --
-	(141.80,198.75);
+\path[draw=drawColor,line width= 0.5pt,line join=round] ( 62.37, 57.56) --
+	( 62.37,198.75);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (101.34, 57.56) --
+	(101.34,198.75);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (140.30, 57.56) --
+	(140.30,198.75);
 
@@
 \path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.10,106.36) --
-	( 45.46,106.36) --
-	( 50.81,106.36) --
-	( 56.16,106.36) --
-	( 61.51,106.36) --
-	( 66.87,106.36) --
-	( 72.22,106.37) --
-	( 77.57,106.38) --
-	( 82.92,106.42) --
-	( 88.28,106.58) --
-	( 93.63,107.23) --
-	( 98.98,109.99) --
-	(104.33,117.90);
+	( 45.67,106.36) --
+	( 51.24,106.36) --
+	( 56.80,106.36) --
+	( 62.37,106.36) --
+	( 67.94,106.37) --
+	( 73.50,106.38) --
+	( 79.07,106.42) --
+	( 84.64,106.58) --
+	( 90.20,107.23) --
+	( 95.77,109.99) --
+	(101.34,117.90);
 \definecolor{drawColor}{RGB}{117,112,179}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 45.46,123.48) --
-	( 50.81,112.22) --
-	( 56.16,112.22) --
-	( 61.51,112.42) --
-	( 66.87,119.02) --
-	( 72.22,162.96);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 40.10,123.48) --
+	( 45.67,112.22) --
+	( 51.24,112.22) --
+	( 56.80,112.42) --
+	( 62.37,119.02) --
+	( 67.94,162.96);
 \definecolor{fillColor}{RGB}{27,158,119}
@@
 
-\path[fill=fillColor] ( 45.46,106.36) circle (  1.96);
-
-\path[fill=fillColor] ( 50.81,106.36) circle (  1.96);
-
-\path[fill=fillColor] ( 56.16,106.36) circle (  1.96);
-
-\path[fill=fillColor] ( 61.51,106.36) circle (  1.96);
-
-\path[fill=fillColor] ( 66.87,106.36) circle (  1.96);
-
-\path[fill=fillColor] ( 72.22,106.37) circle (  1.96);
-
-\path[fill=fillColor] ( 77.57,106.38) circle (  1.96);
-
-\path[fill=fillColor] ( 82.92,106.42) circle (  1.96);
-
-\path[fill=fillColor] ( 88.28,106.58) circle (  1.96);
-
-\path[fill=fillColor] ( 93.63,107.23) circle (  1.96);
-
-\path[fill=fillColor] ( 98.98,109.99) circle (  1.96);
-
-\path[fill=fillColor] (104.33,117.90) circle (  1.96);
+\path[fill=fillColor] ( 45.67,106.36) circle (  1.96);
+
+\path[fill=fillColor] ( 51.24,106.36) circle (  1.96);
+
+\path[fill=fillColor] ( 56.80,106.36) circle (  1.96);
+
+\path[fill=fillColor] ( 62.37,106.36) circle (  1.96);
+
+\path[fill=fillColor] ( 67.94,106.37) circle (  1.96);
+
+\path[fill=fillColor] ( 73.50,106.38) circle (  1.96);
+
+\path[fill=fillColor] ( 79.07,106.42) circle (  1.96);
+
+\path[fill=fillColor] ( 84.64,106.58) circle (  1.96);
+
+\path[fill=fillColor] ( 90.20,107.23) circle (  1.96);
+
+\path[fill=fillColor] ( 95.77,109.99) circle (  1.96);
+
+\path[fill=fillColor] (101.34,117.90) circle (  1.96);
 \definecolor{fillColor}{RGB}{117,112,179}
 
-\path[fill=fillColor] ( 43.49,121.52) --
-	( 47.42,121.52) --
-	( 47.42,125.44) --
-	( 43.49,125.44) --
-	cycle;
-
-\path[fill=fillColor] ( 48.85,110.26) --
-	( 52.77,110.26) --
-	( 52.77,114.18) --
-	( 48.85,114.18) --
-	cycle;
-
-\path[fill=fillColor] ( 54.20,110.26) --
-	( 58.12,110.26) --
-	( 58.12,114.18) --
-	( 54.20,114.18) --
-	cycle;
-
-\path[fill=fillColor] ( 59.55,110.46) --
-	( 63.47,110.46) --
-	( 63.47,114.38) --
-	( 59.55,114.38) --
-	cycle;
-
-\path[fill=fillColor] ( 64.90,117.06) --
-	( 68.83,117.06) --
-	( 68.83,120.99) --
-	( 64.90,120.99) --
-	cycle;
-
-\path[fill=fillColor] ( 70.26,161.00) --
-	( 74.18,161.00) --
-	( 74.18,164.92) --
-	( 70.26,164.92) --
+\path[fill=fillColor] ( 38.14,121.52) --
+	( 42.06,121.52) --
+	( 42.06,125.44) --
+	( 38.14,125.44) --
+	cycle;
+
+\path[fill=fillColor] ( 43.71,110.26) --
+	( 47.63,110.26) --
+	( 47.63,114.18) --
+	( 43.71,114.18) --
+	cycle;
+
+\path[fill=fillColor] ( 49.27,110.26) --
+	( 53.20,110.26) --
+	( 53.20,114.18) --
+	( 49.27,114.18) --
+	cycle;
+
+\path[fill=fillColor] ( 54.84,110.46) --
+	( 58.76,110.46) --
+	( 58.76,114.38) --
+	( 54.84,114.38) --
+	cycle;
+
+\path[fill=fillColor] ( 60.41,117.06) --
+	( 64.33,117.06) --
+	( 64.33,120.99) --
+	( 60.41,120.99) --
+	cycle;
+
+\path[fill=fillColor] ( 65.97,161.00) --
+	( 69.90,161.00) --
+	( 69.90,164.92) --
+	( 65.97,164.92) --
 	cycle;
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 34.75, 57.56) -- ( 34.75, 63.25);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 34.54, 57.56) -- ( 34.54, 63.25);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 45.46, 57.56) -- ( 45.46, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 50.81, 57.56) -- ( 50.81, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 56.16, 57.56) -- ( 56.16, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 61.51, 57.56) -- ( 61.51, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 66.87, 57.56) -- ( 66.87, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 72.22, 57.56) -- ( 72.22, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 77.57, 57.56) -- ( 77.57, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 82.92, 57.56) -- ( 82.92, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 88.28, 57.56) -- ( 88.28, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 93.63, 57.56) -- ( 93.63, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 98.98, 57.56) -- ( 98.98, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (104.33, 57.56) -- (104.33, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (109.69, 57.56) -- (109.69, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (115.04, 57.56) -- (115.04, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (120.39, 57.56) -- (120.39, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (125.74, 57.56) -- (125.74, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (131.10, 57.56) -- (131.10, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (136.45, 57.56) -- (136.45, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (141.80, 57.56) -- (141.80, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (147.15, 57.56) -- (147.15, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (152.51, 57.56) -- (152.51, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (157.86, 57.56) -- (157.86, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (163.21, 57.56) -- (163.21, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (168.56, 57.56) -- (168.56, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (173.92, 57.56) -- (173.92, 63.25);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 45.67, 57.56) -- ( 45.67, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 51.24, 57.56) -- ( 51.24, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 56.80, 57.56) -- ( 56.80, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 62.37, 57.56) -- ( 62.37, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 67.94, 57.56) -- ( 67.94, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 73.50, 57.56) -- ( 73.50, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 79.07, 57.56) -- ( 79.07, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 84.64, 57.56) -- ( 84.64, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 90.20, 57.56) -- ( 90.20, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 95.77, 57.56) -- ( 95.77, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (101.34, 57.56) -- (101.34, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (106.90, 57.56) -- (106.90, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (112.47, 57.56) -- (112.47, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (118.04, 57.56) -- (118.04, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (123.60, 57.56) -- (123.60, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (129.17, 57.56) -- (129.17, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (134.74, 57.56) -- (134.74, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (140.30, 57.56) -- (140.30, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (145.87, 57.56) -- (145.87, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (151.44, 57.56) -- (151.44, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (157.00, 57.56) -- (157.00, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (162.57, 57.56) -- (162.57, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (168.13, 57.56) -- (168.13, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (173.70, 57.56) -- (173.70, 63.25);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (184.62, 57.56) -- (184.62, 63.25);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (184.83, 57.56) -- (184.83, 63.25);
 
@@
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] (205.71, 57.56) --
-	(205.71,198.75);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (243.18, 57.56) --
-	(243.18,198.75);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (280.65, 57.56) --
-	(280.65,198.75);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (318.12, 57.56) --
-	(318.12,198.75);
+\path[draw=drawColor,line width= 0.2pt,line join=round] (200.47, 57.56) --
+	(200.47,198.75);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (239.43, 57.56) --
+	(239.43,198.75);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (278.40, 57.56) --
+	(278.40,198.75);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (317.37, 57.56) --
+	(317.37,198.75);
 
@@
 
-\path[draw=drawColor,line width= 0.5pt,line join=round] (224.45, 57.56) --
-	(224.45,198.75);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (261.91, 57.56) --
-	(261.91,198.75);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (299.38, 57.56) --
-	(299.38,198.75);
+\path[draw=drawColor,line width= 0.5pt,line join=round] (219.95, 57.56) --
+	(219.95,198.75);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (258.92, 57.56) --
+	(258.92,198.75);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (297.88, 57.56) --
+	(297.88,198.75);
 
@@
 \path[draw=drawColor,line width= 0.6pt,line join=round] (197.68, 87.62) --
-	(203.04, 87.62) --
-	(208.39, 87.61) --
-	(213.74, 87.61) --
-	(219.09, 87.61) --
-	(224.45, 87.61) --
-	(229.80, 87.61) --
-	(235.15, 87.62) --
-	(240.50, 87.69) --
-	(245.86, 88.58) --
-	(251.21, 97.29) --
-	(256.56,123.32) --
-	(261.91,157.55) --
-	(267.27,192.33);
+	(203.25, 87.61) --
+	(208.82, 87.61) --
+	(214.38, 87.61) --
+	(219.95, 87.61) --
+	(225.52, 87.61) --
+	(231.08, 87.62) --
+	(236.65, 87.69) --
+	(242.22, 88.58) --
+	(247.78, 97.29) --
+	(253.35,123.32) --
+	(258.92,157.55) --
+	(264.48,192.33);
 \definecolor{drawColor}{RGB}{217,95,2}
@@
 \path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (197.68, 87.37) --
-	(203.04, 87.37) --
-	(208.39, 87.36) --
-	(213.74, 87.36) --
-	(219.09, 87.36) --
-	(224.45, 87.36) --
-	(229.80, 87.36) --
-	(235.15, 87.37) --
-	(240.50, 87.44) --
-	(245.86, 88.34) --
-	(251.21, 97.16) --
-	(256.56,123.35) --
-	(261.91,157.54) --
-	(267.27,192.33);
+	(203.25, 87.36) --
+	(208.82, 87.36) --
+	(214.38, 87.36) --
+	(219.95, 87.36) --
+	(225.52, 87.36) --
+	(231.08, 87.37) --
+	(236.65, 87.44) --
+	(242.22, 88.34) --
+	(247.78, 97.16) --
+	(253.35,123.35) --
+	(258.92,157.54) --
+	(264.48,192.33);
 \definecolor{drawColor}{RGB}{117,112,179}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (203.04,113.24) --
-	(208.39,111.85) --
-	(213.74,111.59) --
-	(219.09,111.66) --
-	(224.45,112.12) --
-	(229.80,112.27) --
-	(235.15,112.50) --
-	(240.50,116.23) --
-	(245.86,130.94) --
-	(251.21,168.51);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (197.68,113.24) --
+	(203.25,111.85) --
+	(208.82,111.59) --
+	(214.38,111.66) --
+	(219.95,112.12) --
+	(225.52,112.27) --
+	(231.08,112.50) --
+	(236.65,116.23) --
+	(242.22,130.94) --
+	(247.78,168.51);
 \definecolor{drawColor}{RGB}{231,41,138}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (203.04, 68.42) --
-	(208.39, 63.98) --
-	(213.74, 63.98) --
-	(219.09, 63.98);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (197.68, 68.42) --
+	(203.25, 63.98) --
+	(208.82, 63.98) --
+	(214.38, 63.98);
 \definecolor{fillColor}{RGB}{117,112,179}
 
-\path[fill=fillColor] (201.07,111.28) --
-	(205.00,111.28) --
-	(205.00,115.20) --
-	(201.07,115.20) --
-	cycle;
-
-\path[fill=fillColor] (206.43,109.89) --
-	(210.35,109.89) --
-	(210.35,113.82) --
-	(206.43,113.82) --
-	cycle;
-
-\path[fill=fillColor] (211.78,109.63) --
-	(215.70,109.63) --
-	(215.70,113.55) --
-	(211.78,113.55) --
-	cycle;
-
-\path[fill=fillColor] (217.13,109.70) --
-	(221.06,109.70) --
-	(221.06,113.62) --
-	(217.13,113.62) --
-	cycle;
-
-\path[fill=fillColor] (222.49,110.16) --
-	(226.41,110.16) --
-	(226.41,114.09) --
-	(222.49,114.09) --
-	cycle;
-
-\path[fill=fillColor] (227.84,110.31) --
-	(231.76,110.31) --
-	(231.76,114.23) --
-	(227.84,114.23) --
-	cycle;
-
-\path[fill=fillColor] (233.19,110.53) --
-	(237.11,110.53) --
-	(237.11,114.46) --
-	(233.19,114.46) --
-	cycle;
-
-\path[fill=fillColor] (238.54,114.27) --
-	(242.47,114.27) --
-	(242.47,118.20) --
-	(238.54,118.20) --
-	cycle;
-
-\path[fill=fillColor] (243.90,128.97) --
-	(247.82,128.97) --
-	(247.82,132.90) --
-	(243.90,132.90) --
-	cycle;
-
-\path[fill=fillColor] (249.25,166.55) --
-	(253.17,166.55) --
-	(253.17,170.47) --
-	(249.25,170.47) --
+\path[fill=fillColor] (195.72,111.28) --
+	(199.65,111.28) --
+	(199.65,115.20) --
+	(195.72,115.20) --
+	cycle;
+
+\path[fill=fillColor] (201.29,109.89) --
+	(205.21,109.89) --
+	(205.21,113.82) --
+	(201.29,113.82) --
+	cycle;
+
+\path[fill=fillColor] (206.86,109.63) --
+	(210.78,109.63) --
+	(210.78,113.55) --
+	(206.86,113.55) --
+	cycle;
+
+\path[fill=fillColor] (212.42,109.70) --
+	(216.35,109.70) --
+	(216.35,113.62) --
+	(212.42,113.62) --
+	cycle;
+
+\path[fill=fillColor] (217.99,110.16) --
+	(221.91,110.16) --
+	(221.91,114.09) --
+	(217.99,114.09) --
+	cycle;
+
+\path[fill=fillColor] (223.56,110.31) --
+	(227.48,110.31) --
+	(227.48,114.23) --
+	(223.56,114.23) --
+	cycle;
+
+\path[fill=fillColor] (229.12,110.53) --
+	(233.05,110.53) --
+	(233.05,114.46) --
+	(229.12,114.46) --
+	cycle;
+
+\path[fill=fillColor] (234.69,114.27) --
+	(238.61,114.27) --
+	(238.61,118.20) --
+	(234.69,118.20) --
+	cycle;
+
+\path[fill=fillColor] (240.26,128.97) --
+	(244.18,128.97) --
+	(244.18,132.90) --
+	(240.26,132.90) --
+	cycle;
+
+\path[fill=fillColor] (245.82,166.55) --
+	(249.75,166.55) --
+	(249.75,170.47) --
+	(245.82,170.47) --
 	cycle;
@@
 
-\path[fill=fillColor] (203.04, 90.42) --
-	(205.68, 85.84) --
-	(200.39, 85.84) --
-	cycle;
-
-\path[fill=fillColor] (208.39, 90.41) --
-	(211.03, 85.84) --
-	(205.75, 85.84) --
-	cycle;
-
-\path[fill=fillColor] (213.74, 90.41) --
-	(216.38, 85.84) --
-	(211.10, 85.84) --
-	cycle;
-
-\path[fill=fillColor] (219.09, 90.41) --
-	(221.74, 85.84) --
-	(216.45, 85.84) --
-	cycle;
-
-\path[fill=fillColor] (224.45, 90.41) --
-	(227.09, 85.84) --
-	(221.80, 85.84) --
-	cycle;
-
-\path[fill=fillColor] (229.80, 90.41) --
-	(232.44, 85.84) --
-	(227.16, 85.84) --
-	cycle;
-
-\path[fill=fillColor] (235.15, 90.42) --
-	(237.79, 85.84) --
-	(232.51, 85.84) --
-	cycle;
-
-\path[fill=fillColor] (240.50, 90.49) --
-	(243.15, 85.92) --
-	(237.86, 85.92) --
-	cycle;
-
-\path[fill=fillColor] (245.86, 91.39) --
-	(248.50, 86.82) --
-	(243.21, 86.82) --
-	cycle;
-
-\path[fill=fillColor] (251.21,100.21) --
-	(253.85, 95.64) --
-	(248.57, 95.64) --
-	cycle;
-
-\path[fill=fillColor] (256.56,126.40) --
-	(259.20,121.82) --
-	(253.92,121.82) --
-	cycle;
-
-\path[fill=fillColor] (261.91,160.59) --
-	(264.56,156.02) --
-	(259.27,156.02) --
-	cycle;
-
-\path[fill=fillColor] (267.27,195.39) --
-	(269.91,190.81) --
-	(264.62,190.81) --
-	cycle;
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.26, 68.42) -- (205.81, 68.42);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.04, 65.64) -- (203.04, 71.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (205.61, 63.98) -- (211.16, 63.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.39, 61.20) -- (208.39, 66.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.97, 63.98) -- (216.52, 63.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (213.74, 61.20) -- (213.74, 66.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (216.32, 63.98) -- (221.87, 63.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (219.09, 61.20) -- (219.09, 66.75);
+\path[fill=fillColor] (203.25, 90.41) --
+	(205.89, 85.84) --
+	(200.61, 85.84) --
+	cycle;
+
+\path[fill=fillColor] (208.82, 90.41) --
+	(211.46, 85.84) --
+	(206.18, 85.84) --
+	cycle;
+
+\path[fill=fillColor] (214.38, 90.41) --
+	(217.03, 85.84) --
+	(211.74, 85.84) --
+	cycle;
+
+\path[fill=fillColor] (219.95, 90.41) --
+	(222.59, 85.84) --
+	(217.31, 85.84) --
+	cycle;
+
+\path[fill=fillColor] (225.52, 90.41) --
+	(228.16, 85.84) --
+	(222.88, 85.84) --
+	cycle;
+
+\path[fill=fillColor] (231.08, 90.42) --
+	(233.73, 85.84) --
+	(228.44, 85.84) --
+	cycle;
+
+\path[fill=fillColor] (236.65, 90.49) --
+	(239.29, 85.92) --
+	(234.01, 85.92) --
+	cycle;
+
+\path[fill=fillColor] (242.22, 91.39) --
+	(244.86, 86.82) --
+	(239.57, 86.82) --
+	cycle;
+
+\path[fill=fillColor] (247.78,100.21) --
+	(250.43, 95.64) --
+	(245.14, 95.64) --
+	cycle;
+
+\path[fill=fillColor] (253.35,126.40) --
+	(255.99,121.82) --
+	(250.71,121.82) --
+	cycle;
+
+\path[fill=fillColor] (258.92,160.59) --
+	(261.56,156.02) --
+	(256.27,156.02) --
+	cycle;
+
+\path[fill=fillColor] (264.48,195.39) --
+	(267.13,190.81) --
+	(261.84,190.81) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.91, 68.42) -- (200.46, 68.42);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.68, 65.64) -- (197.68, 71.19);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.48, 63.98) -- (206.03, 63.98);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.25, 61.20) -- (203.25, 66.75);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.04, 63.98) -- (211.59, 63.98);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.82, 61.20) -- (208.82, 66.75);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.61, 63.98) -- (217.16, 63.98);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.38, 61.20) -- (214.38, 66.75);
 \definecolor{fillColor}{RGB}{27,158,119}
@@
 
-\path[fill=fillColor] (203.04, 87.62) circle (  1.96);
-
-\path[fill=fillColor] (208.39, 87.61) circle (  1.96);
-
-\path[fill=fillColor] (213.74, 87.61) circle (  1.96);
-
-\path[fill=fillColor] (219.09, 87.61) circle (  1.96);
-
-\path[fill=fillColor] (224.45, 87.61) circle (  1.96);
-
-\path[fill=fillColor] (229.80, 87.61) circle (  1.96);
-
-\path[fill=fillColor] (235.15, 87.62) circle (  1.96);
-
-\path[fill=fillColor] (240.50, 87.69) circle (  1.96);
-
-\path[fill=fillColor] (245.86, 88.58) circle (  1.96);
-
-\path[fill=fillColor] (251.21, 97.29) circle (  1.96);
-
-\path[fill=fillColor] (256.56,123.32) circle (  1.96);
-
-\path[fill=fillColor] (261.91,157.55) circle (  1.96);
-
-\path[fill=fillColor] (267.27,192.33) circle (  1.96);
+\path[fill=fillColor] (203.25, 87.61) circle (  1.96);
+
+\path[fill=fillColor] (208.82, 87.61) circle (  1.96);
+
+\path[fill=fillColor] (214.38, 87.61) circle (  1.96);
+
+\path[fill=fillColor] (219.95, 87.61) circle (  1.96);
+
+\path[fill=fillColor] (225.52, 87.61) circle (  1.96);
+
+\path[fill=fillColor] (231.08, 87.62) circle (  1.96);
+
+\path[fill=fillColor] (236.65, 87.69) circle (  1.96);
+
+\path[fill=fillColor] (242.22, 88.58) circle (  1.96);
+
+\path[fill=fillColor] (247.78, 97.29) circle (  1.96);
+
+\path[fill=fillColor] (253.35,123.32) circle (  1.96);
+
+\path[fill=fillColor] (258.92,157.55) circle (  1.96);
+
+\path[fill=fillColor] (264.48,192.33) circle (  1.96);
 \definecolor{drawColor}{gray}{0.70}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (192.33, 57.56) -- (192.33, 63.25);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (192.12, 57.56) -- (192.12, 63.25);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (203.04, 57.56) -- (203.04, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (208.39, 57.56) -- (208.39, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (213.74, 57.56) -- (213.74, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (219.09, 57.56) -- (219.09, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (224.45, 57.56) -- (224.45, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (229.80, 57.56) -- (229.80, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (235.15, 57.56) -- (235.15, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (240.50, 57.56) -- (240.50, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (245.86, 57.56) -- (245.86, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (251.21, 57.56) -- (251.21, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (256.56, 57.56) -- (256.56, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (261.91, 57.56) -- (261.91, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (267.27, 57.56) -- (267.27, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (272.62, 57.56) -- (272.62, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (277.97, 57.56) -- (277.97, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (283.32, 57.56) -- (283.32, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (288.68, 57.56) -- (288.68, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (294.03, 57.56) -- (294.03, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (299.38, 57.56) -- (299.38, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (304.73, 57.56) -- (304.73, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (310.09, 57.56) -- (310.09, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (315.44, 57.56) -- (315.44, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (320.79, 57.56) -- (320.79, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (326.14, 57.56) -- (326.14, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (331.50, 57.56) -- (331.50, 63.25);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (203.25, 57.56) -- (203.25, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (208.82, 57.56) -- (208.82, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (214.38, 57.56) -- (214.38, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (219.95, 57.56) -- (219.95, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (225.52, 57.56) -- (225.52, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (231.08, 57.56) -- (231.08, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (236.65, 57.56) -- (236.65, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (242.22, 57.56) -- (242.22, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (247.78, 57.56) -- (247.78, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (253.35, 57.56) -- (253.35, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (258.92, 57.56) -- (258.92, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (264.48, 57.56) -- (264.48, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (270.05, 57.56) -- (270.05, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (275.62, 57.56) -- (275.62, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (281.18, 57.56) -- (281.18, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.75, 57.56) -- (286.75, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (292.32, 57.56) -- (292.32, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.88, 57.56) -- (297.88, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (303.45, 57.56) -- (303.45, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (309.02, 57.56) -- (309.02, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (314.58, 57.56) -- (314.58, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (320.15, 57.56) -- (320.15, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (325.72, 57.56) -- (325.72, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (331.28, 57.56) -- (331.28, 63.25);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (342.20, 57.56) -- (342.20, 63.25);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (342.42, 57.56) -- (342.42, 63.25);
 
@@
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] (363.30, 57.56) --
-	(363.30,198.75);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (400.76, 57.56) --
-	(400.76,198.75);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (438.23, 57.56) --
-	(438.23,198.75);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (475.70, 57.56) --
-	(475.70,198.75);
+\path[draw=drawColor,line width= 0.2pt,line join=round] (358.05, 57.56) --
+	(358.05,198.75);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (397.02, 57.56) --
+	(397.02,198.75);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (435.98, 57.56) --
+	(435.98,198.75);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (474.95, 57.56) --
+	(474.95,198.75);
 
@@
 
-\path[draw=drawColor,line width= 0.5pt,line join=round] (382.03, 57.56) --
-	(382.03,198.75);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (419.50, 57.56) --
-	(419.50,198.75);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (456.96, 57.56) --
-	(456.96,198.75);
+\path[draw=drawColor,line width= 0.5pt,line join=round] (377.53, 57.56) --
+	(377.53,198.75);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (416.50, 57.56) --
+	(416.50,198.75);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (455.47, 57.56) --
+	(455.47,198.75);
 
@@
 \path[draw=drawColor,line width= 0.6pt,line join=round] (355.27, 89.52) --
-	(360.62, 89.52) --
-	(365.97, 89.52) --
-	(371.32, 89.52) --
-	(376.68, 89.52) --
-	(382.03, 89.52) --
-	(387.38, 89.52) --
-	(392.73, 89.52) --
-	(398.09, 89.52) --
-	(403.44, 89.52) --
-	(408.79, 89.52) --
-	(414.14, 89.52) --
-	(419.50, 89.52) --
-	(424.85, 89.53) --
-	(430.20, 89.55) --
-	(435.55, 89.61) --
-	(440.91, 89.71) --
-	(446.26, 89.97) --
-	(451.61, 90.65) --
-	(456.96, 92.11) --
-	(462.32, 95.47) --
-	(467.67,101.07) --
-	(473.02,108.80) --
-	(478.37,119.46) --
-	(483.73,132.70) --
-	(489.08,144.57) --
+	(360.83, 89.52) --
+	(366.40, 89.52) --
+	(371.97, 89.52) --
+	(377.53, 89.52) --
+	(383.10, 89.52) --
+	(388.67, 89.52) --
+	(394.23, 89.52) --
+	(399.80, 89.52) --
+	(405.37, 89.52) --
+	(410.93, 89.52) --
+	(416.50, 89.52) --
+	(422.07, 89.53) --
+	(427.63, 89.55) --
+	(433.20, 89.61) --
+	(438.77, 89.71) --
+	(444.33, 89.97) --
+	(449.90, 90.65) --
+	(455.47, 92.11) --
+	(461.03, 95.47) --
+	(466.60,101.07) --
+	(472.17,108.80) --
+	(477.73,119.46) --
+	(483.30,132.70) --
+	(488.87,144.57) --
 	(494.43,157.31);
@@
 \path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (355.27, 88.43) --
-	(360.62, 88.43) --
-	(365.97, 88.43) --
-	(371.32, 88.43) --
-	(376.68, 88.43) --
-	(382.03, 88.43) --
-	(387.38, 88.43) --
-	(392.73, 88.43) --
-	(398.09, 88.43) --
-	(403.44, 88.43) --
-	(408.79, 88.43) --
-	(414.14, 88.43) --
-	(419.50, 88.43) --
-	(424.85, 88.44) --
-	(430.20, 88.46) --
-	(435.55, 88.51) --
-	(440.91, 88.64) --
-	(446.26, 88.92) --
-	(451.61, 89.63) --
-	(456.96, 91.16) --
-	(462.32, 94.48) --
-	(467.67,100.45) --
-	(473.02,108.29) --
-	(478.37,119.14) --
-	(483.73,132.38) --
-	(489.08,144.46) --
+	(360.83, 88.43) --
+	(366.40, 88.43) --
+	(371.97, 88.43) --
+	(377.53, 88.43) --
+	(383.10, 88.43) --
+	(388.67, 88.43) --
+	(394.23, 88.43) --
+	(399.80, 88.43) --
+	(405.37, 88.43) --
+	(410.93, 88.43) --
+	(416.50, 88.43) --
+	(422.07, 88.44) --
+	(427.63, 88.46) --
+	(433.20, 88.51) --
+	(438.77, 88.64) --
+	(444.33, 88.92) --
+	(449.90, 89.63) --
+	(455.47, 91.16) --
+	(461.03, 94.48) --
+	(466.60,100.45) --
+	(472.17,108.29) --
+	(477.73,119.14) --
+	(483.30,132.38) --
+	(488.87,144.46) --
 	(494.43,157.43);
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (360.62,114.65) --
-	(365.97,111.15) --
-	(371.32,111.49) --
-	(376.68,111.10) --
-	(382.03,115.68) --
-	(387.38,162.17);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (355.27,114.65) --
+	(360.83,111.15) --
+	(366.40,111.49) --
+	(371.97,111.10) --
+	(377.53,115.68) --
+	(383.10,162.17);
 \definecolor{drawColor}{RGB}{231,41,138}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (360.62, 66.36) --
-	(365.97, 64.61) --
-	(371.32, 64.61) --
-	(376.68, 64.61) --
-	(382.03, 64.61) --
-	(387.38, 64.92) --
-	(392.73, 64.92);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (355.27, 66.36) --
+	(360.83, 64.61) --
+	(366.40, 64.61) --
+	(371.97, 64.61) --
+	(377.53, 64.61) --
+	(383.10, 64.92) --
+	(388.67, 64.92);
 \definecolor{fillColor}{RGB}{27,158,119}
@@
 
-\path[fill=fillColor] (360.62, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (365.97, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (371.32, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (376.68, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (382.03, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (387.38, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (392.73, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (398.09, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (403.44, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (408.79, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (414.14, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (419.50, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (424.85, 89.53) circle (  1.96);
-
-\path[fill=fillColor] (430.20, 89.55) circle (  1.96);
-
-\path[fill=fillColor] (435.55, 89.61) circle (  1.96);
-
-\path[fill=fillColor] (440.91, 89.71) circle (  1.96);
-
-\path[fill=fillColor] (446.26, 89.97) circle (  1.96);
-
-\path[fill=fillColor] (451.61, 90.65) circle (  1.96);
-
-\path[fill=fillColor] (456.96, 92.11) circle (  1.96);
-
-\path[fill=fillColor] (462.32, 95.47) circle (  1.96);
-
-\path[fill=fillColor] (467.67,101.07) circle (  1.96);
-
-\path[fill=fillColor] (473.02,108.80) circle (  1.96);
-
-\path[fill=fillColor] (478.37,119.46) circle (  1.96);
-
-\path[fill=fillColor] (483.73,132.70) circle (  1.96);
-
-\path[fill=fillColor] (489.08,144.57) circle (  1.96);
+\path[fill=fillColor] (360.83, 89.52) circle (  1.96);
+
+\path[fill=fillColor] (366.40, 89.52) circle (  1.96);
+
+\path[fill=fillColor] (371.97, 89.52) circle (  1.96);
+
+\path[fill=fillColor] (377.53, 89.52) circle (  1.96);
+
+\path[fill=fillColor] (383.10, 89.52) circle (  1.96);
+
+\path[fill=fillColor] (388.67, 89.52) circle (  1.96);
+
+\path[fill=fillColor] (394.23, 89.52) circle (  1.96);
+
+\path[fill=fillColor] (399.80, 89.52) circle (  1.96);
+
+\path[fill=fillColor] (405.37, 89.52) circle (  1.96);
+
+\path[fill=fillColor] (410.93, 89.52) circle (  1.96);
+
+\path[fill=fillColor] (416.50, 89.52) circle (  1.96);
+
+\path[fill=fillColor] (422.07, 89.53) circle (  1.96);
+
+\path[fill=fillColor] (427.63, 89.55) circle (  1.96);
+
+\path[fill=fillColor] (433.20, 89.61) circle (  1.96);
+
+\path[fill=fillColor] (438.77, 89.71) circle (  1.96);
+
+\path[fill=fillColor] (444.33, 89.97) circle (  1.96);
+
+\path[fill=fillColor] (449.90, 90.65) circle (  1.96);
+
+\path[fill=fillColor] (455.47, 92.11) circle (  1.96);
+
+\path[fill=fillColor] (461.03, 95.47) circle (  1.96);
+
+\path[fill=fillColor] (466.60,101.07) circle (  1.96);
+
+\path[fill=fillColor] (472.17,108.80) circle (  1.96);
+
+\path[fill=fillColor] (477.73,119.46) circle (  1.96);
+
+\path[fill=fillColor] (483.30,132.70) circle (  1.96);
+
+\path[fill=fillColor] (488.87,144.57) circle (  1.96);
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (357.84, 66.36) -- (363.39, 66.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (360.62, 63.59) -- (360.62, 69.14);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (363.20, 64.61) -- (368.75, 64.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (365.97, 61.83) -- (365.97, 67.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (368.55, 64.61) -- (374.10, 64.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (371.32, 61.83) -- (371.32, 67.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (373.90, 64.61) -- (379.45, 64.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (376.68, 61.83) -- (376.68, 67.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.25, 64.61) -- (384.80, 64.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (382.03, 61.83) -- (382.03, 67.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (384.61, 64.92) -- (390.16, 64.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (387.38, 62.14) -- (387.38, 67.69);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (389.96, 64.92) -- (395.51, 64.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (392.73, 62.14) -- (392.73, 67.69);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (352.49, 66.36) -- (358.04, 66.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (355.27, 63.59) -- (355.27, 69.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (358.06, 64.61) -- (363.61, 64.61);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (360.83, 61.83) -- (360.83, 67.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (363.62, 64.61) -- (369.17, 64.61);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (366.40, 61.83) -- (366.40, 67.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.19, 64.61) -- (374.74, 64.61);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (371.97, 61.83) -- (371.97, 67.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.76, 64.61) -- (380.31, 64.61);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.53, 61.83) -- (377.53, 67.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (380.32, 64.92) -- (385.87, 64.92);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.10, 62.14) -- (383.10, 67.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (385.89, 64.92) -- (391.44, 64.92);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.67, 62.14) -- (388.67, 67.69);
 \definecolor{fillColor}{RGB}{117,112,179}
 
-\path[fill=fillColor] (358.66,112.68) --
-	(362.58,112.68) --
-	(362.58,116.61) --
-	(358.66,116.61) --
-	cycle;
-
-\path[fill=fillColor] (364.01,109.19) --
-	(367.93,109.19) --
-	(367.93,113.11) --
-	(364.01,113.11) --
-	cycle;
-
-\path[fill=fillColor] (369.36,109.53) --
-	(373.29,109.53) --
-	(373.29,113.45) --
-	(369.36,113.45) --
-	cycle;
-
-\path[fill=fillColor] (374.71,109.13) --
-	(378.64,109.13) --
-	(378.64,113.06) --
-	(374.71,113.06) --
-	cycle;
-
-\path[fill=fillColor] (380.07,113.72) --
-	(383.99,113.72) --
-	(383.99,117.64) --
-	(380.07,117.64) --
-	cycle;
-
-\path[fill=fillColor] (385.42,160.21) --
-	(389.34,160.21) --
-	(389.34,164.13) --
-	(385.42,164.13) --
+\path[fill=fillColor] (353.30,112.68) --
+	(357.23,112.68) --
+	(357.23,116.61) --
+	(353.30,116.61) --
+	cycle;
+
+\path[fill=fillColor] (358.87,109.19) --
+	(362.80,109.19) --
+	(362.80,113.11) --
+	(358.87,113.11) --
+	cycle;
+
+\path[fill=fillColor] (364.44,109.53) --
+	(368.36,109.53) --
+	(368.36,113.45) --
+	(364.44,113.45) --
+	cycle;
+
+\path[fill=fillColor] (370.00,109.13) --
+	(373.93,109.13) --
+	(373.93,113.06) --
+	(370.00,113.06) --
+	cycle;
+
+\path[fill=fillColor] (375.57,113.72) --
+	(379.50,113.72) --
+	(379.50,117.64) --
+	(375.57,117.64) --
+	cycle;
+
+\path[fill=fillColor] (381.14,160.21) --
+	(385.06,160.21) --
+	(385.06,164.13) --
+	(381.14,164.13) --
 	cycle;
@@
 \path[fill=fillColor] (355.27, 91.48) --
-	(357.91, 86.91) --
-	(352.62, 86.91) --
-	cycle;
-
-\path[fill=fillColor] (360.62, 91.48) --
-	(363.26, 86.90) --
-	(357.98, 86.90) --
-	cycle;
-
-\path[fill=fillColor] (365.97, 91.48) --
-	(368.61, 86.90) --
-	(363.33, 86.90) --
-	cycle;
-
-\path[fill=fillColor] (371.32, 91.48) --
-	(373.97, 86.90) --
-	(368.68, 86.90) --
-	cycle;
-
-\path[fill=fillColor] (376.68, 91.48) --
-	(379.32, 86.90) --
-	(374.03, 86.90) --
-	cycle;
-
-\path[fill=fillColor] (382.03, 91.48) --
-	(384.67, 86.90) --
-	(379.39, 86.90) --
-	cycle;
-
-\path[fill=fillColor] (387.38, 91.48) --
-	(390.02, 86.90) --
-	(384.74, 86.90) --
-	cycle;
-
-\path[fill=fillColor] (392.73, 91.48) --
-	(395.38, 86.91) --
-	(390.09, 86.91) --
-	cycle;
-
-\path[fill=fillColor] (398.09, 91.48) --
-	(400.73, 86.90) --
-	(395.44, 86.90) --
-	cycle;
-
-\path[fill=fillColor] (403.44, 91.48) --
-	(406.08, 86.90) --
-	(400.80, 86.90) --
-	cycle;
-
-\path[fill=fillColor] (408.79, 91.48) --
-	(411.43, 86.91) --
-	(406.15, 86.91) --
-	cycle;
-
-\path[fill=fillColor] (414.14, 91.48) --
-	(416.79, 86.91) --
-	(411.50, 86.91) --
-	cycle;
-
-\path[fill=fillColor] (419.50, 91.48) --
-	(422.14, 86.91) --
-	(416.85, 86.91) --
-	cycle;
-
-\path[fill=fillColor] (424.85, 91.50) --
-	(427.49, 86.92) --
-	(422.21, 86.92) --
-	cycle;
-
-\path[fill=fillColor] (430.20, 91.51) --
-	(432.84, 86.93) --
-	(427.56, 86.93) --
-	cycle;
-
-\path[fill=fillColor] (435.55, 91.57) --
-	(438.20, 86.99) --
-	(432.91, 86.99) --
-	cycle;
-
-\path[fill=fillColor] (440.91, 91.69) --
-	(443.55, 87.11) --
-	(438.26, 87.11) --
-	cycle;
-
-\path[fill=fillColor] (446.26, 91.97) --
-	(448.90, 87.39) --
-	(443.62, 87.39) --
-	cycle;
-
-\path[fill=fillColor] (451.61, 92.68) --
-	(454.25, 88.10) --
-	(448.97, 88.10) --
-	cycle;
-
-\path[fill=fillColor] (456.96, 94.21) --
-	(459.61, 89.64) --
-	(454.32, 89.64) --
-	cycle;
-
-\path[fill=fillColor] (462.32, 97.53) --
-	(464.96, 92.95) --
-	(459.67, 92.95) --
-	cycle;
-
-\path[fill=fillColor] (467.67,103.50) --
-	(470.31, 98.92) --
-	(465.03, 98.92) --
-	cycle;
-
-\path[fill=fillColor] (473.02,111.34) --
-	(475.66,106.76) --
-	(470.38,106.76) --
-	cycle;
-
-\path[fill=fillColor] (478.37,122.19) --
-	(481.02,117.61) --
-	(475.73,117.61) --
-	cycle;
-
-\path[fill=fillColor] (483.73,135.43) --
-	(486.37,130.86) --
-	(481.08,130.86) --
-	cycle;
-
-\path[fill=fillColor] (489.08,147.51) --
-	(491.72,142.93) --
-	(486.44,142.93) --
+	(357.91, 86.90) --
+	(352.62, 86.90) --
+	cycle;
+
+\path[fill=fillColor] (360.83, 91.48) --
+	(363.48, 86.90) --
+	(358.19, 86.90) --
+	cycle;
+
+\path[fill=fillColor] (366.40, 91.48) --
+	(369.04, 86.90) --
+	(363.76, 86.90) --
+	cycle;
+
+\path[fill=fillColor] (371.97, 91.48) --
+	(374.61, 86.90) --
+	(369.32, 86.90) --
+	cycle;
+
+\path[fill=fillColor] (377.53, 91.48) --
+	(380.18, 86.90) --
+	(374.89, 86.90) --
+	cycle;
+
+\path[fill=fillColor] (383.10, 91.48) --
+	(385.74, 86.90) --
+	(380.46, 86.90) --
+	cycle;
+
+\path[fill=fillColor] (388.67, 91.48) --
+	(391.31, 86.91) --
+	(386.02, 86.91) --
+	cycle;
+
+\path[fill=fillColor] (394.23, 91.48) --
+	(396.88, 86.90) --
+	(391.59, 86.90) --
+	cycle;
+
+\path[fill=fillColor] (399.80, 91.48) --
+	(402.44, 86.90) --
+	(397.16, 86.90) --
+	cycle;
+
+\path[fill=fillColor] (405.37, 91.48) --
+	(408.01, 86.91) --
+	(402.72, 86.91) --
+	cycle;
+
+\path[fill=fillColor] (410.93, 91.48) --
+	(413.58, 86.91) --
+	(408.29, 86.91) --
+	cycle;
+
+\path[fill=fillColor] (416.50, 91.48) --
+	(419.14, 86.91) --
+	(413.86, 86.91) --
+	cycle;
+
+\path[fill=fillColor] (422.07, 91.50) --
+	(424.71, 86.92) --
+	(419.42, 86.92) --
+	cycle;
+
+\path[fill=fillColor] (427.63, 91.51) --
+	(430.27, 86.93) --
+	(424.99, 86.93) --
+	cycle;
+
+\path[fill=fillColor] (433.20, 91.57) --
+	(435.84, 86.99) --
+	(430.56, 86.99) --
+	cycle;
+
+\path[fill=fillColor] (438.77, 91.69) --
+	(441.41, 87.11) --
+	(436.12, 87.11) --
+	cycle;
+
+\path[fill=fillColor] (444.33, 91.97) --
+	(446.97, 87.39) --
+	(441.69, 87.39) --
+	cycle;
+
+\path[fill=fillColor] (449.90, 92.68) --
+	(452.54, 88.10) --
+	(447.26, 88.10) --
+	cycle;
+
+\path[fill=fillColor] (455.47, 94.21) --
+	(458.11, 89.64) --
+	(452.82, 89.64) --
+	cycle;
+
+\path[fill=fillColor] (461.03, 97.53) --
+	(463.67, 92.95) --
+	(458.39, 92.95) --
+	cycle;
+
+\path[fill=fillColor] (466.60,103.50) --
+	(469.24, 98.92) --
+	(463.96, 98.92) --
+	cycle;
+
+\path[fill=fillColor] (472.17,111.34) --
+	(474.81,106.76) --
+	(469.52,106.76) --
+	cycle;
+
+\path[fill=fillColor] (477.73,122.19) --
+	(480.37,117.61) --
+	(475.09,117.61) --
+	cycle;
+
+\path[fill=fillColor] (483.30,135.43) --
+	(485.94,130.86) --
+	(480.66,130.86) --
+	cycle;
+
+\path[fill=fillColor] (488.87,147.51) --
+	(491.51,142.93) --
+	(486.22,142.93) --
 	cycle;
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (349.91, 57.56) -- (349.91, 63.25);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (349.70, 57.56) -- (349.70, 63.25);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (360.62, 57.56) -- (360.62, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (365.97, 57.56) -- (365.97, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (371.32, 57.56) -- (371.32, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (376.68, 57.56) -- (376.68, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (382.03, 57.56) -- (382.03, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (387.38, 57.56) -- (387.38, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (392.73, 57.56) -- (392.73, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (398.09, 57.56) -- (398.09, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (403.44, 57.56) -- (403.44, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (408.79, 57.56) -- (408.79, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (414.14, 57.56) -- (414.14, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (419.50, 57.56) -- (419.50, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (424.85, 57.56) -- (424.85, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (430.20, 57.56) -- (430.20, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (435.55, 57.56) -- (435.55, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (440.91, 57.56) -- (440.91, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (446.26, 57.56) -- (446.26, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (451.61, 57.56) -- (451.61, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (456.96, 57.56) -- (456.96, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (462.32, 57.56) -- (462.32, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (467.67, 57.56) -- (467.67, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (473.02, 57.56) -- (473.02, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (478.37, 57.56) -- (478.37, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (483.73, 57.56) -- (483.73, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (489.08, 57.56) -- (489.08, 63.25);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (360.83, 57.56) -- (360.83, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (366.40, 57.56) -- (366.40, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (371.97, 57.56) -- (371.97, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (377.53, 57.56) -- (377.53, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (383.10, 57.56) -- (383.10, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (388.67, 57.56) -- (388.67, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (394.23, 57.56) -- (394.23, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (399.80, 57.56) -- (399.80, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (405.37, 57.56) -- (405.37, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (410.93, 57.56) -- (410.93, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (416.50, 57.56) -- (416.50, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (422.07, 57.56) -- (422.07, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (427.63, 57.56) -- (427.63, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (433.20, 57.56) -- (433.20, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (438.77, 57.56) -- (438.77, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (444.33, 57.56) -- (444.33, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (449.90, 57.56) -- (449.90, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (455.47, 57.56) -- (455.47, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (461.03, 57.56) -- (461.03, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (466.60, 57.56) -- (466.60, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (472.17, 57.56) -- (472.17, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (477.73, 57.56) -- (477.73, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (483.30, 57.56) -- (483.30, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (488.87, 57.56) -- (488.87, 63.25);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (499.78, 57.56) -- (499.78, 63.25);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (500.00, 57.56) -- (500.00, 63.25);
 
@@
 
-\path[draw=drawColor,line width= 0.5pt,line join=round] ( 66.87, 55.31) --
-	( 66.87, 57.56);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (104.33, 55.31) --
-	(104.33, 57.56);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (141.80, 55.31) --
-	(141.80, 57.56);
+\path[draw=drawColor,line width= 0.5pt,line join=round] ( 62.37, 55.31) --
+	( 62.37, 57.56);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (101.34, 55.31) --
+	(101.34, 57.56);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (140.30, 55.31) --
+	(140.30, 57.56);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 66.87, 48.55) {$2^{5}$};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (104.33, 48.55) {$2^{12}$};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (141.80, 48.55) {$2^{19}$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 62.37, 48.55) {$2^{5}$};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (101.34, 48.55) {$2^{12}$};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (140.30, 48.55) {$2^{19}$};
 
@@
 
-\path[draw=drawColor,line width= 0.5pt,line join=round] (224.45, 55.31) --
-	(224.45, 57.56);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (261.91, 55.31) --
-	(261.91, 57.56);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (299.38, 55.31) --
-	(299.38, 57.56);
+\path[draw=drawColor,line width= 0.5pt,line join=round] (219.95, 55.31) --
+	(219.95, 57.56);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (258.92, 55.31) --
+	(258.92, 57.56);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (297.88, 55.31) --
+	(297.88, 57.56);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (224.45, 48.55) {$2^{5}$};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (261.91, 48.55) {$2^{12}$};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (299.38, 48.55) {$2^{19}$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (219.95, 48.55) {$2^{5}$};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (258.92, 48.55) {$2^{12}$};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (297.88, 48.55) {$2^{19}$};
 
@@
 
-\path[draw=drawColor,line width= 0.5pt,line join=round] (382.03, 55.31) --
-	(382.03, 57.56);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (419.50, 55.31) --
-	(419.50, 57.56);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (456.96, 55.31) --
-	(456.96, 57.56);
+\path[draw=drawColor,line width= 0.5pt,line join=round] (377.53, 55.31) --
+	(377.53, 57.56);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (416.50, 55.31) --
+	(416.50, 57.56);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (455.47, 55.31) --
+	(455.47, 57.56);
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (382.03, 48.55) {$2^{5}$};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (419.50, 48.55) {$2^{12}$};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (456.96, 48.55) {$2^{19}$};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (377.53, 48.55) {$2^{5}$};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (416.50, 48.55) {$2^{12}$};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (455.47, 48.55) {$2^{19}$};
 

### 2024-08-09 analysis/analyse.R

@@ -3,9 +3,9 @@ library(scales)
 library(tikzDevice)
 library(ggpubr)
 
-df <- read.csv("../results/processed/results_with_counts.csv")
-df$count <- NULL
-write.csv(df, "../results/processed/results.csv")
+# df <- read.csv("../results/processed/results_with_counts.csv")
+# df$count <- NULL
+# write.csv(df, "../results/processed/results.csv")
 
 df <- read.csv("../results/processed/results.csv")
 df$compilation.time <- df$compilation.time / 1000
@@ -18,6 +18,7 @@ df$algorithm[df$algorithm == "forclift"] <- "\\textsc{ForcLift}"
 df$sequence[df$sequence == "bijections"] <- "Bijections"
 df$sequence[df$sequence == "friends"] <- "Friends"
 df$sequence[df$sequence == "functions"] <- "Functions"
+df <- df[df$domain.size > 1,]
 
 # Sanity check: differences between max and min counts as a percentage of the
 # min count

### 2024-08-09 doc/paper/paper.tex
Some minor changes

@@
 
-% TODO: consider restructuring the paper (how?)
-
 \section{Introduction}
@@
 
-% TODO: Use FastWFOMC.jl instead, removing the mention of 'privately-obtained'
-
 \renewcommand*{\thefootnote}{\fnsymbol{footnote}}
@@
   methods~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22};
-  \item \UFO{} is the input format supported by a private version of
-  \textsc{FastWFOMC} obtained directly from the authors.
-\end{enumerate*}
-Note that the publicly available
-version\footnote{\url{https://comp.nus.edu.sg/~tvanbr/software/fastwfomc.tar.gz}}
-of \textsc{FastWFOMC} does not support any cardinality constraints. The notation
-we use to refer to each logic is standard in the case of \Ctwo{} and redefined
-to be more specific in the case of the other two logics. All three logics are
-function-free, and domains are always assumed to be finite. As usual, we
-presuppose the \emph{unique name assumption}, which states that two constants
-are equal if and only if they are the same constant~\cite{DBLP:books/aw/RN2020}.
+  \item \UFO{} is the input format supported by the most recent implementation
+  of
+  \textsc{FastWFOMC}\footnote{\url{https://github.com/jan-toth/FastWFOMC.jl}}.
+\end{enumerate*}
+The notation we use to refer to each logic is standard in the case of \Ctwo{}
+and \UFO{}~\cite{tóth2024complexityweightedfirstordermodel} and redefined to be
+more specific in the case of \FO{}. All three logics are function-free, and
+domains are always assumed to be finite. As usual, we presuppose the
+\emph{unique name assumption}, which states that two constants are equal if and
+only if they are the same constant~\cite{DBLP:books/aw/RN2020}.
 
@@
 
+Before describing the main contribution of this work, let us review the key
+aspects of FOKC as realised by \textsc{Crane}. The input formula is compiled
+into:
+\begin{enumerate*}[label=(\roman*)]
+  \item set $\mathcal{E}$ of equations,
+  \item map $\mathcal{F}$ from function names to formulas, and
+  \item map $\mathcal{D}$ from function names and argument indices to domains.
+\end{enumerate*}
+$\mathcal{E}$ can contain any number of functions, one of which (denoted by $f$)
+represents the solution to the FOMC problem. To compute the FOMC of the formula
+for particular domain sizes, $f$ must be evaluated with those domain sizes as
+arguments. $\mathcal{D}$ records this correspondence between function arguments
+and domains.
+
 \begin{algorithm}[t]
@@
 the FOKC algorithm of the original \textsc{Crane} to compile the formula into
-three components:
-\begin{enumerate*}[label=(\roman*)]
-  \item set $\mathcal{E}$ of equations,
-  \item map $\mathcal{F}$ from function names to formulas, and
-  \item map $\mathcal{D}$ from function names and argument indices to domains.
-\end{enumerate*}
-After some algebraic simplification (explained at the end of this section),
+the three components: $\mathcal{E}$, $\mathcal{F}$, and $\mathcal{D}$. After
+some algebraic simplification (explained at the end of this section),
 $\mathcal{E}$ is passed to the \FindBaseCases procedure (explained in
 \cref{sec:identifying}), which identifies the base cases that need to be
-defined.
-
-For each base case $f(\mathbf{x})$, we retrieve the logical formula
+defined. For each base case $f(\mathbf{x})$, we retrieve the logical formula
 $\mathcal{F}(f)$ associated with the function name $f$ and simplify it using the
@@
 
-% TODO: F missing
-
-% TODO: E is not explained other than that we take the example from X
-
-% TODO: include a high-level overview of first-order knowledge compilation and the meaning of the resulting functions.
-For the most part, the compilation process that constructs these function definitions can be treated as a black box for the purposes of this work.
-However, a few high-level details still ought to be mentioned:
-% 1. Each algebraic variable ("m", "n", and "l" in the example) corresponds to a domain size.
-% 2. \mathcal{D} indicates that "m" denotes the size of \Gamma, "n" denotes the size of \Delta, etc.
-% 3. \mathcal{E} can contain any (positive) number of functions.
-% 4. Function denoted by "f" represents the solution to the model counting problem.
-% 3. The model count of the original formula is computed by evaluating f on the desired domain sizes. For example, f(3, 2) is the model count when |\Gamma| = 3, and |\Delta| = 2.
 \begin{example}[Counting bijections]\label{example:overall}
@@
   \end{align*}
-  where $\Delta^{\top}$ is a new domain introduced by \Compile. Then
+  where $\Delta^{\top}$ is a new domain introduced by \Compile. (We omit the
+  definition of $\mathcal{F}$ as the formulas can get a bit verbose.) Then
   \FindBaseCases identifies two base cases: $g(0, m)$ and $g(l, 0)$. In both
@@
 
-% TODO: The asymptotic analysis of the total number of arithmetic operations
-% required to compute the FOMC of some of these formulas was already performed
-% in previous work~\cite{DBLP:conf/kr/DilkasB23}.
-
 \begin{algorithm}[t]
@@
 
+In the rest of this section, we show that the base cases identified by
+\FindBaseCases are sufficient for the algorithm to terminate. Note that
+characterising the fine-grained complexity of the solutions found by \Cranetwo{}
+or other FOMC algorithms is an emerging area of research partially addressed by
+\citeauthor{DBLP:conf/kr/DilkasB23}~\shortcite{DBLP:conf/kr/DilkasB23} and
+\citeauthor{tóth2024complexityweightedfirstordermodel}~\shortcite{tóth2024complexityweightedfirstordermodel}.
 For the rest of this section, let $\mathcal{E}$ represent the equations returned
@@
 \FindBaseCases are sufficient, we begin with a few observations that stem from
-the details of previous
-work~\cite{DBLP:conf/ijcai/BroeckTMDR11,DBLP:conf/kr/DilkasB23} and this work.
+previous~\cite{DBLP:conf/ijcai/BroeckTMDR11,DBLP:conf/kr/DilkasB23} and this
+work.
 

### 2024-08-11 doc/paper/paper.tex
The text is all there. Now I just need to shorten it and do some editing.

@@
 
-% TODO: Having an algorithm that can efficiently handle large domain sizes is
-% crucial in the weighted setting. For example, consider the well-known "friends
-% and smokers" Markov logic network [1]. The utility of such a model would be
-% significantly limited if exact probabilities could only be efficiently
-% computed for social networks of at most 30 people.
-% [1] Richardson, M., & Domingos, P. (2006). Markov logic networks. Machine learning, 62, 107-136.
-
-% TODO: (somewhere) The implementation is only for unweighted (but the
-% definition of WFOMC is still necessary because of Skolemization).
-
 \section{Introduction}
-% TODO: make it extra clear what the gap is that this work is trying to fill
-
-% TODO: mention Crane earlier and describe its importance
-
-% TODO: the last two paragraphs should make more of a BOOM (e.g., include the
-% over 9k claim)
-
-% TODO (here and elsewhere): clarify the distinction between the weighted and
-% unweighted variants of the problem in the final version of the paper. We focus
-% on the unweighted variant in our implementation and experiments, however,
-% Crane2 can handle WFOMC instances as well simply by switching the main data
-% type from integers to rational numbers. Maybe add some weighted experiments as
-% well.
-
-% TODO: (must) more related work, situating my contributions in the broader
-% context
-
-% TODO: (concerning related work) the topic is intimately related to "graded
-% logics", largely investigated in DL, mu-calculus and temporal logics
 
@@
 
-\emph{First-order model counting} is the task of counting the number of models
-of a sentence in first-order logic over some given domain(s). The (symmetric)
-weighted variant of this problem, known as WFOMC, seeks to calculate the sum of
-model weights. In WFOMC, the weight of a model is determined by predicate
-weights~\cite{DBLP:conf/ijcai/BroeckTMDR11}. WFOMC is a key approach to
-\emph{lifted (probabilistic) inference}, which aims to compute probabilities
-more efficiently by leveraging symmetries inherent in the problem
-description~\cite{DBLP:conf/ecai/Kersting12}.
+\emph{First-order model counting} (FOMC) is the task of counting the number of
+models of a sentence in first-order logic over some given domain(s). The
+(symmetric) weighted variant of this problem, known as WFOMC, seeks to compute
+the total weight of the models~\cite{DBLP:conf/ijcai/BroeckTMDR11}. WFOMC
+relates to its propositional predecessor weighted model
+counting~\cite{DBLP:journals/ai/ChaviraD08} and, more conceptually, to other
+attempts to unify logic and probability such as probabilistic
+logic~\cite{DBLP:journals/ai/Nilsson86}, fuzzy
+logic~\cite{novak2012mathematical}, and graded logics~\cite{vsaletic2024graded}.
+Moreover, WFOMC is a key approach to \emph{lifted (probabilistic) inference},
+which aims to compute probabilities more efficiently by leveraging symmetries
+inherent in the problem description~\cite{DBLP:conf/ecai/Kersting12}.
 
@@
 programs~\cite{DBLP:journals/ijar/RiguzziBZCL17}. By considering domains of
-increasing sizes, the model count of a formula can be seen as an integer
-sequence. WFOMC algorithms have been utilised for discovering new
+increasing sizes, the FOMC of a formula can be seen as an integer sequence. FOMC
+algorithms have been utilised for discovering new
 sequences~\cite{DBLP:conf/ijcai/SvatosJT0K23} as well as
@@
 constructing~\cite{DBLP:conf/kr/DilkasB23} recurrence relations and other
-recursive structures that describe these sequences. Additionally, WFOMC
+recursive structures that describe these sequences. Additionally, FOMC
 algorithms have been extended to perform
@@
 
-The complexity of WFOMC is typically characterised in terms of \emph{data
+The complexity of FOMC is typically characterised in terms of \emph{data
   complexity}. This involves fixing the formula and determining whether an
-algorithm exists that can compute the WFOMC in time polynomial with respect to
+algorithm exists that can compute the FOMC in time polynomial with respect to
 the domain size(s). If such an algorithm exists, the formula is called
@@
 
-There are various WFOMC algorithms with different underlying principles. Perhaps
-the most prominent class of WFOMC algorithms is based on \emph{first-order
+There are various FOMC algorithms with different underlying principles. Perhaps
+the most prominent class of FOMC algorithms is based on \emph{first-order
   knowledge compilation} (FOKC). In this approach, the formula is compiled into
@@
 \emph{compilation rules}. This representation can then be used to compute the
-WFOMC for any combination of domain sizes (or weights). Algorithms in this class
-include \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} and its recent
-extension \textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23}. The former compiles
-formulas into circuits, while the latter compiles them first to graphs and then
-to (algebraic) equations. Another WFOMC algorithm,
+FOMC for any combination of domain sizes. Algorithms in this class include
+\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} and its recent extension
+\textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23}. The former compiles formulas into
+circuits, while the latter compiles them first to graphs and then to (algebraic)
+equations. Another FOMC algorithm,
 \textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21}, is based on cell enumeration.
@@
 
-% TODO: introduce MLNs somewhere? maybe use an acronym?
-The recently proposed \textsc{Crane} algorithm, while capable of handling
-formulas beyond the reach of \textsc{ForcLift}, was `incomplete' as it could
-only construct function definitions, which would then need to be evaluated to
-compute the WFOMC.\@ In other words, it could not be used as a black box that
-takes Markov logic networks (or weighted formulas in some other format) and
-outputs numbers (i.e., model counts or probabilities). Additionally, recursive
-functions were presented without base cases. In this work, we introduce
-\Cranetwo{}, an extension of \textsc{Crane} that addresses these two weaknesses.
+The recently proposed \textsc{Crane} algorithm marked significant progress in
+handling formulas beyond the capabilities of \textsc{FastWFOMC} and
+\textsc{ForcLift}, yet it fell short in critical aspects. \textsc{Crane} was
+incomplete in that it could only construct function definitions, leaving users
+to manually evaluate these functions to obtain model counts. This limitation
+prevented \textsc{Crane} from serving as a convenient black box solution for
+FOMC. Furthermore, it introduced recursive functions without defining necessary
+base cases, adding further complexity to the user.
+
+In this work, we present \Cranetwo{}, the breakthrough that not only addresses
+these gaps but also pushes the boundaries of scalability to unprecedented
+levels. With \Cranetwo{}, we eliminate the manual steps, providing a fully
+automated FOMC algorithm. Moreover, \Cranetwo{} can scale to domain sizes over
+\num{500000} times larger than the previous state of the art, redefining what is
+possible in the field of first-order model counting.
 
@@
 from \cref{step2} above required to preserve the correct model count. Next,
-\cref{sec:cpp} elucidates how function definitions encoding a solution to a
-WFOMC problem are compiled into C++ programs. Note that a solution to WFOMC that
-uses compilation to C++ has been considered
-before~\cite{DBLP:conf/kr/KazemiP16}, however, the extent of formulas that could
-be handled was limited. Finally, \cref{sec:experiments} presents experiments
-results comparing \Cranetwo{} with other state-of-the-art WFOMC algorithms.
+\cref{sec:cpp} elucidates how function definitions encoding a solution to a FOMC
+problem are compiled into C++ programs. Note that a solution to FOMC that uses
+compilation to C++ has been considered before~\cite{DBLP:conf/kr/KazemiP16},
+however, the extent of formulas that could be handled was limited. Finally,
+\cref{sec:experiments} presents experiments results comparing \Cranetwo{} with
+other state-of-the-art FOMC algorithms.
 
@@
 In \cref{sec:logic}, we provide a summary of the basic principles of first-order
-logic. Then, in \cref{sec:threelogics}, we formally define WFOMC and discuss the
-distinctions between three variations of first-order logic that are utilised for
-WFOMC.\@ Finally, in \cref{sec:algebra}, we introduce the terminology used to
-describe the output of the original \textsc{Crane} algorithm, i.e., functions
+logic. Then, in \cref{sec:threelogics}, we formally define (W)FOMC and discuss
+the distinctions between three variations of first-order logic that are utilised
+for FOMC.\@ Finally, in \cref{sec:algebra}, we introduce the terminology used
+to describe the output of the original \textsc{Crane} algorithm, i.e., functions
 and equations that define them.
@@
 
-\subsection{WFOMC Algorithms and Their Logics}\label{sec:threelogics}
+\subsection{FOMC Algorithms and Their Logics}\label{sec:threelogics}
 
@@
   \end{tabular}
-  \caption[]{A comparison of the three logics used in WFOMC based on the following aspects:
+  \caption[]{A comparison of the three logics used in FOMC based on the following aspects:
     \begin{enumerate*}[label=(\roman*)]
@@
 In \cref{tbl:logics}, we outline the differences among three first-order logics
-commonly used in WFOMC:
+commonly used in FOMC:
 \begin{enumerate*}[label=(\roman*)]
@@
 \end{remark}
+
+While the focus of this work is on FOMC, we still define the weighted variant of
+the problem as Skolemization relies on weights even for unweighted FOMC.
 
@@
 consistent since $0^{0} = 1$. Generally, let $\phi$ be a formula with two
-domains $\Gamma$ and $\Delta$, and let $n, m \in \mathbb{N}_{0}$. Then the WFOMC
+domains $\Gamma$ and $\Delta$, and let $n, m \in \mathbb{N}_{0}$. Then the FOMC
 of \Propagate{$\phi$, $\Delta$, $n$} assuming $|\Gamma| = m$ is the same as the
-WFOMC of \Propagate{$\phi$, $\Gamma$, $m$} assuming $|\Delta| = n$.
+FOMC of \Propagate{$\phi$, $\Gamma$, $m$} assuming $|\Delta| = n$.
 
@@
 \end{algorithm}
-% TODO (later, let's not bother yet): replace x_i-c_i on Line 7 of Algorithm 2
-% with a generalisation of x_i that can be an arbitrary summation/subtraction of
-% domain sizes (propagating this change to the rest of the paper, particularly
+% (later, let's not bother yet): replace x_i-c_i on Line 7 of Algorithm 2 with a
+% generalisation of x_i that can be an arbitrary summation/subtraction of domain
+% sizes (propagating this change to the rest of the paper, particularly
 % Assumption 1, the proof of Lemma 1)
@@
   \cref{eq:example1} is vacuously satisfied by all structures. Therefore, the
-  correct WFOMC should be $2^{|\Gamma|^2 - |\Gamma'|^2}$.
+  correct FOMC should be $2^{|\Gamma|^2 - |\Gamma'|^2}$.
 
@@
 by \citeauthor{DBLP:conf/kr/DilkasB23}~\shortcite{DBLP:conf/kr/DilkasB23}. The
-second is a variant of the well-known `Friends \& Smokers' Markov logic
+second is a variant of the well-known `Friends and Smokers' Markov logic
 network~\cite{DBLP:conf/aaai/SinglaD08,DBLP:conf/uai/BroeckCD12}. In \Ctwo{},
@@
 
-% TODO: run this section through editgpt and grammarly
-
 \section{Conclusion and Future Work}
@@
 larger domain sizes than \textsc{FastWFOMC} while handling more formulas than
-\textsc{ForcLift}.
+\textsc{ForcLift}. Having FOMC algorithms that can efficiently handle large
+domain sizes is especially crucial in the weighted setting. For example,
+consider the `friends' instance examined in \cref{sec:experiments}, which models
+a social network with friendships, smoking habits, and the probability of having
+cancer. The utility of such a model would be significantly limited if
+probabilities could only be efficiently computed for networks of at most
+\num{1000} people.
 
 There are many potential avenues for future work. Specifically, a more thorough
-experimental study is needed to understand how WFOMC algorithms compare in terms
+experimental study is needed to understand how FOMC algorithms compare in terms
 of their ability to handle different formulas and their scalability with respect
@@
 for a fragment of first-order logic such as \Ctwo{} (using a suitable encoding
-of counting quantifiers). Moreover, the efficiency of a WFOMC algorithm in
+of counting quantifiers). Moreover, the efficiency of a FOMC algorithm in
 handling a particular formula can be assessed using \emph{fine-grained

### 2024-08-11 doc/paper/paper.tex
Made it fit

@@
 \crefname{line}{line}{lines}
-\crefname{fact}{Observation}{Observations}
+%\crefname{fact}{Observation}{Observations}
 \crefname{assumption}{Assumption}{Assumptions}
@@
 models of a sentence in first-order logic over some given domain(s). The
-(symmetric) weighted variant of this problem, known as WFOMC, seeks to compute
-the total weight of the models~\cite{DBLP:conf/ijcai/BroeckTMDR11}. WFOMC
-relates to its propositional predecessor weighted model
-counting~\cite{DBLP:journals/ai/ChaviraD08} and, more conceptually, to other
-attempts to unify logic and probability such as probabilistic
-logic~\cite{DBLP:journals/ai/Nilsson86}, fuzzy
-logic~\cite{novak2012mathematical}, and graded logics~\cite{vsaletic2024graded}.
-Moreover, WFOMC is a key approach to \emph{lifted (probabilistic) inference},
-which aims to compute probabilities more efficiently by leveraging symmetries
-inherent in the problem description~\cite{DBLP:conf/ecai/Kersting12}.
+weighted variant of this problem, known as WFOMC, seeks to compute the total
+weight of the models~\cite{DBLP:conf/ijcai/BroeckTMDR11}. WFOMC is related to
+its propositional predecessor weighted model
+counting~\cite{DBLP:journals/ai/ChaviraD08} and other attempts to unify logic
+and
+probability~\cite{DBLP:journals/ai/Nilsson86,novak2012mathematical,vsaletic2024graded}.
+It is also a key approach to \emph{lifted inference}, which aims to compute
+probabilities more efficiently by leveraging symmetries in the
+problem~\cite{DBLP:conf/ecai/Kersting12}.
 
@@
 databases~\cite{DBLP:journals/debu/GribkoffSB14} and probabilistic logic
-programs~\cite{DBLP:journals/ijar/RiguzziBZCL17}. By considering domains of
-increasing sizes, the FOMC of a formula can be seen as an integer sequence. FOMC
-algorithms have been utilised for discovering new
-sequences~\cite{DBLP:conf/ijcai/SvatosJT0K23} as well as
+programs~\cite{DBLP:journals/ijar/RiguzziBZCL17}. FOMC algorithms have been
+utilised for discovering new integer
+sequences~\cite{DBLP:conf/ijcai/SvatosJT0K23}, and for
 conjecturing~\cite{DBLP:conf/ilp/BarvinekB0ZK21} and
 constructing~\cite{DBLP:conf/kr/DilkasB23} recurrence relations and other
-recursive structures that describe these sequences. Additionally, FOMC
-algorithms have been extended to perform
+recursive structures that describe these sequences. FOMC algorithms have also
+been extended to perform
 \emph{sampling}~\cite{DBLP:conf/aaai/WangB0K22,DBLP:conf/lics/WangP0K23}.
 
+% By considering domains of increasing sizes, the FOMC of a formula can be seen
+% as an integer sequence.
+
 % 3. Why is it hard? (E.g., why do naive approaches fail?)
@@
 The complexity of FOMC is typically characterised in terms of \emph{data
-  complexity}. This involves fixing the formula and determining whether an
-algorithm exists that can compute the FOMC in time polynomial with respect to
-the domain size(s). If such an algorithm exists, the formula is called
+  complexity}. If there is an algorithm that can compute the FOMC of a formula
+in polynomial time with respect to the domain size(s), that formula is called
 \emph{liftable}~\cite{DBLP:conf/starai/JaegerB12}.
@@
 demonstrated the existence of an unliftable formula with three variables. It is
-also known that all formulas with up to two variables are
+also known that formulas with up to two variables are
 liftable~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/kr/BroeckMD14}. The liftable
@@
 
+% This involves fixing the formula and determining whether an
+% algorithm exists that can compute the FOMC in time polynomial with respect to
+% the domain size(s).
+
 % 4. Why hasn't it been solved before? (Or, what's wrong with previous proposed
@@
 
-There are various FOMC algorithms with different underlying principles. Perhaps
-the most prominent class of FOMC algorithms is based on \emph{first-order
-  knowledge compilation} (FOKC). In this approach, the formula is compiled into
-a representation (such as a circuit or graph) by iteratively applying
-\emph{compilation rules}. This representation can then be used to compute the
-FOMC for any combination of domain sizes. Algorithms in this class include
-\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} and its recent extension
-\textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23}. The former compiles formulas into
-circuits, while the latter compiles them first to graphs and then to (algebraic)
-equations. Another FOMC algorithm,
+There are many FOMC algorithms with different underlying principles. Perhaps the
+most prominent class of FOMC algorithms is based on \emph{first-order knowledge
+  compilation} (FOKC). In this approach, the formula is compiled into a
+representation (such as a circuit or graph) by applying \emph{compilation
+  rules}. Algorithms in this class include
+\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} and its extension
+\textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23}. Another FOMC algorithm,
 \textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21}, is based on cell enumeration.
@@
 
+% This representation can then be used to compute the FOMC for any combination
+% of domain sizes.
+
+% The former compiles formulas into circuits, while the latter compiles them
+% first to graphs and then to (algebraic) equations.
+
 % 5. What are the key components of my approach and results? Also include any
@@
 \textsc{ForcLift}, yet it fell short in critical aspects. \textsc{Crane} was
-incomplete in that it could only construct function definitions, leaving users
+incomplete since it could only construct function definitions, requiring users
 to manually evaluate these functions to obtain model counts. This limitation
@@
 FOMC. Furthermore, it introduced recursive functions without defining necessary
-base cases, adding further complexity to the user.
-
-In this work, we present \Cranetwo{}, the breakthrough that not only addresses
-these gaps but also pushes the boundaries of scalability to unprecedented
-levels. With \Cranetwo{}, we eliminate the manual steps, providing a fully
-automated FOMC algorithm. Moreover, \Cranetwo{} can scale to domain sizes over
-\num{500000} times larger than the previous state of the art, redefining what is
-possible in the field of first-order model counting.
+base cases, adding further complexity to the users. In this work, we present
+\Cranetwo{}, addressing these gaps and pushing scalability to unprecedented
+levels. Unlike its predecessor, \Cranetwo{} is a fully automated FOMC algorithm,
+capable of handling domain sizes over \num{500000} times larger than previous
+algorithms.
 
@@
 \Cref{fig:overview} outlines the workflow of the new algorithm. In
-\cref{sec:main}, we describe how \CompileWithBaseCases finds the base cases for
-recursive functions by:
-\begin{enumerate*}[label=(\roman*)]
-  \item identifying a sufficient set of base cases for each function,
-  \item constructing formulas corresponding to these base cases,
-  and\label[step]{step2}
-  \item recursing on these new formulas.
-\end{enumerate*}
-Then, \cref{sec:smoothing} explains post-processing techniques for the formulas
-from \cref{step2} above required to preserve the correct model count. Next,
-\cref{sec:cpp} elucidates how function definitions encoding a solution to a FOMC
-problem are compiled into C++ programs. Note that a solution to FOMC that uses
-compilation to C++ has been considered before~\cite{DBLP:conf/kr/KazemiP16},
-however, the extent of formulas that could be handled was limited. Finally,
-\cref{sec:experiments} presents experiments results comparing \Cranetwo{} with
-other state-of-the-art FOMC algorithms.
+\cref{sec:main}, we describe how \CompileWithBaseCases finds base cases for
+recursive functions. \Cref{sec:smoothing} explains post-processing techniques to
+preserve the correct model count. \Cref{sec:cpp} elucidates how function
+definitions are compiled into C++ programs. Note that a solution to FOMC that
+uses compilation to C++ has been considered
+before~\cite{DBLP:conf/kr/KazemiP16}, however, the extent of formulas that could
+be handled was limited. Finally, \cref{sec:experiments} presents experimental
+results comparing \Cranetwo{} with other FOMC algorithms.
+
+% by:
+% \begin{enumerate*}[label=(\roman*)]
+%   \item identifying a sufficient set of base cases for each function,
+%   \item constructing formulas corresponding to these base cases,
+%   and\label[step]{step2}
+%   \item recursing on these new formulas.
+% \end{enumerate*}
 
@@
 
-In \cref{sec:logic}, we provide a summary of the basic principles of first-order
-logic. Then, in \cref{sec:threelogics}, we formally define (W)FOMC and discuss
-the distinctions between three variations of first-order logic that are utilised
-for FOMC.\@ Finally, in \cref{sec:algebra}, we introduce the terminology used
-to describe the output of the original \textsc{Crane} algorithm, i.e., functions
-and equations that define them.
+In \cref{sec:logic}, we summarise the basic principles of first-order logic.
+Then, in \cref{sec:threelogics}, we formally define (W)FOMC and discuss the
+distinctions between three variations of first-order logic used for FOMC.\@
+Finally, in \cref{sec:algebra}, we introduce the terminology used to describe
+the output of the original \textsc{Crane} algorithm, i.e., functions and
+equations that define them.
 
@@
 
-In this section, we review the basic concepts of first-order logic as they are
-used in FOKC algorithms. There are two key differences between the logic used by
-such algorithms and the logic supported as input. First,
-Skolemization~\cite{DBLP:conf/kr/BroeckMD14} is employed to eliminate
-existential quantifiers by introducing additional predicates. Note that
-Skolemization here is different from the standard Skolemization procedure that
-introduces function symbols~\cite{DBLP:books/daglib/0030198}. Second, the input
-formula is rewritten as a conjunction of clauses, each of which is in
-\emph{prenex normal form}~\cite{hinman2018fundamentals}.
-
-A \emph{term} is either a variable or a constant. An \emph{atom} is either
+In this section, we will review the basic concepts of first-order logic as they
+are used in FOKC algorithms. There are two key differences between the logic
+used by these algorithms and the logic supported as input. First,
+Skolemization~\cite{DBLP:conf/kr/BroeckMD14} eliminates existential quantifiers
+by introducing additional predicates. Please note that Skolemization here
+differs from the standard Skolemization procedure that introduces function
+symbols~\cite{DBLP:books/daglib/0030198}. Second, the input formula is rewritten
+as a conjunction of clauses, each in \emph{prenex normal
+  form}~\cite{hinman2018fundamentals}.
+
+A \emph{term} can be either a variable or a constant. An \emph{atom} can be
+either
 \begin{enumerate*}[label=(\roman*)]
@@
 The \emph{arity} of a predicate is the number of arguments it takes, i.e., $m$
-in the case of predicate $P$ above. We write $P/m$ to denote a predicate
-together with its arity. A \emph{literal} is either an atom (i.e., a
+in the case of the predicate $P$ mentioned above. We write $P/m$ to denote a
+predicate along with its arity. A \emph{literal} can be either an atom (i.e., a
 \emph{positive} literal) or its negation (i.e., a \emph{negative} literal). An
 atom is \emph{ground} if it contains no variables, i.e., only constants. A
-\emph{clause} is of the form
-$\forall x_{1} \in \Delta_{1}\text{.}\forall x_{2} \in \Delta_{2}\dots\text{}\forall x_{n} \in \Delta_{n}\text{.}\phi(x_{1}, x_{2}, \dots, x_{n})$,
-where $\phi$ is a disjunction of literals that only contain variables
-$x_{1}, \dots, x_{n}$ (and any constants). We say that a clause is a
-\emph{(positive) unit clause} if
+\emph{clause} is of the form $\forall x_{1} \in \Delta_{1}\text{.
+}\forall x_{2} \in \Delta_{2}\dots\text{ }\forall x_{n} \in \Delta_{n}\text{.
+}\phi(x_{1}, x_{2}, \dots, x_{n})$, where $\phi$ is a disjunction of literals
+that only contain variables $x_{1}, \dots, x_{n}$ (and any constants). We say
+that a clause is a \emph{(positive) unit clause} if
 \begin{enumerate*}[label=(\roman*)]
@@
 Finally, a \emph{formula} is a conjunction of clauses. Throughout the paper, we
-use set-theoretic notation, interpreting a formula as a set of clauses and a
-clause as a set of literals.
+will use set-theoretic notation, interpreting a formula as a set of clauses and
+a clause as a set of literals.
 
@@
       \item supported quantifiers, and
-      \item supported atoms in addition to those of the form $P(\mathbf{t})$ for a predicate $P/n$ and $n$-tuple of terms $\mathbf{t}$.
+      \item supported atoms in addition to those of the form $P(\mathbf{t})$ for a predicate $P/n$ and an $n$-tuple of terms $\mathbf{t}$.
     \end{enumerate*}
@@
 
-Compared to \FO{}, \Ctwo{} and \UFO{} lack support for:
+Compared to \FO{}, \Ctwo{} and \UFO{} lack support for
 \begin{enumerate*}[label=(\roman*)]
@@
   Let $\phi$ be a formula in \FO{}. For each predicate $P/n$ in $\phi$, let
-  ${(\Delta_{i}^{P})}_{i=1}^{n}$ be a list of the corresponding domains (which
-  may not be distinct). Let $\sigma$ be a map from the domains of $\phi$ to
-  their interpretations as sets, satisfying the following conditions:
+  ${(\Delta_{i}^{P})}_{i=1}^{n}$ be a list of the corresponding domains. Let
+  $\sigma$ be a map from the domains of $\phi$ to their interpretations as sets,
+  satisfying the following conditions:
   \begin{enumerate*}[label=(\roman*)]
@@
   \end{enumerate*}
-  (In practice, we typically only specify the size of each domain.) A
-  \emph{structure} of $\phi$ (with respect to $\sigma$) is a set $M$ of ground
-  literals defined by adding to $M$ either $P(\mathbf{t})$ or
-  $\neg P(\mathbf{t})$ for every predicate $P/n$ in $\phi$ and $n$-tuple
+  A \emph{structure} of $\phi$ is a set $M$ of ground literals defined by adding
+  to $M$ either $P(\mathbf{t})$ or $\neg P(\mathbf{t})$ for every predicate
+  $P/n$ in $\phi$ and $n$-tuple
   $\mathbf{t} \in \prod_{i=1}^{n} \sigma(\Delta_{i}^{P})$. A structure is a
@@
 
+% (In practice, we typically only specify the size of each domain.)
+
 \begin{remark}
   The distinctness of domains is important in two ways. First, in terms of
-  expressiveness, clauses such as $\forall x \in \Delta\text{. }P(x, x)$ are
+  expressiveness, a clause such as $\forall x \in \Delta\text{. }P(x, x)$ is
   valid if predicate $P$ is defined over two copies of the same domain and
   invalid otherwise. Second, having more distinct domains makes the problem more
-  decomposable for the FOKC algorithm. With more distinct domains, the algorithm
-  can make assumptions or deductions about, e.g., the first domain of predicate
-  $P$ without worrying how (or if) they apply to the second domain.
+  decomposable for the FOKC algorithm. With distinct domains, the algorithm can
+  make assumptions or deductions about, e.g., the first domain of predicate $P$
+  without worrying how (or if) they apply to the second domain.
 \end{remark}
 
-While the focus of this work is on FOMC, we still define the weighted variant of
-the problem as Skolemization relies on weights even for unweighted FOMC.
-
-\begin{definition}[WFOMC Instance]\label{def:instance}
-  A \emph{WFOMC instance} comprises of:
+While this work focuses on FOMC, we still define the weighted variant of the
+problem as Skolemization relies on weights even for unweighted FOMC.
+
+\begin{definition}[WFOMC instance]\label{def:instance}
+  A \emph{WFOMC instance} comprises:
   \begin{enumerate*}[label=(\roman*)]
@@
   \cref{def:instance}, the \emph{(symmetric) weighted first-order model count}
-  (WFOMC) of $\phi$ (with respect to $\sigma$, $w^{+}$, and $w^{-}$) is
+  (WFOMC) of $\phi$ is
   \begin{equation}\label{eq:wfomc}
@@
 We write $\expr{}$ to represent an arbitrary algebraic expression. It is
-important to note that some terms have different meanings in algebra compared to
+important to note that some terms have different meanings in algebra and
 logic. In algebra, a \emph{constant} refers to a non-negative integer. Likewise,
@@
 
-Before describing the main contribution of this work, let us review the key
-aspects of FOKC as realised by \textsc{Crane}. The input formula is compiled
-into:
+Before describing the main contribution of this work, let us review the
+essential aspects of FOKC as realised by \textsc{Crane}. The input formula is
+compiled into:
 \begin{enumerate*}[label=(\roman*)]
@@
 $\mathcal{E}$ can contain any number of functions, one of which (denoted by $f$)
-represents the solution to the FOMC problem. To compute the FOMC of the formula
-for particular domain sizes, $f$ must be evaluated with those domain sizes as
-arguments. $\mathcal{D}$ records this correspondence between function arguments
-and domains.
+represents the solution to the FOMC problem. To compute the FOMC for particular
+domain sizes, $f$ must be evaluated with those domain sizes as arguments.
+$\mathcal{D}$ records this correspondence between function arguments and
+domains.
 
@@
 the three components: $\mathcal{E}$, $\mathcal{F}$, and $\mathcal{D}$. After
-some algebraic simplification (explained at the end of this section),
-$\mathcal{E}$ is passed to the \FindBaseCases procedure (explained in
-\cref{sec:identifying}), which identifies the base cases that need to be
-defined. For each base case $f(\mathbf{x})$, we retrieve the logical formula
-$\mathcal{F}(f)$ associated with the function name $f$ and simplify it using the
-\Propagate procedure (explained in detail in \cref{sec:simplifying}). We do this
-by iterating over all indices of $\mathbf{x}$, where $x_{i}$ is a constant, and
-using \Propagate to simplify $\psi$ by assuming that domain $\mathcal{D}(f, i)$
-has size $x_{i}$. Finally, on \cref{line:final}, \CompileWithBaseCases recurses
-on these simplified formulas and adds the resulting base case equations to
-$\mathcal{E}$. \Cref{example:overall} below provides more detail.
+some algebraic simplification, $\mathcal{E}$ is passed to the \FindBaseCases
+procedure (see \cref{sec:identifying}). For each base case $f(\mathbf{x})$, we
+retrieve the logical formula $\mathcal{F}(f)$ associated with the function name
+$f$ and simplify it using the \Propagate procedure (explained in detail in
+\cref{sec:simplifying}). We do this by iterating over all indices of
+$\mathbf{x}$, where $x_{i}$ is a constant, and using \Propagate to simplify
+$\psi$ by assuming that domain $\mathcal{D}(f, i)$ has size $x_{i}$. Finally, on
+\cref{line:final}, \CompileWithBaseCases recurses on these simplified formulas
+and adds the resulting base case equations to $\mathcal{E}$.
+\Cref{example:overall} below provides more detail.
 
@@
   \end{align*}
-  where $\Delta^{\top}$ is a new domain introduced by \Compile. (We omit the
-  definition of $\mathcal{F}$ as the formulas can get a bit verbose.) Then
-  \FindBaseCases identifies two base cases: $g(0, m)$ and $g(l, 0)$. In both
-  cases, \CompileWithBaseCases recurses on the formula $\mathcal{F}(g)$
-  simplified by assuming that one of the domains is empty. In the first case, we
-  recurse on the formula $\forall x \in \Gamma\text{. }S(x) \lor \neg S(x)$,
-  where $S$ is a predicate introduced by Skolemization with weights
-  $w^{+}(S) = 1$ and $w^{-}(S) = -1$. Hence, we obtain the base case
-  $g(0, m) = 0^{m}$. In the case of $g(l, 0)$, \Propagate{$\psi$, $\Gamma$, $0$}
-  returns an empty formula, resulting in $g(l, 0) = 1$.
+  where $\Delta^{\top}$ is a new domain. (We omit the definition of
+  $\mathcal{F}$ as the formulas can get a bit verbose.) Then \FindBaseCases
+  identifies two base cases: $g(0, m)$ and $g(l, 0)$. In both cases,
+  \CompileWithBaseCases recurses on the formula $\mathcal{F}(g)$ simplified by
+  assuming that one of the domains is empty. In the first case, we recurse on
+  the formula $\forall x \in \Gamma\text{. }S(x) \lor \neg S(x)$, where $S$ is a
+  predicate introduced by Skolemization with weights $w^{+}(S) = 1$ and
+  $w^{-}(S) = -1$. Hence, we obtain the base case $g(0, m) = 0^{m}$. In the case
+  of $g(l, 0)$, \Propagate{$\psi$, $\Gamma$, $0$} returns an empty formula,
+  resulting in $g(l, 0) = 1$.
 \end{example}
@@
 
-Finally, we main responsibility of the \Simplify procedure is in handling the
+Finally, the main responsibility of the \Simplify procedure is to handle the
 algebraic pattern $\sum_{m=0}^{n}[a \le m \le b] f(m)$. Here:
@@
 
-\Cref{alg:findbasecases} summarises the implementation of the \FindBaseCases
-function. When a function $f$ calls itself recursively, \FindBaseCases considers
-two types of arguments:
+\Cref{alg:findbasecases} summarises the implementation of \FindBaseCases.
+\FindBaseCases considers two types of arguments when a function $f$ calls itself
+recursively:
 \begin{enumerate*}[label=(\roman*)]
@@
 \end{enumerate*}
-If the argument is a constant $c_{i}$, a base case with $c_{i}$ is added. In the
-second case, a base case is added for each constant from zero up to (but not
-including) $c_{i}$. The following discussion explains the reasoning behind this
-approach.
+When the argument is a constant $c_{i}$, a base case with $c_{i}$ is added. In
+the second case, a base case is added for each constant from $0$ up to (but not
+including) $c_{i}$.
 
 \begin{example}
-  Consider the recursive function $g$ from \cref{example:overall}. Then
+  Consider the recursive function $g$ from \cref{example:overall}.
   \FindBaseCases iterates over two function calls: $g(l-1, m)$ and
@@
 
-In the rest of this section, we show that the base cases identified by
-\FindBaseCases are sufficient for the algorithm to terminate. Note that
-characterising the fine-grained complexity of the solutions found by \Cranetwo{}
-or other FOMC algorithms is an emerging area of research partially addressed by
-\citeauthor{DBLP:conf/kr/DilkasB23}~\shortcite{DBLP:conf/kr/DilkasB23} and
-\citeauthor{tóth2024complexityweightedfirstordermodel}~\shortcite{tóth2024complexityweightedfirstordermodel}.
-For the rest of this section, let $\mathcal{E}$ represent the equations returned
-by \CompileWithBaseCases. To demonstrate that the base cases identified by
-\FindBaseCases are sufficient, we begin with a few observations that stem from
-previous~\cite{DBLP:conf/ijcai/BroeckTMDR11,DBLP:conf/kr/DilkasB23} and this
-work.
-
-\begin{fact}\label{assumption1}
-  For each function $f$, there is precisely one equation $e \in \mathcal{E}$
-  with $f(\mathbf{x})$ on the left-hand side where all $x_{i}$'s are variables
-  (i.e., $e$ is not a base case). We refer to $e$ as the \emph{definition} of
-  $f$.
-\end{fact}
-
-\begin{fact}\label{assumption2}
-  There is a \emph{topological ordering} of all functions ${(f_{i})}_{i}$ in
-  $\mathcal{E}$ such that equations in $\mathcal{E}$ with $f_{i}$ on the
-  left-hand side do not contain function calls to $f_{j}$ with $j > i$. This
-  condition prevents mutual recursion and other cyclic scenarios.
-\end{fact}
-
-\begin{fact}\label{assumption3}
-  For every equation $(f(\mathbf{x}) = \expr) \in \mathcal{E}$, the evaluation
-  of $\expr$ terminates when provided with the values of all relevant function
-  calls.
-\end{fact}
-
-\begin{corollary}\label{fact}
-  If $f$ is a non-recursive function with no function calls on the right-hand
-  side of its definition, then the evaluation of any function call
-  $f(\mathbf{x})$ terminates.
-\end{corollary}
-
-\begin{fact}\label{fact2}
-  For any equation $f(\mathbf{x}) = \expr{}$, if $\mathbf{x}$ contains only
-  constants, then $\expr{}$ cannot include any function calls to $f$.
-\end{fact}
-
-Additionally, we introduce an assumption about the structure of recursion.
-
-\begin{assumption}\label{assumption4}
-  For every equation $(f(\mathbf{x}) = \expr) \in \mathcal{E}$, every recursive
-  function call $f(\mathbf{y}) \in \expr$ satisfies the
-  following:
-  \begin{itemize}
-    \item Each $y_{i}$ is either $x_{i} - c_{i}$ or $c_{i}$ for some constant
-          $c_{i}$.
-    \item There exists $i$ such that $y_{i} = x_{i} - c_{i}$ for some
-          $c_{i} > 0$.
-  \end{itemize}
-\end{assumption}
-
-Finally, we assume a particular order of evaluation for function calls using the
-equations in $\mathcal{E}$. Specifically, we assume that base cases are
-considered before the recursive definition. The exact order in which base cases
-are considered is immaterial.
-
-\begin{assumption}
-  When multiple equations in $\mathcal{E}$ match a function call
-  $f(\mathbf{x})$, preference is given to an equation with the most constants on
-  its left-hand side.
-\end{assumption}
-
-With the observations and assumptions mentioned above, we prove the following
-theorem.
+It can be shown that the base cases identified by \FindBaseCases are sufficient
+for the algorithm to terminate.\footnote{Note that characterising the
+  fine-grained complexity of the solutions found by \Cranetwo{} or other FOMC
+  algorithms is an emerging area of research. These questions have been
+  partially addressed in previous
+  work~\cite{DBLP:conf/kr/DilkasB23,tóth2024complexityweightedfirstordermodel}
+  and are orthogonal to the goals of this section.}
 
 \begin{theorem}[Termination]\label{thm:halting}
+  Let $\mathcal{E}$ represent the equations returned by \CompileWithBaseCases.
   Let $f$ be an $n$-ary function in $\mathcal{E}$ and
@@
 
-We prove \cref{thm:halting} using double induction. First, we apply induction on
+We prove \cref{thm:halting} using double induction. First, we apply induction to
 the number of functions in $\mathcal{E}$. Then, we use induction on the arity of
-the `last' function in $\mathcal{E}$ according to some topological ordering (as
-defined in \cref{assumption2}). For readability, we divide the proof into
-several lemmas of increasing generality.
-
-\begin{lemma}\label{lemma:oneunary}
-  Assume that $\mathcal{E}$ consists of just \emph{one unary} function $f$. Then
-  the evaluation of a function call $f(x)$ terminates for any
-  $x \in \mathbb{N}_{0}$.
-\end{lemma}
-\begin{proof}
-  If $f(x)$ is captured by a base case, then its evaluation terminates by
-  \cref{fact,fact2}. If $f$ is not recursive, the evaluation of
-  $f(x)$ terminates by \cref{fact}.
-
-  Otherwise, let $f(y)$ be an arbitrary function call on the right-hand side of
-  the definition of $f(x)$. If $y$ is a constant, then there is a base case for
-  $f(y)$. Otherwise, let $y = x - c$ for some $c > 0$. Then there exists
-  $k \in \mathbb{N}_{0}$ such that $0 \le x - kc \le c-1$. So, after $k$
-  iterations, the sequence of function calls $f(x), f(x-c), f(x-2c),\dots$ will
-  be captured by the base case $f(x \mod c)$.
-\end{proof}
-
-\begin{lemma}\label{lemma:onefunction}
-  Generalising \cref{lemma:oneunary}, let $\mathcal{E}$ be a set of equations
-  for \emph{one} $n$-ary function $f$ for some $n \ge 1$. Then the evaluation of
-  $f(\mathbf{x})$ terminates for any $\mathbf{x} \in \mathbb{N}_{0}^{n}$.
-\end{lemma}
-\begin{proof}
-  If $f$ is non-recursive, the evaluation of $f(\mathbf{x})$ terminates by
-  previous arguments. We proceed by induction on $n$, with the base case of
-  $n=1$ handled by \cref{lemma:oneunary}. Assume that $n > 1$. Any base case of
-  $f$ can be seen as a function of arity $n-1$, since one of the parameters is
-  fixed. Thus, the evaluation of any base case terminates by the inductive
-  hypothesis. It remains to show that the evaluation of the recursive equation
-  for $f$ terminates, but that follows from \cref{assumption3}.
-\end{proof}
-
-\begin{proof}[Proof of \cref{thm:halting}]
-  We proceed by induction on the number of functions $n$. The base case of $n=1$
-  is handled by \cref{lemma:onefunction}. Let ${(f_{i})}_{i=1}^{n}$ be some
-  topological ordering of these $n > 1$ functions. If $f = f_{j}$ for $j < n$,
-  then the evaluation of $f(\mathbf{x})$ terminates by the inductive hypothesis
-  since $f_{j}$ cannot call $f_{n}$ by \cref{assumption2}. Using the inductive
-  hypothesis that all function calls to $f_{j}$ (with $j < n$) terminate, the
-  proof proceeds similarly to the Proof of \cref{lemma:onefunction}.
-\end{proof}
+the `last' function in $\mathcal{E}$ according to some topological ordering. For
+the detailed proof, please refer to the technical appendix.
 
@@
 
-\emph{Smoothing} is the process of modifying a circuit to re-introduce atoms
-that might have been eliminated, thus ensuring that the circuit preserves the
-correct (weighted) model
+\emph{Smoothing} modifies a circuit to reintroduce eliminated atoms, ensuring
+the correct model
 count~\cite{darwiche2001tractable,DBLP:conf/ijcai/BroeckTMDR11}. In this
-section, we motivate and describe a similar process performed on
+section, we describe a similar process performed on
 \cref{line:smoothing1,line:smoothing2} of \cref{alg:propagate}.
-\Cref{line:presmoothing} checks whether smoothing is necessary, and
+\Cref{line:presmoothing} checks if smoothing is necessary, and
 \cref{line:smoothing1,line:smoothing2} execute it. If the condition on
-\cref{line:presmoothing} is not satisfied, the clause is not smoothed but rather
-completely omitted.
-
-Suppose that \Propagate is called with arguments $(\phi, \Delta, 0)$, which
-means we are simplifying the formula $\phi$ by assuming that the domain $\Delta$
-is empty. Informally, if there is a predicate $P$ in $\phi$ unrelated to
-$\Delta$, smoothing preserves all occurrences of $P$ even if all clauses with
-$P$ become vacuously satisfied.
+\cref{line:presmoothing} is not satisfied, the clause is not smoothed but
+omitted.
+
+Suppose \Propagate is called with arguments $(\phi, \Delta, 0)$, i.e., we are
+simplifying the formula $\phi$ by assuming that the domain $\Delta$ is empty.
+Informally, if there is a predicate $P$ in $\phi$ unrelated to $\Delta$,
+smoothing preserves all occurrences of $P$ even if all clauses with $P$ become
+vacuously satisfied.
 
@@
   The value of $P$ is fixed over $\Gamma' \times \Gamma'$ by \cref{eq:example2},
-  but it is allowed to vary freely over
+  but it can vary freely over
   $(\Gamma \times \Gamma) \setminus (\Gamma' \times \Gamma')$ since
   \cref{eq:example1} is vacuously satisfied by all structures. Therefore, the
-  correct FOMC should be $2^{|\Gamma|^2 - |\Gamma'|^2}$.
-
-  However, without \cref{line:smoothing2}, \Propagate would simplify $\phi$ to
+  correct FOMC should be $2^{|\Gamma|^2 - |\Gamma'|^2}$. However, without
+  \cref{line:smoothing2}, \Propagate would simplify $\phi$ to
   $\forall y, z \in \Gamma'\text{. }P(y, z)$. In this case, $P$ is a subset of
   $\Gamma' \times \Gamma'$. This simplified formula has only one model:
-  $\{\, P(y, z) \mid y, z \in \Gamma' \,\}$.
-
-  By including \cref{line:smoothing2}, \Propagate transforms $\phi$ to:
+  $\{\, P(y, z) \mid y, z \in \Gamma' \,\}$. By including
+  \cref{line:smoothing2}, \Propagate transforms $\phi$ to:
   \begin{gather*}
@@
 
-In this section, we present experimental results examining the scalability of
-\Cranetwo{} compared to two other notable FOMC algorithms: \textsc{FastWFOMC}
-and \textsc{ForcLift}. Note that it would not make sense to include the original
-\textsc{Crane} algorithm in the experiments or to evaluate \Cranetwo{} without
-the C++ code generation described in \cref{sec:cpp}. Indeed, these algorithms
-can only produce mathematical definitions of functions without evaluating them.
-
-In our experiments, we include two versions of \Cranetwo{}: \Cranegreedy{} and
-\Cranebfs{}. Like its predecessor, \Cranetwo{} has two modes that decide how
-compilation rules are applied to formulas: one that uses greedy search similarly
-to \textsc{ForcLift} and another that combines greedy and breadth-first search.
-While greedy search is more efficient (in terms of being able to handle larger
-formulas), it is a heuristic that can miss some solutions.
+In this section, we present experimental results that analyse the scalability of
+\Cranetwo{} in comparison to two other notable FOMC algorithms:
+\textsc{FastWFOMC} and \textsc{ForcLift}. Our experiments involve two versions
+of \Cranetwo{}: \Cranegreedy{} and \Cranebfs{}. Like its predecessor,
+\Cranetwo{} has two modes for applying compilation rules to formulas: one that
+uses a greedy search algorithm similar to \textsc{ForcLift} and another that
+combines greedy and breadth-first search.
+
+% It would not make sense to include the original \textsc{Crane} algorithm in
+% the experiments or evaluate \Cranetwo{} without the C++ code generation
+% described in \cref{sec:cpp}. Indeed, these algorithms can only produce
+% mathematical definitions of functions without evaluating them.
+
+% While greedy search is more efficient (in terms of being able to handle larger
+% formulas), it is a heuristic that can miss some solutions.
 
@@
 
-We compare the algorithms on three benchmarks from previous work. The first is
-the function-counting problem from \cref{example:functions}, previously examined
-by \citeauthor{DBLP:conf/kr/DilkasB23}~\shortcite{DBLP:conf/kr/DilkasB23}. The
-second is a variant of the well-known `Friends and Smokers' Markov logic
-network~\cite{DBLP:conf/aaai/SinglaD08,DBLP:conf/uai/BroeckCD12}. In \Ctwo{},
-\FO{}, and \UFO{}, it can be formulated as
+We compare these algorithms using three benchmarks from previous studies. The
+first benchmark is the function-counting problem from \cref{example:functions},
+previously examined by
+\citeauthor{DBLP:conf/kr/DilkasB23}~\shortcite{DBLP:conf/kr/DilkasB23}. The
+second benchmark is a variant of the well-known `Friends and Smokers' Markov
+logic network~\cite{DBLP:conf/aaai/SinglaD08,DBLP:conf/uai/BroeckCD12}. In
+\Ctwo{}, \FO{}, and \UFO{}, this problem can be formulated as
 \begin{gather*}
@@
 \end{gather*}
-Finally, we include the bijection-counting problem previously used by
+Finally, we include the bijection-counting problem previously utilised by
 \citeauthor{DBLP:conf/kr/DilkasB23}~\shortcite{DBLP:conf/kr/DilkasB23}. Its
@@
 
+\begin{figure*}[t]
+  \centering
+  \includegraphics{plot.pdf}
+  \caption{The runtime of the algorithms as a function of the domain size. Note
+    that both axes are on a logarithmic scale.}\label{fig:plot}
+\end{figure*}
+
 Since \textsc{FastWFOMC} does not support many-sorted logic, our experiments are
-restricted to formulas with a single domain. However, many of the counting
-problems examined in the experimental evaluation of
-\textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23} become equivalent (in the sense
-that they generate the same integer sequences) when restricted to a single
-domain. Moreover, it is challenging to compare \Cranetwo{} and
-\textsc{FastWFOMC} on a larger set of problems because each problem has to be
-represented in two (fairly different) logics: \FO{} and \UFO{}. Nonetheless, the
-three benchmarks cover a diverse range of possibilities. Unlike the other two,
-the `friends' benchmark uses multiple predicates and can be written in \FO{}
-using only two variables and no cardinality constraints or counting quantifiers.
-Next, the `functions' benchmark, while still liftable by all of the algorithms,
-requires either the use of cardinality constraints, counting quantifiers, or
-more than two variables. Finally, the `bijections' benchmark is an example of a
-formula that can be handled by \textsc{FastWFOMC} but not \textsc{ForcLift}.
+limited to formulas with a single domain. However, many of the counting problems
+used in the experimental evaluation of
+\textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23} become equivalent (in terms of
+generating equivalent integer sequences) when restricted to a single domain.
+Additionally, comparing \Cranetwo{} and \textsc{FastWFOMC} on a broader set of
+problems is challenging because each problem needs to be represented in two
+(quite different) logics: \FO{} and \UFO{}. Nevertheless, the three benchmarks
+cover a wide range of possibilities.
+
+Among the three benchmarks, the `friends' benchmark stands out as it uses
+multiple predicates and can be expressed in \FO{} using just two variables
+without cardinality constraints or counting quantifiers. The `functions'
+benchmark, on the other hand, can still be handled by all the algorithms, but it
+requires cardinality constraints, counting quantifiers, or more than two
+variables. Lastly, the `bijections' benchmark is an example of a formula that
+\textsc{FastWFOMC} can handle but \textsc{ForcLift} cannot.
 
@@
 
-A major difference between \textsc{ForcLift} and the other two algorithms is
-that \textsc{ForcLift} does not support arbitrary-precision arithmetic whereas
-the other two algorithms both use the GNU Multiple Precision Arithmetic Library.
-Instead, when the numerical value of the count becomes too big to be accurately
-presented using finite precision, \textsc{ForcLift} returns $\infty$. We run
-each algorithm on each benchmark on domains of size $2^{1}, 2^{2}, 2^{3},\dots$
-until the algorithm times out after \SI{1}{\hour}, runs out of memory, or (in
-the case of \textsc{ForcLift}) returns $\infty$. We measure compilation and
-inference time separately, but primarily focus on total runtime (i.e., the sum
-of both), which is dominated by the latter.
+A considerable difference between \textsc{ForcLift} and the other two algorithms
+is that \textsc{ForcLift} does not support arbitrary precision whereas the other
+algorithms use the GNU Multiple Precision Arithmetic Library. Thus, when the
+count exceeds finite precision, \textsc{ForcLift} returns $\infty$. For
+evaluation purposes, we ran each algorithm on each benchmark using domains of
+sizes $2^{1}, 2^{2}, 2^{3}$, and so on, until a timeout occurred after
+\SI{1}{\hour}, the algorithm ran out of memory, or \textsc{ForcLift} returned
+$\infty$. We separately measured compilation and inference time but primarily
+focused on total runtime, dominated by the latter.
 
@@
 
-The experiments were run on an Intel Skylake \SI{2.4}{\giga\hertz} CPU with
-\SI{188}{\gibi\byte} of memory and CentOS~7 operating system. C++ programs were
-compiled using the Intel C++ Compiler 2020u4. \textsc{FastWFOMC} was run on
-Julia~1.10.4, while all other algorithms were run on the Java Virtual Machine
-1.8.0\_201.
+The experiments were conducted using an Intel Skylake \SI{2.4}{\giga\hertz} CPU
+with \SI{188}{\gibi\byte} of memory and CentOS~7. C++ programs were compiled
+using the Intel C++ Compiler 2020u4. \textsc{FastWFOMC} ran on Julia~1.10.4,
+while the other algorithms were executed on the Java Virtual Machine 1.8.0\_201.
 
@@
 
-\begin{figure*}[t]
-  \centering
-  \includegraphics{plot.pdf}
-  \caption{The runtime of the algorithms as a function of the domain size. Note
-    that both axes are on a logarithmic scale.}\label{fig:plot}
-\end{figure*}
-
-\Cref{fig:plot} summarises the experimental results. Only \textsc{FastWFOMC} and
-\Cranebfs{} could lift the bijection-counting problem. On this benchmark, the
-largest domain sizes that these algorithms could handle were \num{64} and
-\num{4096}, respectively. On the other two benchmarks, \textsc{ForcLift} has the
-lowest runtime, but, as it is finite-precision, only scales up to domain sizes
-of \num{16} and \num{128} in the case of `friends' and `functions',
-respectively. Next, \textsc{FastWFOMC} outperforms \textsc{ForcLift} in the case
-of `friends' but not `functions': it scales up to domains of size \num{1024} and
-\num{64}, respectively. Finally, both \Cranebfs{} and \Cranegreedy{} perform
-nearly identically on both of these benchmarks. Similarly to the `bijections'
-benchmark, \Cranetwo{} significantly surpasses the other two algorithms, scaling
-up to domains of size \num{8192} and \num{67108864}, respectively.
-
-Another aspect of the experimental results worth discussing separately is that
-of compilation. As both Julia and Scala use just-in-time (JIT) compilation, both
-\textsc{FastWFOMC} and \textsc{ForcLift} take longer when run on the smallest
-domain size, as that is when most JIT compilation happens. As \Cranetwo{} is run
-only once per benchmark, JIT compilation time is incorporated into its runtime
-across all domain sizes. Moreover, while \textsc{ForcLift} compilation is
-generally faster than that of \Cranetwo{}, neither is significant in comparison
-to inference time. Indeed, typically, \textsc{ForcLift} compilation took around
-\SI{0.5}{\second}, while \Cranetwo{} compilation took around \SI{2.3}{\second}.
+\Cref{fig:plot} presents a summary of the experimental results. Only
+\textsc{FastWFOMC} and \Cranebfs{} could handle the bijection-counting problem.
+For this benchmark, the largest domain sizes these algorithms could accommodate
+were \num{64} and \num{4096}, respectively. On the other two benchmarks,
+\textsc{ForcLift} had the lowest runtime. However, due to its finite precision,
+it only scaled up to domain sizes of \num{16} and \num{128} for `friends' and
+`functions', respectively. \textsc{FastWFOMC} outperformed \textsc{ForcLift} in
+the case of `friends', but not `functions', as it could handle domains of size
+\num{1024} and \num{64}, respectively. Furthermore, both \Cranebfs{} and
+\Cranegreedy{} performed similarly on both benchmarks. Similarly to the
+`bijections' benchmark, \Cranetwo{} significantly outperformed the other two
+algorithms, scaling up to domains of size \num{8192} and \num{67108864},
+respectively.
+
+Another aspect of the experimental results that deserves separate discussion is
+compilation. Both Julia and Scala use just-in-time (JIT) compilation, which
+means that \textsc{FastWFOMC} and \textsc{ForcLift} take longer to run on the
+smallest domain size, where most JIT compilation occurs. In the case of
+\Cranetwo{}, it is only run once per benchmark, so the JIT compilation time is
+included in its overall runtime across all domain sizes. Additionally, while
+\textsc{ForcLift}'s compilation is generally faster than that of \Cranetwo{},
+neither significantly affects the inference time. Specifically,
+\textsc{ForcLift} compilation typically takes around \SI{0.5}{\second}, while
+\Cranetwo{} compilation takes around \SI{2.3}{\second}.
 
@@
 
-So what do our experiments reveal about which algorithm should one use in
-practice? If the formula can be handled by \textsc{ForcLift} and the domain
-sizes are reasonably small, it is likely to be the fastest algorithm. In other
-cases, \Cranetwo{} is likely to be significantly faster than \textsc{FastWFOMC}
-across all domain sizes (but especially with higher domain sizes), assuming the
-formula can be handled by both algorithms.
+Based on our experiments, which algorithm should be used in practice? If the
+formula can be handled by \textsc{ForcLift} and the domain sizes are reasonably
+small, \textsc{ForcLift} is likely the fastest algorithm. In other situations,
+\Cranetwo{} is expected to be significantly more efficient than
+\textsc{FastWFOMC} regardless of domain size, provided both algorithms can
+handle the formula.
 
@@
 
-In this work, we have presented several contributions. First, we have developed
+In this work, we have made several contributions. First, we have developed
 algorithmic techniques to find the base cases of recursive functions generated
-by the original \textsc{Crane} algorithm. Second, we have extended the smoothing
-procedure of \textsc{ForcLift} and \textsc{Crane} to support base case formulas.
-Third, we have proposed an approach to compile function definitions into C++
-programs with support for arbitrary-precision arithmetic. Lastly, we have
-provided experimental evidence demonstrating that \Cranetwo{} can scale to much
-larger domain sizes than \textsc{FastWFOMC} while handling more formulas than
+by \textsc{Crane}. Second, we have extended the smoothing procedure of
+\textsc{ForcLift} and \textsc{Crane} to support base case formulas. Third, we
+have proposed an approach to compile function definitions into C++ programs with
+support for arbitrary-precision arithmetic. Lastly, we have provided
+experimental evidence demonstrating that \Cranetwo{} can scale to much larger
+domain sizes than \textsc{FastWFOMC} while handling more formulas than
 \textsc{ForcLift}. Having FOMC algorithms that can efficiently handle large
@@
 handling a particular formula can be assessed using \emph{fine-grained
-  complexity}. In the case of \textsc{Crane} and \Cranetwo{}, this can be done
-by analysing the equations~\cite{DBLP:conf/kr/DilkasB23}. By doing so,
-efficiency can be reasoned about in a more implementation-independent manner by
-making claims about the maximum degree of the polynomial that characterises any
-given solution.
+  complexity}. In the case of \Cranetwo{}, this can be done by analysing the
+equations~\cite{DBLP:conf/kr/DilkasB23}. By doing so, efficiency can be reasoned
+about in a more implementation-independent manner by making claims about the
+maximum degree of the polynomial that characterises any given solution.
 

### 2024-08-12 doc/paper/paper.tex
Minor edits

@@
 problems is challenging because each problem needs to be represented in two
-(quite different) logics: \FO{} and \UFO{}. Nevertheless, the three benchmarks
-cover a wide range of possibilities.
-
-Among the three benchmarks, the `friends' benchmark stands out as it uses
-multiple predicates and can be expressed in \FO{} using just two variables
-without cardinality constraints or counting quantifiers. The `functions'
-benchmark, on the other hand, can still be handled by all the algorithms, but it
-requires cardinality constraints, counting quantifiers, or more than two
-variables. Lastly, the `bijections' benchmark is an example of a formula that
-\textsc{FastWFOMC} can handle but \textsc{ForcLift} cannot.
+(quite different) logics: \FO{} and \UFO{}.
+
+Nevertheless, the three benchmarks cover a wide range of possibilities. The
+`friends' benchmark stands out as it uses multiple predicates and can be
+expressed in \FO{} using just two variables without cardinality constraints or
+counting quantifiers. The `functions' benchmark, on the other hand, can still be
+handled by all the algorithms, but it requires cardinality constraints, counting
+quantifiers, or more than two variables. Lastly, the `bijections' benchmark is
+an example of a formula that \textsc{FastWFOMC} can handle but \textsc{ForcLift}
+cannot.
 
@@
 \textsc{ForcLift}'s compilation is generally faster than that of \Cranetwo{},
-neither significantly affects the inference time. Specifically,
-\textsc{ForcLift} compilation typically takes around \SI{0.5}{\second}, while
-\Cranetwo{} compilation takes around \SI{2.3}{\second}.
+neither significantly affects overall runtime. Specifically, \textsc{ForcLift}
+compilation typically takes around \SI{0.5}{\second}, while \Cranetwo{}
+compilation takes around \SI{2.3}{\second}.
 

### 2024-08-14 doc/paper/paper.tex
minor edits

@@
   First-order model counting (FOMC) is the problem of counting the number of
-  models of a sentence in first-order logic. Recently, a new algorithm for FOMC
-  was proposed that, instead of simply providing the final count, generates
+  models of a sentence in first-order logic.
+Since lifted inference techniques rely on reductions to variants of FOMC, the design of scalable methods for FOMC has attracted attention from theoreticians and practitioners alike over the past decade.
+Recently, significant advances were achieved with the introduction of first-order knowledge compilation-based approach, called \textsc{crane}, that instead of simply providing the final count, generates
   definitions of (possibly recursive) functions, which can be evaluated with
-  different arguments to compute the model count for any domain size. However,
-  the algorithm did not include base cases in the recursive definitions. This
-  work makes three contributions. First, we demonstrate how to construct
-  function definitions that include base cases by modifying the logical formulas
-  used in the FOMC algorithm. Second, we extend the well-known circuit
-  modification technique in knowledge compilation, known as smoothing, to work
-  with the formulas corresponding to base cases. Third, we introduce a
+  different arguments to compute the model count for any domain size.  We introduce a
   compilation algorithm that transforms the function definitions into C++ code,
@@
   the current state of the art, as demonstrated through experimental results.
+
+%While \textsc{crane} was shown to handle formulas beyond the capabilites of prior state of the art approaches, the \textsc{crane} still required manual evaluation of constructed functions to obtain model counts.
+The primary contribution of our work is a fully automated FOMC algorithm that relies on function construction.
+%  
+%  the algorithm did not include base cases in the recursive definitions. This
+%  work makes three contributions. First, we demonstrate how to construct
+%  function definitions that include base cases by modifying the logical formulas
+%  used in the FOMC algorithm. Second, we extend the well-known circuit
+%  modification technique in knowledge compilation, known as smoothing, to work
+%  with the formulas corresponding to base cases. Third, we introduce a
+%  compilation algorithm that transforms the function definitions into C++ code,
+%  equipped with arbitrary-precision arithmetic. These additions allow the new
+%  FOMC algorithm to scale to domain sizes over \num{500000} times larger than
+%  the current state of the art, as demonstrated through experimental results.
 \end{abstract}

### 2024-08-14 doc/paper/paper.tex
edit

@@
 \begin{abstract}
-  First-order model counting (FOMC) is the problem of counting the number of
-  models of a sentence in first-order logic.
-Since lifted inference techniques rely on reductions to variants of FOMC, the design of scalable methods for FOMC has attracted attention from theoreticians and practitioners alike over the past decade.
-Recently, significant advances were achieved with the introduction of first-order knowledge compilation-based approach, called \textsc{crane}, that instead of simply providing the final count, generates
-  definitions of (possibly recursive) functions, which can be evaluated with
-  different arguments to compute the model count for any domain size.  We introduce a
-  compilation algorithm that transforms the function definitions into C++ code,
-  equipped with arbitrary-precision arithmetic. These additions allow the new
-  FOMC algorithm to scale to domain sizes over \num{500000} times larger than
-  the current state of the art, as demonstrated through experimental results.
+	First-order model counting (FOMC) is the problem of counting the number of models of a sentence in first-order logic.
+Since lifted inference techniques rely on reductions to variants of FOMC, the design of scalable methods for FOMC has attracted attention from both theoreticians and practitioners over the past decade.
+Recently, a new approach based on first-order knowledge compilation was proposed.
+This approach, called \textsc{crane}, instead of simply providing the final count, generates definitions of (possibly recursive) functions that can be evaluated with different arguments to compute the model count for any domain size.
+However, this approach is not fully automated, as it requires manual evaluation of the constructed functions.
+The primary contribution of this work is a fully automated compilation algorithm, called \textsc{crane2}, which transforms the function definitions into C++ code equipped with arbitrary-precision arithmetic.
+These additions allow the new FOMC algorithm to scale to domain sizes over \num{500000} times larger than the current state of the art, as demonstrated through experimental results.
 

### 2024-08-14 doc/paper/paper.tex
minor edit

@@
 
-In this section, we present experimental results that analyse the scalability of
-\Cranetwo{} in comparison to two other notable FOMC algorithms:
-\textsc{FastWFOMC} and \textsc{ForcLift}. Our experiments involve two versions
+Our empirical evaluation sought to compare the runtime performance of {\Cranetwo} with the current state of the art, namely 
+\textsc{FastWFOMC} and \textsc{ForcLift}. It is worth remarking that  \textsc{ForcLift} does not support arbitrary precision, and returns error for cases that requires arbitrary precision reasoning. 
+Our experiments involve two versions
 of \Cranetwo{}: \Cranegreedy{} and \Cranebfs{}. Like its predecessor,
@@
 
+The experiments were conducted using an Intel Skylake \SI{2.4}{\giga\hertz} CPU
+with \SI{188}{\gibi\byte} of memory and CentOS~7. C++ programs were compiled
+using the Intel C++ Compiler 2020u4. \textsc{FastWFOMC} ran on Julia~1.10.4,
+while the other algorithms were executed on the Java Virtual Machine 1.8.0\_201.
+
 % It would not make sense to include the original \textsc{Crane} algorithm in
@@
 
+\subsection{Benchmarks}
 We compare these algorithms using three benchmarks from previous studies. The
@@
 
-Since \textsc{FastWFOMC} does not support many-sorted logic, our experiments are
-limited to formulas with a single domain. However, many of the counting problems
-used in the experimental evaluation of
-\textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23} become equivalent (in terms of
-generating equivalent integer sequences) when restricted to a single domain.
-Additionally, comparing \Cranetwo{} and \textsc{FastWFOMC} on a broader set of
-problems is challenging because each problem needs to be represented in two
-(quite different) logics: \FO{} and \UFO{}.
-
-Nevertheless, the three benchmarks cover a wide range of possibilities. The
+%Since \textsc{FastWFOMC} does not support many-sorted logic, our experiments are
+%limited to formulas with a single domain. However, many of the counting problems
+%used in the experimental evaluation of
+%\textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23} become equivalent (in terms of
+%generating equivalent integer sequences) when restricted to a single domain.
+%Additionally, comparing \Cranetwo{} and \textsc{FastWFOMC} on a broader set of
+%problems is challenging because each problem needs to be represented in two
+%(quite different) logics: \FO{} and \UFO{}.
+
+The three benchmark families cover a wide range of possibilities. The
 `friends' benchmark stands out as it uses multiple predicates and can be
@@
 
-A considerable difference between \textsc{ForcLift} and the other two algorithms
-is that \textsc{ForcLift} does not support arbitrary precision whereas the other
-algorithms use the GNU Multiple Precision Arithmetic Library. Thus, when the
-count exceeds finite precision, \textsc{ForcLift} returns $\infty$. For
+%A considerable difference between \textsc{ForcLift} and the other two algorithms
+%is that \textsc{ForcLift} does not support arbitrary precision whereas the other
+%algorithms use the GNU Multiple Precision Arithmetic Library. Thus, when the
+%count exceeds finite precision, \textsc{ForcLift} returns $\infty$.
+
+For
 evaluation purposes, we ran each algorithm on each benchmark using domains of
-sizes $2^{1}, 2^{2}, 2^{3}$, and so on, until a timeout occurred after
-\SI{1}{\hour}, the algorithm ran out of memory, or \textsc{ForcLift} returned
-$\infty$. We separately measured compilation and inference time but primarily
+sizes $2^{1}, 2^{2}, 2^{3}$, and so on, until an algorithm failed to handle a domain size due to timeout, out of memory error, or out of precision errors.
+While we separately measured compilation and inference time but primarily
 focused on total runtime, dominated by the latter.
@@
 % specifications of the computer, operating system, libraries, and tools used).
-
-The experiments were conducted using an Intel Skylake \SI{2.4}{\giga\hertz} CPU
-with \SI{188}{\gibi\byte} of memory and CentOS~7. C++ programs were compiled
-using the Intel C++ Compiler 2020u4. \textsc{FastWFOMC} ran on Julia~1.10.4,
-while the other algorithms were executed on the Java Virtual Machine 1.8.0\_201.
 
@@
 
+\subsection{Results}
 \Cref{fig:plot} presents a summary of the experimental results. Only

### 2024-08-14 doc/paper/paper.tex
edits

@@
 
-In this work, we have made several contributions. First, we have developed
-algorithmic techniques to find the base cases of recursive functions generated
-by \textsc{Crane}. Second, we have extended the smoothing procedure of
-\textsc{ForcLift} and \textsc{Crane} to support base case formulas. Third, we
-have proposed an approach to compile function definitions into C++ programs with
-support for arbitrary-precision arithmetic. Lastly, we have provided
-experimental evidence demonstrating that \Cranetwo{} can scale to much larger
+In this work, we present a scalable automated first-order knowledge compilation-based approach to first order model counting.
+The proposed approach relies on automatically generating the C++ code corresponding to the recursive functions extracted from knowledge compilation.
+The enusing empirical evaluatino demonstrated  that \Cranetwo{} can scale to much larger
 domain sizes than \textsc{FastWFOMC} while handling more formulas than

### 2024-08-15 doc/paper/paper.tex
A version good enough to submit?

@@
 
+\sisetup{group-separator = {,}}
+
 \newcommand{\cmark}{\ding{51}}
@@
 \newcommand{\UFO}{$\mathsf{UFO}^{2} + \mathsf{CC}$}
-\newcommand{\Cranetwo}{\textsc{Crane2}}
-\newcommand{\Cranebfs}{\textsc{Crane2-BFS}}
-\newcommand{\Cranegreedy}{\textsc{Crane2-Greedy}}
+\newcommand{\Cranetwo}{\textsc{Gantry}}
+\newcommand{\Cranebfs}{\textsc{Gantry-BFS}}
+\newcommand{\Cranegreedy}{\textsc{Gantry-Greedy}}
 
@@
 \begin{abstract}
-	First-order model counting (FOMC) is the problem of counting the number of models of a sentence in first-order logic.
-Since lifted inference techniques rely on reductions to variants of FOMC, the design of scalable methods for FOMC has attracted attention from both theoreticians and practitioners over the past decade.
-Recently, a new approach based on first-order knowledge compilation was proposed.
-This approach, called \textsc{crane}, instead of simply providing the final count, generates definitions of (possibly recursive) functions that can be evaluated with different arguments to compute the model count for any domain size.
-However, this approach is not fully automated, as it requires manual evaluation of the constructed functions.
-The primary contribution of this work is a fully automated compilation algorithm, called \textsc{crane2}, which transforms the function definitions into C++ code equipped with arbitrary-precision arithmetic.
-These additions allow the new FOMC algorithm to scale to domain sizes over \num{500000} times larger than the current state of the art, as demonstrated through experimental results.
-
-%While \textsc{crane} was shown to handle formulas beyond the capabilites of prior state of the art approaches, the \textsc{crane} still required manual evaluation of constructed functions to obtain model counts.
-The primary contribution of our work is a fully automated FOMC algorithm that relies on function construction.
-%  
-%  the algorithm did not include base cases in the recursive definitions. This
-%  work makes three contributions. First, we demonstrate how to construct
-%  function definitions that include base cases by modifying the logical formulas
-%  used in the FOMC algorithm. Second, we extend the well-known circuit
-%  modification technique in knowledge compilation, known as smoothing, to work
-%  with the formulas corresponding to base cases. Third, we introduce a
-%  compilation algorithm that transforms the function definitions into C++ code,
-%  equipped with arbitrary-precision arithmetic. These additions allow the new
-%  FOMC algorithm to scale to domain sizes over \num{500000} times larger than
-%  the current state of the art, as demonstrated through experimental results.
+  First-order model counting (FOMC) is the problem of counting the number of
+  models of a sentence in first-order logic. Since lifted inference techniques
+  rely on reductions to variants of FOMC, the design of scalable methods for
+  FOMC has attracted attention from both theoreticians and practitioners over
+  the past decade. Recently, a new approach based on first-order knowledge
+  compilation was proposed. This approach, called \textsc{Crane}, instead of
+  simply providing the final count, generates definitions of (possibly
+  recursive) functions that can be evaluated with different arguments to compute
+  the model count for any domain size. However, this approach is not fully
+  automated, as it requires manual evaluation of the constructed functions. The
+  primary contribution of this work is a fully automated compilation algorithm,
+  called \Cranetwo{}, which transforms the function definitions into C++ code
+  equipped with arbitrary-precision arithmetic. These additions allow the new
+  FOMC algorithm to scale to domain sizes over \num{500000} times larger than
+  the current state of the art, as demonstrated through experimental results.
 \end{abstract}
@@
 % 1. What is the problem?
-
-\emph{First-order model counting} (FOMC) is the task of counting the number of
-models of a sentence in first-order logic over some given domain(s). The
-weighted variant of this problem, known as WFOMC, seeks to compute the total
-weight of the models~\cite{DBLP:conf/ijcai/BroeckTMDR11}. WFOMC is related to
-its propositional predecessor weighted model
-counting~\cite{DBLP:journals/ai/ChaviraD08} and other attempts to unify logic
+% 2. Why is it interesting and important?
+
+\emph{First-order model counting} (FOMC) is the task of determining the number
+of models for a sentence in first-order logic over a specified domain. The
+weighted variant, WFOMC, computes the total weight of these models, linking
+logical reasoning with probabilistic
+frameworks~\cite{DBLP:conf/ijcai/BroeckTMDR11}. It builds upon earlier efforts
+in weighted model counting for propositional
+logic~\cite{DBLP:journals/ai/ChaviraD08} and broader attempts to bridge logic
 and
 probability~\cite{DBLP:journals/ai/Nilsson86,novak2012mathematical,vsaletic2024graded}.
-It is also a key approach to \emph{lifted inference}, which aims to compute
-probabilities more efficiently by leveraging symmetries in the
-problem~\cite{DBLP:conf/ecai/Kersting12}.
-
-% 2. Why is it interesting and important?
-
-Lifted inference is an active area of research, with recent work in domains such
-as constraint satisfaction problems~\cite{DBLP:journals/jair/TotisDRK23} and
-probabilistic answer set programming~\cite{DBLP:journals/ijar/AzzoliniR23}.
-WFOMC has been used for inference on probabilistic
+WFOMC is central to \emph{lifted inference}, which enhances the efficiency of
+probabilistic calculations by exploiting
+symmetries~\cite{DBLP:conf/ecai/Kersting12}. Lifted inference continues to
+advance, with applications extending to constraint satisfaction
+problems~\cite{DBLP:journals/jair/TotisDRK23} and probabilistic answer set
+programming~\cite{DBLP:journals/ijar/AzzoliniR23}. Moreover, WFOMC has proven
+effective at reasoning over probabilistic
 databases~\cite{DBLP:journals/debu/GribkoffSB14} and probabilistic logic
-programs~\cite{DBLP:journals/ijar/RiguzziBZCL17}. FOMC algorithms have been
-utilised for discovering new integer
-sequences~\cite{DBLP:conf/ijcai/SvatosJT0K23}, and for
-conjecturing~\cite{DBLP:conf/ilp/BarvinekB0ZK21} and
-constructing~\cite{DBLP:conf/kr/DilkasB23} recurrence relations and other
-recursive structures that describe these sequences. FOMC algorithms have also
-been extended to perform
-\emph{sampling}~\cite{DBLP:conf/aaai/WangB0K22,DBLP:conf/lics/WangP0K23}.
-
-% By considering domains of increasing sizes, the FOMC of a formula can be seen
-% as an integer sequence.
+programs~\cite{DBLP:journals/ijar/RiguzziBZCL17}. FOMC algorithms have also
+facilitated breakthroughs in discovering integer
+sequences~\cite{DBLP:conf/ijcai/SvatosJT0K23} and developing recurrence
+relations for these sequences~\cite{DBLP:conf/kr/DilkasB23}. Recently, these
+algorithms have been extended to perform sampling
+tasks~\cite{DBLP:journals/ai/WangPWK24}.
 
@@
 
-The complexity of FOMC is typically characterised in terms of \emph{data
-  complexity}. If there is an algorithm that can compute the FOMC of a formula
-in polynomial time with respect to the domain size(s), that formula is called
-\emph{liftable}~\cite{DBLP:conf/starai/JaegerB12}.
+The complexity of FOMC is generally measured by \emph{data complexity}, with a
+formula classified as \emph{liftable} if it can be solved in polynomial time
+relative to the domain size~\cite{DBLP:conf/starai/JaegerB12}. While all
+formulas with up to two variables are known to be
+liftable~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/kr/BroeckMD14},
 \citeauthor{DBLP:conf/pods/BeameBGS15}~\shortcite{DBLP:conf/pods/BeameBGS15}
-demonstrated the existence of an unliftable formula with three variables. It is
-also known that formulas with up to two variables are
-liftable~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/kr/BroeckMD14}. The liftable
-fragment of formulas with two variables has been expanded with various
-axioms~\cite{DBLP:conf/aaai/TothK23,DBLP:journals/ai/BremenK23}, counting
-quantifiers~\cite{DBLP:journals/jair/Kuzelka21} and in other
-ways~\cite{DBLP:conf/nips/KazemiKBP16}.
-
-% This involves fixing the formula and determining whether an
-% algorithm exists that can compute the FOMC in time polynomial with respect to
-% the domain size(s).
+demonstrated that liftability does not extend to all formulas, identifying an
+unliftable formula with three variables. Recent work has further extended the
+liftable fragment with additional
+axioms~\cite{DBLP:conf/aaai/TothK23,DBLP:journals/ai/BremenK23} and counting
+quantifiers~\cite{DBLP:journals/jair/Kuzelka21}, expanding our understanding of
+liftability.
 
@@
 
-There are many FOMC algorithms with different underlying principles. Perhaps the
-most prominent class of FOMC algorithms is based on \emph{first-order knowledge
-  compilation} (FOKC). In this approach, the formula is compiled into a
-representation (such as a circuit or graph) by applying \emph{compilation
-  rules}. Algorithms in this class include
-\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} and its extension
-\textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23}. Another FOMC algorithm,
-\textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21}, is based on cell enumeration.
-Other algorithms utilise local search~\cite{DBLP:journals/pvldb/NiuRDS11},
-junction trees~\cite{DBLP:conf/aaai/VenugopalSG15}, Monte Carlo
-sampling~\cite{DBLP:journals/cacm/GogateD16}, and anytime approximation via
-upper/lower bound construction~\cite{DBLP:conf/ijcai/BremenK20}.
-
-% This representation can then be used to compute the FOMC for any combination
-% of domain sizes.
-
-% The former compiles formulas into circuits, while the latter compiles them
-% first to graphs and then to (algebraic) equations.
+FOMC algorithms are diverse, with approaches ranging from \emph{first-order
+  knowledge compilation} (FOKC) to local
+search~\cite{DBLP:journals/pvldb/NiuRDS11}, Monte Carlo
+sampling~\cite{DBLP:journals/cacm/GogateD16}, and anytime
+approximation~\cite{DBLP:conf/ijcai/BremenK20}. Among these, FOKC-based
+algorithms are particularly prominent, transforming formulas into structured
+representations such as circuits or graphs. Notable examples include
+\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} and its successor
+\textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23}. Another important algorithm,
+\textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21}, uses cell enumeration as its
+foundation.
 
@@
 
-The recently proposed \textsc{Crane} algorithm marked significant progress in
-handling formulas beyond the capabilities of \textsc{FastWFOMC} and
-\textsc{ForcLift}, yet it fell short in critical aspects. \textsc{Crane} was
-incomplete since it could only construct function definitions, requiring users
-to manually evaluate these functions to obtain model counts. This limitation
-prevented \textsc{Crane} from serving as a convenient black box solution for
-FOMC. Furthermore, it introduced recursive functions without defining necessary
-base cases, adding further complexity to the users. In this work, we present
-\Cranetwo{}, addressing these gaps and pushing scalability to unprecedented
-levels. Unlike its predecessor, \Cranetwo{} is a fully automated FOMC algorithm,
-capable of handling domain sizes over \num{500000} times larger than previous
-algorithms.
-
-\begin{figure*}[t]
-  \centering
-  \begin{tikzpicture}
-    \node at (-1, 0) (formula) {$\phi$};
-    \node[draw,rounded rectangle] at (3, 0) (compilewithbasecases) {\CompileWithBaseCases};
-    \node[draw,rounded rectangle] at (9, 0) (compilation) {Compile to C++};
-
-    \node[draw,rounded rectangle,dashed] at (12, 0) (cpp) {C++ code};
-    \node at (12, -1) (sizes) {Domain sizes};
-
-    \node at (15, 0) (count) {Model count};
-
-    \node[draw,rounded rectangle] at (3, -2) (findbasecases) {\FindBaseCases};
-    \node[draw,rounded rectangle,left = 0.1cm of findbasecases] (crane) {\Compile};
-    \node[draw,rounded rectangle,right = 0.1cm of findbasecases] (propagate) {\Propagate};
-    \node[draw,rounded rectangle,right = 0.1cm of propagate] (simplify) {\Simplify};
-
-    \node[draw,fit={(compilewithbasecases) (compilation) (crane) (findbasecases) (propagate)},inner ysep=7pt,yshift=5pt] {};
-    \node at (0.6, 0.5) {\Cranetwo};
-
-    \draw[-Latex] (formula) -- (compilewithbasecases);
-    \draw[-Latex] (compilewithbasecases) -- node[above] {$\mathcal{E}$} (compilation);
-    \draw[-Latex] (compilation) -- (cpp);
-    \draw[-Latex] (sizes) -- (cpp);
-    \draw[-Latex] (cpp) -- (count);
-
-    \draw[-Latex,dashed] (compilewithbasecases) -- node[midway,left] {uses} (crane);
-    \draw[-Latex,dashed] (compilewithbasecases) -- node[midway,left] {uses} (findbasecases);
-    \draw[-Latex,dashed] (compilewithbasecases) -- node[midway,left] {uses} (propagate);
-    \draw[-Latex,dashed] (compilewithbasecases) -- node[midway,right] {uses} (simplify);
-  \end{tikzpicture}
-  \caption[]{The outline of using \Cranetwo{} to compute the model count of a formula $\phi$.
-First, the formula is compiled into a set of equations, which are then used to create a C++ program.
-This program can be executed with different command line arguments to calculate the model count of $\phi$ for different domain sizes.
-To accomplish this, the \CompileWithBaseCases function employs several components:
-    \begin{enumerate*}[label=(\roman*)]
-      \item the FOKC algorithm of \textsc{Crane},
-      \item a procedure called \FindBaseCases, which identifies a sufficient set of base cases,
-      \item a procedure called \Propagate, which constructs a formula corresponding to a given base case, and
-      \item algebraic simplification techniques (denoted as \Simplify).
-    \end{enumerate*}
-  }\label{fig:overview}
-\end{figure*}
-
-\Cref{fig:overview} outlines the workflow of the new algorithm. In
-\cref{sec:main}, we describe how \CompileWithBaseCases finds base cases for
-recursive functions. \Cref{sec:smoothing} explains post-processing techniques to
-preserve the correct model count. \Cref{sec:cpp} elucidates how function
-definitions are compiled into C++ programs. Note that a solution to FOMC that
-uses compilation to C++ has been considered
-before~\cite{DBLP:conf/kr/KazemiP16}, however, the extent of formulas that could
-be handled was limited. Finally, \cref{sec:experiments} presents experimental
-results comparing \Cranetwo{} with other FOMC algorithms.
-
-% by:
-% \begin{enumerate*}[label=(\roman*)]
-%   \item identifying a sufficient set of base cases for each function,
-%   \item constructing formulas corresponding to these base cases,
-%   and\label[step]{step2}
-%   \item recursing on these new formulas.
-% \end{enumerate*}
-
-\section{Preliminaries}
+The \textsc{Crane} algorithm marked a significant step forward, expanding the
+range of formulas handled by FOMC algorithms. However, it had notable
+limitations:
+\begin{enumerate*}[label=(\roman*)]
+  \item it required manual evaluation of function definitions to compute model
+  counts, and
+  \item it introduced recursive functions without proper base cases, making it
+  more complex to use.
+\end{enumerate*}
+To address these shortcomings, we present \Cranetwo{}, a fully automated FOMC
+algorithm that overcomes the constraints of its predecessor. \Cranetwo{} can
+handle domain sizes over \num{500000} times larger than previous algorithms and
+simplifies the user experience by automatically handling base cases and
+compiling function definitions into efficient C++ programs.
+
+In \cref{sec:preliminaries}, we cover some preliminaries, and in
+\cref{sec:main}, we detail all our technical contributions. Finally, in
+\cref{sec:experiments}, we present our experimental results, demonstrating
+\Cranetwo{}'s performance compared to other FOMC algorithms, and, in
+\cref{sec:conclusion}, we conclude the paper by discussing promising avenues for
+future work.
+
+\section{Preliminaries}\label{sec:preliminaries}
 
@@
 
-\section{Completing the Definitions of Functions}\label{sec:main}
+\section{Technical Contributions}\label{sec:main}
+
+\begin{figure*}[t]
+  \centering
+  \begin{tikzpicture}
+    \node at (-1, 0) (formula) {$\phi$};
+    \node[draw,rounded rectangle] at (3, 0) (compilewithbasecases) {\CompileWithBaseCases};
+    \node[draw,rounded rectangle] at (9, 0) (compilation) {Compile to C++};
+
+    \node[draw,rounded rectangle,dashed] at (12, 0) (cpp) {C++ code};
+    \node at (12, -1) (sizes) {Domain sizes};
+
+    \node at (15, 0) (count) {Model count};
+
+    \node[draw,rounded rectangle] at (3, -2) (findbasecases) {\FindBaseCases};
+    \node[draw,rounded rectangle,left = 0.1cm of findbasecases] (crane) {\Compile};
+    \node[draw,rounded rectangle,right = 0.1cm of findbasecases] (propagate) {\Propagate};
+    \node[draw,rounded rectangle,right = 0.1cm of propagate] (simplify) {\Simplify};
+
+    \node[draw,fit={(compilewithbasecases) (compilation) (crane) (findbasecases) (propagate)},inner ysep=7pt,yshift=5pt] {};
+    \node at (0.6, 0.5) {\Cranetwo};
+
+    \draw[-Latex] (formula) -- (compilewithbasecases);
+    \draw[-Latex] (compilewithbasecases) -- node[above] {$\mathcal{E}$} (compilation);
+    \draw[-Latex] (compilation) -- (cpp);
+    \draw[-Latex] (sizes) -- (cpp);
+    \draw[-Latex] (cpp) -- (count);
+
+    \draw[-Latex,dashed] (compilewithbasecases) -- node[midway,left] {uses} (crane);
+    \draw[-Latex,dashed] (compilewithbasecases) -- node[midway,left] {uses} (findbasecases);
+    \draw[-Latex,dashed] (compilewithbasecases) -- node[midway,left] {uses} (propagate);
+    \draw[-Latex,dashed] (compilewithbasecases) -- node[midway,right] {uses} (simplify);
+  \end{tikzpicture}
+  \caption[]{The outline of using \Cranetwo{} to compute the model count of a formula $\phi$.
+First, the formula is compiled into a set of equations, which are then used to create a C++ program.
+This program can be executed with different command line arguments to calculate the model count of $\phi$ for different domain sizes.
+To accomplish this, the \CompileWithBaseCases function employs several components:
+    \begin{enumerate*}[label=(\roman*)]
+      \item the FOKC algorithm of \textsc{Crane},
+      \item a procedure called \FindBaseCases, which identifies a sufficient set of base cases,
+      \item a procedure called \Propagate, which constructs a formula corresponding to a given base case, and
+      \item algebraic simplification techniques (denoted as \Simplify).
+    \end{enumerate*}
+  }\label{fig:overview}
+\end{figure*}
+
+\Cref{fig:overview} provides an overview of \Cranetwo{}'s workflow.
+\Cref{sec:completing} describes the main algorithm for completing the
+definitions of recursive functions with a sufficient set of base cases.
+\Cref{sec:identifying,sec:propagating} describe subsidiary algorithms for
+constructing a set of base cases and their corresponding logical formulas.
+\Cref{sec:smoothing} explains the post-processing techniques for ensuring
+accurate model counting. Additionally, \cref{sec:cpp} explains the process of
+compiling function definitions into C++ code, greatly expanding upon the range
+of formulas that could previously be handled by similar
+approaches~\cite{DBLP:conf/kr/KazemiP16}.
+
+\subsection{Completing the Definitions of Functions}\label{sec:completing}
 
@@
 $f$ and simplify it using the \Propagate procedure (explained in detail in
-\cref{sec:simplifying}). We do this by iterating over all indices of
+\cref{sec:propagating}). We do this by iterating over all indices of
 $\mathbf{x}$, where $x_{i}$ is a constant, and using \Propagate to simplify
@@
 
-\subsection{Propagating Domain Size Assumptions}\label{sec:simplifying}
+\subsection{Propagating Domain Size Assumptions}\label{sec:propagating}
 
@@
 
-\section{Smoothing the Base Cases}\label{sec:smoothing}
+\subsection{Smoothing the Base Cases}\label{sec:smoothing}
 
@@
 
-\section{Generating C++ Code}\label{sec:cpp}
+\subsection{Generating C++ Code}\label{sec:cpp}
 
@@
 
-For
-evaluation purposes, we ran each algorithm on each benchmark using domains of
-sizes $2^{1}, 2^{2}, 2^{3}$, and so on, until an algorithm failed to handle a domain size due to timeout, out of memory error, or out of precision errors.
-While we separately measured compilation and inference time but primarily
-focused on total runtime, dominated by the latter.
+For evaluation purposes, we ran each algorithm on each benchmark using domains
+of sizes $2^{1}, 2^{2}, 2^{3}$, and so on, until an algorithm failed to handle a
+domain size due to timeout, out of memory error, or out of precision errors.
+While we separately measured compilation and inference time, we primarily focus
+on total runtime, dominated by the latter.
 
@@
 
-\section{Conclusion and Future Work}
-
-In this work, we present a scalable automated first-order knowledge compilation-based approach to first order model counting.
-The proposed approach relies on automatically generating the C++ code corresponding to the recursive functions extracted from knowledge compilation.
-The enusing empirical evaluatino demonstrated  that \Cranetwo{} can scale to much larger
-domain sizes than \textsc{FastWFOMC} while handling more formulas than
-\textsc{ForcLift}. Having FOMC algorithms that can efficiently handle large
-domain sizes is especially crucial in the weighted setting. For example,
-consider the `friends' instance examined in \cref{sec:experiments}, which models
-a social network with friendships, smoking habits, and the probability of having
-cancer. The utility of such a model would be significantly limited if
-probabilities could only be efficiently computed for networks of at most
-\num{1000} people.
-
-There are many potential avenues for future work. Specifically, a more thorough
-experimental study is needed to understand how FOMC algorithms compare in terms
-of their ability to handle different formulas and their scalability with respect
-to domain size. Additionally, further characterisation of the capabilities of
-\Cranetwo{} can be explored. For example, \emph{completeness} could be proven
-for a fragment of first-order logic such as \Ctwo{} (using a suitable encoding
-of counting quantifiers). Moreover, the efficiency of a FOMC algorithm in
-handling a particular formula can be assessed using \emph{fine-grained
-  complexity}. In the case of \Cranetwo{}, this can be done by analysing the
-equations~\cite{DBLP:conf/kr/DilkasB23}. By doing so, efficiency can be reasoned
-about in a more implementation-independent manner by making claims about the
-maximum degree of the polynomial that characterises any given solution.
+\section{Conclusion and Future Work}\label{sec:conclusion}
+
+In this work, we have presented a scalable automated FOKC-based approach to
+FOMC. Our algorithm involves completing the definitions of recursive functions
+and subsequently translating all function definitions into C++ code. Empirical
+results demonstrate that \Cranetwo{} can scale to larger domain sizes than
+\textsc{FastWFOMC} while supporting a wider range of formulas than
+\textsc{ForcLift}. The ability to efficiently handle large domain sizes is
+particularly crucial in the weighted setting, as illustrated by the `friends'
+example discussed in \cref{sec:experiments}, where the model captures complex
+social networks with probabilistic relationships. Without this scalability, the
+practical usefulness of these models would be limited.
+
+Future directions for research include conducting a comprehensive experimental
+comparison of FOMC algorithms to better understand their comparative performance
+across various formulas. The capabilities of \Cranetwo{} could also be
+characterised theoretically, e.g.\ by proving completeness for specific logic
+fragments like \Ctwo{}. Additionally, the efficiency of FOMC algorithms can be
+further analysed using fine-grained complexity, which would provide more
+detailed insights into the computational demands of different formulas.
 
@@
 
+\section{Reproducibility Checklist}
+
+This paper:
+\begin{itemize}
+  \item Includes a conceptual outline and/or pseudocode description of AI
+        methods introduced (\textbf{yes}/partial/no/NA)
+  \item Clearly delineates statements that are opinions, hypothesis, and
+        speculation from objective facts and results (\textbf{yes}/no)
+  \item Provides well marked pedagogical references for less-familiare readers
+        to gain background necessary to replicate the paper (\textbf{yes}/no)
+\end{itemize}
+
+Does this paper make theoretical contributions? (\textbf{yes}/no) If yes, please
+complete the list below.
+
+\begin{itemize}
+  \item All assumptions and restrictions are stated clearly and formally.
+        (\textbf{yes}/partial/no)
+  \item All novel claims are stated formally (e.g., in theorem statements).
+        (\textbf{yes}/partial/no)
+  \item Proofs of all novel claims are included. (\textbf{yes}/partial/no)
+  \item Proof sketches or intuitions are given for complex and/or novel results.
+        (\textbf{yes}/partial/no)
+  \item Appropriate citations to theoretical tools used are given.
+        (\textbf{yes}/partial/no)
+  \item All theoretical claims are demonstrated empirically to hold.
+        (\textbf{yes}/partial/no/NA)
+  \item All experimental code used to eliminate or disprove claims is included.
+        (yes/no/\textbf{NA})
+\end{itemize}
+
+Does this paper rely on one or more datasets? (\textbf{yes}/no) If yes, please
+complete the list below.
+
+\begin{itemize}
+  \item A motivation is given for why the experiments are conducted on the
+        selected datasets (\textbf{yes}/partial/no/NA)
+  \item All novel datasets introduced in this paper are included in a data
+        appendix. (\textbf{yes}/partial/no/NA)
+  \item All novel datasets introduced in this paper will be made publicly
+        available upon publication of the paper with a license that allows free
+        usage for research purposes. (\textbf{yes}/partial/no/NA)
+  \item All datasets drawn from the existing literature (potentially including
+        authors’ own previously published work) are accompanied by appropriate
+        citations. (\textbf{yes}/no/NA)
+  \item All datasets drawn from the existing literature (potentially including
+        authors’ own previously published work) are publicly available.
+        (\textbf{yes}/partial/no/NA)
+  \item All datasets that are not publicly available are described in detail,
+        with explanation why publicly available alternatives are not
+        scientifically satisficing. (\textbf{yes}/partial/no/NA)
+\end{itemize}
+
+Does this paper include computational experiments? (\textbf{yes}/no) If yes,
+please complete the list below.
+
+\begin{itemize}
+  \item Any code required for pre-processing data is included in the appendix.
+        (\textbf{yes}/partial/no).
+  \item All source code required for conducting and analyzing the experiments is
+        included in a code appendix. (\textbf{yes}/partial/no)
+  \item All source code required for conducting and analyzing the experiments
+        will be made publicly available upon publication of the paper with a
+        license that allows free usage for research purposes.
+        (\textbf{yes}/partial/no)
+  \item All source code implementing new methods have comments detailing the
+        implementation, with references to the paper where each step comes from
+        (yes/\textbf{partial}/no)
+  \item If an algorithm depends on randomness, then the method used for setting
+        seeds is described in a way sufficient to allow replication of results.
+        (yes/partial/no/\textbf{NA})
+  \item This paper specifies the computing infrastructure used for running
+        experiments (hardware and software), including GPU/CPU models; amount of
+        memory; operating system; names and versions of relevant software
+        libraries and frameworks. (\textbf{yes}/partial/no)
+  \item This paper formally describes evaluation metrics used and explains the
+        motivation for choosing these metrics. (\textbf{yes}/partial/no)
+  \item This paper states the number of algorithm runs used to compute each
+        reported result. (\textbf{yes}/no)
+  \item Analysis of experiments goes beyond single-dimensional summaries of
+        performance (e.g., average; median) to include measures of variation,
+        confidence, or other distributional information. (\textbf{yes}/no)
+  \item The significance of any improvement or decrease in performance is judged
+        using appropriate statistical tests (e.g., Wilcoxon signed-rank).
+        (\textbf{yes}/partial/no)
+  \item This paper lists all final (hyper-)parameters used for each
+        model/algorithm in the paper’s experiments. (yes/partial/no/\textbf{NA})
+  \item This paper states the number and range of values tried per (hyper-)
+        parameter during development of the paper, along with the criterion used
+        for selecting the final parameter setting. (yes/partial/no/\textbf{NA})
+\end{itemize}
+
 \end{document}

### 2024-08-15 analysis/analyse.R

@@ -11,8 +11,8 @@ df <- read.csv("../results/processed/results.csv")
 df$compilation.time <- df$compilation.time / 1000
 df$inference.time <- df$inference.time / 1000
 df$time <- df$compilation.time + df$inference.time
-df$algorithm[df$algorithm == "bfs"] <- "\\textsc{Crane2-BFS}"
-df$algorithm[df$algorithm == "greedy"] <- "\\textsc{Crane2-Greedy}"
+df$algorithm[df$algorithm == "bfs"] <- "\\textsc{Gantry-BFS}"
+df$algorithm[df$algorithm == "greedy"] <- "\\textsc{Gantry-Greedy}"
 df$algorithm[df$algorithm == "fastwfomc"] <- "\\textsc{FastWFOMC}"
 df$algorithm[df$algorithm == "forclift"] <- "\\textsc{ForcLift}"
 df$sequence[df$sequence == "bijections"] <- "Bijections"

### 2025-01-11 doc/old_paper/plot.tex
First draft of the SAT version

--- 2024-08-09 doc/paper/plot.tex
@@
-% Created by tikzDevice version 0.12.6 on 2024-08-07 14:16:35
+% Created by tikzDevice version 0.12.6 on 2024-08-15 12:12:55
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.10,106.36) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.10,123.48) --
+	( 45.67,112.22) --
+	( 51.24,112.22) --
+	( 56.80,112.42) --
+	( 62.37,119.02) --
+	( 67.94,162.96);
+\definecolor{drawColor}{RGB}{117,112,179}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 40.10,106.36) --
 	( 45.67,106.36) --
@@
 	(101.34,117.90);
-\definecolor{drawColor}{RGB}{117,112,179}
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 40.10,123.48) --
-	( 45.67,112.22) --
-	( 51.24,112.22) --
-	( 56.80,112.42) --
-	( 62.37,119.02) --
-	( 67.94,162.96);
+\definecolor{fillColor}{RGB}{117,112,179}
+
+\path[fill=fillColor] ( 38.14,104.40) --
+	( 42.06,104.40) --
+	( 42.06,108.33) --
+	( 38.14,108.33) --
+	cycle;
+
+\path[fill=fillColor] ( 43.71,104.40) --
+	( 47.63,104.40) --
+	( 47.63,108.33) --
+	( 43.71,108.33) --
+	cycle;
+
+\path[fill=fillColor] ( 49.27,104.40) --
+	( 53.20,104.40) --
+	( 53.20,108.33) --
+	( 49.27,108.33) --
+	cycle;
+
+\path[fill=fillColor] ( 54.84,104.40) --
+	( 58.76,104.40) --
+	( 58.76,108.33) --
+	( 54.84,108.33) --
+	cycle;
+
+\path[fill=fillColor] ( 60.41,104.40) --
+	( 64.33,104.40) --
+	( 64.33,108.33) --
+	( 60.41,108.33) --
+	cycle;
+
+\path[fill=fillColor] ( 65.97,104.40) --
+	( 69.90,104.40) --
+	( 69.90,108.33) --
+	( 65.97,108.33) --
+	cycle;
+
+\path[fill=fillColor] ( 71.54,104.41) --
+	( 75.46,104.41) --
+	( 75.46,108.34) --
+	( 71.54,108.34) --
+	cycle;
+
+\path[fill=fillColor] ( 77.11,104.45) --
+	( 81.03,104.45) --
+	( 81.03,108.38) --
+	( 77.11,108.38) --
+	cycle;
+
+\path[fill=fillColor] ( 82.67,104.62) --
+	( 86.60,104.62) --
+	( 86.60,108.54) --
+	( 82.67,108.54) --
+	cycle;
+
+\path[fill=fillColor] ( 88.24,105.27) --
+	( 92.16,105.27) --
+	( 92.16,109.19) --
+	( 88.24,109.19) --
+	cycle;
+
+\path[fill=fillColor] ( 93.81,108.02) --
+	( 97.73,108.02) --
+	( 97.73,111.95) --
+	( 93.81,111.95) --
+	cycle;
+
+\path[fill=fillColor] ( 99.37,115.94) --
+	(103.30,115.94) --
+	(103.30,119.87) --
+	( 99.37,119.87) --
+	cycle;
 \definecolor{fillColor}{RGB}{27,158,119}
 
-\path[fill=fillColor] ( 40.10,106.36) circle (  1.96);
-
-\path[fill=fillColor] ( 45.67,106.36) circle (  1.96);
-
-\path[fill=fillColor] ( 51.24,106.36) circle (  1.96);
-
-\path[fill=fillColor] ( 56.80,106.36) circle (  1.96);
-
-\path[fill=fillColor] ( 62.37,106.36) circle (  1.96);
-
-\path[fill=fillColor] ( 67.94,106.37) circle (  1.96);
-
-\path[fill=fillColor] ( 73.50,106.38) circle (  1.96);
-
-\path[fill=fillColor] ( 79.07,106.42) circle (  1.96);
-
-\path[fill=fillColor] ( 84.64,106.58) circle (  1.96);
-
-\path[fill=fillColor] ( 90.20,107.23) circle (  1.96);
-
-\path[fill=fillColor] ( 95.77,109.99) circle (  1.96);
-
-\path[fill=fillColor] (101.34,117.90) circle (  1.96);
-\definecolor{fillColor}{RGB}{117,112,179}
-
-\path[fill=fillColor] ( 38.14,121.52) --
-	( 42.06,121.52) --
-	( 42.06,125.44) --
-	( 38.14,125.44) --
-	cycle;
-
-\path[fill=fillColor] ( 43.71,110.26) --
-	( 47.63,110.26) --
-	( 47.63,114.18) --
-	( 43.71,114.18) --
-	cycle;
-
-\path[fill=fillColor] ( 49.27,110.26) --
-	( 53.20,110.26) --
-	( 53.20,114.18) --
-	( 49.27,114.18) --
-	cycle;
-
-\path[fill=fillColor] ( 54.84,110.46) --
-	( 58.76,110.46) --
-	( 58.76,114.38) --
-	( 54.84,114.38) --
-	cycle;
-
-\path[fill=fillColor] ( 60.41,117.06) --
-	( 64.33,117.06) --
-	( 64.33,120.99) --
-	( 60.41,120.99) --
-	cycle;
-
-\path[fill=fillColor] ( 65.97,161.00) --
-	( 69.90,161.00) --
-	( 69.90,164.92) --
-	( 65.97,164.92) --
-	cycle;
+\path[fill=fillColor] ( 40.10,123.48) circle (  1.96);
+
+\path[fill=fillColor] ( 45.67,112.22) circle (  1.96);
+
+\path[fill=fillColor] ( 51.24,112.22) circle (  1.96);
+
+\path[fill=fillColor] ( 56.80,112.42) circle (  1.96);
+
+\path[fill=fillColor] ( 62.37,119.02) circle (  1.96);
+
+\path[fill=fillColor] ( 67.94,162.96) circle (  1.96);
 \definecolor{drawColor}{gray}{0.70}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (197.68, 87.62) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] (197.68,113.24) --
+	(203.25,111.85) --
+	(208.82,111.59) --
+	(214.38,111.66) --
+	(219.95,112.12) --
+	(225.52,112.27) --
+	(231.08,112.50) --
+	(236.65,116.23) --
+	(242.22,130.94) --
+	(247.78,168.51);
+\definecolor{drawColor}{RGB}{217,95,2}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (197.68, 68.42) --
+	(203.25, 63.98) --
+	(208.82, 63.98) --
+	(214.38, 63.98);
+\definecolor{drawColor}{RGB}{117,112,179}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (197.68, 87.62) --
 	(203.25, 87.61) --
@@
 	(264.48,192.33);
-\definecolor{drawColor}{RGB}{217,95,2}
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (197.68, 87.37) --
+\definecolor{drawColor}{RGB}{231,41,138}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (197.68, 87.37) --
 	(203.25, 87.36) --
@@
 	(264.48,192.33);
-\definecolor{drawColor}{RGB}{117,112,179}
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (197.68,113.24) --
-	(203.25,111.85) --
-	(208.82,111.59) --
-	(214.38,111.66) --
-	(219.95,112.12) --
-	(225.52,112.27) --
-	(231.08,112.50) --
-	(236.65,116.23) --
-	(242.22,130.94) --
-	(247.78,168.51);
-\definecolor{drawColor}{RGB}{231,41,138}
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (197.68, 68.42) --
-	(203.25, 63.98) --
-	(208.82, 63.98) --
-	(214.38, 63.98);
+\definecolor{fillColor}{RGB}{27,158,119}
+
+\path[fill=fillColor] (197.68,113.24) circle (  1.96);
+
+\path[fill=fillColor] (203.25,111.85) circle (  1.96);
+
+\path[fill=fillColor] (208.82,111.59) circle (  1.96);
+
+\path[fill=fillColor] (214.38,111.66) circle (  1.96);
+
+\path[fill=fillColor] (219.95,112.12) circle (  1.96);
+
+\path[fill=fillColor] (225.52,112.27) circle (  1.96);
+
+\path[fill=fillColor] (231.08,112.50) circle (  1.96);
+
+\path[fill=fillColor] (236.65,116.23) circle (  1.96);
+
+\path[fill=fillColor] (242.22,130.94) circle (  1.96);
+
+\path[fill=fillColor] (247.78,168.51) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.91, 87.37) -- (200.46, 87.37);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.68, 84.59) -- (197.68, 90.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.48, 87.36) -- (206.03, 87.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.25, 84.59) -- (203.25, 90.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.04, 87.36) -- (211.59, 87.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.82, 84.59) -- (208.82, 90.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.61, 87.36) -- (217.16, 87.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.38, 84.59) -- (214.38, 90.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (217.18, 87.36) -- (222.73, 87.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (219.95, 84.59) -- (219.95, 90.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (222.74, 87.36) -- (228.29, 87.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (225.52, 84.59) -- (225.52, 90.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (228.31, 87.37) -- (233.86, 87.37);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (231.08, 84.59) -- (231.08, 90.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (233.88, 87.44) -- (239.43, 87.44);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (236.65, 84.67) -- (236.65, 90.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (239.44, 88.34) -- (244.99, 88.34);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.22, 85.57) -- (242.22, 91.12);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (245.01, 97.16) -- (250.56, 97.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (247.78, 94.39) -- (247.78, 99.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (250.58,123.35) -- (256.13,123.35);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (253.35,120.57) -- (253.35,126.12);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (256.14,157.54) -- (261.69,157.54);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (258.92,154.77) -- (258.92,160.32);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.71,192.33) -- (267.26,192.33);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.48,189.56) -- (264.48,195.11);
+\definecolor{fillColor}{RGB}{217,95,2}
+
+\path[fill=fillColor] (197.68, 71.47) --
+	(200.33, 66.89) --
+	(195.04, 66.89) --
+	cycle;
+
+\path[fill=fillColor] (203.25, 67.03) --
+	(205.89, 62.45) --
+	(200.61, 62.45) --
+	cycle;
+
+\path[fill=fillColor] (208.82, 67.03) --
+	(211.46, 62.45) --
+	(206.18, 62.45) --
+	cycle;
+
+\path[fill=fillColor] (214.38, 67.03) --
+	(217.03, 62.45) --
+	(211.74, 62.45) --
+	cycle;
 \definecolor{fillColor}{RGB}{117,112,179}
 
-\path[fill=fillColor] (195.72,111.28) --
-	(199.65,111.28) --
-	(199.65,115.20) --
-	(195.72,115.20) --
-	cycle;
-
-\path[fill=fillColor] (201.29,109.89) --
-	(205.21,109.89) --
-	(205.21,113.82) --
-	(201.29,113.82) --
-	cycle;
-
-\path[fill=fillColor] (206.86,109.63) --
-	(210.78,109.63) --
-	(210.78,113.55) --
-	(206.86,113.55) --
-	cycle;
-
-\path[fill=fillColor] (212.42,109.70) --
-	(216.35,109.70) --
-	(216.35,113.62) --
-	(212.42,113.62) --
-	cycle;
-
-\path[fill=fillColor] (217.99,110.16) --
-	(221.91,110.16) --
-	(221.91,114.09) --
-	(217.99,114.09) --
-	cycle;
-
-\path[fill=fillColor] (223.56,110.31) --
-	(227.48,110.31) --
-	(227.48,114.23) --
-	(223.56,114.23) --
-	cycle;
-
-\path[fill=fillColor] (229.12,110.53) --
-	(233.05,110.53) --
-	(233.05,114.46) --
-	(229.12,114.46) --
-	cycle;
-
-\path[fill=fillColor] (234.69,114.27) --
-	(238.61,114.27) --
-	(238.61,118.20) --
-	(234.69,118.20) --
-	cycle;
-
-\path[fill=fillColor] (240.26,128.97) --
-	(244.18,128.97) --
-	(244.18,132.90) --
-	(240.26,132.90) --
-	cycle;
-
-\path[fill=fillColor] (245.82,166.55) --
-	(249.75,166.55) --
-	(249.75,170.47) --
-	(245.82,170.47) --
-	cycle;
-\definecolor{fillColor}{RGB}{217,95,2}
-
-\path[fill=fillColor] (197.68, 90.42) --
-	(200.33, 85.84) --
-	(195.04, 85.84) --
-	cycle;
-
-\path[fill=fillColor] (203.25, 90.41) --
-	(205.89, 85.84) --
-	(200.61, 85.84) --
-	cycle;
-
-\path[fill=fillColor] (208.82, 90.41) --
-	(211.46, 85.84) --
-	(206.18, 85.84) --
-	cycle;
-
-\path[fill=fillColor] (214.38, 90.41) --
-	(217.03, 85.84) --
-	(211.74, 85.84) --
-	cycle;
-
-\path[fill=fillColor] (219.95, 90.41) --
-	(222.59, 85.84) --
-	(217.31, 85.84) --
-	cycle;
-
-\path[fill=fillColor] (225.52, 90.41) --
-	(228.16, 85.84) --
-	(222.88, 85.84) --
-	cycle;
-
-\path[fill=fillColor] (231.08, 90.42) --
-	(233.73, 85.84) --
-	(228.44, 85.84) --
-	cycle;
-
-\path[fill=fillColor] (236.65, 90.49) --
-	(239.29, 85.92) --
-	(234.01, 85.92) --
-	cycle;
-
-\path[fill=fillColor] (242.22, 91.39) --
-	(244.86, 86.82) --
-	(239.57, 86.82) --
-	cycle;
-
-\path[fill=fillColor] (247.78,100.21) --
-	(250.43, 95.64) --
-	(245.14, 95.64) --
-	cycle;
-
-\path[fill=fillColor] (253.35,126.40) --
-	(255.99,121.82) --
-	(250.71,121.82) --
-	cycle;
-
-\path[fill=fillColor] (258.92,160.59) --
-	(261.56,156.02) --
-	(256.27,156.02) --
-	cycle;
-
-\path[fill=fillColor] (264.48,195.39) --
-	(267.13,190.81) --
-	(261.84,190.81) --
-	cycle;
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.91, 68.42) -- (200.46, 68.42);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.68, 65.64) -- (197.68, 71.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.48, 63.98) -- (206.03, 63.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.25, 61.20) -- (203.25, 66.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.04, 63.98) -- (211.59, 63.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.82, 61.20) -- (208.82, 66.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.61, 63.98) -- (217.16, 63.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.38, 61.20) -- (214.38, 66.75);
-\definecolor{fillColor}{RGB}{27,158,119}
-
-\path[fill=fillColor] (197.68, 87.62) circle (  1.96);
-
-\path[fill=fillColor] (203.25, 87.61) circle (  1.96);
-
-\path[fill=fillColor] (208.82, 87.61) circle (  1.96);
-
-\path[fill=fillColor] (214.38, 87.61) circle (  1.96);
-
-\path[fill=fillColor] (219.95, 87.61) circle (  1.96);
-
-\path[fill=fillColor] (225.52, 87.61) circle (  1.96);
-
-\path[fill=fillColor] (231.08, 87.62) circle (  1.96);
-
-\path[fill=fillColor] (236.65, 87.69) circle (  1.96);
-
-\path[fill=fillColor] (242.22, 88.58) circle (  1.96);
-
-\path[fill=fillColor] (247.78, 97.29) circle (  1.96);
-
-\path[fill=fillColor] (253.35,123.32) circle (  1.96);
-
-\path[fill=fillColor] (258.92,157.55) circle (  1.96);
-
-\path[fill=fillColor] (264.48,192.33) circle (  1.96);
+\path[fill=fillColor] (195.72, 85.66) --
+	(199.65, 85.66) --
+	(199.65, 89.58) --
+	(195.72, 89.58) --
+	cycle;
+
+\path[fill=fillColor] (201.29, 85.65) --
+	(205.21, 85.65) --
+	(205.21, 89.58) --
+	(201.29, 89.58) --
+	cycle;
+
+\path[fill=fillColor] (206.86, 85.65) --
+	(210.78, 85.65) --
+	(210.78, 89.58) --
+	(206.86, 89.58) --
+	cycle;
+
+\path[fill=fillColor] (212.42, 85.65) --
+	(216.35, 85.65) --
+	(216.35, 89.58) --
+	(212.42, 89.58) --
+	cycle;
+
+\path[fill=fillColor] (217.99, 85.65) --
+	(221.91, 85.65) --
+	(221.91, 89.58) --
+	(217.99, 89.58) --
+	cycle;
+
+\path[fill=fillColor] (223.56, 85.65) --
+	(227.48, 85.65) --
+	(227.48, 89.58) --
+	(223.56, 89.58) --
+	cycle;
+
+\path[fill=fillColor] (229.12, 85.66) --
+	(233.05, 85.66) --
+	(233.05, 89.58) --
+	(229.12, 89.58) --
+	cycle;
+
+\path[fill=fillColor] (234.69, 85.73) --
+	(238.61, 85.73) --
+	(238.61, 89.66) --
+	(234.69, 89.66) --
+	cycle;
+
+\path[fill=fillColor] (240.26, 86.62) --
+	(244.18, 86.62) --
+	(244.18, 90.54) --
+	(240.26, 90.54) --
+	cycle;
+
+\path[fill=fillColor] (245.82, 95.32) --
+	(249.75, 95.32) --
+	(249.75, 99.25) --
+	(245.82, 99.25) --
+	cycle;
+
+\path[fill=fillColor] (251.39,121.35) --
+	(255.31,121.35) --
+	(255.31,125.28) --
+	(251.39,125.28) --
+	cycle;
+
+\path[fill=fillColor] (256.96,155.59) --
+	(260.88,155.59) --
+	(260.88,159.51) --
+	(256.96,159.51) --
+	cycle;
+
+\path[fill=fillColor] (262.52,190.37) --
+	(266.45,190.37) --
+	(266.45,194.30) --
+	(262.52,194.30) --
+	cycle;
 \definecolor{drawColor}{gray}{0.70}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (355.27, 89.52) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] (355.27,114.65) --
+	(360.83,111.15) --
+	(366.40,111.49) --
+	(371.97,111.10) --
+	(377.53,115.68) --
+	(383.10,162.17);
+\definecolor{drawColor}{RGB}{217,95,2}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (355.27, 66.36) --
+	(360.83, 64.61) --
+	(366.40, 64.61) --
+	(371.97, 64.61) --
+	(377.53, 64.61) --
+	(383.10, 64.92) --
+	(388.67, 64.92);
+\definecolor{drawColor}{RGB}{117,112,179}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (355.27, 89.52) --
 	(360.83, 89.52) --
@@
 	(494.43,157.31);
-\definecolor{drawColor}{RGB}{217,95,2}
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (355.27, 88.43) --
+\definecolor{drawColor}{RGB}{231,41,138}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (355.27, 88.43) --
 	(360.83, 88.43) --
@@
 	(494.43,157.43);
-\definecolor{drawColor}{RGB}{117,112,179}
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (355.27,114.65) --
-	(360.83,111.15) --
-	(366.40,111.49) --
-	(371.97,111.10) --
-	(377.53,115.68) --
-	(383.10,162.17);
-\definecolor{drawColor}{RGB}{231,41,138}
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (355.27, 66.36) --
-	(360.83, 64.61) --
-	(366.40, 64.61) --
-	(371.97, 64.61) --
-	(377.53, 64.61) --
-	(383.10, 64.92) --
-	(388.67, 64.92);
+\definecolor{fillColor}{RGB}{117,112,179}
+
+\path[fill=fillColor] (353.30, 87.55) --
+	(357.23, 87.55) --
+	(357.23, 91.48) --
+	(353.30, 91.48) --
+	cycle;
+
+\path[fill=fillColor] (358.87, 87.55) --
+	(362.80, 87.55) --
+	(362.80, 91.48) --
+	(358.87, 91.48) --
+	cycle;
+
+\path[fill=fillColor] (364.44, 87.55) --
+	(368.36, 87.55) --
+	(368.36, 91.48) --
+	(364.44, 91.48) --
+	cycle;
+
+\path[fill=fillColor] (370.00, 87.55) --
+	(373.93, 87.55) --
+	(373.93, 91.48) --
+	(370.00, 91.48) --
+	cycle;
+
+\path[fill=fillColor] (375.57, 87.55) --
+	(379.50, 87.55) --
+	(379.50, 91.48) --
+	(375.57, 91.48) --
+	cycle;
+
+\path[fill=fillColor] (381.14, 87.56) --
+	(385.06, 87.56) --
+	(385.06, 91.48) --
+	(381.14, 91.48) --
+	cycle;
+
+\path[fill=fillColor] (386.70, 87.55) --
+	(390.63, 87.55) --
+	(390.63, 91.48) --
+	(386.70, 91.48) --
+	cycle;
+
+\path[fill=fillColor] (392.27, 87.55) --
+	(396.19, 87.55) --
+	(396.19, 91.48) --
+	(392.27, 91.48) --
+	cycle;
+
+\path[fill=fillColor] (397.84, 87.55) --
+	(401.76, 87.55) --
+	(401.76, 91.48) --
+	(397.84, 91.48) --
+	cycle;
+
+\path[fill=fillColor] (403.40, 87.56) --
+	(407.33, 87.56) --
+	(407.33, 91.48) --
+	(403.40, 91.48) --
+	cycle;
+
+\path[fill=fillColor] (408.97, 87.56) --
+	(412.89, 87.56) --
+	(412.89, 91.48) --
+	(408.97, 91.48) --
+	cycle;
+
+\path[fill=fillColor] (414.54, 87.56) --
+	(418.46, 87.56) --
+	(418.46, 91.48) --
+	(414.54, 91.48) --
+	cycle;
+
+\path[fill=fillColor] (420.10, 87.57) --
+	(424.03, 87.57) --
+	(424.03, 91.50) --
+	(420.10, 91.50) --
+	cycle;
+
+\path[fill=fillColor] (425.67, 87.58) --
+	(429.59, 87.58) --
+	(429.59, 91.51) --
+	(425.67, 91.51) --
+	cycle;
+
+\path[fill=fillColor] (431.24, 87.64) --
+	(435.16, 87.64) --
+	(435.16, 91.57) --
+	(431.24, 91.57) --
+	cycle;
+
+\path[fill=fillColor] (436.80, 87.75) --
+	(440.73, 87.75) --
+	(440.73, 91.67) --
+	(436.80, 91.67) --
+	cycle;
+
+\path[fill=fillColor] (442.37, 88.01) --
+	(446.29, 88.01) --
+	(446.29, 91.94) --
+	(442.37, 91.94) --
+	cycle;
+
+\path[fill=fillColor] (447.94, 88.69) --
+	(451.86, 88.69) --
+	(451.86, 92.61) --
+	(447.94, 92.61) --
+	cycle;
+
+\path[fill=fillColor] (453.50, 90.15) --
+	(457.43, 90.15) --
+	(457.43, 94.07) --
+	(453.50, 94.07) --
+	cycle;
+
+\path[fill=fillColor] (459.07, 93.51) --
+	(462.99, 93.51) --
+	(462.99, 97.43) --
+	(459.07, 97.43) --
+	cycle;
+
+\path[fill=fillColor] (464.64, 99.11) --
+	(468.56, 99.11) --
+	(468.56,103.03) --
+	(464.64,103.03) --
+	cycle;
+
+\path[fill=fillColor] (470.20,106.84) --
+	(474.13,106.84) --
+	(474.13,110.76) --
+	(470.20,110.76) --
+	cycle;
+
+\path[fill=fillColor] (475.77,117.50) --
+	(479.69,117.50) --
+	(479.69,121.43) --
+	(475.77,121.43) --
+	cycle;
+
+\path[fill=fillColor] (481.34,130.74) --
+	(485.26,130.74) --
+	(485.26,134.66) --
+	(481.34,134.66) --
+	cycle;
+
+\path[fill=fillColor] (486.90,142.61) --
+	(490.83,142.61) --
+	(490.83,146.54) --
+	(486.90,146.54) --
+	cycle;
+
+\path[fill=fillColor] (492.47,155.35) --
+	(496.39,155.35) --
+	(496.39,159.27) --
+	(492.47,159.27) --
+	cycle;
+\definecolor{fillColor}{RGB}{217,95,2}
+
+\path[fill=fillColor] (355.27, 69.41) --
+	(357.91, 64.83) --
+	(352.62, 64.83) --
+	cycle;
+
+\path[fill=fillColor] (360.83, 67.66) --
+	(363.48, 63.08) --
+	(358.19, 63.08) --
+	cycle;
+
+\path[fill=fillColor] (366.40, 67.66) --
+	(369.04, 63.08) --
+	(363.76, 63.08) --
+	cycle;
+
+\path[fill=fillColor] (371.97, 67.66) --
+	(374.61, 63.08) --
+	(369.32, 63.08) --
+	cycle;
+
+\path[fill=fillColor] (377.53, 67.66) --
+	(380.18, 63.08) --
+	(374.89, 63.08) --
+	cycle;
+
+\path[fill=fillColor] (383.10, 67.97) --
+	(385.74, 63.39) --
+	(380.46, 63.39) --
+	cycle;
+
+\path[fill=fillColor] (388.67, 67.97) --
+	(391.31, 63.39) --
+	(386.02, 63.39) --
+	cycle;
 \definecolor{fillColor}{RGB}{27,158,119}
 
-\path[fill=fillColor] (355.27, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (360.83, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (366.40, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (371.97, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (377.53, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (383.10, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (388.67, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (394.23, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (399.80, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (405.37, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (410.93, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (416.50, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (422.07, 89.53) circle (  1.96);
-
-\path[fill=fillColor] (427.63, 89.55) circle (  1.96);
-
-\path[fill=fillColor] (433.20, 89.61) circle (  1.96);
-
-\path[fill=fillColor] (438.77, 89.71) circle (  1.96);
-
-\path[fill=fillColor] (444.33, 89.97) circle (  1.96);
-
-\path[fill=fillColor] (449.90, 90.65) circle (  1.96);
-
-\path[fill=fillColor] (455.47, 92.11) circle (  1.96);
-
-\path[fill=fillColor] (461.03, 95.47) circle (  1.96);
-
-\path[fill=fillColor] (466.60,101.07) circle (  1.96);
-
-\path[fill=fillColor] (472.17,108.80) circle (  1.96);
-
-\path[fill=fillColor] (477.73,119.46) circle (  1.96);
-
-\path[fill=fillColor] (483.30,132.70) circle (  1.96);
-
-\path[fill=fillColor] (488.87,144.57) circle (  1.96);
-
-\path[fill=fillColor] (494.43,157.31) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (352.49, 66.36) -- (358.04, 66.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (355.27, 63.59) -- (355.27, 69.14);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (358.06, 64.61) -- (363.61, 64.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (360.83, 61.83) -- (360.83, 67.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (363.62, 64.61) -- (369.17, 64.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (366.40, 61.83) -- (366.40, 67.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.19, 64.61) -- (374.74, 64.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (371.97, 61.83) -- (371.97, 67.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.76, 64.61) -- (380.31, 64.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.53, 61.83) -- (377.53, 67.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (380.32, 64.92) -- (385.87, 64.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.10, 62.14) -- (383.10, 67.69);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (385.89, 64.92) -- (391.44, 64.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.67, 62.14) -- (388.67, 67.69);
-\definecolor{fillColor}{RGB}{117,112,179}
-
-\path[fill=fillColor] (353.30,112.68) --
-	(357.23,112.68) --
-	(357.23,116.61) --
-	(353.30,116.61) --
-	cycle;
-
-\path[fill=fillColor] (358.87,109.19) --
-	(362.80,109.19) --
-	(362.80,113.11) --
-	(358.87,113.11) --
-	cycle;
-
-\path[fill=fillColor] (364.44,109.53) --
-	(368.36,109.53) --
-	(368.36,113.45) --
-	(364.44,113.45) --
-	cycle;
-
-\path[fill=fillColor] (370.00,109.13) --
-	(373.93,109.13) --
-	(373.93,113.06) --
-	(370.00,113.06) --
-	cycle;
-
-\path[fill=fillColor] (375.57,113.72) --
-	(379.50,113.72) --
-	(379.50,117.64) --
-	(375.57,117.64) --
-	cycle;
-
-\path[fill=fillColor] (381.14,160.21) --
-	(385.06,160.21) --
-	(385.06,164.13) --
-	(381.14,164.13) --
-	cycle;
-\definecolor{fillColor}{RGB}{217,95,2}
-
-\path[fill=fillColor] (355.27, 91.48) --
-	(357.91, 86.90) --
-	(352.62, 86.90) --
-	cycle;
-
-\path[fill=fillColor] (360.83, 91.48) --
-	(363.48, 86.90) --
-	(358.19, 86.90) --
-	cycle;
-
-\path[fill=fillColor] (366.40, 91.48) --
-	(369.04, 86.90) --
-	(363.76, 86.90) --
-	cycle;
-
-\path[fill=fillColor] (371.97, 91.48) --
-	(374.61, 86.90) --
-	(369.32, 86.90) --
-	cycle;
-
-\path[fill=fillColor] (377.53, 91.48) --
-	(380.18, 86.90) --
-	(374.89, 86.90) --
-	cycle;
-
-\path[fill=fillColor] (383.10, 91.48) --
-	(385.74, 86.90) --
-	(380.46, 86.90) --
-	cycle;
-
-\path[fill=fillColor] (388.67, 91.48) --
-	(391.31, 86.91) --
-	(386.02, 86.91) --
-	cycle;
-
-\path[fill=fillColor] (394.23, 91.48) --
-	(396.88, 86.90) --
-	(391.59, 86.90) --
-	cycle;
-
-\path[fill=fillColor] (399.80, 91.48) --
-	(402.44, 86.90) --
-	(397.16, 86.90) --
-	cycle;
-
-\path[fill=fillColor] (405.37, 91.48) --
-	(408.01, 86.91) --
-	(402.72, 86.91) --
-	cycle;
-
-\path[fill=fillColor] (410.93, 91.48) --
-	(413.58, 86.91) --
-	(408.29, 86.91) --
-	cycle;
-
-\path[fill=fillColor] (416.50, 91.48) --
-	(419.14, 86.91) --
-	(413.86, 86.91) --
-	cycle;
-
-\path[fill=fillColor] (422.07, 91.50) --
-	(424.71, 86.92) --
-	(419.42, 86.92) --
-	cycle;
-
-\path[fill=fillColor] (427.63, 91.51) --
-	(430.27, 86.93) --
-	(424.99, 86.93) --
-	cycle;
-
-\path[fill=fillColor] (433.20, 91.57) --
-	(435.84, 86.99) --
-	(430.56, 86.99) --
-	cycle;
-
-\path[fill=fillColor] (438.77, 91.69) --
-	(441.41, 87.11) --
-	(436.12, 87.11) --
-	cycle;
-
-\path[fill=fillColor] (444.33, 91.97) --
-	(446.97, 87.39) --
-	(441.69, 87.39) --
-	cycle;
-
-\path[fill=fillColor] (449.90, 92.68) --
-	(452.54, 88.10) --
-	(447.26, 88.10) --
-	cycle;
-
-\path[fill=fillColor] (455.47, 94.21) --
-	(458.11, 89.64) --
-	(452.82, 89.64) --
-	cycle;
-
-\path[fill=fillColor] (461.03, 97.53) --
-	(463.67, 92.95) --
-	(458.39, 92.95) --
-	cycle;
-
-\path[fill=fillColor] (466.60,103.50) --
-	(469.24, 98.92) --
-	(463.96, 98.92) --
-	cycle;
-
-\path[fill=fillColor] (472.17,111.34) --
-	(474.81,106.76) --
-	(469.52,106.76) --
-	cycle;
-
-\path[fill=fillColor] (477.73,122.19) --
-	(480.37,117.61) --
-	(475.09,117.61) --
-	cycle;
-
-\path[fill=fillColor] (483.30,135.43) --
-	(485.94,130.86) --
-	(480.66,130.86) --
-	cycle;
-
-\path[fill=fillColor] (488.87,147.51) --
-	(491.51,142.93) --
-	(486.22,142.93) --
-	cycle;
-
-\path[fill=fillColor] (494.43,160.48) --
-	(497.07,155.91) --
-	(491.79,155.91) --
-	cycle;
+\path[fill=fillColor] (355.27,114.65) circle (  1.96);
+
+\path[fill=fillColor] (360.83,111.15) circle (  1.96);
+
+\path[fill=fillColor] (366.40,111.49) circle (  1.96);
+
+\path[fill=fillColor] (371.97,111.10) circle (  1.96);
+
+\path[fill=fillColor] (377.53,115.68) circle (  1.96);
+
+\path[fill=fillColor] (383.10,162.17) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (352.49, 88.43) -- (358.04, 88.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (355.27, 85.65) -- (355.27, 91.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (358.06, 88.43) -- (363.61, 88.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (360.83, 85.65) -- (360.83, 91.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (363.62, 88.43) -- (369.17, 88.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (366.40, 85.65) -- (366.40, 91.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.19, 88.43) -- (374.74, 88.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (371.97, 85.65) -- (371.97, 91.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.76, 88.43) -- (380.31, 88.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.53, 85.65) -- (377.53, 91.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (380.32, 88.43) -- (385.87, 88.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.10, 85.65) -- (383.10, 91.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (385.89, 88.43) -- (391.44, 88.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.67, 85.66) -- (388.67, 91.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (391.46, 88.43) -- (397.01, 88.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (394.23, 85.65) -- (394.23, 91.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (397.02, 88.43) -- (402.57, 88.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (399.80, 85.65) -- (399.80, 91.20);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (402.59, 88.43) -- (408.14, 88.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (405.37, 85.66) -- (405.37, 91.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (408.16, 88.43) -- (413.71, 88.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (410.93, 85.66) -- (410.93, 91.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (413.72, 88.43) -- (419.27, 88.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (416.50, 85.66) -- (416.50, 91.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (419.29, 88.44) -- (424.84, 88.44);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (422.07, 85.67) -- (422.07, 91.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (424.86, 88.46) -- (430.41, 88.46);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (427.63, 85.68) -- (427.63, 91.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (430.42, 88.51) -- (435.97, 88.51);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (433.20, 85.74) -- (433.20, 91.29);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (435.99, 88.64) -- (441.54, 88.64);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (438.77, 85.86) -- (438.77, 91.41);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (441.56, 88.92) -- (447.11, 88.92);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (444.33, 86.14) -- (444.33, 91.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (447.12, 89.63) -- (452.67, 89.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (449.90, 86.85) -- (449.90, 92.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (452.69, 91.16) -- (458.24, 91.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (455.47, 88.39) -- (455.47, 93.94);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (458.26, 94.48) -- (463.81, 94.48);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (461.03, 91.70) -- (461.03, 97.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (463.82,100.45) -- (469.37,100.45);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (466.60, 97.67) -- (466.60,103.22);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (469.39,108.29) -- (474.94,108.29);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (472.17,105.51) -- (472.17,111.06);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (474.96,119.14) -- (480.51,119.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.73,116.36) -- (477.73,121.91);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (480.52,132.38) -- (486.07,132.38);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (483.30,129.61) -- (483.30,135.16);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (486.09,144.46) -- (491.64,144.46);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (488.87,141.68) -- (488.87,147.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (491.66,157.43) -- (497.21,157.43);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (494.43,154.66) -- (494.43,160.21);
 \definecolor{drawColor}{gray}{0.70}
@@
 
-\path[fill=fillColor] (124.58,  4.50) rectangle (409.95, 27.95);
+\path[fill=fillColor] (124.07,  4.50) rectangle (410.47, 27.95);
 \end{scope}
@@
 
-\path[fill=fillColor] (133.58,  9.00) rectangle (148.04, 23.45);
+\path[fill=fillColor] (133.07,  9.00) rectangle (147.52, 23.45);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (135.03, 16.23) -- (146.59, 16.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (134.51, 16.23) -- (146.08, 16.23);
 \end{scope}
@@
 
-\path[fill=fillColor] (140.81, 16.23) circle (  1.96);
+\path[fill=fillColor] (140.29, 16.23) circle (  1.96);
 \end{scope}
@@
 
-\path[fill=fillColor] (201.65,  9.00) rectangle (216.10, 23.45);
+\path[fill=fillColor] (204.51,  9.00) rectangle (218.96, 23.45);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (203.10, 16.23) -- (214.66, 16.23);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (205.95, 16.23) -- (217.52, 16.23);
 \end{scope}
@@
 
-\path[fill=fillColor] (208.88, 19.28) --
-	(211.52, 14.70) --
-	(206.24, 14.70) --
+\path[fill=fillColor] (211.73, 19.28) --
+	(214.38, 14.70) --
+	(209.09, 14.70) --
 	cycle;
@@
 
-\path[fill=fillColor] (281.98,  9.00) rectangle (296.43, 23.45);
+\path[fill=fillColor] (261.04,  9.00) rectangle (275.49, 23.45);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (283.42, 16.23) -- (294.99, 16.23);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (262.49, 16.23) -- (274.05, 16.23);
 \end{scope}
@@
 
-\path[fill=fillColor] (287.24, 14.26) --
-	(291.17, 14.26) --
-	(291.17, 18.19) --
-	(287.24, 18.19) --
+\path[fill=fillColor] (266.30, 14.26) --
+	(270.23, 14.26) --
+	(270.23, 18.19) --
+	(266.30, 18.19) --
 	cycle;
@@
 
-\path[fill=fillColor] (353.42,  9.00) rectangle (367.87, 23.45);
+\path[fill=fillColor] (329.62,  9.00) rectangle (344.08, 23.45);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (354.86, 16.23) -- (366.43, 16.23);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (331.07, 16.23) -- (342.63, 16.23);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (357.87, 16.23) -- (363.42, 16.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (360.65, 13.45) -- (360.65, 19.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.08, 16.23) -- (339.62, 16.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (336.85, 13.45) -- (336.85, 19.00);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (152.54, 13.75) {\textsc{Crane2-BFS}};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (152.02, 13.75) {\textsc{FastWFOMC}};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (220.60, 13.75) {\textsc{Crane2-Greedy}};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (223.46, 13.75) {\textsc{ForcLift}};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (300.93, 13.75) {\textsc{FastWFOMC}};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (279.99, 13.75) {\textsc{Gantry-BFS}};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (372.37, 13.75) {\textsc{ForcLift}};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (348.58, 13.75) {\textsc{Gantry-Greedy}};
 \end{scope}

### 2025-01-11 doc/old_paper/technical_appendix.tex
First draft of the SAT version

--- 2024-04-29 doc/paper.tex
@@
-\documentclass{article}
-\pdfpagewidth=8.5in
-\pdfpageheight=11in
+%File: anonymous-submission-latex-2025.tex
+\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
+\usepackage[submission]{aaai25}  % DO NOT CHANGE THIS
+\usepackage{times}  % DO NOT CHANGE THIS
+\usepackage{helvet}  % DO NOT CHANGE THIS
+\usepackage{courier}  % DO NOT CHANGE THIS
+\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
+\usepackage{graphicx} % DO NOT CHANGE THIS
+\urlstyle{rm} % DO NOT CHANGE THIS
+\def\UrlFont{\rm}  % DO NOT CHANGE THIS
+\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
+\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
+\frenchspacing  % DO NOT CHANGE THIS
+\setlength{\pdfpagewidth}{8.5in} % DO NOT CHANGE THIS
+\setlength{\pdfpageheight}{11in} % DO NOT CHANGE THIS
 
-\usepackage{kr}
-
-\usepackage{times}
-\usepackage{soul}
-\usepackage{url}
-\usepackage[hidelinks]{hyperref}
-\usepackage[utf8]{inputenc}
-\usepackage[small]{caption}
-\usepackage{graphicx}
+\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
+\usepackage{amsfonts}
 \usepackage{amsmath}
 \usepackage{amsthm}
-\usepackage{booktabs}
-\urlstyle{same}
+\usepackage[capitalize,noabbrev]{cleveref}
 
-\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-\usepackage[capitalize,noabbrev]{cleveref}
-\usepackage{microtype}
-\usepackage{mathtools}
-\usepackage{forest}
-\usepackage{siunitx}
-\usepackage{amsfonts}
-\usepackage{pifont}
-\usepackage[inline]{enumitem}
+% Keep the \pdfinfo as shown here. There's no need
+% for you to add the /Title and /Author tags.
+\pdfinfo{
+/TemplateVersion (2025.1)
+}
 
-\usetikzlibrary{arrows.meta}
-\usetikzlibrary{positioning}
+\setcounter{secnumdepth}{2} %May be changed to 1 or 2 if section numbers are desired.
+
+\SetKwFunction{CompileWithBaseCases}{CompileWithBaseCases}
+\SetKwFunction{FindBaseCases}{FindBaseCases}
+
+\newcommand{\Cranetwo}{\textsc{Crane2}}
+\newcommand{\expr}{\mathtt{expr}}
 
 \newtheorem{theorem}{Theorem}
+\newtheorem{assumption}{Assumption}
+\newtheorem{corollary}{Corollary}
+\newtheorem{fact}{Observation}
 \newtheorem{lemma}{Lemma}
-\newtheorem{fact}{Observation}
-\newtheorem{corollary}{Corollary}
-\newtheorem{assumption}{Assumption}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
-\theoremstyle{remark}
-\newtheorem*{remark}{Remark}
 
-\pdfinfo{
-/TemplateVersion (KR.2022.0, KR.2023.0, KR.2024.0)
-}
-
-\forestset{
-  sn edges/.style={for tree={edge={-Latex}}}
-}
-
-\newcommand{\crefrangeconjunction}{--}
-
-\crefname{line}{line}{lines}
-
-\crefname{fact}{Observation}{Observations}
-\crefname{assumption}{Assumption}{Assumptions}
-
-\crefalias{enumi}{type}
-\crefname{type}{Type}{Types}
-\creflabelformat{type}{#2\textup{#1}#3}
-
-\crefalias{enumi}{step}
-\crefname{step}{Step}{Steps}
-\creflabelformat{step}{#2\textup{#1}#3}
-
-\crefalias{clause}{equation}
-\crefname{clause}{Clause}{Clauses}
-\creflabelformat{clause}{#2\textup{(#1)}#3}
-
-\crefalias{formula}{equation}
-\crefname{formula}{Formula}{Formulas}
-\creflabelformat{formula}{#2\textup{(#1)}#3}
-
-\DeclareMathOperator{\CR}{CR}
-\DeclareMathOperator{\DR}{DR}
-\DeclareMathOperator{\Reff}{Ref}
-
-\DeclareMathOperator{\Doms}{Doms}
-
-\newcommand{\cmark}{\ding{51}}
-\newcommand{\xmark}{\ding{55}}
-
-\newcommand{\expr}{\mathtt{expr}}
-\newcommand{\Ctwo}{$\mathsf{C}^{2}$}
-\newcommand{\FO}{$\mathsf{FO}$}
-\newcommand{\UFO}{$\mathsf{UFO}^{2} + \mathsf{EQ}$}
-
-\newcommand{\Cranetwo}{\textsc{Crane2}}
-\newcommand{\Cranebfs}{\textsc{Crane2-BFS}}
-\newcommand{\Cranegreedy}{\textsc{Crane2-Greedy}}
-
-\SetKwFunction{CompileWithBaseCases}{CompileWithBaseCases}
-\SetKwFunction{Compile}{Compile}
-\SetKwFunction{Propagate}{Propagate}
-\SetKwFunction{FindBaseCases}{FindBaseCases}
-\SetKwFunction{Simplify}{Simplify}
-
-\title{Towards Practical First-Order Model Counting}
-
-\author{%
-  Ananth K. Kidambi$^1$\footnote{The first and second authors contributed equally and were affiliated with the National University of Singapore during the completion of this work.}\and
-Guramrit Singh$^1$\and
-Paulius Dilkas$^2$\and
-Kuldeep S. Meel$^3$ \\
-\affiliations
-$^1$Indian Institute of Technology Bombay, Mumbai, India\\
-$^2$National University of Singapore, Singapore, Singapore\\
-$^3$University of Toronto, Toronto, Canada\\
-\emails
-210051002@iitb.ac.in,
-guramrit@iitb.ac.in,
-paulius.dilkas@nus.edu.sg,
-meel@cs.toronto.edu
-}
+\title{Towards Practical First-Order Model Counting: Technical Appendix}
+\author{Anonymous Submission}
+\affiliations{}
 
@@
 
-\begin{abstract}
-  First-order model counting (FOMC) is the problem of counting the number of
-  models of a sentence in first-order logic. Recently, a new algorithm for FOMC
-  was proposed that, instead of simply providing the final count, generates
-  definitions of (possibly recursive) functions, which can be evaluated with
-  different arguments to compute the model count for any domain size. However,
-  the algorithm did not include base cases in the recursive definitions. This
-  work makes three contributions. First, we demonstrate how to construct
-  function definitions that include base cases by modifying the logical formulas
-  used in the FOMC algorithm. Second, we extend the well-known circuit
-  modification technique in knowledge compilation, known as smoothing, to work
-  with the formulas corresponding to base cases and the recently proposed node
-  types, such as domain recursion and constraint removal. Third, we introduce a
-  compilation algorithm that transforms the function definitions into C++ code,
-  equipped with arbitrary-precision arithmetic. These additions allow the new
-  FOMC algorithm to scale to domain sizes over \num{9000} times larger than the
-  current state of the art, as demonstrated through experimental results.
-\end{abstract}
+\section{The Proof of Theorem 1}
 
-\section{Introduction}
-
-% 1. What is the problem?
-
-\emph{First-order model counting} is the task of counting the number of models
-of a sentence in first-order logic over some given domain(s). The (symmetric)
-weighted variant of this problem, known as WFOMC, seeks to calculate the sum of
-model weights. In WFOMC, the weight of a model is determined by predicate
-weights~\cite{DBLP:conf/ijcai/BroeckTMDR11}. WFOMC is a key approach to
-\emph{lifted (probabilistic) inference}, which aims to compute probabilities
-more efficiently by leveraging symmetries inherent in the problem
-description~\cite{DBLP:conf/ecai/Kersting12}.
-
-% 2. Why is it interesting and important?
-
-Lifted inference is an active area of research, with recent work in domains such
-as constraint satisfaction problems~\cite{DBLP:journals/jair/TotisDRK23} and
-probabilistic answer set programming~\cite{DBLP:journals/ijar/AzzoliniR23}.
-WFOMC has been used for inference on probabilistic
-databases~\cite{DBLP:journals/debu/GribkoffSB14} and probabilistic logic
-programs~\cite{DBLP:journals/ijar/RiguzziBZCL17}. By considering domains of
-increasing sizes, the model count of a formula can be seen as an integer
-sequence. WFOMC algorithms have been utilised for discovering new
-sequences~\cite{DBLP:conf/ijcai/SvatosJT0K23} as well as
-conjecturing~\cite{DBLP:conf/ilp/BarvinekB0ZK21} and
-constructing~\cite{DBLP:conf/kr/DilkasB23} recurrence relations and other
-recursive structures that describe these sequences. Additionally, WFOMC
-algorithms have been extended to perform
-\emph{sampling}~\cite{DBLP:conf/aaai/WangB0K22,DBLP:conf/lics/WangP0K23}.
-
-% 3. Why is it hard? (E.g., why do naive approaches fail?)
-
-The complexity of WFOMC is typically characterised in terms of \emph{data
-  complexity}. This involves fixing the formula and determining whether an
-algorithm exists that can compute the WFOMC in time polynomial with respect to
-the domain size(s). If such an algorithm exists, the formula is called
-\emph{liftable}~\cite{DBLP:conf/starai/JaegerB12}. Beame et
-al.~\shortcite{DBLP:conf/pods/BeameBGS15} demonstrated the existence of an
-unliftable formula with three variables. It is also known that all formulas with
-up to two variables are
-liftable~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/kr/BroeckMD14}. The liftable
-fragment of formulas with two variables has been expanded with various
-axioms~\cite{DBLP:conf/aaai/TothK23,DBLP:journals/ai/BremenK23}, counting
-quantifiers~\cite{DBLP:journals/jair/Kuzelka21} and in other
-ways~\cite{DBLP:conf/nips/KazemiKBP16}.
-
-% 4. Why hasn't it been solved before? (Or, what's wrong with previous proposed
-% solutions? How does mine differ?)
-
-There are various WFOMC algorithms with different underlying principles. Perhaps
-the most prominent class of WFOMC algorithms is based on \emph{first-order
-  knowledge compilation}. In this approach, the formula is compiled into a
-representation (such as a circuit or graph) by iteratively applying
-\emph{compilation rules}. This representation can then be used to compute the
-WFOMC for any combination of domain sizes (or weights). Algorithms in this class
-include \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} and its recent
-extension \textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23}. The former compiles
-formulas into circuits, while the latter compiles them first to
-\emph{first-order computational graphs} (FCGs) and then to (algebraic)
-equations. Another WFOMC algorithm,
-\textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21}, is based on cell enumeration.
-Other algorithms utilise local search~\cite{DBLP:journals/pvldb/NiuRDS11},
-junction trees~\cite{DBLP:conf/aaai/VenugopalSG15}, Monte Carlo
-sampling~\cite{DBLP:journals/cacm/GogateD16}, and anytime approximation via
-upper/lower bound construction~\cite{DBLP:conf/ijcai/BremenK20}.
-
-% 5. What are the key components of my approach and results? Also include any
-% specific limitations.
-
-The recently proposed \textsc{Crane} algorithm, while capable of handling
-formulas beyond the reach of \textsc{ForcLift}, was incomplete as it could only
-construct function definitions, which would then need to be evaluated to compute
-the WFOMC.\@ Additionally, recursive functions were presented without base
-cases. In this work, we introduce \Cranetwo{}, an extension of \textsc{Crane}
-that addresses these two weaknesses.
-
-\begin{figure*}[t]
-  \centering
-  \begin{tikzpicture}
-    \node at (-1, 0) (formula) {$\phi$};
-    \node[draw,rounded rectangle] at (3, 0) (compilewithbasecases) {\CompileWithBaseCases};
-    \node[draw,rounded rectangle] at (9, 0) (compilation) {Compile to C++};
-
-    \node[draw,rounded rectangle,dashed] at (12, 0) (cpp) {C++ code};
-    \node at (12, -1) (sizes) {Domain sizes};
-
-    \node at (15, 0) (count) {Model count};
-
-    \node[draw,rounded rectangle] at (3, -2) (findbasecases) {\FindBaseCases};
-    \node[draw,rounded rectangle,left = 0.1cm of findbasecases] (crane) {\Compile};
-    \node[draw,rounded rectangle,right = 0.1cm of findbasecases] (propagate) {\Propagate};
-    \node[draw,rounded rectangle,right = 0.1cm of propagate] (simplify) {\Simplify};
-
-    \node[draw,fit={(compilewithbasecases) (compilation) (crane) (findbasecases) (propagate)},inner ysep=7pt,yshift=5pt] {};
-    \node at (0.2, 0.5) {\Cranetwo};
-
-    \draw[-Latex] (formula) -- (compilewithbasecases);
-    \draw[-Latex] (compilewithbasecases) -- node[above] {$\mathcal{E}$} (compilation);
-    \draw[-Latex] (compilation) -- (cpp);
-    \draw[-Latex] (sizes) -- (cpp);
-    \draw[-Latex] (cpp) -- (count);
-
-    \draw[-Latex,dashed] (compilewithbasecases) -- node[midway,left] {uses} (crane);
-    \draw[-Latex,dashed] (compilewithbasecases) -- node[midway,left] {uses} (findbasecases);
-    \draw[-Latex,dashed] (compilewithbasecases) -- node[midway,left] {uses} (propagate);
-    \draw[-Latex,dashed] (compilewithbasecases) -- node[midway,right] {uses} (simplify);
-  \end{tikzpicture}
-  \caption[]{The outline of using \Cranetwo{} to compute the model count of a formula $\phi$.
-First, the formula is compiled into a set of equations, which are then used to create a C++ program.
-This program can be executed with different command line arguments to calculate the model count of $\phi$ for different domain sizes.
-To accomplish this, the \CompileWithBaseCases function employs several components:
-    \begin{enumerate*}[label=(\roman*)]
-      \item the knowledge compilation algorithm of \textsc{Crane}, referred to as \Compile,
-      \item a procedure called \FindBaseCases, which identifies a sufficient set of base cases,
-      \item a procedure called \Propagate, which constructs a formula corresponding to a given base case, and
-      \item algebraic simplification techniques (denoted as \Simplify).
-    \end{enumerate*}
-  }\label{fig:overview}
-\end{figure*}
-
-\Cref{fig:overview} outlines the workflow of the new algorithm. In
-\cref{sec:main}, we describe how \CompileWithBaseCases finds the base cases for
-recursive functions by:
-\begin{enumerate*}[label=(\roman*)]
-  \item identifying a sufficient set of base cases for each function,
-  \item constructing formulas corresponding to these base cases,
-  and\label[step]{step2}
-  \item recursing on these new formulas.
-\end{enumerate*}
-Then, \cref{sec:smoothing} explains post-processing techniques for FCGs and the
-formulas from \cref{step2} above required to preserve the correct model count.
-Next, \cref{sec:cpp} elucidates how function definitions encoding a solution to
-a WFOMC problem are compiled into C++ programs.\footnote{The possibility of
-  compiling WFOMC solutions to C++ programs has been previously
-  considered~\cite{DBLP:conf/kr/KazemiP16}. However, the extent of formulas that
-  could be handled was limited.} Finally, \cref{sec:experiments} presents two
-experiments comparing \Cranetwo{} with other state-of-the-art WFOMC algorithms.
-
-\section{Preliminaries}
-
-In \cref{sec:logic}, we provide a summary of the basic principles of first-order
-logic. Then, in \cref{sec:threelogics}, we formally define WFOMC and discuss the
-distinctions between three variations of first-order logic that are utilised for
-WFOMC.\@ Finally, in \cref{sec:algebra}, we introduce the terminology used to
-describe the output of the original \textsc{Crane} algorithm, i.e., functions
-and equations that define them.
-
-We use $\mathbb{N}_{0}$ to represent the set of non-negative integers. In both
-algebra and logic, we write $S\sigma$ to denote the application of a
-\emph{substitution} $\sigma$ to an expression $S$, where
-$\sigma = [x_{1} \mapsto y_{1}, x_{2} \mapsto y_{2}, \dots, x_{n} \mapsto y_{n}]$
-signifies the replacement of all instances of $x_{i}$ with $y_{i}$ for all
-$i = 1, \dots, n$.
-
-\subsection{First-Order Logic}\label{sec:logic}
-
-In this section, we will review the basic concepts of first-order logic as they
-are used in first-order knowledge compilation algorithms. There are two key
-differences between the logic used within such algorithms and the logic
-supported as input. First, Skolemization~\cite{DBLP:conf/kr/BroeckMD14} is
-employed to eliminate existential quantifiers by introducing additional
-predicates. Second, the input formula is rewritten as a conjunction of clauses,
-each of which is in \emph{prenex normal form}~\cite{hinman2018fundamentals}.
-
-A \emph{formula} is a conjunction of clauses. A \emph{clause} is of the form
-$\forall x_{1} \in \Delta_{1}\text{.}\forall x_{2} \in \Delta_{2}\dots\text{
-}\forall x_{n} \in \Delta_{n}\text{.}\phi(x_{1}, x_{2}, \dots, x_{n})$, where
-$\phi$ is a disjunction of literals that only contain variables
-$x_{1}, \dots, x_{n}$ (and any constants). We say that a clause is a
-\emph{(positive) unit clause} if
-\begin{enumerate*}[label=(\roman*)]
-  \item there is only one literal with a predicate, and
-  \item it is a positive literal.
-\end{enumerate*}
-A \emph{literal} is either an atom (i.e., a \emph{positive} literal) or its
-negation (i.e., a \emph{negative} literal). An \emph{atom} is either
-\begin{enumerate*}[label=(\roman*)]
-  \item $P(t_{1}, \dots, t_{m})$ for some predicate $P$ and terms
-  $t_{1}, \dots, t_{m}$ (written as $P(\mathbf{t})$ for short) or
-  \item $x=y$ for some terms $x$ and $y$.
-\end{enumerate*}
-An atom is \emph{ground} if it contains no variables, i.e., only constants. The
-\emph{arity} of a predicate is the number of arguments it takes, i.e., $m$ in
-the case of predicate $P$ mentioned above. When we want to denote a predicate
-together with its arity, we write $P/m$. A \emph{term} is either a variable or a
-constant. Throughout the paper, we will use set-theoretic notation, interpreting
-a formula as a set of clauses and a clause as a set of literals. Moreover, for
-readability, clauses written on separate lines are implicitly conjoined.
-
-\subsection{WFOMC Algorithms and Their Logics}\label{sec:threelogics}
-
-\begin{table*}[t]
-  \centering
-  \begin{tabular}{llclll}
-    \toprule
-    Logic & Sorts & Constants & Variables & Quantifiers & Additional atoms\\
-    \midrule
-    \FO & one or more & \cmark & unlimited & $\forall$, $\exists$ & $x = y$\\
-    \Ctwo & one & \xmark & two & $\forall$, $\exists$, $\exists^{= k}$, $\exists^{\le k}$, $\exists^{\ge k}$ & ---\\
-    \UFO & one & \xmark & two & $\forall$ & $|P| = m$\\
-    \bottomrule
-  \end{tabular}
-  \caption[]{Comparison of three logics used in WFOMC based on the following aspects:
-    \begin{enumerate*}[label=(\roman*)]
-      \item number of sorts,
-      \item support for constants,
-      \item maximum number of variables,
-      \item supported quantifiers, and
-      \item supported atoms in addition to those of the form $P(\mathbf{t})$ for a predicate $P/n$ and $n$-tuple of terms $\mathbf{t}$.
-    \end{enumerate*}
-    Here:
-    \begin{enumerate*}[label=(\roman*)]
-      \item $k$ and $m$ are non-negative integers, with the latter depending on the domain size,
-      \item $P$ represents a predicate, and
-      \item $x$ and $y$ are terms.
-    \end{enumerate*}
-  }\label{tbl:logics}
-\end{table*}
-
-In \cref{tbl:logics}, we outline the differences among three first-order logics
-commonly used in WFOMC:
-\begin{enumerate*}[label=(\roman*)]
-  \item \FO{} is the input format for
-  \textsc{ForcLift}\footnote{\url{https://github.com/UCLA-StarAI/Forclift}} and
-  its extensions
-  \textsc{Crane}\footnote{\url{https://doi.org/10.5281/zenodo.8004077}} and
-  \Cranetwo{};
-  \item \Ctwo{} is often used in the literature on \textsc{FastWFOMC} and
-  related
-  methods~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22};
-  \item \UFO{} is the input format supported by a private version of
-  \textsc{FastWFOMC} obtained directly from the authors.
-\end{enumerate*}
-Note that the publicly available
-version\footnote{\url{https://comp.nus.edu.sg/~tvanbr/software/fastwfomc.tar.gz}}
-of \textsc{FastWFOMC} does not support any cardinality constraints. The notation
-we use to refer to each logic is standard in the case of \Ctwo{}, new in the
-case of \UFO{}, and redefined to be more specific in the case of \FO{}. All
-three logics are function-free, and domains are always assumed to be finite.
-
-In \FO{}, each term is assigned to a \emph{sort}, and each predicate $P/n$ is
-assigned to a sequence of $n$ sorts. Each sort has its corresponding domain.
-Most of these assignments to sorts are typically left implicit and can be
-reconstructed from the quantifiers. For example, $\forall x,y \in \Delta\text{.
-}P(x, y)$ implies that variables $x$ and $y$ have the same sort. On the other
-hand, $\forall x \in \Delta\text{. }\forall y \in \Gamma\text{. } P(x, y)$
-implies that $x$ and $y$ have different sorts, and it would be improper to
-write, for example, $\forall x \in \Delta\text{. }\forall y \in \Gamma\text{.
-} P(x, y) \lor x = y$. \FO{} is also the only logic to support constants,
-formulas with more than two variables, and the equality predicate.
-
-\begin{remark}
-  In the case of \textsc{ForcLift} and its extensions, support for a formula as
-  valid input does not imply that the algorithm can compile the formula into a
-  circuit or graph suitable for lifted model counting. However, it is known that
-  \textsc{ForcLift} compilation is guaranteed to succeed on any \FO{} formula
-  without constants and with at most two
-  variables~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/kr/BroeckMD14}.
-\end{remark}
-
-\Ctwo{} and \UFO{} are single-sorted (i.e., all variables are quantified over
-the same domain) and only include formulas with at most two variables and no
-constants. Unlike \UFO{}, \Ctwo{} supports existential quantifiers, including
-\emph{counting quantifiers}. For example, $\exists^{=1} x\text{. }\phi(x)$ means
-that there exists \emph{exactly one} $x$ such that $\phi(x)$, and
-$\exists^{\le 2} x\text{. }\phi(x)$ means that there exist \emph{at most two}
-such $x$. The advantage \UFO{} brings over \Ctwo{} is the support for
-\emph{(equality) cardinality constraints}. For example, $|P| = 3$ constrains all
-models to have \emph{precisely three positive literals with the predicate $P$}.
-
-\begin{definition}[Model]\label{def:model}
-  Let $\phi$ be a formula in \FO{}. For each predicate $P/n$ in $\phi$, let
-  ${(\Delta_{i}^{P})}_{i=1}^{n}$ be a list of the corresponding domains (which
-  may not be distinct). Let $\sigma$ be a map from the domains of $\phi$ to
-  their interpretations as sets, satisfying the following conditions:
-  \begin{enumerate*}[label=(\roman*)]
-    \item the sets are pairwise disjoint, and
-    \item the constants in $\phi$ are included in the corresponding domains.
-  \end{enumerate*}
-  Then a \emph{structure} of $\phi$ (with respect to $\sigma$) is a set $M$ of
-  ground literals defined by adding either $P(\mathbf{t})$ or
-  $\neg P(\mathbf{t})$ for every predicate $P/n$ in $\phi$ and $n$-tuple
-  $\mathbf{t} \in \prod_{i=1}^{n} \sigma(\Delta_{i}^{P})$. A structure is a
-  \emph{model} if it satisfies $\phi$.
-\end{definition}
-
-\begin{definition}[WFOMC~\cite{DBLP:conf/ijcai/BroeckTMDR11}]
-  Continuing from \cref{def:model}, for each predicate $P$ in $\phi$, let
-  $w^{+}(P)$ and $w^{-}(P)$ be its \emph{weights} in $\mathbb{Q}$. Unless
-  specified otherwise, we assume all weights are equal to one. The
-  \emph{(symmetric) weighted first-order model count} (WFOMC) of $\phi$ (with
-  respect to $\sigma$, $w^{+}$, and $w^{-}$) is:
-  \[
-    \sum_{M \models \phi} \prod_{P(\mathbf{t}) \in M} w^{+}(P) \prod_{\neg P(\mathbf{t}) \in M} w^{-}(P),
-  \]
-  where the sum is over all models of $\phi$.
-\end{definition}
-
-\begin{example}[Counting functions]\label{example:functions}
-  To define predicate $P$ as an endofunction on $\Delta$, in \Ctwo{} one would
-  write $\forall x \in \Delta\text{. }\exists^{=1} y \in \Delta\text{.
-  }P(x, y)$. In \UFO{}, the same could be written as
-  \begin{equation}\label[formula]{eq:functions1}
-    \begin{gathered}
-      \forall x, y \in \Delta\text{. }S(x) \lor \neg P(x, y)\\
-      |P| = |\Delta|,
-    \end{gathered}
-  \end{equation}
-  where $w^{-}(S) = -1$. Although \cref{eq:functions1} has more models compared
-  to its counterpart in \Ctwo{}, the weight function makes the \emph{weighted}
-  model count of \cref{eq:functions1} equal to the number of endofunctions on
-  $\Delta$.
-
-  Equivalently, in \FO{} we would write
-  \begin{equation}\label[formula]{eq:fo}
-    \begin{gathered}
-      \forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }P(x, y)\\
-      \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z.
-    \end{gathered}
-  \end{equation}
-  The first clause asserts that each $x$ must have at least one corresponding
-  $y$, while the second statement adds the condition that if $x$ is mapped to
-  both $y$ and $z$, then $y$ must equal $z$. It is important to note that
-  \cref{eq:fo} is written with two domains instead of just one. However, we can
-  still determine the number of endofunctions by assuming that the sizes of
-  $\Gamma$ and $\Delta$ are equal. This formulation, as observed by Dilkas and
-  Belle~\shortcite{DBLP:conf/kr/DilkasB23}, can prove beneficial in enabling
-  first-order knowledge compilation algorithms to find efficient solutions.
-\end{example}
-
-\subsection{Algebra}\label{sec:algebra}
-
-We write $\expr{}$ to represent an arbitrary algebraic expression. It is
-important to note that some terms have different meanings in algebra compared to
-logic. In algebra, a \emph{constant} refers to a non-negative integer. Likewise,
-a \emph{variable} can either be a parameter of a function or a variable
-introduced through summation, such as $i$ in the expression
-$\sum_{i=1}^{n} \expr$. A (function) \emph{signature} is
-$f(x_{1}, \dots, x_{n})$ (or $f(\mathbf{x})$ for short), where $f$ represents an
-$n$-ary function, and each $x_{i}$ represents a variable. An \emph{equation} is
-$f(\mathbf{x}) = \expr{}$, with $f(\mathbf{x})$ representing a signature.
-
-\begin{definition}[Base case]\label{def:basecase}
-  Let $f(\mathbf{x})$ be a function call where each $x_{i}$ is either a constant
-  or a variable (note that signatures are included in this definition). Then
-  function call $f(\mathbf{y})$ is considered a \emph{base case} of
-  $f(\mathbf{x})$ if $f(\mathbf{y}) = f(\mathbf{x})\sigma$, where $\sigma$ is a
-  substitution that replaces one or more $x_{i}$ with a constant.
-\end{definition}
-
-\section{Completing the Definitions of Recursive Functions}\label{sec:main}
-
-\begin{algorithm}[t]
-  \caption{\protect\CompileWithBaseCases{$\phi$}}\label{alg:compilewithbasecases}
-  \KwIn{formula $\phi$}
-  \KwOut{set $\mathcal{E}$ of equations}
-  $(\mathcal{E}, \mathcal{F}, \mathcal{D}) \gets \Compile{$\phi$}$\;\label{line:first}
-  $\mathcal{E} \gets \Simplify{$\mathcal{E}$}$\;\label{line:second}
-  \ForEach{base case $f(\mathbf{x}) \in \FindBaseCases{$\mathcal{E}$}$}{
-    $\psi \gets \mathcal{F}(f)$\;
-    \ForEach{$i$ such that $x_{i} \in \mathbb{N}_{0}$}{
-      $\psi \gets \Propagate{$\psi$, $\mathcal{D}(f, i)$, $x_i$}$\;
-    }
-    $\mathcal{E} \gets \mathcal{E} \cup \CompileWithBaseCases{$\psi$}$\;
-  }
-\end{algorithm}
-
-\Cref{alg:compilewithbasecases} presents our overall approach for compiling a
-formula into equations that include the necessary base cases. To begin, we
-utilise the knowledge compilation algorithm from the original \textsc{Crane} to
-compile the formula into three components:
-\begin{enumerate*}[label=(\roman*)]
-  \item set $\mathcal{E}$ of equations,
-  \item map $\mathcal{F}$ from function names to formulas, and
-  \item map $\mathcal{D}$ from function names and argument indices to domains.
-\end{enumerate*}
-After some algebraic simplification, $\mathcal{E}$ is then passed to the
-\FindBaseCases procedure (explained in \cref{sec:identifying}), which identifies
-the base cases that need to be defined. For each base case $f(\mathbf{x})$, we
-determine the formula associated with the function name $f$ and simplify it
-using the \Propagate procedure (explained in \cref{sec:simplifying}). The
-algorithm then calls itself on these simplified formulas and adds the resulting
-base case equations to $\mathcal{E}$. \Cref{example:overall} provides a more
-detailed explanation of \cref{alg:compilewithbasecases}.
-
-\begin{example}[Counting bijections]\label{example:overall}
-  Consider the following formula (previously examined by Dilkas and
-  Belle~\shortcite{DBLP:conf/kr/DilkasB23}) that defines predicate $P$ as a
-  bijection between two sets $\Gamma$ and $\Delta$:
-  \[
-    \begin{gathered}
-      \forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }P(x, y)\\
-      \forall y \in \Delta\text{. }\exists x \in \Gamma\text{. }P(x, y)\\
-      \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z\\
-      \forall x, z \in \Gamma\text{. }\forall y \in \Delta\text{. }P(x, y) \land P(z, y) \Rightarrow x = z.
-    \end{gathered}
-  \]
-  We specifically examine the first solution returned by \Cranetwo{} for this
-  formula.
-
-  After \cref{line:first,line:second}, we have
-  \begin{align*}
-    \mathcal{E} &= \left\{\,\begin{aligned}f(m, n) &= \sum_{l=0}^{n} \binom{n}{l}{(-1)}^{n-l}g(l, m),\\ g(l, m) &= g(l-1, m) + mg(l-1, m-1)\end{aligned}\,\right\};\\
-    \mathcal{D} &= \{\, (f, 1) \mapsto \Gamma, (f, 2) \mapsto \Delta, (g, 1) \mapsto \Delta^{\top}, (g, 2) \mapsto \Gamma \,\},
-  \end{align*}
-  where $\Delta^{\top}$ is a new domain introduced by \Compile. Then
-  \FindBaseCases identifies two base cases: $g(0, m)$ and $g(l, 0)$. In both
-  cases, \CompileWithBaseCases recurses on the formula $\mathcal{F}(g)$
-  simplified by assuming that one of the domains is empty. In the first case, we
-  recurse on the formula $\forall x \in \Gamma\text{. }S(x) \lor \neg S(x)$,
-  where $S$ is a predicate introduced by Skolemization with weights
-  $w^{+}(S) = 1$ and $w^{-}(S) = -1$. Hence, we obtain the base case
-  $g(0, m) = 0^{m}$. In the case of $g(l, 0)$, \Propagate{$\psi$, $\Gamma$, $0$}
-  returns an empty formula, resulting in $g(l, 0) = 1$.
-\end{example}
-
-It is worth noting that these base cases overlap when $l = m = 0$ but remain
-consistent since $0^{0} = 1$. Generally, let $\phi$ be a formula with two
-domains $\Gamma$ and $\Delta$, and let $n, m \in \mathbb{N}_{0}$. Then the WFOMC
-of \Propagate{$\phi$, $\Delta$, $n$} assuming $|\Gamma| = m$ is the same as the
-WFOMC of \Propagate{$\phi$, $\Gamma$, $m$} assuming $|\Delta| = n$.
-
-Finally, we highlight the crucial role of the \Simplify procedure in simplifying
-the algebraic pattern $\sum_{m=0}^{n}[a \le m \le b] f(m)$. Here:
-\begin{enumerate*}[label=(\roman*)]
-  \item $n$ is a variable,
-  \item $a, b \in \mathbb{N}_{0}$ are constants,
-  \item $f$ is an expression that may depend on $m$, and
-  \item $[a \le m \le b] =
-  \begin{cases}
-    1 & \text{if $a \le m \le b$} \\
-    0 & \text{otherwise}
-  \end{cases}$ represents the Iverson bracket.
-\end{enumerate*}
-\Simplify transforms this pattern into
-$f(a) + f(a+1) + \cdots + f(\min\{\, n, b \,\})$. For instance, in the case of
-\cref{example:overall}, \Simplify transforms
-$g(l, m) = \sum_{k=0}^{m}[0 \le k \le 1]\binom{m}{k}g(l-1, m-k)$ into the
-simplified form mentioned above.
-
-\subsection{Identifying a Sufficient Set of Base Cases}\label{sec:identifying}
-
-\begin{algorithm}[t]
-  \caption{\protect\FindBaseCases{$\mathcal{E}$}}\label{alg:findbasecases}
-  \KwIn{set $\mathcal{E}$ of equations}
-  \KwOut{set $\mathcal{B}$ of base cases}
-
-  $\mathcal{B} \gets \emptyset$\;
-  \ForEach{equation $(f(\mathbf{x}) = \expr{}) \in \mathcal{E}$}{
-    \ForEach{function call $f(\mathbf{y}) \in \expr{}$}{\label{line:functioncall}
-      \ForEach{$y_{i} \in \mathbf{y}$} {
-        \uIf{$y_{i} \in \mathbb{N}_{0}$}{
-          $\mathcal{B} \gets \mathcal{B} \cup \{\, f(\mathbf{x})[x_{i} \mapsto y_{i}] \,\}$\;
-        }
-        \ElseIf{$y_{i} = x_{i} - c_{i}$ for some $c_{i} \in \mathbb{N}_{0}$}{
-          \For{$j \gets 0$ \KwTo $c_{i} - 1$}{\label{line:lim}
-            $\mathcal{B} \gets \mathcal{B} \cup \{\, f(\mathbf{x})[x_{i} \mapsto j] \,\}$\;\label{line:insert}
-          }
-        }
-      }
-    }
-  }
-\end{algorithm}
-
-\Cref{alg:findbasecases} summarises the implementation of the \FindBaseCases
-function. When a function $f$ calls itself recursively, \FindBaseCases considers
-two types of arguments:
-\begin{enumerate*}[label=(\roman*)]
-  \item constants and
-  \item arguments of the form $x_{i} - c_{i}$, where $c_{i}$ is a constant and
-  $x_{i}$ is the $i$-th argument of the signature of $f$.
-\end{enumerate*}
-If the argument is a constant $c_{i}$, a base case with $c_{i}$ is added. In the
-second case, a base case is added for each constant from zero up to (but not
-including) $c_{i}$. The following discussion explains the reasoning behind this
-approach.
-
-\begin{example}
-  Let us consider the recursive function $g$ from \cref{example:overall}. In
-  this case, \FindBaseCases iterates over two function calls: $g(l-1, m)$ and
-  $g(l-1, m-1)$. The former produces the base case $g(0, m)$, while the latter
-  produces both $g(0, m)$ and $g(l, 0)$.
-\end{example}
-
-For the rest of this section, let $\mathcal{E}$ represent the equations returned
-by \CompileWithBaseCases. To demonstrate that the base cases identified by
-\FindBaseCases are sufficient, we begin with a few observations that stem from
-the details of previous
-work~\cite{DBLP:conf/ijcai/BroeckTMDR11,DBLP:conf/kr/DilkasB23} and this work.
+To demonstrate that the base cases identified by \FindBaseCases are sufficient,
+we begin with a few observations that stem from
+previous~\cite{DBLP:conf/ijcai/BroeckTMDR11,DBLP:conf/kr/DilkasB23} and this
+work. Let $\mathcal{E}$ represent the equations returned by
+\CompileWithBaseCases.
 
@@
 
-We prove \cref{thm:halting} using double induction. First, we apply induction on
-the number of functions in $\mathcal{E}$. Then, we use induction on the arity of
-the `last' function in $\mathcal{E}$ according to some topological ordering (as
-defined in \cref{assumption2}). For readability, we divide the proof into
-several lemmas of increasing generality.
+For readability, we divide the proof into several lemmas of increasing
+generality.
 
@@
 
-\subsection{Propagating Domain Size Assumptions}\label{sec:simplifying}
-
-\begin{algorithm}[t]
-  \caption{\protect\Propagate{$\phi$, $\Delta$, $n$}}\label{alg:propagate}
-  \KwIn{formula $\phi$, domain $\Delta$, $n \in \mathbb{N}_{0}$}
-  \KwOut{formula $\phi'$}
-  $\phi' \gets \emptyset$\;
-  \uIf{$n = 0$}{
-    \ForEach{clause $C \in \phi$}{
-      \lIf{$\Delta \not\in \Doms(C)$}{$\phi' \gets \phi' \cup \{\, C \,\}$}
-      \Else{
-        $C' \gets \{\, l \in C \mid \Delta \not\in \Doms(l) \,\}$\;
-        \If{$C' \ne \emptyset$}{
-          $l \gets \text{an arbitrary literal in } C'$\;\label{line:smoothing1}
-          $\phi' \gets \phi' \cup \{\, C' \cup \{\, \neg l \,\} \,\} $\;\label{line:smoothing2}
-        }
-      }
-    }
-  }
-  \Else{
-    $D \gets \text{a set of $n$ new constants in $\Delta$}$\;
-    \ForEach{clause $C \in \phi$}{
-      ${(x_{i})}_{i=1}^{m} \gets \text{the variables in $C$ with domain $\Delta$}$\;
-      \lIf{$m = 0$}{$\phi' \gets \phi' \cup \{\, C \,\}$}
-      \Else{
-        $\phi' \gets \phi' \cup \{\, C[x_{1} \mapsto c_{1}, \dots, x_{m} \mapsto c_{m}] \mid {(c_{i})}_{i=1}^{m} \in D^{m} \,\}$\;
-      }
-    }
-  }
-\end{algorithm}
-
-\Cref{alg:propagate}, called \Propagate, modifies the formula $\phi$ based on
-the assumption that $|\Delta| = n$. When $n=0$, some clauses become vacuously
-satisfied and can be removed. When $n > 0$\footnote{None of the formulas
-  examined in this study had $n > 1$.}, partial grounding is performed by
-replacing all variables quantified over $\Delta$ with constants.
-\Cref{alg:propagate} handles these two cases separately. For a literal or a
-clause $C$, the set of corresponding domains is denoted as $\Doms(C)$.
-
-In the case of $n = 0$, there are three types of clauses to consider:
-\begin{enumerate*}[label=(\roman*)]
-  \item those that do not mention $\Delta$,\label[type]{type1}
-  \item those in which every literal contains variables quantified over
-  $\Delta$, and\label[type]{type2}
-  \item those that have some literals with variables quantified over $\Delta$
-  and some without.\label[type]{type3}
-\end{enumerate*}
-Clauses of \cref{type1} are transferred to the new formula $\phi'$ without any
-changes. For clauses of \cref{type2}, $C'$ is empty, so these clauses are
-filtered out. As for clauses of \cref{type3}, a new kind of smoothing is
-performed, which will be explained in \cref{sec:smoothingbase}.
-
-In the case of $n>0$, $n$ new constants are introduced. Let $C$ be an arbitrary
-clause in $\phi$, and let $m \in \mathbb{N}_{0}$ be the number of variables in
-$C$ quantified over $\Delta$. If $m=0$, $C$ is added directly to $\phi'$.
-Otherwise, a clause is added to $\phi'$ for every possible combination of
-replacing the $m$ variables in $C$ with the $n$ new constants.
-
-\begin{example}
-  Let $C \equiv \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{.
-  } \neg P(x, y) \lor \neg P(x, z) \lor y=z$. Then
-  $\Doms(C) = \Doms(\neg P(x, y)) = \Doms(\neg P(x, z)) = \{\, \Gamma, \Delta \,\}$,
-  and $\Doms(y=z) = \{\, \Delta \,\}$. A call to \Propagate{$\{\, C \,\}$,
-    $\Delta$, $3$} would result in the following formula with nine clauses:
-  \begin{align*}
-    \forall x \in \Gamma\text{. }\neg P(x, c_{1}) \lor& \neg P(x, c_{1}) \lor c_{1}=c_{1}\\
-    \forall x \in \Gamma\text{. }\neg P(x, c_{1}) \lor& \neg P(x, c_{2}) \lor c_{1}=c_{2}\\
-    \vdots&\\
-    \forall x \in \Gamma\text{. }\neg P(x, c_{3}) \lor& \neg P(x, c_{3}) \lor c_{3}=c_{3}.\\
-  \end{align*}
-  Here, $c_{1}$, $c_{2}$, and $c_{3}$ are the new constants.
-\end{example}
-
-\section{Smoothing}\label{sec:smoothing}
-
-\emph{Smoothness} is a property originating in propositional knowledge
-compilation, where it refers to the situation where all disjuncts in a
-disjunction node contain the same atoms~\cite{darwiche2001tractable}. Van den
-Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11} extend this concept to
-first-order logic, introducing set-disjunction and inclusion-exclusion nodes in
-addition to disjunction.
-
-The purpose of smoothing is as follows. When compilation rules such as unit
-propagation and inclusion-exclusion simplify a formula, certain ground atoms may
-be eliminated (see \cref{example:basecasesmoothing} below). To properly account
-for these atoms during counting, smoothing nodes (i.e., tautological clauses
-such as $P(c) \lor \neg P(c)$) are added to the FCG in the appropriate location.
-
-The remainder of this section presents an extension to the smoothing algorithm
-of Van den Broeck et al.~\shortcite{DBLP:conf/ijcai/BroeckTMDR11}.
-\Cref{sec:smoothingbase} explains the role of smoothing in the base-case-finding
-algorithm described in \cref{sec:main}. \Cref{sec:smoothingfcg1} demonstrates
-how to adapt smoothing to the compilation rules introduced by Dilkas and
-Belle~\shortcite{DBLP:conf/kr/DilkasB23}.
-
-\subsection{Smoothing for Base Cases}\label{sec:smoothingbase}
-
-In this section, we motivate and describe \cref{line:smoothing1,line:smoothing2}
-of \cref{alg:propagate}. Suppose that \Propagate is called with arguments
-$(\phi, \Delta, 0)$, which means we are simplifying the formula $\phi$ by
-assuming that the domain $\Delta$ is empty. Informally, if there is a predicate
-$P$ in $\phi$ that has nothing to do with the domain $\Delta$, smoothing
-preserves all occurrences of $P$ even if all clauses with $P$ become vacuously
-satisfied. It is important to note that the approach presented in this section
-is not unique. We explain it via the example below.
-
-\begin{example}\label{example:basecasesmoothing}
-  Let $\phi$ be:
-  \begin{align}
-    \forall x \in \Delta\text{. }\forall y, z \in \Gamma&\text{. }Q(x) \lor P(y, z)\label[clause]{eq:example1}\\
-    \forall y, z \in \Gamma'&\text{. }P(y, z)\label[clause]{eq:example2},
-  \end{align}
-  where $\Gamma' \subseteq \Gamma$ is a domain introduced by a compilation rule.
-  It should be noted that $P$, as a relation, is a subset of
-  $\Gamma \times \Gamma$.
-
-  Now, let us reason manually about the model count of $\phi$ when
-  $\Delta = \emptyset$. Predicate $Q$ can only take one value, $Q = \emptyset$.
-  The value of $P$ is fixed over $\Gamma' \times \Gamma'$ by \cref{eq:example2},
-  but it is allowed to vary freely over
-  $(\Gamma \times \Gamma) \setminus (\Gamma' \times \Gamma')$ since
-  \cref{eq:example1} is vacuously satisfied by all structures. Therefore, the
-  correct WFOMC should be $2^{|\Gamma|^2 - |\Gamma'|^2}$.
-
-  However, without \cref{line:smoothing2}, \Propagate would simplify $\phi$ to
-  $\forall y, z \in \Gamma'\text{. }P(y, z)$. In this case, $P$ is a subset of
-  $\Gamma' \times \Gamma'$. This simplified formula has only one model:
-  $\{\, P(y, z) \mid y, z \in \Gamma' \,\}$.
-
-  By including \cref{line:smoothing2}, \Propagate transforms $\phi$ to:
-  \begin{gather*}
-    \forall y, z \in \Gamma\text{. }P(y, z) \lor \neg P(y, z)\\
-    \forall y, z \in \Gamma'\text{. }P(y, z),
-  \end{gather*}
-  which retains the correct model count.
-\end{example}
-
-It is worth mentioning that the choice of $l$ on \cref{line:smoothing1} of
-\cref{alg:propagate} is inconsequential because any choice achieves the same
-goal: constructing a tautological clause that retains the literals in $C'$.
-
-\subsection{Smoothing the FCG}\label{sec:smoothingfcg1}
-
-Smoothing is a two-step process that involves propagating unit clauses upwards
-(i.e., in the opposite direction of FCG arcs) and adding smoothing nodes to
-account for missing atoms. In this section, we will
-\begin{enumerate*}[label=(\roman*)]
-  \item describe the relevant node types from previous work,
-  \item explain how smoothing should work for these node types, and
-  \item demonstrate the new smoothing techniques using two example FCGs.
-\end{enumerate*}
-
-Before discussing the proposed changes to smoothing, let us briefly review the
-compilation rules and their corresponding node types introduced by Dilkas and
-Belle~\shortcite{DBLP:conf/kr/DilkasB23}. \emph{Domain recursion} involves
-selecting a domain $\Delta$, introducing a new constant $c \in \Delta$, and
-modifying the formula based on two possibilities for each variable $x$
-quantified over $\Delta$: $x = c$ or $x \ne c$. The resulting node is denoted as
-$\DR(c \in \Delta)$. \emph{Constraint removal} applies to formulas where each
-variable $x$ quantified over a domain $\Delta$ is followed by the inequality
-constraint $x \ne c$. These formulas can be rewritten so that each clause begins
-with $\forall x \in \Delta\text{. }x \ne c \Rightarrow \ldots$ Constraint
-removal replaces $\Delta$ with a new domain $\Delta'$ and removes the $x \ne c$
-constraints. The resulting node is denoted as
-$\CR(\Delta' \gets \Delta \setminus \{\,c\,\})$. Finally, \emph{caching} detects
-when the input formula $\phi$ is equal to a previously encountered formula
-$\psi$ except for having different domains. The resulting node is denoted as
-$\Reff(\sigma)$, with $\sigma$ representing the substitution mapping the domains
-of $\psi$ to their corresponding domains in $\phi$.
-
-\paragraph{Stage~1 for Domain Recursion}
-When visiting a $\DR(c \in \Delta)$ node, we replace each occurrence of
-$\phi(c)$ or $\forall x \in \Delta\text{. } x \ne c \Rightarrow \phi(x)$ with
-$\forall x \in \Delta\text{. }\phi(x)$ for each unit clause received from the
-child node. This way, we ensure that if the subgraph below the domain recursion
-node covers some of the ground atoms affected by domain recursion, it covers all
-of them. If the relevant subgraph already covers those ground atoms, Stage~2
-will not make any changes. Otherwise, smoothing nodes will be added below the
-domain recursion node to account for the difference in the sets of ground atoms
-assigned to the domain recursion node and its child node.
-
-\paragraph{Stage~1 for Constraint Removal and Caching}
-When visiting a $\CR(\Delta' \gets \Delta \setminus \{\,c\,\})$ node, we reverse
-constraint removal by replacing each $\forall x \in \Delta'\text{. }\phi(x)$
-with $\forall x \in \Delta\text{. }x \ne c \Rightarrow \phi(x)$. When visiting a
-$\Reff(\sigma)$ node, we apply the substitution $\sigma$ to the unit clauses
-from the child node.
-
-\paragraph{Stage~2 for Domain Recursion}
-We do not need to add smoothing nodes immediately below constraint removal or
-caching nodes. However, for domain recursion, we follow a specific process.
-\begin{enumerate}
-  \item If the set of unit clauses assigned to the child node during Stage~1
-        contains both $\phi(c)$ and $\forall x \in \Delta\text{.
-        } x \ne c \Rightarrow \phi(x)$, we merge the two clauses into
-        $\forall x \in \Delta\text{. }\phi(x)$. The only difference between
-        these two clauses is that one has the constant $c$ while the other has a
-        variable $x \ne c$.
-  \item If necessary, we add smoothing nodes below the domain recursion node to
-        account for the difference between the unit clauses assigned to the
-        domain recursion node during Stage~1 and the unit clauses of the child
-        node post-processed by the step above.
-\end{enumerate}
-
-\begin{figure}[t]
-  \centering
-  \begin{forest}
-    for tree={sn edges}
-    [$\DR(c \in \Delta)$,name=dr,ellipse,draw
-    [$\land$,ellipse,draw,dashed,edge=dashed
-    [$P(c)$,rectangle,draw,fill=green!20]
-    [$\forall x \in \Delta\text{. }x \ne c \Rightarrow P(x) \lor \neg P(x)$,rectangle,dashed,edge=dashed,draw,fill=blue!20]
-    ]
-    ]
-  \end{forest}
-  \caption{An artificial example of an FCG where a smoothing node needs to be
-    added below a domain recursion node. The dashed nodes and arcs are added
-    during Stage~2 of smoothing.}\label{fig:smoothing2}
-\end{figure}
-
-\begin{example}[An FCG that requires smoothing]
-  \Cref{fig:smoothing2} depicts an FCG with a domain recursion node
-  $\DR(c \in \Delta)$ followed directly by a single $P(c)$ node. In this
-  scenario, Stage~1 assigns $\{\, \forall x \in \Delta\text{. }P(x) \,\}$ to the
-  former node and $\{\, P(c) \,\}$ to the latter. As these two sets of unit
-  clauses cover different ground atoms, Stage~2 adds a smoothing node to address
-  $P(x)$ for all $x \in \Delta \setminus \{\, c \,\}$.
-\end{example}
-
-\begin{figure}[t]
-  \centering
-  \begin{forest}
-    for tree={sn edges}
-    [$\DR(c \in \Delta)$,name=dr,ellipse,draw,label={right:\textcolor{blue}{3. $\{\, \forall x \in \Delta\text{. }P(x) \,\}$}}
-    [$\land$,ellipse,draw,label={left:\textcolor{blue}{2. $\{\, P(c) \,\}$}},label={right:\textcolor{blue}{6. $\{\, P(c), \forall x \in \Delta\text{. }x \ne c \Rightarrow P(x) \,\}$}}
-    [$P(c)$,rectangle,draw,fill=green!20,label={272:\textcolor{blue}{1. $\{\, P(c) \,\}$}}]
-    [$\CR(\Delta' \gets \Delta \setminus \{\, c \,\})$,ellipse,draw,label={87:\textcolor{blue}{5. $\{\, \forall x \in \Delta\text{. }x \ne c \Rightarrow P(x) \,\}$}}
-    [$\Reff(\Delta \mapsto \Delta')$,name=ref,ellipse,draw,label={below:\textcolor{blue}{4. $\{\, \forall x \in \Delta'\text{. }P(x) \,\}$}}]
-    ]
-    ]
-    ]
-  \end{forest}
-  \caption{A smooth FCG based on \cref{example:overall}. For compactness, the
-    arc between the caching node and the domain recursion node is not shown. The
-    labels next to the nodes indicate the sets of unit clauses assigned to each
-    node during Stage~1 and the order in which these assignments were made.
-    Empty assignments that replace a set $S$ with $S$ itself are not
-    included.}\label{fig:smoothing1}
-\end{figure}
-
-\begin{example}[A smooth FCG]\label{example:smooth}
-  Stage~1 of the smoothing process is more complex in the case of the FCG shown
-  in \cref{fig:smoothing1}. The unit clause $P(c)$ propagates to the conjunction
-  node and is then generalised to $\forall x \in \Delta\text{. }P(x)$ by the
-  domain recursion node. It continues to propagate to the caching node, changing
-  its form to $(\forall x \in \Delta\text{.
-  }P(x))[\Delta \mapsto \Delta'] \equiv \forall x \in \Delta'\text{. }P(x)$. The
-  constraint removal node re-introduces the constraints, transforming the clause
-  to $\forall x \in \Delta\text{. }x \ne c \Rightarrow P(x)$, which then
-  propagates to the conjunction node, joining $P(c)$.
-
-  During Stage~2, $P(c)$ and $\forall x \in \Delta\text{.
-  }x \ne c \Rightarrow P(x)$ are combined into $\forall x \in \Delta\text{.
-  }P(x)$. Since the resulting clause matches the clause assigned to the domain
-  recursion node, the FCG is already smooth.
-\end{example}
-
-The algebraic interpretation of \cref{fig:smoothing1} is an equation $e$ that
-defines a recursive function. The right-hand side of $e$ already encompasses
-$P(c)$, and the smoothing algorithm correctly recognises that the recursive call
-also encompasses $P(x)$ for all $x \in \Delta \setminus \{\, c \,\}$.
-
-\section{Generating C++ Code}\label{sec:cpp}
-
-In this section, we will describe the final step of \Cranetwo{} as outlined in
-\cref{fig:overview}. This step involves translating the set of equations
-$\mathcal{E}$ into C++ code. The resulting C++ program can then be compiled and
-executed with different command-line arguments to compute the model count of the
-formula for various domain sizes.
-
-Each equation in $\mathcal{E}$ is compiled into a C++ function, along with a
-separate cache for memoisation. Let us consider an arbitrary equation
-$e = (f(\mathbf{x}) = \expr{}) \in \mathcal{E}$, and let
-$\mathbf{c} \in \mathbb{N}_{0}^{n}$ represent the arguments of the corresponding
-C++ function. The implementation of $e$ consists of three parts. First, we check
-if $\mathbf{c}$ is already present in the cache of $e$. If it is, we simply
-return the cached value. Second, for each base case $f(\mathbf{y})$ of
-$f(\mathbf{x})$ (as defined in \cref{def:basecase}), we check if $\mathbf{c}$
-\emph{matches} $\mathbf{y}$, i.e., $c_{i} = y_{i}$ whenever
-$y_{i} \in \mathbb{N}_{0}$. If this condition is satisfied, $\mathbf{c}$ is
-redirected to the C++ function that corresponds to the definition of the base
-case $f(\mathbf{y})$. Finally, if none of the above cases apply, we evaluate
-$\mathbf{c}$ based on the expression $\expr{}$, store the result in the cache,
-and return it.
-
-\section{Experimental Evaluation}\label{sec:experiments}
-
-We compared \Cranetwo{}\footnote{\textsc{Crane} has two modes that decide how
-  compilation rules are applied to formulas: one that uses greedy search and
-  another that combines greedy and breadth-first search. In our experiments, we
-  refer to these modes as \Cranegreedy{} and \Cranebfs{}, respectively.} with
-\textsc{FastWFOMC} and \textsc{ForcLift} on two problems previously considered
-by Dilkas and Belle~\shortcite{DBLP:conf/kr/DilkasB23}. The first problem is the
-function-counting problem from \cref{example:functions}, and the second problem
-is the bijection-counting problem described below. It is important to note that
-comparing \Cranetwo{} and \textsc{FastWFOMC} on a more substantial set of
-benchmarks is challenging because there is no automated way to translate a
-formula in \FO{} or \Ctwo{} into \UFO{}, or even check if such an encoding is
-possible. We ran the experiments on an AMD~Ryzen~7~5800H processor with
-\SI{16}{\gibi\byte} of memory and Arch Linux~6.8.2-arch2-1 operating system.
-\textsc{FastWFOMC} was executed using Python~3.8.19 with Python-FLINT~0.5.0.
-
-The \FO{} formula for bijections is described in \cref{example:overall}. The
-equivalent formula in \Ctwo{} is
-\begin{gather*}
-  \forall x \in \Delta\text{. }\exists^{=1} y \in \Delta\text{. }P(x, y)\\
-  \forall y \in \Delta\text{. }\exists^{=1} x \in \Delta\text{. }P(x, y).
-\end{gather*}
-Similarly, in \UFO{} the same formula can be written as
-\begin{gather*}
-  \forall x, y \in \Delta\text{. }R(x) \lor \neg P(x, y)\\
-  \forall x, y \in \Delta\text{. }S(x) \lor \neg P(y, x)\\
-  |P| = |\Delta|,
-\end{gather*}
-where $w^{-}(R) = w^{-}(S) = -1$.
-
-\begin{figure}[t]
-  \centering
-  \input{plot}
-  \caption{The running time of WFOMC algorithms. Note that the $y$-axis is on a
-    logarithmic scale.}\label{fig:plot}
-\end{figure}
-
-In the first experiment, we ran each of the four algorithms once on each
-combination of benchmark and domain size, ranging from one up to and including
-35. \Cref{fig:plot} shows the total runtime values as a measure of the overall
-performance of each algorithm. We also separately tracked compilation and
-inference times and commented on them where relevant. It is worth noting that
-\Cranebfs{} can handle more instances than either \textsc{ForcLift} or
-\Cranegreedy{}, including the bijection-counting problem in our experiments as
-well as similar formulas examined previously~\cite{DBLP:conf/kr/DilkasB23}.
-
-As shown in \cref{fig:plot}, the runtimes of all compilation-based algorithms
-remained practically constant, in contrast to the rapidly increasing runtimes of
-\textsc{FastWFOMC}. Although the search/compilation part is slower in
-\Cranetwo{} than in \textsc{ForcLift}, the difference is negligible. The
-runtimes of the knowledge compilation algorithms appear constant because, for
-these counting problems and domain sizes, compilation time dominates inference
-time (remember that compilation time is independent of domain sizes). Indeed,
-the maximum inference time of \Cranebfs{} and \Cranegreedy{} across these
-experiments is only \SI{4}{\milli\second}. The runtimes of \Cranetwo{} have
-lower variation than those of \textsc{ForcLift} because we compile the formula
-anew for each domain size with \textsc{ForcLift}, whereas with \Cranetwo{}, we
-compile it once and reuse the resulting C++ program for all domain sizes.
-
-\begin{table}[t]
-  \centering
-  \begin{tabular}{lrr}
-    \toprule
-    Algorithm & Bijections & Functions \\
-    \midrule
-    \Cranebfs{} & \num{e4} & \num{3e5} \\
-    \Cranegreedy{} & --- & \num{3e5} \\
-    \textsc{FastWFOMC} & 28 & 32 \\
-    \textsc{ForcLift} & --- & 143 \\
-    \bottomrule
-  \end{tabular}
-  \caption{The maximum domain sizes that each algorithm can handle within
-    \SI{45}{\second}. A dash symbol `---' indicates that the algorithm was
-    unable to find a solution. The domain sizes for \Cranetwo{} are accurate up
-    to the first digit, while the domain sizes for the other domain sizes are
-    exact.}\label{table:results}
-\end{table}
-
-For the second experiment, we examined the maximum domain size the algorithms
-can handle in at most \SI{45}{\second} of total runtime. As shown in
-\cref{table:results}, \Cranebfs{} can scale to domain sizes \num{357} and
-\num{9375} times larger than \textsc{FastWFOMC} for the bijection-counting and
-function-counting problems, respectively. It is important to note that while
-\textsc{ForcLift} may have runtime performance comparable to \Cranetwo{}, its
-finite-precision arithmetic cannot represent model counts for domain sizes
-greater than 143 and returns $\infty$ instead.
-
-\section{Conclusion and Future Work}
-
-In this work, we have presented several contributions. First, we have developed
-algorithmic techniques to find the base cases of recursive functions generated
-by the original \textsc{Crane} algorithm. Second, we have extended the smoothing
-procedure of \textsc{ForcLift} and \textsc{Crane} to support base case formulas
-and the compilation rules introduced by Dilkas and
-Belle~\shortcite{DBLP:conf/kr/DilkasB23}. Third, we have proposed an approach to
-compile function definitions into C++ programs with support for
-arbitrary-precision arithmetic. Lastly, we have provided experimental evidence
-demonstrating that \Cranetwo{} can scale to much larger domain sizes than
-\textsc{FastWFOMC} while handling more formulas than \textsc{ForcLift}.
-
-There are many potential avenues for future work. Specifically, a more thorough
-experimental study is needed to understand how WFOMC algorithms compare in terms
-of their ability to handle different formulas and their scalability with respect
-to domain size. Additionally, further characterisation of the capabilities of
-\Cranetwo{} can be explored. For example, \emph{completeness} could be proven
-for a fragment of first-order logic such as \Ctwo{} (using a suitable encoding
-of counting quantifiers). Moreover, the efficiency of a WFOMC algorithm in
-handling a particular formula can be assessed using \emph{fine-grained
-  complexity}. In the case of \textsc{Crane} and \Cranetwo{}, this can be done
-by analysing the equations~\cite{DBLP:conf/kr/DilkasB23}. By doing so,
-efficiency can be reasoned about in a more implementation-independent manner by
-making claims about the maximum degree of the polynomial that characterises any
-given solution.
-
-\bibliographystyle{kr}
 \bibliography{paper}

### 2025-01-12 doc/paper/paper.tex
Front matter + references to line numbers

@@
-\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
-\usepackage[submission]{aaai25}  % DO NOT CHANGE THIS
-\usepackage{times}  % DO NOT CHANGE THIS
-\usepackage{helvet}  % DO NOT CHANGE THIS
-\usepackage{courier}  % DO NOT CHANGE THIS
-\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
-\usepackage{graphicx} % DO NOT CHANGE THIS
-\urlstyle{rm} % DO NOT CHANGE THIS
-\def\UrlFont{\rm}  % DO NOT CHANGE THIS
-\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
-\frenchspacing  % DO NOT CHANGE THIS
-\setlength{\pdfpagewidth}{8.5in} % DO NOT CHANGE THIS
-\setlength{\pdfpageheight}{11in} % DO NOT CHANGE THIS
+\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate]{lipics-v2021}
+%This is a template for producing LIPIcs articles. 
+%See lipics-v2021-authors-guidelines.pdf for further information.
+%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
+%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
+%for section-numbered lemmas etc., use "numberwithinsect"
+%for enabling cleveref support, use "cleveref"
+%for enabling autoref support, use "autoref"
+%for anonymousing the authors (e.g. for double-blind review), add "anonymous"
+%for enabling thm-restate support, use "thm-restate"
+%for enabling a two-column layout for the author/affilation part (only applicable for > 6 authors), use "authorcolumns"
+%for producing a PDF according the PDF/A standard, add "pdfa"
+
+\pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
+\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
+
+%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory
+
+\bibliographystyle{plainurl}% the mandatory bibstyle
+
+\title{Towards Practical First-Order Model Counting}
+
+\author{Ananth K. Kidambi}{Indian Institute of Technology Bombay, Mumbai, India}{}{}{TODO: funding}
+\author{Guramrit Singh}{Indian Institute of Technology Bombay, Mumbai, India}{}{}{TODO: funding}
+\author{Paulius Dilkas}{University of Toronto, Toronto, Canada \and Vector Institute, Toronto, Canada}{}{}{TODO: funding}
+\author{Kuldeep S. Meel}{University of Toronto, Toronto, Canada}{}{}{TODO: funding}
+
+\authorrunning{A.\,K. Kidambi, G. Singh, P. Dilkas, and K.\,S. Meel}
+
+\Copyright{Ananth K. Kidambi, Guramrit Singh, Paulius Dilkas, and Kuldeep S. Meel}
+
+\ccsdesc{Computing methodologies~Knowledge representation and reasoning}
+
+\keywords{first-order model counting, knowledge compilation, lifted inference}
+
+\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
+
+%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
+%\supplementdetails[linktext={opt.
+text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g.
+Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional
+
+%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors.
+Please enter author specific funding statements as fifth argument of the \author macro.
+
+%\acknowledgements{I want to thank \dots}%optional
+
+%\nolinenumbers %uncomment to disable line numbering
+
+%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\EventEditors{John Q. Open and Joan R. Access}
+\EventNoEds{2}
+\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
+\EventShortTitle{CVIT 2016}
+\EventAcronym{CVIT}
+\EventYear{2016}
+\EventDate{December 24--27, 2016}
+\EventLocation{Little Whinging, United Kingdom}
+\EventLogo{}
+\SeriesVolume{42}
+\ArticleNo{23}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \usepackage[linesnumbered,ruled,vlined]{algorithm2e}
+\usepackage{booktabs}
+\usepackage{pifont}
+\usepackage{siunitx}
+\usepackage{tikz}
 \usepackage{microtype}
-\usepackage{mathtools}
-\usepackage{forest}
-\usepackage{siunitx}
-\usepackage{amsfonts}
-\usepackage{pifont}
-\usepackage[inline]{enumitem}
-\usepackage[capitalize,noabbrev]{cleveref}
-\usepackage{booktabs}
-\usepackage{amsthm}
-
-\newtheorem{theorem}{Theorem}
-\newtheorem{assumption}{Assumption}
-\newtheorem{corollary}{Corollary}
-\newtheorem{fact}{Observation}
-\newtheorem{lemma}{Lemma}
-\theoremstyle{remark}
-\newtheorem*{remark}{Remark}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
 
 \usetikzlibrary{arrows.meta}
+\usetikzlibrary{fit}
 \usetikzlibrary{positioning}
-
-\forestset{
-  sn edges/.style={for tree={edge={-Latex}}}
-}
-
-\sisetup{group-separator = {,}}
+\usetikzlibrary{shapes.misc}
 
@@
 
-\newcommand{\crefrangeconjunction}{--}
-\crefname{line}{line}{lines}
-%\crefname{fact}{Observation}{Observations}
-\crefname{assumption}{Assumption}{Assumptions}
+\SetKwFunction{CompileWithBaseCases}{CompileWithBaseCases}
+\SetKwFunction{Compile}{{\normalfont \textsc{Crane}}}
+\SetKwFunction{Propagate}{Propagate}
+\SetKwFunction{FindBaseCases}{FindBaseCases}
+\SetKwFunction{Simplify}{Simplify}
+
+\DeclareMathOperator{\CR}{CR}
+\DeclareMathOperator{\DR}{DR}
+\DeclareMathOperator{\Reff}{Ref}
+\DeclareMathOperator{\Doms}{Doms}
+
+\sisetup{group-separator = {,}}
+
 \crefalias{enumi}{type}
@@
 \creflabelformat{type}{#2\textup{#1}#3}
-\crefalias{enumi}{step}
-\crefname{step}{Step}{Steps}
-\creflabelformat{step}{#2\textup{#1}#3}
 \crefalias{clause}{equation}
@@
 \creflabelformat{formula}{#2\textup{(#1)}#3}
-
-\DeclareMathOperator{\CR}{CR}
-\DeclareMathOperator{\DR}{DR}
-\DeclareMathOperator{\Reff}{Ref}
-\DeclareMathOperator{\Doms}{Doms}
-
-\SetKwFunction{CompileWithBaseCases}{CompileWithBaseCases}
-\SetKwFunction{Compile}{{\normalfont \textsc{Crane}}}
-\SetKwFunction{Propagate}{Propagate}
-\SetKwFunction{FindBaseCases}{FindBaseCases}
-\SetKwFunction{Simplify}{Simplify}
-
-\pdfinfo{
-/TemplateVersion (2025.1)
-}
-
-\setcounter{secnumdepth}{2} %May be changed to 1 or 2 if section numbers are desired.
-
-\title{Towards Practical First-Order Model Counting}
-\author{Anonymous Submission}
-\affiliations{}
 
@@
 formulas with up to two variables are known to be
-liftable~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/kr/BroeckMD14},
-\citeauthor{DBLP:conf/pods/BeameBGS15}~\shortcite{DBLP:conf/pods/BeameBGS15}
-demonstrated that liftability does not extend to all formulas, identifying an
-unliftable formula with three variables. Recent work has further extended the
-liftable fragment with additional
+liftable~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/kr/BroeckMD14}, Beame et
+al.~\cite{DBLP:conf/pods/BeameBGS15} demonstrated that liftability does not
+extend to all formulas, identifying an unliftable formula with three variables.
+Recent work has further extended the liftable fragment with additional
 axioms~\cite{DBLP:conf/aaai/TothK23,DBLP:journals/ai/BremenK23} and counting
@@
 limitations:
-\begin{enumerate*}[label=(\roman*)]
+\begin{enumerate}
   \item it required manual evaluation of function definitions to compute model
@@
   more complex to use.
-\end{enumerate*}
+\end{enumerate}
 To address these shortcomings, we present \Cranetwo{}, a fully automated FOMC
@@
 either
-\begin{enumerate*}[label=(\roman*)]
+\begin{enumerate}
   \item $P(t_{1}, \dots, t_{m})$ for some predicate $P$ and terms
@@
   \item $x=y$ for some terms $x$ and $y$.
-\end{enumerate*}
+\end{enumerate}
 The \emph{arity} of a predicate is the number of arguments it takes, i.e., $m$
@@
 that a clause is a \emph{(positive) unit clause} if
-\begin{enumerate*}[label=(\roman*)]
+\begin{enumerate}
   \item there is only one literal with a predicate, and
   \item it is a positive literal.
-\end{enumerate*}
+\end{enumerate}
 Finally, a \emph{formula} is a conjunction of clauses. Throughout the paper, we
@@
   \caption[]{A comparison of the three logics used in FOMC based on the following aspects:
-    \begin{enumerate*}[label=(\roman*)]
+    \begin{enumerate}
       \item the number of sorts,
@@
       \item supported atoms in addition to those of the form $P(\mathbf{t})$ for a predicate $P/n$ and an $n$-tuple of terms $\mathbf{t}$.
-    \end{enumerate*}
+    \end{enumerate}
     Here:
-    \begin{enumerate*}[label=(\roman*)]
+    \begin{enumerate}
       \item $k$ and $m$ are non-negative integers, with the latter depending on the domain size,
@@
       \item $x$ and $y$ are terms.
-    \end{enumerate*}
+    \end{enumerate}
   }\label{tbl:logics}
@@
 commonly used in FOMC:
-\begin{enumerate*}[label=(\roman*)]
+\begin{enumerate}
   \item \FO{} is the input format for
@@
   \textsc{FastWFOMC}\footnote{\url{https://github.com/jan-toth/FastWFOMC.jl}}.
-\end{enumerate*}
+\end{enumerate}
 The notation we use to refer to each logic is standard in the case of \Ctwo{}
@@
 Compared to \FO{}, \Ctwo{} and \UFO{} lack support for
-\begin{enumerate*}[label=(\roman*)]
+\begin{enumerate}
   \item constants,
@@
   \item formulas with more than two variables.
-\end{enumerate*}
+\end{enumerate}
 The advantage that \Ctwo{} brings over \FO{} is the inclusion of \emph{counting
@@
   satisfying the following conditions:
-  \begin{enumerate*}[label=(\roman*)]
+  \begin{enumerate}
     \item the sets are pairwise disjoint, and
     \item the constants in $\phi$ are included in the corresponding domains.
-  \end{enumerate*}
+  \end{enumerate}
   A \emph{structure} of $\phi$ is a set $M$ of ground literals defined by adding
@@
   A \emph{WFOMC instance} comprises:
-  \begin{enumerate*}[label=(\roman*)]
+  \begin{enumerate}
     \item a formula $\phi$ in \FO{},
@@
     \item $\sigma$ as described in \cref{def:model}.
-  \end{enumerate*}
+  \end{enumerate}
   Unless specified otherwise, we assume all weights to be equal to 1.
@@
   still determine the correct number of functions by assuming that the sizes of
-  $\Gamma$ and $\Delta$ are equal. This formulation, as observed by
-  \citeauthor{DBLP:conf/kr/DilkasB23}~\shortcite{DBLP:conf/kr/DilkasB23}, can
-  prove beneficial in enabling FOKC algorithms to find efficient solutions.
+  $\Gamma$ and $\Delta$ are equal. This formulation, as observed by Dilkas and
+  Belle~\cite{DBLP:conf/kr/DilkasB23}, can prove beneficial in enabling FOKC
+  algorithms to find efficient solutions.
 \end{example}
@@
 To accomplish this, the \CompileWithBaseCases function employs several components:
-    \begin{enumerate*}[label=(\roman*)]
+    \begin{enumerate}
       \item the FOKC algorithm of \textsc{Crane},
@@
       \item algebraic simplification techniques (denoted as \Simplify).
-    \end{enumerate*}
+    \end{enumerate}
   }\label{fig:overview}
@@
 compiled into:
-\begin{enumerate*}[label=(\roman*)]
+\begin{enumerate}
   \item set $\mathcal{E}$ of equations,
@@
   \item map $\mathcal{D}$ from function names and argument indices to domains.
-\end{enumerate*}
+\end{enumerate}
 $\mathcal{E}$ can contain any number of functions, one of which (denoted by $f$)
@@
 $\psi$ by assuming that domain $\mathcal{D}(f, i)$ has size $x_{i}$. Finally, on
-\cref{line:final}, \CompileWithBaseCases recurses on these simplified formulas
-and adds the resulting base case equations to $\mathcal{E}$.
+\autoref{line:final}, \CompileWithBaseCases recurses on these simplified
+formulas and adds the resulting base case equations to $\mathcal{E}$.
 \Cref{example:overall} below provides more detail.
@@
 \begin{example}[Counting bijections]\label{example:overall}
-  Consider the following formula (previously examined by
-  \citeauthor{DBLP:conf/kr/DilkasB23}~\shortcite{DBLP:conf/kr/DilkasB23}) that
-  defines predicate $P$ as a bijection between two sets $\Gamma$ and $\Delta$:
+  Consider the following formula (previously examined by Dilkas and
+  Belle~\cite{DBLP:conf/kr/DilkasB23}) that defines predicate $P$ as a bijection
+  between two sets $\Gamma$ and $\Delta$:
   \[
@@
 
-  After \cref{line:first,line:second}, we have
+  After \autoref{line:second}, we have
   \begin{align*}
@@
 algebraic pattern $\sum_{m=0}^{n}[a \le m \le b] f(m)$. Here:
-\begin{enumerate*}[label=(\roman*)]
+\begin{enumerate}
   \item $n$ is a variable,
@@
   \end{cases}$.
-\end{enumerate*}
+\end{enumerate}
 \Simplify transforms this pattern into
@@
 recursively:
-\begin{enumerate*}[label=(\roman*)]
+\begin{enumerate}
   \item constants and
@@
   $x_{i}$ is the $i$-th argument of the signature of $f$.
-\end{enumerate*}
+\end{enumerate}
 When the argument is a constant $c_{i}$, a base case with $c_{i}$ is added. In
@@
 In the case of $n = 0$, there are three types of clauses to consider:
-\begin{enumerate*}[label=(\roman*)]
+\begin{enumerate}
   \item those that do not mention $\Delta$,\label[type]{type1}
@@
   and some without.\label[type]{type3}
-\end{enumerate*}
+\end{enumerate}
 Clauses of \cref{type1} are transferred to the new formula $\phi'$ without any
@@
 section, we describe a similar process performed on
-\cref{line:smoothing1,line:smoothing2} of \cref{alg:propagate}.
-\Cref{line:presmoothing} checks if smoothing is necessary, and
-\cref{line:smoothing1,line:smoothing2} execute it. If the condition on
-\cref{line:presmoothing} is not satisfied, the clause is not smoothed but
-omitted.
+lines~\ref{line:presmoothing}--\ref{line:smoothing2} of \cref{alg:propagate}.
+Line~\ref{line:presmoothing} checks if smoothing is necessary, and
+lines~\ref{line:smoothing1} and~\ref{line:smoothing2} execute it. If the
+condition on \autoref{line:presmoothing} is not satisfied, the clause is not
+smoothed but omitted.
 
@@
   correct FOMC should be $2^{|\Gamma|^2 - |\Gamma'|^2}$. However, without
-  \cref{line:smoothing2}, \Propagate would simplify $\phi$ to
+  \autoref{line:smoothing2}, \Propagate would simplify $\phi$ to
   $\forall y, z \in \Gamma'\text{. }P(y, z)$. In this case, $P$ is a subset of
@@
   $\{\, P(y, z) \mid y, z \in \Gamma' \,\}$. By including
-  \cref{line:smoothing2}, \Propagate transforms $\phi$ to:
+  \autoref{line:smoothing2}, \Propagate transforms $\phi$ to:
   \begin{gather*}
@@
 
-It is worth mentioning that the choice of $l$ on \cref{line:smoothing1} of
+It is worth mentioning that the choice of $l$ on \autoref{line:smoothing1} of
 \cref{alg:propagate} is inconsequential because any choice achieves the same
@@
 first benchmark is the function-counting problem from \cref{example:functions},
-previously examined by
-\citeauthor{DBLP:conf/kr/DilkasB23}~\shortcite{DBLP:conf/kr/DilkasB23}. The
+previously examined by Dilkas and Belle~\cite{DBLP:conf/kr/DilkasB23}. The
 second benchmark is a variant of the well-known `Friends and Smokers' Markov
@@
 \end{gather*}
-Finally, we include the bijection-counting problem previously utilised by
-\citeauthor{DBLP:conf/kr/DilkasB23}~\shortcite{DBLP:conf/kr/DilkasB23}. Its
-formulation in \FO{} is described in \cref{example:overall}. The equivalent
-formula in \Ctwo{} is
+Finally, we include the bijection-counting problem previously utilised by Dilkas
+and Belle~\cite{DBLP:conf/kr/DilkasB23}. Its formulation in \FO{} is described
+in \cref{example:overall}. The equivalent formula in \Ctwo{} is
 \begin{align*}
@@
 
-\section{Reproducibility Checklist}
-
-This paper:
-\begin{itemize}
-  \item Includes a conceptual outline and/or pseudocode description of AI
-        methods introduced (\textbf{yes}/partial/no/NA)
-  \item Clearly delineates statements that are opinions, hypothesis, and
-        speculation from objective facts and results (\textbf{yes}/no)
-  \item Provides well marked pedagogical references for less-familiare readers
-        to gain background necessary to replicate the paper (\textbf{yes}/no)
-\end{itemize}
-
-Does this paper make theoretical contributions? (\textbf{yes}/no) If yes, please
-complete the list below.
-
-\begin{itemize}
-  \item All assumptions and restrictions are stated clearly and formally.
-        (\textbf{yes}/partial/no)
-  \item All novel claims are stated formally (e.g., in theorem statements).
-        (\textbf{yes}/partial/no)
-  \item Proofs of all novel claims are included. (\textbf{yes}/partial/no)
-  \item Proof sketches or intuitions are given for complex and/or novel results.
-        (\textbf{yes}/partial/no)
-  \item Appropriate citations to theoretical tools used are given.
-        (\textbf{yes}/partial/no)
-  \item All theoretical claims are demonstrated empirically to hold.
-        (\textbf{yes}/partial/no/NA)
-  \item All experimental code used to eliminate or disprove claims is included.
-        (yes/no/\textbf{NA})
-\end{itemize}
-
-Does this paper rely on one or more datasets? (\textbf{yes}/no) If yes, please
-complete the list below.
-
-\begin{itemize}
-  \item A motivation is given for why the experiments are conducted on the
-        selected datasets (\textbf{yes}/partial/no/NA)
-  \item All novel datasets introduced in this paper are included in a data
-        appendix. (\textbf{yes}/partial/no/NA)
-  \item All novel datasets introduced in this paper will be made publicly
-        available upon publication of the paper with a license that allows free
-        usage for research purposes. (\textbf{yes}/partial/no/NA)
-  \item All datasets drawn from the existing literature (potentially including
-        authors’ own previously published work) are accompanied by appropriate
-        citations. (\textbf{yes}/no/NA)
-  \item All datasets drawn from the existing literature (potentially including
-        authors’ own previously published work) are publicly available.
-        (\textbf{yes}/partial/no/NA)
-  \item All datasets that are not publicly available are described in detail,
-        with explanation why publicly available alternatives are not
-        scientifically satisficing. (\textbf{yes}/partial/no/NA)
-\end{itemize}
-
-Does this paper include computational experiments? (\textbf{yes}/no) If yes,
-please complete the list below.
-
-\begin{itemize}
-  \item Any code required for pre-processing data is included in the appendix.
-        (\textbf{yes}/partial/no).
-  \item All source code required for conducting and analyzing the experiments is
-        included in a code appendix. (\textbf{yes}/partial/no)
-  \item All source code required for conducting and analyzing the experiments
-        will be made publicly available upon publication of the paper with a
-        license that allows free usage for research purposes.
-        (\textbf{yes}/partial/no)
-  \item All source code implementing new methods have comments detailing the
-        implementation, with references to the paper where each step comes from
-        (yes/\textbf{partial}/no)
-  \item If an algorithm depends on randomness, then the method used for setting
-        seeds is described in a way sufficient to allow replication of results.
-        (yes/partial/no/\textbf{NA})
-  \item This paper specifies the computing infrastructure used for running
-        experiments (hardware and software), including GPU/CPU models; amount of
-        memory; operating system; names and versions of relevant software
-        libraries and frameworks. (\textbf{yes}/partial/no)
-  \item This paper formally describes evaluation metrics used and explains the
-        motivation for choosing these metrics. (\textbf{yes}/partial/no)
-  \item This paper states the number of algorithm runs used to compute each
-        reported result. (\textbf{yes}/no)
-  \item Analysis of experiments goes beyond single-dimensional summaries of
-        performance (e.g., average; median) to include measures of variation,
-        confidence, or other distributional information. (\textbf{yes}/no)
-  \item The significance of any improvement or decrease in performance is judged
-        using appropriate statistical tests (e.g., Wilcoxon signed-rank).
-        (\textbf{yes}/partial/no)
-  \item This paper lists all final (hyper-)parameters used for each
-        model/algorithm in the paper’s experiments. (yes/partial/no/\textbf{NA})
-  \item This paper states the number and range of values tried per (hyper-)
-        parameter during development of the paper, along with the criterion used
-        for selecting the final parameter setting. (yes/partial/no/\textbf{NA})
-\end{itemize}
-
 \end{document}

### 2025-01-12 doc/paper/paper.tex
Adjust to the new margins

@@
   \begin{equation}\label[formula]{eq:functions1}
-    \begin{gathered}
-      (\forall x, y \in \Delta\text{. }S(x) \lor \neg P(x, y)) \land{}\\
-      (|P| = |\Delta|),
-    \end{gathered}
+    (\forall x, y \in \Delta\text{. }S(x) \lor \neg P(x, y)) \land (|P| = |\Delta|),
   \end{equation}
@@
     \begin{gathered}
-      (\forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }P(x, y)) \land{}\\
-      (\forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z).
+      (\forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }P(x, y)) \land (\forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z).
     \end{gathered}
@@
   \begin{tikzpicture}
-    \node at (-1, 0) (formula) {$\phi$};
+    \node[anchor=west] at (-1, 0) (formula) {$\phi$};
     \node[draw,rounded rectangle] at (3, 0) (compilewithbasecases) {\CompileWithBaseCases};
@@
 
-    \node[draw,rounded rectangle,dashed] at (12, 0) (cpp) {C++ code};
-    \node at (12, -1) (sizes) {Domain sizes};
-
-    \node at (15, 0) (count) {Model count};
+    \node[draw,rounded rectangle,dashed] at (9, -3) (cpp) {C++ code};
+    \node[anchor=west] at (-1, -3) (sizes) {Domain sizes};
+    \node at (12, -3) (count) {Answer};
 
@@
     \node[draw,fit={(compilewithbasecases) (compilation) (crane) (findbasecases) (propagate)},inner ysep=7pt,yshift=5pt] {};
-    \node at (0.6, 0.5) {\Cranetwo};
+    \node at (0.7, 0.5) {\Cranetwo};
 
@@
   \KwOut{set $\mathcal{E}$ of equations}
-  $(\mathcal{E}, \mathcal{F}, \mathcal{D}) \gets \Compile{$\phi$}$\;\label{line:first}
+  $(\mathcal{E}, \mathcal{F}, \mathcal{D}) \gets \Compile{$\phi$}$\;
   $\mathcal{E} \gets \Simplify{$\mathcal{E}$}$\;\label{line:second}
@@
     $\psi \gets \mathcal{F}(f)$\;
-    \ForEach{index $i$ such that $x_{i} \in \mathbb{N}_{0}$}{\label{line:loop}
-      $\psi \gets \Propagate{$\psi$, $\mathcal{D}(f, i)$, $x_i$}$\;
-    }
+    \lForEach{index $i$ such that $x_{i} \in \mathbb{N}_{0}$}{$\psi \gets \Propagate{$\psi$, $\mathcal{D}(f, i)$, $x_i$}$}
     $\mathcal{E} \gets \mathcal{E} \cup \CompileWithBaseCases{$\psi$}$\;\label{line:final}
@@
   $\mathcal{B} \gets \emptyset$\;
-  \ForEach{function call $f(\mathbf{y})$ on the right-hand side of an equation in $\mathcal{E}$}{\label{line:functioncall}
+  \ForEach{function call $f(\mathbf{y})$ on the right-hand side of an equation in $\mathcal{E}$}{
     $\mathbf{x} \gets \text{the parameters of $f$ in its definition}$\;
     \ForEach{$y_{i} \in \mathbf{y}$} {
-      \uIf{$y_{i} \in \mathbb{N}_{0}$}{
-        $\mathcal{B} \gets \mathcal{B} \cup \{\, f(\mathbf{x})[x_{i} \mapsto y_{i}] \,\}$\;
-      }
+      \lIf{$y_{i} \in \mathbb{N}_{0}$}{$\mathcal{B} \gets \mathcal{B} \cup \{\, f(\mathbf{x})[x_{i} \mapsto y_{i}] \,\}$}
       \ElseIf{$y_{i} = x_{i} - c_{i}$ for some $c_{i} \in \mathbb{N}_{0}$}{
-        \For{$j \gets 0$ \KwTo $c_{i} - 1$}{\label{line:lim}
-          $\mathcal{B} \gets \mathcal{B} \cup \{\, f(\mathbf{x})[x_{i} \mapsto j] \,\}$\;\label{line:insert}
-        }
+        \lFor{$j \gets 0$ \KwTo $c_{i} - 1$}{$\mathcal{B} \gets \mathcal{B} \cup \{\, f(\mathbf{x})[x_{i} \mapsto j] \,\}$}
       }
@@
       \lIf{$m = 0$}{$\phi' \gets \phi' \cup \{\, C \,\}$}
-      \Else{
-        $\phi' \gets \phi' \cup \{\, C[x_{1} \mapsto c_{1}, \dots, x_{m} \mapsto c_{m}] \mid {(c_{i})}_{i=1}^{m} \in D^{m} \,\}$\;
-      }
+      \lElse{$\phi' \gets \phi' \cup \{\, C[x_{1} \mapsto c_{1}, \dots, x_{m} \mapsto c_{m}] \mid {(c_{i})}_{i=1}^{m} \in D^{m} \,\}$}
     }
@@
     \vdots&\\
-    (\forall x \in \Gamma\text{. }\neg P(x, c_{3}) \lor& \neg P(x, c_{3}) \lor c_{3}=c_{3}).\\
+    (\forall x \in \Gamma\text{. }\neg P(x, c_{3}) \lor& \neg P(x, c_{3}) \lor c_{3}=c_{3}).
   \end{align*}
@@
 \begin{example}\label{example:basecasesmoothing}
-  Let $\phi$ be:
+  Let $\phi$ be
   \begin{align}
@@
   $\{\, P(y, z) \mid y, z \in \Gamma' \,\}$. By including
-  \autoref{line:smoothing2}, \Propagate transforms $\phi$ to:
-  \begin{gather*}
-    (\forall y, z \in \Gamma\text{. }P(y, z) \lor \neg P(y, z))\land{}\\
-    (\forall y, z \in \Gamma'\text{. }P(y, z)),
-  \end{gather*}
+  \autoref{line:smoothing2}, \Propagate transforms $\phi$ to
+  \[
+    (\forall y, z \in \Gamma\text{. }P(y, z) \lor \neg P(y, z)) \land (\forall y, z \in \Gamma'\text{. }P(y, z)),
+  \]
   which retains the correct model count.
@@
 
-Our empirical evaluation sought to compare the runtime performance of {\Cranetwo} with the current state of the art, namely
-\textsc{FastWFOMC} and \textsc{ForcLift}. It is worth remarking that  \textsc{ForcLift} does not support arbitrary precision, and returns error for cases that requires arbitrary precision reasoning.
-Our experiments involve two versions
-of \Cranetwo{}: \Cranegreedy{} and \Cranebfs{}. Like its predecessor,
-\Cranetwo{} has two modes for applying compilation rules to formulas: one that
-uses a greedy search algorithm similar to \textsc{ForcLift} and another that
-combines greedy and breadth-first search.
+Our empirical evaluation sought to compare the runtime performance of
+{\Cranetwo} with the current state of the art, namely \textsc{FastWFOMC} and
+\textsc{ForcLift}. It is worth remarking that \textsc{ForcLift} does not support
+arbitrary precision, and returns error for cases that requires arbitrary
+precision reasoning. Our experiments involve two versions of \Cranetwo{}:
+\Cranegreedy{} and \Cranebfs{}. Like its predecessor, \Cranetwo{} has two modes
+for applying compilation rules to formulas: one that uses a greedy search
+algorithm similar to \textsc{ForcLift} and another that combines greedy and
+breadth-first search.
 
@@
 \Ctwo{}, \FO{}, and \UFO{}, this problem can be formulated as
-\begin{gather*}
-  (\forall x,y \in \Delta\text{. } S(x) \land F(x, y) \Rightarrow S(y)) \land{}\\
-  (\forall x \in \Delta\text{. }S(x) \Rightarrow C(x))
-\end{gather*}
+\[
+  (\forall x,y \in \Delta\text{. } S(x) \land F(x, y) \Rightarrow S(y)) \land (\forall x \in \Delta\text{. }S(x) \Rightarrow C(x))
+\]
 or, equivalently, in conjunctive normal form as
-\begin{gather*}
-  (\forall x,y \in \Delta\text{. }S(y) \lor \neg S(x) \lor \neg F(x, y)) \land{}\\
-  (\forall x \in \Delta\text{. } C(x) \lor \neg S(x)).
-\end{gather*}
+\[
+  (\forall x,y \in \Delta\text{. }S(y) \lor \neg S(x) \lor \neg F(x, y)) \land (\forall x \in \Delta\text{. } C(x) \lor \neg S(x)).
+\]
 Finally, we include the bijection-counting problem previously utilised by Dilkas
@@
 in \cref{example:overall}. The equivalent formula in \Ctwo{} is
-\begin{align*}
-  (\forall x \in \Delta\text{. }\exists^{=1} y \in \Delta&\text{. }P(x, y))\land{}\\
-  (\forall y \in \Delta\text{. }\exists^{=1} x \in \Delta&\text{. }P(x, y)).
-\end{align*}
+\[
+  (\forall x \in \Delta\text{. }\exists^{=1} y \in \Delta\text{. }P(x, y)) \land (\forall y \in \Delta\text{. }\exists^{=1} x \in \Delta\text{. }P(x, y)).
+\]
 Similarly, in \UFO{} the same formula can be written as
-\begin{gather*}
-  (\forall x, y \in \Delta\text{. }R(x) \lor \neg P(x, y))\land{}\\
-  (\forall x, y \in \Delta\text{. }S(x) \lor \neg P(y, x))\land{}\\
-  (|P| = |\Delta|),
-\end{gather*}
+\[
+  (\forall x, y \in \Delta\text{. }R(x) \lor \neg P(x, y)) \land (\forall x, y \in \Delta\text{. }S(x) \lor \neg P(y, x)) \land (|P| = |\Delta|),
+\]
 where $w^{-}(R) = w^{-}(S) = -1$.
@@
 \end{figure*}
+% TODO: shrink to fit into the margins
 

### 2025-01-14 doc/paper/paper.tex
Update front matter

@@
 
-\author{Ananth K. Kidambi}{Indian Institute of Technology Bombay, Mumbai, India}{}{}{TODO: funding}
-\author{Guramrit Singh}{Indian Institute of Technology Bombay, Mumbai, India}{}{}{TODO: funding}
-\author{Paulius Dilkas}{University of Toronto, Toronto, Canada \and Vector Institute, Toronto, Canada}{}{}{TODO: funding}
-\author{Kuldeep S. Meel}{University of Toronto, Toronto, Canada}{}{}{TODO: funding}
+\author{Ananth K. Kidambi}{Indian Institute of Technology Bombay, Mumbai, India}{210051002@iitb.ac.in}{}{TODO: funding}
+\author{Guramrit Singh}{Indian Institute of Technology Bombay, Mumbai, India}{guramrit@iitb.ac.in}{}{TODO: funding}
+\author{Paulius Dilkas}{University of Toronto, Toronto, Canada \and Vector Institute, Toronto, Canada \and \url{https://dilkas.github.io/}}{paulius.dilkas@utoronto.ca}{https://orcid.org/0000-0001-9185-7840}{TODO: funding}
+\author{Kuldeep S. Meel}{University of Toronto, Toronto, Canada \and \url{https://www.cs.toronto.edu/~meel/}}{meel@cs.toronto.edu}{https://orcid.org/0000-0001-9423-5270}{TODO: funding}
 
 \authorrunning{A.\,K. Kidambi, G. Singh, P. Dilkas, and K.\,S. Meel}
-
 \Copyright{Ananth K. Kidambi, Guramrit Singh, Paulius Dilkas, and Kuldeep S. Meel}
 
-\ccsdesc{Computing methodologies~Knowledge representation and reasoning}
+\ccsdesc{Theory of computation~Automated reasoning}
+\ccsdesc{Theory of computation~Logic and verification}
+\ccsdesc{Mathematics of computing~Combinatorics}
 

### 2025-01-16 doc/paper/paper.tex
Add AAAI feedback
Move TODOs around
Rewrite inline enumerates

@@
 
-%\acknowledgements{I want to thank \dots}%optional
+\acknowledgements{Part of the research was conducted while all authors were at the National University of Singapore.}
 
@@
 \creflabelformat{formula}{#2\textup{(#1)}#3}
+
+% TODO: the technical appendix should follow the same template (probably just
+% integrate it into the main paper)
+
+% TODO (for the entire paper):
+% * 15 pages excluding references
+% * draw a clear line between prior work and new developments
 
@@
 \section{Introduction}
+% TODO: We would like to clarify that the main contribution of this work
+% consists of everything needed to complement recursive function definitions
+% with the necessary base cases. This process includes identifying the base
+% cases and their corresponding formulas, transforming them (including applying
+% a new smoothing procedure), and recursively reusing Crane. C++ code
+% generation, although relatively straightforward, is crucial for the usability
+% of the algorithm
+
+% TODO: focus more on current work
 
@@
 
+% TODO: don't assume that the reader knows FOMC and FOMC algorithms
+
+% TODO: It would be nice to give the necessary introduction to FOKC, or CRANE
+% (an intuitive explanation early in the paper)
+
+% TODO: The principal motivation of a knowledge compilation-based approach to
+% FOMC comes from its ability to find polynomial-time solutions, where the
+% polynomial has a lower degree compared to, e.g., FastWFOMC (Dilkas and Belle,
+% 2023). The ability of the algorithm to mathematically describe recursive
+% solutions is also noteworthy as the only other available alternative is to
+% guess them (Barvı́nek, van Bremen, Wang, Zelezný, Kuzelka, ILP 2021).
 FOMC algorithms are diverse, with approaches ranging from \emph{first-order
@@
 range of formulas handled by FOMC algorithms. However, it had notable
-limitations:
-\begin{enumerate}
-  \item it required manual evaluation of function definitions to compute model
-  counts, and
-  \item it introduced recursive functions without proper base cases, making it
-  more complex to use.
-\end{enumerate}
-To address these shortcomings, we present \Cranetwo{}, a fully automated FOMC
-algorithm that overcomes the constraints of its predecessor. \Cranetwo{} can
-handle domain sizes over \num{500000} times larger than previous algorithms and
-simplifies the user experience by automatically handling base cases and
-compiling function definitions into efficient C++ programs.
+limitations: it required manual evaluation of function definitions to compute
+model counts and introduced recursive functions without proper base cases,
+making it more complex to use. To address these shortcomings, we present
+\Cranetwo{}, a fully automated FOMC algorithm that overcomes the constraints of
+its predecessor. \Cranetwo{} can handle domain sizes over \num{500000} times
+larger than previous algorithms and simplifies the user experience by
+automatically handling base cases and compiling function definitions into
+efficient C++ programs.
 
@@
 
+% TODO: focus more on current work
+
+% TODO: Section 2 until 2.3 (Algebra) could be drastically shortened
+
 In \cref{sec:logic}, we summarise the basic principles of first-order logic.
@@
 
+% TODO: Skolemization is a procedure that transforms a formula with existential
+% quantifiers into an ’equivalent’ formula without existential quantifiers with
+% the same WFOMC.
 In this section, we will review the basic concepts of first-order logic as they
@@
 A \emph{term} can be either a variable or a constant. An \emph{atom} can be
-either
-\begin{enumerate}
-  \item $P(t_{1}, \dots, t_{m})$ for some predicate $P$ and terms
-  $t_{1}, \dots, t_{m}$ (written as $P(\mathbf{t})$ for short) or
-  \item $x=y$ for some terms $x$ and $y$.
-\end{enumerate}
-The \emph{arity} of a predicate is the number of arguments it takes, i.e., $m$
-in the case of the predicate $P$ mentioned above. We write $P/m$ to denote a
+either $P(t_{1}, \dots, t_{m})$ (or $P(\mathbf{t})$) for some predicate $P$ and
+terms $t_{1}, \dots, t_{m}$ or $x=y$ for some terms $x$ and $y$. The
+\emph{arity} of a predicate is the number of arguments it takes, i.e., $m$ in
+the case of the predicate $P$ mentioned above. We write $P/m$ to denote a
 predicate along with its arity. A \emph{literal} can be either an atom (i.e., a
@@
 that only contain variables $x_{1}, \dots, x_{n}$ (and any constants). We say
-that a clause is a \emph{(positive) unit clause} if
-\begin{enumerate}
-  \item there is only one literal with a predicate, and
-  \item it is a positive literal.
-\end{enumerate}
-Finally, a \emph{formula} is a conjunction of clauses. Throughout the paper, we
-will use set-theoretic notation, interpreting a formula as a set of clauses and
-a clause as a set of literals.
+that a clause is a \emph{(positive) unit clause} if there is only one literal
+with a predicate, and it is a positive literal. Finally, a \emph{formula} is a
+conjunction of clauses. Throughout the paper, we will use set-theoretic
+notation, interpreting a formula as a set of clauses and a clause as a set of
+literals.
+
+% TODO: Page 2, Section 2.1, paragraph 2, line 10 - ”A clause is of the form ...” - are the quantifiers really part of the clause?
+Shouldn’t it be possible to quantify a conjunction of several clauses?
+% Conforming with previous work, the definition of a clause includes universal quantifiers for all variables within.
+While it is possible to rewrite the entire formula in prenex normal form, the format we describe has proven itself convenient to work with.
 
 \subsection{FOMC Algorithms and Their Logics}\label{sec:threelogics}
+
+% TODO: shorten the part about the three logics
 
@@
   \end{tabular}
-  \caption[]{A comparison of the three logics used in FOMC based on the following aspects:
-    \begin{enumerate}
-      \item the number of sorts,
-      \item support for constants,
-      \item the maximum number of variables,
-      \item supported quantifiers, and
-      \item supported atoms in addition to those of the form $P(\mathbf{t})$ for a predicate $P/n$ and an $n$-tuple of terms $\mathbf{t}$.
-    \end{enumerate}
-    Here:
-    \begin{enumerate}
-      \item $k$ and $m$ are non-negative integers, with the latter depending on the domain size,
-      \item $P$ represents a predicate, and
-      \item $x$ and $y$ are terms.
-    \end{enumerate}
-  }\label{tbl:logics}
+  \caption{A comparison of the three logics used in FOMC\@. The
+    2\textsuperscript{nd}--5\textsuperscript{th} columns refer to: the number of
+    sorts, support for constants, the maximum number of variables, and supported
+    quantifiers, respectively. The last column lists supported atoms in addition
+    to those of the form $P(\mathbf{t})$ for a predicate $P/n$ and an $n$-tuple
+    of terms $\mathbf{t}$. Here: $k$ and $m$ are non-negative integers, with the
+    latter depending on the domain size, $P$ represents a predicate, and $x$ and
+    $y$ are terms. }\label{tbl:logics}
 \end{table*}
@@
 In \cref{tbl:logics}, we outline the differences among three first-order logics
-commonly used in FOMC:
-\begin{enumerate}
-  \item \FO{} is the input format for
+commonly used in FOMC: \FO{}, \Ctwo{}, and \UFO{}. First, \FO{} is the input
+format for
 \textsc{ForcLift}\footnote{\url{https://github.com/UCLA-StarAI/Forclift}} and
@@
 \textsc{Crane}\footnote{\url{https://doi.org/10.5281/zenodo.8004077}} and
-  \Cranetwo{};
-  \item \Ctwo{} is often used in the literature on \textsc{FastWFOMC} and
-  related
-  methods~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22};
-  \item \UFO{} is the input format supported by the most recent implementation
-  of
-  \textsc{FastWFOMC}\footnote{\url{https://github.com/jan-toth/FastWFOMC.jl}}.
-\end{enumerate}
-The notation we use to refer to each logic is standard in the case of \Ctwo{}
-and \UFO{}~\cite{tóth2024complexityweightedfirstordermodel} and redefined to be
-more specific in the case of \FO{}. All three logics are function-free, and
-domains are always assumed to be finite. As usual, we presuppose the
-\emph{unique name assumption}, which states that two constants are equal if and
-only if they are the same constant~\cite{DBLP:books/aw/RN2020}.
+\Cranetwo{}. Second, \Ctwo{} is often used in the literature on
+\textsc{FastWFOMC} and related
+methods~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}. Finally,
+\UFO{} is the input format supported by the most recent implementation of
+\textsc{FastWFOMC}\footnote{\url{https://github.com/jan-toth/FastWFOMC.jl}}. The
+notation we use to refer to each logic is standard in the case of \Ctwo{} and
+\UFO{}~\cite{tóth2024complexityweightedfirstordermodel} and redefined to be more
+specific in the case of \FO{}. All three logics are function-free, and domains
+are always assumed to be finite. As usual, we presuppose the \emph{unique name
+  assumption}, which states that two constants are equal if and only if they are
+the same constant~\cite{DBLP:books/aw/RN2020}.
 
@@
 
-Compared to \FO{}, \Ctwo{} and \UFO{} lack support for
-\begin{enumerate}
-  \item constants,
-  \item the equality predicate,
-  \item multiple domains, and
-  \item formulas with more than two variables.
-\end{enumerate}
-The advantage that \Ctwo{} brings over \FO{} is the inclusion of \emph{counting
+Compared to \FO{}, \Ctwo{} and \UFO{} lack support for constants, the equality
+predicate, multiple domains, and formulas with more than two variables. The
+advantage that \Ctwo{} brings over \FO{} is the inclusion of \emph{counting
   quantifiers}. That is, alongside $\forall$ and $\exists$, \Ctwo{} supports
@@
   ${(\Delta_{i}^{P})}_{i=1}^{n}$ be a list of the corresponding domains. Let
-  $\sigma$ be a map from the domains of $\phi$ to their interpretations as sets,
-  satisfying the following conditions:
-  \begin{enumerate}
-    \item the sets are pairwise disjoint, and
-    \item the constants in $\phi$ are included in the corresponding domains.
-  \end{enumerate}
-  A \emph{structure} of $\phi$ is a set $M$ of ground literals defined by adding
-  to $M$ either $P(\mathbf{t})$ or $\neg P(\mathbf{t})$ for every predicate
-  $P/n$ in $\phi$ and $n$-tuple
+  $\sigma$ be a map from the domains of $\phi$ to their interpretations as sets
+  such that the sets are pairwise disjoint, and the constants in $\phi$ are
+  included in the corresponding domains. A \emph{structure} of $\phi$ is a set
+  $M$ of ground literals defined by adding to $M$ either $P(\mathbf{t})$ or
+  $\neg P(\mathbf{t})$ for every predicate $P/n$ in $\phi$ and $n$-tuple
   $\mathbf{t} \in \prod_{i=1}^{n} \sigma(\Delta_{i}^{P})$. A structure is a
@@
 \end{definition}
+% TODO: Page 2, Definition 1 - ”A structure is a model if it satisfies ϕ” - do you mean that it makes ϕ valid?
 
@@
 problem as Skolemization relies on weights even for unweighted FOMC.
+% TODO: Even though we are evaluating the algorithms on FOMC benchmarks, for
+% sentences with existential quantifiers, computing FOMC using Gantry requires
+% the use of WFOMC. For such sentences, Skolemization introduces predicates with
+% non-unary weights that must be accounted for to compute the correct model
+% count.
 
 \begin{definition}[WFOMC instance]\label{def:instance}
-  A \emph{WFOMC instance} comprises:
-  \begin{enumerate}
-    \item a formula $\phi$ in \FO{},
-    \item two (rational) \emph{weights} $w^{+}(P)$ and $w^{-}(P)$ assigned to
-    each predicate $P$ in $\phi$, and
-    \item $\sigma$ as described in \cref{def:model}.
-  \end{enumerate}
-  Unless specified otherwise, we assume all weights to be equal to 1.
+  A \emph{WFOMC instance} comprises: a formula $\phi$ in \FO{}, two (rational)
+  \emph{weights} $w^{+}(P)$ and $w^{-}(P)$ assigned to each predicate $P$ in
+  $\phi$, and $\sigma$ as described in \cref{def:model}. Unless specified
+  otherwise, we assume all weights to be equal to 1.
 \end{definition}
@@
 
+% TODO: this subsection could be expanded a little
+
 We write $\expr{}$ to represent an arbitrary algebraic expression. It is
@@
 
+% TODO: The algorithm’s recursive nature and its interaction with CRANE could be
+% explained more clearly
+
+% TODO: more emphasis on the motivation for each part of GANTRY (e.g., how
+% FindBaseCases addresses key issues in CRANE) would add depth to the
+% contribution.
+
+% TODO: Section 3: you seem to use "equation" and "function" interchangeably
+
+% TODO: this section "would benefit from cleaner reasoning"
+
+% TODO: this section should be expanded by 1 page ("a clear discussion of the
+% innovation aspect and technical parts")
+
 \begin{figure*}[t]
@@
   \end{tikzpicture}
-  \caption[]{The outline of using \Cranetwo{} to compute the model count of a formula $\phi$.
-First, the formula is compiled into a set of equations, which are then used to create a C++ program.
-This program can be executed with different command line arguments to calculate the model count of $\phi$ for different domain sizes.
-To accomplish this, the \CompileWithBaseCases function employs several components:
-    \begin{enumerate}
-      \item the FOKC algorithm of \textsc{Crane},
-      \item a procedure called \FindBaseCases, which identifies a sufficient set of base cases,
-      \item a procedure called \Propagate, which constructs a formula corresponding to a given base case, and
-      \item algebraic simplification techniques (denoted as \Simplify).
-    \end{enumerate}
-  }\label{fig:overview}
+  \caption[]{The outline of using \Cranetwo{} to compute the model count of a
+    formula $\phi$. First, the formula is compiled into a set of equations,
+    which are then used to create a C++ program. This program can be executed
+    with different command line arguments to calculate the model count of $\phi$
+    for different domain sizes. To accomplish this, the \CompileWithBaseCases
+    function makes use of the FOKC algorithm of \textsc{Crane}, algebraic
+    simplification techniques (denoted as \Simplify), and two other auxiliary
+    procedures. }\label{fig:overview}
 \end{figure*}
@@
 essential aspects of FOKC as realised by \textsc{Crane}. The input formula is
-compiled into:
-\begin{enumerate}
-  \item set $\mathcal{E}$ of equations,
-  \item map $\mathcal{F}$ from function names to formulas, and
-  \item map $\mathcal{D}$ from function names and argument indices to domains.
-\end{enumerate}
-$\mathcal{E}$ can contain any number of functions, one of which (denoted by $f$)
-represents the solution to the FOMC problem. To compute the FOMC for particular
-domain sizes, $f$ must be evaluated with those domain sizes as arguments.
-$\mathcal{D}$ records this correspondence between function arguments and
-domains.
+compiled into: set $\mathcal{E}$ of equations, map $\mathcal{F}$ from function
+names to formulas, and map $\mathcal{D}$ from function names and argument
+indices to domains. $\mathcal{E}$ can contain any number of functions, one of
+which (denoted by $f$) represents the solution to the FOMC problem. To compute
+the FOMC for particular domain sizes, $f$ must be evaluated with those domain
+sizes as arguments. $\mathcal{D}$ records this correspondence between function
+arguments and domains.
 
@@
 
+% TODO: move this example right after the definition of WFOMC (or near the
+% definition of a model)
 \begin{example}[Counting bijections]\label{example:overall}
@@
 Finally, the main responsibility of the \Simplify procedure is to handle the
-algebraic pattern $\sum_{m=0}^{n}[a \le m \le b] f(m)$. Here:
-\begin{enumerate}
-  \item $n$ is a variable,
-  \item $a, b \in \mathbb{N}_{0}$ are constants,
-  \item $f$ is an expression that may depend on $m$, and
-  \item $[a \le m \le b] =
-  \begin{cases}
+algebraic pattern $\sum_{m=0}^{n}[a \le m \le b] f(m)$. Here: $n$ is a variable,
+$a, b \in \mathbb{N}_{0}$ are constants, and $f$ is an expression that may
+depend on $m$. Additionally, $[a \le m \le b] = \begin{cases}
   1 & \text{if $a \le m \le b$} \\
@@
 \end{cases}$.
-\end{enumerate}
 \Simplify transforms this pattern into
@@
 \subsection{Identifying a Sufficient Set of Base Cases}\label{sec:identifying}
+% TODO: prove correctness?
 
@@
 
-\Cref{alg:findbasecases} summarises the implementation of \FindBaseCases.
-\FindBaseCases considers two types of arguments when a function $f$ calls itself
-recursively:
-\begin{enumerate}
-  \item constants and
-  \item arguments of the form $x_{i} - c_{i}$, where $c_{i}$ is a constant and
-  $x_{i}$ is the $i$-th argument of the signature of $f$.
-\end{enumerate}
-When the argument is a constant $c_{i}$, a base case with $c_{i}$ is added. In
-the second case, a base case is added for each constant from $0$ up to (but not
-including) $c_{i}$.
+\Cref{alg:findbasecases} summarises the implementation of \FindBaseCases. It
+considers two types of arguments when a function $f$ calls itself recursively:
+constants and arguments of the form $x_{i} - c_{i}$. Here, $c_{i}$ is a
+constant, and $x_{i}$ is the $i$-th argument of the signature of $f$. When the
+argument is a constant $c_{i}$, a base case with $c_{i}$ is added. In the second
+case, a base case is added for each constant from $0$ up to (but not including)
+$c_{i}$.
 
@@
 
+% NOTE: keep this enumerate
 In the case of $n = 0$, there are three types of clauses to consider:
@@
 \subsection{Generating C++ Code}\label{sec:cpp}
+% TODO (must): expand this section
+% TODO: The purpose of C++ code generation is to turn mathematical equations into executable code.
 
@@
 
+% TODO Experiments could be expanded by 1 page ("a more thorough and independent
+% practical assessment")
+
+% TODO: this section "would benefit from cleaner reasoning"
+
+% TODO: The difference between Gantry-Greedy and Gantry-BFS is in how the
+% algorithm chooses which compilation rule to apply to a formula. The former
+% uses greedy search: there is a list of rules, and the first applicable rule is
+% the one that gets used, disregarding all the others. The latter uses a
+% combination of greedy and breadth-first search (BFS). That is, each
+% compilation rule is identified as either greedy or non-greedy. Greedy rules
+% are applied as soon as possible at any stage of the compilation process. BFS
+% is executed over all applicable non-greedy rules, identifying the solution
+% that can be constructed using the smallest number of such rules.
+
 Our empirical evaluation sought to compare the runtime performance of
@@
 \subsection{Benchmarks}
+% TODO: more benchmarks from NOT my work
+% TODO: make sure it's clear what the 'raw' instances are
+% TODO: don't emphasise that the benchmarks come from my previous work
+
 We compare these algorithms using three benchmarks from previous studies. The
@@
 \end{figure*}
-% TODO: shrink to fit into the margins
+% TODO: shrink/restructure to fit into the margins
 
@@
 \subsection{Results}
+
+% TODO: On the ’friends’ and ’functions’ benchmarks, ForcLift runs until the
+% model count exceeds 231 − 1.
+
+% TODO: We are not aware of any formulas on which Gantry scales worse compared
+% to either ForcLift or FastWFOMC. The one advantage that FastWFOMC has over
+% Gantry is its support for counting quantifiers.
+
+% TODO: Regarding programming languages and accuracy, we verified that the
+% answers match for smaller domain sizes. Also, although written in different
+% languages, both Gantry and FastWFOMC use the GNU Multiple Precision Arithmetic
+% Library.
+
 \Cref{fig:plot} presents a summary of the experimental results. Only

### 2025-01-16 doc/paper/paper.tex
Add proofs

@@
 \sisetup{group-separator = {,}}
+\newtheorem{assumption}[theorem]{Assumption}
 
@@
 
-% TODO: the technical appendix should follow the same template (probably just
-% integrate it into the main paper)
-
 % TODO (for the entire paper):
 % * 15 pages excluding references
-% * draw a clear line between prior work and new developments
 
@@
   work~\cite{DBLP:conf/kr/DilkasB23,tóth2024complexityweightedfirstordermodel}
-  and are orthogonal to the goals of this section.}
+  and are orthogonal to the goals of this section.} For the remainder of this
+section, let $\mathcal{E}$ denote the equations returned by
+\CompileWithBaseCases.
 
 \begin{theorem}[Termination]\label{thm:halting}
-  Let $\mathcal{E}$ represent the equations returned by \CompileWithBaseCases.
   Let $f$ be an $n$-ary function in $\mathcal{E}$ and
@@
 the number of functions in $\mathcal{E}$. Then, we use induction on the arity of
-the `last' function in $\mathcal{E}$ according to some topological ordering. For
-the detailed proof, please refer to the technical appendix.
+the `last' function in $\mathcal{E}$ according to some topological ordering. We
+begin with a few observations that stem from
+previous~\cite{DBLP:conf/kr/DilkasB23,DBLP:conf/ijcai/BroeckTMDR11} and this
+work. Let $\mathcal{E}$ represent the equations returned by
+\CompileWithBaseCases.
+
+\begin{observation}\label{assumption1}
+  For each function $f$, there is precisely one equation $e \in \mathcal{E}$
+  with $f(\mathbf{x})$ on the left-hand side where all $x_{i}$'s are variables
+  (i.e., $e$ is not a base case). We refer to $e$ as the \emph{definition} of
+  $f$.
+\end{observation}
+
+\begin{observation}\label{assumption2}
+  There is a \emph{topological ordering} of all functions ${(f_{i})}_{i}$ in
+  $\mathcal{E}$ such that equations in $\mathcal{E}$ with $f_{i}$ on the
+  left-hand side do not contain function calls to $f_{j}$ with $j > i$. This
+  condition prevents mutual recursion and other cyclic scenarios.
+\end{observation}
+
+\begin{observation}\label{assumption3}
+  For every equation $(f(\mathbf{x}) = \expr) \in \mathcal{E}$, the evaluation
+  of $\expr$ terminates when provided with the values of all relevant function
+  calls.
+\end{observation}
+
+\begin{corollary}\label{fact}
+  If $f$ is a non-recursive function with no function calls on the right-hand
+  side of its definition, then the evaluation of any function call
+  $f(\mathbf{x})$ terminates.
+\end{corollary}
+
+\begin{observation}\label{fact2}
+  For any equation $f(\mathbf{x}) = \expr{}$, if $\mathbf{x}$ contains only
+  constants, then $\expr{}$ cannot include any function calls to $f$.
+\end{observation}
+
+Additionally, we introduce an assumption about the structure of recursion.
+
+\begin{assumption}\label{assumption4}
+  For every equation $(f(\mathbf{x}) = \expr) \in \mathcal{E}$, every recursive
+  function call $f(\mathbf{y}) \in \expr$ satisfies the
+  following:
+  \begin{itemize}
+    \item Each $y_{i}$ is either $x_{i} - c_{i}$ or $c_{i}$ for some constant
+          $c_{i}$.
+    \item There exists $i$ such that $y_{i} = x_{i} - c_{i}$ for some
+          $c_{i} > 0$.
+  \end{itemize}
+\end{assumption}
+
+Finally, we assume a particular order of evaluation for function calls using the
+equations in $\mathcal{E}$. Specifically, we assume that base cases are
+considered before the recursive definition. The exact order in which base cases
+are considered is immaterial.
+
+\begin{assumption}
+  When multiple equations in $\mathcal{E}$ match a function call
+  $f(\mathbf{x})$, preference is given to an equation with the most constants on
+  its left-hand side.
+\end{assumption}
+
+With the observations and assumptions mentioned above, we are ready to prove
+\cref{thm:halting}. For readability, we divide the proof into several lemmas of
+increasing generality.
+
+\begin{lemma}\label{lemma:oneunary}
+  Assume that $\mathcal{E}$ consists of just \emph{one unary} function $f$. Then
+  the evaluation of a function call $f(x)$ terminates for any
+  $x \in \mathbb{N}_{0}$.
+\end{lemma}
+\begin{proof}
+  If $f(x)$ is captured by a base case, then its evaluation terminates by
+  \cref{fact,fact2}. If $f$ is not recursive, the evaluation of
+  $f(x)$ terminates by \cref{fact}.
+
+  Otherwise, let $f(y)$ be an arbitrary function call on the right-hand side of
+  the definition of $f(x)$. If $y$ is a constant, then there is a base case for
+  $f(y)$. Otherwise, let $y = x - c$ for some $c > 0$. Then there exists
+  $k \in \mathbb{N}_{0}$ such that $0 \le x - kc \le c-1$. So, after $k$
+  iterations, the sequence of function calls $f(x), f(x-c), f(x-2c),\dots$ will
+  be captured by the base case $f(x \mod c)$.
+\end{proof}
+
+\begin{lemma}\label{lemma:onefunction}
+  Generalising \cref{lemma:oneunary}, let $\mathcal{E}$ be a set of equations
+  for \emph{one} $n$-ary function $f$ for some $n \ge 1$. Then the evaluation of
+  $f(\mathbf{x})$ terminates for any $\mathbf{x} \in \mathbb{N}_{0}^{n}$.
+\end{lemma}
+\begin{proof}
+  If $f$ is non-recursive, the evaluation of $f(\mathbf{x})$ terminates by
+  previous arguments. We proceed by induction on $n$, with the base case of
+  $n=1$ handled by \cref{lemma:oneunary}. Assume that $n > 1$. Any base case of
+  $f$ can be seen as a function of arity $n-1$, since one of the parameters is
+  fixed. Thus, the evaluation of any base case terminates by the inductive
+  hypothesis. It remains to show that the evaluation of the recursive equation
+  for $f$ terminates, but that follows from \cref{assumption3}.
+\end{proof}
+
+\begin{proof}[Proof of \cref{thm:halting}]
+  We proceed by induction on the number of functions $n$. The base case of $n=1$
+  is handled by \cref{lemma:onefunction}. Let ${(f_{i})}_{i=1}^{n}$ be some
+  topological ordering of these $n > 1$ functions. If $f = f_{j}$ for $j < n$,
+  then the evaluation of $f(\mathbf{x})$ terminates by the inductive hypothesis
+  since $f_{j}$ cannot call $f_{n}$ by \cref{assumption2}. Using the inductive
+  hypothesis that all function calls to $f_{j}$ (with $j < n$) terminate, the
+  proof proceeds similarly to the Proof of \cref{lemma:onefunction}.
+\end{proof}
 

### 2025-01-16 doc/paper/paper.tex
Rewrite Section 2.1

@@
 % TODO (for the entire paper):
+% * sentence vs formula: be consistent and not confusing
 % * 15 pages excluding references
@@
 \section{Preliminaries}\label{sec:preliminaries}
-
 % TODO: focus more on current work
-
 % TODO: Section 2 until 2.3 (Algebra) could be drastically shortened
@@
 
-% TODO: Skolemization is a procedure that transforms a formula with existential
-% quantifiers into an ’equivalent’ formula without existential quantifiers with
-% the same WFOMC.
 In this section, we will review the basic concepts of first-order logic as they
-are used in FOKC algorithms. There are two key differences between the logic
-used by these algorithms and the logic supported as input. First,
-Skolemization~\cite{DBLP:conf/kr/BroeckMD14} eliminates existential quantifiers
-by introducing additional predicates. Please note that Skolemization here
-differs from the standard Skolemization procedure that introduces function
-symbols~\cite{DBLP:books/daglib/0030198}. Second, the input formula is rewritten
-as a conjunction of clauses, each in \emph{prenex normal
-  form}~\cite{hinman2018fundamentals}.
+are used in FOKC algorithms. We begin by introducing the format used internally
+by \textsc{ForcLift} and its descendants. Afterwards, we provide a high-level
+description of how an arbitrary sentence in first-order logic is transformed
+into this internal format.
 
 A \emph{term} can be either a variable or a constant. An \emph{atom} can be
-either $P(t_{1}, \dots, t_{m})$ (or $P(\mathbf{t})$) for some predicate $P$ and
-terms $t_{1}, \dots, t_{m}$ or $x=y$ for some terms $x$ and $y$. The
+either $P(t_{1}, \dots, t_{m})$ (i.e., $P(\mathbf{t})$) for some predicate $P$
+and terms $t_{1}, \dots, t_{m}$ or $x=y$ for some terms $x$ and $y$. The
 \emph{arity} of a predicate is the number of arguments it takes, i.e., $m$ in
@@
 
-% TODO: Page 2, Section 2.1, paragraph 2, line 10 - ”A clause is of the form ...” - are the quantifiers really part of the clause?
-Shouldn’t it be possible to quantify a conjunction of several clauses?
-% Conforming with previous work, the definition of a clause includes universal quantifiers for all variables within.
-While it is possible to rewrite the entire formula in prenex normal form, the format we describe has proven itself convenient to work with.
+\begin{remark*}
+  Conforming with previous work~\cite{DBLP:conf/ijcai/BroeckTMDR11}, the
+  definition of a clause includes universal quantifiers for all variables
+  within. While it is possible to rewrite the entire formula with all
+  quantifiers at the front~\cite{hinman2018fundamentals}, the format we describe
+  has proven itself convenient to work with.
+\end{remark*}
+
+There are two crucial preprocessing steps that transform an arbitrary sentence
+in first-order logic into the form used internally: Skolemization and rewriting
+the sentence as a conjunction of clauses. We describe the former in more detail.
+\emph{Skolemization}~\cite{DBLP:conf/kr/BroeckMD14} is a procedure that
+transforms a formula with existential quantifiers into a formula without
+existential quantifiers \emph{with the same WFOMC}. (Note that it is different
+from the standard Skolemization that introduces function
+symbols~\cite{DBLP:books/daglib/0030198}.)
+
+\begin{example}
+  Skolemization transforms
+  \begin{equation}\label[formula]{eq:skolemizationinitial}
+    \forall x \in \Gamma\text{. }\exists y \in \Delta\text{. } P(x, y)
+  \end{equation}
+  into
+  \begin{equation}\label[formula]{eq:skolemization}
+    \begin{aligned}
+      (\forall x \in \Gamma\text{. } &Z(x))\land{}\\
+      (\forall x \in \Gamma\text{. } \forall y \in \Delta\text{. } &Z(x) \lor \neg P(x, y))\land{}\\
+      (\forall x \in \Gamma\text{. } &S(x) \lor Z(x))\land{}\\
+      (\forall x \in \Gamma\text{. } \forall y \in \Delta\text{. } &S(x) \lor \neg P(x, y)).
+    \end{aligned}
+  \end{equation}
+  We will see how, with suitable weights on the new predicates $S/1$ and $Z/1$,
+  the WFOMC of \cref{eq:skolemization} is equal to the FOMC of
+  \cref{eq:skolemizationinitial}.
+\end{example}
+% TODO: make sure to revisit this in the future
 
@@
 
-\begin{remark}
+\begin{remark*}
   In the case of \textsc{ForcLift} and its extensions, support for a formula as
@@
   variables~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/kr/BroeckMD14}.
-\end{remark}
+\end{remark*}
 
@@
 
-\begin{remark}
+\begin{remark*}
   The distinctness of domains is important in two ways. First, in terms of
@@
   without worrying how (or if) they apply to the second domain.
-\end{remark}
+\end{remark*}
 
@@
 
-\begin{remark}
+\begin{remark*}
   Although \CompileWithBaseCases starts with a call to \textsc{Crane}, the
@@
   \textsc{Crane} on various derived formulas.
-\end{remark}
+\end{remark*}
 

### 2025-01-16 doc/paper/paper.tex
Expand Section 2.3

@@
 \section{Preliminaries}\label{sec:preliminaries}
-% TODO: focus more on current work
-% TODO: Section 2 until 2.3 (Algebra) could be drastically shortened
 
@@
 
-% TODO: this subsection could be expanded a little
-
-We write $\expr{}$ to represent an arbitrary algebraic expression. It is
-important to note that some terms have different meanings in algebra and
-logic. In algebra, a \emph{constant} refers to a non-negative integer. Likewise,
-a \emph{variable} can either be a parameter of a function or a variable
-introduced through summation, such as $i$ in the expression
-$\sum_{i=1}^{n} \expr$. A (function) \emph{signature} is
-$f(x_{1}, \dots, x_{n})$ (or $f(\mathbf{x})$ for short), where $f$ represents an
-$n$-ary function, and each $x_{i}$ represents a variable. An \emph{equation} is
-$f(\mathbf{x}) = \expr{}$, with $f(\mathbf{x})$ representing a signature.
+We write $\expr{}$ for an arbitrary algebraic expression. In the context of
+algebra, a \emph{constant} is a non-negative integer. Likewise, a
+\emph{variable} can either be a parameter of a function or a variable introduced
+through summation, such as $i$ in the expression $\sum_{i=1}^{n} \expr$. A
+\emph{function call} is $f(x_{1}, \dots, x_{n})$ (or $f(\mathbf{x})$ for short),
+where $f$ is an $n$-ary function, and each $x_{i}$ is an algebraic expression
+consisting of variables and constants. A (function) \emph{signature} is function
+call that contains only variables. An \emph{equation} is
+$f(\mathbf{x}) = \expr{}$, where $f(\mathbf{x})$ is a signature.
 
@@
   Let $f(\mathbf{x})$ be a function call where each $x_{i}$ is either a constant
-  or a variable (note that signatures are included in this definition). Then
-  function call $f(\mathbf{y})$ is considered a \emph{base case} of
+  or a variable. Then function call $f(\mathbf{y})$ is a \emph{base case} of
   $f(\mathbf{x})$ if $f(\mathbf{y}) = f(\mathbf{x})\sigma$, where $\sigma$ is a
@@
 \end{definition}
+
+\begin{example}
+  In equation $f(m, n) = f(m-1, n) + nf(m-1, n-1)$, the only constant is $1$,
+  and the variables are $m$ and $n$. The equation contains three function calls:
+  one on the left-hand side, and two on the right-hand side. The function call
+  on the left-hand side is a signature. Function calls such as $f(4, n)$,
+  $f(m, 0)$, and $f(8, 1)$ are all considered base cases of $f(m, n)$ (only some
+  of which are useful).
+\end{example}
 

### 2025-01-18 doc/paper/paper.tex
Pseudocode for an example C++ program
Finish Section 3.5

@@
 
+\SetKwProg{Fn}{Function}{:}{}
+\SetKwData{Cache}{Cache}
+
 \SetKwFunction{CompileWithBaseCases}{CompileWithBaseCases}
@@
 \SetKwFunction{Simplify}{Simplify}
+\SetKwFunction{Main}{Main}
+\SetKwFunction{Input}{ParseCommandLineArguments}
 
@@
 % TODO (for the entire paper):
+% * finish add DOIs or URLs to (non-book) references (and reformatting indentation) (and check reference formatting)
 % * sentence vs formula: be consistent and not confusing
@@
   $\mathbf{t} \in \prod_{i=1}^{n} \sigma(\Delta_{i}^{P})$. A structure is a
-  \emph{model} if it satisfies $\phi$.
+  \emph{model} if it makes $\phi$ valid.
 \end{definition}
-% TODO: Page 2, Definition 1 - ”A structure is a model if it satisfies ϕ” - do you mean that it makes ϕ valid?
 
@@
 consisting of variables and constants. A (function) \emph{signature} is function
-call that contains only variables. An \emph{equation} is
-$f(\mathbf{x}) = \expr{}$, where $f(\mathbf{x})$ is a signature.
+call that contains only variables. Given two function calls $f(\mathbf{x})$ and
+$f(\mathbf{y})$, we say that $f(\mathbf{y})$ \emph{matches} $f(\mathbf{x})$ if
+$x_{i} = y_{i}$ whenever $x_{i}, y_{i} \in \mathbb{N}_{0}$. An \emph{equation}
+is $f(\mathbf{x}) = \expr{}$, where $f(\mathbf{x})$ is a signature.
 
@@
   and the variables are $m$ and $n$. The equation contains three function calls:
-  one on the left-hand side, and two on the right-hand side. The function call
-  on the left-hand side is a signature. Function calls such as $f(4, n)$,
+  one on the left-hand side (LHS), and two on the right-hand side (RHS). The
+  function call on the LHS is a signature. Function calls such as $f(4, n)$,
   $f(m, 0)$, and $f(8, 1)$ are all considered base cases of $f(m, n)$ (only some
@@
 % contribution.
-
-% TODO: Section 3: you seem to use "equation" and "function" interchangeably
-
-% TODO: this section "would benefit from cleaner reasoning"
 
@@
     for different domain sizes. To accomplish this, the \CompileWithBaseCases
-    function makes use of the FOKC algorithm of \textsc{Crane}, algebraic
+    procedure makes use of the FOKC algorithm of \textsc{Crane}, algebraic
     simplification techniques (denoted as \Simplify), and two other auxiliary
@@
 accurate model counting. Additionally, \cref{sec:cpp} explains the process of
-compiling function definitions into C++ code, greatly expanding upon the range
-of formulas that could previously be handled by similar
+compiling equations into C++ code, greatly expanding upon the range of formulas
+that could previously be handled by similar
 approaches~\cite{DBLP:conf/kr/KazemiP16}.
+
+% TODO (somewhere): Recall that each equation is either the definition (did I
+% define what a definition is?) of a function or the definition of a base case
+% of a function. (I could put this in the preliminaries as definitions and then
+% reference them below)
 
@@
   $\mathcal{B} \gets \emptyset$\;
-  \ForEach{function call $f(\mathbf{y})$ on the right-hand side of an equation in $\mathcal{E}$}{
+  \ForEach{function call $f(\mathbf{y})$ on the RHS of an equation in $\mathcal{E}$}{
     $\mathbf{x} \gets \text{the parameters of $f$ in its definition}$\;
@@
 previous~\cite{DBLP:conf/kr/DilkasB23,DBLP:conf/ijcai/BroeckTMDR11} and this
-work. Let $\mathcal{E}$ represent the equations returned by
-\CompileWithBaseCases.
+work.
 
@@
   For each function $f$, there is precisely one equation $e \in \mathcal{E}$
-  with $f(\mathbf{x})$ on the left-hand side where all $x_{i}$'s are variables
-  (i.e., $e$ is not a base case). We refer to $e$ as the \emph{definition} of
-  $f$.
+  with $f(\mathbf{x})$ on the LHS where all $x_{i}$'s are variables (i.e., $e$
+  is not a base case). We refer to $e$ as the \emph{definition} of $f$.
 \end{observation}
@@
   There is a \emph{topological ordering} of all functions ${(f_{i})}_{i}$ in
-  $\mathcal{E}$ such that equations in $\mathcal{E}$ with $f_{i}$ on the
-  left-hand side do not contain function calls to $f_{j}$ with $j > i$. This
-  condition prevents mutual recursion and other cyclic scenarios.
+  $\mathcal{E}$ such that equations in $\mathcal{E}$ with $f_{i}$ on the LHS do
+  not contain function calls to $f_{j}$ with $j > i$. This condition prevents
+  mutual recursion and other cyclic scenarios.
 \end{observation}
@@
 \begin{observation}\label{assumption3}
-  For every equation $(f(\mathbf{x}) = \expr) \in \mathcal{E}$, the evaluation
+  For each equation $(f(\mathbf{x}) = \expr) \in \mathcal{E}$, the evaluation
   of $\expr$ terminates when provided with the values of all relevant function
@@
 \begin{corollary}\label{fact}
-  If $f$ is a non-recursive function with no function calls on the right-hand
-  side of its definition, then the evaluation of any function call
-  $f(\mathbf{x})$ terminates.
+  If $f$ is a non-recursive function with no function calls on the RHS of its
+  definition, then the evaluation of any function call $f(\mathbf{x})$
+  terminates.
 \end{corollary}
@@
 \begin{observation}\label{fact2}
-  For any equation $f(\mathbf{x}) = \expr{}$, if $\mathbf{x}$ contains only
-  constants, then $\expr{}$ cannot include any function calls to $f$.
+  For each equation $(f(\mathbf{x}) = \expr{}) \in \mathcal{E}$, if $\mathbf{x}$
+  contains only constants, then $\expr{}$ cannot include any function calls to
+  $f$.
 \end{observation}
@@
 \begin{assumption}\label{assumption4}
-  For every equation $(f(\mathbf{x}) = \expr) \in \mathcal{E}$, every recursive
-  function call $f(\mathbf{y}) \in \expr$ satisfies the
-  following:
+  For each equation $(f(\mathbf{x}) = \expr) \in \mathcal{E}$, every recursive
+  function call $f(\mathbf{y}) \in \expr$ satisfies the following:
   \begin{itemize}
@@
   $f(\mathbf{x})$, preference is given to an equation with the most constants on
-  its left-hand side.
+  its LHS.
 \end{assumption}
@@
 
-  Otherwise, let $f(y)$ be an arbitrary function call on the right-hand side of
-  the definition of $f(x)$. If $y$ is a constant, then there is a base case for
+  Otherwise, let $f(y)$ be an arbitrary function call on the RHS of the
+  definition of $f(x)$. If $y$ is a constant, then there is a base case for
   $f(y)$. Otherwise, let $y = x - c$ for some $c > 0$. Then there exists
@@
 \subsection{Generating C++ Code}\label{sec:cpp}
-% TODO (must): expand this section
-% TODO: The purpose of C++ code generation is to turn mathematical equations into executable code.
 
 In this section, we will describe the final step of \Cranetwo{} as outlined in
-\cref{fig:overview}. This step involves translating the set of equations
-$\mathcal{E}$ into C++ code. The resulting C++ program can then be compiled and
-executed with different command-line arguments to compute the model count of the
-formula for various domain sizes.
-
-Each equation in $\mathcal{E}$ is compiled into a C++ function, along with a
-separate cache for memoisation. Let us consider an arbitrary equation
-$e = (f(\mathbf{x}) = \expr{}) \in \mathcal{E}$, and let
-$\mathbf{c} \in \mathbb{N}_{0}^{n}$ represent the arguments of the corresponding
-C++ function. The implementation of $e$ consists of three parts. First, we check
-if $\mathbf{c}$ is already present in the cache of $e$. If it is, we simply
-return the cached value. Second, for each base case $f(\mathbf{y})$ of
-$f(\mathbf{x})$ (as defined in \cref{def:basecase}), we check if $\mathbf{c}$
-\emph{matches} $\mathbf{y}$, i.e., $c_{i} = y_{i}$ whenever
-$y_{i} \in \mathbb{N}_{0}$. If this condition is satisfied, $\mathbf{c}$ is
-redirected to the C++ function that corresponds to the definition of the base
-case $f(\mathbf{y})$. Finally, if none of the above cases apply, we evaluate
-$\mathbf{c}$ based on the expression $\expr{}$, store the result in the cache,
-and return it.
+\cref{fig:overview}, i.e., translating the set of equations $\mathcal{E}$ into
+C++ code. Recall that this step is crucial for the usability of the algorithm,
+otherwise function definitions would remain purely mathematical, with no
+convenient way to compute the model count for particular domain sizes. Once a
+C++ program is produced, it can be executed with different command-line
+arguments to compute the model count of the formula for various domain sizes.
+
+\begin{algorithm}[t]
+  \caption{A sketch of the C++ program for the bijection-counting problem in \cref{example:overall}, particularly highlighting the recursive definition of function $g$.}\label{alg:cpp}
+  initialise $\Cache_{g(0, m)}$, $\Cache_{g(l, 0)}$, $\Cache_{g}$, and $\Cache_{f}$\;
+  \DontPrintSemicolon
+  \textbf{Function} $g_{0,m}(m)$\textbf{:} \dots\;
+  \textbf{Function} $g_{l,0}(l)$\textbf{:} \dots\;
+  \PrintSemicolon
+  \Fn{$g(l, m)$}{
+    \lIf{$(l, m) \in \Cache_{g}$}{\Return{$\Cache_{g}(l, m)$}}\label{line:cache}
+    \lIf{$l = 0$}{\Return{$g_{0,m}(m)$}}\label{line:basecaseone}
+    \lIf{$m = 0$}{\Return{$g_{l,0}(l)$}}\label{line:basecasetwo}
+    $r \gets g(l-1, m) + mg(l-1,m-1)$\;
+    $\Cache_{g}(l, m) \gets r$\;
+    \Return{$r$}\;
+  }
+  \DontPrintSemicolon
+  \textbf{Function} $f(m, n)$\textbf{:} \dots\;
+  \PrintSemicolon
+  \Fn{\Main}{
+    $(m, n) \gets \Input{}$\;
+    \Return{$f(m, n)$}\;
+  }
+\end{algorithm}
+
+See \cref{alg:cpp} for the typical structure of a generated C++ program. Each
+equation in $\mathcal{E}$ is compiled into a C++ function, along with a separate
+cache for memoisation. Hence, \cref{alg:cpp} has a function and a cache for
+$f(\cdot, \cdot)$, $g(\cdot, \cdot)$, $g(\cdot, 0)$, and $g(0, \cdot)$. The
+implementation of an equation consists of three parts. First (on
+\autoref{line:cache}), we check if the arguments are already present in the
+corresponding cache. If so, we simply return the cached value. Second (on
+lines~\ref{line:basecaseone} and~\ref{line:basecasetwo}), for each base case, we
+check if the arguments match the base case (as defined in \cref{sec:algebra}).
+If so, the arguments are redirected to the C++ function for that base case.
+Finally, if none of the above cases apply, we evaluate the arguments based on
+the expression on the RHS of the equation, store the result in the cache, and
+return it.
 

### 2025-01-18 doc/paper/paper.tex
Use todonotes

@@
 \usepackage{microtype}
+\usepackage[backgroundcolor=lightgray]{todonotes}
 
@@
 \creflabelformat{formula}{#2\textup{(#1)}#3}
-
-% TODO (for the entire paper):
-% * finish add DOIs or URLs to (non-book) references (and reformatting indentation) (and check reference formatting)
-% * sentence vs formula: be consistent and not confusing
-% * 15 pages excluding references
 
@@
 
+\todo[inline,caption={}]{
+  For the entire paper:
+  \begin{itemize}
+    \item Finish adding DOIs or URLs to (non-book) references (and reformatting
+          indentation) (and check reference formatting)
+    \item Sentence vs formula: be consistent and not confusing
+    \item 15 pages excluding references
+    \item Go through the rest of formatting instructions (in GTD)
+  \end{itemize}
+}
 \section{Introduction}
-% TODO: We would like to clarify that the main contribution of this work
-% consists of everything needed to complement recursive function definitions
-% with the necessary base cases. This process includes identifying the base
-% cases and their corresponding formulas, transforming them (including applying
-% a new smoothing procedure), and recursively reusing Crane. C++ code
-% generation, although relatively straightforward, is crucial for the usability
-% of the algorithm
-
-% TODO: focus more on current work
+
+\todo[inline,caption={}]{
+  \begin{itemize}
+    \item We would like to clarify that the main contribution of this work
+          consists of everything needed to complement recursive function
+          definitions with the necessary base cases. This process includes
+          identifying the base cases and their corresponding formulas,
+          transforming them (including applying a new smoothing procedure), and
+          recursively reusing Crane. C++ code generation, although relatively
+          straightforward, is crucial for the usability of the algorithm.
+    \item Focus more on current work
+  \end{itemize}
+}
 
@@
 
-% TODO: don't assume that the reader knows FOMC and FOMC algorithms
-
-% TODO: It would be nice to give the necessary introduction to FOKC, or CRANE
-% (an intuitive explanation early in the paper)
-
-% TODO: The principal motivation of a knowledge compilation-based approach to
-% FOMC comes from its ability to find polynomial-time solutions, where the
-% polynomial has a lower degree compared to, e.g., FastWFOMC (Dilkas and Belle,
-% 2023). The ability of the algorithm to mathematically describe recursive
-% solutions is also noteworthy as the only other available alternative is to
-% guess them (Barvı́nek, van Bremen, Wang, Zelezný, Kuzelka, ILP 2021).
+\todo[inline,caption={}]{
+  \begin{itemize}
+    \item Don't assume that the reader knows FOMC and FOMC algorithms
+    \item It would be nice to give the necessary introduction to FOKC, or
+          \textsc{Crane} (an intuitive explanation early in the paper)
+    \item The principal motivation of a knowledge compilation-based approach to
+          FOMC comes from its ability to find polynomial-time solutions, where
+          the polynomial has a lower degree compared to, e.g.,
+          \textsc{FastWFOMC}~\cite{DBLP:conf/kr/DilkasB23}. The ability of the
+          algorithm to mathematically describe recursive solutions is also
+          noteworthy as the only other available alternative is to guess
+          them~\cite{DBLP:conf/ilp/BarvinekB0ZK21}.
+  \end{itemize}
+}
+
 FOMC algorithms are diverse, with approaches ranging from \emph{first-order
@@
 \end{example}
-% TODO: make sure to revisit this in the future
+
+\todo[inline]{Make sure to revisit this in the future}
 
@@
 
-% TODO: shorten the part about the three logics
+\todo[inline]{Shorten the part about the three logics}
 
@@
 problem as Skolemization relies on weights even for unweighted FOMC.
-% TODO: Even though we are evaluating the algorithms on FOMC benchmarks, for
-% sentences with existential quantifiers, computing FOMC using Gantry requires
-% the use of WFOMC. For such sentences, Skolemization introduces predicates with
-% non-unary weights that must be accounted for to compute the correct model
-% count.
+
+\todo[inline]{Even though we are evaluating the algorithms on FOMC benchmarks,
+  for sentences with existential quantifiers, computing FOMC using \Cranetwo{}
+  requires the use of WFOMC. For such sentences, Skolemization introduces
+  predicates with non-unary weights that must be accounted for to compute the
+  correct model count.}
 
@@
 
-% TODO: The algorithm’s recursive nature and its interaction with CRANE could be
-% explained more clearly
-
-% TODO: more emphasis on the motivation for each part of GANTRY (e.g., how
-% FindBaseCases addresses key issues in CRANE) would add depth to the
-% contribution.
-
-% TODO: this section should be expanded by 1 page ("a clear discussion of the
-% innovation aspect and technical parts")
+\todo[inline,caption={}]{
+  \begin{itemize}
+    \item The algorithm’s recursive nature and its interaction with
+          \textsc{Crane} could be explained more clearly
+    \item More emphasis on the motivation for each part of \Cranetwo{} (e.g.,
+          how \FindBaseCases addresses key issues in \textsc{Crane}) would add
+          depth to the contribution
+    \item this section should be expanded by 1 page (``a clear discussion of the
+          innovation aspect and technical parts'')
+  \end{itemize}
+}
 
@@
 
-% TODO (somewhere): Recall that each equation is either the definition (did I
-% define what a definition is?) of a function or the definition of a base case
-% of a function. (I could put this in the preliminaries as definitions and then
-% reference them below)
+\todo[inline]{Somewhere: Recall that each equation is either the definition (did
+  I define what a definition is?) of a function or the definition of a base case
+  of a function. (I could put this in the preliminaries as definitions and then
+  reference them below)}
 
@@
 
-% TODO: move this example right after the definition of WFOMC (or near the
-% definition of a model)
+\todo[inline]{Move this example right after the definition of WFOMC (or near the
+  definition of a model)}
+
 \begin{example}[Counting bijections]\label{example:overall}
@@
 \subsection{Identifying a Sufficient Set of Base Cases}\label{sec:identifying}
-% TODO: prove correctness?
+
+\todo[inline]{Prove correctness?}
 
@@
 
-% TODO Experiments could be expanded by 1 page ("a more thorough and independent
-% practical assessment")
-
-% TODO: this section "would benefit from cleaner reasoning"
-
-% TODO: The difference between Gantry-Greedy and Gantry-BFS is in how the
-% algorithm chooses which compilation rule to apply to a formula. The former
-% uses greedy search: there is a list of rules, and the first applicable rule is
-% the one that gets used, disregarding all the others. The latter uses a
-% combination of greedy and breadth-first search (BFS). That is, each
-% compilation rule is identified as either greedy or non-greedy. Greedy rules
-% are applied as soon as possible at any stage of the compilation process. BFS
-% is executed over all applicable non-greedy rules, identifying the solution
-% that can be constructed using the smallest number of such rules.
+\todo[inline,caption={}]{
+  \begin{itemize}
+    \item Experiments could be expanded by 1 page (``a more thorough and
+          independent practical assessment'')
+    \item The difference between \Cranegreedy{} and \Cranebfs{} is in how the
+          algorithm chooses which compilation rule to apply to a formula. The
+          former uses greedy search: there is a list of rules, and the first
+          applicable rule is the one that gets used, disregarding all the
+          others. The latter uses a combination of greedy and breadth-first
+          search (BFS). That is, each compilation rule is identified as either
+          greedy or non-greedy. Greedy rules are applied as soon as possible at
+          any stage of the compilation process. BFS is executed over all
+          applicable non-greedy rules, identifying the solution that can be
+          constructed using the smallest number of such rules.
+  \end{itemize}
+}
 
@@
 \subsection{Benchmarks}
-% TODO: more benchmarks from NOT my work
-% TODO: make sure it's clear what the 'raw' instances are
-% TODO: don't emphasise that the benchmarks come from my previous work
+
+\todo[inline,caption={}]{
+  \begin{itemize}
+    \item More benchmarks from NOT my work
+    \item Make sure it's clear what the `raw' instances are
+    \item Don't emphasise that the benchmarks come from my previous work
+  \end{itemize}
+}
 
@@
 \end{figure*}
-% TODO: shrink/restructure to fit into the margins
+
+\todo[inline]{Shrink/restructure to fit into the margins}
 
@@
 
-% TODO: On the ’friends’ and ’functions’ benchmarks, ForcLift runs until the
-% model count exceeds 231 − 1.
-
-% TODO: We are not aware of any formulas on which Gantry scales worse compared
-% to either ForcLift or FastWFOMC. The one advantage that FastWFOMC has over
-% Gantry is its support for counting quantifiers.
-
-% TODO: Regarding programming languages and accuracy, we verified that the
-% answers match for smaller domain sizes. Also, although written in different
-% languages, both Gantry and FastWFOMC use the GNU Multiple Precision Arithmetic
-% Library.
+\todo[inline,caption={}]{
+  \begin{itemize}
+    \item On the `friends' and `functions' benchmarks, \textsc{ForcLift} runs
+          until the model count exceeds $2^{31}-1$.
+    \item We are not aware of any formulas on which \Cranetwo{} scales worse
+          compared to either \textsc{ForcLift} or \textsc{FastWFOMC}. The one
+          advantage that \textsc{FastWFOMC} has over \Cranetwo{} is its support
+          for counting quantifiers.
+    \item Regarding programming languages and accuracy, we verified that the
+          answers match for smaller domain sizes. Also, although written in
+          different languages, both \Cranetwo{} and \textsc{FastWFOMC} use the
+          GNU Multiple Precision Arithmetic Library.
+  \end{itemize}
+}
 

### 2025-01-18 doc/paper/paper.tex
Start rewriting preliminaries

@@
 
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item Don't assume that the reader knows FOMC and FOMC algorithms
-    \item It would be nice to give the necessary introduction to FOKC, or
-          \textsc{Crane} (an intuitive explanation early in the paper)
-    \item The principal motivation of a knowledge compilation-based approach to
-          FOMC comes from its ability to find polynomial-time solutions, where
-          the polynomial has a lower degree compared to, e.g.,
-          \textsc{FastWFOMC}~\cite{DBLP:conf/kr/DilkasB23}. The ability of the
-          algorithm to mathematically describe recursive solutions is also
-          noteworthy as the only other available alternative is to guess
-          them~\cite{DBLP:conf/ilp/BarvinekB0ZK21}.
-  \end{itemize}
-}
-
 FOMC algorithms are diverse, with approaches ranging from \emph{first-order
-  knowledge compilation} (FOKC) to local
-search~\cite{DBLP:journals/pvldb/NiuRDS11}, Monte Carlo
-sampling~\cite{DBLP:journals/cacm/GogateD16}, and anytime
-approximation~\cite{DBLP:conf/ijcai/BremenK20}. Among these, FOKC-based
-algorithms are particularly prominent, transforming formulas into structured
-representations such as circuits or graphs. Notable examples include
-\textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} and its successor
-\textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23}. Another important algorithm,
-\textsc{FastWFOMC}~\cite{DBLP:conf/uai/BremenK21}, uses cell enumeration as its
-foundation.
+  knowledge compilation} (FOKC) to cell
+enumeration~\cite{DBLP:conf/uai/BremenK21}, local
+search~\cite{DBLP:journals/pvldb/NiuRDS11}, and Monte Carlo
+sampling~\cite{DBLP:journals/cacm/GogateD16}. Among these, FOKC-based algorithms
+are particularly prominent, transforming formulas into structured
+representations such as circuits or graphs. Even when multiple algorithms are
+able to solve the same instance, FOKC algorithms are known to find
+polynomial-time solutions, where the polynomial has a lower degree compared to
+other approaches~\cite{DBLP:conf/kr/DilkasB23}. The recently developed ability
+of a FOKC algorithm to formulate solutions in terms of recursive
+functions~\cite{DBLP:conf/kr/DilkasB23} is also noteworthy as the only other
+proposed alternative is to guess recursive
+relations~\cite{DBLP:conf/ilp/BarvinekB0ZK21}. Notable examples of FOKC
+algorithms include \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} and its
+successor \textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23}.
 
@@
 \section{Preliminaries}\label{sec:preliminaries}
+
+\todo[inline]{Adjust the introduction to the new structure (with more
+  subsections)}
 
@@
 
-There are two crucial preprocessing steps that transform an arbitrary sentence
-in first-order logic into the form used internally: Skolemization and rewriting
-the sentence as a conjunction of clauses. We describe the former in more detail.
-\emph{Skolemization}~\cite{DBLP:conf/kr/BroeckMD14} is a procedure that
-transforms a formula with existential quantifiers into a formula without
-existential quantifiers \emph{with the same WFOMC}. (Note that it is different
-from the standard Skolemization that introduces function
-symbols~\cite{DBLP:books/daglib/0030198}.)
-
-\begin{example}
-  Skolemization transforms
-  \begin{equation}\label[formula]{eq:skolemizationinitial}
-    \forall x \in \Gamma\text{. }\exists y \in \Delta\text{. } P(x, y)
-  \end{equation}
-  into
-  \begin{equation}\label[formula]{eq:skolemization}
-    \begin{aligned}
-      (\forall x \in \Gamma\text{. } &Z(x))\land{}\\
-      (\forall x \in \Gamma\text{. } \forall y \in \Delta\text{. } &Z(x) \lor \neg P(x, y))\land{}\\
-      (\forall x \in \Gamma\text{. } &S(x) \lor Z(x))\land{}\\
-      (\forall x \in \Gamma\text{. } \forall y \in \Delta\text{. } &S(x) \lor \neg P(x, y)).
-    \end{aligned}
-  \end{equation}
-  We will see how, with suitable weights on the new predicates $S/1$ and $Z/1$,
-  the WFOMC of \cref{eq:skolemization} is equal to the FOMC of
-  \cref{eq:skolemizationinitial}.
-\end{example}
-
-\todo[inline]{Make sure to revisit this in the future}
-
-\subsection{FOMC Algorithms and Their Logics}\label{sec:threelogics}
-
-\todo[inline]{Shorten the part about the three logics}
-
-\begin{table*}[t]
-  \centering
-  \begin{tabular}{llclll}
-    \toprule
-    Logic & Sorts & Constants & Variables & Quantifiers & Additional atoms\\
-    \midrule
-    \FO & one or more & \cmark & unlimited & $\forall$, $\exists$ & $x = y$\\
-    \Ctwo & one & \xmark & two & $\forall$, $\exists$, $\exists^{= k}$, $\exists^{\le k}$, $\exists^{\ge k}$ & ---\\
-    \UFO & one & \xmark & two & $\forall$ & $|P| = m$\\
-    \bottomrule
-  \end{tabular}
-  \caption{A comparison of the three logics used in FOMC\@. The
-    2\textsuperscript{nd}--5\textsuperscript{th} columns refer to: the number of
-    sorts, support for constants, the maximum number of variables, and supported
-    quantifiers, respectively. The last column lists supported atoms in addition
-    to those of the form $P(\mathbf{t})$ for a predicate $P/n$ and an $n$-tuple
-    of terms $\mathbf{t}$. Here: $k$ and $m$ are non-negative integers, with the
-    latter depending on the domain size, $P$ represents a predicate, and $x$ and
-    $y$ are terms. }\label{tbl:logics}
-\end{table*}
+\subsection{The Three Logics of FOMC}\label{sec:threelogics}
+
+% \begin{table*}[t]
+%   \centering
+%   \begin{tabular}{llclll}
+%     \toprule
+%     Logic & Sorts & Constants & Variables & Quantifiers & Additional atoms\\
+%     \midrule
+%     \FO & one or more & \cmark & unlimited & $\forall$, $\exists$ & $x = y$\\
+%     \Ctwo & one & \xmark & two & $\forall$, $\exists$, $\exists^{= k}$, $\exists^{\le k}$, $\exists^{\ge k}$ & ---\\
+%     \UFO & one & \xmark & two & $\forall$ & $|P| = m$\\
+%     \bottomrule
+%   \end{tabular}
+%   \caption{A comparison of the three logics used in FOMC\@. The
+%     2\textsuperscript{nd}--5\textsuperscript{th} columns refer to: the number of
+%     sorts, support for constants, the maximum number of variables, and supported
+%     quantifiers, respectively. The last column lists supported atoms in addition
+%     to those of the form $P(\mathbf{t})$ for a predicate $P/n$ and an $n$-tuple
+%     of terms $\mathbf{t}$. Here: $k$ and $m$ are non-negative integers, with the
+%     latter depending on the domain size, $P$ represents a predicate, and $x$ and
+%     $y$ are terms. }\label{tbl:logics}
+% \end{table*}
 
@@
 
-In \cref{tbl:logics}, we outline the differences among three first-order logics
-commonly used in FOMC: \FO{}, \Ctwo{}, and \UFO{}. First, \FO{} is the input
-format for
+There are three first-order logics commonly used in FOMC: \FO{}, \Ctwo{}, and
+\UFO{}. First, \FO{} is the input format for
 \textsc{ForcLift}\footnote{\url{https://github.com/UCLA-StarAI/Forclift}} and
@@
 \Cranetwo{}. Second, \Ctwo{} is often used in the literature on
-\textsc{FastWFOMC} and related
-methods~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}. Finally,
-\UFO{} is the input format supported by the most recent implementation of
-\textsc{FastWFOMC}\footnote{\url{https://github.com/jan-toth/FastWFOMC.jl}}. The
-notation we use to refer to each logic is standard in the case of \Ctwo{} and
-\UFO{}~\cite{tóth2024complexityweightedfirstordermodel} and redefined to be more
-specific in the case of \FO{}. All three logics are function-free, and domains
-are always assumed to be finite. As usual, we presuppose the \emph{unique name
-  assumption}, which states that two constants are equal if and only if they are
-the same constant~\cite{DBLP:books/aw/RN2020}.
+\textsc{FastWFOMC}\footnote{\url{https://github.com/jan-toth/FastWFOMC.jl}} and
+related methods~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}.
+Finally, \UFO{} is the input format supported by the most recent implementation
+of \textsc{FastWFOMC}~\cite{tóth2024complexityweightedfirstordermodel}. All
+three logics are function-free, and domains are always assumed to be finite. As
+usual, we presuppose the \emph{unique name assumption}, which states that two
+constants are equal if and only if they are the same
+constant~\cite{DBLP:books/aw/RN2020}.
 
@@
 
+\subsection{First-Order Model Counting}
+
+\todo[inline,caption={}]{
+  \begin{itemize}
+    \item Write a proper introductory paragraph
+    \item Maybe a bit more (easy-to-understand) detail about FOMC?
+  \end{itemize}
+}
+
 \begin{definition}[Model]\label{def:model}
@@
 
-% (In practice, we typically only specify the size of each domain.)
-
 \begin{remark*}
@@
 
-While this work focuses on FOMC, we still define the weighted variant of the
-problem as Skolemization relies on weights even for unweighted FOMC.
-
-\todo[inline]{Even though we are evaluating the algorithms on FOMC benchmarks,
-  for sentences with existential quantifiers, computing FOMC using \Cranetwo{}
-  requires the use of WFOMC. For such sentences, Skolemization introduces
+\begin{remark*}
+  Even though this work focuses on FOMC, for sentences with existential
+  quantifiers, computing FOMC using \Cranetwo{} requires the use of WFOMC. For
+  such sentences, Skolemization (described in \cref{sec:crane}) introduces
   predicates with non-unary weights that must be accounted for to compute the
-  correct model count.}
+  correct model count.
+\end{remark*}
 
@@
 
+\subsection{First-Order Knowledge Compilation}\label{sec:crane}
+
+\todo[inline]{It would be nice to give the necessary introduction to FOKC, or
+  \textsc{Crane} (an intuitive explanation early in the paper)}
+
+There are two crucial preprocessing steps that transform an arbitrary sentence
+in first-order logic into the form used internally: Skolemization and rewriting
+the sentence as a conjunction of clauses. We describe the former in more detail.
+\emph{Skolemization}~\cite{DBLP:conf/kr/BroeckMD14} is a procedure that
+transforms a formula with existential quantifiers into a formula without
+existential quantifiers \emph{with the same WFOMC}. (Note that it is different
+from the standard Skolemization that introduces function
+symbols~\cite{DBLP:books/daglib/0030198}.)
+
+\begin{example}
+  Skolemization transforms
+  \begin{equation}\label[formula]{eq:skolemizationinitial}
+    \forall x \in \Gamma\text{. }\exists y \in \Delta\text{. } P(x, y)
+  \end{equation}
+  into
+  \begin{equation}\label[formula]{eq:skolemization}
+    \begin{aligned}
+      (\forall x \in \Gamma\text{. } &Z(x))\land{}\\
+      (\forall x \in \Gamma\text{. } \forall y \in \Delta\text{. } &Z(x) \lor \neg P(x, y))\land{}\\
+      (\forall x \in \Gamma\text{. } &S(x) \lor Z(x))\land{}\\
+      (\forall x \in \Gamma\text{. } \forall y \in \Delta\text{. } &S(x) \lor \neg P(x, y)).
+    \end{aligned}
+  \end{equation}
+  With suitable weights on the new predicates $S/1$ and $Z/1$, the WFOMC of
+  \cref{eq:skolemization} is equal to the FOMC of
+  \cref{eq:skolemizationinitial}.
+\end{example}
+
 \subsection{Algebra}\label{sec:algebra}
 
-We write $\expr{}$ for an arbitrary algebraic expression. In the context of
-algebra, a \emph{constant} is a non-negative integer. Likewise, a
+In this paper, we use both logical and algebraic constructs. While the rest of
+\cref{sec:preliminaries} focused on the former, this section describes the
+latter. We write $\expr{}$ for an arbitrary algebraic expression. In the context
+of algebra, a \emph{constant} is a non-negative integer. Likewise, a
 \emph{variable} can either be a parameter of a function or a variable introduced

### 2025-01-19 doc/paper/paper.tex
Section 2.3

@@
 \usepackage[backgroundcolor=lightgray]{todonotes}
+\usepackage{mathtools}
 
@@
     \item Finish adding DOIs or URLs to (non-book) references (and reformatting
-          indentation) (and check reference formatting)
+          indentation) (and check reference formatting) (is the part about
+          non-book references correct? Check previous proceedings) (maybe one
+          more exception (graded logics)?) (I might be done)
     \item Sentence vs formula: be consistent and not confusing
@@
 
+\paragraph*{Notation}
 We use $\mathbb{N}_{0}$ to represent the set of non-negative integers. In both
@@
 
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item Write a proper introductory paragraph
-    \item Maybe a bit more (easy-to-understand) detail about FOMC?
-  \end{itemize}
-}
-
-\begin{definition}[Model]\label{def:model}
+In this section, we will formally define FOMC and its weighted variant. Note
+that, although this work focuses on FOMC, for sentences with existential
+quantifiers, computing the FOMC using \Cranetwo{} requires the use of WFOMC\@.
+For such sentences, Skolemization (described in \cref{sec:crane}) introduces
+predicates with non-unary weights that must be accounted for to compute the
+correct model count. Additionally, our formulation of the definition of WFOMC is
+somewhat complicated by the need to support any number of domains.
+
+\begin{definition}[Structure, model]\label{def:model}
   Let $\phi$ be a formula in \FO{}. For each predicate $P/n$ in $\phi$, let
   ${(\Delta_{i}^{P})}_{i=1}^{n}$ be a list of the corresponding domains. Let
-  $\sigma$ be a map from the domains of $\phi$ to their interpretations as sets
-  such that the sets are pairwise disjoint, and the constants in $\phi$ are
-  included in the corresponding domains. A \emph{structure} of $\phi$ is a set
-  $M$ of ground literals defined by adding to $M$ either $P(\mathbf{t})$ or
-  $\neg P(\mathbf{t})$ for every predicate $P/n$ in $\phi$ and $n$-tuple
-  $\mathbf{t} \in \prod_{i=1}^{n} \sigma(\Delta_{i}^{P})$. A structure is a
-  \emph{model} if it makes $\phi$ valid.
+  $\sigma$ be a map from the domains of $\phi$ to their interpretations as
+  finite sets such that the sets are pairwise disjoint, and the constants in
+  $\phi$ are included in the corresponding domains. A \emph{structure} of $\phi$
+  is a set $M$ of ground literals defined by adding to $M$ either
+  $P(\mathbf{t})$ or $\neg P(\mathbf{t})$ for every predicate $P/n$ in $\phi$
+  and $n$-tuple $\mathbf{t} \in \prod_{i=1}^{n} \sigma(\Delta_{i}^{P})$. A
+  structure is a \emph{model} if it makes $\phi$ valid.
 \end{definition}
+
+\begin{example}[Counting bijections]\label{example:overall}
+  Let $\phi$ be the following formula (previously examined by Dilkas and
+  Belle~\cite{DBLP:conf/kr/DilkasB23}) that defines predicate $P$ as a bijection
+  between two domains $\Gamma$ and $\Delta$:
+  \[
+    \begin{gathered}
+      (\forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }P(x, y))\land{}\\
+      (\forall y \in \Delta\text{. }\exists x \in \Gamma\text{. }P(x, y))\land{}\\
+      (\forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z)\land{}\\
+      (\forall x, z \in \Gamma\text{. }\forall y \in \Delta\text{. }P(x, y) \land P(z, y) \Rightarrow x = z).
+    \end{gathered}
+  \]
+  Let $\sigma$ be defined as $\sigma(\Gamma) \coloneqq \{\, 1, 2\,\}$, and
+  $\sigma(\Delta) \coloneqq \{\,a, b\,\}$. Then $\phi$ has two models:
+  \[
+    \{\, P(1, a), P(2, b), \neg P(1, b), \neg P(2, a) \,\} \qquad \text{and} \qquad \{\, P(1, b), P(2, a), \neg P(1, a), \neg P(2, b) \,\}.
+  \]
+\end{example}
 
@@
 
-\begin{remark*}
-  Even though this work focuses on FOMC, for sentences with existential
-  quantifiers, computing FOMC using \Cranetwo{} requires the use of WFOMC. For
-  such sentences, Skolemization (described in \cref{sec:crane}) introduces
-  predicates with non-unary weights that must be accounted for to compute the
-  correct model count.
-\end{remark*}
-
 \begin{definition}[WFOMC instance]\label{def:instance}
@@
 \end{definition}
-
-\begin{example}[Counting functions]\label{example:functions}
-  To define predicate $P$ as a function from a domain $\Delta$ to itself, in
-  \Ctwo{} one would write $\forall x \in \Delta\text{.
-  }\exists^{=1} y \in \Delta\text{. }P(x, y)$. In \UFO{}, the same could be
-  written as
-  \begin{equation}\label[formula]{eq:functions1}
-    (\forall x, y \in \Delta\text{. }S(x) \lor \neg P(x, y)) \land (|P| = |\Delta|),
-  \end{equation}
-  where $w^{-}(S) = -1$. Although \cref{eq:functions1} has more models compared
-  to its counterpart in \Ctwo{}, the negative weight $w^{-}(S) = -1$ makes some
-  of the terms in \cref{eq:wfomc} cancel out.
-
-  Equivalently, in \FO{} we would write
-  \begin{equation}\label[formula]{eq:fo}
-    \begin{gathered}
-      (\forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }P(x, y)) \land (\forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z).
-    \end{gathered}
-  \end{equation}
-  The first clause asserts that each $x$ must have at least one corresponding
-  $y$, while the second statement adds the condition that if $x$ is mapped to
-  both $y$ and $z$, then $y$ must equal $z$. It is important to note that
-  \cref{eq:fo} is written with two domains instead of just one. However, we can
-  still determine the correct number of functions by assuming that the sizes of
-  $\Gamma$ and $\Delta$ are equal. This formulation, as observed by Dilkas and
-  Belle~\cite{DBLP:conf/kr/DilkasB23}, can prove beneficial in enabling FOKC
-  algorithms to find efficient solutions.
-\end{example}
 
@@
 
-\todo[inline]{Move this example right after the definition of WFOMC (or near the
-  definition of a model)}
-
-\begin{example}[Counting bijections]\label{example:overall}
-  Consider the following formula (previously examined by Dilkas and
-  Belle~\cite{DBLP:conf/kr/DilkasB23}) that defines predicate $P$ as a bijection
-  between two sets $\Gamma$ and $\Delta$:
-  \[
-    \begin{gathered}
-      (\forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }P(x, y))\land{}\\
-      (\forall y \in \Delta\text{. }\exists x \in \Gamma\text{. }P(x, y))\land{}\\
-      (\forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z)\land{}\\
-      (\forall x, z \in \Gamma\text{. }\forall y \in \Delta\text{. }P(x, y) \land P(z, y) \Rightarrow x = z).
-    \end{gathered}
-  \]
-  We specifically examine the first solution returned by \Cranetwo{} for this
-  formula.
-
-  After \autoref{line:second}, we have
+\begin{example}\label{example:overalltwo}
+  Let us examine the first solution returned by \Cranetwo{} for the
+  bijection-counting problem in \cref{example:overall}. After
+  \autoref{line:second}, we have
   \begin{align*}
@@
 $f(a) + f(a+1) + \cdots + f(\min\{\, n, b \,\})$. For instance, in the case of
-\cref{example:overall}, \Simplify transforms
+\cref{example:overalltwo}, \Simplify transforms
 $g(l, m) = \sum_{k=0}^{m}[0 \le k \le 1]\binom{m}{k}g(l-1, m-k)$ into
@@
 \begin{example}
-  Consider the recursive function $g$ from \cref{example:overall}.
+  Consider the recursive function $g$ from \cref{example:overalltwo}.
   \FindBaseCases iterates over two function calls: $g(l-1, m)$ and
@@
 \begin{algorithm}[t]
-  \caption{A sketch of the C++ program for the bijection-counting problem in \cref{example:overall}, particularly highlighting the recursive definition of function $g$.}\label{alg:cpp}
+  \caption{A sketch of the C++ program for the equations in \cref{example:overalltwo}, particularly highlighting the recursive definition of function $g$.}\label{alg:cpp}
   initialise $\Cache_{g(0, m)}$, $\Cache_{g(l, 0)}$, $\Cache_{g}$, and $\Cache_{f}$\;
@@
     \item Don't emphasise that the benchmarks come from my previous work
+    \item Integrate the example below into the text, possibly moving irrelevant
+          details (such as the formulas in other logics) to supplementary
+          material
   \end{itemize}
 }
+
+\begin{example}[Counting functions]\label{example:functions}
+  To define predicate $P$ as a function from a domain $\Delta$ to itself, in
+  \Ctwo{} one would write $\forall x \in \Delta\text{.
+  }\exists^{=1} y \in \Delta\text{. }P(x, y)$. In \UFO{}, the same could be
+  written as
+  \begin{equation}\label[formula]{eq:functions1}
+    (\forall x, y \in \Delta\text{. }S(x) \lor \neg P(x, y)) \land (|P| = |\Delta|),
+  \end{equation}
+  where $w^{-}(S) = -1$. Although \cref{eq:functions1} has more models compared
+  to its counterpart in \Ctwo{}, the negative weight $w^{-}(S) = -1$ makes some
+  of the terms in \cref{eq:wfomc} cancel out.
+
+  Equivalently, in \FO{} we would write
+  \begin{equation}\label[formula]{eq:fo}
+    \begin{gathered}
+      (\forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }P(x, y)) \land (\forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z).
+    \end{gathered}
+  \end{equation}
+  The first clause asserts that each $x$ must have at least one corresponding
+  $y$, while the second statement adds the condition that if $x$ is mapped to
+  both $y$ and $z$, then $y$ must equal $z$. It is important to note that
+  \cref{eq:fo} is written with two domains instead of just one. However, we can
+  still determine the correct number of functions by assuming that the sizes of
+  $\Gamma$ and $\Delta$ are equal. This formulation, as observed by Dilkas and
+  Belle~\cite{DBLP:conf/kr/DilkasB23}, can prove beneficial in enabling FOKC
+  algorithms to find efficient solutions.
+\end{example}
 

### 2025-01-20 doc/paper/paper.tex
Section 2.4

@@
     \item Go through the rest of formatting instructions (in GTD)
+    \item Make sure all the references (e.g., to examples are still valid)
+    \item Maybe add extra references to subsections
   \end{itemize}
@@
 
-\todo[inline]{Adjust the introduction to the new structure (with more
-  subsections)}
+\todo[inline,caption={}]{
+  \begin{itemize}
+    \item Adjust the introduction to the new structure (with more subsections)
+    \item If I need more space elsewhere, shortening the preliminaries to two
+          pages could work (I could expand the introduction by 0.5 page)
+  \end{itemize}
+}
 
@@
 signifies the replacement of all instances of $x_{i}$ with $y_{i}$ for all
-$i = 1, \dots, n$.
+$i = 1, \dots, n$. Additionally, for any variable $n$ and
+$a, b \in \mathbb{N}_{0}$, let $[a \le n \le b] \coloneqq \begin{cases}
+  1 & \text{if $a \le n \le b$} \\
+  0 & \text{otherwise}
+\end{cases}$.
 
@@
 quantifiers, computing the FOMC using \Cranetwo{} requires the use of WFOMC\@.
-For such sentences, Skolemization (described in \cref{sec:crane}) introduces
+For such sentences, preprocessing (described in \cref{sec:crane}) introduces
 predicates with non-unary weights that must be accounted for to compute the
-correct model count. Additionally, our formulation of the definition of WFOMC is
-somewhat complicated by the need to support any number of domains.
+correct model count.
+
+% Additionally, our formulation of the definition of WFOMC is
+% somewhat complicated by the need to support any number of domains.
 
@@
 \begin{example}[Counting bijections]\label{example:overall}
-  Let $\phi$ be the following formula (previously examined by Dilkas and
+  Let us consider the following formula (previously examined by Dilkas and
   Belle~\cite{DBLP:conf/kr/DilkasB23}) that defines predicate $P$ as a bijection
   between two domains $\Gamma$ and $\Delta$:
-  \[
+  \begin{equation}\label[formula]{eq:bijections}
     \begin{gathered}
@@
     \end{gathered}
-  \]
+  \end{equation}
   Let $\sigma$ be defined as $\sigma(\Gamma) \coloneqq \{\, 1, 2\,\}$, and
-  $\sigma(\Delta) \coloneqq \{\,a, b\,\}$. Then $\phi$ has two models:
+  $\sigma(\Delta) \coloneqq \{\,a, b\,\}$. Then \cref{eq:bijections} has two
+  models:
   \[
@@
 
-\subsection{First-Order Knowledge Compilation}\label{sec:crane}
-
-\todo[inline]{It would be nice to give the necessary introduction to FOKC, or
-  \textsc{Crane} (an intuitive explanation early in the paper)}
-
-There are two crucial preprocessing steps that transform an arbitrary sentence
-in first-order logic into the form used internally: Skolemization and rewriting
-the sentence as a conjunction of clauses. We describe the former in more detail.
-\emph{Skolemization}~\cite{DBLP:conf/kr/BroeckMD14} is a procedure that
-transforms a formula with existential quantifiers into a formula without
-existential quantifiers \emph{with the same WFOMC}. (Note that it is different
-from the standard Skolemization that introduces function
-symbols~\cite{DBLP:books/daglib/0030198}.)
-
-\begin{example}
-  Skolemization transforms
+\subsection{Crane and First-Order Knowledge Compilation}\label{sec:crane}
+
+\todo[inline]{Make sure the distinction between function definitions and
+  equations is clear.}
+
+As our work builds on \textsc{Crane}, in this section we will briefly outline
+the steps \textsc{Crane} goes through to compile an \FO{} formula into a set of
+function definitions. We divide the inner workings of the algorithm into two
+stages: preprocessing and compilation.
+
+\subsubsection{Preprocessing}
+
+The goal of this stage is to transform an arbitrary \FO{} formula into the
+format described in \cref{sec:logic}, most importantly by eliminating
+existential quantifiers. For example, the first conjunct of
+\cref{eq:bijections}, i.e.,
 \begin{equation}\label[formula]{eq:skolemizationinitial}
@@
 \end{equation}
-  into
+is transformed into
 \begin{equation}\label[formula]{eq:skolemization}
@@
     (\forall x \in \Gamma\text{. } &S(x) \lor Z(x))\land{}\\
-      (\forall x \in \Gamma\text{. } \forall y \in \Delta\text{. } &S(x) \lor \neg P(x, y)).
+    (\forall x \in \Gamma\text{. } \forall y \in \Delta\text{. } &S(x) \lor \neg P(x, y)),
   \end{aligned}
 \end{equation}
-  With suitable weights on the new predicates $S/1$ and $Z/1$, the WFOMC of
-  \cref{eq:skolemization} is equal to the FOMC of
-  \cref{eq:skolemizationinitial}.
+where $Z/1$ and $S/1$ are two new predicates with $w^{-}(S) = -1$. One can check
+that the WFOMC of \cref{eq:skolemizationinitial,eq:skolemization} is the same.
+
+\subsubsection{Compilation}
+
+At this stage, the preprocessed formula is compiled into the set $\mathcal{E}$
+of equations and two auxiliary maps $\mathcal{F}$ and $\mathcal{D}$.
+$\mathcal{F}$ maps function names to formulas, and $\mathcal{D}$ maps function
+names and argument indices to domains. $\mathcal{E}$ can contain any number of
+functions, one of which (which we will always denote by $f$) represents the
+solution to the FOMC problem. To compute the FOMC for particular domain sizes,
+$f$ must be evaluated with those domain sizes as arguments. $\mathcal{D}$
+records this correspondence between function arguments and domains.
+
+\begin{example}
+  \textsc{Crane} compiles \cref{eq:bijections} for bijection counting into
+  \begin{align*}
+    \mathcal{E} &= \left\{\,\begin{aligned}f(m, n) &= \sum_{l=0}^{n} \binom{n}{l}{(-1)}^{n-l}g(l, m),\\ g(l, m) &= \sum_{k=0}^{m}[0 \le k \le 1]\binom{m}{k}g(l-1, m-k)\end{aligned}\,\right\};\\
+    \mathcal{D} &= \{\, (f, 1) \mapsto \Gamma, (f, 2) \mapsto \Delta, (g, 1) \mapsto \Delta^{\top}, (g, 2) \mapsto \Gamma \,\},
+  \end{align*}
+  where $\Delta^{\top}$ is a newly introduced domain. (We omit the definition of
+  $\mathcal{F}$ as the formulas can get quite verbose.) To compute the number of
+  bijections between two sets of cardinality 3, one would evaluate $f(3, 3)$,
+  however, the definition of $g$ is incomplete: $g$ is a recursive function
+  presented without any base cases. $\mathcal{D}$ encodes that in $f(m, n)$, $m$
+  and $n$ represent $|\Gamma|$ and $|\Delta|$, respectively. Similarly, in
+  $g(l, m)$, $l$ represents $|\Delta^{\top}|$, and $m$ represents $|\Gamma|$.
 \end{example}
+
+Compilation is performed primarily by applying \emph{(compilation) rules} to
+formulas. \textsc{Crane} has two modes depending on how the algorithm chooses
+which compilation rule to apply to a formula (in case several alternatives are
+available). The first option is to use greedy search: there is a list of rules,
+and the first applicable rule is the one that gets used, disregarding all the
+others. The second option is to use a combination of greedy and
+\emph{breadth-first search} (BFS). That is, each compilation rule is identified
+as either greedy or non-greedy. Greedy rules are applied as soon as possible at
+any stage of the compilation process. BFS is executed over all applicable
+non-greedy rules, identifying the solution that can be constructed using the
+smallest number of such rules.
 
@@
 
-Before describing the main contribution of this work, let us review the
-essential aspects of FOKC as realised by \textsc{Crane}. The input formula is
-compiled into: set $\mathcal{E}$ of equations, map $\mathcal{F}$ from function
-names to formulas, and map $\mathcal{D}$ from function names and argument
-indices to domains. $\mathcal{E}$ can contain any number of functions, one of
-which (denoted by $f$) represents the solution to the FOMC problem. To compute
-the FOMC for particular domain sizes, $f$ must be evaluated with those domain
-sizes as arguments. $\mathcal{D}$ records this correspondence between function
-arguments and domains.
-
 \begin{algorithm}[t]
@@
 \end{algorithm}
+
+\todo[inline]{Connect this with the preliminaries?}
 
@@
 
+\todo[inline]{The example below builds on \cref{sec:crane}. Shorten it.}
+
 \begin{example}\label{example:overalltwo}
@@
   the formula $\forall x \in \Gamma\text{. }S(x) \lor \neg S(x)$, where $S$ is a
-  predicate introduced by Skolemization with weights $w^{+}(S) = 1$ and
+  predicate introduced by preprocessing with weights $w^{+}(S) = 1$ and
   $w^{-}(S) = -1$. Hence, we obtain the base case $g(0, m) = 0^{m}$. In the case
@@
 $a, b \in \mathbb{N}_{0}$ are constants, and $f$ is an expression that may
-depend on $m$. Additionally, $[a \le m \le b] = \begin{cases}
-  1 & \text{if $a \le m \le b$} \\
-  0 & \text{otherwise}
-\end{cases}$.
-\Simplify transforms this pattern into
+depend on $m$. \Simplify transforms this pattern into
 $f(a) + f(a+1) + \cdots + f(\min\{\, n, b \,\})$. For instance, in the case of
@@
 $g(l, m) = g(l-1, m) + mg(l-1, m-1)$.
+
+\todo[inline]{Check if the above is still clear given all the changes.}
 
@@
           independent practical assessment'')
-    \item The difference between \Cranegreedy{} and \Cranebfs{} is in how the
-          algorithm chooses which compilation rule to apply to a formula. The
-          former uses greedy search: there is a list of rules, and the first
-          applicable rule is the one that gets used, disregarding all the
-          others. The latter uses a combination of greedy and breadth-first
-          search (BFS). That is, each compilation rule is identified as either
-          greedy or non-greedy. Greedy rules are applied as soon as possible at
-          any stage of the compilation process. BFS is executed over all
-          applicable non-greedy rules, identifying the solution that can be
-          constructed using the smallest number of such rules.
   \end{itemize}
@@
 algorithm similar to \textsc{ForcLift} and another that combines greedy and
-breadth-first search.
+BFS\@.
 

### 2025-01-20 doc/paper/paper.tex
Done with Section 2 for now

@@
   \begin{itemize}
-    \item Adjust the introduction to the new structure (with more subsections)
     \item If I need more space elsewhere, shortening the preliminaries to two
-          pages could work (I could expand the introduction by 0.5 page)
+          pages (perhaps skipping Section 2.2 altogether?)
+    \item Adjust the introductory paragraph below to the new structure (with
+          more subsections)
   \end{itemize}
@@
 
-\todo[inline]{Make sure the distinction between function definitions and
-  equations is clear.}
-
 As our work builds on \textsc{Crane}, in this section we will briefly outline
@@
 $x_{i} = y_{i}$ whenever $x_{i}, y_{i} \in \mathbb{N}_{0}$. An \emph{equation}
-is $f(\mathbf{x}) = \expr{}$, where $f(\mathbf{x})$ is a signature.
+is $f(\mathbf{x}) = \expr{}$, where $f(\mathbf{x})$ is a function call.
 
@@
 approaches~\cite{DBLP:conf/kr/KazemiP16}.
-
-\todo[inline]{Somewhere: Recall that each equation is either the definition (did
-  I define what a definition is?) of a function or the definition of a base case
-  of a function. (I could put this in the preliminaries as definitions and then
-  reference them below)}
 

### 2025-01-20 doc/paper/paper.tex
Rework Example 8

@@
 
-\begin{example}[Counting bijections]\label{example:overall}
+\begin{example}[Counting bijections]\label{example:bijections}
   Let us consider the following formula (previously examined by Dilkas and
@@
 
-\subsubsection{Compilation}
+\subsubsection{Compilation}\label{sec:compilation}
 
@@
   \begin{itemize}
-    \item The algorithm’s recursive nature and its interaction with
-          \textsc{Crane} could be explained more clearly
     \item More emphasis on the motivation for each part of \Cranetwo{} (e.g.,
@@
 
-\todo[inline]{Connect this with the preliminaries?}
+\todo[inline,caption={}]{
+  \begin{itemize}
+    \item Reorganise this section (e.g., where do I put the description of
+          Simplify?), bringing some TODOs from above.
+    \item The algorithm’s recursive nature and its interaction with
+          \textsc{Crane} could be explained more clearly
+  \end{itemize}
+}
 
@@
 formula into equations that include the necessary base cases. To begin, we use
-the FOKC algorithm of the original \textsc{Crane} to compile the formula into
-the three components: $\mathcal{E}$, $\mathcal{F}$, and $\mathcal{D}$. After
+\textsc{Crane} to compile the formula into the three components: $\mathcal{E}$,
+$\mathcal{F}$, and $\mathcal{D}$ (as described in \cref{sec:compilation}). After
 some algebraic simplification, $\mathcal{E}$ is passed to the \FindBaseCases
@@
 formulas and adds the resulting base case equations to $\mathcal{E}$.
-\Cref{example:overall} below provides more detail.
+\Cref{example:bijections} below provides more detail.
 
@@
 
-\todo[inline]{The example below builds on \cref{sec:crane}. Shorten it.}
-
-\begin{example}\label{example:overalltwo}
-  Let us examine the first solution returned by \Cranetwo{} for the
-  bijection-counting problem in \cref{example:overall}. After
-  \autoref{line:second}, we have
-  \begin{align*}
-    \mathcal{E} &= \left\{\,\begin{aligned}f(m, n) &= \sum_{l=0}^{n} \binom{n}{l}{(-1)}^{n-l}g(l, m),\\ g(l, m) &= g(l-1, m) + mg(l-1, m-1)\end{aligned}\,\right\};\\
-    \mathcal{D} &= \{\, (f, 1) \mapsto \Gamma, (f, 2) \mapsto \Delta, (g, 1) \mapsto \Delta^{\top}, (g, 2) \mapsto \Gamma \,\},
-  \end{align*}
-  where $\Delta^{\top}$ is a new domain. (We omit the definition of
-  $\mathcal{F}$ as the formulas can get a bit verbose.) Then \FindBaseCases
-  identifies two base cases: $g(0, m)$ and $g(l, 0)$. In both cases,
-  \CompileWithBaseCases recurses on the formula $\mathcal{F}(g)$ simplified by
-  assuming that one of the domains is empty. In the first case, we recurse on
-  the formula $\forall x \in \Gamma\text{. }S(x) \lor \neg S(x)$, where $S$ is a
-  predicate introduced by preprocessing with weights $w^{+}(S) = 1$ and
-  $w^{-}(S) = -1$. Hence, we obtain the base case $g(0, m) = 0^{m}$. In the case
-  of $g(l, 0)$, \Propagate{$\psi$, $\Gamma$, $0$} returns an empty formula,
-  resulting in $g(l, 0) = 1$.
-\end{example}
-
-It is worth noting that these base cases overlap when $l = m = 0$ but remain
-consistent since $0^{0} = 1$. Generally, let $\phi$ be a formula with two
-domains $\Gamma$ and $\Delta$, and let $n, m \in \mathbb{N}_{0}$. Then the FOMC
-of \Propagate{$\phi$, $\Delta$, $n$} assuming $|\Gamma| = m$ is the same as the
-FOMC of \Propagate{$\phi$, $\Gamma$, $m$} assuming $|\Delta| = n$.
-
-Finally, the main responsibility of the \Simplify procedure is to handle the
-algebraic pattern $\sum_{m=0}^{n}[a \le m \le b] f(m)$. Here: $n$ is a variable,
+\paragraph*{Simplify}
+The main responsibility of the \Simplify procedure is to handle the algebraic
+pattern $\sum_{m=0}^{n}[a \le m \le b] f(m)$. Here: $n$ is a variable,
 $a, b \in \mathbb{N}_{0}$ are constants, and $f$ is an expression that may
 depend on $m$. \Simplify transforms this pattern into
-$f(a) + f(a+1) + \cdots + f(\min\{\, n, b \,\})$. For instance, in the case of
-\cref{example:overalltwo}, \Simplify transforms
+$f(a) + f(a+1) + \cdots + f(\min\{\, n, b \,\})$.
+
+\begin{example}\label{example:bijectionstwo}
+  Let us return to the bijection-counting problem from \cref{example:bijections}
+  and its initial solution described in \cref{example:bijectionstwo}. On
+  \autoref{line:second}, \Simplify transforms
   $g(l, m) = \sum_{k=0}^{m}[0 \le k \le 1]\binom{m}{k}g(l-1, m-k)$ into
-$g(l, m) = g(l-1, m) + mg(l-1, m-1)$.
-
-\todo[inline]{Check if the above is still clear given all the changes.}
+  $g(l, m) = g(l-1, m) + mg(l-1, m-1)$. Then \FindBaseCases identifies two base
+  cases: $g(0, m)$ and $g(l, 0)$. In both cases, \CompileWithBaseCases recurses
+  on the formula $\mathcal{F}(g)$ simplified by assuming that one of the domains
+  is empty. In the first case, we recurse on the formula
+  $\forall x \in \Gamma\text{. }S(x) \lor \neg S(x)$, where $S$ is a predicate
+  introduced by preprocessing with weights $w^{+}(S) = 1$ and $w^{-}(S) = -1$.
+  Hence, we obtain the base case $g(0, m) = 0^{m}$. In the case of $g(l, 0)$,
+  \Propagate{$\psi$, $\Gamma$, $0$} returns an empty formula, resulting in
+  $g(l, 0) = 1$.
+
+  While these base cases overlap when $l = m = 0$, they remain consistent since
+  $0^{0} = 1$. Generally, let $\phi$ be a formula with two domains $\Gamma$ and
+  $\Delta$, and let $n, m \in \mathbb{N}_{0}$. Then the FOMC of
+  \Propagate{$\phi$, $\Delta$, $n$} assuming $|\Gamma| = m$ is the same as the
+  FOMC of \Propagate{$\phi$, $\Gamma$, $m$} assuming $|\Delta| = n$.
+\end{example}
 
 \subsection{Identifying a Sufficient Set of Base Cases}\label{sec:identifying}
-
-\todo[inline]{Prove correctness?}
 
@@
 \begin{example}
-  Consider the recursive function $g$ from \cref{example:overalltwo}.
+  Consider the recursive function $g$ from \cref{example:bijectionstwo}.
   \FindBaseCases iterates over two function calls: $g(l-1, m)$ and
@@
 \begin{algorithm}[t]
-  \caption{A sketch of the C++ program for the equations in \cref{example:overalltwo}, particularly highlighting the recursive definition of function $g$.}\label{alg:cpp}
+  \caption{A sketch of the C++ program for the equations in \cref{example:bijectionstwo}, particularly highlighting the recursive definition of function $g$.}\label{alg:cpp}
   initialise $\Cache_{g(0, m)}$, $\Cache_{g(l, 0)}$, $\Cache_{g}$, and $\Cache_{f}$\;
@@
 and Belle~\cite{DBLP:conf/kr/DilkasB23}. Its formulation in \FO{} is described
-in \cref{example:overall}. The equivalent formula in \Ctwo{} is
+in \cref{example:bijections}. The equivalent formula in \Ctwo{} is
 \[

### 2025-01-21 doc/paper/paper.tex
Clean up Section 3.1, adding another termination proof

@@
 
-\begin{example}
+\begin{example}\label{example:solution}
   \textsc{Crane} compiles \cref{eq:bijections} for bijection counting into
@@
 
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item More emphasis on the motivation for each part of \Cranetwo{} (e.g.,
-          how \FindBaseCases addresses key issues in \textsc{Crane}) would add
-          depth to the contribution
-    \item this section should be expanded by 1 page (``a clear discussion of the
-          innovation aspect and technical parts'')
-  \end{itemize}
-}
+\todo[inline,caption={}]{Add a discussion of the innovation aspect and technical
+  parts. Motivate each part of \Cranetwo{} (e.g., how \FindBaseCases addresses
+  key issues in \textsc{Crane}).}
 
@@
   $\mathcal{E} \gets \Simplify{$\mathcal{E}$}$\;\label{line:second}
-  \ForEach{base case $f(\mathbf{x}) \in \FindBaseCases{$\mathcal{E}$}$}{
+  \ForEach{base case $f(\mathbf{x}) \in \FindBaseCases{$\mathcal{E}$}$}{\label{line:loopy}
     $\psi \gets \mathcal{F}(f)$\;
-    \lForEach{index $i$ such that $x_{i} \in \mathbb{N}_{0}$}{$\psi \gets \Propagate{$\psi$, $\mathcal{D}(f, i)$, $x_i$}$}
+    \lForEach{index $i$ such that $x_{i} \in \mathbb{N}_{0}$}{$\psi \gets \Propagate{$\psi$, $\mathcal{D}(f, i)$, $x_i$}$}\label{line:propagate}
     $\mathcal{E} \gets \mathcal{E} \cup \CompileWithBaseCases{$\psi$}$\;\label{line:final}
@@
 \end{algorithm}
-
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item Reorganise this section (e.g., where do I put the description of
-          Simplify?), bringing some TODOs from above.
-    \item The algorithm’s recursive nature and its interaction with
-          \textsc{Crane} could be explained more clearly
-  \end{itemize}
-}
 
@@
 $\mathcal{F}$, and $\mathcal{D}$ (as described in \cref{sec:compilation}). After
-some algebraic simplification, $\mathcal{E}$ is passed to the \FindBaseCases
-procedure (see \cref{sec:identifying}). For each base case $f(\mathbf{x})$, we
-retrieve the logical formula $\mathcal{F}(f)$ associated with the function name
-$f$ and simplify it using the \Propagate procedure (explained in detail in
-\cref{sec:propagating}). We do this by iterating over all indices of
-$\mathbf{x}$, where $x_{i}$ is a constant, and using \Propagate to simplify
-$\psi$ by assuming that domain $\mathcal{D}(f, i)$ has size $x_{i}$. Finally, on
-\autoref{line:final}, \CompileWithBaseCases recurses on these simplified
-formulas and adds the resulting base case equations to $\mathcal{E}$.
-\Cref{example:bijections} below provides more detail.
-
-\begin{remark*}
-  Although \CompileWithBaseCases starts with a call to \textsc{Crane}, the
-  proposed algorithm is not just a post-processing step for FOKC because
-  \cref{alg:compilewithbasecases} is recursive and can issue more calls to
-  \textsc{Crane} on various derived formulas.
-\end{remark*}
+some algebraic simplifications (described below), $\mathcal{E}$ is passed to the
+\FindBaseCases procedure (see \cref{sec:identifying}). For each base case
+$f(\mathbf{x})$, we retrieve the logical formula $\mathcal{F}(f)$ associated
+with the function name $f$ and simplify it using the \Propagate procedure
+(explained in detail in \cref{sec:propagating}). We do this by iterating over
+all indices of $\mathbf{x}$, where $x_{i}$ is a constant, and using \Propagate
+to simplify $\psi$ by assuming that domain $\mathcal{D}(f, i)$ has size $x_{i}$.
+Finally, on \autoref{line:final}, \CompileWithBaseCases recurses on these
+simplified formulas and adds the resulting base case equations to $\mathcal{E}$.
 
@@
   Let us return to the bijection-counting problem from \cref{example:bijections}
-  and its initial solution described in \cref{example:bijectionstwo}. On
-  \autoref{line:second}, \Simplify transforms
-  $g(l, m) = \sum_{k=0}^{m}[0 \le k \le 1]\binom{m}{k}g(l-1, m-k)$ into
-  $g(l, m) = g(l-1, m) + mg(l-1, m-1)$. Then \FindBaseCases identifies two base
-  cases: $g(0, m)$ and $g(l, 0)$. In both cases, \CompileWithBaseCases recurses
-  on the formula $\mathcal{F}(g)$ simplified by assuming that one of the domains
-  is empty. In the first case, we recurse on the formula
+  and its initial solution described in \cref{example:solution}. \Simplify
+  transforms $g(l, m) = \sum_{k=0}^{m}[0 \le k \le 1]\binom{m}{k}g(l-1, m-k)$
+  into $g(l, m) = g(l-1, m) + mg(l-1, m-1)$. Then \FindBaseCases identifies two
+  base cases: $g(0, m)$ and $g(l, 0)$. In both cases, \CompileWithBaseCases
+  recurses on the formula $\mathcal{F}(g)$ simplified by assuming that one of
+  the domains is empty. In the first case, we recurse on the formula
   $\forall x \in \Gamma\text{. }S(x) \lor \neg S(x)$, where $S$ is a predicate
@@
   \Propagate{$\psi$, $\Gamma$, $0$} returns an empty formula, resulting in
-  $g(l, 0) = 1$.
-
-  While these base cases overlap when $l = m = 0$, they remain consistent since
-  $0^{0} = 1$. Generally, let $\phi$ be a formula with two domains $\Gamma$ and
-  $\Delta$, and let $n, m \in \mathbb{N}_{0}$. Then the FOMC of
-  \Propagate{$\phi$, $\Delta$, $n$} assuming $|\Gamma| = m$ is the same as the
-  FOMC of \Propagate{$\phi$, $\Gamma$, $m$} assuming $|\Delta| = n$.
+  $g(l, 0) = 1$. While these base cases overlap when $l = m = 0$, they remain
+  consistent since $0^{0} = 1$.
 \end{example}
+
+% Generally, let $\phi$ be a formula with two domains $\Gamma$ and $\Delta$, and
+% let $n, m \in \mathbb{N}_{0}$. Then the FOMC of \Propagate{$\phi$, $\Delta$,
+%   $n$} assuming $|\Gamma| = m$ is the same as the FOMC of \Propagate{$\phi$,
+%   $\Gamma$, $m$} assuming $|\Delta| = n$.
+
+% Although \CompileWithBaseCases starts with a call to \textsc{Crane}, the
+% proposed algorithm is not just a post-processing step for FOKC because
+% \cref{alg:compilewithbasecases} is recursive and can issue more calls to
+% \textsc{Crane} on various derived formulas.
+
+We end this section by proving that \CompileWithBaseCases terminates since each
+recursive call on \autoref{line:final} reduces the number of domains in the
+formula.
+
+\begin{theorem}
+  Given any \FO{} formula $\phi$, \CompileWithBaseCases{$\phi$} terminates.
+\end{theorem}
+
+To prove the theorem, we rely on two observations about the algorithms presented
+in \cref{sec:identifying,sec:propagating}.
+
+\begin{observation}\label{observation1}
+  Each base case returned by \FindBaseCases has at least one constant (in line
+  with \cref{def:basecase}).
+\end{observation}
+
+\begin{observation}\label{observation2}
+  For any formula $\phi$, domain $\Delta$, and $n \in \mathbb{N}_{0}$,
+  \Propagate{$\phi$, $\Delta$, $n$} returns a formula with no variables
+  quantified over $\Delta$.
+\end{observation}
+
+\begin{proof}
+  We proceed by induction on the number of domains that variables in $\phi$ are
+  quantified over. If there are no domains, then $\phi$ is essentially a
+  propositional formula, and \textsc{Crane} compiles it into an equation of the
+  form $f = \expr$ with no `function calls'. Suppose that \CompileWithBaseCases
+  terminates for all formulas with at most $n \in \mathbb{N}_{0}$ domains. Let
+  $\phi$ be a formula with $n+1$ domains. By \cref{observation1}, each base case
+  on \autoref{line:loopy} of \cref{alg:compilewithbasecases} has at least one
+  constant. Therefore, by \cref{observation2}, after \autoref{line:propagate},
+  formula $\psi$ has at most $n$ domains. Thus, \autoref{line:final} terminates
+  by the inductive hypothesis, completing the proof that \CompileWithBaseCases
+  terminates for an arbitrary formula with $n+1$ domains.
+\end{proof}
 
@@
 \begin{example}
-  Consider the recursive function $g$ from \cref{example:bijectionstwo}.
+  Consider the recursive function $g$ from \cref{example:solution}.
   \FindBaseCases iterates over two function calls: $g(l-1, m)$ and
@@
 
-\begin{theorem}[Termination]\label{thm:halting}
+\begin{theorem}\label{thm:halting}
   Let $f$ be an $n$-ary function in $\mathcal{E}$ and
@@
 \begin{algorithm}[t]
-  \caption{A sketch of the C++ program for the equations in \cref{example:bijectionstwo}, particularly highlighting the recursive definition of function $g$.}\label{alg:cpp}
-  initialise $\Cache_{g(0, m)}$, $\Cache_{g(l, 0)}$, $\Cache_{g}$, and $\Cache_{f}$\;
-  \DontPrintSemicolon
-  \textbf{Function} $g_{0,m}(m)$\textbf{:} \dots\;
-  \textbf{Function} $g_{l,0}(l)$\textbf{:} \dots\;
-  \PrintSemicolon
+  \caption{A sketch of the C++ program for the equations in \cref{example:solution}, particularly highlighting the recursive definition of function $g$.}\label{alg:cpp}
+  initialise $\Cache_{g(0, m)}$, $\Cache_{g(l, 0)}$, $\Cache_{g}$, and
+  $\Cache_{f}$\; \DontPrintSemicolon \textbf{Function} $g_{0,m}(m)$\textbf{:}
+  \dots\; \textbf{Function} $g_{l,0}(l)$\textbf{:} \dots\; \PrintSemicolon
   \Fn{$g(l, m)$}{
@@
     \lIf{$m = 0$}{\Return{$g_{l,0}(l)$}}\label{line:basecasetwo}
-    $r \gets g(l-1, m) + mg(l-1,m-1)$\;
-    $\Cache_{g}(l, m) \gets r$\;
-    \Return{$r$}\;
-  }
-  \DontPrintSemicolon
-  \textbf{Function} $f(m, n)$\textbf{:} \dots\;
-  \PrintSemicolon
-  \Fn{\Main}{
-    $(m, n) \gets \Input{}$\;
-    \Return{$f(m, n)$}\;
-  }
+    $r \gets g(l-1, m) + mg(l-1,m-1)$\; $\Cache_{g}(l, m) \gets r$\;
+    \Return{$r$}\; } \DontPrintSemicolon \textbf{Function} $f(m, n)$\textbf{:}
+  \dots\; \PrintSemicolon \Fn{\Main}{ $(m, n) \gets \Input{}$\;
+    \Return{$f(m, n)$}\; }
 \end{algorithm}
@@
 
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item Experiments could be expanded by 1 page (``a more thorough and
-          independent practical assessment'')
-  \end{itemize}
-}
+\todo[inline]{Expand the section, adding a more thorough and independent
+  practical assessment}
 

### 2025-01-22 doc/paper/paper.tex
Significantly expand the introductory part of Section 3

@@
 
-\todo[inline,caption={}]{Add a discussion of the innovation aspect and technical
-  parts. Motivate each part of \Cranetwo{} (e.g., how \FindBaseCases addresses
-  key issues in \textsc{Crane}).}
-
 \begin{figure*}[t]
@@
     for different domain sizes. To accomplish this, the \CompileWithBaseCases
-    procedure makes use of the FOKC algorithm of \textsc{Crane}, algebraic
-    simplification techniques (denoted as \Simplify), and two other auxiliary
-    procedures. }\label{fig:overview}
+    procedure uses \textsc{Crane}, algebraic simplification techniques (denoted
+    as \Simplify), and two other auxiliary procedures. }\label{fig:overview}
 \end{figure*}
 
-\Cref{fig:overview} provides an overview of \Cranetwo{}'s workflow.
-\Cref{sec:completing} describes the main algorithm for completing the
-definitions of recursive functions with a sufficient set of base cases.
-\Cref{sec:identifying,sec:propagating} describe subsidiary algorithms for
-constructing a set of base cases and their corresponding logical formulas.
-\Cref{sec:smoothing} explains the post-processing techniques for ensuring
-accurate model counting. Additionally, \cref{sec:cpp} explains the process of
-compiling equations into C++ code, greatly expanding upon the range of formulas
-that could previously be handled by similar
-approaches~\cite{DBLP:conf/kr/KazemiP16}.
+\Cref{fig:overview} provides an overview of \Cranetwo{}'s workflow. Below we
+briefly describe and motivate each procedure before going into more detail in
+the corresponding subsection.
+
+\CompileWithBaseCases (see \cref{sec:completing}), the core procedure of
+\Cranetwo{}, is responsible for completing the function definitions produced by
+\textsc{Crane} with the necessary base cases. To do so, it may recursively call
+itself (and \textsc{Crane}) on other formulas. We prove that the number of such
+recursive calls is upper bounded by the number of domains in the formula.
+
+\cref{sec:completing} also describes the \Simplify procedure for algebraic
+simplification. It is crucial for simplifying, e.g., a sum of $n$ terms, only
+two of which are non-zero. More generally, the equations returned by
+\textsc{Crane} often benefit from easy-to-detect algebraic simplifications such
+as $0 \cdot \text{anything} = 0$ and $\text{anything}^{0} = 1$.
+
+\FindBaseCases (described in \cref{sec:identifying}) inspects a set of equations
+to identify a sufficient set of base cases for a given set of equations. We
+prove that the returned set of base cases is sufficient, and the evaluation of
+the resulting function definitions will never get stuck in an infinite loop.
+
+\Cref{sec:propagating} introduces the \Propagate procedure that takes a formula
+$\phi$, a domain $\Delta$, and $n \in \mathbb{N}_{0}$. It returns $\phi$
+transformed with the assumption that $|\Delta| = n$, introducing $n$ new
+constants and removing all variables quantified over $\Delta$. For example, when
+computing a base case such as $f(0, y)$, \Propagate will significantly simplify
+$\phi$ with the assumption that the domain associated with the first parameter
+of $f$ (i.e., $\mathcal{D}(f, 1)$) is empty. When run on this simplified
+formula, \CompileWithBaseCases will return the equations for the base case
+$f(0, y)$.
+
+\Cref{sec:smoothing} describes a new kind of \emph{smoothing} used to ensure
+that \Propagate preserves the correct model count. Smoothing is a well-known
+technique in knowledge compilation algorithms for propositional model
+counting~\cite{darwiche2001tractable}. Although it has been applied to FOMC
+before~\cite{DBLP:conf/ijcai/BroeckTMDR11}, our setting requires a novel
+approach.
+
+\CompileWithBaseCases, together with the other procedures outlined above, return
+a set of equations that fully cover the base cases of all recursive functions.
+While these equations can be interesting and valuable in their own right, the
+users of FOMC algorithms typically expect a numerical answer. Thus,
+\cref{sec:cpp} describes how these equations are compiled into a C++ program
+that can be executed with different command-line arguments to compute the model
+count for different combinations of domain sizes.
 
@@
 
-\emph{Smoothing} modifies a circuit to reintroduce eliminated atoms, ensuring
-the correct model
-count~\cite{darwiche2001tractable,DBLP:conf/ijcai/BroeckTMDR11}. In this
-section, we describe a similar process performed on
+Smoothing modifies a circuit to reintroduce eliminated atoms, ensuring the
+correct model count~\cite{darwiche2001tractable,DBLP:conf/ijcai/BroeckTMDR11}.
+In this section, we describe a similar process performed on
 lines~\ref{line:presmoothing}--\ref{line:smoothing2} of \cref{alg:propagate}.

### 2025-01-24 doc/paper/paper.tex
Resize the figure

@@
 
-% 1. Introduction
-% Objective: Briefly state the goals of the experiments.
-% Overview: Summarize the structure of the section.
-
-% 2. Experimental Setup
-
-% Baselines: List and describe the baseline methods or systems used for
-% comparison.
-
 \todo[inline]{Expand the section, adding a more thorough and independent
@@
 while the other algorithms were executed on the Java Virtual Machine 1.8.0\_201.
-
-% It would not make sense to include the original \textsc{Crane} algorithm in
-% the experiments or evaluate \Cranetwo{} without the C++ code generation
-% described in \cref{sec:cpp}. Indeed, these algorithms can only produce
-% mathematical definitions of functions without evaluating them.
-
-% While greedy search is more efficient (in terms of being able to handle larger
-% formulas), it is a heuristic that can miss some solutions.
-
-% Datasets: Provide details about the datasets used in the experiments,
-% including size, source, and any preprocessing steps.
 
@@
 
-%Since \textsc{FastWFOMC} does not support many-sorted logic, our experiments are
-%limited to formulas with a single domain. However, many of the counting problems
-%used in the experimental evaluation of
-%\textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23} become equivalent (in terms of
-%generating equivalent integer sequences) when restricted to a single domain.
-%Additionally, comparing \Cranetwo{} and \textsc{FastWFOMC} on a broader set of
-%problems is challenging because each problem needs to be represented in two
-%(quite different) logics: \FO{} and \UFO{}.
-
 The three benchmark families cover a wide range of possibilities. The
@@
 
-% Metrics: Define the performance metrics used to evaluate the results (e.g.,
-% accuracy, precision, recall, F1-score, runtime).
-
-%A considerable difference between \textsc{ForcLift} and the other two algorithms
-%is that \textsc{ForcLift} does not support arbitrary precision whereas the other
-%algorithms use the GNU Multiple Precision Arithmetic Library. Thus, when the
-%count exceeds finite precision, \textsc{ForcLift} returns $\infty$.
-
 For evaluation purposes, we ran each algorithm on each benchmark using domains
@@
 
-% Environment: Describe the hardware and software environment (e.g.,
-% specifications of the computer, operating system, libraries, and tools used).
-
-% 3. Results and Analysis
-% Presentation of Results: Use tables, graphs, and charts to present the experimental results clearly.
-% Comparison with Baselines: Compare your method’s results with the baselines.
-% Discussion: Analyze and interpret the results, highlighting the strengths and potential weaknesses of your approach.
-% Insights: Provide insights or patterns observed from the results.
-% Challenges: Discuss any challenges or unexpected outcomes.
-% Acknowledgement: Honestly acknowledge any limitations of your experiments or method.
-
 \subsection{Results}
@@
   \begin{itemize}
-    \item On the `friends' and `functions' benchmarks, \textsc{ForcLift} runs
-          until the model count exceeds $2^{31}-1$.
      \item We are not aware of any formulas on which \Cranetwo{} scales worse
@@
 were \num{64} and \num{4096}, respectively. On the other two benchmarks,
-\textsc{ForcLift} had the lowest runtime. However, due to its finite precision,
-it only scaled up to domain sizes of \num{16} and \num{128} for `friends' and
-`functions', respectively. \textsc{FastWFOMC} outperformed \textsc{ForcLift} in
-the case of `friends', but not `functions', as it could handle domains of size
-\num{1024} and \num{64}, respectively. Furthermore, both \Cranebfs{} and
-\Cranegreedy{} performed similarly on both benchmarks. Similarly to the
-`bijections' benchmark, \Cranetwo{} significantly outperformed the other two
-algorithms, scaling up to domains of size \num{8192} and \num{67108864},
-respectively.
+\textsc{ForcLift} had the lowest runtime. However, since it can only handle
+model counts smaller than $2^{31}$, it only scales up to domain sizes of
+\num{16} and \num{128} for `friends' and `functions', respectively.
+\textsc{FastWFOMC} outperformed \textsc{ForcLift} in the case of `friends', but
+not `functions', as it could handle domains of size \num{1024} and \num{64},
+respectively. Furthermore, both \Cranebfs{} and \Cranegreedy{} performed
+similarly on both benchmarks. Similarly to the `bijections' benchmark,
+\Cranetwo{} significantly outperformed the other two algorithms, scaling up to
+domains of size \num{8192} and \num{67108864}, respectively.
 
@@
 
-% 8. Conclusion
-% Summary: Briefly summarize the key findings from the experimental results.
-% Future Work: Suggest directions for future research based on your findings.
-
 Based on our experiments, which algorithm should be used in practice? If the
@@
 In this work, we have presented a scalable automated FOKC-based approach to
-FOMC. Our algorithm involves completing the definitions of recursive functions
+FOMC\@. Our algorithm involves completing the definitions of recursive functions
 and subsequently translating all function definitions into C++ code. Empirical

### 2025-01-24 doc/paper/plot.tex
Resize the figure

@@
-% Created by tikzDevice version 0.12.6 on 2024-08-07 14:16:35
+% Created by tikzDevice version 0.12.6 on 2025-01-24 14:00:20
 % !TEX encoding = UTF-8 Unicode
@@
 \definecolor{fillColor}{RGB}{255,255,255}
-\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (505.89,216.81);
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
+\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (361.35,144.54);
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
 \definecolor{drawColor}{RGB}{255,255,255}
@@
 
-\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (505.89,216.81);
-\end{scope}
-\begin{scope}
-\path[clip] ( 33.14, 57.56) rectangle (186.23,198.75);
+\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (361.35,144.54);
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (138.05,126.48);
 \definecolor{fillColor}{gray}{0.92}
 
-\path[fill=fillColor] ( 33.14, 57.56) rectangle (186.23,198.75);
+\path[fill=fillColor] ( 33.14, 57.56) rectangle (138.05,126.48);
 \definecolor{drawColor}{RGB}{255,255,255}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14, 70.17) --
-	(186.23, 70.17);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14,101.68) --
-	(186.23,101.68);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14,133.19) --
-	(186.23,133.19);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14,164.70) --
-	(186.23,164.70);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14,196.21) --
-	(186.23,196.21);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] ( 42.89, 57.56) --
-	( 42.89,198.75);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] ( 81.85, 57.56) --
-	( 81.85,198.75);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (120.82, 57.56) --
-	(120.82,198.75);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (159.78, 57.56) --
-	(159.78,198.75);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] ( 33.14, 85.92) --
-	(186.23, 85.92);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] ( 33.14,117.43) --
-	(186.23,117.43);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] ( 33.14,148.95) --
-	(186.23,148.95);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] ( 33.14,180.46) --
-	(186.23,180.46);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] ( 62.37, 57.56) --
-	( 62.37,198.75);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (101.34, 57.56) --
-	(101.34,198.75);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (140.30, 57.56) --
-	(140.30,198.75);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (179.27, 57.56) --
-	(179.27,198.75);
+\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14, 63.71) --
+	(138.05, 63.71);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14, 79.10) --
+	(138.05, 79.10);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14, 94.48) --
+	(138.05, 94.48);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14,109.86) --
+	(138.05,109.86);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14,125.24) --
+	(138.05,125.24);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] ( 39.82, 57.56) --
+	( 39.82,126.48);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] ( 66.52, 57.56) --
+	( 66.52,126.48);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] ( 93.22, 57.56) --
+	( 93.22,126.48);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (119.93, 57.56) --
+	(119.93,126.48);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] ( 33.14, 71.41) --
+	(138.05, 71.41);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] ( 33.14, 86.79) --
+	(138.05, 86.79);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] ( 33.14,102.17) --
+	(138.05,102.17);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] ( 33.14,117.55) --
+	(138.05,117.55);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] ( 53.17, 57.56) --
+	( 53.17,126.48);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] ( 79.87, 57.56) --
+	( 79.87,126.48);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (106.58, 57.56) --
+	(106.58,126.48);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (133.28, 57.56) --
+	(133.28,126.48);
 \definecolor{drawColor}{RGB}{27,158,119}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 40.10,106.36) --
-	( 45.67,106.36) --
-	( 51.24,106.36) --
-	( 56.80,106.36) --
-	( 62.37,106.36) --
-	( 67.94,106.37) --
-	( 73.50,106.38) --
-	( 79.07,106.42) --
-	( 84.64,106.58) --
-	( 90.20,107.23) --
-	( 95.77,109.99) --
-	(101.34,117.90);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 37.91, 89.74) --
+	( 41.73, 84.24) --
+	( 45.54, 84.24) --
+	( 49.36, 84.34) --
+	( 53.17, 87.56) --
+	( 56.99,109.01);
 \definecolor{drawColor}{RGB}{117,112,179}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 40.10,123.48) --
-	( 45.67,112.22) --
-	( 51.24,112.22) --
-	( 56.80,112.42) --
-	( 62.37,119.02) --
-	( 67.94,162.96);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 37.91, 81.38) --
+	( 41.73, 81.38) --
+	( 45.54, 81.38) --
+	( 49.36, 81.38) --
+	( 53.17, 81.38) --
+	( 56.99, 81.38) --
+	( 60.80, 81.39) --
+	( 64.62, 81.41) --
+	( 68.43, 81.49) --
+	( 72.24, 81.81) --
+	( 76.06, 83.15) --
+	( 79.87, 87.02);
+\definecolor{fillColor}{RGB}{117,112,179}
+
+\path[fill=fillColor] ( 35.95, 79.42) --
+	( 39.87, 79.42) --
+	( 39.87, 83.35) --
+	( 35.95, 83.35) --
+	cycle;
+
+\path[fill=fillColor] ( 39.77, 79.42) --
+	( 43.69, 79.42) --
+	( 43.69, 83.35) --
+	( 39.77, 83.35) --
+	cycle;
+
+\path[fill=fillColor] ( 43.58, 79.42) --
+	( 47.50, 79.42) --
+	( 47.50, 83.35) --
+	( 43.58, 83.35) --
+	cycle;
+
+\path[fill=fillColor] ( 47.39, 79.42) --
+	( 51.32, 79.42) --
+	( 51.32, 83.35) --
+	( 47.39, 83.35) --
+	cycle;
+
+\path[fill=fillColor] ( 51.21, 79.42) --
+	( 55.13, 79.42) --
+	( 55.13, 83.35) --
+	( 51.21, 83.35) --
+	cycle;
+
+\path[fill=fillColor] ( 55.02, 79.42) --
+	( 58.95, 79.42) --
+	( 58.95, 83.35) --
+	( 55.02, 83.35) --
+	cycle;
+
+\path[fill=fillColor] ( 58.84, 79.43) --
+	( 62.76, 79.43) --
+	( 62.76, 83.35) --
+	( 58.84, 83.35) --
+	cycle;
+
+\path[fill=fillColor] ( 62.65, 79.45) --
+	( 66.58, 79.45) --
+	( 66.58, 83.37) --
+	( 62.65, 83.37) --
+	cycle;
+
+\path[fill=fillColor] ( 66.47, 79.53) --
+	( 70.39, 79.53) --
+	( 70.39, 83.45) --
+	( 66.47, 83.45) --
+	cycle;
+
+\path[fill=fillColor] ( 70.28, 79.84) --
+	( 74.21, 79.84) --
+	( 74.21, 83.77) --
+	( 70.28, 83.77) --
+	cycle;
+
+\path[fill=fillColor] ( 74.10, 81.19) --
+	( 78.02, 81.19) --
+	( 78.02, 85.11) --
+	( 74.10, 85.11) --
+	cycle;
+
+\path[fill=fillColor] ( 77.91, 85.05) --
+	( 81.84, 85.05) --
+	( 81.84, 88.98) --
+	( 77.91, 88.98) --
+	cycle;
 \definecolor{fillColor}{RGB}{27,158,119}
 
-\path[fill=fillColor] ( 40.10,106.36) circle (  1.96);
-
-\path[fill=fillColor] ( 45.67,106.36) circle (  1.96);
-
-\path[fill=fillColor] ( 51.24,106.36) circle (  1.96);
-
-\path[fill=fillColor] ( 56.80,106.36) circle (  1.96);
-
-\path[fill=fillColor] ( 62.37,106.36) circle (  1.96);
-
-\path[fill=fillColor] ( 67.94,106.37) circle (  1.96);
-
-\path[fill=fillColor] ( 73.50,106.38) circle (  1.96);
-
-\path[fill=fillColor] ( 79.07,106.42) circle (  1.96);
-
-\path[fill=fillColor] ( 84.64,106.58) circle (  1.96);
-
-\path[fill=fillColor] ( 90.20,107.23) circle (  1.96);
-
-\path[fill=fillColor] ( 95.77,109.99) circle (  1.96);
-
-\path[fill=fillColor] (101.34,117.90) circle (  1.96);
+\path[fill=fillColor] ( 37.91, 89.74) circle (  1.96);
+
+\path[fill=fillColor] ( 41.73, 84.24) circle (  1.96);
+
+\path[fill=fillColor] ( 45.54, 84.24) circle (  1.96);
+
+\path[fill=fillColor] ( 49.36, 84.34) circle (  1.96);
+
+\path[fill=fillColor] ( 53.17, 87.56) circle (  1.96);
+
+\path[fill=fillColor] ( 56.99,109.01) circle (  1.96);
+\definecolor{drawColor}{gray}{0.70}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 34.10, 57.56) -- ( 34.10, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 37.91, 57.56) -- ( 37.91, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.73, 57.56) -- ( 41.73, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 45.54, 57.56) -- ( 45.54, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 49.36, 57.56) -- ( 49.36, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 53.17, 57.56) -- ( 53.17, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 56.99, 57.56) -- ( 56.99, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 60.80, 57.56) -- ( 60.80, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 64.62, 57.56) -- ( 64.62, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 68.43, 57.56) -- ( 68.43, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 72.24, 57.56) -- ( 72.24, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 76.06, 57.56) -- ( 76.06, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 79.87, 57.56) -- ( 79.87, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 83.69, 57.56) -- ( 83.69, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 87.50, 57.56) -- ( 87.50, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 91.32, 57.56) -- ( 91.32, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 95.13, 57.56) -- ( 95.13, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 98.95, 57.56) -- ( 98.95, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (102.76, 57.56) -- (102.76, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (106.58, 57.56) -- (106.58, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (110.39, 57.56) -- (110.39, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (114.21, 57.56) -- (114.21, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (118.02, 57.56) -- (118.02, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (121.83, 57.56) -- (121.83, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (125.65, 57.56) -- (125.65, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (129.46, 57.56) -- (129.46, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (133.28, 57.56) -- (133.28, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (137.09, 57.56) -- (137.09, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 61.15) -- ( 38.84, 61.15);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 66.28) -- ( 38.84, 66.28);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 71.41) -- ( 38.84, 71.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 76.53) -- ( 38.84, 76.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 81.66) -- ( 38.84, 81.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 86.79) -- ( 38.84, 86.79);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 91.91) -- ( 38.84, 91.91);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 97.04) -- ( 38.84, 97.04);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,102.17) -- ( 38.84,102.17);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,107.30) -- ( 38.84,107.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,112.42) -- ( 38.84,112.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,117.55) -- ( 38.84,117.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,122.68) -- ( 38.84,122.68);
+\end{scope}
+\begin{scope}
+\path[clip] (142.55, 57.56) rectangle (247.45,126.48);
+\definecolor{fillColor}{gray}{0.92}
+
+\path[fill=fillColor] (142.55, 57.56) rectangle (247.45,126.48);
+\definecolor{drawColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (142.55, 63.71) --
+	(247.45, 63.71);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (142.55, 79.10) --
+	(247.45, 79.10);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (142.55, 94.48) --
+	(247.45, 94.48);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (142.55,109.86) --
+	(247.45,109.86);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (142.55,125.24) --
+	(247.45,125.24);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (149.22, 57.56) --
+	(149.22,126.48);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (175.92, 57.56) --
+	(175.92,126.48);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (202.63, 57.56) --
+	(202.63,126.48);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (229.33, 57.56) --
+	(229.33,126.48);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (142.55, 71.41) --
+	(247.45, 71.41);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (142.55, 86.79) --
+	(247.45, 86.79);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (142.55,102.17) --
+	(247.45,102.17);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (142.55,117.55) --
+	(247.45,117.55);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (162.57, 57.56) --
+	(162.57,126.48);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (189.28, 57.56) --
+	(189.28,126.48);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (215.98, 57.56) --
+	(215.98,126.48);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (242.68, 57.56) --
+	(242.68,126.48);
+\definecolor{drawColor}{RGB}{27,158,119}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (147.31, 84.74) --
+	(151.13, 84.06) --
+	(154.94, 83.93) --
+	(158.76, 83.97) --
+	(162.57, 84.20) --
+	(166.39, 84.27) --
+	(170.20, 84.38) --
+	(174.02, 86.20) --
+	(177.83, 93.38) --
+	(181.65,111.72);
+\definecolor{drawColor}{RGB}{217,95,2}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (147.31, 62.86) --
+	(151.13, 60.69) --
+	(154.94, 60.69) --
+	(158.76, 60.69);
+\definecolor{drawColor}{RGB}{117,112,179}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (147.31, 72.23) --
+	(151.13, 72.23) --
+	(154.94, 72.23) --
+	(158.76, 72.23) --
+	(162.57, 72.23) --
+	(166.39, 72.23) --
+	(170.20, 72.23) --
+	(174.02, 72.27) --
+	(177.83, 72.70) --
+	(181.65, 76.95) --
+	(185.46, 89.66) --
+	(189.28,106.37) --
+	(193.09,123.35);
+\definecolor{drawColor}{RGB}{231,41,138}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (147.31, 72.11) --
+	(151.13, 72.11) --
+	(154.94, 72.11) --
+	(158.76, 72.11) --
+	(162.57, 72.11) --
+	(166.39, 72.11) --
+	(170.20, 72.11) --
+	(174.02, 72.15) --
+	(177.83, 72.59) --
+	(181.65, 76.89) --
+	(185.46, 89.67) --
+	(189.28,106.37) --
+	(193.09,123.35);
+\definecolor{fillColor}{RGB}{27,158,119}
+
+\path[fill=fillColor] (147.31, 84.74) circle (  1.96);
+
+\path[fill=fillColor] (151.13, 84.06) circle (  1.96);
+
+\path[fill=fillColor] (154.94, 83.93) circle (  1.96);
+
+\path[fill=fillColor] (158.76, 83.97) circle (  1.96);
+
+\path[fill=fillColor] (162.57, 84.20) circle (  1.96);
+
+\path[fill=fillColor] (166.39, 84.27) circle (  1.96);
+
+\path[fill=fillColor] (170.20, 84.38) circle (  1.96);
+
+\path[fill=fillColor] (174.02, 86.20) circle (  1.96);
+
+\path[fill=fillColor] (177.83, 93.38) circle (  1.96);
+
+\path[fill=fillColor] (181.65,111.72) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (144.54, 72.11) -- (150.09, 72.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (147.31, 69.34) -- (147.31, 74.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.35, 72.11) -- (153.90, 72.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.13, 69.33) -- (151.13, 74.88);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.17, 72.11) -- (157.72, 72.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (154.94, 69.33) -- (154.94, 74.88);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.98, 72.11) -- (161.53, 72.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.76, 69.33) -- (158.76, 74.88);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.80, 72.11) -- (165.35, 72.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.57, 69.33) -- (162.57, 74.88);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.61, 72.11) -- (169.16, 72.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (166.39, 69.33) -- (166.39, 74.88);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.43, 72.11) -- (172.98, 72.11);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.20, 69.34) -- (170.20, 74.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.24, 72.15) -- (176.79, 72.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.02, 69.37) -- (174.02, 74.92);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.06, 72.59) -- (180.61, 72.59);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.83, 69.81) -- (177.83, 75.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.87, 76.89) -- (184.42, 76.89);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.65, 74.12) -- (181.65, 79.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.69, 89.67) -- (188.24, 89.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.46, 86.90) -- (185.46, 92.45);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.50,106.37) -- (192.05,106.37);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.28,103.59) -- (189.28,109.14);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.32,123.35) -- (195.86,123.35);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.09,120.57) -- (193.09,126.12);
+\definecolor{fillColor}{RGB}{217,95,2}
+
+\path[fill=fillColor] (147.31, 65.91) --
+	(149.96, 61.33) --
+	(144.67, 61.33) --
+	cycle;
+
+\path[fill=fillColor] (151.13, 63.74) --
+	(153.77, 59.17) --
+	(148.49, 59.17) --
+	cycle;
+
+\path[fill=fillColor] (154.94, 63.74) --
+	(157.59, 59.17) --
+	(152.30, 59.17) --
+	cycle;
+
+\path[fill=fillColor] (158.76, 63.74) --
+	(161.40, 59.17) --
+	(156.12, 59.17) --
+	cycle;
 \definecolor{fillColor}{RGB}{117,112,179}
 
-\path[fill=fillColor] ( 38.14,121.52) --
-	( 42.06,121.52) --
-	( 42.06,125.44) --
-	( 38.14,125.44) --
-	cycle;
-
-\path[fill=fillColor] ( 43.71,110.26) --
-	( 47.63,110.26) --
-	( 47.63,114.18) --
-	( 43.71,114.18) --
-	cycle;
-
-\path[fill=fillColor] ( 49.27,110.26) --
-	( 53.20,110.26) --
-	( 53.20,114.18) --
-	( 49.27,114.18) --
-	cycle;
-
-\path[fill=fillColor] ( 54.84,110.46) --
-	( 58.76,110.46) --
-	( 58.76,114.38) --
-	( 54.84,114.38) --
-	cycle;
-
-\path[fill=fillColor] ( 60.41,117.06) --
-	( 64.33,117.06) --
-	( 64.33,120.99) --
-	( 60.41,120.99) --
-	cycle;
-
-\path[fill=fillColor] ( 65.97,161.00) --
-	( 69.90,161.00) --
-	( 69.90,164.92) --
-	( 65.97,164.92) --
+\path[fill=fillColor] (145.35, 70.27) --
+	(149.28, 70.27) --
+	(149.28, 74.20) --
+	(145.35, 74.20) --
+	cycle;
+
+\path[fill=fillColor] (149.17, 70.27) --
+	(153.09, 70.27) --
+	(153.09, 74.19) --
+	(149.17, 74.19) --
+	cycle;
+
+\path[fill=fillColor] (152.98, 70.27) --
+	(156.91, 70.27) --
+	(156.91, 74.19) --
+	(152.98, 74.19) --
+	cycle;
+
+\path[fill=fillColor] (156.80, 70.27) --
+	(160.72, 70.27) --
+	(160.72, 74.19) --
+	(156.80, 74.19) --
+	cycle;
+
+\path[fill=fillColor] (160.61, 70.27) --
+	(164.54, 70.27) --
+	(164.54, 74.19) --
+	(160.61, 74.19) --
+	cycle;
+
+\path[fill=fillColor] (164.43, 70.27) --
+	(168.35, 70.27) --
+	(168.35, 74.19) --
+	(164.43, 74.19) --
+	cycle;
+
+\path[fill=fillColor] (168.24, 70.27) --
+	(172.16, 70.27) --
+	(172.16, 74.20) --
+	(168.24, 74.20) --
+	cycle;
+
+\path[fill=fillColor] (172.05, 70.31) --
+	(175.98, 70.31) --
+	(175.98, 74.23) --
+	(172.05, 74.23) --
+	cycle;
+
+\path[fill=fillColor] (175.87, 70.74) --
+	(179.79, 70.74) --
+	(179.79, 74.66) --
+	(175.87, 74.66) --
+	cycle;
+
+\path[fill=fillColor] (179.68, 74.99) --
+	(183.61, 74.99) --
+	(183.61, 78.91) --
+	(179.68, 78.91) --
+	cycle;
+
+\path[fill=fillColor] (183.50, 87.70) --
+	(187.42, 87.70) --
+	(187.42, 91.62) --
+	(183.50, 91.62) --
+	cycle;
+
+\path[fill=fillColor] (187.31,104.41) --
+	(191.24,104.41) --
+	(191.24,108.33) --
+	(187.31,108.33) --
+	cycle;
+
+\path[fill=fillColor] (191.13,121.39) --
+	(195.05,121.39) --
+	(195.05,125.31) --
+	(191.13,125.31) --
 	cycle;
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 34.54, 57.56) -- ( 34.54, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 40.10, 57.56) -- ( 40.10, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 45.67, 57.56) -- ( 45.67, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 51.24, 57.56) -- ( 51.24, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 56.80, 57.56) -- ( 56.80, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 62.37, 57.56) -- ( 62.37, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 67.94, 57.56) -- ( 67.94, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 73.50, 57.56) -- ( 73.50, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 79.07, 57.56) -- ( 79.07, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 84.64, 57.56) -- ( 84.64, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 90.20, 57.56) -- ( 90.20, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 95.77, 57.56) -- ( 95.77, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (101.34, 57.56) -- (101.34, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (106.90, 57.56) -- (106.90, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (112.47, 57.56) -- (112.47, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (118.04, 57.56) -- (118.04, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (123.60, 57.56) -- (123.60, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (129.17, 57.56) -- (129.17, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (134.74, 57.56) -- (134.74, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (140.30, 57.56) -- (140.30, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (145.87, 57.56) -- (145.87, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (151.44, 57.56) -- (151.44, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (157.00, 57.56) -- (157.00, 63.25);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (143.50, 57.56) -- (143.50, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (147.31, 57.56) -- (147.31, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (151.13, 57.56) -- (151.13, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (154.94, 57.56) -- (154.94, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (158.76, 57.56) -- (158.76, 63.25);
 
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (168.13, 57.56) -- (168.13, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (173.70, 57.56) -- (173.70, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (179.27, 57.56) -- (179.27, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (184.83, 57.56) -- (184.83, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 64.92) -- ( 38.84, 64.92);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 75.42) -- ( 38.84, 75.42);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 85.92) -- ( 38.84, 85.92);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 96.43) -- ( 38.84, 96.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,106.93) -- ( 38.84,106.93);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,117.43) -- ( 38.84,117.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,127.94) -- ( 38.84,127.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,138.44) -- ( 38.84,138.44);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,148.95) -- ( 38.84,148.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,159.45) -- ( 38.84,159.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,169.95) -- ( 38.84,169.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,180.46) -- ( 38.84,180.46);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,190.96) -- ( 38.84,190.96);
-\end{scope}
-\begin{scope}
-\path[clip] (190.73, 57.56) rectangle (343.81,198.75);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (166.39, 57.56) -- (166.39, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (170.20, 57.56) -- (170.20, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (174.02, 57.56) -- (174.02, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (177.83, 57.56) -- (177.83, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (181.65, 57.56) -- (181.65, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (185.46, 57.56) -- (185.46, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (189.28, 57.56) -- (189.28, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (193.09, 57.56) -- (193.09, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (196.90, 57.56) -- (196.90, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (200.72, 57.56) -- (200.72, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (204.53, 57.56) -- (204.53, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (208.35, 57.56) -- (208.35, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (212.16, 57.56) -- (212.16, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (215.98, 57.56) -- (215.98, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (219.79, 57.56) -- (219.79, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (223.61, 57.56) -- (223.61, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (227.42, 57.56) -- (227.42, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (231.24, 57.56) -- (231.24, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (235.05, 57.56) -- (235.05, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (238.87, 57.56) -- (238.87, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (242.68, 57.56) -- (242.68, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (246.49, 57.56) -- (246.49, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (142.55, 61.15) -- (148.24, 61.15);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (142.55, 66.28) -- (148.24, 66.28);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (142.55, 71.41) -- (148.24, 71.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (142.55, 76.53) -- (148.24, 76.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (142.55, 81.66) -- (148.24, 81.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (142.55, 86.79) -- (148.24, 86.79);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (142.55, 91.91) -- (148.24, 91.91);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (142.55, 97.04) -- (148.24, 97.04);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (142.55,102.17) -- (148.24,102.17);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (142.55,107.30) -- (148.24,107.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (142.55,112.42) -- (148.24,112.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (142.55,117.55) -- (148.24,117.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (142.55,122.68) -- (148.24,122.68);
+\end{scope}
+\begin{scope}
+\path[clip] (251.95, 57.56) rectangle (356.85,126.48);
 \definecolor{fillColor}{gray}{0.92}
 
-\path[fill=fillColor] (190.73, 57.56) rectangle (343.81,198.75);
+\path[fill=fillColor] (251.95, 57.56) rectangle (356.85,126.48);
 \definecolor{drawColor}{RGB}{255,255,255}
 
-\path[draw=drawColor,line width= 0.2pt,line join=round] (190.73, 70.17) --
-	(343.81, 70.17);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (190.73,101.68) --
-	(343.81,101.68);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (190.73,133.19) --
-	(343.81,133.19);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (190.73,164.70) --
-	(343.81,164.70);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (190.73,196.21) --
-	(343.81,196.21);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (200.47, 57.56) --
-	(200.47,198.75);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (239.43, 57.56) --
-	(239.43,198.75);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (278.40, 57.56) --
-	(278.40,198.75);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (317.37, 57.56) --
-	(317.37,198.75);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (190.73, 85.92) --
-	(343.81, 85.92);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (190.73,117.43) --
-	(343.81,117.43);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (190.73,148.95) --
-	(343.81,148.95);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (190.73,180.46) --
-	(343.81,180.46);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (219.95, 57.56) --
-	(219.95,198.75);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (258.92, 57.56) --
-	(258.92,198.75);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (297.88, 57.56) --
-	(297.88,198.75);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (336.85, 57.56) --
-	(336.85,198.75);
+\path[draw=drawColor,line width= 0.2pt,line join=round] (251.95, 63.71) --
+	(356.85, 63.71);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (251.95, 79.10) --
+	(356.85, 79.10);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (251.95, 94.48) --
+	(356.85, 94.48);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (251.95,109.86) --
+	(356.85,109.86);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (251.95,125.24) --
+	(356.85,125.24);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (258.62, 57.56) --
+	(258.62,126.48);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (285.33, 57.56) --
+	(285.33,126.48);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (312.03, 57.56) --
+	(312.03,126.48);
+
+\path[draw=drawColor,line width= 0.2pt,line join=round] (338.73, 57.56) --
+	(338.73,126.48);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (251.95, 71.41) --
+	(356.85, 71.41);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (251.95, 86.79) --
+	(356.85, 86.79);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (251.95,102.17) --
+	(356.85,102.17);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (251.95,117.55) --
+	(356.85,117.55);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (271.97, 57.56) --
+	(271.97,126.48);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (298.68, 57.56) --
+	(298.68,126.48);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (325.38, 57.56) --
+	(325.38,126.48);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (352.08, 57.56) --
+	(352.08,126.48);
 \definecolor{drawColor}{RGB}{27,158,119}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (197.68, 87.62) --
-	(203.25, 87.61) --
-	(208.82, 87.61) --
-	(214.38, 87.61) --
-	(219.95, 87.61) --
-	(225.52, 87.61) --
-	(231.08, 87.62) --
-	(236.65, 87.69) --
-	(242.22, 88.58) --
-	(247.78, 97.29) --
-	(253.35,123.32) --
-	(258.92,157.55) --
-	(264.48,192.33);
+\path[draw=drawColor,line width= 0.6pt,line join=round] (256.72, 85.43) --
+	(260.53, 83.72) --
+	(264.35, 83.89) --
+	(268.16, 83.69) --
+	(271.97, 85.93) --
+	(275.79,108.62);
 \definecolor{drawColor}{RGB}{217,95,2}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (197.68, 87.37) --
-	(203.25, 87.36) --
-	(208.82, 87.36) --
-	(214.38, 87.36) --
-	(219.95, 87.36) --
-	(225.52, 87.36) --
-	(231.08, 87.37) --
-	(236.65, 87.44) --
-	(242.22, 88.34) --
-	(247.78, 97.16) --
-	(253.35,123.35) --
-	(258.92,157.54) --
-	(264.48,192.33);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (256.72, 61.86) --
+	(260.53, 61.00) --
+	(264.35, 61.00) --
+	(268.16, 61.00) --
+	(271.97, 61.00) --
+	(275.79, 61.15) --
+	(279.60, 61.15);
 \definecolor{drawColor}{RGB}{117,112,179}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (197.68,113.24) --
-	(203.25,111.85) --
-	(208.82,111.59) --
-	(214.38,111.66) --
-	(219.95,112.12) --
-	(225.52,112.27) --
-	(231.08,112.50) --
-	(236.65,116.23) --
-	(242.22,130.94) --
-	(247.78,168.51);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (256.72, 73.16) --
+	(260.53, 73.16) --
+	(264.35, 73.16) --
+	(268.16, 73.16) --
+	(271.97, 73.16) --
+	(275.79, 73.16) --
+	(279.60, 73.16) --
+	(283.42, 73.16) --
+	(287.23, 73.16) --
+	(291.05, 73.16) --
+	(294.86, 73.16) --
+	(298.68, 73.16) --
+	(302.49, 73.17) --
+	(306.31, 73.17) --
+	(310.12, 73.20) --
+	(313.94, 73.25) --
+	(317.75, 73.38) --
+	(321.56, 73.71) --
+	(325.38, 74.42) --
+	(329.19, 76.07) --
+	(333.01, 78.80) --
+	(336.82, 82.57) --
+	(340.64, 87.78) --
+	(344.45, 94.24) --
+	(348.27,100.04) --
+	(352.08,106.25);
 \definecolor{drawColor}{RGB}{231,41,138}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (197.68, 68.42) --
-	(203.25, 63.98) --
-	(208.82, 63.98) --
-	(214.38, 63.98);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (256.72, 72.63) --
+	(260.53, 72.63) --
+	(264.35, 72.63) --
+	(268.16, 72.63) --
+	(271.97, 72.63) --
+	(275.79, 72.63) --
+	(279.60, 72.63) --
+	(283.42, 72.63) --
+	(287.23, 72.63) --
+	(291.05, 72.63) --
+	(294.86, 72.63) --
+	(298.68, 72.63) --
+	(302.49, 72.64) --
+	(306.31, 72.64) --
+	(310.12, 72.67) --
+	(313.94, 72.73) --
+	(317.75, 72.87) --
+	(321.56, 73.21) --
+	(325.38, 73.96) --
+	(329.19, 75.58) --
+	(333.01, 78.49) --
+	(336.82, 82.32) --
+	(340.64, 87.62) --
+	(344.45, 94.08) --
+	(348.27, 99.98) --
+	(352.08,106.31);
 \definecolor{fillColor}{RGB}{117,112,179}
 
-\path[fill=fillColor] (195.72,111.28) --
-	(199.65,111.28) --
-	(199.65,115.20) --
-	(195.72,115.20) --
-	cycle;
-
-\path[fill=fillColor] (201.29,109.89) --
-	(205.21,109.89) --
-	(205.21,113.82) --
-	(201.29,113.82) --
-	cycle;
-
-\path[fill=fillColor] (206.86,109.63) --
-	(210.78,109.63) --
-	(210.78,113.55) --
-	(206.86,113.55) --
-	cycle;
-
-\path[fill=fillColor] (212.42,109.70) --
-	(216.35,109.70) --
-	(216.35,113.62) --
-	(212.42,113.62) --
-	cycle;
-
-\path[fill=fillColor] (217.99,110.16) --
-	(221.91,110.16) --
-	(221.91,114.09) --
-	(217.99,114.09) --
-	cycle;
-
-\path[fill=fillColor] (223.56,110.31) --
-	(227.48,110.31) --
-	(227.48,114.23) --
-	(223.56,114.23) --
-	cycle;
-
-\path[fill=fillColor] (229.12,110.53) --
-	(233.05,110.53) --
-	(233.05,114.46) --
-	(229.12,114.46) --
-	cycle;
-
-\path[fill=fillColor] (234.69,114.27) --
-	(238.61,114.27) --
-	(238.61,118.20) --
-	(234.69,118.20) --
-	cycle;
-
-\path[fill=fillColor] (240.26,128.97) --
-	(244.18,128.97) --
-	(244.18,132.90) --
-	(240.26,132.90) --
-	cycle;
-
-\path[fill=fillColor] (245.82,166.55) --
-	(249.75,166.55) --
-	(249.75,170.47) --
-	(245.82,170.47) --
+\path[fill=fillColor] (254.75, 71.20) --
+	(258.68, 71.20) --
+	(258.68, 75.12) --
+	(254.75, 75.12) --
+	cycle;
+
+\path[fill=fillColor] (258.57, 71.20) --
+	(262.49, 71.20) --
+	(262.49, 75.12) --
+	(258.57, 75.12) --
+	cycle;
+
+\path[fill=fillColor] (262.38, 71.20) --
+	(266.31, 71.20) --
+	(266.31, 75.12) --
+	(262.38, 75.12) --
+	cycle;
+
+\path[fill=fillColor] (266.20, 71.20) --
+	(270.12, 71.20) --
+	(270.12, 75.12) --
+	(266.20, 75.12) --
+	cycle;
+
+\path[fill=fillColor] (270.01, 71.20) --
+	(273.94, 71.20) --
+	(273.94, 75.12) --
+	(270.01, 75.12) --
+	cycle;
+
+\path[fill=fillColor] (273.83, 71.20) --
+	(277.75, 71.20) --
+	(277.75, 75.12) --
+	(273.83, 75.12) --
+	cycle;
+
+\path[fill=fillColor] (277.64, 71.20) --
+	(281.57, 71.20) --
+	(281.57, 75.12) --
+	(277.64, 75.12) --
+	cycle;
+
+\path[fill=fillColor] (281.46, 71.20) --
+	(285.38, 71.20) --
+	(285.38, 75.12) --
+	(281.46, 75.12) --
+	cycle;
+
+\path[fill=fillColor] (285.27, 71.20) --
+	(289.20, 71.20) --
+	(289.20, 75.12) --
+	(285.27, 75.12) --
+	cycle;
+
+\path[fill=fillColor] (289.09, 71.20) --
+	(293.01, 71.20) --
+	(293.01, 75.12) --
+	(289.09, 75.12) --
+	cycle;
+
+\path[fill=fillColor] (292.90, 71.20) --
+	(296.82, 71.20) --
+	(296.82, 75.12) --
+	(292.90, 75.12) --
+	cycle;
+
+\path[fill=fillColor] (296.72, 71.20) --
+	(300.64, 71.20) --
+	(300.64, 75.12) --
+	(296.72, 75.12) --
+	cycle;
+
+\path[fill=fillColor] (300.53, 71.21) --
+	(304.45, 71.21) --
+	(304.45, 75.13) --
+	(300.53, 75.13) --
+	cycle;
+
+\path[fill=fillColor] (304.34, 71.21) --
+	(308.27, 71.21) --
+	(308.27, 75.14) --
+	(304.34, 75.14) --
+	cycle;
+
+\path[fill=fillColor] (308.16, 71.24) --
+	(312.08, 71.24) --
+	(312.08, 75.16) --
+	(308.16, 75.16) --
+	cycle;
+
+\path[fill=fillColor] (311.97, 71.29) --
+	(315.90, 71.29) --
+	(315.90, 75.22) --
+	(311.97, 75.22) --
+	cycle;
+
+\path[fill=fillColor] (315.79, 71.42) --
+	(319.71, 71.42) --
+	(319.71, 75.35) --
+	(315.79, 75.35) --
+	cycle;
+
+\path[fill=fillColor] (319.60, 71.75) --
+	(323.53, 71.75) --
+	(323.53, 75.67) --
+	(319.60, 75.67) --
+	cycle;
+
+\path[fill=fillColor] (323.42, 72.46) --
+	(327.34, 72.46) --
+	(327.34, 76.39) --
+	(323.42, 76.39) --
+	cycle;
+
+\path[fill=fillColor] (327.23, 74.10) --
+	(331.16, 74.10) --
+	(331.16, 78.03) --
+	(327.23, 78.03) --
+	cycle;
+
+\path[fill=fillColor] (331.05, 76.84) --
+	(334.97, 76.84) --
+	(334.97, 80.76) --
+	(331.05, 80.76) --
+	cycle;
+
+\path[fill=fillColor] (334.86, 80.61) --
+	(338.79, 80.61) --
+	(338.79, 84.53) --
+	(334.86, 84.53) --
+	cycle;
+
+\path[fill=fillColor] (338.68, 85.82) --
+	(342.60, 85.82) --
+	(342.60, 89.74) --
+	(338.68, 89.74) --
+	cycle;
+
+\path[fill=fillColor] (342.49, 92.28) --
+	(346.41, 92.28) --
+	(346.41, 96.20) --
+	(342.49, 96.20) --
+	cycle;
+
+\path[fill=fillColor] (346.30, 98.07) --
+	(350.23, 98.07) --
+	(350.23,102.00) --
+	(346.30,102.00) --
+	cycle;
+
+\path[fill=fillColor] (350.12,104.29) --
+	(354.04,104.29) --
+	(354.04,108.21) --
+	(350.12,108.21) --
 	cycle;
@@
 
-\path[fill=fillColor] (197.68, 90.42) --
-	(200.33, 85.84) --
-	(195.04, 85.84) --
-	cycle;
-
-\path[fill=fillColor] (203.25, 90.41) --
-	(205.89, 85.84) --
-	(200.61, 85.84) --
-	cycle;
-
-\path[fill=fillColor] (208.82, 90.41) --
-	(211.46, 85.84) --
-	(206.18, 85.84) --
-	cycle;
-
-\path[fill=fillColor] (214.38, 90.41) --
-	(217.03, 85.84) --
-	(211.74, 85.84) --
-	cycle;
-
-\path[fill=fillColor] (219.95, 90.41) --
-	(222.59, 85.84) --
-	(217.31, 85.84) --
-	cycle;
-
-\path[fill=fillColor] (225.52, 90.41) --
-	(228.16, 85.84) --
-	(222.88, 85.84) --
-	cycle;
-
-\path[fill=fillColor] (231.08, 90.42) --
-	(233.73, 85.84) --
-	(228.44, 85.84) --
-	cycle;
-
-\path[fill=fillColor] (236.65, 90.49) --
-	(239.29, 85.92) --
-	(234.01, 85.92) --
-	cycle;
-
-\path[fill=fillColor] (242.22, 91.39) --
-	(244.86, 86.82) --
-	(239.57, 86.82) --
-	cycle;
-
-\path[fill=fillColor] (247.78,100.21) --
-	(250.43, 95.64) --
-	(245.14, 95.64) --
-	cycle;
-
-\path[fill=fillColor] (253.35,126.40) --
-	(255.99,121.82) --
-	(250.71,121.82) --
-	cycle;
-
-\path[fill=fillColor] (258.92,160.59) --
-	(261.56,156.02) --
-	(256.27,156.02) --
-	cycle;
-
-\path[fill=fillColor] (264.48,195.39) --
-	(267.13,190.81) --
-	(261.84,190.81) --
-	cycle;
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.91, 68.42) -- (200.46, 68.42);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.68, 65.64) -- (197.68, 71.19);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (200.48, 63.98) -- (206.03, 63.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.25, 61.20) -- (203.25, 66.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.04, 63.98) -- (211.59, 63.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.82, 61.20) -- (208.82, 66.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.61, 63.98) -- (217.16, 63.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (214.38, 61.20) -- (214.38, 66.75);
+\path[fill=fillColor] (256.72, 64.91) --
+	(259.36, 60.33) --
+	(254.07, 60.33) --
+	cycle;
+
+\path[fill=fillColor] (260.53, 64.05) --
+	(263.17, 59.48) --
+	(257.89, 59.48) --
+	cycle;
+
+\path[fill=fillColor] (264.35, 64.05) --
+	(266.99, 59.48) --
+	(261.70, 59.48) --
+	cycle;
+
+\path[fill=fillColor] (268.16, 64.05) --
+	(270.80, 59.48) --
+	(265.52, 59.48) --
+	cycle;
+
+\path[fill=fillColor] (271.97, 64.05) --
+	(274.62, 59.48) --
+	(269.33, 59.48) --
+	cycle;
+
+\path[fill=fillColor] (275.79, 64.20) --
+	(278.43, 59.63) --
+	(273.15, 59.63) --
+	cycle;
+
+\path[fill=fillColor] (279.60, 64.20) --
+	(282.25, 59.63) --
+	(276.96, 59.63) --
+	cycle;
 \definecolor{fillColor}{RGB}{27,158,119}
 
-\path[fill=fillColor] (197.68, 87.62) circle (  1.96);
-
-\path[fill=fillColor] (203.25, 87.61) circle (  1.96);
-
-\path[fill=fillColor] (208.82, 87.61) circle (  1.96);
-
-\path[fill=fillColor] (214.38, 87.61) circle (  1.96);
-
-\path[fill=fillColor] (219.95, 87.61) circle (  1.96);
-
-\path[fill=fillColor] (225.52, 87.61) circle (  1.96);
-
-\path[fill=fillColor] (231.08, 87.62) circle (  1.96);
-
-\path[fill=fillColor] (236.65, 87.69) circle (  1.96);
-
-\path[fill=fillColor] (242.22, 88.58) circle (  1.96);
-
-\path[fill=fillColor] (247.78, 97.29) circle (  1.96);
-
-\path[fill=fillColor] (253.35,123.32) circle (  1.96);
-
-\path[fill=fillColor] (258.92,157.55) circle (  1.96);
-
-\path[fill=fillColor] (264.48,192.33) circle (  1.96);
+\path[fill=fillColor] (256.72, 85.43) circle (  1.96);
+
+\path[fill=fillColor] (260.53, 83.72) circle (  1.96);
+
+\path[fill=fillColor] (264.35, 83.89) circle (  1.96);
+
+\path[fill=fillColor] (268.16, 83.69) circle (  1.96);
+
+\path[fill=fillColor] (271.97, 85.93) circle (  1.96);
+
+\path[fill=fillColor] (275.79,108.62) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (253.94, 72.63) -- (259.49, 72.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (256.72, 69.85) -- (256.72, 75.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.76, 72.63) -- (263.31, 72.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (260.53, 69.85) -- (260.53, 75.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.57, 72.63) -- (267.12, 72.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.35, 69.85) -- (264.35, 75.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (265.39, 72.63) -- (270.94, 72.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (268.16, 69.85) -- (268.16, 75.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (269.20, 72.63) -- (274.75, 72.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.97, 69.85) -- (271.97, 75.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.01, 72.63) -- (278.56, 72.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.79, 69.85) -- (275.79, 75.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (276.83, 72.63) -- (282.38, 72.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (279.60, 69.86) -- (279.60, 75.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (280.64, 72.63) -- (286.19, 72.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.42, 69.85) -- (283.42, 75.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (284.46, 72.63) -- (290.01, 72.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (287.23, 69.85) -- (287.23, 75.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (288.27, 72.63) -- (293.82, 72.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (291.05, 69.86) -- (291.05, 75.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.09, 72.63) -- (297.64, 72.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (294.86, 69.86) -- (294.86, 75.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (295.90, 72.63) -- (301.45, 72.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.68, 69.86) -- (298.68, 75.40);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (299.72, 72.64) -- (305.27, 72.64);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.49, 69.86) -- (302.49, 75.41);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (303.53, 72.64) -- (309.08, 72.64);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (306.31, 69.87) -- (306.31, 75.42);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (307.35, 72.67) -- (312.90, 72.67);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (310.12, 69.90) -- (310.12, 75.45);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (311.16, 72.73) -- (316.71, 72.73);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (313.94, 69.95) -- (313.94, 75.50);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (314.98, 72.87) -- (320.53, 72.87);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (317.75, 70.09) -- (317.75, 75.64);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (318.79, 73.21) -- (324.34, 73.21);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (321.56, 70.44) -- (321.56, 75.99);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (322.60, 73.96) -- (328.15, 73.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (325.38, 71.19) -- (325.38, 76.74);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (326.42, 75.58) -- (331.97, 75.58);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (329.19, 72.81) -- (329.19, 78.36);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (330.23, 78.49) -- (335.78, 78.49);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.01, 75.72) -- (333.01, 81.27);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.05, 82.32) -- (339.60, 82.32);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (336.82, 79.55) -- (336.82, 85.10);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (337.86, 87.62) -- (343.41, 87.62);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (340.64, 84.84) -- (340.64, 90.39);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (341.68, 94.08) -- (347.23, 94.08);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (344.45, 91.31) -- (344.45, 96.86);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (345.49, 99.98) -- (351.04, 99.98);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (348.27, 97.20) -- (348.27,102.75);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (349.31,106.31) -- (354.86,106.31);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (352.08,103.54) -- (352.08,109.09);
 \definecolor{drawColor}{gray}{0.70}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (192.12, 57.56) -- (192.12, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (197.68, 57.56) -- (197.68, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (203.25, 57.56) -- (203.25, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (208.82, 57.56) -- (208.82, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (214.38, 57.56) -- (214.38, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (219.95, 57.56) -- (219.95, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (225.52, 57.56) -- (225.52, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (231.08, 57.56) -- (231.08, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (236.65, 57.56) -- (236.65, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (242.22, 57.56) -- (242.22, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (247.78, 57.56) -- (247.78, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (253.35, 57.56) -- (253.35, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (258.92, 57.56) -- (258.92, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (264.48, 57.56) -- (264.48, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (270.05, 57.56) -- (270.05, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (275.62, 57.56) -- (275.62, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (281.18, 57.56) -- (281.18, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.75, 57.56) -- (286.75, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (292.32, 57.56) -- (292.32, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (297.88, 57.56) -- (297.88, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (303.45, 57.56) -- (303.45, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (309.02, 57.56) -- (309.02, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (314.58, 57.56) -- (314.58, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (320.15, 57.56) -- (320.15, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (325.72, 57.56) -- (325.72, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (331.28, 57.56) -- (331.28, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (336.85, 57.56) -- (336.85, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (342.42, 57.56) -- (342.42, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73, 64.92) -- (196.42, 64.92);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73, 75.42) -- (196.42, 75.42);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73, 85.92) -- (196.42, 85.92);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73, 96.43) -- (196.42, 96.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73,106.93) -- (196.42,106.93);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73,117.43) -- (196.42,117.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73,127.94) -- (196.42,127.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73,138.44) -- (196.42,138.44);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73,148.95) -- (196.42,148.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73,159.45) -- (196.42,159.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73,169.95) -- (196.42,169.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73,180.46) -- (196.42,180.46);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.73,190.96) -- (196.42,190.96);
-\end{scope}
-\begin{scope}
-\path[clip] (348.31, 57.56) rectangle (501.39,198.75);
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (252.90, 57.56) -- (252.90, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (256.72, 57.56) -- (256.72, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (260.53, 57.56) -- (260.53, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (264.35, 57.56) -- (264.35, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (268.16, 57.56) -- (268.16, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (271.97, 57.56) -- (271.97, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (275.79, 57.56) -- (275.79, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (279.60, 57.56) -- (279.60, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (283.42, 57.56) -- (283.42, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (287.23, 57.56) -- (287.23, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (291.05, 57.56) -- (291.05, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (294.86, 57.56) -- (294.86, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (298.68, 57.56) -- (298.68, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (302.49, 57.56) -- (302.49, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (306.31, 57.56) -- (306.31, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (310.12, 57.56) -- (310.12, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (313.94, 57.56) -- (313.94, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (317.75, 57.56) -- (317.75, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (321.56, 57.56) -- (321.56, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (325.38, 57.56) -- (325.38, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (329.19, 57.56) -- (329.19, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (333.01, 57.56) -- (333.01, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (336.82, 57.56) -- (336.82, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (340.64, 57.56) -- (340.64, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (344.45, 57.56) -- (344.45, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.27, 57.56) -- (348.27, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (352.08, 57.56) -- (352.08, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (355.90, 57.56) -- (355.90, 63.25);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (251.95, 61.15) -- (257.64, 61.15);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (251.95, 66.28) -- (257.64, 66.28);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (251.95, 71.41) -- (257.64, 71.41);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (251.95, 76.53) -- (257.64, 76.53);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (251.95, 81.66) -- (257.64, 81.66);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (251.95, 86.79) -- (257.64, 86.79);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (251.95, 91.91) -- (257.64, 91.91);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (251.95, 97.04) -- (257.64, 97.04);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (251.95,102.17) -- (257.64,102.17);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (251.95,107.30) -- (257.64,107.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (251.95,112.42) -- (257.64,112.42);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (251.95,117.55) -- (257.64,117.55);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (251.95,122.68) -- (257.64,122.68);
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14,126.48) rectangle (138.05,140.04);
+\definecolor{fillColor}{gray}{0.85}
+
+\path[fill=fillColor] ( 33.14,126.48) rectangle (138.05,140.04);
+\definecolor{drawColor}{gray}{0.10}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 85.60,130.78) {Bijections};
+\end{scope}
+\begin{scope}
+\path[clip] (142.55,126.48) rectangle (247.45,140.04);
+\definecolor{fillColor}{gray}{0.85}
+
+\path[fill=fillColor] (142.55,126.48) rectangle (247.45,140.04);
+\definecolor{drawColor}{gray}{0.10}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (195.00,130.78) {Friends};
+\end{scope}
+\begin{scope}
+\path[clip] (251.95,126.48) rectangle (356.85,140.04);
+\definecolor{fillColor}{gray}{0.85}
+
+\path[fill=fillColor] (251.95,126.48) rectangle (356.85,140.04);
+\definecolor{drawColor}{gray}{0.10}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (304.40,130.78) {Functions};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] ( 53.17, 55.31) --
+	( 53.17, 57.56);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] ( 79.87, 55.31) --
+	( 79.87, 57.56);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (106.58, 55.31) --
+	(106.58, 57.56);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (133.28, 55.31) --
+	(133.28, 57.56);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
+\definecolor{drawColor}{gray}{0.30}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 53.17, 48.55) {$2^{5}$};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 79.87, 48.55) {$2^{12}$};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (106.58, 48.55) {$2^{19}$};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (133.28, 48.55) {$2^{26}$};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (162.57, 55.31) --
+	(162.57, 57.56);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (189.28, 55.31) --
+	(189.28, 57.56);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (215.98, 55.31) --
+	(215.98, 57.56);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (242.68, 55.31) --
+	(242.68, 57.56);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
+\definecolor{drawColor}{gray}{0.30}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (162.57, 48.55) {$2^{5}$};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (189.28, 48.55) {$2^{12}$};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (215.98, 48.55) {$2^{19}$};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (242.68, 48.55) {$2^{26}$};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (271.97, 55.31) --
+	(271.97, 57.56);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (298.68, 55.31) --
+	(298.68, 57.56);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (325.38, 55.31) --
+	(325.38, 57.56);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] (352.08, 55.31) --
+	(352.08, 57.56);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
+\definecolor{drawColor}{gray}{0.30}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (271.97, 48.55) {$2^{5}$};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (298.68, 48.55) {$2^{12}$};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (325.38, 48.55) {$2^{19}$};
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (352.08, 48.55) {$2^{26}$};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
+\definecolor{drawColor}{gray}{0.30}
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 29.09, 68.93) {2};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 29.09, 84.31) {16};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 29.09, 99.69) {128};
+
+\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 29.09,115.07) {1024};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] ( 30.89, 71.41) --
+	( 33.14, 71.41);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] ( 30.89, 86.79) --
+	( 33.14, 86.79);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] ( 30.89,102.17) --
+	( 33.14,102.17);
+
+\path[draw=drawColor,line width= 0.5pt,line join=round] ( 30.89,117.55) --
+	( 33.14,117.55);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (195.00, 38.70) {Domain size};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
+\definecolor{drawColor}{RGB}{0,0,0}
+
+\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 10.70, 92.02) {Total runtime (s)};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[fill=fillColor] ( 51.80,  4.50) rectangle (338.20, 27.95);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
 \definecolor{fillColor}{gray}{0.92}
 
-\path[fill=fillColor] (348.31, 57.56) rectangle (501.39,198.75);
-\definecolor{drawColor}{RGB}{255,255,255}
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (348.31, 70.17) --
-	(501.39, 70.17);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (348.31,101.68) --
-	(501.39,101.68);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (348.31,133.19) --
-	(501.39,133.19);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (348.31,164.70) --
-	(501.39,164.70);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (348.31,196.21) --
-	(501.39,196.21);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (358.05, 57.56) --
-	(358.05,198.75);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (397.02, 57.56) --
-	(397.02,198.75);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (435.98, 57.56) --
-	(435.98,198.75);
-
-\path[draw=drawColor,line width= 0.2pt,line join=round] (474.95, 57.56) --
-	(474.95,198.75);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (348.31, 85.92) --
-	(501.39, 85.92);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (348.31,117.43) --
-	(501.39,117.43);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (348.31,148.95) --
-	(501.39,148.95);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (348.31,180.46) --
-	(501.39,180.46);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (377.53, 57.56) --
-	(377.53,198.75);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (416.50, 57.56) --
-	(416.50,198.75);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (455.47, 57.56) --
-	(455.47,198.75);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (494.43, 57.56) --
-	(494.43,198.75);
+\path[fill=fillColor] ( 60.80,  9.00) rectangle ( 75.25, 23.45);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
 \definecolor{drawColor}{RGB}{27,158,119}
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (355.27, 89.52) --
-	(360.83, 89.52) --
-	(366.40, 89.52) --
-	(371.97, 89.52) --
-	(377.53, 89.52) --
-	(383.10, 89.52) --
-	(388.67, 89.52) --
-	(394.23, 89.52) --
-	(399.80, 89.52) --
-	(405.37, 89.52) --
-	(410.93, 89.52) --
-	(416.50, 89.52) --
-	(422.07, 89.53) --
-	(427.63, 89.55) --
-	(433.20, 89.61) --
-	(438.77, 89.71) --
-	(444.33, 89.97) --
-	(449.90, 90.65) --
-	(455.47, 92.11) --
-	(461.03, 95.47) --
-	(466.60,101.07) --
-	(472.17,108.80) --
-	(477.73,119.46) --
-	(483.30,132.70) --
-	(488.87,144.57) --
-	(494.43,157.31);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.24, 16.23) -- ( 73.81, 16.23);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
+\definecolor{fillColor}{RGB}{27,158,119}
+
+\path[fill=fillColor] ( 68.02, 16.23) circle (  1.96);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
+\definecolor{fillColor}{gray}{0.92}
+
+\path[fill=fillColor] (132.24,  9.00) rectangle (146.69, 23.45);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
 \definecolor{drawColor}{RGB}{217,95,2}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (355.27, 88.43) --
-	(360.83, 88.43) --
-	(366.40, 88.43) --
-	(371.97, 88.43) --
-	(377.53, 88.43) --
-	(383.10, 88.43) --
-	(388.67, 88.43) --
-	(394.23, 88.43) --
-	(399.80, 88.43) --
-	(405.37, 88.43) --
-	(410.93, 88.43) --
-	(416.50, 88.43) --
-	(422.07, 88.44) --
-	(427.63, 88.46) --
-	(433.20, 88.51) --
-	(438.77, 88.64) --
-	(444.33, 88.92) --
-	(449.90, 89.63) --
-	(455.47, 91.16) --
-	(461.03, 94.48) --
-	(466.60,100.45) --
-	(472.17,108.29) --
-	(477.73,119.14) --
-	(483.30,132.38) --
-	(488.87,144.46) --
-	(494.43,157.43);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (133.68, 16.23) -- (145.25, 16.23);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
+\definecolor{fillColor}{RGB}{217,95,2}
+
+\path[fill=fillColor] (139.46, 19.28) --
+	(142.11, 14.70) --
+	(136.82, 14.70) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
+\definecolor{fillColor}{gray}{0.92}
+
+\path[fill=fillColor] (188.77,  9.00) rectangle (203.22, 23.45);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
 \definecolor{drawColor}{RGB}{117,112,179}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (355.27,114.65) --
-	(360.83,111.15) --
-	(366.40,111.49) --
-	(371.97,111.10) --
-	(377.53,115.68) --
-	(383.10,162.17);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (190.22, 16.23) -- (201.78, 16.23);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
+\definecolor{fillColor}{RGB}{117,112,179}
+
+\path[fill=fillColor] (194.03, 14.26) --
+	(197.96, 14.26) --
+	(197.96, 18.19) --
+	(194.03, 18.19) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
+\definecolor{fillColor}{gray}{0.92}
+
+\path[fill=fillColor] (257.35,  9.00) rectangle (271.81, 23.45);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
 \definecolor{drawColor}{RGB}{231,41,138}
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (355.27, 66.36) --
-	(360.83, 64.61) --
-	(366.40, 64.61) --
-	(371.97, 64.61) --
-	(377.53, 64.61) --
-	(383.10, 64.92) --
-	(388.67, 64.92);
-\definecolor{fillColor}{RGB}{27,158,119}
-
-\path[fill=fillColor] (355.27, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (360.83, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (366.40, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (371.97, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (377.53, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (383.10, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (388.67, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (394.23, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (399.80, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (405.37, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (410.93, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (416.50, 89.52) circle (  1.96);
-
-\path[fill=fillColor] (422.07, 89.53) circle (  1.96);
-
-\path[fill=fillColor] (427.63, 89.55) circle (  1.96);
-
-\path[fill=fillColor] (433.20, 89.61) circle (  1.96);
-
-\path[fill=fillColor] (438.77, 89.71) circle (  1.96);
-
-\path[fill=fillColor] (444.33, 89.97) circle (  1.96);
-
-\path[fill=fillColor] (449.90, 90.65) circle (  1.96);
-
-\path[fill=fillColor] (455.47, 92.11) circle (  1.96);
-
-\path[fill=fillColor] (461.03, 95.47) circle (  1.96);
-
-\path[fill=fillColor] (466.60,101.07) circle (  1.96);
-
-\path[fill=fillColor] (472.17,108.80) circle (  1.96);
-
-\path[fill=fillColor] (477.73,119.46) circle (  1.96);
-
-\path[fill=fillColor] (483.30,132.70) circle (  1.96);
-
-\path[fill=fillColor] (488.87,144.57) circle (  1.96);
-
-\path[fill=fillColor] (494.43,157.31) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (352.49, 66.36) -- (358.04, 66.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (355.27, 63.59) -- (355.27, 69.14);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (358.06, 64.61) -- (363.61, 64.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (360.83, 61.83) -- (360.83, 67.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (363.62, 64.61) -- (369.17, 64.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (366.40, 61.83) -- (366.40, 67.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (369.19, 64.61) -- (374.74, 64.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (371.97, 61.83) -- (371.97, 67.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.76, 64.61) -- (380.31, 64.61);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (377.53, 61.83) -- (377.53, 67.38);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (380.32, 64.92) -- (385.87, 64.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (383.10, 62.14) -- (383.10, 67.69);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (385.89, 64.92) -- (391.44, 64.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (388.67, 62.14) -- (388.67, 67.69);
-\definecolor{fillColor}{RGB}{117,112,179}
-
-\path[fill=fillColor] (353.30,112.68) --
-	(357.23,112.68) --
-	(357.23,116.61) --
-	(353.30,116.61) --
-	cycle;
-
-\path[fill=fillColor] (358.87,109.19) --
-	(362.80,109.19) --
-	(362.80,113.11) --
-	(358.87,113.11) --
-	cycle;
-
-\path[fill=fillColor] (364.44,109.53) --
-	(368.36,109.53) --
-	(368.36,113.45) --
-	(364.44,113.45) --
-	cycle;
-
-\path[fill=fillColor] (370.00,109.13) --
-	(373.93,109.13) --
-	(373.93,113.06) --
-	(370.00,113.06) --
-	cycle;
-
-\path[fill=fillColor] (375.57,113.72) --
-	(379.50,113.72) --
-	(379.50,117.64) --
-	(375.57,117.64) --
-	cycle;
-
-\path[fill=fillColor] (381.14,160.21) --
-	(385.06,160.21) --
-	(385.06,164.13) --
-	(381.14,164.13) --
-	cycle;
-\definecolor{fillColor}{RGB}{217,95,2}
-
-\path[fill=fillColor] (355.27, 91.48) --
-	(357.91, 86.90) --
-	(352.62, 86.90) --
-	cycle;
-
-\path[fill=fillColor] (360.83, 91.48) --
-	(363.48, 86.90) --
-	(358.19, 86.90) --
-	cycle;
-
-\path[fill=fillColor] (366.40, 91.48) --
-	(369.04, 86.90) --
-	(363.76, 86.90) --
-	cycle;
-
-\path[fill=fillColor] (371.97, 91.48) --
-	(374.61, 86.90) --
-	(369.32, 86.90) --
-	cycle;
-
-\path[fill=fillColor] (377.53, 91.48) --
-	(380.18, 86.90) --
-	(374.89, 86.90) --
-	cycle;
-
-\path[fill=fillColor] (383.10, 91.48) --
-	(385.74, 86.90) --
-	(380.46, 86.90) --
-	cycle;
-
-\path[fill=fillColor] (388.67, 91.48) --
-	(391.31, 86.91) --
-	(386.02, 86.91) --
-	cycle;
-
-\path[fill=fillColor] (394.23, 91.48) --
-	(396.88, 86.90) --
-	(391.59, 86.90) --
-	cycle;
-
-\path[fill=fillColor] (399.80, 91.48) --
-	(402.44, 86.90) --
-	(397.16, 86.90) --
-	cycle;
-
-\path[fill=fillColor] (405.37, 91.48) --
-	(408.01, 86.91) --
-	(402.72, 86.91) --
-	cycle;
-
-\path[fill=fillColor] (410.93, 91.48) --
-	(413.58, 86.91) --
-	(408.29, 86.91) --
-	cycle;
-
-\path[fill=fillColor] (416.50, 91.48) --
-	(419.14, 86.91) --
-	(413.86, 86.91) --
-	cycle;
-
-\path[fill=fillColor] (422.07, 91.50) --
-	(424.71, 86.92) --
-	(419.42, 86.92) --
-	cycle;
-
-\path[fill=fillColor] (427.63, 91.51) --
-	(430.27, 86.93) --
-	(424.99, 86.93) --
-	cycle;
-
-\path[fill=fillColor] (433.20, 91.57) --
-	(435.84, 86.99) --
-	(430.56, 86.99) --
-	cycle;
-
-\path[fill=fillColor] (438.77, 91.69) --
-	(441.41, 87.11) --
-	(436.12, 87.11) --
-	cycle;
-
-\path[fill=fillColor] (444.33, 91.97) --
-	(446.97, 87.39) --
-	(441.69, 87.39) --
-	cycle;
-
-\path[fill=fillColor] (449.90, 92.68) --
-	(452.54, 88.10) --
-	(447.26, 88.10) --
-	cycle;
-
-\path[fill=fillColor] (455.47, 94.21) --
-	(458.11, 89.64) --
-	(452.82, 89.64) --
-	cycle;
-
-\path[fill=fillColor] (461.03, 97.53) --
-	(463.67, 92.95) --
-	(458.39, 92.95) --
-	cycle;
-
-\path[fill=fillColor] (466.60,103.50) --
-	(469.24, 98.92) --
-	(463.96, 98.92) --
-	cycle;
-
-\path[fill=fillColor] (472.17,111.34) --
-	(474.81,106.76) --
-	(469.52,106.76) --
-	cycle;
-
-\path[fill=fillColor] (477.73,122.19) --
-	(480.37,117.61) --
-	(475.09,117.61) --
-	cycle;
-
-\path[fill=fillColor] (483.30,135.43) --
-	(485.94,130.86) --
-	(480.66,130.86) --
-	cycle;
-
-\path[fill=fillColor] (488.87,147.51) --
-	(491.51,142.93) --
-	(486.22,142.93) --
-	cycle;
-
-\path[fill=fillColor] (494.43,160.48) --
-	(497.07,155.91) --
-	(491.79,155.91) --
-	cycle;
-\definecolor{drawColor}{gray}{0.70}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (349.70, 57.56) -- (349.70, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (355.27, 57.56) -- (355.27, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (360.83, 57.56) -- (360.83, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (366.40, 57.56) -- (366.40, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (371.97, 57.56) -- (371.97, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (377.53, 57.56) -- (377.53, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (383.10, 57.56) -- (383.10, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (388.67, 57.56) -- (388.67, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (394.23, 57.56) -- (394.23, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (399.80, 57.56) -- (399.80, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (405.37, 57.56) -- (405.37, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (410.93, 57.56) -- (410.93, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (416.50, 57.56) -- (416.50, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (422.07, 57.56) -- (422.07, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (427.63, 57.56) -- (427.63, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (433.20, 57.56) -- (433.20, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (438.77, 57.56) -- (438.77, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (444.33, 57.56) -- (444.33, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (449.90, 57.56) -- (449.90, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (455.47, 57.56) -- (455.47, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (461.03, 57.56) -- (461.03, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (466.60, 57.56) -- (466.60, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (472.17, 57.56) -- (472.17, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (477.73, 57.56) -- (477.73, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (483.30, 57.56) -- (483.30, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (488.87, 57.56) -- (488.87, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (494.43, 57.56) -- (494.43, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (500.00, 57.56) -- (500.00, 63.25);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31, 64.92) -- (354.00, 64.92);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31, 75.42) -- (354.00, 75.42);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31, 85.92) -- (354.00, 85.92);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31, 96.43) -- (354.00, 96.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31,106.93) -- (354.00,106.93);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31,117.43) -- (354.00,117.43);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31,127.94) -- (354.00,127.94);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31,138.44) -- (354.00,138.44);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31,148.95) -- (354.00,148.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31,159.45) -- (354.00,159.45);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31,169.95) -- (354.00,169.95);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31,180.46) -- (354.00,180.46);
-
-\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (348.31,190.96) -- (354.00,190.96);
-\end{scope}
-\begin{scope}
-\path[clip] ( 33.14,198.75) rectangle (186.23,212.31);
-\definecolor{fillColor}{gray}{0.85}
-
-\path[fill=fillColor] ( 33.14,198.75) rectangle (186.23,212.31);
-\definecolor{drawColor}{gray}{0.10}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (109.69,203.05) {Bijections};
-\end{scope}
-\begin{scope}
-\path[clip] (190.73,198.75) rectangle (343.81,212.31);
-\definecolor{fillColor}{gray}{0.85}
-
-\path[fill=fillColor] (190.73,198.75) rectangle (343.81,212.31);
-\definecolor{drawColor}{gray}{0.10}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (267.27,203.05) {Friends};
-\end{scope}
-\begin{scope}
-\path[clip] (348.31,198.75) rectangle (501.39,212.31);
-\definecolor{fillColor}{gray}{0.85}
-
-\path[fill=fillColor] (348.31,198.75) rectangle (501.39,212.31);
-\definecolor{drawColor}{gray}{0.10}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (424.85,203.05) {Functions};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] ( 62.37, 55.31) --
-	( 62.37, 57.56);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (101.34, 55.31) --
-	(101.34, 57.56);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (140.30, 55.31) --
-	(140.30, 57.56);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (179.27, 55.31) --
-	(179.27, 57.56);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
-\definecolor{drawColor}{gray}{0.30}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 62.37, 48.55) {$2^{5}$};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (101.34, 48.55) {$2^{12}$};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (140.30, 48.55) {$2^{19}$};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (179.27, 48.55) {$2^{26}$};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (219.95, 55.31) --
-	(219.95, 57.56);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (258.92, 55.31) --
-	(258.92, 57.56);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (297.88, 55.31) --
-	(297.88, 57.56);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (336.85, 55.31) --
-	(336.85, 57.56);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
-\definecolor{drawColor}{gray}{0.30}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (219.95, 48.55) {$2^{5}$};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (258.92, 48.55) {$2^{12}$};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (297.88, 48.55) {$2^{19}$};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (336.85, 48.55) {$2^{26}$};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (377.53, 55.31) --
-	(377.53, 57.56);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (416.50, 55.31) --
-	(416.50, 57.56);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (455.47, 55.31) --
-	(455.47, 57.56);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] (494.43, 55.31) --
-	(494.43, 57.56);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
-\definecolor{drawColor}{gray}{0.30}
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (377.53, 48.55) {$2^{5}$};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (416.50, 48.55) {$2^{12}$};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (455.47, 48.55) {$2^{19}$};
-
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (494.43, 48.55) {$2^{26}$};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
-\definecolor{drawColor}{gray}{0.30}
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 29.09, 83.44) {2};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 29.09,114.96) {16};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 29.09,146.47) {128};
-
-\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 29.09,177.98) {1024};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
-\definecolor{drawColor}{gray}{0.20}
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] ( 30.89, 85.92) --
-	( 33.14, 85.92);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] ( 30.89,117.43) --
-	( 33.14,117.43);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] ( 30.89,148.95) --
-	( 33.14,148.95);
-
-\path[draw=drawColor,line width= 0.5pt,line join=round] ( 30.89,180.46) --
-	( 33.14,180.46);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (258.80, 16.23) -- (270.36, 16.23);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
+\definecolor{drawColor}{RGB}{231,41,138}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.81, 16.23) -- (267.35, 16.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.58, 13.45) -- (264.58, 19.00);
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (267.27, 38.70) {Domain size};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 79.75, 13.75) {\textsc{FastWFOMC}};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 10.70,128.16) {Total runtime (s)};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
-\definecolor{fillColor}{RGB}{255,255,255}
-
-\path[fill=fillColor] (124.58,  4.50) rectangle (409.95, 27.95);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
-\definecolor{fillColor}{gray}{0.92}
-
-\path[fill=fillColor] (133.58,  9.00) rectangle (148.04, 23.45);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
-\definecolor{drawColor}{RGB}{27,158,119}
-
-\path[draw=drawColor,line width= 0.6pt,line join=round] (135.03, 16.23) -- (146.59, 16.23);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
-\definecolor{fillColor}{RGB}{27,158,119}
-
-\path[fill=fillColor] (140.81, 16.23) circle (  1.96);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
-\definecolor{fillColor}{gray}{0.92}
-
-\path[fill=fillColor] (201.65,  9.00) rectangle (216.10, 23.45);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
-\definecolor{drawColor}{RGB}{217,95,2}
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (203.10, 16.23) -- (214.66, 16.23);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
-\definecolor{fillColor}{RGB}{217,95,2}
-
-\path[fill=fillColor] (208.88, 19.28) --
-	(211.52, 14.70) --
-	(206.24, 14.70) --
-	cycle;
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
-\definecolor{fillColor}{gray}{0.92}
-
-\path[fill=fillColor] (281.98,  9.00) rectangle (296.43, 23.45);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
-\definecolor{drawColor}{RGB}{117,112,179}
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (283.42, 16.23) -- (294.99, 16.23);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
-\definecolor{fillColor}{RGB}{117,112,179}
-
-\path[fill=fillColor] (287.24, 14.26) --
-	(291.17, 14.26) --
-	(291.17, 18.19) --
-	(287.24, 18.19) --
-	cycle;
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
-\definecolor{fillColor}{gray}{0.92}
-
-\path[fill=fillColor] (353.42,  9.00) rectangle (367.87, 23.45);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
-\definecolor{drawColor}{RGB}{231,41,138}
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (354.86, 16.23) -- (366.43, 16.23);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
-\definecolor{drawColor}{RGB}{231,41,138}
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (357.87, 16.23) -- (363.42, 16.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (360.65, 13.45) -- (360.65, 19.00);
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (151.19, 13.75) {\textsc{ForcLift}};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (152.54, 13.75) {\textsc{Crane2-BFS}};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (207.72, 13.75) {\textsc{Gantry-BFS}};
+\end{scope}
+\begin{scope}
+\path[clip] (  0.00,  0.00) rectangle (361.35,144.54);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (220.60, 13.75) {\textsc{Crane2-Greedy}};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (300.93, 13.75) {\textsc{FastWFOMC}};
-\end{scope}
-\begin{scope}
-\path[clip] (  0.00,  0.00) rectangle (505.89,216.81);
-\definecolor{drawColor}{RGB}{0,0,0}
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (372.37, 13.75) {\textsc{ForcLift}};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (276.31, 13.75) {\textsc{Gantry-Greedy}};
 \end{scope}

### 2025-01-24 analysis/analyse.R

@@ -3,9 +3,9 @@ library(scales)
 library(tikzDevice)
 library(ggpubr)
 
-# df <- read.csv("../results/processed/results_with_counts.csv")
-# df$count <- NULL
-# write.csv(df, "../results/processed/results.csv")
+df <- read.csv("../results/processed/results_with_counts.csv")
+df$count <- NULL
+write.csv(df, "../results/processed/results.csv")
 
 df <- read.csv("../results/processed/results.csv")
 df$compilation.time <- df$compilation.time / 1000
@@ -25,7 +25,7 @@ df <- df[df$domain.size > 1,]
 # differences <- df %>% group_by(sequence, domain.size) %>%
 #   summarise(diff = 100 * (max(count) - min(count)) / min(count))
 
-tikz(file = "../doc/paper/plot.tex", width = 7, height = 3,
+tikz(file = "../doc/paper/plot.tex", width = 5, height = 2,
      standAlone = TRUE)
 ggplot(df, aes(domain.size, time, color = algorithm, linetype = algorithm,
                shape = algorithm)) +

### 2025-01-25 doc/paper/paper.tex
Move the section about three logics to the appendix

@@
   \begin{itemize}
+    \item Perhaps I can list the `authors contributed equally' statement as part
+          of Funding. Check K's recent papers.
     \item Finish adding DOIs or URLs to (non-book) references (and reformatting
@@
 
-\subsection{The Three Logics of FOMC}\label{sec:threelogics}
-
-% \begin{table*}[t]
-%   \centering
-%   \begin{tabular}{llclll}
-%     \toprule
-%     Logic & Sorts & Constants & Variables & Quantifiers & Additional atoms\\
-%     \midrule
-%     \FO & one or more & \cmark & unlimited & $\forall$, $\exists$ & $x = y$\\
-%     \Ctwo & one & \xmark & two & $\forall$, $\exists$, $\exists^{= k}$, $\exists^{\le k}$, $\exists^{\ge k}$ & ---\\
-%     \UFO & one & \xmark & two & $\forall$ & $|P| = m$\\
-%     \bottomrule
-%   \end{tabular}
-%   \caption{A comparison of the three logics used in FOMC\@. The
-%     2\textsuperscript{nd}--5\textsuperscript{th} columns refer to: the number of
-%     sorts, support for constants, the maximum number of variables, and supported
-%     quantifiers, respectively. The last column lists supported atoms in addition
-%     to those of the form $P(\mathbf{t})$ for a predicate $P/n$ and an $n$-tuple
-%     of terms $\mathbf{t}$. Here: $k$ and $m$ are non-negative integers, with the
-%     latter depending on the domain size, $P$ represents a predicate, and $x$ and
-%     $y$ are terms. }\label{tbl:logics}
-% \end{table*}
-
-\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
-
-There are three first-order logics commonly used in FOMC: \FO{}, \Ctwo{}, and
-\UFO{}. First, \FO{} is the input format for
-\textsc{ForcLift}\footnote{\url{https://github.com/UCLA-StarAI/Forclift}} and
-its extensions
-\textsc{Crane}\footnote{\url{https://doi.org/10.5281/zenodo.8004077}} and
-\Cranetwo{}. Second, \Ctwo{} is often used in the literature on
-\textsc{FastWFOMC}\footnote{\url{https://github.com/jan-toth/FastWFOMC.jl}} and
-related methods~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}.
-Finally, \UFO{} is the input format supported by the most recent implementation
-of \textsc{FastWFOMC}~\cite{tóth2024complexityweightedfirstordermodel}. All
-three logics are function-free, and domains are always assumed to be finite. As
-usual, we presuppose the \emph{unique name assumption}, which states that two
-constants are equal if and only if they are the same
-constant~\cite{DBLP:books/aw/RN2020}.
-
-\renewcommand*{\thefootnote}{\arabic{footnote}}
-
-In \FO{}, each term is assigned to a \emph{sort}, and each predicate $P/n$ is
-assigned to a sequence of $n$ sorts. Each sort has its corresponding domain.
-These assignments to sorts are typically left implicit and can be reconstructed
-from the quantifiers. For example, $\forall x,y \in \Delta\text{. }P(x, y)$
-implies that variables $x$ and $y$ have the same sort. On the other hand,
-$\forall x \in \Delta\text{. }\forall y \in \Gamma\text{. } P(x, y)$ implies
-that $x$ and $y$ have different sorts, and it would be improper to write, for
-example, $\forall x \in \Delta\text{. }\forall y \in \Gamma\text{.
-} P(x, y) \lor x = y$. \FO{} is also the only logic to support constants,
-formulas with more than two variables, and the equality predicate. While we do
-not explicitly refer to sorts in subsequent sections of this paper, the
-many-sorted nature of \FO{} is paramount to the algorithms presented therein.
-
-\begin{remark*}
-  In the case of \textsc{ForcLift} and its extensions, support for a formula as
-  valid input does not imply that the algorithm can compile the formula into a
-  circuit or graph suitable for lifted model counting. However, it is known that
-  \textsc{ForcLift} compilation is guaranteed to succeed on any \FO{} formula
-  without constants and with at most two
-  variables~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/kr/BroeckMD14}.
-\end{remark*}
-
-Compared to \FO{}, \Ctwo{} and \UFO{} lack support for constants, the equality
-predicate, multiple domains, and formulas with more than two variables. The
-advantage that \Ctwo{} brings over \FO{} is the inclusion of \emph{counting
-  quantifiers}. That is, alongside $\forall$ and $\exists$, \Ctwo{} supports
-$\exists^{=k}$, $\exists^{\le k}$, and $\exists^{\ge k}$ for any positive
-integer $k$. For example, $\exists^{=1} x\text{. }\phi(x)$ means that there
-exists \emph{exactly one} $x$ such that $\phi(x)$, and $\exists^{\le 2} x\text{.
-}\phi(x)$ means that there exist \emph{at most two} such $x$. \UFO{}, on the
-other hand, does not support any existential quantifiers but instead
-incorporates \emph{(equality) cardinality constraints}. For example, $|P| = 3$
-constrains all models to have \emph{precisely three positive literals with the
-  predicate $P$}.
-
 \subsection{First-Order Model Counting}
@@
 
-\todo[inline]{Expand the section, adding a more thorough and independent
-  practical assessment}
-
 Our empirical evaluation sought to compare the runtime performance of
@@
   \begin{itemize}
-    \item More benchmarks from NOT my work
     \item Make sure it's clear what the `raw' instances are
@@
 
-\todo[inline]{Shrink/restructure to fit into the margins}
+\todo[inline]{Add lines of best fit (and comment on them) to expand this section
+  a bit?}
 
@@
 
+\appendix
+\section{The Three Logics of FOMC}\label{sec:threelogics}
+
+\begin{table}[t]
+  \centering
+  \begin{tabular}{llclll}
+    \toprule
+    Logic & Sorts & Constants & Variables & Quantifiers & Additional atoms\\
+    \midrule
+    \FO & one or more & \cmark & unlimited & $\forall$, $\exists$ & $x = y$\\
+    \Ctwo & one & \xmark & two & $\forall$, $\exists$, $\exists^{= k}$, $\exists^{\le k}$, $\exists^{\ge k}$ & ---\\
+    \UFO & one & \xmark & two & $\forall$ & $|P| = m$\\
+    \bottomrule
+  \end{tabular}
+  \caption{A comparison of the three logics used in FOMC\@. The
+    2\textsuperscript{nd}--5\textsuperscript{th} columns refer to: the number of
+    sorts, support for constants, the maximum number of variables, and supported
+    quantifiers, respectively. The last column lists supported atoms in addition
+    to those of the form $P(\mathbf{t})$ for a predicate $P/n$ and an $n$-tuple
+    of terms $\mathbf{t}$. Here: $k$ and $m$ are non-negative integers, with the
+    latter depending on the domain size, $P$ represents a predicate, and $x$ and
+    $y$ are terms. }\label{tbl:logics}
+\end{table}
+
+\todo[inline,caption={}]{
+  \begin{itemize}
+    \item Reference the table
+    \item Delete references to this appendix (except for one place, probably in
+          \cref{sec:experiments})
+    \item Make sure the rest of the paper doesn't refer to these logics (or
+          describe examples in them)
+  \end{itemize}
+}
+
+\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
+
+There are three first-order logics commonly used in FOMC: \FO{}, \Ctwo{}, and
+\UFO{}. First, \FO{} is the input format for
+\textsc{ForcLift}\footnote{\url{https://github.com/UCLA-StarAI/Forclift}} and
+its extensions
+\textsc{Crane}\footnote{\url{https://doi.org/10.5281/zenodo.8004077}} and
+\Cranetwo{}. Second, \Ctwo{} is often used in the literature on
+\textsc{FastWFOMC}\footnote{\url{https://github.com/jan-toth/FastWFOMC.jl}} and
+related methods~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}.
+Finally, \UFO{} is the input format supported by the most recent implementation
+of \textsc{FastWFOMC}~\cite{tóth2024complexityweightedfirstordermodel}. All
+three logics are function-free, and domains are always assumed to be finite. As
+usual, we presuppose the \emph{unique name assumption}, which states that two
+constants are equal if and only if they are the same
+constant~\cite{DBLP:books/aw/RN2020}.
+
+\renewcommand*{\thefootnote}{\arabic{footnote}}
+
+In \FO{}, each term is assigned to a \emph{sort}, and each predicate $P/n$ is
+assigned to a sequence of $n$ sorts. Each sort has its corresponding domain.
+These assignments to sorts are typically left implicit and can be reconstructed
+from the quantifiers. For example, $\forall x,y \in \Delta\text{. }P(x, y)$
+implies that variables $x$ and $y$ have the same sort. On the other hand,
+$\forall x \in \Delta\text{. }\forall y \in \Gamma\text{. } P(x, y)$ implies
+that $x$ and $y$ have different sorts, and it would be improper to write, for
+example, $\forall x \in \Delta\text{. }\forall y \in \Gamma\text{.
+} P(x, y) \lor x = y$. \FO{} is also the only logic to support constants,
+formulas with more than two variables, and the equality predicate. While we do
+not explicitly refer to sorts in subsequent sections of this paper, the
+many-sorted nature of \FO{} is paramount to the algorithms presented therein.
+
+\begin{remark*}
+  In the case of \textsc{ForcLift} and its extensions, support for a formula as
+  valid input does not imply that the algorithm can compile the formula into a
+  circuit or graph suitable for lifted model counting. However, it is known that
+  \textsc{ForcLift} compilation is guaranteed to succeed on any \FO{} formula
+  without constants and with at most two
+  variables~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/kr/BroeckMD14}.
+\end{remark*}
+
+Compared to \FO{}, \Ctwo{} and \UFO{} lack support for constants, the equality
+predicate, multiple domains, and formulas with more than two variables. The
+advantage that \Ctwo{} brings over \FO{} is the inclusion of \emph{counting
+  quantifiers}. That is, alongside $\forall$ and $\exists$, \Ctwo{} supports
+$\exists^{=k}$, $\exists^{\le k}$, and $\exists^{\ge k}$ for any positive
+integer $k$. For example, $\exists^{=1} x\text{. }\phi(x)$ means that there
+exists \emph{exactly one} $x$ such that $\phi(x)$, and $\exists^{\le 2} x\text{.
+}\phi(x)$ means that there exist \emph{at most two} such $x$. \UFO{}, on the
+other hand, does not support any existential quantifiers but instead
+incorporates \emph{(equality) cardinality constraints}. For example, $|P| = 3$
+constrains all models to have \emph{precisely three positive literals with the
+  predicate $P$}.
+
 \end{document}

### 2025-01-25 analysis/analyse.R

@@ -2,10 +2,11 @@ library(tidyverse)
 library(scales)
 library(tikzDevice)
 library(ggpubr)
+library(RColorBrewer)
 
-df <- read.csv("../results/processed/results_with_counts.csv")
-df$count <- NULL
-write.csv(df, "../results/processed/results.csv")
+#df <- read.csv("../results/processed/results_with_counts.csv")
+#df$count <- NULL
+#write.csv(df, "../results/processed/results.csv")
 
 df <- read.csv("../results/processed/results.csv")
 df$compilation.time <- df$compilation.time / 1000
@@ -19,6 +20,7 @@ df$sequence[df$sequence == "bijections"] <- "Bijections"
 df$sequence[df$sequence == "friends"] <- "Friends"
 df$sequence[df$sequence == "functions"] <- "Functions"
 df <- df[df$domain.size > 1,]
+dark2_colors <- brewer.pal(8, "Dark2")
 
 # Sanity check: differences between max and min counts as a percentage of the
 # min count
@@ -44,6 +46,65 @@ ggplot(df, aes(domain.size, time, color = algorithm, linetype = algorithm,
   theme(legend.position = "bottom") +
   scale_color_brewer(palette = "Dark2") +
   facet_wrap(vars(sequence))
+dev.off()
+
+tikz(file = "../../misc/talks-and-notes/monthly_talk/bijections.tex",
+     width = 4.25, height = 3, standAlone = TRUE)
+ggplot(df[df$sequence == "Bijections",],
+       aes(domain.size, time, color = algorithm, linetype = algorithm,
+           shape = algorithm)) +
+  geom_line() +
+  geom_point() +
+  scale_x_continuous(trans = log2_trans(), breaks = c(8, 64, 512, 4096),
+                     labels = c("$2^{3}$", "$2^{6}$", "$2^{9}$", "$2^{12}$")) +
+  scale_y_continuous(trans = log2_trans()) +
+  annotation_logticks(sides = "bl", colour = "#b3b3b3", base = 2) +
+  ylab("Total runtime (s)") +
+  xlab("Domain size") +
+  labs(color = "", linetype = "", shape = "") +
+  theme_grey(base_size = 9) +
+  theme(legend.position = "bottom") +
+  scale_color_manual(values = c(dark2_colors[1], dark2_colors[3])) +
+  scale_linetype_manual(values = c(1, 5)) +
+  scale_shape_manual(values = c(16, 15))
[…]

### 2025-01-25 doc/paper/paper.tex
Add DOIs/URLs to most references (as requested by the formatting instructions that all published papers seem to ignore)

@@
           of Funding. Check K's recent papers.
-    \item Finish adding DOIs or URLs to (non-book) references (and reformatting
-          indentation) (and check reference formatting) (is the part about
-          non-book references correct? Check previous proceedings) (maybe one
-          more exception (graded logics)?) (I might be done)
     \item Sentence vs formula: be consistent and not confusing
@@
     \item Go through the rest of formatting instructions (in GTD)
-    \item Make sure all the references (e.g., to examples are still valid)
+    \item Make sure all the internal references (e.g., to examples) are still
+          valid
     \item Maybe add extra references to subsections
@@
   partially addressed in previous
-  work~\cite{DBLP:conf/kr/DilkasB23,tóth2024complexityweightedfirstordermodel}
+  work~\cite{DBLP:conf/kr/DilkasB23,DBLP:conf/kr/TothK24}
   and are orthogonal to the goals of this section.} For the remainder of this
@@
 {\Cranetwo} with the current state of the art, namely \textsc{FastWFOMC} and
-\textsc{ForcLift}. It is worth remarking that \textsc{ForcLift} does not support
-arbitrary precision, and returns error for cases that requires arbitrary
-precision reasoning. Our experiments involve two versions of \Cranetwo{}:
+\textsc{ForcLift}. Our experiments involve two versions of \Cranetwo{}:
 \Cranegreedy{} and \Cranebfs{}. Like its predecessor, \Cranetwo{} has two modes
@@
 
+We compare these algorithms using three benchmarks from previous studies. The
+first benchmark is the function-counting problem from \cref{example:functions},
+previously examined by Dilkas and Belle~\cite{DBLP:conf/kr/DilkasB23}. The
+second benchmark is a variant of the well-known `Friends and Smokers' (hitherto
+referred to as `friends') Markov logic
+network~\cite{DBLP:conf/aaai/SinglaD08,DBLP:conf/uai/BroeckCD12}. In \Ctwo{},
+\FO{}, and \UFO{}, this problem can be formulated as
+\[
+  (\forall x,y \in \Delta\text{. } S(x) \land F(x, y) \Rightarrow S(y)) \land (\forall x \in \Delta\text{. }S(x) \Rightarrow C(x))
+\]
+or, equivalently, in conjunctive normal form as
+\[
+  (\forall x,y \in \Delta\text{. }S(y) \lor \neg S(x) \lor \neg F(x, y)) \land (\forall x \in \Delta\text{. } C(x) \lor \neg S(x)).
+\]
+Finally, we include the bijection-counting problem previously utilised by Dilkas
+and Belle~\cite{DBLP:conf/kr/DilkasB23}. Its formulation in \FO{} is described
+in \cref{example:bijections}.
+
 \begin{example}[Counting functions]\label{example:functions}
   To define predicate $P$ as a function from a domain $\Delta$ to itself, in
-  \Ctwo{} one would write $\forall x \in \Delta\text{.
-  }\exists^{=1} y \in \Delta\text{. }P(x, y)$. In \UFO{}, the same could be
-  written as
-  \begin{equation}\label[formula]{eq:functions1}
-    (\forall x, y \in \Delta\text{. }S(x) \lor \neg P(x, y)) \land (|P| = |\Delta|),
-  \end{equation}
-  where $w^{-}(S) = -1$. Although \cref{eq:functions1} has more models compared
-  to its counterpart in \Ctwo{}, the negative weight $w^{-}(S) = -1$ makes some
-  of the terms in \cref{eq:wfomc} cancel out.
-
-  Equivalently, in \FO{} we would write
+  \FO{} we would write
   \begin{equation}\label[formula]{eq:fo}
@@
 
-We compare these algorithms using three benchmarks from previous studies. The
-first benchmark is the function-counting problem from \cref{example:functions},
-previously examined by Dilkas and Belle~\cite{DBLP:conf/kr/DilkasB23}. The
-second benchmark is a variant of the well-known `Friends and Smokers' Markov
-logic network~\cite{DBLP:conf/aaai/SinglaD08,DBLP:conf/uai/BroeckCD12}. In
-\Ctwo{}, \FO{}, and \UFO{}, this problem can be formulated as
-\[
-  (\forall x,y \in \Delta\text{. } S(x) \land F(x, y) \Rightarrow S(y)) \land (\forall x \in \Delta\text{. }S(x) \Rightarrow C(x))
-\]
-or, equivalently, in conjunctive normal form as
-\[
-  (\forall x,y \in \Delta\text{. }S(y) \lor \neg S(x) \lor \neg F(x, y)) \land (\forall x \in \Delta\text{. } C(x) \lor \neg S(x)).
-\]
-Finally, we include the bijection-counting problem previously utilised by Dilkas
-and Belle~\cite{DBLP:conf/kr/DilkasB23}. Its formulation in \FO{} is described
-in \cref{example:bijections}. The equivalent formula in \Ctwo{} is
-\[
-  (\forall x \in \Delta\text{. }\exists^{=1} y \in \Delta\text{. }P(x, y)) \land (\forall y \in \Delta\text{. }\exists^{=1} x \in \Delta\text{. }P(x, y)).
-\]
-Similarly, in \UFO{} the same formula can be written as
-\[
-  (\forall x, y \in \Delta\text{. }R(x) \lor \neg P(x, y)) \land (\forall x, y \in \Delta\text{. }S(x) \lor \neg P(y, x)) \land (|P| = |\Delta|),
-\]
-where $w^{-}(R) = w^{-}(S) = -1$.
-
 \begin{figure*}[t]
@@
 
-\todo[inline]{Add lines of best fit (and comment on them) to expand this section
-  a bit?}
+\todo[inline]{For each curve, check which polynomial or exponential model best
+  fits the data to expand this section a bit (without plotting them, but
+  describing the method).}
 
@@
 }
+
+\todo[inline]{Incorporate into the text below: It is worth remarking that
+  \textsc{ForcLift} does not support arbitrary precision, and returns error for
+  cases that requires arbitrary precision reasoning. }
 
@@
           describe examples in them)
+    \item Move the URLs to the main text
+    \item Later (probably) move this to a different file
   \end{itemize}
@@
 Finally, \UFO{} is the input format supported by the most recent implementation
-of \textsc{FastWFOMC}~\cite{tóth2024complexityweightedfirstordermodel}. All
-three logics are function-free, and domains are always assumed to be finite. As
-usual, we presuppose the \emph{unique name assumption}, which states that two
-constants are equal if and only if they are the same
-constant~\cite{DBLP:books/aw/RN2020}.
+of \textsc{FastWFOMC}~\cite{DBLP:conf/kr/TothK24}. All three logics are
+function-free, and domains are always assumed to be finite. As usual, we
+presuppose the \emph{unique name assumption}, which states that two constants
+are equal if and only if they are the same constant~\cite{DBLP:books/aw/RN2020}.
 
@@
 
+\subsection{Our Benchmarks in \Ctwo{} and \UFO{}}
+
+\todo[inline,caption={}]{
+  \begin{itemize}
+    \item An introductory paragraph
+    \item Figure out the right order in which the information below should be
+          presented
+    \item Make the text below coherent
+    \item Refer to it in the main text (and make sure the reference sticks when
+          I transfer this to a separate file)
+  \end{itemize}
+}
+
+`Friends' in \Ctwo{} and \UFO{} is the same as in \FO{}.
+
+For `bijections', the equivalent formula in \Ctwo{} is
+\[
+  (\forall x \in \Delta\text{. }\exists^{=1} y \in \Delta\text{.
+  }P(x, y)) \land (\forall y \in \Delta\text{. }\exists^{=1} x \in \Delta\text{.
+  }P(x, y)).
+\]
+Similarly, in \UFO{} the same formula can be written as
+\[
+  (\forall x, y \in \Delta\text{.
+  }R(x) \lor \neg P(x, y)) \land (\forall x, y \in \Delta\text{.
+  }S(x) \lor \neg P(y, x)) \land (|P| = |\Delta|),
+\]
+where $w^{-}(R) = w^{-}(S) = -1$.
+
+For `functions', in \Ctwo{} one would write $\forall x \in \Delta\text{.
+}\exists^{=1} y \in \Delta\text{. }P(x, y)$. In \UFO{}, the same could be
+written as
+\begin{equation}\label[formula]{eq:functions1}
+  (\forall x, y \in \Delta\text{. }S(x) \lor \neg P(x, y)) \land (|P| = |\Delta|),
+\end{equation}
+where $w^{-}(S) = -1$. Although \cref{eq:functions1} has more models compared to
+its counterpart in \Ctwo{}, the negative weight $w^{-}(S) = -1$ makes some of
+the terms in \cref{eq:wfomc} cancel out.
+
 \end{document}

### 2025-01-31 doc/paper/paper.tex
Funding

@@
 
-\author{Ananth K. Kidambi}{Indian Institute of Technology Bombay, Mumbai, India}{210051002@iitb.ac.in}{}{TODO: funding}
-\author{Guramrit Singh}{Indian Institute of Technology Bombay, Mumbai, India}{guramrit@iitb.ac.in}{}{TODO: funding}
-\author{Paulius Dilkas}{University of Toronto, Toronto, Canada \and Vector Institute, Toronto, Canada \and \url{https://dilkas.github.io/}}{paulius.dilkas@utoronto.ca}{https://orcid.org/0000-0001-9185-7840}{TODO: funding}
-\author{Kuldeep S. Meel}{University of Toronto, Toronto, Canada \and \url{https://www.cs.toronto.edu/~meel/}}{meel@cs.toronto.edu}{https://orcid.org/0000-0001-9423-5270}{TODO: funding}
+\author{Ananth K. Kidambi}{Indian Institute of Technology Bombay, Mumbai, India}{210051002@iitb.ac.in}{}{}
+\author{Guramrit Singh}{Indian Institute of Technology Bombay, Mumbai, India}{guramrit@iitb.ac.in}{}{}
+\author{Paulius Dilkas}{University of Toronto, Toronto, Canada \and Vector Institute, Toronto, Canada \and \url{https://dilkas.github.io/}}{paulius.dilkas@utoronto.ca}{https://orcid.org/0000-0001-9185-7840}{}
+\author{Kuldeep S. Meel}{University of Toronto, Toronto, Canada \and \url{https://www.cs.toronto.edu/~meel/}}{meel@cs.toronto.edu}{https://orcid.org/0000-0001-9423-5270}{}
 
@@
 
-%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors.
-Please enter author specific funding statements as fifth argument of the \author macro.
-
-\acknowledgements{Part of the research was conducted while all authors were at the National University of Singapore.}
+\funding{This research was funded in part by the Natural Sciences and
+  Engineering Research Council of Canada (NSERC), funding reference number
+  RGPIN-2024-05956, and the Digital Research Alliance of Canada
+  (\texttt{\href{https://alliancecan.ca/}{alliancecan.ca}}).}
+
+\acknowledgements{The first two authors contributed equally. Part of the
+  research was conducted while all authors were at the National University of
+  Singapore.}
 
@@
   \begin{itemize}
-    \item Perhaps I can list the `authors contributed equally' statement as part
-          of Funding. Check K's recent papers.
     \item Sentence vs formula: be consistent and not confusing
     \item 15 pages excluding references
-    \item Go through the rest of formatting instructions (in GTD)
     \item Make sure all the internal references (e.g., to examples) are still
@@
     \item Maybe add extra references to subsections
+    \item When submitting: go through the rest of formatting instructions (in
+          GTD)
   \end{itemize}

### 2025-01-31 analysis/analyse.R

@@ -95,8 +95,12 @@ ggplot(df[df$sequence == "Functions",],
            shape = algorithm)) +
   geom_line() +
   geom_point() +
-  scale_x_continuous(trans = log2_trans(), breaks = c(8, 64, 512, 4096),
-                     labels = c("$2^{3}$", "$2^{6}$", "$2^{9}$", "$2^{12}$")) +
+  scale_x_continuous(trans = log2_trans(),
+                     breaks = c(8, 64, 512, 4096, 32768, 262144, 2097152,
+                                16777216, 134217728),
+                     labels = c("$2^{3}$", "$2^{6}$", "$2^{9}$", "$2^{12}$",
+                                "$2^{15}$", "$2^{18}$", "$2^{21}$", "$2^{24}$",
+                                "$2^{27}$")) +
   scale_y_continuous(trans = log2_trans()) +
   annotation_logticks(sides = "bl", colour = "#b3b3b3", base = 2) +
   ylab("Total runtime (s)") +

### 2025-02-02 doc/paper/paper.tex
Section 4.1

@@
 \newcommand{\Cranegreedy}{\textsc{Gantry-Greedy}}
+\newcommand{\friends}{\emph{Friends \& Smokers}}
+\newcommand{\functions}{\emph{Functions}}
+\newcommand{\bijections}{\emph{Bijections}}
 
@@
 
+\todo[inline]{Reformulate the theorem above into an upper bound (as I informally
+  mention earlier in the text)}
+
 To prove the theorem, we rely on two observations about the algorithms presented
@@
 \textsc{ForcLift}. Our experiments involve two versions of \Cranetwo{}:
-\Cranegreedy{} and \Cranebfs{}. Like its predecessor, \Cranetwo{} has two modes
-for applying compilation rules to formulas: one that uses a greedy search
-algorithm similar to \textsc{ForcLift} and another that combines greedy and
-BFS\@.
+\Cranegreedy{} and \Cranebfs{}. Like its predecessor (see
+\cref{sec:compilation}), \Cranetwo{} has two modes for applying compilation
+rules to formulas: one that uses a greedy search algorithm similar to
+\textsc{ForcLift} and another that combines greedy and BFS\@.
 
@@
 
+We ran each algorithm on each benchmark using domains of sizes
+$2^{1}, 2^{2}, 2^{3}$, and so on, until an algorithm failed to handle a domain
+size due to timeout (of \SI{1}{\hour}), out of memory error, or out of precision
+errors. While we separately measured compilation and inference time, we
+primarily focus on total runtime, dominated by the latter.
+
 \subsection{Benchmarks}
 
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item Make sure it's clear what the `raw' instances are
-    \item Don't emphasise that the benchmarks come from my previous work
-    \item Integrate the example below into the text, possibly moving irrelevant
-          details (such as the formulas in other logics) to supplementary
-          material
-  \end{itemize}
-}
-
-We compare these algorithms using three benchmarks from previous studies. The
-first benchmark is the function-counting problem from \cref{example:functions},
-previously examined by Dilkas and Belle~\cite{DBLP:conf/kr/DilkasB23}. The
-second benchmark is a variant of the well-known `Friends and Smokers' (hitherto
-referred to as `friends') Markov logic
-network~\cite{DBLP:conf/aaai/SinglaD08,DBLP:conf/uai/BroeckCD12}. In \Ctwo{},
-\FO{}, and \UFO{}, this problem can be formulated as
+We compare these algorithms using three benchmarks from previous work. The first
+benchmark is the bijection-counting problem from \cref{example:bijections}. The
+next benchmark is a variant of the well-known \friends{} Markov logic
+network~\cite{DBLP:conf/aaai/SinglaD08,DBLP:conf/uai/BroeckCD12}, which can be
+formulated as
 \[
-  (\forall x,y \in \Delta\text{. } S(x) \land F(x, y) \Rightarrow S(y)) \land (\forall x \in \Delta\text{. }S(x) \Rightarrow C(x))
+  (\forall x,y \in \Delta\text{.
+  } S(x) \land F(x, y) \Rightarrow S(y)) \land (\forall x \in \Delta\text{.
+  }S(x) \Rightarrow C(x)).
 \]
-or, equivalently, in conjunctive normal form as
+In this formula, we have three predicates $S$, $F$, and $C$ that denote smoking,
+friendship, and cancer, respectively. The first clause states that friends of
+smokers are also smokers, and the second clause asserts that smoking causes
+cancer. Common additions to this formula include making the friendship relation
+symmetric and assigning probabilities to each clause. Finally, we include the
+function-counting problem~\cite{DBLP:conf/kr/DilkasB23}
 \[
-  (\forall x,y \in \Delta\text{. }S(y) \lor \neg S(x) \lor \neg F(x, y)) \land (\forall x \in \Delta\text{. } C(x) \lor \neg S(x)).
+  (\forall x \in \Gamma\text{. }\exists y \in \Delta\text{.
+  }P(x, y)) \land (\forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{.
+  }P(x, y) \land P(x, z) \Rightarrow y = z)
 \]
-Finally, we include the bijection-counting problem previously utilised by Dilkas
-and Belle~\cite{DBLP:conf/kr/DilkasB23}. Its formulation in \FO{} is described
-in \cref{example:bijections}.
-
-\begin{example}[Counting functions]\label{example:functions}
-  To define predicate $P$ as a function from a domain $\Delta$ to itself, in
-  \FO{} we would write
-  \begin{equation}\label[formula]{eq:fo}
-    \begin{gathered}
-      (\forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }P(x, y)) \land (\forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z).
-    \end{gathered}
-  \end{equation}
-  The first clause asserts that each $x$ must have at least one corresponding
-  $y$, while the second statement adds the condition that if $x$ is mapped to
-  both $y$ and $z$, then $y$ must equal $z$. It is important to note that
-  \cref{eq:fo} is written with two domains instead of just one. However, we can
-  still determine the correct number of functions by assuming that the sizes of
-  $\Gamma$ and $\Delta$ are equal. This formulation, as observed by Dilkas and
-  Belle~\cite{DBLP:conf/kr/DilkasB23}, can prove beneficial in enabling FOKC
-  algorithms to find efficient solutions.
-\end{example}
+as our last benchmark. Here, predicate $P$ is defined as a function from
+$\Gamma$ to $\Delta$. The first clause asserts that each $x$ must have at least
+one corresponding $y$, while the second clause ensures that there is only one
+such $y$.
+
+\begin{remark*}
+  We formulate \bijections{} and \functions{} benchmarks using two domains
+  $\Gamma$ and $\Delta$ as such a formulation is known to help FOKC algorithms
+  find efficient solutions~\cite{DBLP:conf/kr/DilkasB23}. To compare \Cranetwo{}
+  and \textsc{ForcLift} with \textsc{FastWFOMC} that has no support for multiple
+  domains, we set $|\Gamma| = |\Delta|$.
+\end{remark*}
+
+The three benchmarks cover a wide range of possibilities. The \friends{}
+benchmark uses multiple predicates and can be expressed in \FO{} using two
+variables without cardinality constraints or counting quantifiers. The
+\functions{} benchmark, on the other hand, can still be handled by all the
+algorithms, but it requires cardinality constraints, counting quantifiers, or
+more than two variables, depending on the formulation and the capabilities of
+the algorithm. Lastly, the \bijections{} benchmark is an example of a formula
+that \textsc{FastWFOMC} can handle but \textsc{ForcLift} cannot.
+
+\subsection{Results}
 
@@
 
-\todo[inline]{For each curve, check which polynomial or exponential model best
-  fits the data to expand this section a bit (without plotting them, but
-  describing the method).}
-
-The three benchmark families cover a wide range of possibilities. The
-`friends' benchmark stands out as it uses multiple predicates and can be
-expressed in \FO{} using just two variables without cardinality constraints or
-counting quantifiers. The `functions' benchmark, on the other hand, can still be
-handled by all the algorithms, but it requires cardinality constraints, counting
-quantifiers, or more than two variables. Lastly, the `bijections' benchmark is
-an example of a formula that \textsc{FastWFOMC} can handle but \textsc{ForcLift}
-cannot.
-
-For evaluation purposes, we ran each algorithm on each benchmark using domains
-of sizes $2^{1}, 2^{2}, 2^{3}$, and so on, until an algorithm failed to handle a
-domain size due to timeout, out of memory error, or out of precision errors.
-While we separately measured compilation and inference time, we primarily focus
-on total runtime, dominated by the latter.
-
-\subsection{Results}
-
 \todo[inline,caption={}]{
   \begin{itemize}
+    \item Maybe add exact powers of two as vertical dotted lines (with both
+          labels and lines in, say, red). Also try to expand this section a bit.
     \item We are not aware of any formulas on which \Cranetwo{} scales worse
@@
 model counts smaller than $2^{31}$, it only scales up to domain sizes of
-\num{16} and \num{128} for `friends' and `functions', respectively.
-\textsc{FastWFOMC} outperformed \textsc{ForcLift} in the case of `friends', but
-not `functions', as it could handle domains of size \num{1024} and \num{64},
+\num{16} and \num{128} for \friends{} and \functions{}, respectively.
+\textsc{FastWFOMC} outperformed \textsc{ForcLift} in the case of \friends{}, but
+not \functions{}, as it could handle domains of size \num{1024} and \num{64},
 respectively. Furthermore, both \Cranebfs{} and \Cranegreedy{} performed
-similarly on both benchmarks. Similarly to the `bijections' benchmark,
+similarly on both benchmarks. Similarly to the \bijections{} benchmark,
 \Cranetwo{} significantly outperformed the other two algorithms, scaling up to
@@
 \textsc{ForcLift}. The ability to efficiently handle large domain sizes is
-particularly crucial in the weighted setting, as illustrated by the `friends'
+particularly crucial in the weighted setting, as illustrated by the \friends{}
 example discussed in \cref{sec:experiments}, where the model captures complex
@@
 
-`Friends' in \Ctwo{} and \UFO{} is the same as in \FO{}.
-
-For `bijections', the equivalent formula in \Ctwo{} is
+\friends{} in \Ctwo{} and \UFO{} is the same as in \FO{}.
+
+For \bijections{}, the equivalent formula in \Ctwo{} is
 \[
@@
 
-For `functions', in \Ctwo{} one would write $\forall x \in \Delta\text{.
+For \functions{}, in \Ctwo{} one would write $\forall x \in \Delta\text{.
 }\exists^{=1} y \in \Delta\text{. }P(x, y)$. In \UFO{}, the same could be

### 2025-02-02 analysis/analyse.R

@@ -17,7 +17,7 @@ df$algorithm[df$algorithm == "greedy"] <- "\\textsc{Gantry-Greedy}"
 df$algorithm[df$algorithm == "fastwfomc"] <- "\\textsc{FastWFOMC}"
 df$algorithm[df$algorithm == "forclift"] <- "\\textsc{ForcLift}"
 df$sequence[df$sequence == "bijections"] <- "Bijections"
-df$sequence[df$sequence == "friends"] <- "Friends"
+df$sequence[df$sequence == "friends"] <- "Friends \\& Smokers"
 df$sequence[df$sequence == "functions"] <- "Functions"
 df <- df[df$domain.size > 1,]
 dark2_colors <- brewer.pal(8, "Dark2")

### 2025-02-03 doc/paper/paper.tex
Section 4.2

@@
 while the other algorithms were executed on the Java Virtual Machine 1.8.0\_201.
+Note that, although implemented in different languages, both \Cranetwo{} and
+\textsc{FastWFOMC} use the GNU Multiple Precision Arithmetic Library for
+arbitrary-precision arithmetic.
 
@@
 errors. While we separately measured compilation and inference time, we
-primarily focus on total runtime, dominated by the latter.
+primarily focus on total runtime, dominated by the latter. We verified the
+accuracy of the numerical answers using the corresponding integer sequences on
+the On-Line Encyclopedia of Integer Sequences~\cite{oeis}.
 
@@
 
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item Maybe add exact powers of two as vertical dotted lines (with both
-          labels and lines in, say, red). Also try to expand this section a bit.
-    \item We are not aware of any formulas on which \Cranetwo{} scales worse
-          compared to either \textsc{ForcLift} or \textsc{FastWFOMC}. The one
-          advantage that \textsc{FastWFOMC} has over \Cranetwo{} is its support
-          for counting quantifiers.
-    \item Regarding programming languages and accuracy, we verified that the
-          answers match for smaller domain sizes. Also, although written in
-          different languages, both \Cranetwo{} and \textsc{FastWFOMC} use the
-          GNU Multiple Precision Arithmetic Library.
-  \end{itemize}
-}
-
-\todo[inline]{Incorporate into the text below: It is worth remarking that
-  \textsc{ForcLift} does not support arbitrary precision, and returns error for
-  cases that requires arbitrary precision reasoning. }
-
 \Cref{fig:plot} presents a summary of the experimental results. Only
@@
 
-Another aspect of the experimental results that deserves separate discussion is
-compilation. Both Julia and Scala use just-in-time (JIT) compilation, which
-means that \textsc{FastWFOMC} and \textsc{ForcLift} take longer to run on the
-smallest domain size, where most JIT compilation occurs. In the case of
-\Cranetwo{}, it is only run once per benchmark, so the JIT compilation time is
-included in its overall runtime across all domain sizes. Additionally, while
-\textsc{ForcLift}'s compilation is generally faster than that of \Cranetwo{},
-neither significantly affects overall runtime. Specifically, \textsc{ForcLift}
-compilation typically takes around \SI{0.5}{\second}, while \Cranetwo{}
-compilation takes around \SI{2.3}{\second}.
+One might notice that the runtime of \textsc{FastWFOMC} and \textsc{ForcLift} is
+slightly higher on the smallest domain size. This peculiarity is the consequence
+of \emph{just-in-time} (JIT) compilation. As \Cranetwo{} is only run once per
+benchmark, the JIT compilation time is included in its overall runtime across
+all domain sizes. Additionally, while \textsc{ForcLift}'s compilation is
+generally faster than that of \Cranetwo{}, neither significantly affects overall
+runtime. Specifically, \textsc{ForcLift} compilation typically takes around
+\SI{0.5}{\second}, while \Cranetwo{} compilation takes around \SI{2.3}{\second}.
 
@@
 \section{Conclusion and Future Work}\label{sec:conclusion}
+
+\todo[inline,caption={}]{
+  \begin{itemize}
+    \item Somewhere: reference the appendix, saying that `we provide a more
+          detailed comparison of the capabilities of the algorithms'
+  \end{itemize}
+}
 

### 2025-02-03 doc/paper/paper.tex
Move the appendix to a separate file

@@
 \usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-\usepackage{booktabs}
-\usepackage{pifont}
 \usepackage{siunitx}
@@
 \usepackage{microtype}
-\usepackage[backgroundcolor=lightgray]{todonotes}
+\usepackage[backgroundcolor=lightgray]{todonotes} % TODO: temporary
 \usepackage{mathtools}
@@
 
-\newcommand{\cmark}{\ding{51}}
-\newcommand{\xmark}{\ding{55}}
 \newcommand{\expr}{\mathtt{expr}}
-\newcommand{\Ctwo}{$\mathsf{C}^{2}$}
 \newcommand{\FO}{$\mathsf{FO}$}
-\newcommand{\UFO}{$\mathsf{UFO}^{2} + \mathsf{CC}$}
 \newcommand{\Cranetwo}{\textsc{Gantry}}
@@
 search~\cite{DBLP:journals/pvldb/NiuRDS11}, and Monte Carlo
-sampling~\cite{DBLP:journals/cacm/GogateD16}. Among these, FOKC-based algorithms
-are particularly prominent, transforming formulas into structured
-representations such as circuits or graphs. Even when multiple algorithms are
-able to solve the same instance, FOKC algorithms are known to find
-polynomial-time solutions, where the polynomial has a lower degree compared to
-other approaches~\cite{DBLP:conf/kr/DilkasB23}. The recently developed ability
-of a FOKC algorithm to formulate solutions in terms of recursive
+sampling~\cite{DBLP:journals/cacm/GogateD16}. (See the technical appendix for a
+more detailed comparison of the state-of-the-art FOMC algorithms.) Among these,
+FOKC-based algorithms are particularly prominent, transforming formulas into
+structured representations such as circuits or graphs. Even when multiple
+algorithms are able to solve the same instance, FOKC algorithms are known to
+find polynomial-time solutions, where the polynomial has a lower degree compared
+to other approaches~\cite{DBLP:conf/kr/DilkasB23}. The recently developed
+ability of a FOKC algorithm to formulate solutions in terms of recursive
 functions~\cite{DBLP:conf/kr/DilkasB23} is also noteworthy as the only other
@@
 In \cref{sec:logic}, we summarise the basic principles of first-order logic.
-Then, in \cref{sec:threelogics}, we formally define (W)FOMC and discuss the
-distinctions between three variations of first-order logic used for FOMC.\@
-Finally, in \cref{sec:algebra}, we introduce the terminology used to describe
-the output of the original \textsc{Crane} algorithm, i.e., functions and
-equations that define them.
+Then, in ??, we formally define (W)FOMC and\ldots Finally, in
+\cref{sec:algebra}, we introduce the terminology used to describe the output of
+the original \textsc{Crane} algorithm, i.e., functions and equations that define
+them.
 
@@
 
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item Somewhere: reference the appendix, saying that `we provide a more
-          detailed comparison of the capabilities of the algorithms'
-  \end{itemize}
-}
-
 In this work, we have presented a scalable automated FOKC-based approach to
@@
 across various formulas. The capabilities of \Cranetwo{} could also be
-characterised theoretically, e.g.\ by proving completeness for specific logic
-fragments like \Ctwo{}. Additionally, the efficiency of FOMC algorithms can be
-further analysed using fine-grained complexity, which would provide more
+characterised theoretically, e.g., by proving completeness for logic fragments
+liftable by other algorithms. Additionally, the efficiency of FOMC algorithms
+can be further analysed using fine-grained complexity, which would provide more
 detailed insights into the computational demands of different formulas.
 
+\todo[inline]{Cite a bunch of papers for the liftable fragments.}
+
 \bibliography{paper}
 
-\appendix
-\section{The Three Logics of FOMC}\label{sec:threelogics}
-
-\begin{table}[t]
-  \centering
-  \begin{tabular}{llclll}
-    \toprule
-    Logic & Sorts & Constants & Variables & Quantifiers & Additional atoms\\
-    \midrule
-    \FO & one or more & \cmark & unlimited & $\forall$, $\exists$ & $x = y$\\
-    \Ctwo & one & \xmark & two & $\forall$, $\exists$, $\exists^{= k}$, $\exists^{\le k}$, $\exists^{\ge k}$ & ---\\
-    \UFO & one & \xmark & two & $\forall$ & $|P| = m$\\
-    \bottomrule
-  \end{tabular}
-  \caption{A comparison of the three logics used in FOMC\@. The
-    2\textsuperscript{nd}--5\textsuperscript{th} columns refer to: the number of
-    sorts, support for constants, the maximum number of variables, and supported
-    quantifiers, respectively. The last column lists supported atoms in addition
-    to those of the form $P(\mathbf{t})$ for a predicate $P/n$ and an $n$-tuple
-    of terms $\mathbf{t}$. Here: $k$ and $m$ are non-negative integers, with the
-    latter depending on the domain size, $P$ represents a predicate, and $x$ and
-    $y$ are terms. }\label{tbl:logics}
-\end{table}
-
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item Reference the table
-    \item Delete references to this appendix (except for one place, probably in
-          \cref{sec:experiments})
-    \item Make sure the rest of the paper doesn't refer to these logics (or
-          describe examples in them)
-    \item Move the URLs to the main text
-    \item Later (probably) move this to a different file
-  \end{itemize}
-}
-
-\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
-
-There are three first-order logics commonly used in FOMC: \FO{}, \Ctwo{}, and
-\UFO{}. First, \FO{} is the input format for
-\textsc{ForcLift}\footnote{\url{https://github.com/UCLA-StarAI/Forclift}} and
-its extensions
-\textsc{Crane}\footnote{\url{https://doi.org/10.5281/zenodo.8004077}} and
-\Cranetwo{}. Second, \Ctwo{} is often used in the literature on
-\textsc{FastWFOMC}\footnote{\url{https://github.com/jan-toth/FastWFOMC.jl}} and
-related methods~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}.
-Finally, \UFO{} is the input format supported by the most recent implementation
-of \textsc{FastWFOMC}~\cite{DBLP:conf/kr/TothK24}. All three logics are
-function-free, and domains are always assumed to be finite. As usual, we
-presuppose the \emph{unique name assumption}, which states that two constants
-are equal if and only if they are the same constant~\cite{DBLP:books/aw/RN2020}.
-
-\renewcommand*{\thefootnote}{\arabic{footnote}}
-
-In \FO{}, each term is assigned to a \emph{sort}, and each predicate $P/n$ is
-assigned to a sequence of $n$ sorts. Each sort has its corresponding domain.
-These assignments to sorts are typically left implicit and can be reconstructed
-from the quantifiers. For example, $\forall x,y \in \Delta\text{. }P(x, y)$
-implies that variables $x$ and $y$ have the same sort. On the other hand,
-$\forall x \in \Delta\text{. }\forall y \in \Gamma\text{. } P(x, y)$ implies
-that $x$ and $y$ have different sorts, and it would be improper to write, for
-example, $\forall x \in \Delta\text{. }\forall y \in \Gamma\text{.
-} P(x, y) \lor x = y$. \FO{} is also the only logic to support constants,
-formulas with more than two variables, and the equality predicate. While we do
-not explicitly refer to sorts in subsequent sections of this paper, the
-many-sorted nature of \FO{} is paramount to the algorithms presented therein.
-
-\begin{remark*}
-  In the case of \textsc{ForcLift} and its extensions, support for a formula as
-  valid input does not imply that the algorithm can compile the formula into a
-  circuit or graph suitable for lifted model counting. However, it is known that
-  \textsc{ForcLift} compilation is guaranteed to succeed on any \FO{} formula
-  without constants and with at most two
-  variables~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/kr/BroeckMD14}.
-\end{remark*}
-
-Compared to \FO{}, \Ctwo{} and \UFO{} lack support for constants, the equality
-predicate, multiple domains, and formulas with more than two variables. The
-advantage that \Ctwo{} brings over \FO{} is the inclusion of \emph{counting
-  quantifiers}. That is, alongside $\forall$ and $\exists$, \Ctwo{} supports
-$\exists^{=k}$, $\exists^{\le k}$, and $\exists^{\ge k}$ for any positive
-integer $k$. For example, $\exists^{=1} x\text{. }\phi(x)$ means that there
-exists \emph{exactly one} $x$ such that $\phi(x)$, and $\exists^{\le 2} x\text{.
-}\phi(x)$ means that there exist \emph{at most two} such $x$. \UFO{}, on the
-other hand, does not support any existential quantifiers but instead
-incorporates \emph{(equality) cardinality constraints}. For example, $|P| = 3$
-constrains all models to have \emph{precisely three positive literals with the
-  predicate $P$}.
-
-\subsection{Our Benchmarks in \Ctwo{} and \UFO{}}
-
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item An introductory paragraph
-    \item Figure out the right order in which the information below should be
-          presented
-    \item Make the text below coherent
-    \item Refer to it in the main text (and make sure the reference sticks when
-          I transfer this to a separate file)
-  \end{itemize}
-}
-
-\friends{} in \Ctwo{} and \UFO{} is the same as in \FO{}.
-
-For \bijections{}, the equivalent formula in \Ctwo{} is
-\[
-  (\forall x \in \Delta\text{. }\exists^{=1} y \in \Delta\text{.
-  }P(x, y)) \land (\forall y \in \Delta\text{. }\exists^{=1} x \in \Delta\text{.
-  }P(x, y)).
-\]
-Similarly, in \UFO{} the same formula can be written as
-\[
-  (\forall x, y \in \Delta\text{.
-  }R(x) \lor \neg P(x, y)) \land (\forall x, y \in \Delta\text{.
-  }S(x) \lor \neg P(y, x)) \land (|P| = |\Delta|),
-\]
-where $w^{-}(R) = w^{-}(S) = -1$.
-
-For \functions{}, in \Ctwo{} one would write $\forall x \in \Delta\text{.
-}\exists^{=1} y \in \Delta\text{. }P(x, y)$. In \UFO{}, the same could be
-written as
-\begin{equation}\label[formula]{eq:functions1}
-  (\forall x, y \in \Delta\text{. }S(x) \lor \neg P(x, y)) \land (|P| = |\Delta|),
-\end{equation}
-where $w^{-}(S) = -1$. Although \cref{eq:functions1} has more models compared to
-its counterpart in \Ctwo{}, the negative weight $w^{-}(S) = -1$ makes some of
-the terms in \cref{eq:wfomc} cancel out.
-
 \end{document}

### 2025-02-03 doc/technical_appendix/technical_appendix.tex
Move the appendix to a separate file

\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate]{lipics-v2021}
%This is a template for producing LIPIcs articles. 
%See lipics-v2021-authors-guidelines.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
%for section-numbered lemmas etc., use "numberwithinsect"
%for enabling cleveref support, use "cleveref"
%for enabling autoref support, use "autoref"
%for anonymousing the authors (e.g. for double-blind review), add "anonymous"
%for enabling thm-restate support, use "thm-restate"
%for enabling a two-column layout for the author/affilation part (only applicable for > 6 authors), use "authorcolumns"
%for producing a PDF according the PDF/A standard, add "pdfa"

\pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository

%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory

\bibliographystyle{plainurl}% the mandatory bibstyle

\title{Towards Practical First-Order Model Counting: Technical Appendix}

\author{Ananth K. Kidambi}{Indian Institute of Technology Bombay, Mumbai, India}{210051002@iitb.ac.in}{}{}
\author{Guramrit Singh}{Indian Institute of Technology Bombay, Mumbai, India}{guramrit@iitb.ac.in}{}{}
\author{Paulius Dilkas}{University of Toronto, Toronto, Canada \and Vector Institute, Toronto, Canada \and \url{https://dilkas.github.io/}}{paulius.dilkas@utoronto.ca}{https://orcid.org/0000-0001-9185-7840}{}
\author{Kuldeep S. Meel}{University of Toronto, Toronto, Canada \and \url{https://www.cs.toronto.edu/~meel/}}{meel@cs.toronto.edu}{https://orcid.org/0000-0001-9423-5270}{}

\authorrunning{A.\,K. Kidambi, G. Singh, P. Dilkas, and K.\,S. Meel}
\Copyright{Ananth K. Kidambi, Guramrit Singh, Paulius Dilkas, and Kuldeep S. Meel}

\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website

%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
%\supplementdetails[linktext={opt. text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g. Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional

%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors. Please enter author specific funding statements as fifth argument of the \author macro.

%\acknowledgements{I want to thank \dots}%optional

%\nolinenumbers %uncomment to disable line numbering

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{John Q. Open and Joan R. Access}
\EventNoEds{2}
\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
\EventShortTitle{CVIT 2016}
\EventAcronym{CVIT}
\EventYear{2016}
\EventDate{December 24--27, 2016}
\EventLocation{Little Whinging, United Kingdom}
\EventLogo{}
\SeriesVolume{42}
\ArticleNo{23}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{booktabs}
\usepackage{pifont}
\usepackage[backgroundcolor=lightgray]{todonotes} % TODO: temporary

\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}
\newcommand{\Ctwo}{$\mathsf{C}^{2}$}
\newcommand{\FO}{$\mathsf{FO}$}
\newcommand{\UFO}{$\mathsf{UFO}^{2} + \mathsf{CC}$}
\newcommand{\Cranetwo}{\textsc{Gantry}}
\newcommand{\friends}{\emph{Friends \& Smokers}}
\newcommand{\functions}{\emph{Functions}}
\newcommand{\bijections}{\emph{Bijections}}

\crefalias{formula}{equation}
\crefname{formula}{Formula}{Formulas}
\creflabelformat{formula}{#2\textup{(#1)}#3}

\begin{document}

\maketitle

\section{The Three Logics of FOMC}\label{sec:threelogics}

\begin{table}[t]
  \centering
  \begin{tabular}{llclll}
    \toprule
    Logic & Sorts & Constants & Variables & Quantifiers & Additional atoms\\
    \midrule
    \FO & one or more & \cmark & unlimited & $\forall$, $\exists$ & $x = y$\\
    \Ctwo & one & \xmark & two & $\forall$, $\exists$, $\exists^{= k}$, $\exists^{\le k}$, $\exists^{\ge k}$ & ---\\
    \UFO & one & \xmark & two & $\forall$ & $|P| = m$\\
    \bottomrule
  \end{tabular}
  \caption{A comparison of the three logics used in FOMC\@. The
    2\textsuperscript{nd}--5\textsuperscript{th} columns refer to: the number of
    sorts, support for constants, the maximum number of variables, and supported
    quantifiers, respectively. The last column lists supported atoms in addition
    to those of the form $P(\mathbf{t})$ for a predicate $P/n$ and an $n$-tuple
    of terms $\mathbf{t}$. Here: $k$ and $m$ are non-negative integers, with the
    latter depending on the domain size, $P$ represents a predicate, and $x$ and
    $y$ are terms. }\label{tbl:logics}
\end{table}

\todo[inline,caption={}]{
  \begin{itemize}
    \item Reference the table
    \item Make sure the rest of the paper doesn't refer to these logics (or
          describe examples in them)
    \item Move the URLs to the main text (and make sure that each algorithm name
          is combined with a citation at least once)
    \item Later (probably) move this to a different file
  \end{itemize}
}

\renewcommand*{\thefootnote}{\fnsymbol{footnote}}

There are three first-order logics commonly used in FOMC: \FO{}, \Ctwo{}, and
\UFO{}. First, \FO{} is the input format for
\textsc{ForcLift}\footnote{\url{https://github.com/UCLA-StarAI/Forclift}} and
its extensions
\textsc{Crane}\footnote{\url{https://doi.org/10.5281/zenodo.8004077}} and
\Cranetwo{}. Second, \Ctwo{} is often used in the literature on
\textsc{FastWFOMC}\footnote{\url{https://github.com/jan-toth/FastWFOMC.jl}} and
related methods~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}.
Finally, \UFO{} is the input format supported by the most recent implementation
of \textsc{FastWFOMC}~\cite{DBLP:conf/kr/TothK24}. All three logics are
function-free, and domains are always assumed to be finite. As usual, we
presuppose the \emph{unique name assumption}, which states that two constants
are equal if and only if they are the same constant~\cite{DBLP:books/aw/RN2020}.

\renewcommand*{\thefootnote}{\arabic{footnote}}

In \FO{}, each term is assigned to a \emph{sort}, and each predicate $P/n$ is
assigned to a sequence of $n$ sorts. Each sort has its corresponding domain.
These assignments to sorts are typically left implicit and can be reconstructed
from the quantifiers. For example, $\forall x,y \in \Delta\text{. }P(x, y)$
implies that variables $x$ and $y$ have the same sort. On the other hand,
$\forall x \in \Delta\text{. }\forall y \in \Gamma\text{. } P(x, y)$ implies
that $x$ and $y$ have different sorts, and it would be improper to write, for
example, $\forall x \in \Delta\text{. }\forall y \in \Gamma\text{.
} P(x, y) \lor x = y$. \FO{} is also the only logic to support constants,
formulas with more than two variables, and the equality predicate. While we do
not explicitly refer to sorts in subsequent sections of this paper, the
many-sorted nature of \FO{} is paramount to the algorithms presented therein.

\begin{remark*}
  In the case of \textsc{ForcLift} and its extensions, support for a formula as
  valid input does not imply that the algorithm can compile the formula into a
  circuit or graph suitable for lifted model counting. However, it is known that
  \textsc{ForcLift} compilation is guaranteed to succeed on any \FO{} formula
  without constants and with at most two
  variables~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/kr/BroeckMD14}.
\end{remark*}

Compared to \FO{}, \Ctwo{} and \UFO{} lack support for constants, the equality
predicate, multiple domains, and formulas with more than two variables. The
advantage that \Ctwo{} brings over \FO{} is the inclusion of \emph{counting
  quantifiers}. That is, alongside $\forall$ and $\exists$, \Ctwo{} supports
$\exists^{=k}$, $\exists^{\le k}$, and $\exists^{\ge k}$ for any positive
integer $k$. For example, $\exists^{=1} x\text{. }\phi(x)$ means that there
exists \emph{exactly one} $x$ such that $\phi(x)$, and $\exists^{\le 2} x\text{.
}\phi(x)$ means that there exist \emph{at most two} such $x$. \UFO{}, on the
other hand, does not support any existential quantifiers but instead
incorporates \emph{(equality) cardinality constraints}. For example, $|P| = 3$
constrains all models to have \emph{precisely three positive literals with the
  predicate $P$}.

\subsection{Our Benchmarks in \Ctwo{} and \UFO{}}

\todo[inline,caption={}]{
  \begin{itemize}
    \item An introductory paragraph
    \item Figure out the right order in which the information below should be
          presented
    \item Make the text below coherent
    \item Refer to it in the main text (and make sure the reference sticks when
          I transfer this to a separate file)
  \end{itemize}
}

\friends{} in \Ctwo{} and \UFO{} is the same as in \FO{}.

For \bijections{}, the equivalent formula in \Ctwo{} is
\[
  (\forall x \in \Delta\text{. }\exists^{=1} y \in \Delta\text{.
  }P(x, y)) \land (\forall y \in \Delta\text{. }\exists^{=1} x \in \Delta\text{.
  }P(x, y)).
\]
Similarly, in \UFO{} the same formula can be written as
\[
  (\forall x, y \in \Delta\text{.
  }R(x) \lor \neg P(x, y)) \land (\forall x, y \in \Delta\text{.
  }S(x) \lor \neg P(y, x)) \land (|P| = |\Delta|),
\]
where $w^{-}(R) = w^{-}(S) = -1$.

For \functions{}, in \Ctwo{} one would write $\forall x \in \Delta\text{.
}\exists^{=1} y \in \Delta\text{. }P(x, y)$. In \UFO{}, the same could be
written as
\begin{equation}\label[formula]{eq:functions1}
  (\forall x, y \in \Delta\text{. }S(x) \lor \neg P(x, y)) \land (|P| = |\Delta|),
\end{equation}
where $w^{-}(S) = -1$. Although \cref{eq:functions1} has more models compared to
its counterpart in \Ctwo{}, the negative weight $w^{-}(S) = -1$ makes some of
the terms in the definition of WFOMC cancel out.

\bibliography{../paper/paper.bib}

\end{document}

### 2025-02-06 doc/paper/paper.tex
Sentence, not formula

@@
 \crefalias{formula}{equation}
-\crefname{formula}{Formula}{Formulas}
+\crefname{formula}{Sentence}{Sentence}
 \creflabelformat{formula}{#2\textup{(#1)}#3}
@@
   \begin{itemize}
-    \item Sentence vs formula: be consistent and not confusing
     \item 15 pages excluding references
@@
           definitions with the necessary base cases. This process includes
-          identifying the base cases and their corresponding formulas,
+          identifying the base cases and their corresponding sentences,
           transforming them (including applying a new smoothing procedure), and
@@
 The complexity of FOMC is generally measured by \emph{data complexity}, with a
-formula classified as \emph{liftable} if it can be solved in polynomial time
+sentence classified as \emph{liftable} if it can be solved in polynomial time
 relative to the domain size~\cite{DBLP:conf/starai/JaegerB12}. While all
-formulas with up to two variables are known to be
+sentences with up to two variables are known to be
 liftable~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/kr/BroeckMD14}, Beame et
 al.~\cite{DBLP:conf/pods/BeameBGS15} demonstrated that liftability does not
-extend to all formulas, identifying an unliftable formula with three variables.
-Recent work has further extended the liftable fragment with additional
-axioms~\cite{DBLP:conf/aaai/TothK23,DBLP:journals/ai/BremenK23} and counting
-quantifiers~\cite{DBLP:journals/jair/Kuzelka21}, expanding our understanding of
-liftability.
+extend to all sentences, identifying an unliftable sentence with three
+variables. Recent work has further extended the liftable fragment with
+additional axioms~\cite{DBLP:conf/aaai/TothK23,DBLP:journals/ai/BremenK23} and
+counting quantifiers~\cite{DBLP:journals/jair/Kuzelka21}, expanding our
+understanding of liftability.
 
@@
 more detailed comparison of the state-of-the-art FOMC algorithms.) Among these,
-FOKC-based algorithms are particularly prominent, transforming formulas into
+FOKC-based algorithms are particularly prominent, transforming sentences into
 structured representations such as circuits or graphs. Even when multiple
@@
 The \textsc{Crane} algorithm marked a significant step forward, expanding the
-range of formulas handled by FOMC algorithms. However, it had notable
+range of sentences handled by FOMC algorithms. However, it had notable
 limitations: it required manual evaluation of function definitions to compute
@@
 
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item If I need more space elsewhere, shortening the preliminaries to two
-          pages (perhaps skipping Section 2.2 altogether?)
-    \item Adjust the introductory paragraph below to the new structure (with
-          more subsections)
-  \end{itemize}
-}
-
-In \cref{sec:logic}, we summarise the basic principles of first-order logic.
-Then, in ??, we formally define (W)FOMC and\ldots Finally, in
-\cref{sec:algebra}, we introduce the terminology used to describe the output of
-the original \textsc{Crane} algorithm, i.e., functions and equations that define
-them.
+We begin this section by describing some notation that we will use throughout
+the paper. Then, in \cref{sec:logic,sec:fomc} respectively, we introduce the
+basic terminology of first-order logic and formally define (W)FOMC\@.
+\Cref{sec:crane} outlines the principles of FOKC, particularly in the context of
+\textsc{Crane}. Finally, in \cref{sec:algebra}, we introduce the algebraic
+terminology used to describe the output of \textsc{Crane}, i.e., functions and
+equations that define them.
 
@@
 that a clause is a \emph{(positive) unit clause} if there is only one literal
-with a predicate, and it is a positive literal. Finally, a \emph{formula} is a
+with a predicate, and it is a positive literal. Finally, a \emph{sentence} is a
 conjunction of clauses. Throughout the paper, we will use set-theoretic
-notation, interpreting a formula as a set of clauses and a clause as a set of
+notation, interpreting a sentence as a set of clauses and a clause as a set of
 literals.
@@
   definition of a clause includes universal quantifiers for all variables
-  within. While it is possible to rewrite the entire formula with all
+  within. While it is possible to rewrite the entire sentence with all
   quantifiers at the front~\cite{hinman2018fundamentals}, the format we describe
@@
 
-\subsection{First-Order Model Counting}
+\subsection{First-Order Model Counting}\label{sec:fomc}
 
@@
 
-% Additionally, our formulation of the definition of WFOMC is
-% somewhat complicated by the need to support any number of domains.
-
 \begin{definition}[Structure, model]\label{def:model}
-  Let $\phi$ be a formula in \FO{}. For each predicate $P/n$ in $\phi$, let
+  Let $\phi$ be a sentence in \FO{}. For each predicate $P/n$ in $\phi$, let
   ${(\Delta_{i}^{P})}_{i=1}^{n}$ be a list of the corresponding domains. Let
@@
 \begin{example}[Counting bijections]\label{example:bijections}
-  Let us consider the following formula (previously examined by Dilkas and
+  Let us consider the following sentence (previously examined by Dilkas and
   Belle~\cite{DBLP:conf/kr/DilkasB23}) that defines predicate $P$ as a bijection
@@
 \begin{definition}[WFOMC instance]\label{def:instance}
-  A \emph{WFOMC instance} comprises: a formula $\phi$ in \FO{}, two (rational)
+  A \emph{WFOMC instance} comprises: a sentence $\phi$ in \FO{}, two (rational)
   \emph{weights} $w^{+}(P)$ and $w^{-}(P)$ assigned to each predicate $P$ in
@@
 As our work builds on \textsc{Crane}, in this section we will briefly outline
-the steps \textsc{Crane} goes through to compile an \FO{} formula into a set of
+the steps \textsc{Crane} goes through to compile an \FO{} sentence into a set of
 function definitions. We divide the inner workings of the algorithm into two
@@
 
-The goal of this stage is to transform an arbitrary \FO{} formula into the
+The goal of this stage is to transform an arbitrary \FO{} sentence into the
 format described in \cref{sec:logic}, most importantly by eliminating
@@
 
-At this stage, the preprocessed formula is compiled into the set $\mathcal{E}$
+At this stage, the preprocessed sentence is compiled into the set $\mathcal{E}$
 of equations and two auxiliary maps $\mathcal{F}$ and $\mathcal{D}$.
-$\mathcal{F}$ maps function names to formulas, and $\mathcal{D}$ maps function
+$\mathcal{F}$ maps function names to sentences, and $\mathcal{D}$ maps function
 names and argument indices to domains. $\mathcal{E}$ can contain any number of
@@
   where $\Delta^{\top}$ is a newly introduced domain. (We omit the definition of
-  $\mathcal{F}$ as the formulas can get quite verbose.) To compute the number of
-  bijections between two sets of cardinality 3, one would evaluate $f(3, 3)$,
+  $\mathcal{F}$ as the sentences can get quite verbose.) To compute the number
+  of bijections between two sets of cardinality 3, one would evaluate $f(3, 3)$,
   however, the definition of $g$ is incomplete: $g$ is a recursive function
@@
 Compilation is performed primarily by applying \emph{(compilation) rules} to
-formulas. \textsc{Crane} has two modes depending on how the algorithm chooses
-which compilation rule to apply to a formula (in case several alternatives are
+sentences. \textsc{Crane} has two modes depending on how the algorithm chooses
+which compilation rule to apply to a sentence (in case several alternatives are
 available). The first option is to use greedy search: there is a list of rules,
@@
   \caption[]{The outline of using \Cranetwo{} to compute the model count of a
-    formula $\phi$. First, the formula is compiled into a set of equations,
-    which are then used to create a C++ program. This program can be executed
-    with different command line arguments to calculate the model count of $\phi$
-    for different domain sizes. To accomplish this, the \CompileWithBaseCases
+    sentence $\phi$. First, $\phi$ is compiled into a set of equations, which
+    are then used to create a C++ program. This program can be executed with
+    different command line arguments to calculate the model count of $\phi$ for
+    different domain sizes. To accomplish this, the \CompileWithBaseCases
     procedure uses \textsc{Crane}, algebraic simplification techniques (denoted
@@
 \textsc{Crane} with the necessary base cases. To do so, it may recursively call
-itself (and \textsc{Crane}) on other formulas. We prove that the number of such
-recursive calls is upper bounded by the number of domains in the formula.
+itself (and \textsc{Crane}) on other sentences. We prove that the number of such
+recursive calls is upper bounded by the number of domains in the sentences.
 
@@
 
-\Cref{sec:propagating} introduces the \Propagate procedure that takes a formula
+\Cref{sec:propagating} introduces the \Propagate procedure that takes a sentence
 $\phi$, a domain $\Delta$, and $n \in \mathbb{N}_{0}$. It returns $\phi$
@@
 of $f$ (i.e., $\mathcal{D}(f, 1)$) is empty. When run on this simplified
-formula, \CompileWithBaseCases will return the equations for the base case
+sentence, \CompileWithBaseCases will return the equations for the base case
 $f(0, y)$.
@@
   \caption{\protect\CompileWithBaseCases{$\phi$}}\label{alg:compilewithbasecases}
-  \KwIn{formula $\phi$}
+  \KwIn{sentence $\phi$}
   \KwOut{set $\mathcal{E}$ of equations}
@@
 \Cref{alg:compilewithbasecases} presents our overall approach for compiling a
-formula into equations that include the necessary base cases. To begin, we use
-\textsc{Crane} to compile the formula into the three components: $\mathcal{E}$,
+sentence into equations that include the necessary base cases. To begin, we use
+\textsc{Crane} to compile the sentence into the three components: $\mathcal{E}$,
 $\mathcal{F}$, and $\mathcal{D}$ (as described in \cref{sec:compilation}). After
@@
 \FindBaseCases procedure (see \cref{sec:identifying}). For each base case
-$f(\mathbf{x})$, we retrieve the logical formula $\mathcal{F}(f)$ associated
-with the function name $f$ and simplify it using the \Propagate procedure
-(explained in detail in \cref{sec:propagating}). We do this by iterating over
-all indices of $\mathbf{x}$, where $x_{i}$ is a constant, and using \Propagate
-to simplify $\psi$ by assuming that domain $\mathcal{D}(f, i)$ has size $x_{i}$.
-Finally, on \autoref{line:final}, \CompileWithBaseCases recurses on these
-simplified formulas and adds the resulting base case equations to $\mathcal{E}$.
+$f(\mathbf{x})$, we retrieve the sentence $\mathcal{F}(f)$ associated with the
+function name $f$ and simplify it using the \Propagate procedure (explained in
+detail in \cref{sec:propagating}). We do this by iterating over all indices of
+$\mathbf{x}$, where $x_{i}$ is a constant, and using \Propagate to simplify
+$\psi$ by assuming that domain $\mathcal{D}(f, i)$ has size $x_{i}$. Finally, on
+\autoref{line:final}, \CompileWithBaseCases recurses on these simplified
+sentences and adds the resulting base case equations to $\mathcal{E}$.
 
@@
   base cases: $g(0, m)$ and $g(l, 0)$. In both cases, \CompileWithBaseCases
-  recurses on the formula $\mathcal{F}(g)$ simplified by assuming that one of
-  the domains is empty. In the first case, we recurse on the formula
+  recurses on the sentence $\mathcal{F}(g)$ simplified by assuming that one of
+  the domains is empty. In the first case, we recurse on the sentence
   $\forall x \in \Gamma\text{. }S(x) \lor \neg S(x)$, where $S$ is a predicate
@@
   Hence, we obtain the base case $g(0, m) = 0^{m}$. In the case of $g(l, 0)$,
-  \Propagate{$\psi$, $\Gamma$, $0$} returns an empty formula, resulting in
+  \Propagate{$\psi$, $\Gamma$, $0$} returns an empty sentence, resulting in
   $g(l, 0) = 1$. While these base cases overlap when $l = m = 0$, they remain
@@
 
-% Generally, let $\phi$ be a formula with two domains $\Gamma$ and $\Delta$, and
-% let $n, m \in \mathbb{N}_{0}$. Then the FOMC of \Propagate{$\phi$, $\Delta$,
-%   $n$} assuming $|\Gamma| = m$ is the same as the FOMC of \Propagate{$\phi$,
-%   $\Gamma$, $m$} assuming $|\Delta| = n$.
+% Generally, let $\phi$ be a sentence with two domains $\Gamma$ and $\Delta$,
+% and let $n, m \in \mathbb{N}_{0}$. Then the FOMC of \Propagate{$\phi$,
+% $\Delta$, $n$} assuming $|\Gamma| = m$ is the same as the FOMC of
+% \Propagate{$\phi$, $\Gamma$, $m$} assuming $|\Delta| = n$.
 
@@
 % \cref{alg:compilewithbasecases} is recursive and can issue more calls to
-% \textsc{Crane} on various derived formulas.
+% \textsc{Crane} on various derived sentences.
 
@@
 recursive call on \autoref{line:final} reduces the number of domains in the
-formula.
+sentence.
 
 \begin{theorem}
-  Given any \FO{} formula $\phi$, \CompileWithBaseCases{$\phi$} terminates.
+  Given any \FO{} sentence $\phi$, \CompileWithBaseCases{$\phi$} terminates.
 \end{theorem}
@@
 \begin{observation}\label{observation2}
-  For any formula $\phi$, domain $\Delta$, and $n \in \mathbb{N}_{0}$,
-  \Propagate{$\phi$, $\Delta$, $n$} returns a formula with no variables
+  For any sentence $\phi$, domain $\Delta$, and $n \in \mathbb{N}_{0}$,
+  \Propagate{$\phi$, $\Delta$, $n$} returns a sentence with no variables
   quantified over $\Delta$.
@@
   form $f = \expr$ with no `function calls'. Suppose that \CompileWithBaseCases
-  terminates for all formulas with at most $n \in \mathbb{N}_{0}$ domains. Let
-  $\phi$ be a formula with $n+1$ domains. By \cref{observation1}, each base case
-  on \autoref{line:loopy} of \cref{alg:compilewithbasecases} has at least one
-  constant. Therefore, by \cref{observation2}, after \autoref{line:propagate},
-  formula $\psi$ has at most $n$ domains. Thus, \autoref{line:final} terminates
-  by the inductive hypothesis, completing the proof that \CompileWithBaseCases
-  terminates for an arbitrary formula with $n+1$ domains.
+  terminates for all sentences with at most $n \in \mathbb{N}_{0}$ domains. Let
+  $\phi$ be a sentence with $n+1$ domains. By \cref{observation1}, each base
+  case on \autoref{line:loopy} of \cref{alg:compilewithbasecases} has at least
+  one constant. Therefore, by \cref{observation2}, after
+  \autoref{line:propagate}, sentence $\psi$ has at most $n$ domains. Thus,
+  \autoref{line:final} terminates by the inductive hypothesis, completing the
+  proof that \CompileWithBaseCases terminates for an arbitrary sentence with
+  $n+1$ domains.
 \end{proof}
@@
   \caption{\protect\Propagate{$\phi$, $\Delta$, $n$}}\label{alg:propagate}
-  \KwIn{formula $\phi$, domain $\Delta$, $n \in \mathbb{N}_{0}$}
-  \KwOut{formula $\phi'$}
+  \KwIn{sentence $\phi$, domain $\Delta$, $n \in \mathbb{N}_{0}$}
+  \KwOut{sentence $\phi'$}
   $\phi' \gets \emptyset$\;
@@
 
-\Cref{alg:propagate}, called \Propagate, modifies the formula $\phi$ based on
+\Cref{alg:propagate}, called \Propagate, modifies the sentence $\phi$ based on
 the assumption that $|\Delta| = n$. When $n=0$, some clauses become vacuously
@@
 replacing all variables quantified over $\Delta$ with constants. (None of the
-formulas examined in this work had $n > 1$.) \Cref{alg:propagate} handles these
+sentences examined in this work had $n > 1$.) \Cref{alg:propagate} handles these
 two cases separately. For a literal or a clause $C$, the set of corresponding
@@
 \end{enumerate}
-Clauses of \cref{type1} are transferred to the new formula $\phi'$ without any
+Clauses of \cref{type1} are transferred to the new sentence $\phi'$ without any
 changes. For clauses of \cref{type2}, $C'$ is empty, so these clauses are
@@
   and $\Doms(y=z) = \{\, \Delta \,\}$. A call to \Propagate{$\{\, C \,\}$,
-    $\Delta$, $3$} would result in the following formula with nine clauses:
+    $\Delta$, $3$} would result in the following sentence with nine clauses:
   \begin{align*}
@@
 Suppose \Propagate is called with arguments $(\phi, \Delta, 0)$, i.e., we are
-simplifying the formula $\phi$ by assuming that the domain $\Delta$ is empty.
+simplifying the sentence $\phi$ by assuming that the domain $\Delta$ is empty.
 Informally, if there is a predicate $P$ in $\phi$ unrelated to $\Delta$,
@@
   $\forall y, z \in \Gamma'\text{. }P(y, z)$. In this case, $P$ is a subset of
-  $\Gamma' \times \Gamma'$. This simplified formula has only one model:
+  $\Gamma' \times \Gamma'$. This simplified sentence has only one model:
   $\{\, P(y, z) \mid y, z \in \Gamma' \,\}$. By including
@@
 C++ program is produced, it can be executed with different command-line
-arguments to compute the model count of the formula for various domain sizes.
+arguments to compute the model count of the sentence for various domain sizes.
 
@@
 \cref{sec:compilation}), \Cranetwo{} has two modes for applying compilation
-rules to formulas: one that uses a greedy search algorithm similar to
+rules to sentences: one that uses a greedy search algorithm similar to
 \textsc{ForcLift} and another that combines greedy and BFS\@.
@@
 \]
-In this formula, we have three predicates $S$, $F$, and $C$ that denote smoking,
-friendship, and cancer, respectively. The first clause states that friends of
-smokers are also smokers, and the second clause asserts that smoking causes
-cancer. Common additions to this formula include making the friendship relation
-symmetric and assigning probabilities to each clause. Finally, we include the
-function-counting problem~\cite{DBLP:conf/kr/DilkasB23}
+In this sentence, we have three predicates $S$, $F$, and $C$ that denote
+smoking, friendship, and cancer, respectively. The first clause states that
+friends of smokers are also smokers, and the second clause asserts that smoking
+causes cancer. Common additions to this sentence include making the friendship
+relation symmetric and assigning probabilities to each clause. Finally, we
+include the function-counting problem~\cite{DBLP:conf/kr/DilkasB23}
 \[
@@
 more than two variables, depending on the formulation and the capabilities of
-the algorithm. Lastly, the \bijections{} benchmark is an example of a formula
+the algorithm. Lastly, the \bijections{} benchmark is an example of a sentence
 that \textsc{FastWFOMC} can handle but \textsc{ForcLift} cannot.
@@
 Based on our experiments, which algorithm should be used in practice? If the
-formula can be handled by \textsc{ForcLift} and the domain sizes are reasonably
+sentence can be handled by \textsc{ForcLift} and the domain sizes are reasonably
 small, \textsc{ForcLift} is likely the fastest algorithm. In other situations,
@@
 \textsc{FastWFOMC} regardless of domain size, provided both algorithms can
-handle the formula.
+handle the sentence.
 
@@
 results demonstrate that \Cranetwo{} can scale to larger domain sizes than
-\textsc{FastWFOMC} while supporting a wider range of formulas than
+\textsc{FastWFOMC} while supporting a wider range of sentences than
 \textsc{ForcLift}. The ability to efficiently handle large domain sizes is
@@
 comparison of FOMC algorithms to better understand their comparative performance
-across various formulas. The capabilities of \Cranetwo{} could also be
+across various sentences. The capabilities of \Cranetwo{} could also be
 characterised theoretically, e.g., by proving completeness for logic fragments
@@
 can be further analysed using fine-grained complexity, which would provide more
-detailed insights into the computational demands of different formulas.
+detailed insights into the computational demands of different sentences.
 

### 2025-02-06 doc/technical_appendix/technical_appendix.tex
Ditto for the appendix

@@
 \crefalias{formula}{equation}
-\crefname{formula}{Formula}{Formulas}
+\crefname{formula}{Sentence}{Sentences}
 \creflabelformat{formula}{#2\textup{(#1)}#3}
@@
 } P(x, y) \lor x = y$. \FO{} is also the only logic to support constants,
-formulas with more than two variables, and the equality predicate. While we do
+sentences with more than two variables, and the equality predicate. While we do
 not explicitly refer to sorts in subsequent sections of this paper, the
@@
 \begin{remark*}
-  In the case of \textsc{ForcLift} and its extensions, support for a formula as
-  valid input does not imply that the algorithm can compile the formula into a
+  In the case of \textsc{ForcLift} and its extensions, support for a sentence as
+  valid input does not imply that the algorithm can compile the sentence into a
   circuit or graph suitable for lifted model counting. However, it is known that
-  \textsc{ForcLift} compilation is guaranteed to succeed on any \FO{} formula
+  \textsc{ForcLift} compilation is guaranteed to succeed on any \FO{} sentence
   without constants and with at most two
@@
 Compared to \FO{}, \Ctwo{} and \UFO{} lack support for constants, the equality
-predicate, multiple domains, and formulas with more than two variables. The
+predicate, multiple domains, and sentences with more than two variables. The
 advantage that \Ctwo{} brings over \FO{} is the inclusion of \emph{counting
@@
 
-For \bijections{}, the equivalent formula in \Ctwo{} is
+For \bijections{}, the equivalent sentence in \Ctwo{} is
 \[
@@
 \]
-Similarly, in \UFO{} the same formula can be written as
+Similarly, in \UFO{} the same sentence can be written as
 \[

### 2025-02-06 doc/paper/paper.tex
Improve the introduction

@@
 \section{Introduction}
-
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item We would like to clarify that the main contribution of this work
-          consists of everything needed to complement recursive function
-          definitions with the necessary base cases. This process includes
-          identifying the base cases and their corresponding sentences,
-          transforming them (including applying a new smoothing procedure), and
-          recursively reusing Crane. C++ code generation, although relatively
-          straightforward, is crucial for the usability of the algorithm.
-    \item Focus more on current work
-  \end{itemize}
-}
 
@@
 
-In \cref{sec:preliminaries}, we cover some preliminaries, and in
-\cref{sec:main}, we detail all our technical contributions. Finally, in
-\cref{sec:experiments}, we present our experimental results, demonstrating
-\Cranetwo{}'s performance compared to other FOMC algorithms, and, in
-\cref{sec:conclusion}, we conclude the paper by discussing promising avenues for
+The paper is structured as follows. \Cref{sec:preliminaries} covers the
+necessary preliminaries including notation, terminology, and background
+information about (W)FOMC and FOKC\@. \Cref{sec:main} describes all aspects of
+\Cranetwo{}:
+\begin{itemize}
+  \item its overall structure and interactions with \textsc{Crane},
+  \item how we identify a sufficient set of base cases for a recursive function,
+  \item how we construct the sentence that `describes' each base case, and
+  \item how function definitions are compiled into a C++ program with caching
+        mechanisms that ensure efficiency.
+\end{itemize}
+Then, \cref{sec:experiments} presents our experimental results, demonstrating
+\Cranetwo{}'s performance compared to other FOMC algorithms. Finally,
+\cref{sec:conclusion} concludes the paper by discussing promising avenues for
 future work.

### 2025-02-06 doc/paper/paper.tex
(Possibly) final major improvements to the paper itself

@@
 
-We end this section by proving that \CompileWithBaseCases terminates since each
-recursive call on \autoref{line:final} reduces the number of domains in the
-sentence.
+We end this section by bounding the recursion depth of the \CompileWithBaseCases
+procedure, thus proving that the algorithm terminates.
 
 \begin{theorem}
-  Given any \FO{} sentence $\phi$, \CompileWithBaseCases{$\phi$} terminates.
+  Let $\phi$ be an \FO{} sentence with $n$ domains. Then the maximum recursion
+  depth of \CompileWithBaseCases{$\phi$} is $n$.
 \end{theorem}
-
-\todo[inline]{Reformulate the theorem above into an upper bound (as I informally
-  mention earlier in the text)}
 
@@
 \begin{proof}
-  We proceed by induction on the number of domains that variables in $\phi$ are
-  quantified over. If there are no domains, then $\phi$ is essentially a
+  We proceed by induction on $n$. If $n=0$, then $\phi$ is essentially a
   propositional formula, and \textsc{Crane} compiles it into an equation of the
-  form $f = \expr$ with no `function calls'. Suppose that \CompileWithBaseCases
-  terminates for all sentences with at most $n \in \mathbb{N}_{0}$ domains. Let
-  $\phi$ be a sentence with $n+1$ domains. By \cref{observation1}, each base
-  case on \autoref{line:loopy} of \cref{alg:compilewithbasecases} has at least
-  one constant. Therefore, by \cref{observation2}, after
-  \autoref{line:propagate}, sentence $\psi$ has at most $n$ domains. Thus,
-  \autoref{line:final} terminates by the inductive hypothesis, completing the
-  proof that \CompileWithBaseCases terminates for an arbitrary sentence with
-  $n+1$ domains.
+  form $f = \expr$ with no `function calls'. Suppose that---for all sentences
+  with at most $n$ domains---\CompileWithBaseCases terminates with a recursion
+  depth of at most $n$. Let $\phi$ be a sentence with $n+1$ domains. By
+  \cref{observation1}, each base case on \autoref{line:loopy} of
+  \cref{alg:compilewithbasecases} has at least one constant. Therefore, by
+  \cref{observation2}, after \autoref{line:propagate}, sentence $\psi$ has at
+  most $n$ domains. Thus, \autoref{line:final} terminates with a recursion depth
+  of at most $n$ by the inductive hypothesis, completing the inductive proof.
 \end{proof}
@@
 characterised theoretically, e.g., by proving completeness for logic fragments
-liftable by other algorithms. Additionally, the efficiency of FOMC algorithms
-can be further analysed using fine-grained complexity, which would provide more
-detailed insights into the computational demands of different sentences.
-
-\todo[inline]{Cite a bunch of papers for the liftable fragments.}
+liftable by other
+algorithms~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/TothK23,DBLP:journals/ai/BremenK23}.
+Additionally, the efficiency of FOMC algorithms can be further analysed using
+fine-grained complexity, which would provide more detailed insights into the
+computational demands of different sentences.
 

### 2025-02-06 doc/paper/paper.tex
Complete technical appendix (barring minor editing)

@@
 \newcommand{\expr}{\mathtt{expr}}
-\newcommand{\FO}{$\mathsf{FO}$}
 \newcommand{\Cranetwo}{\textsc{Gantry}}
@@
 \begin{definition}[Structure, model]\label{def:model}
-  Let $\phi$ be a sentence in \FO{}. For each predicate $P/n$ in $\phi$, let
+  Let $\phi$ be a sentence. For each predicate $P/n$ in $\phi$, let
   ${(\Delta_{i}^{P})}_{i=1}^{n}$ be a list of the corresponding domains. Let
@@
 
+% TODO: maybe itemize?
 \begin{definition}[WFOMC instance]\label{def:instance}
-  A \emph{WFOMC instance} comprises: a sentence $\phi$ in \FO{}, two (rational)
+  A \emph{WFOMC instance} comprises: a sentence $\phi$, two (rational)
   \emph{weights} $w^{+}(P)$ and $w^{-}(P)$ assigned to each predicate $P$ in
@@
 As our work builds on \textsc{Crane}, in this section we will briefly outline
-the steps \textsc{Crane} goes through to compile an \FO{} sentence into a set of
+the steps \textsc{Crane} goes through to compile a sentence into a set of
 function definitions. We divide the inner workings of the algorithm into two
@@
 
-The goal of this stage is to transform an arbitrary \FO{} sentence into the
-format described in \cref{sec:logic}, most importantly by eliminating
-existential quantifiers. For example, the first conjunct of
-\cref{eq:bijections}, i.e.,
+The goal of this stage is to transform an arbitrary sentence into the format
+described in \cref{sec:logic}, most importantly by eliminating existential
+quantifiers. For example, the first conjunct of \cref{eq:bijections}, i.e.,
 \begin{equation}\label[formula]{eq:skolemizationinitial}
@@
 \begin{theorem}
-  Let $\phi$ be an \FO{} sentence with $n$ domains. Then the maximum recursion
-  depth of \CompileWithBaseCases{$\phi$} is $n$.
+  Let $\phi$ be a sentence with $n$ domains. Then the maximum recursion depth of
+  \CompileWithBaseCases{$\phi$} is $n$.
 \end{theorem}
@@
 
+% TODO: maybe turn the footnote into a remark?
+
 \begin{example}
@@
 Our empirical evaluation sought to compare the runtime performance of
-{\Cranetwo} with the current state of the art, namely \textsc{FastWFOMC} and
-\textsc{ForcLift}. Our experiments involve two versions of \Cranetwo{}:
-\Cranegreedy{} and \Cranebfs{}. Like its predecessor (see
-\cref{sec:compilation}), \Cranetwo{} has two modes for applying compilation
-rules to sentences: one that uses a greedy search algorithm similar to
-\textsc{ForcLift} and another that combines greedy and BFS\@.
+{\Cranetwo} with the current state of the art, namely
+\textsc{FastWFOMC}\footnote{\url{https://github.com/jan-toth/FastWFOMC.jl}}~\cite{DBLP:conf/kr/TothK24,DBLP:conf/uai/BremenK21}
+and \textsc{ForcLift}\footnote{\url{https://github.com/UCLA-StarAI/Forclift}}.
+Our experiments involve two versions of \Cranetwo{}: \Cranegreedy{} and
+\Cranebfs{}. Like its predecessor (see \cref{sec:compilation}), \Cranetwo{} has
+two modes for applying compilation rules to sentences: one that uses a greedy
+search algorithm similar to \textsc{ForcLift} and another that combines greedy
+and BFS\@.
 
@@
 benchmark is the bijection-counting problem from \cref{example:bijections}. The
-next benchmark is a variant of the well-known \friends{} Markov logic
+second benchmark is a variant of the well-known \friends{} Markov logic
 network~\cite{DBLP:conf/aaai/SinglaD08,DBLP:conf/uai/BroeckCD12}, which can be
@@
 \]
-as our last benchmark. Here, predicate $P$ is defined as a function from
+as our third benchmark. Here, predicate $P$ is defined as a function from
 $\Gamma$ to $\Delta$. The first clause asserts that each $x$ must have at least
@@
 
+\begin{remark*}
+  For completeness, the technical appendix includes translations of these
+  sentences to logics relevant to other (W)FOMC algorithms.
+\end{remark*}
+
+% TODO: this paragraph might not make any sense without the technical appendix
 The three benchmarks cover a wide range of possibilities. The \friends{}
-benchmark uses multiple predicates and can be expressed in \FO{} using two
-variables without cardinality constraints or counting quantifiers. The
-\functions{} benchmark, on the other hand, can still be handled by all the
-algorithms, but it requires cardinality constraints, counting quantifiers, or
-more than two variables, depending on the formulation and the capabilities of
-the algorithm. Lastly, the \bijections{} benchmark is an example of a sentence
-that \textsc{FastWFOMC} can handle but \textsc{ForcLift} cannot.
+benchmark uses multiple predicates and can be expressed using two variables
+without cardinality constraints or counting quantifiers. The \functions{}
+benchmark, on the other hand, can still be handled by all the algorithms, but it
+requires cardinality constraints, counting quantifiers, or more than two
+variables, depending on the formulation and the capabilities of the algorithm.
+Lastly, the \bijections{} benchmark is an example of a sentence that
+\textsc{FastWFOMC} can handle but \textsc{ForcLift} cannot.
 

### 2025-02-06 doc/technical_appendix/technical_appendix.tex
Complete technical appendix (barring minor editing)

@@
     to those of the form $P(\mathbf{t})$ for a predicate $P/n$ and an $n$-tuple
-    of terms $\mathbf{t}$. Here: $k$ and $m$ are non-negative integers, with the
-    latter depending on the domain size, $P$ represents a predicate, and $x$ and
-    $y$ are terms. }\label{tbl:logics}
+    of terms $\mathbf{t}$. Here $k$ and $m$ are non-negative integers, with the
+    latter depending on the domain size, $P$ is a predicate, and $x$ and $y$ are
+    terms. }\label{tbl:logics}
 \end{table}
 
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item Reference the table
-    \item Make sure the rest of the paper doesn't refer to these logics (or
-          describe examples in them)
-    \item Move the URLs to the main text (and make sure that each algorithm name
-          is combined with a citation at least once)
-    \item Later (probably) move this to a different file
-  \end{itemize}
-}
-
-\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
-
 There are three first-order logics commonly used in FOMC: \FO{}, \Ctwo{}, and
-\UFO{}. First, \FO{} is the input format for
-\textsc{ForcLift}\footnote{\url{https://github.com/UCLA-StarAI/Forclift}} and
-its extensions
-\textsc{Crane}\footnote{\url{https://doi.org/10.5281/zenodo.8004077}} and
-\Cranetwo{}. Second, \Ctwo{} is often used in the literature on
-\textsc{FastWFOMC}\footnote{\url{https://github.com/jan-toth/FastWFOMC.jl}} and
+\UFO{}. \Cref{tbl:logics} summarises the key differences among them. \FO{} is
+the input format for \textsc{ForcLift} and its extensions \textsc{Crane} and
+\Cranetwo{}. \Ctwo{} is often used in the literature on \textsc{FastWFOMC} and
 related methods~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}.
@@
 are equal if and only if they are the same constant~\cite{DBLP:books/aw/RN2020}.
-
-\renewcommand*{\thefootnote}{\arabic{footnote}}
 
@@
 sentences with more than two variables, and the equality predicate. While we do
-not explicitly refer to sorts in subsequent sections of this paper, the
-many-sorted nature of \FO{} is paramount to the algorithms presented therein.
+not explicitly refer to sorts in the paper, the many-sorted nature of \FO{} is
+paramount to the algorithms presented therein.
 
@@
 
-\subsection{Our Benchmarks in \Ctwo{} and \UFO{}}
-
-\todo[inline,caption={}]{
-  \begin{itemize}
-    \item An introductory paragraph
-    \item Figure out the right order in which the information below should be
-          presented
-    \item Make the text below coherent
-    \item Refer to it in the main text (and make sure the reference sticks when
-          I transfer this to a separate file)
-  \end{itemize}
-}
-
-\friends{} in \Ctwo{} and \UFO{} is the same as in \FO{}.
-
-For \bijections{}, the equivalent sentence in \Ctwo{} is
+\paragraph*{Our Benchmarks in \Ctwo{} and \UFO{}}
+For completeness and reproducibility, let us translate the benchmark sentences
+from \FO{} to \Ctwo{} and \UFO{}. As \friends{} is a relatively simple sentence,
+it remains the same in \Ctwo{} and \UFO{}. For \functions{}, in \Ctwo{} one
+would write
+\[
+  \forall x \in \Delta\text{. }\exists^{=1} y \in \Delta\text{. }P(x, y).
+\]
+In \UFO{}, the same could be written as
+\begin{equation}\label[formula]{eq:functions1}
+  (\forall x, y \in \Delta\text{. }S(x) \lor \neg P(x, y)) \land (|P| = |\Delta|),
+\end{equation}
+where $w^{-}(S) = -1$. Although \cref{eq:functions1} has more models compared to
+its counterpart in \Ctwo{}, the negative weight $w^{-}(S) = -1$ makes some of
+the terms in the definition of WFOMC cancel out. The translation of
+\bijections{} is similar to that of \functions{}. In \Ctwo{}, one could write
 \[
@@
 
-For \functions{}, in \Ctwo{} one would write $\forall x \in \Delta\text{.
-}\exists^{=1} y \in \Delta\text{. }P(x, y)$. In \UFO{}, the same could be
-written as
-\begin{equation}\label[formula]{eq:functions1}
-  (\forall x, y \in \Delta\text{. }S(x) \lor \neg P(x, y)) \land (|P| = |\Delta|),
-\end{equation}
-where $w^{-}(S) = -1$. Although \cref{eq:functions1} has more models compared to
-its counterpart in \Ctwo{}, the negative weight $w^{-}(S) = -1$ makes some of
-the terms in the definition of WFOMC cancel out.
-
 \bibliography{../paper/paper.bib}

### 2025-02-10 doc/technical_appendix/technical_appendix.tex
Lots of editing

@@
 \documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate]{lipics-v2021}
-%This is a template for producing LIPIcs articles. 
-%See lipics-v2021-authors-guidelines.pdf for further information.
-%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
-%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
-%for section-numbered lemmas etc., use "numberwithinsect"
-%for enabling cleveref support, use "cleveref"
-%for enabling autoref support, use "autoref"
-%for anonymousing the authors (e.g. for double-blind review), add "anonymous"
-%for enabling thm-restate support, use "thm-restate"
-%for enabling a two-column layout for the author/affilation part (only applicable for > 6 authors), use "authorcolumns"
-%for producing a PDF according the PDF/A standard, add "pdfa"
-
-\pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
-\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
-
-%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory
-
-\bibliographystyle{plainurl}% the mandatory bibstyle
+\pdfoutput=1
+\hideLIPIcs
+\bibliographystyle{plainurl}
 
@@
 
-\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
+\relatedversion{}
 
-%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
-%\supplementdetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g.
-Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional
-
-%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors.
-Please enter author specific funding statements as fifth argument of the \author macro.
-
-%\acknowledgements{I want to thank \dots}%optional
-
-%\nolinenumbers %uncomment to disable line numbering
-
-%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \EventEditors{John Q. Open and Joan R. Access}
@@
 \ArticleNo{23}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \usepackage{pifont}
-\usepackage[backgroundcolor=lightgray]{todonotes} % TODO: temporary
 
@@
 \crefalias{formula}{equation}
-\crefname{formula}{Sentence}{Sentences}
+\crefname{formula}{sentence}{sentences}
 \creflabelformat{formula}{#2\textup{(#1)}#3}
@@
   \caption{A comparison of the three logics used in FOMC\@. The
-    2\textsuperscript{nd}--5\textsuperscript{th} columns refer to: the number of
+    2\textsuperscript{nd}--5\textsuperscript{th} columns refer to the number of
     sorts, support for constants, the maximum number of variables, and supported
@@
     to those of the form $P(\mathbf{t})$ for a predicate $P/n$ and an $n$-tuple
-    of terms $\mathbf{t}$. Here $k$ and $m$ are non-negative integers, with the
-    latter depending on the domain size, $P$ is a predicate, and $x$ and $y$ are
-    terms. }\label{tbl:logics}
+    of terms $\mathbf{t}$. Here, $k$ and $m$ are non-negative integers, where
+    $m$ depends on the domain size, $P$ is a predicate, and $x$ and $y$ are
+    terms.}\label{tbl:logics}
 \end{table}
 
-There are three first-order logics commonly used in FOMC: \FO{}, \Ctwo{}, and
+FOMC commonly utilises three types of first-order logic: \FO{}, \Ctwo{}, and
 \UFO{}. \Cref{tbl:logics} summarises the key differences among them. \FO{} is
@@
 related methods~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}.
-Finally, \UFO{} is the input format supported by the most recent implementation
-of \textsc{FastWFOMC}~\cite{DBLP:conf/kr/TothK24}. All three logics are
+(Note that no algorithm accepts \Ctwo{} as input.) Finally, \UFO{} is the input
+format supported by the most recent implementation of
+\textsc{FastWFOMC}~\cite{DBLP:conf/kr/TothK24}. All three logics are
 function-free, and domains are always assumed to be finite. As usual, we
@@
 
-In \FO{}, each term is assigned to a \emph{sort}, and each predicate $P/n$ is
-assigned to a sequence of $n$ sorts. Each sort has its corresponding domain.
-These assignments to sorts are typically left implicit and can be reconstructed
-from the quantifiers. For example, $\forall x,y \in \Delta\text{. }P(x, y)$
-implies that variables $x$ and $y$ have the same sort. On the other hand,
+In \FO{}, each term has a designated \emph{sort}, and each predicate $P/n$
+corresponds to a sequence of $n$ sorts. Each sort has its corresponding domain.
+These assignments to sorts are typically left implicit and follow from the
+quantifiers, e.g., $\forall x,y \in \Delta\text{. }P(x, y)$ implies that the
+variables $x$ and $y$ have the same sort. On the other hand,
 $\forall x \in \Delta\text{. }\forall y \in \Gamma\text{. } P(x, y)$ implies
@@
   valid input does not imply that the algorithm can compile the sentence into a
-  circuit or graph suitable for lifted model counting. However, it is known that
-  \textsc{ForcLift} compilation is guaranteed to succeed on any \FO{} sentence
-  without constants and with at most two
+  circuit or graph suitable for lifted model counting. However,
+  \textsc{ForcLift} compilation always succeeds on any \FO{} sentence without
+  constants and with at most two
   variables~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/kr/BroeckMD14}.
@@
 For completeness and reproducibility, let us translate the benchmark sentences
-from \FO{} to \Ctwo{} and \UFO{}. As \friends{} is a relatively simple sentence,
-it remains the same in \Ctwo{} and \UFO{}. For \functions{}, in \Ctwo{} one
-would write
+from \FO{} to \Ctwo{} and \UFO{}. Since \friends{} is a relatively simple
+sentence, it remains the same in \Ctwo{} and \UFO{}. For \functions{}, in
+\Ctwo{}, one would write
 \[
@@
 \]
-In \UFO{}, the same could be written as
+In \UFO{}, the equivalent formulation is
 \begin{equation}\label[formula]{eq:functions1}
@@
 \end{equation}
-where $w^{-}(S) = -1$. Although \cref{eq:functions1} has more models compared to
-its counterpart in \Ctwo{}, the negative weight $w^{-}(S) = -1$ makes some of
-the terms in the definition of WFOMC cancel out. The translation of
-\bijections{} is similar to that of \functions{}. In \Ctwo{}, one could write
+where $w^{-}(S) = -1$. Although \cref{eq:functions1} has more models than its
+counterpart in \Ctwo{}, the negative weight $w^{-}(S) = -1$ causes some of the
+terms in the definition of WFOMC to cancel out. The translation of \bijections{}
+is similar to that of \functions{}. In \Ctwo{}, one could write
 \[
@@
 \]
-Similarly, in \UFO{} the same sentence can be written as
+Similarly, in \UFO{}, the equivalent formulation is
 \[

### 2025-05-31 doc/paper_original/paper.tex
Move things around

--- 2025-02-06 doc/paper/paper.tex
@@
 
-\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
-
-%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
-%\supplementdetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g.
-Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional
+\relatedversion{}
 
@@
 
-%\nolinenumbers %uncomment to disable line numbering
-
-%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \EventEditors{John Q. Open and Joan R. Access}
@@
 \usepackage{microtype}
-\usepackage[backgroundcolor=lightgray]{todonotes} % TODO: temporary
 \usepackage{mathtools}
@@
 \crefalias{clause}{equation}
-\crefname{clause}{Clause}{Clauses}
+\crefname{clause}{clause}{clauses}
 \creflabelformat{clause}{#2\textup{(#1)}#3}
 \crefalias{formula}{equation}
-\crefname{formula}{Sentence}{Sentence}
+\crefname{formula}{sentence}{sentences}
 \creflabelformat{formula}{#2\textup{(#1)}#3}
@@
 
-\todo[inline,caption={}]{
-  For the entire paper:
-  \begin{itemize}
-    \item 15 pages excluding references
-    \item Make sure all the internal references (e.g., to examples) are still
-          valid
-    \item Maybe add extra references to subsections
-    \item When submitting: go through the rest of formatting instructions (in
-          GTD)
-  \end{itemize}
-}
 \section{Introduction}
-
-% 1. What is the problem?
-% 2. Why is it interesting and important?
 
@@
 
-% 3. Why is it hard? (E.g., why do naive approaches fail?)
-
 The complexity of FOMC is generally measured by \emph{data complexity}, with a
-sentence classified as \emph{liftable} if it can be solved in polynomial time
+sentence classified as \emph{liftable} if it admits a polynomial-time solution
 relative to the domain size~\cite{DBLP:conf/starai/JaegerB12}. While all
@@
 extend to all sentences, identifying an unliftable sentence with three
-variables. Recent work has further extended the liftable fragment with
-additional axioms~\cite{DBLP:conf/aaai/TothK23,DBLP:journals/ai/BremenK23} and
-counting quantifiers~\cite{DBLP:journals/jair/Kuzelka21}, expanding our
-understanding of liftability.
-
-% 4. Why hasn't it been solved before? (Or, what's wrong with previous proposed
-% solutions? How does mine differ?)
+variables. Recent work has extended the liftable fragment with additional
+axioms~\cite{DBLP:conf/aaai/TothK23,DBLP:journals/ai/BremenK23} and counting
+quantifiers~\cite{DBLP:journals/jair/Kuzelka21}, expanding our understanding of
+liftability.
 
@@
 sampling~\cite{DBLP:journals/cacm/GogateD16}. (See the technical appendix for a
-more detailed comparison of the state-of-the-art FOMC algorithms.) Among these,
-FOKC-based algorithms are particularly prominent, transforming sentences into
-structured representations such as circuits or graphs. Even when multiple
-algorithms are able to solve the same instance, FOKC algorithms are known to
-find polynomial-time solutions, where the polynomial has a lower degree compared
-to other approaches~\cite{DBLP:conf/kr/DilkasB23}. The recently developed
-ability of a FOKC algorithm to formulate solutions in terms of recursive
-functions~\cite{DBLP:conf/kr/DilkasB23} is also noteworthy as the only other
+more detailed comparison of the state-of-the-art FOMC algorithms.) FOKC-based
+algorithms are particularly prominent, transforming sentences into structured
+representations such as circuits or graphs. Even when multiple algorithms can
+solve the same instance, FOKC algorithms are known to find polynomial-time
+solutions where the polynomial has a lower degree than other
+approaches~\cite{DBLP:conf/kr/DilkasB23}. The recently developed ability of a
+FOKC algorithm to formulate solutions in terms of recursive
+functions~\cite{DBLP:conf/kr/DilkasB23} is also noteworthy since the only other
 proposed alternative is to guess recursive
@@
 algorithms include \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} and its
-successor \textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23}.
-
-% 5. What are the key components of my approach and results? Also include any
-% specific limitations.
+extension \textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23}.
 
@@
 model counts and introduced recursive functions without proper base cases,
-making it more complex to use. To address these shortcomings, we present
+making it more difficult to use. To address these shortcomings, we present
 \Cranetwo{}, a fully automated FOMC algorithm that overcomes the constraints of
 its predecessor. \Cranetwo{} can handle domain sizes over \num{500000} times
-larger than previous algorithms and simplifies the user experience by
-automatically handling base cases and compiling function definitions into
+larger than those of previous algorithms and simplifies the user experience by
+automatically managing base cases and compiling function definitions into
 efficient C++ programs.
@@
 The paper is structured as follows. \Cref{sec:preliminaries} covers the
-necessary preliminaries including notation, terminology, and background
+necessary preliminaries, including notation, terminology, and background
 information about (W)FOMC and FOKC\@. \Cref{sec:main} describes all aspects of
@@
   \item how we identify a sufficient set of base cases for a recursive function,
-  \item how we construct the sentence that `describes' each base case, and
-  \item how function definitions are compiled into a C++ program with caching
+  \item how we construct the sentence that describes each base case, and
+  \item how we compile function definitions into a C++ program with caching
         mechanisms that ensure efficiency.
@@
 We begin this section by describing some notation that we will use throughout
-the paper. Then, in \cref{sec:logic,sec:fomc} respectively, we introduce the
-basic terminology of first-order logic and formally define (W)FOMC\@.
-\Cref{sec:crane} outlines the principles of FOKC, particularly in the context of
-\textsc{Crane}. Finally, in \cref{sec:algebra}, we introduce the algebraic
-terminology used to describe the output of \textsc{Crane}, i.e., functions and
-equations that define them.
+the paper. Then, in \cref{sec:logic,sec:fomc}, we introduce the basic
+terminology of first-order logic and formally define (W)FOMC\@. \Cref{sec:crane}
+outlines the principles of FOKC, particularly in the context of \textsc{Crane}.
+Finally, in \cref{sec:algebra}, we introduce the algebraic terminology used to
+describe the output of \textsc{Crane}, i.e., functions and equations that define
+them.
 
@@
 
-In this section, we will review the basic concepts of first-order logic as they
-are used in FOKC algorithms. We begin by introducing the format used internally
-by \textsc{ForcLift} and its descendants. Afterwards, we provide a high-level
-description of how an arbitrary sentence in first-order logic is transformed
-into this internal format.
+This section reviews the basic concepts of first-order logic used in FOKC
+algorithms. We focus specifically on the format used internally by
+\textsc{ForcLift} and its descendants. See \cref{sec:preprocessing} for a brief
+overview of how \Cranetwo{} transforms an arbitrary sentence in first-order
+logic into this internal format.
 
@@
 either $P(t_{1}, \dots, t_{m})$ (i.e., $P(\mathbf{t})$) for some predicate $P$
-and terms $t_{1}, \dots, t_{m}$ or $x=y$ for some terms $x$ and $y$. The
+and terms $t_{1}, \dots, t_{m}$, or $x=y$ for some terms $x$ and $y$. The
 \emph{arity} of a predicate is the number of arguments it takes, i.e., $m$ in
@@
 \emph{positive} literal) or its negation (i.e., a \emph{negative} literal). An
-atom is \emph{ground} if it contains no variables, i.e., only constants. A
+atom containing no variables, only constants, is called \emph{ground}. A
 \emph{clause} is of the form $\forall x_{1} \in \Delta_{1}\text{.
@@
 }\phi(x_{1}, x_{2}, \dots, x_{n})$, where $\phi$ is a disjunction of literals
-that only contain variables $x_{1}, \dots, x_{n}$ (and any constants). We say
-that a clause is a \emph{(positive) unit clause} if there is only one literal
-with a predicate, and it is a positive literal. Finally, a \emph{sentence} is a
-conjunction of clauses. Throughout the paper, we will use set-theoretic
-notation, interpreting a sentence as a set of clauses and a clause as a set of
-literals.
+that contain only the variables $x_{1}, \dots, x_{n}$ (and any constants). We
+say that a clause is a \emph{(positive) unit clause} if there is only one
+literal with a predicate, and it is a positive literal. Finally, a
+\emph{sentence} is a conjunction of clauses. Throughout the paper, we will use
+set-theoretic notation, interpreting a sentence as a set of clauses and a clause
+as a set of literals.
 
 \begin{remark*}
-  Conforming with previous work~\cite{DBLP:conf/ijcai/BroeckTMDR11}, the
-  definition of a clause includes universal quantifiers for all variables
-  within. While it is possible to rewrite the entire sentence with all
-  quantifiers at the front~\cite{hinman2018fundamentals}, the format we describe
-  has proven itself convenient to work with.
+  Conforming to previous work~\cite{DBLP:conf/ijcai/BroeckTMDR11}, the
+  definition of a clause includes universal quantifiers for all its variables.
+  While it is possible to rewrite the entire sentence with all quantifiers at
+  the front, the format we describe has proven convenient for practical use.
 \end{remark*}
@@
 
-In this section, we will formally define FOMC and its weighted variant. Note
-that, although this work focuses on FOMC, for sentences with existential
-quantifiers, computing the FOMC using \Cranetwo{} requires the use of WFOMC\@.
-For such sentences, preprocessing (described in \cref{sec:crane}) introduces
-predicates with non-unary weights that must be accounted for to compute the
-correct model count.
+In this section, we will formally define FOMC and its weighted variant. Although
+this work focuses on FOMC, computing the FOMC using \Cranetwo{} requires using
+WFOMC for sentences with existential quantifiers. For such sentences,
+preprocessing (described in \cref{sec:preprocessing}) introduces predicates with
+non-unary weights that must be accounted for to compute the correct model count.
 
@@
   $\sigma$ be a map from the domains of $\phi$ to their interpretations as
-  finite sets such that the sets are pairwise disjoint, and the constants in
-  $\phi$ are included in the corresponding domains. A \emph{structure} of $\phi$
-  is a set $M$ of ground literals defined by adding to $M$ either
-  $P(\mathbf{t})$ or $\neg P(\mathbf{t})$ for every predicate $P/n$ in $\phi$
-  and $n$-tuple $\mathbf{t} \in \prod_{i=1}^{n} \sigma(\Delta_{i}^{P})$. A
-  structure is a \emph{model} if it makes $\phi$ valid.
+  finite sets, ensuring the sets are pairwise disjoint and contain the
+  corresponding constants from $\phi$. A \emph{structure} of $\phi$ is a set $M$
+  of ground literals defined by adding to $M$ either $P(\mathbf{t})$ or
+  $\neg P(\mathbf{t})$ for every predicate $P/n$ in $\phi$ and every $n$-tuple
+  $\mathbf{t} \in \prod_{i=1}^{n} \sigma(\Delta_{i}^{P})$. A structure is a
+  \emph{model} if it makes $\phi$ valid.
 \end{definition}
@@
   \end{equation}
-  Let $\sigma$ be defined as $\sigma(\Gamma) \coloneqq \{\, 1, 2\,\}$, and
-  $\sigma(\Delta) \coloneqq \{\,a, b\,\}$. Then \cref{eq:bijections} has two
-  models:
+  Let $\sigma$ be defined as $\sigma(\Gamma) \coloneqq \{\, 1, 2\,\}$ and
+  $\sigma(\Delta) \coloneqq \{\,a, b\,\}$. \Cref{eq:bijections} has two models:
   \[
@@
 \begin{remark*}
-  The distinctness of domains is important in two ways. First, in terms of
+  The distinctness of domains is significant in two respects. First, in terms of
   expressiveness, a clause such as $\forall x \in \Delta\text{. }P(x, x)$ is
-  valid if predicate $P$ is defined over two copies of the same domain and
-  invalid otherwise. Second, having more distinct domains makes the problem more
+  valid if predicate $P$ operates over two copies of the same domain and invalid
+  otherwise. Second, having more distinct domains makes the problem more
   decomposable for the FOKC algorithm. With distinct domains, the algorithm can
@@
 
-% TODO: maybe itemize?
 \begin{definition}[WFOMC instance]\label{def:instance}
-  A \emph{WFOMC instance} comprises: a sentence $\phi$, two (rational)
-  \emph{weights} $w^{+}(P)$ and $w^{-}(P)$ assigned to each predicate $P$ in
-  $\phi$, and $\sigma$ as described in \cref{def:model}. Unless specified
-  otherwise, we assume all weights to be equal to 1.
+  A \emph{WFOMC instance} comprises:
+  \begin{itemize}
+    \item a sentence $\phi$,
+    \item two (rational) \emph{weights} $w^{+}(P)$ and $w^{-}(P)$ assigned to
+          each predicate $P$ in $\phi$, and
+    \item $\sigma$ as described in \cref{def:model}.
+  \end{itemize}
+  Unless specified otherwise, we assume all weights are equal to 1.
 \end{definition}
@@
 
-As our work builds on \textsc{Crane}, in this section we will briefly outline
+As our work builds on \textsc{Crane}, in this section, we will briefly outline
 the steps \textsc{Crane} goes through to compile a sentence into a set of
@@
 
-\subsubsection{Preprocessing}
-
-The goal of this stage is to transform an arbitrary sentence into the format
-described in \cref{sec:logic}, most importantly by eliminating existential
-quantifiers. For example, the first conjunct of \cref{eq:bijections}, i.e.,
+\subsubsection{Preprocessing}\label{sec:preprocessing}
+
+This stage transforms an arbitrary sentence into the format described in
+\cref{sec:logic}, primarily by eliminating existential quantifiers. For example,
+the first conjunct of \cref{eq:bijections}, i.e.,
 \begin{equation}\label[formula]{eq:skolemizationinitial}
@@
 \end{equation}
-where $Z/1$ and $S/1$ are two new predicates with $w^{-}(S) = -1$. One can check
-that the WFOMC of \cref{eq:skolemizationinitial,eq:skolemization} is the same.
+where $Z/1$ and $S/1$ are two new predicates with $w^{-}(S) = -1$. One can
+verify that the WFOMC of \cref{eq:skolemizationinitial,eq:skolemization} is the
+same.
 
@@
 
-At this stage, the preprocessed sentence is compiled into the set $\mathcal{E}$
-of equations and two auxiliary maps $\mathcal{F}$ and $\mathcal{D}$.
-$\mathcal{F}$ maps function names to sentences, and $\mathcal{D}$ maps function
-names and argument indices to domains. $\mathcal{E}$ can contain any number of
-functions, one of which (which we will always denote by $f$) represents the
-solution to the FOMC problem. To compute the FOMC for particular domain sizes,
-$f$ must be evaluated with those domain sizes as arguments. $\mathcal{D}$
-records this correspondence between function arguments and domains.
+After preprocessing, \textsc{Crane} compiles the sentence into the triple
+$(\mathcal{E}, \mathcal{F}, \mathcal{D})$, where $\mathcal{E}$ is the set of
+equations, and $\mathcal{F}$ and $\mathcal{D}$ are auxiliary maps. $\mathcal{F}$
+maps function names to sentences. $\mathcal{D}$ maps function names and argument
+indices to domains. $\mathcal{E}$ can contain any number of functions, one of
+which (which we will always denote as $f$) represents the solution to the FOMC
+problem. Computing the FOMC for specific domain sizes involves invoking $f$ with
+those sizes as inputs. $\mathcal{D}$ records this correspondence between
+function arguments and domains.
 
@@
   where $\Delta^{\top}$ is a newly introduced domain. (We omit the definition of
-  $\mathcal{F}$ as the sentences can get quite verbose.) To compute the number
-  of bijections between two sets of cardinality 3, one would evaluate $f(3, 3)$,
-  however, the definition of $g$ is incomplete: $g$ is a recursive function
-  presented without any base cases. $\mathcal{D}$ encodes that in $f(m, n)$, $m$
-  and $n$ represent $|\Gamma|$ and $|\Delta|$, respectively. Similarly, in
-  $g(l, m)$, $l$ represents $|\Delta^{\top}|$, and $m$ represents $|\Gamma|$.
+  $\mathcal{F}$ as the sentences can become quite verbose.) To compute the
+  number of bijections between two sets of cardinality 3, one would evaluate
+  $f(3, 3)$; however, the definition of $g$ is incomplete: $g$ is a recursive
+  function presented without any base cases. $\mathcal{D}$ encodes that in
+  $f(m, n)$, $m$ and $n$ represent $|\Gamma|$ and $|\Delta|$, respectively.
+  Similarly, in $g(l, m)$, $l$ represents $|\Delta^{\top}|$, and $m$ represents
+  $|\Gamma|$.
 \end{example}
@@
 Compilation is performed primarily by applying \emph{(compilation) rules} to
-sentences. \textsc{Crane} has two modes depending on how the algorithm chooses
-which compilation rule to apply to a sentence (in case several alternatives are
-available). The first option is to use greedy search: there is a list of rules,
-and the first applicable rule is the one that gets used, disregarding all the
-others. The second option is to use a combination of greedy and
-\emph{breadth-first search} (BFS). That is, each compilation rule is identified
-as either greedy or non-greedy. Greedy rules are applied as soon as possible at
-any stage of the compilation process. BFS is executed over all applicable
-non-greedy rules, identifying the solution that can be constructed using the
-smallest number of such rules.
+sentences. \textsc{Crane} has two modes depending on the selection process for
+compilation rules when multiple alternatives are available. The first option is
+to use greedy search: there is a list of rules, and the first applicable rule is
+the one that gets used, disregarding all the others. The second option is to use
+a combination of greedy and \emph{breadth-first search} (BFS). In this approach,
+we classify each compilation rule as greedy or non-greedy. Greedy rules are
+applied as soon as possible at any stage of the compilation process, while BFS
+is executed over all applicable non-greedy rules, identifying the solution that
+necessitates the smallest number of non-greedy rules.
 
@@
 where $f$ is an $n$-ary function, and each $x_{i}$ is an algebraic expression
-consisting of variables and constants. A (function) \emph{signature} is function
-call that contains only variables. Given two function calls $f(\mathbf{x})$ and
-$f(\mathbf{y})$, we say that $f(\mathbf{y})$ \emph{matches} $f(\mathbf{x})$ if
-$x_{i} = y_{i}$ whenever $x_{i}, y_{i} \in \mathbb{N}_{0}$. An \emph{equation}
-is $f(\mathbf{x}) = \expr{}$, where $f(\mathbf{x})$ is a function call.
+consisting of variables and constants. A (function) \emph{signature} is a
+function call that contains only variables. Given two function calls,
+$f(\mathbf{x})$ and $f(\mathbf{y})$, we say that $f(\mathbf{y})$ \emph{matches}
+$f(\mathbf{x})$ if $x_{i} = y_{i}$ whenever $x_{i}, y_{i} \in \mathbb{N}_{0}$.
+An \emph{equation} is $f(\mathbf{x}) = \expr{}$, where $f(\mathbf{x})$ is a
+function call.
 
@@
   Let $f(\mathbf{x})$ be a function call where each $x_{i}$ is either a constant
-  or a variable. Then function call $f(\mathbf{y})$ is a \emph{base case} of
+  or a variable. Then the function call $f(\mathbf{y})$ is a \emph{base case} of
   $f(\mathbf{x})$ if $f(\mathbf{y}) = f(\mathbf{x})\sigma$, where $\sigma$ is a
-  substitution that replaces one or more $x_{i}$ with a constant.
+  substitution that replaces one or more \emph{variable} $x_{i}$'s with a
+  constant while leaving constants unchanged.
 \end{definition}
@@
 \begin{example}
-  In equation $f(m, n) = f(m-1, n) + nf(m-1, n-1)$, the only constant is $1$,
-  and the variables are $m$ and $n$. The equation contains three function calls:
-  one on the left-hand side (LHS), and two on the right-hand side (RHS). The
-  function call on the LHS is a signature. Function calls such as $f(4, n)$,
+  In the equation $f(m, n) = f(m-1, n) + nf(m-1, n-1)$, the only constant is
+  $1$, and the variables are $m$ and $n$. The equation contains three function
+  calls: one on the left-hand side (LHS) and two on the right-hand side (RHS).
+  The function call on the LHS is a signature. Function calls such as $f(4, n)$,
   $f(m, 0)$, and $f(8, 1)$ are all considered base cases of $f(m, n)$ (only some
@@
   \end{tikzpicture}
-  \caption[]{The outline of using \Cranetwo{} to compute the model count of a
-    sentence $\phi$. First, $\phi$ is compiled into a set of equations, which
-    are then used to create a C++ program. This program can be executed with
-    different command line arguments to calculate the model count of $\phi$ for
-    different domain sizes. To accomplish this, the \CompileWithBaseCases
-    procedure uses \textsc{Crane}, algebraic simplification techniques (denoted
-    as \Simplify), and two other auxiliary procedures. }\label{fig:overview}
+  \caption[]{Using \Cranetwo{} to compute the model count of a sentence $\phi$.
+    First, \Cranetwo{} compiles $\phi$ into a set of equations, which form the
+    basis for creating a C++ program. Executing the program with different
+    command line arguments calculates the model count of $\phi$ for various
+    domain sizes. To accomplish this, the \CompileWithBaseCases procedure
+    employs \textsc{Crane}, algebraic simplification techniques (denoted as
+    \Simplify), and two other auxiliary procedures. }\label{fig:overview}
 \end{figure*}
 
-\Cref{fig:overview} provides an overview of \Cranetwo{}'s workflow. Below we
+\Cref{fig:overview} provides an overview of \Cranetwo{}'s workflow. We will
 briefly describe and motivate each procedure before going into more detail in
@@
 itself (and \textsc{Crane}) on other sentences. We prove that the number of such
-recursive calls is upper bounded by the number of domains in the sentences.
+recursive calls is upper bound by the number of domains.
 
@@
 simplification. It is crucial for simplifying, e.g., a sum of $n$ terms, only
-two of which are non-zero. More generally, the equations returned by
-\textsc{Crane} often benefit from easy-to-detect algebraic simplifications such
-as $0 \cdot \text{anything} = 0$ and $\text{anything}^{0} = 1$.
+some of which are non-zero. More generally, the equations returned by
+\textsc{Crane} often benefit from easily detectable algebraic simplifications
+such as $0 \cdot \text{anything} = 0$ and $\text{anything}^{0} = 1$.
 
@@
 to identify a sufficient set of base cases for a given set of equations. We
-prove that the returned set of base cases is sufficient, and the evaluation of
-the resulting function definitions will never get stuck in an infinite loop.
-
-\Cref{sec:propagating} introduces the \Propagate procedure that takes a sentence
-$\phi$, a domain $\Delta$, and $n \in \mathbb{N}_{0}$. It returns $\phi$
-transformed with the assumption that $|\Delta| = n$, introducing $n$ new
-constants and removing all variables quantified over $\Delta$. For example, when
-computing a base case such as $f(0, y)$, \Propagate will significantly simplify
-$\phi$ with the assumption that the domain associated with the first parameter
-of $f$ (i.e., $\mathcal{D}(f, 1)$) is empty. When run on this simplified
-sentence, \CompileWithBaseCases will return the equations for the base case
-$f(0, y)$.
-
-\Cref{sec:smoothing} describes a new kind of \emph{smoothing} used to ensure
-that \Propagate preserves the correct model count. Smoothing is a well-known
+prove that the returned set of base cases ensures that the evaluation of the
+resulting function definitions will never get stuck in an infinite loop.
+
+\Cref{sec:propagating} introduces the \Propagate procedure, which takes a
+sentence $\phi$, a domain $\Delta$, and $n \in \mathbb{N}_{0}$. It returns
+$\phi$ transformed under the assumption that $|\Delta| = n$, with $n$ new
+constants added and all variables quantified over $\Delta$ eliminated. For
+example, when computing a base case such as $f(0, y)$, \Propagate will
+significantly simplify $\phi$ with the assumption that the domain associated
+with the first parameter of $f$ (i.e., $\mathcal{D}(f, 1)$) is empty.
+\CompileWithBaseCases{\Propagate{$\phi$, $\mathcal{D}(f, 1)$, $0$}} will then
+return the equations for the base case $f(0, y)$.
+
+\Cref{sec:smoothing} describes a new \emph{smoothing} procedure that ensures
+\Propagate preserves the correct model count. Smoothing is a well-known
 technique in knowledge compilation algorithms for propositional model
-counting~\cite{darwiche2001tractable}. Although it has been applied to FOMC
-before~\cite{DBLP:conf/ijcai/BroeckTMDR11}, our setting requires a novel
-approach.
-
-\CompileWithBaseCases, together with the other procedures outlined above, return
+counting~\cite{darwiche2001tractable}. Although FOMC algorithms have used
+smoothing before~\cite{DBLP:conf/ijcai/BroeckTMDR11}, our setting requires a
+novel approach.
+
+With the help of other procedures outlined above, \CompileWithBaseCases returns
 a set of equations that fully cover the base cases of all recursive functions.
-While these equations can be interesting and valuable in their own right, the
-users of FOMC algorithms typically expect a numerical answer. Thus,
-\cref{sec:cpp} describes how these equations are compiled into a C++ program
-that can be executed with different command-line arguments to compute the model
-count for different combinations of domain sizes.
+While these equations can be intriguing and valuable in their own right, users
+of FOMC algorithms typically expect a numerical answer. Thus, \cref{sec:cpp}
+describes how \Cranetwo{} compiles these equations into a C++ program that one
+can execute with different command-line arguments to compute the model count for
+various combinations of domain sizes.
 
@@
 \Cref{alg:compilewithbasecases} presents our overall approach for compiling a
-sentence into equations that include the necessary base cases. To begin, we use
-\textsc{Crane} to compile the sentence into the three components: $\mathcal{E}$,
+sentence into equations that include the necessary base cases. First, we use
+\textsc{Crane} to compile the sentence into three components: $\mathcal{E}$,
 $\mathcal{F}$, and $\mathcal{D}$ (as described in \cref{sec:compilation}). After
-some algebraic simplifications (described below), $\mathcal{E}$ is passed to the
-\FindBaseCases procedure (see \cref{sec:identifying}). For each base case
-$f(\mathbf{x})$, we retrieve the sentence $\mathcal{F}(f)$ associated with the
-function name $f$ and simplify it using the \Propagate procedure (explained in
-detail in \cref{sec:propagating}). We do this by iterating over all indices of
-$\mathbf{x}$, where $x_{i}$ is a constant, and using \Propagate to simplify
-$\psi$ by assuming that domain $\mathcal{D}(f, i)$ has size $x_{i}$. Finally, on
-\autoref{line:final}, \CompileWithBaseCases recurses on these simplified
-sentences and adds the resulting base case equations to $\mathcal{E}$.
+some algebraic simplifications (described below), the algorithm passes
+$\mathcal{E}$ to the \FindBaseCases procedure (see \cref{sec:identifying}). For
+each base case $f(\mathbf{x})$, we retrieve the sentence $\mathcal{F}(f)$
+associated with the function name $f$ and simplify it using the \Propagate
+procedure (explained in detail in \cref{sec:propagating}). We do this by
+iterating over all indices of $\mathbf{x}$, where $x_{i}$ is a constant, and
+using \Propagate to simplify $\psi$ by assuming that domain $\mathcal{D}(f, i)$
+has size $x_{i}$. Finally, on \autoref{line:final}, \CompileWithBaseCases
+recurses on these simplified sentences and adds the resulting base case
+equations to $\mathcal{E}$.
 
@@
 The main responsibility of the \Simplify procedure is to handle the algebraic
-pattern $\sum_{m=0}^{n}[a \le m \le b] f(m)$. Here: $n$ is a variable,
-$a, b \in \mathbb{N}_{0}$ are constants, and $f$ is an expression that may
-depend on $m$. \Simplify transforms this pattern into
-$f(a) + f(a+1) + \cdots + f(\min\{\, n, b \,\})$.
+pattern $\sum_{m=0}^{n}[a \le m \le b] f(m)$. Here, $n$ is a variable, $a$ and
+$b$ are constants, and $f$ is an expression that may depend on $m$. \Simplify
+transforms this pattern into $f(a) + f(a+1) + \cdots + f(\min\{\, n, b \,\})$.
 
 \begin{example}\label{example:bijectionstwo}
-  Let us return to the bijection-counting problem from \cref{example:bijections}
-  and its initial solution described in \cref{example:solution}. \Simplify
-  transforms $g(l, m) = \sum_{k=0}^{m}[0 \le k \le 1]\binom{m}{k}g(l-1, m-k)$
-  into $g(l, m) = g(l-1, m) + mg(l-1, m-1)$. Then \FindBaseCases identifies two
-  base cases: $g(0, m)$ and $g(l, 0)$. In both cases, \CompileWithBaseCases
-  recurses on the sentence $\mathcal{F}(g)$ simplified by assuming that one of
-  the domains is empty. In the first case, we recurse on the sentence
-  $\forall x \in \Gamma\text{. }S(x) \lor \neg S(x)$, where $S$ is a predicate
-  introduced by preprocessing with weights $w^{+}(S) = 1$ and $w^{-}(S) = -1$.
-  Hence, we obtain the base case $g(0, m) = 0^{m}$. In the case of $g(l, 0)$,
-  \Propagate{$\psi$, $\Gamma$, $0$} returns an empty sentence, resulting in
-  $g(l, 0) = 1$. While these base cases overlap when $l = m = 0$, they remain
-  consistent since $0^{0} = 1$.
+  {\par\sloppy
+  We return to the bijection-counting problem from \cref{example:bijections} and
+  its initial solution described in \cref{example:solution}. \Simplify
+  transforms
+  \[
+    g(l, m) = \sum_{k=0}^{m}[0 \le k \le 1]\binom{m}{k}g(l-1, m-k)
+  \]
+  into
+  \[
+    g(l, m) = g(l-1, m) + mg(l-1, m-1).
+  \]
+  Then \FindBaseCases identifies two base cases: $g(0, m)$ and $g(l, 0)$. In
+  both cases, \CompileWithBaseCases recurses on the sentence $\mathcal{F}(g)$
+  simplified by assuming that one of the domains is empty. In the first case, we
+  recurse on the sentence $\forall x \in \Gamma\text{. }S(x) \lor \neg S(x)$,
+  where $S$ is a predicate introduced by preprocessing with weights
+  $w^{+}(S) = 1$ and $w^{-}(S) = -1$. Hence, we obtain the base case
+  $g(0, m) = 0^{m}$. In the case of $g(l, 0)$, \Propagate{$\psi$, $\Gamma$, $0$}
+  returns an empty sentence, resulting in $g(l, 0) = 1$. While these base cases
+  overlap when $l = m = 0$, they remain consistent since $0^{0} = 1$.
+  \par}
 \end{example}
 
-% Generally, let $\phi$ be a sentence with two domains $\Gamma$ and $\Delta$,
-% and let $n, m \in \mathbb{N}_{0}$. Then the FOMC of \Propagate{$\phi$,
-% $\Delta$, $n$} assuming $|\Gamma| = m$ is the same as the FOMC of
-% \Propagate{$\phi$, $\Gamma$, $m$} assuming $|\Delta| = n$.
-
-% Although \CompileWithBaseCases starts with a call to \textsc{Crane}, the
-% proposed algorithm is not just a post-processing step for FOKC because
-% \cref{alg:compilewithbasecases} is recursive and can issue more calls to
-% \textsc{Crane} on various derived sentences.
-
-We end this section by bounding the recursion depth of the \CompileWithBaseCases
-procedure, thus proving that the algorithm terminates.
+Generally, let $\phi$ be a sentence with two domains $\Gamma$ and $\Delta$, and
+let $n, m \in \mathbb{N}_{0}$. Then the FOMC of \Propagate{$\phi$, $\Delta$,
+  $n$}, assuming $|\Gamma| = m$, is the same as the FOMC of \Propagate{$\phi$,
+  $\Gamma$, $m$}, assuming $|\Delta| = n$.
+
+Although \CompileWithBaseCases starts with a call to \textsc{Crane}, the
+proposed algorithm is not merely a post-processing step for FOKC because
+\cref{alg:compilewithbasecases} is recursive and can issue additional calls to
+\textsc{Crane} on various derived sentences. We conclude this section by
+bounding the recursion depth of the \CompileWithBaseCases procedure, thereby
+also proving that the algorithm terminates.
 
 \begin{theorem}
-  Let $\phi$ be a sentence with $n$ domains. Then the maximum recursion depth of
-  \CompileWithBaseCases{$\phi$} is $n$.
+  Let $\phi$ be a sentence with $n$ domains. The maximum recursion depth of
+  \CompileWithBaseCases{$\phi$} is then $n$.
 \end{theorem}
 
-To prove the theorem, we rely on two observations about the algorithms presented
-in \cref{sec:identifying,sec:propagating}.
+The proof of this theorem relies on two observations regarding the algorithms
+presented in \cref{sec:identifying,sec:propagating}.
 
 \begin{observation}\label{observation1}
-  Each base case returned by \FindBaseCases has at least one constant (in line
-  with \cref{def:basecase}).
+  Each base case returned by \FindBaseCases contains at least one constant (in
+  line with \cref{def:basecase}).
 \end{observation}
@@
   \cref{alg:compilewithbasecases} has at least one constant. Therefore, by
-  \cref{observation2}, after \autoref{line:propagate}, sentence $\psi$ has at
-  most $n$ domains. Thus, \autoref{line:final} terminates with a recursion depth
-  of at most $n$ by the inductive hypothesis, completing the inductive proof.
+  \cref{observation2}, after \autoref{line:propagate}, the sentence $\psi$ has
+  at most $n$ domains. Thus, \autoref{line:final} terminates with a recursion
+  depth of at most $n$ by the inductive hypothesis, completing the inductive
+  proof.
 \end{proof}
@@
     \ForEach{$y_{i} \in \mathbf{y}$} {
-      \lIf{$y_{i} \in \mathbb{N}_{0}$}{$\mathcal{B} \gets \mathcal{B} \cup \{\, f(\mathbf{x})[x_{i} \mapsto y_{i}] \,\}$}
+      \lIf{$y_{i} \in \mathbb{N}_{0}$}{$\mathcal{B} \gets \mathcal{B} \cup \{\, f(\mathbf{x})[x_{i} \mapsto y_{i}] \,\}$}\label{line:constant}
       \ElseIf{$y_{i} = x_{i} - c_{i}$ for some $c_{i} \in \mathbb{N}_{0}$}{
-        \lFor{$j \gets 0$ \KwTo $c_{i} - 1$}{$\mathcal{B} \gets \mathcal{B} \cup \{\, f(\mathbf{x})[x_{i} \mapsto j] \,\}$}
+        \lFor{$j \gets 0$ \KwTo $c_{i} - 1$}{$\mathcal{B} \gets \mathcal{B} \cup \{\, f(\mathbf{x})[x_{i} \mapsto j] \,\}$}\label{line:nonconstant}
       }
@@
 \end{algorithm}
-% (later, let's not bother yet): replace x_i-c_i on Line 7 of Algorithm 2 with a
-% generalisation of x_i that can be an arbitrary summation/subtraction of domain
-% sizes (propagating this change to the rest of the paper, particularly
-% Assumption 1, the proof of Lemma 1)
 
@@
 considers two types of arguments when a function $f$ calls itself recursively:
-constants and arguments of the form $x_{i} - c_{i}$. Here, $c_{i}$ is a
-constant, and $x_{i}$ is the $i$-th argument of the signature of $f$. When the
-argument is a constant $c_{i}$, a base case with $c_{i}$ is added. In the second
-case, a base case is added for each constant from $0$ up to (but not including)
-$c_{i}$.
+constants and arguments of the form $x_{i} - c_{i}$. When the argument is a
+constant $c_{i}$, \autoref{line:constant} adds a base case with $c_{i}$ to the
+set of all base cases $\mathcal{B}$. In the second case,
+\autoref{line:nonconstant} adds a base case to $\mathcal{B}$ for each constant
+from $0$ to (but not including) $c_{i}$.
 
@@
 
-It can be shown that the base cases identified by \FindBaseCases are sufficient
-for the algorithm to terminate.\footnote{Note that characterising the
-  fine-grained complexity of the solutions found by \Cranetwo{} or other FOMC
-  algorithms is an emerging area of research. These questions have been
-  partially addressed in previous
-  work~\cite{DBLP:conf/kr/DilkasB23,DBLP:conf/kr/TothK24}
-  and are orthogonal to the goals of this section.} For the remainder of this
-section, let $\mathcal{E}$ denote the equations returned by
+In the rest of this section, we will show that the base cases identified by
+\FindBaseCases are sufficient for the algorithm to terminate.\footnote{Note that
+  characterising the fine-grained complexity of the solutions found by
+  \Cranetwo{} or other FOMC algorithms is an emerging area of research. These
+  questions have been partially addressed in previous
+  work~\cite{DBLP:conf/kr/DilkasB23,DBLP:conf/kr/TothK24} and are unrelated to
+  the goals of this section.} Let $\mathcal{E}$ denote the equations returned by
 \CompileWithBaseCases.
@@
 \begin{theorem}\label{thm:halting}
-  Let $f$ be an $n$-ary function in $\mathcal{E}$ and
-  $\mathbf{x} \in \mathbb{N}_{0}^{n}$. Then the evaluation of $f(\mathbf{x})$
+  Given an $n$-ary function $f$ in $\mathcal{E}$ and
+  $\mathbf{x} \in \mathbb{N}_{0}^{n}$, the evaluation of $f(\mathbf{x})$
   terminates.
@@
 the number of functions in $\mathcal{E}$. Then, we use induction on the arity of
-the `last' function in $\mathcal{E}$ according to some topological ordering. We
-begin with a few observations that stem from
-previous~\cite{DBLP:conf/kr/DilkasB23,DBLP:conf/ijcai/BroeckTMDR11} and this
-work.
+the `last' function in $\mathcal{E}$ according to a topological ordering. Before
+proving \cref{thm:halting}, we make a few observations about this and
+previous~\cite{DBLP:conf/kr/DilkasB23,DBLP:conf/ijcai/BroeckTMDR11} work.
 
@@
 \begin{observation}\label{assumption2}
-  There is a \emph{topological ordering} of all functions ${(f_{i})}_{i}$ in
+  There is a \emph{topological ordering} ${(f_{i})}_{i}$ of all functions in
   $\mathcal{E}$ such that equations in $\mathcal{E}$ with $f_{i}$ on the LHS do
-  not contain function calls to $f_{j}$ with $j > i$. This condition prevents
-  mutual recursion and other cyclic scenarios.
+  not contain function calls to $f_{j}$ with $j > i$.
 \end{observation}
+
+\Cref{assumption2} prevents mutual recursion and other cyclic scenarios.
 
@@
   \begin{itemize}
-    \item Each $y_{i}$ is either $x_{i} - c_{i}$ or $c_{i}$ for some constant
-          $c_{i}$.
-    \item There exists $i$ such that $y_{i} = x_{i} - c_{i}$ for some
+    \item each $y_{i}$ is either $x_{i} - c_{i}$ or $c_{i}$ for some constant
+          $c_{i}$ and
+    \item there exists $i$ such that $y_{i} = x_{i} - c_{i}$ for some
           $c_{i} > 0$.
@@
 Finally, we assume a particular order of evaluation for function calls using the
-equations in $\mathcal{E}$. Specifically, we assume that base cases are
-considered before the recursive definition. The exact order in which base cases
-are considered is immaterial.
+equations in $\mathcal{E}$; specifically, base cases precede the recursive
+definition.
 
@@
   When multiple equations in $\mathcal{E}$ match a function call
-  $f(\mathbf{x})$, preference is given to an equation with the most constants on
-  its LHS.
+  $f(\mathbf{x})$, preference is given to the equation with the most constants
+  on its LHS.
 \end{assumption}
@@
 \begin{lemma}\label{lemma:oneunary}
-  Assume that $\mathcal{E}$ consists of just \emph{one unary} function $f$. Then
-  the evaluation of a function call $f(x)$ terminates for any
-  $x \in \mathbb{N}_{0}$.
+  Assume that $\mathcal{E}$ consists of just \emph{one unary} function called
+  $f$. Then the evaluation of $f(x)$ terminates for any $x \in \mathbb{N}_{0}$.
 \end{lemma}
 \begin{proof}
-  If $f(x)$ is captured by a base case, then its evaluation terminates by
-  \cref{fact,fact2}. If $f$ is not recursive, the evaluation of
-  $f(x)$ terminates by \cref{fact}.
+  If $f(x)$ matches a base case, then its evaluation terminates by
+  \cref{fact,fact2}. If $f$ is not recursive, the evaluation of $f(x)$ also
+  terminates by \cref{fact}.
 
@@
   iterations, the sequence of function calls $f(x), f(x-c), f(x-2c),\dots$ will
-  be captured by the base case $f(x \mod c)$.
+  match the base case $f(x \mod c)$.
 \end{proof}
@@
   Generalising \cref{lemma:oneunary}, let $\mathcal{E}$ be a set of equations
-  for \emph{one} $n$-ary function $f$ for some $n \ge 1$. Then the evaluation of
+  for \emph{one} $n$-ary function $f$ for some $n \ge 1$. The evaluation of
   $f(\mathbf{x})$ terminates for any $\mathbf{x} \in \mathbb{N}_{0}^{n}$.
@@
   $n=1$ handled by \cref{lemma:oneunary}. Assume that $n > 1$. Any base case of
-  $f$ can be seen as a function of arity $n-1$, since one of the parameters is
-  fixed. Thus, the evaluation of any base case terminates by the inductive
+  $f$ can be seen as a function of arity $n-1$ since one of the parameters is
+  constant. Thus, the evaluation of any base case terminates by the inductive
   hypothesis. It remains to show that the evaluation of the recursive equation
-  for $f$ terminates, but that follows from \cref{assumption3}.
+  for $f$ terminates, but this follows from \cref{assumption3}.
 \end{proof}
@@
   hypothesis that all function calls to $f_{j}$ (with $j < n$) terminate, the
-  proof proceeds similarly to the Proof of \cref{lemma:onefunction}.
+  proof proceeds similarly to the proof of \cref{lemma:onefunction}.
 \end{proof}
@@
 the assumption that $|\Delta| = n$. When $n=0$, some clauses become vacuously
-satisfied and can be removed. When $n > 0$, partial grounding is performed by
-replacing all variables quantified over $\Delta$ with constants. (None of the
-sentences examined in this work had $n > 1$.) \Cref{alg:propagate} handles these
-two cases separately. For a literal or a clause $C$, the set of corresponding
-domains is denoted as $\Doms(C)$.
-
-% NOTE: keep this enumerate
-In the case of $n = 0$, there are three types of clauses to consider:
+satisfied and can be removed. When $n > 0$, partial grounding replaces all
+variables with domain $\Delta$ with constants. (None of the sentences examined
+in this work had $n > 1$.) \Cref{alg:propagate} handles these two cases
+separately. For a literal or clause $C$, we write the set of corresponding
+domains as $\Doms(C)$. In the case of $n = 0$, there are three types of clauses
+to consider:
 \begin{enumerate}
@@
   \item those in which every literal contains variables quantified over
-  $\Delta$, and\label[type]{type2}
-  \item those that have some literals with variables quantified over $\Delta$
-  and some without.\label[type]{type3}
+  $\Delta$ and\label[type]{type2}
+  \item those with some literals containing such variables and some
+        without.\label[type]{type3}
 \end{enumerate}
-Clauses of \cref{type1} are transferred to the new sentence $\phi'$ without any
+We transfer clauses of \cref{type1} to the new sentence $\phi'$ without any
 changes. For clauses of \cref{type2}, $C'$ is empty, so these clauses are
-filtered out. As for clauses of \cref{type3}, a new kind of smoothing is
-performed, which will be explained in \cref{sec:smoothing}.
+filtered out. As for clauses of \cref{type3},
+lines~\ref{line:presmoothing}--\ref{line:smoothing2} perform a new kind of
+smoothing, the explanation of which we defer to \cref{sec:smoothing}.
 
@@
 
-% TODO: maybe turn the footnote into a remark?
-
 \begin{example}
-  Let $C \equiv \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{.
+  Let $C \coloneqq \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{.
   } \neg P(x, y) \lor \neg P(x, z) \lor y=z$. Then
@@
 correct model count~\cite{darwiche2001tractable,DBLP:conf/ijcai/BroeckTMDR11}.
-In this section, we describe a similar process performed on
+This section describes a similar process performed on
 lines~\ref{line:presmoothing}--\ref{line:smoothing2} of \cref{alg:propagate}.
@@
 
-Suppose \Propagate is called with arguments $(\phi, \Delta, 0)$, i.e., we are
-simplifying the sentence $\phi$ by assuming that the domain $\Delta$ is empty.
-Informally, if there is a predicate $P$ in $\phi$ unrelated to $\Delta$,
-smoothing preserves all occurrences of $P$ even if all clauses with $P$ become
-vacuously satisfied.
+Suppose \CompileWithBaseCases calls \Propagate with arguments
+$(\phi, \Delta, 0)$, i.e., we are simplifying the sentence $\phi$ by assuming
+that the domain $\Delta$ is empty. Informally, if there is a predicate $P$ in
+$\phi$ unrelated to $\Delta$, smoothing preserves all occurrences of $P$, even
+if all clauses with $P$ become vacuously satisfied.
 
@@
   where $\Gamma' \subseteq \Gamma$ is a domain introduced by a compilation rule.
-  It should be noted that $P$, as a relation, is a subset of
-  $\Gamma \times \Gamma$.
+  Note that $P$, as a relation, is a subset of $\Gamma \times \Gamma$.
 
@@
 \cref{fig:overview}, i.e., translating the set of equations $\mathcal{E}$ into
-C++ code. Recall that this step is crucial for the usability of the algorithm,
-otherwise function definitions would remain purely mathematical, with no
+C++ code. Recall that this step is crucial for the usability of the algorithm;
+otherwise, function definitions would remain purely mathematical, with no
 convenient way to compute the model count for particular domain sizes. Once a
 C++ program is produced, it can be executed with different command-line
-arguments to compute the model count of the sentence for various domain sizes.
+arguments to determine the model count of the sentence for various domain sizes.
 
 \begin{algorithm}[t]
-  \caption{A sketch of the C++ program for the equations in \cref{example:solution}, particularly highlighting the recursive definition of function $g$.}\label{alg:cpp}
+  \caption{A sketch of the C++ program for the equations in
+    \cref{example:solution}, particularly highlighting the recursive definition
+    of the function $g$.}\label{alg:cpp}
   initialise $\Cache_{g(0, m)}$, $\Cache_{g(l, 0)}$, $\Cache_{g}$, and
@@
 See \cref{alg:cpp} for the typical structure of a generated C++ program. Each
-equation in $\mathcal{E}$ is compiled into a C++ function, along with a separate
-cache for memoisation. Hence, \cref{alg:cpp} has a function and a cache for
+equation in $\mathcal{E}$ turns into a C++ function with a separate cache for
+memoisation. Hence, \cref{alg:cpp} has a function and a cache for
 $f(\cdot, \cdot)$, $g(\cdot, \cdot)$, $g(\cdot, 0)$, and $g(0, \cdot)$. The
 implementation of an equation consists of three parts. First (on
-\autoref{line:cache}), we check if the arguments are already present in the
-corresponding cache. If so, we simply return the cached value. Second (on
-lines~\ref{line:basecaseone} and~\ref{line:basecasetwo}), for each base case, we
-check if the arguments match the base case (as defined in \cref{sec:algebra}).
-If so, the arguments are redirected to the C++ function for that base case.
-Finally, if none of the above cases apply, we evaluate the arguments based on
-the expression on the RHS of the equation, store the result in the cache, and
-return it.
+\autoref{line:cache}), we check if the arguments already exist in the
+corresponding cache. If they do, we return the cached value. Second (on
+lines~\ref{line:basecaseone} and~\ref{line:basecasetwo}), we check if the
+arguments match any of the base cases (as defined in \cref{sec:algebra}). If so,
+we redirect the arguments to the C++ function for that base case. Finally, if
+none of the above cases applies, we evaluate the arguments based on the
+expression on the RHS of the equation, store the result in the cache, and return
+it.
 
@@
 and \textsc{ForcLift}\footnote{\url{https://github.com/UCLA-StarAI/Forclift}}.
-Our experiments involve two versions of \Cranetwo{}: \Cranegreedy{} and
+Our experiments involved two versions of \Cranetwo{}: \Cranegreedy{} and
 \Cranebfs{}. Like its predecessor (see \cref{sec:compilation}), \Cranetwo{} has
@@
 
-The experiments were conducted using an Intel Skylake \SI{2.4}{\giga\hertz} CPU
-with \SI{188}{\gibi\byte} of memory and CentOS~7. C++ programs were compiled
-using the Intel C++ Compiler 2020u4. \textsc{FastWFOMC} ran on Julia~1.10.4,
-while the other algorithms were executed on the Java Virtual Machine 1.8.0\_201.
-Note that, although implemented in different languages, both \Cranetwo{} and
-\textsc{FastWFOMC} use the GNU Multiple Precision Arithmetic Library for
-arbitrary-precision arithmetic.
-
-We ran each algorithm on each benchmark using domains of sizes
-$2^{1}, 2^{2}, 2^{3}$, and so on, until an algorithm failed to handle a domain
-size due to timeout (of \SI{1}{\hour}), out of memory error, or out of precision
-errors. While we separately measured compilation and inference time, we
-primarily focus on total runtime, dominated by the latter. We verified the
-accuracy of the numerical answers using the corresponding integer sequences on
-the On-Line Encyclopedia of Integer Sequences~\cite{oeis}.
+The experiments used an Intel Skylake \SI{2.4}{\giga\hertz} CPU with
+\SI{188}{\gibi\byte} of memory and CentOS~7. We used the Intel C++ Compiler
+2020u4 for C++ programs, Julia~1.10.4 for \textsc{FastWFOMC}, and the Java
+Virtual Machine 1.8.0\_201 for \textsc{ForcLift} and \Cranetwo{}. Although
+implemented in different languages, \Cranetwo{} and \textsc{FastWFOMC} use the
+same GNU Multiple Precision Arithmetic Library for arbitrary-precision
+arithmetic.
+
+We ran each algorithm on each benchmark using domains of size
+$2^{1}, 2^{2}, 2^{3}$, and so on until an algorithm failed to handle a domain
+size due to a timeout (of one hour) or out-of-memory or out-of-precision errors.
+While we separately measured compilation and inference time, we primarily focus
+on total runtime, dominated by the latter. We verified the accuracy of the
+numerical answers using the corresponding integer sequences in the On-Line
+Encyclopedia of Integer Sequences~\cite{oeis}.
 
@@
 second benchmark is a variant of the well-known \friends{} Markov logic
-network~\cite{DBLP:conf/aaai/SinglaD08,DBLP:conf/uai/BroeckCD12}, which can be
-formulated as
+network~\cite{DBLP:conf/aaai/SinglaD08,DBLP:conf/uai/BroeckCD12}, which takes
+the form of
 \[
@@
 \]
-In this sentence, we have three predicates $S$, $F$, and $C$ that denote
+In this sentence, we have three predicates, $S$, $F$, and $C$, that denote
 smoking, friendship, and cancer, respectively. The first clause states that
@@
 include the function-counting problem~\cite{DBLP:conf/kr/DilkasB23}
-\[
+\begin{equation}\label[formula]{eq:functions}
   (\forall x \in \Gamma\text{. }\exists y \in \Delta\text{.
@@
   }P(x, y) \land P(x, z) \Rightarrow y = z)
-\]
-as our third benchmark. Here, predicate $P$ is defined as a function from
-$\Gamma$ to $\Delta$. The first clause asserts that each $x$ must have at least
-one corresponding $y$, while the second clause ensures that there is only one
-such $y$.
+\end{equation}
+as our third benchmark. Here, predicate $P$ represents a function from $\Gamma$
+to $\Delta$. The first clause asserts that each $x$ must have at least one
+corresponding $y$, while the second clause ensures the uniqueness of such a $y$.
 
 \begin{remark*}
-  We formulate \bijections{} and \functions{} benchmarks using two domains
-  $\Gamma$ and $\Delta$ as such a formulation is known to help FOKC algorithms
+  We formulate the \bijections{} and \functions{} benchmarks using two domains,
+  $\Gamma$ and $\Delta$, as this formulation is known to help FOKC algorithms
   find efficient solutions~\cite{DBLP:conf/kr/DilkasB23}. To compare \Cranetwo{}
-  and \textsc{ForcLift} with \textsc{FastWFOMC} that has no support for multiple
-  domains, we set $|\Gamma| = |\Delta|$.
+  and \textsc{ForcLift} with \textsc{FastWFOMC}, which has no support for
+  multiple domains, we set $|\Gamma| = |\Delta|$.
 \end{remark*}
 
-\begin{remark*}
-  For completeness, the technical appendix includes translations of these
-  sentences to logics relevant to other (W)FOMC algorithms.
-\end{remark*}
-
-% TODO: this paragraph might not make any sense without the technical appendix
 The three benchmarks cover a wide range of possibilities. The \friends{}
-benchmark uses multiple predicates and can be expressed using two variables
-without cardinality constraints or counting quantifiers. The \functions{}
-benchmark, on the other hand, can still be handled by all the algorithms, but it
-requires cardinality constraints, counting quantifiers, or more than two
-variables, depending on the formulation and the capabilities of the algorithm.
-Lastly, the \bijections{} benchmark is an example of a sentence that
-\textsc{FastWFOMC} can handle but \textsc{ForcLift} cannot.
+benchmark uses multiple predicates and only two variables without employing any
+constructs specific to only one of the (W)FOMC algorithms. The \functions{}
+benchmark, on the other hand, can still be handled by all the algorithms, but
+its formulation relies on algorithm-specific constructs. Namely, for
+\textsc{ForcLift} and \Cranetwo{}, the sentence is written using three
+variables. Since \textsc{FastWFOMC} supports at most two variables, we rewrite
+the \cref{eq:functions} with two variables and a \emph{cardinality constraint}
+(see the technical appendix for details about translating the benchmarks to
+other first-order logics). Lastly, the \bijections{} benchmark is an example of
+a sentence that \textsc{FastWFOMC} can handle but \textsc{ForcLift} cannot.
 
@@
   \includegraphics{plot.pdf}
-  \caption{The runtime of the algorithms as a function of the domain size. Note
-    that both axes are on a logarithmic scale.}\label{fig:plot}
+  \caption{The runtime of the algorithms as a function of domain size. Note that
+    both axes are on a logarithmic scale.}\label{fig:plot}
 \end{figure*}
@@
 One might notice that the runtime of \textsc{FastWFOMC} and \textsc{ForcLift} is
-slightly higher on the smallest domain size. This peculiarity is the consequence
-of \emph{just-in-time} (JIT) compilation. As \Cranetwo{} is only run once per
-benchmark, the JIT compilation time is included in its overall runtime across
-all domain sizes. Additionally, while \textsc{ForcLift}'s compilation is
-generally faster than that of \Cranetwo{}, neither significantly affects overall
-runtime. Specifically, \textsc{ForcLift} compilation typically takes around
-\SI{0.5}{\second}, while \Cranetwo{} compilation takes around \SI{2.3}{\second}.
-
-Based on our experiments, which algorithm should be used in practice? If the
-sentence can be handled by \textsc{ForcLift} and the domain sizes are reasonably
-small, \textsc{ForcLift} is likely the fastest algorithm. In other situations,
-\Cranetwo{} is expected to be significantly more efficient than
-\textsc{FastWFOMC} regardless of domain size, provided both algorithms can
-handle the sentence.
+slightly higher for the smallest domain size. This peculiarity is the
+consequence of \emph{just-in-time} (JIT) compilation. As \Cranetwo{} is only run
+once per benchmark, we include the JIT compilation time in its overall runtime
+across all domain sizes. Additionally, while the compilation time of
+\textsc{ForcLift} is generally lower compared to \Cranetwo{}, neither
+significantly affects the overall runtime. Specifically, \textsc{ForcLift}
+compilation typically takes around \SI{0.5}{\second}, while \Cranetwo{}
+compilation takes around \SI{2.3}{\second}.
+
+Based on our experiments, which algorithm should one use in practice? If
+\textsc{ForcLift} can handle the sentence and the domain sizes are reasonably
+small, it is likely the fastest algorithm. In other situations, \Cranetwo{} will
+likely be significantly more efficient than \textsc{FastWFOMC} regardless of
+domain size, provided both algorithms can handle the sentence.
 
@@
 
-In this work, we have presented a scalable automated FOKC-based approach to
+In this work, we have presented a scalable, automated FOKC-based approach to
 FOMC\@. Our algorithm involves completing the definitions of recursive functions
@@
 particularly crucial in the weighted setting, as illustrated by the \friends{}
-example discussed in \cref{sec:experiments}, where the model captures complex
-social networks with probabilistic relationships. Without this scalability, the
-practical usefulness of these models would be limited.
+example, where the model captures complex social networks with probabilistic
+relationships. Without this scalability, these models would have limited
+practical value.
 
@@
 across various sentences. The capabilities of \Cranetwo{} could also be
-characterised theoretically, e.g., by proving completeness for logic fragments
-liftable by other
+characterised theoretically, for example, by proving completeness for logic
+fragments liftable by other
 algorithms~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/TothK23,DBLP:journals/ai/BremenK23}.

### 2025-06-01 doc/paper/paper.tex
Remove arxiv version (for now) and update conference info

@@
-\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate]{lipics-v2021}
-%This is a template for producing LIPIcs articles. 
-%See lipics-v2021-authors-guidelines.pdf for further information.
-%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
-%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
-%for section-numbered lemmas etc., use "numberwithinsect"
-%for enabling cleveref support, use "cleveref"
-%for enabling autoref support, use "autoref"
-%for anonymousing the authors (e.g. for double-blind review), add "anonymous"
-%for enabling thm-restate support, use "thm-restate"
-%for enabling a two-column layout for the author/affilation part (only applicable for > 6 authors), use "authorcolumns"
-%for producing a PDF according the PDF/A standard, add "pdfa"
-
-\pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
-\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
-
-%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory
-
-\bibliographystyle{plainurl}% the mandatory bibstyle
+\documentclass[a4paper,UKenglish,cleveref,autoref,thm-restate]{lipics-v2021}
+\pdfoutput=1
+\bibliographystyle{plainurl}
 
@@
 
-\keywords{first-order model counting, knowledge compilation, lifted inference}
-
-\relatedversion{} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
-
-%\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
-%\supplementdetails[linktext={opt.
-text shown instead of the URL}, cite=DBLP:books/mk/GrayR93, subcategory={Description, Subcategory}, swhid={Software Heritage Identifier}]{General Classification (e.g.
-Software, Dataset, Model, ...)}{URL to related version} %linktext, cite, and subcategory are optional
+\keywords{First-order model counting, knowledge compilation, lifted inference}
+
+\relatedversion{}
 
@@
   Singapore.}
-
-%\nolinenumbers %uncomment to disable line numbering
-
-%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\EventEditors{John Q. Open and Joan R. Access}
+\nolinenumbers
+
+\EventEditors{Jeremias Berg and Jakob Nordstr\"{o}m}
 \EventNoEds{2}
-\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
-\EventShortTitle{CVIT 2016}
-\EventAcronym{CVIT}
-\EventYear{2016}
-\EventDate{December 24--27, 2016}
-\EventLocation{Little Whinging, United Kingdom}
+\EventLongTitle{28th International Conference on Theory and Applications of Satisfiability Testing (SAT 2025)}
+\EventShortTitle{SAT 2025}
+\EventAcronym{SAT}
+\EventYear{2025}
+\EventDate{August 12--15, 2025}
+\EventLocation{Glasgow, Scotland}
 \EventLogo{}
-\SeriesVolume{42}
-\ArticleNo{23}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\SeriesVolume{341}
+\ArticleNo{5}
 

### 2025-06-05 doc/paper/paper.tex
Cleanup
Potentially the final (camera-ready) version

@@
-\documentclass[a4paper,UKenglish,cleveref,autoref,thm-restate]{lipics-v2021}
+\documentclass[a4paper,UKenglish,cleveref,autoref]{lipics-v2021}
 \pdfoutput=1
@@
 \author{Paulius Dilkas}{University of Toronto, Toronto, Canada \and Vector Institute, Toronto, Canada \and \url{https://dilkas.github.io/}}{paulius.dilkas@utoronto.ca}{https://orcid.org/0000-0001-9185-7840}{}
-\author{Kuldeep S. Meel}{University of Toronto, Toronto, Canada \and \url{https://www.cs.toronto.edu/~meel/}}{meel@cs.toronto.edu}{https://orcid.org/0000-0001-9423-5270}{}
+\author{Kuldeep S.
+Meel}{Georgia Institute of Technology, Atlanta, GA, USA \and University of Toronto, Toronto, Canada \and \url{https://www.cs.toronto.edu/~meel/}}{meel@cs.toronto.edu}{https://orcid.org/0000-0001-9423-5270}{}
 
@@
 \relatedversion{}
+
+\supplementdetails[subcategory={Source Code}]{Software}{https://doi.org/10.5281/zenodo.15583934}
 
@@
   research was conducted while all authors were at the National University of
-  Singapore.}
+  Singapore. We express our gratitude to the anonymous reviewers for their
+  valuable comments and suggestions.}
+
 \nolinenumbers
@@
 \usepackage{tikz}
-\usepackage{microtype}
 \usepackage{mathtools}
+\usepackage{booktabs}
+\usepackage[table]{xcolor}
+\usepackage{pifont}
 
@@
 \newcommand{\expr}{\mathtt{expr}}
-\newcommand{\Cranetwo}{\textsc{Gantry}}
-\newcommand{\Cranebfs}{\textsc{Gantry-BFS}}
-\newcommand{\Cranegreedy}{\textsc{Gantry-Greedy}}
+\newcommand{\Cranetwo}{\textsc{Crane2}}
+\newcommand{\Cranebfs}{\textsc{Crane2-BFS}}
+\newcommand{\Cranegreedy}{\textsc{Crane2-Greedy}}
 \newcommand{\friends}{\emph{Friends \& Smokers}}
@@
 \newcommand{\bijections}{\emph{Bijections}}
+
+\newcommand{\cmark}{\ding{51}}
+\newcommand{\xmark}{\ding{55}}
+\newcommand{\Ctwo}{$\mathsf{C}^{2}$}
+\newcommand{\FO}{$\mathsf{FO}$}
+\newcommand{\UFO}{$\mathsf{UFO}^{2} + \mathsf{CC}$}
 
@@
 \sisetup{group-separator = {,}}
+\sisetup{range-phrase=--}
+
 \newtheorem{assumption}[theorem]{Assumption}
@@
 search~\cite{DBLP:journals/pvldb/NiuRDS11}, and Monte Carlo
-sampling~\cite{DBLP:journals/cacm/GogateD16}. (See the technical appendix for a
-more detailed comparison of the state-of-the-art FOMC algorithms.) FOKC-based
-algorithms are particularly prominent, transforming sentences into structured
-representations such as circuits or graphs. Even when multiple algorithms can
-solve the same instance, FOKC algorithms are known to find polynomial-time
-solutions where the polynomial has a lower degree than other
+sampling~\cite{DBLP:journals/cacm/GogateD16}. FOKC-based algorithms are
+particularly prominent, transforming sentences into structured representations
+such as circuits or graphs. Even when multiple algorithms can solve the same
+instance, FOKC algorithms are known to find polynomial-time solutions where the
+polynomial has a lower degree than other
 approaches~\cite{DBLP:conf/kr/DilkasB23}. The recently developed ability of a
@@
 the paper. Then, in \cref{sec:logic,sec:fomc}, we introduce the basic
-terminology of first-order logic and formally define (W)FOMC\@. \Cref{sec:crane}
-outlines the principles of FOKC, particularly in the context of \textsc{Crane}.
-Finally, in \cref{sec:algebra}, we introduce the algebraic terminology used to
-describe the output of \textsc{Crane}, i.e., functions and equations that define
-them.
+terminology of first-order logic and formally define (W)FOMC\@.
+\Cref{sec:threelogics} provides a brief overview of the different types of
+first-order logics commonly used in FOMC literature. \Cref{sec:crane} outlines
+the principles of FOKC, particularly in the context of \textsc{Crane}. Finally,
+in \cref{sec:algebra}, we introduce the algebraic terminology used to describe
+the output of \textsc{Crane}, i.e., functions and equations that define them.
 
@@
 We use $\mathbb{N}_{0}$ to represent the set of non-negative integers. In both
-algebra and logic, we write $S\sigma$ to denote the application of a
-\emph{substitution} $\sigma$ to an expression $S$, where
-$\sigma = [x_{1} \mapsto y_{1}, x_{2} \mapsto y_{2}, \dots, x_{n} \mapsto y_{n}]$
-signifies the replacement of all instances of $x_{i}$ with $y_{i}$ for all
-$i = 1, \dots, n$. Additionally, for any variable $n$ and
-$a, b \in \mathbb{N}_{0}$, let $[a \le n \le b] \coloneqq \begin{cases}
+algebra and logic, we write
+$S[x_{1} \mapsto y_{1}, x_{2} \mapsto y_{2}, \dots, x_{n} \mapsto y_{n}]$ to
+denote the application of a \emph{substitution} to an expression $S$, where all
+instances of $x_{i}$ are replaced with $y_{i}$ for all $i = 1, \dots, n$.
+Additionally, for any variable $n$ and $a, b \in \mathbb{N}_{0}$, let
+$[a \le n \le b] \coloneqq \begin{cases}
   1 & \text{if $a \le n \le b$} \\
@@
   corresponding constants from $\phi$. A \emph{structure} of $\phi$ is a set $M$
-  of ground literals defined by adding to $M$ either $P(\mathbf{t})$ or
+  of ground literals. It is defined by adding to $M$ either $P(\mathbf{t})$ or
   $\neg P(\mathbf{t})$ for every predicate $P/n$ in $\phi$ and every $n$-tuple
-  $\mathbf{t} \in \prod_{i=1}^{n} \sigma(\Delta_{i}^{P})$. A structure is a
-  \emph{model} if it makes $\phi$ valid.
+  $\mathbf{t} \in \prod_{i=1}^{n} \sigma(\Delta_{i}^{P})$. (Here, $\prod$ is the
+  usual Cartesian product.) A structure is a \emph{model} if it makes $\phi$
+  valid.
 \end{definition}
@@
 
-\begin{remark*}
-  The distinctness of domains is significant in two respects. First, in terms of
-  expressiveness, a clause such as $\forall x \in \Delta\text{. }P(x, x)$ is
-  valid if predicate $P$ operates over two copies of the same domain and invalid
-  otherwise. Second, having more distinct domains makes the problem more
-  decomposable for the FOKC algorithm. With distinct domains, the algorithm can
-  make assumptions or deductions about, e.g., the first domain of predicate $P$
-  without worrying how (or if) they apply to the second domain.
-\end{remark*}
-
 \begin{definition}[WFOMC instance]\label{def:instance}
@@
 
+\subsection{The Three Logics of FOMC}\label{sec:threelogics}
+
+\begin{table}[t]
+  \centering
+  \caption{A comparison of the three logics used in FOMC\@. The
+    2\textsuperscript{nd}--5\textsuperscript{th} columns refer to the number of
+    sorts, support for constants, the maximum number of variables, and supported
+    quantifiers, respectively. The last column lists supported atoms in addition
+    to those of the form $P(\mathbf{t})$ for a predicate $P/n$ and an $n$-tuple
+    of terms $\mathbf{t}$. Here, $k$ and $m$ are non-negative integers, where
+    $m$ depends on the domain size, $P$ is a predicate, and $x$ and $y$ are
+    terms.}\label{tbl:logics}
+  \begin{tabular}{llclll}
+    \toprule
+    Logic & Sorts & Constants & Variables & Quantifiers & Add.\ atoms\\
+    \midrule
+    \rowcolor{gray!10}
+    \FO & one or more & \cmark & unlimited & $\forall$, $\exists$ & $x = y$\\
+    \Ctwo & \multirow{2}{*}{one} & \multirow{2}{*}{\xmark} & \multirow{2}{*}{two} & $\forall$, $\exists$, $\exists^{= k}$, $\exists^{\le k}$, $\exists^{\ge k}$ & ---\\
+    \UFO & & & & $\forall$ & $|P| = m$\\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+FOMC commonly utilises three types of first-order logic: \FO{}, \Ctwo{}, and
+\UFO{}. \Cref{tbl:logics} summarises the key differences among them. \FO{} is
+the input format for \textsc{ForcLift} and its extensions \textsc{Crane} and
+\Cranetwo{}. \Ctwo{} is often used in the literature on \textsc{FastWFOMC} and
+related methods~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/MalhotraS22}.
+(Note that no algorithm accepts \Ctwo{} as input.) Finally, \UFO{} is the input
+format supported by the most recent implementation of
+\textsc{FastWFOMC}~\cite{DBLP:conf/kr/TothK24}. All three logics are
+function-free, and domains are always assumed to be finite. As usual, we
+presuppose the \emph{unique name assumption}, which states that two constants
+are equal if and only if they are the same constant~\cite{DBLP:books/aw/RN2020}.
+
+In \FO{}, each term has a designated \emph{sort}, and each predicate $P/n$
+corresponds to a sequence of $n$ sorts. Each sort has its corresponding domain.
+These assignments to sorts are typically left implicit and follow from the
+quantifiers, e.g., $\forall x,y \in \Delta\text{. }P(x, y)$ implies that the
+variables $x$ and $y$ have the same sort. On the other hand,
+$\forall x \in \Delta\text{. }\forall y \in \Gamma\text{. } P(x, y)$ implies
+that $x$ and $y$ have different sorts, and it would be improper to write, for
+example, $\forall x \in \Delta\text{. }\forall y \in \Gamma\text{.
+} P(x, y) \lor x = y$. \FO{} is also the only logic to support constants,
+sentences with more than two variables, and the equality predicate. While we do
+not explicitly refer to sorts in the rest of the paper, the many-sorted nature
+of \FO{} is paramount to the algorithms presented therein.
+
+\begin{remark*}
+  In the case of \textsc{ForcLift} and its extensions, support for a sentence as
+  valid input does not imply that the algorithm can compile the sentence into a
+  circuit or graph suitable for lifted model counting. However,
+  \textsc{ForcLift} compilation always succeeds on any \FO{} sentence without
+  constants and with at most two
+  variables~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/kr/BroeckMD14}.
+\end{remark*}
+
+Compared to \FO{}, \Ctwo{} and \UFO{} lack support for constants, the equality
+predicate, multiple domains, and sentences with more than two variables. The
+advantage that \Ctwo{} brings over \FO{} is the inclusion of \emph{counting
+  quantifiers}. That is, alongside $\forall$ and $\exists$, \Ctwo{} supports
+$\exists^{=k}$, $\exists^{\le k}$, and $\exists^{\ge k}$ for any positive
+integer $k$. For example, $\exists^{=1} x\text{. }\phi(x)$ means that there
+exists \emph{exactly one} $x$ such that $\phi(x)$, and $\exists^{\le 2} x\text{.
+}\phi(x)$ means that there exist \emph{at most two} such $x$. \UFO{}, on the
+other hand, does not support any existential quantifiers but instead
+incorporates \emph{(equality) cardinality constraints}. For example, $|P| = 3$
+constrains all models to have \emph{precisely three positive literals with the
+  predicate $P$}. Except when stated otherwise, we will write all example
+sentences in \FO{}.
+
 \subsection{Crane and First-Order Knowledge Compilation}\label{sec:crane}
@@
 This stage transforms an arbitrary sentence into the format described in
-\cref{sec:logic}, primarily by eliminating existential quantifiers. For example,
-the first conjunct of \cref{eq:bijections}, i.e.,
+\cref{sec:logic}, primarily by eliminating existential quantifiers via a process
+called \emph{Skolemization}~\cite{DBLP:conf/kr/BroeckMD14}. For example, the
+first conjunct of \cref{eq:bijections}, i.e.,
 \begin{equation}\label[formula]{eq:skolemizationinitial}
@@
 \end{equation}
-where $Z/1$ and $S/1$ are two new predicates with $w^{-}(S) = -1$. One can
-verify that the WFOMC of \cref{eq:skolemizationinitial,eq:skolemization} is the
-same.
+where $Z/1$ and $S/1$ are two new predicates with $w^{-}(S) = -1$. The idea
+behind Skolemization is that the output sentence has more models, but for every
+additional model with a positive weight, there is an equivalent model with a
+negative weight. Hence, the WFOMC of
+\cref{eq:skolemizationinitial,eq:skolemization} is the same. Moreover, note that
+in this example, preprocessing introduces some redundancy, i.e., the second and
+third clauses of \cref{eq:skolemization} could be removed. These redundancies
+are handled at the beginning of the compilation process described in
+\cref{sec:compilation}.
+
+To illustrate how Skolemization preserves the WFOMC, we let $\Gamma = \{\,a\,\}$
+and $\Delta = \{\,1, 2\,\}$ and assume that $w^+(P) = w^-(P) = 1$. Here, for
+conciseness, we omit negative literals when writing models.
+\Cref{eq:skolemizationinitial} has three models: $\{\,P(a, 1)\,\}$,
+$\{\,P(a, 2)\,\}$, and $\{\,P(a, 1), P(a, 2)\,\}$, all with weight 1, so the
+WFOMC is 3. \Cref{eq:skolemization} has the following models:
+\begin{itemize}
+  \item $\{\,Z(a)\,\}$,
+  \item $\{\,Z(a), S(a)\,\}$,
+  \item $\{\,Z(a), S(a), P(a, 1)\,\}$,
+  \item $\{\,Z(a), S(a), P(a, 2)\,\}$,
+  \item $\{\,Z(a), S(a), P(a, 1), P(a, 2)\,\}$.
+\end{itemize}
+The first model has a weight of -1 because $w^-(S) = -1$, while all the other
+models have a weight of 1. Hence, the WFOMC is $4 - 1 = 3$.
 
@@
 equations, and $\mathcal{F}$ and $\mathcal{D}$ are auxiliary maps. $\mathcal{F}$
-maps function names to sentences. $\mathcal{D}$ maps function names and argument
-indices to domains. $\mathcal{E}$ can contain any number of functions, one of
-which (which we will always denote as $f$) represents the solution to the FOMC
-problem. Computing the FOMC for specific domain sizes involves invoking $f$ with
-those sizes as inputs. $\mathcal{D}$ records this correspondence between
-function arguments and domains.
+maps function names to sentences in such a way that the evaluation of the former
+corresponds to the FOMC of the latter. $\mathcal{D}$ maps function names and
+argument indices to domains. The equations in $\mathcal{E}$ can define an
+arbitrary number of functions, one of which (which we will always denote as $f$)
+represents the solution to the FOMC problem. Computing the FOMC for specific
+domain sizes involves invoking $f$ with those sizes as inputs. $\mathcal{D}$
+records this correspondence between function arguments and domains.
 
@@
 
-\begin{figure*}[t]
+\begin{figure}[t]
   \centering
@@
     \Simplify), and two other auxiliary procedures. }\label{fig:overview}
-\end{figure*}
+\end{figure}
 
@@
 \textsc{Crane} often benefit from easily detectable algebraic simplifications
-such as $0 \cdot \text{anything} = 0$ and $\text{anything}^{0} = 1$.
+such as $0 \cdot \text{anything} = 0$ and $\text{anything}^{0} = 1$. Note that
+the latter includes $0^{0} = 1$, as 1 is the multiplicative identity.
 
@@
   work~\cite{DBLP:conf/kr/DilkasB23,DBLP:conf/kr/TothK24} and are unrelated to
-  the goals of this section.} Let $\mathcal{E}$ denote the equations returned by
-\CompileWithBaseCases.
+  the goals of this section.}
 
 \begin{theorem}\label{thm:halting}
-  Given an $n$-ary function $f$ in $\mathcal{E}$ and
-  $\mathbf{x} \in \mathbb{N}_{0}^{n}$, the evaluation of $f(\mathbf{x})$
-  terminates.
+  Let $\mathcal{E}$ denote the set of equations returned by
+  \CompileWithBaseCases, and let $f$ be one of the functions defined in
+  $\mathcal{E}$. The evaluation of $f(\mathbf{x})$ terminates for any tuple
+  $\mathbf{x}$ of non-negative integers (of appropriate length).
 \end{theorem}
@@
 the `last' function in $\mathcal{E}$ according to a topological ordering. Before
-proving \cref{thm:halting}, we make a few observations about this and
-previous~\cite{DBLP:conf/kr/DilkasB23,DBLP:conf/ijcai/BroeckTMDR11} work.
+proving \cref{thm:halting}, we make a few observations that are immediate
+consequences of this and previous
+work~\cite{DBLP:conf/kr/DilkasB23,DBLP:conf/ijcai/BroeckTMDR11}.
 
@@
 
-\Cref{assumption2} prevents mutual recursion and other cyclic scenarios.
+\Cref{assumption2} prevents mutual recursion and other cyclic scenarios. It
+arises from the timeline of FOKC and the fact that, while constructing a graph,
+the algorithm cannot draw an edge to a vertex that does not yet exist.
 
@@
 \end{observation}
+
+Indeed, each $\expr$ is defined by a node type, all of which are finite
+computations listed in previous
+work~\cite{DBLP:conf/kr/DilkasB23,DBLP:conf/nips/Broeck11,DBLP:conf/ijcai/BroeckTMDR11}.
 
@@
 \end{proof}
+
+Now that we have handled the special case when $\mathcal{E}$ defines one
+function, we are ready to prove the main theorem.
 
@@
 \cref{fig:overview}, i.e., translating the set of equations $\mathcal{E}$ into
-C++ code. Recall that this step is crucial for the usability of the algorithm;
+C++ code. (Note that the compilation does not rely on any unique features of
+C++; the equations could easily be compiled into any other programming
+language.) Recall that this step is crucial for the usability of the algorithm;
 otherwise, function definitions would remain purely mathematical, with no
@@
 arguments to determine the model count of the sentence for various domain sizes.
+A typical C++ program for one of the benchmarks in \cref{sec:experiments}
+contains about \numrange{80}{100} lines of code. Moreover, although we focus on
+FOMC in this work, support for WFOMC could easily be added by using
+floating-point numbers instead of integers.
 
@@
 same GNU Multiple Precision Arithmetic Library for arbitrary-precision
-arithmetic.
+arithmetic. Additionally, while \textsc{ForcLift} could be extended to support
+arbitrary-precision arithmetic, its compilation rules are not extensive enough
+to handle some of the benchmarks.
 
@@
 size due to a timeout (of one hour) or out-of-memory or out-of-precision errors.
-While we separately measured compilation and inference time, we primarily focus
-on total runtime, dominated by the latter. We verified the accuracy of the
-numerical answers using the corresponding integer sequences in the On-Line
-Encyclopedia of Integer Sequences~\cite{oeis}.
+We verified the accuracy of the numerical answers using the corresponding
+integer sequences in the On-Line Encyclopedia of Integer Sequences~\cite{oeis}.
 
@@
 
+\paragraph*{Our Benchmarks in \Ctwo{} and \UFO{}}
+For completeness and reproducibility, let us translate the benchmark sentences
+from \FO{} to \Ctwo{} and \UFO{}. Since \friends{} is a relatively simple
+sentence, it remains the same in \Ctwo{} and \UFO{}. For \functions{}, in
+\Ctwo{}, one would write
+\[
+  \forall x \in \Delta\text{. }\exists^{=1} y \in \Delta\text{. }P(x, y).
+\]
+In \UFO{}, the equivalent formulation is
+\begin{equation}\label[formula]{eq:functions1}
+  (\forall x, y \in \Delta\text{. }S(x) \lor \neg P(x, y)) \land (|P| = |\Delta|),
+\end{equation}
+where $w^{-}(S) = -1$. Although \cref{eq:functions1} has more models than its
+counterpart in \Ctwo{}, the negative weight $w^{-}(S) = -1$ causes some of the
+terms in the definition of WFOMC to cancel out. The translation of \bijections{}
+is similar to that of \functions{}. In \Ctwo{}, one could write
+\[
+  (\forall x \in \Delta\text{. }\exists^{=1} y \in \Delta\text{.
+  }P(x, y)) \land (\forall y \in \Delta\text{. }\exists^{=1} x \in \Delta\text{.
+  }P(x, y)).
+\]
+Similarly, in \UFO{}, the equivalent formulation is
+\[
+  (\forall x, y \in \Delta\text{.
+  }R(x) \lor \neg P(x, y)) \land (\forall x, y \in \Delta\text{.
+  }S(x) \lor \neg P(y, x)) \land (|P| = |\Delta|),
+\]
+where $w^{-}(R) = w^{-}(S) = -1$.
+
 The three benchmarks cover a wide range of possibilities. The \friends{}
@@
 variables. Since \textsc{FastWFOMC} supports at most two variables, we rewrite
-the \cref{eq:functions} with two variables and a \emph{cardinality constraint}
-(see the technical appendix for details about translating the benchmarks to
-other first-order logics). Lastly, the \bijections{} benchmark is an example of
-a sentence that \textsc{FastWFOMC} can handle but \textsc{ForcLift} cannot.
+the \cref{eq:functions} with two variables and a \emph{cardinality constraint}.
+Lastly, the \bijections{} benchmark is an example of a sentence that
+\textsc{FastWFOMC} can handle but \textsc{ForcLift} cannot.
 
@@
 
-\begin{figure*}[t]
+\begin{figure}[t]
   \centering
   \includegraphics{plot.pdf}
-  \caption{The runtime of the algorithms as a function of domain size. Note that
-    both axes are on a logarithmic scale.}\label{fig:plot}
-\end{figure*}
+  \caption{The (total) runtime of the algorithms as a function of domain size.
+    Note that both axes are on a logarithmic scale.}\label{fig:plot}
+\end{figure}
 
@@
 
+\begin{table}[t]
+  \caption{The compilation times of FOKC algorithms, sorted in ascending
+    order.}\label{tbl:compilation}
+  \centering
+  \begin{tabular}{llr}
+    \toprule
+    Algorithm & Benchmark & Compilation time (s)\\
+    \midrule
+    \rowcolor{gray!10}
+              & \functions{} & 0.44\\
+    \rowcolor{gray!10}
+    \multirow{-2}{*}{\textsc{ForcLift}} & \friends{} & 0.52\\
+              & \friends{} & 2.20\\
+    \multirow{-2}{*}{\Cranegreedy{}} & \functions{} & 2.36\\
+    \rowcolor{gray!10}
+              & \friends{} & 2.23\\
+    \rowcolor{gray!10}
+              & \functions{} & 2.53\\
+    \rowcolor{gray!10}
+    \multirow{-3}{*}{\Cranebfs{}} & \bijections{} & 7.70\\
+  \end{tabular}
+\end{table}
+
 One might notice that the runtime of \textsc{FastWFOMC} and \textsc{ForcLift} is
@@
 once per benchmark, we include the JIT compilation time in its overall runtime
-across all domain sizes. Additionally, while the compilation time of
-\textsc{ForcLift} is generally lower compared to \Cranetwo{}, neither
-significantly affects the overall runtime. Specifically, \textsc{ForcLift}
-compilation typically takes around \SI{0.5}{\second}, while \Cranetwo{}
-compilation takes around \SI{2.3}{\second}.
+across all domain sizes. Additionally, \cref{tbl:compilation} summarises the
+compilation time of each FOKC algorithm on each suitable benchmark. While the
+compilation time of \textsc{ForcLift} is generally lower compared to
+\Cranetwo{}, neither significantly affects the overall runtime.
 

### 2025-06-05 doc/paper/plot.tex
Potentially the final (camera-ready) version

@@
-% Created by tikzDevice version 0.12.6 on 2025-01-24 14:00:20
+% Created by tikzDevice version 0.12.6 on 2025-06-03 07:37:32
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 37.91, 89.74) --
-	( 41.73, 84.24) --
-	( 45.54, 84.24) --
-	( 49.36, 84.34) --
-	( 53.17, 87.56) --
-	( 56.99,109.01);
-\definecolor{drawColor}{RGB}{117,112,179}
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 37.91, 81.38) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 37.91, 81.38) --
 	( 41.73, 81.38) --
@@
 	( 79.87, 87.02);
+\definecolor{drawColor}{RGB}{117,112,179}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 37.91, 89.74) --
+	( 41.73, 84.24) --
+	( 45.54, 84.24) --
+	( 49.36, 84.34) --
+	( 53.17, 87.56) --
+	( 56.99,109.01);
+\definecolor{fillColor}{RGB}{27,158,119}
+
+\path[fill=fillColor] ( 37.91, 81.38) circle (  1.96);
+
+\path[fill=fillColor] ( 41.73, 81.38) circle (  1.96);
+
+\path[fill=fillColor] ( 45.54, 81.38) circle (  1.96);
+
+\path[fill=fillColor] ( 49.36, 81.38) circle (  1.96);
+
+\path[fill=fillColor] ( 53.17, 81.38) circle (  1.96);
+
+\path[fill=fillColor] ( 56.99, 81.38) circle (  1.96);
+
+\path[fill=fillColor] ( 60.80, 81.39) circle (  1.96);
+
+\path[fill=fillColor] ( 64.62, 81.41) circle (  1.96);
+
+\path[fill=fillColor] ( 68.43, 81.49) circle (  1.96);
+
+\path[fill=fillColor] ( 72.24, 81.81) circle (  1.96);
+
+\path[fill=fillColor] ( 76.06, 83.15) circle (  1.96);
+
+\path[fill=fillColor] ( 79.87, 87.02) circle (  1.96);
 \definecolor{fillColor}{RGB}{117,112,179}
 
-\path[fill=fillColor] ( 35.95, 79.42) --
-	( 39.87, 79.42) --
-	( 39.87, 83.35) --
-	( 35.95, 83.35) --
-	cycle;
-
-\path[fill=fillColor] ( 39.77, 79.42) --
-	( 43.69, 79.42) --
-	( 43.69, 83.35) --
-	( 39.77, 83.35) --
-	cycle;
-
-\path[fill=fillColor] ( 43.58, 79.42) --
-	( 47.50, 79.42) --
-	( 47.50, 83.35) --
-	( 43.58, 83.35) --
-	cycle;
-
-\path[fill=fillColor] ( 47.39, 79.42) --
-	( 51.32, 79.42) --
-	( 51.32, 83.35) --
-	( 47.39, 83.35) --
-	cycle;
-
-\path[fill=fillColor] ( 51.21, 79.42) --
-	( 55.13, 79.42) --
-	( 55.13, 83.35) --
-	( 51.21, 83.35) --
-	cycle;
-
-\path[fill=fillColor] ( 55.02, 79.42) --
-	( 58.95, 79.42) --
-	( 58.95, 83.35) --
-	( 55.02, 83.35) --
-	cycle;
-
-\path[fill=fillColor] ( 58.84, 79.43) --
-	( 62.76, 79.43) --
-	( 62.76, 83.35) --
-	( 58.84, 83.35) --
-	cycle;
-
-\path[fill=fillColor] ( 62.65, 79.45) --
-	( 66.58, 79.45) --
-	( 66.58, 83.37) --
-	( 62.65, 83.37) --
-	cycle;
-
-\path[fill=fillColor] ( 66.47, 79.53) --
-	( 70.39, 79.53) --
-	( 70.39, 83.45) --
-	( 66.47, 83.45) --
-	cycle;
-
-\path[fill=fillColor] ( 70.28, 79.84) --
-	( 74.21, 79.84) --
-	( 74.21, 83.77) --
-	( 70.28, 83.77) --
-	cycle;
-
-\path[fill=fillColor] ( 74.10, 81.19) --
-	( 78.02, 81.19) --
-	( 78.02, 85.11) --
-	( 74.10, 85.11) --
-	cycle;
-
-\path[fill=fillColor] ( 77.91, 85.05) --
-	( 81.84, 85.05) --
-	( 81.84, 88.98) --
-	( 77.91, 88.98) --
-	cycle;
-\definecolor{fillColor}{RGB}{27,158,119}
-
-\path[fill=fillColor] ( 37.91, 89.74) circle (  1.96);
-
-\path[fill=fillColor] ( 41.73, 84.24) circle (  1.96);
-
-\path[fill=fillColor] ( 45.54, 84.24) circle (  1.96);
-
-\path[fill=fillColor] ( 49.36, 84.34) circle (  1.96);
-
-\path[fill=fillColor] ( 53.17, 87.56) circle (  1.96);
-
-\path[fill=fillColor] ( 56.99,109.01) circle (  1.96);
+\path[fill=fillColor] ( 35.95, 87.78) --
+	( 39.87, 87.78) --
+	( 39.87, 91.70) --
+	( 35.95, 91.70) --
+	cycle;
+
+\path[fill=fillColor] ( 39.77, 82.28) --
+	( 43.69, 82.28) --
+	( 43.69, 86.20) --
+	( 39.77, 86.20) --
+	cycle;
+
+\path[fill=fillColor] ( 43.58, 82.28) --
+	( 47.50, 82.28) --
+	( 47.50, 86.20) --
+	( 43.58, 86.20) --
+	cycle;
+
+\path[fill=fillColor] ( 47.39, 82.38) --
+	( 51.32, 82.38) --
+	( 51.32, 86.30) --
+	( 47.39, 86.30) --
+	cycle;
+
+\path[fill=fillColor] ( 51.21, 85.60) --
+	( 55.13, 85.60) --
+	( 55.13, 89.53) --
+	( 51.21, 89.53) --
+	cycle;
+
+\path[fill=fillColor] ( 55.02,107.05) --
+	( 58.95,107.05) --
+	( 58.95,110.97) --
+	( 55.02,110.97) --
+	cycle;
 \definecolor{drawColor}{gray}{0.70}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (147.31, 84.74) --
-	(151.13, 84.06) --
-	(154.94, 83.93) --
-	(158.76, 83.97) --
-	(162.57, 84.20) --
-	(166.39, 84.27) --
-	(170.20, 84.38) --
-	(174.02, 86.20) --
-	(177.83, 93.38) --
-	(181.65,111.72);
-\definecolor{drawColor}{RGB}{217,95,2}
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (147.31, 62.86) --
-	(151.13, 60.69) --
-	(154.94, 60.69) --
-	(158.76, 60.69);
-\definecolor{drawColor}{RGB}{117,112,179}
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (147.31, 72.23) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] (147.31, 72.23) --
 	(151.13, 72.23) --
@@
 	(193.09,123.35);
-\definecolor{drawColor}{RGB}{231,41,138}
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (147.31, 72.11) --
+\definecolor{drawColor}{RGB}{217,95,2}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (147.31, 72.11) --
 	(151.13, 72.11) --
@@
 	(193.09,123.35);
+\definecolor{drawColor}{RGB}{117,112,179}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (147.31, 84.74) --
+	(151.13, 84.06) --
+	(154.94, 83.93) --
+	(158.76, 83.97) --
+	(162.57, 84.20) --
+	(166.39, 84.27) --
+	(170.20, 84.38) --
+	(174.02, 86.20) --
+	(177.83, 93.38) --
+	(181.65,111.72);
+\definecolor{drawColor}{RGB}{231,41,138}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (147.31, 62.86) --
+	(151.13, 60.69) --
+	(154.94, 60.69) --
+	(158.76, 60.69);
+\definecolor{fillColor}{RGB}{117,112,179}
+
+\path[fill=fillColor] (145.35, 82.78) --
+	(149.28, 82.78) --
+	(149.28, 86.70) --
+	(145.35, 86.70) --
+	cycle;
+
+\path[fill=fillColor] (149.17, 82.10) --
+	(153.09, 82.10) --
+	(153.09, 86.02) --
+	(149.17, 86.02) --
+	cycle;
+
+\path[fill=fillColor] (152.98, 81.97) --
+	(156.91, 81.97) --
+	(156.91, 85.90) --
+	(152.98, 85.90) --
+	cycle;
+
+\path[fill=fillColor] (156.80, 82.01) --
+	(160.72, 82.01) --
+	(160.72, 85.93) --
+	(156.80, 85.93) --
+	cycle;
+
+\path[fill=fillColor] (160.61, 82.23) --
+	(164.54, 82.23) --
+	(164.54, 86.16) --
+	(160.61, 86.16) --
+	cycle;
+
+\path[fill=fillColor] (164.43, 82.30) --
+	(168.35, 82.30) --
+	(168.35, 86.23) --
+	(164.43, 86.23) --
+	cycle;
+
+\path[fill=fillColor] (168.24, 82.41) --
+	(172.16, 82.41) --
+	(172.16, 86.34) --
+	(168.24, 86.34) --
+	cycle;
+
+\path[fill=fillColor] (172.05, 84.24) --
+	(175.98, 84.24) --
+	(175.98, 88.16) --
+	(172.05, 88.16) --
+	cycle;
+
+\path[fill=fillColor] (175.87, 91.42) --
+	(179.79, 91.42) --
+	(179.79, 95.34) --
+	(175.87, 95.34) --
+	cycle;
+
+\path[fill=fillColor] (179.68,109.76) --
+	(183.61,109.76) --
+	(183.61,113.68) --
+	(179.68,113.68) --
+	cycle;
+\definecolor{fillColor}{RGB}{217,95,2}
+
+\path[fill=fillColor] (147.31, 75.16) --
+	(149.96, 70.58) --
+	(144.67, 70.58) --
+	cycle;
+
+\path[fill=fillColor] (151.13, 75.16) --
+	(153.77, 70.58) --
+	(148.49, 70.58) --
+	cycle;
+
+\path[fill=fillColor] (154.94, 75.16) --
+	(157.59, 70.58) --
+	(152.30, 70.58) --
+	cycle;
+
+\path[fill=fillColor] (158.76, 75.16) --
+	(161.40, 70.58) --
+	(156.12, 70.58) --
+	cycle;
+
+\path[fill=fillColor] (162.57, 75.16) --
+	(165.22, 70.58) --
+	(159.93, 70.58) --
+	cycle;
+
+\path[fill=fillColor] (166.39, 75.16) --
+	(169.03, 70.58) --
+	(163.75, 70.58) --
+	cycle;
+
+\path[fill=fillColor] (170.20, 75.16) --
+	(172.84, 70.58) --
+	(167.56, 70.58) --
+	cycle;
+
+\path[fill=fillColor] (174.02, 75.20) --
+	(176.66, 70.62) --
+	(171.37, 70.62) --
+	cycle;
+
+\path[fill=fillColor] (177.83, 75.64) --
+	(180.47, 71.06) --
+	(175.19, 71.06) --
+	cycle;
+
+\path[fill=fillColor] (181.65, 79.94) --
+	(184.29, 75.37) --
+	(179.00, 75.37) --
+	cycle;
+
+\path[fill=fillColor] (185.46, 92.72) --
+	(188.10, 88.15) --
+	(182.82, 88.15) --
+	cycle;
+
+\path[fill=fillColor] (189.28,109.42) --
+	(191.92,104.84) --
+	(186.63,104.84) --
+	cycle;
+
+\path[fill=fillColor] (193.09,126.40) --
+	(195.73,121.82) --
+	(190.45,121.82) --
+	cycle;
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (144.54, 62.86) -- (150.09, 62.86);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (147.31, 60.09) -- (147.31, 65.64);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.35, 60.69) -- (153.90, 60.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.13, 57.92) -- (151.13, 63.47);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.17, 60.69) -- (157.72, 60.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (154.94, 57.92) -- (154.94, 63.47);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.98, 60.69) -- (161.53, 60.69);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.76, 57.92) -- (158.76, 63.47);
 \definecolor{fillColor}{RGB}{27,158,119}
 
-\path[fill=fillColor] (147.31, 84.74) circle (  1.96);
-
-\path[fill=fillColor] (151.13, 84.06) circle (  1.96);
-
-\path[fill=fillColor] (154.94, 83.93) circle (  1.96);
-
-\path[fill=fillColor] (158.76, 83.97) circle (  1.96);
-
-\path[fill=fillColor] (162.57, 84.20) circle (  1.96);
-
-\path[fill=fillColor] (166.39, 84.27) circle (  1.96);
-
-\path[fill=fillColor] (170.20, 84.38) circle (  1.96);
-
-\path[fill=fillColor] (174.02, 86.20) circle (  1.96);
-
-\path[fill=fillColor] (177.83, 93.38) circle (  1.96);
-
-\path[fill=fillColor] (181.65,111.72) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (144.54, 72.11) -- (150.09, 72.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (147.31, 69.34) -- (147.31, 74.89);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.35, 72.11) -- (153.90, 72.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (151.13, 69.33) -- (151.13, 74.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (152.17, 72.11) -- (157.72, 72.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (154.94, 69.33) -- (154.94, 74.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (155.98, 72.11) -- (161.53, 72.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (158.76, 69.33) -- (158.76, 74.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (159.80, 72.11) -- (165.35, 72.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.57, 69.33) -- (162.57, 74.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.61, 72.11) -- (169.16, 72.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (166.39, 69.33) -- (166.39, 74.88);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (167.43, 72.11) -- (172.98, 72.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (170.20, 69.34) -- (170.20, 74.89);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (171.24, 72.15) -- (176.79, 72.15);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.02, 69.37) -- (174.02, 74.92);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.06, 72.59) -- (180.61, 72.59);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.83, 69.81) -- (177.83, 75.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (178.87, 76.89) -- (184.42, 76.89);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.65, 74.12) -- (181.65, 79.67);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (182.69, 89.67) -- (188.24, 89.67);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.46, 86.90) -- (185.46, 92.45);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.50,106.37) -- (192.05,106.37);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.28,103.59) -- (189.28,109.14);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (190.32,123.35) -- (195.86,123.35);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.09,120.57) -- (193.09,126.12);
-\definecolor{fillColor}{RGB}{217,95,2}
-
-\path[fill=fillColor] (147.31, 65.91) --
-	(149.96, 61.33) --
-	(144.67, 61.33) --
-	cycle;
-
-\path[fill=fillColor] (151.13, 63.74) --
-	(153.77, 59.17) --
-	(148.49, 59.17) --
-	cycle;
-
-\path[fill=fillColor] (154.94, 63.74) --
-	(157.59, 59.17) --
-	(152.30, 59.17) --
-	cycle;
-
-\path[fill=fillColor] (158.76, 63.74) --
-	(161.40, 59.17) --
-	(156.12, 59.17) --
-	cycle;
-\definecolor{fillColor}{RGB}{117,112,179}
-
-\path[fill=fillColor] (145.35, 70.27) --
-	(149.28, 70.27) --
-	(149.28, 74.20) --
-	(145.35, 74.20) --
-	cycle;
-
-\path[fill=fillColor] (149.17, 70.27) --
-	(153.09, 70.27) --
-	(153.09, 74.19) --
-	(149.17, 74.19) --
-	cycle;
-
-\path[fill=fillColor] (152.98, 70.27) --
-	(156.91, 70.27) --
-	(156.91, 74.19) --
-	(152.98, 74.19) --
-	cycle;
-
-\path[fill=fillColor] (156.80, 70.27) --
-	(160.72, 70.27) --
-	(160.72, 74.19) --
-	(156.80, 74.19) --
-	cycle;
-
-\path[fill=fillColor] (160.61, 70.27) --
-	(164.54, 70.27) --
-	(164.54, 74.19) --
-	(160.61, 74.19) --
-	cycle;
-
-\path[fill=fillColor] (164.43, 70.27) --
-	(168.35, 70.27) --
-	(168.35, 74.19) --
-	(164.43, 74.19) --
-	cycle;
-
-\path[fill=fillColor] (168.24, 70.27) --
-	(172.16, 70.27) --
-	(172.16, 74.20) --
-	(168.24, 74.20) --
-	cycle;
-
-\path[fill=fillColor] (172.05, 70.31) --
-	(175.98, 70.31) --
-	(175.98, 74.23) --
-	(172.05, 74.23) --
-	cycle;
-
-\path[fill=fillColor] (175.87, 70.74) --
-	(179.79, 70.74) --
-	(179.79, 74.66) --
-	(175.87, 74.66) --
-	cycle;
-
-\path[fill=fillColor] (179.68, 74.99) --
-	(183.61, 74.99) --
-	(183.61, 78.91) --
-	(179.68, 78.91) --
-	cycle;
-
-\path[fill=fillColor] (183.50, 87.70) --
-	(187.42, 87.70) --
-	(187.42, 91.62) --
-	(183.50, 91.62) --
-	cycle;
-
-\path[fill=fillColor] (187.31,104.41) --
-	(191.24,104.41) --
-	(191.24,108.33) --
-	(187.31,108.33) --
-	cycle;
-
-\path[fill=fillColor] (191.13,121.39) --
-	(195.05,121.39) --
-	(195.05,125.31) --
-	(191.13,125.31) --
-	cycle;
+\path[fill=fillColor] (147.31, 72.23) circle (  1.96);
+
+\path[fill=fillColor] (151.13, 72.23) circle (  1.96);
+
+\path[fill=fillColor] (154.94, 72.23) circle (  1.96);
+
+\path[fill=fillColor] (158.76, 72.23) circle (  1.96);
+
+\path[fill=fillColor] (162.57, 72.23) circle (  1.96);
+
+\path[fill=fillColor] (166.39, 72.23) circle (  1.96);
+
+\path[fill=fillColor] (170.20, 72.23) circle (  1.96);
+
+\path[fill=fillColor] (174.02, 72.27) circle (  1.96);
+
+\path[fill=fillColor] (177.83, 72.70) circle (  1.96);
+
+\path[fill=fillColor] (181.65, 76.95) circle (  1.96);
+
+\path[fill=fillColor] (185.46, 89.66) circle (  1.96);
+
+\path[fill=fillColor] (189.28,106.37) circle (  1.96);
+
+\path[fill=fillColor] (193.09,123.35) circle (  1.96);
 \definecolor{drawColor}{gray}{0.70}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] (256.72, 85.43) --
-	(260.53, 83.72) --
-	(264.35, 83.89) --
-	(268.16, 83.69) --
-	(271.97, 85.93) --
-	(275.79,108.62);
-\definecolor{drawColor}{RGB}{217,95,2}
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (256.72, 61.86) --
-	(260.53, 61.00) --
-	(264.35, 61.00) --
-	(268.16, 61.00) --
-	(271.97, 61.00) --
-	(275.79, 61.15) --
-	(279.60, 61.15);
-\definecolor{drawColor}{RGB}{117,112,179}
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (256.72, 73.16) --
+\path[draw=drawColor,line width= 0.6pt,line join=round] (256.72, 73.16) --
 	(260.53, 73.16) --
@@
 	(352.08,106.25);
-\definecolor{drawColor}{RGB}{231,41,138}
-
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (256.72, 72.63) --
+\definecolor{drawColor}{RGB}{217,95,2}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (256.72, 72.63) --
 	(260.53, 72.63) --
@@
 	(352.08,106.31);
+\definecolor{drawColor}{RGB}{117,112,179}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (256.72, 85.43) --
+	(260.53, 83.72) --
+	(264.35, 83.89) --
+	(268.16, 83.69) --
+	(271.97, 85.93) --
+	(275.79,108.62);
+\definecolor{drawColor}{RGB}{231,41,138}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (256.72, 61.86) --
+	(260.53, 61.00) --
+	(264.35, 61.00) --
+	(268.16, 61.00) --
+	(271.97, 61.00) --
+	(275.79, 61.15) --
+	(279.60, 61.15);
+\definecolor{fillColor}{RGB}{27,158,119}
+
+\path[fill=fillColor] (256.72, 73.16) circle (  1.96);
+
+\path[fill=fillColor] (260.53, 73.16) circle (  1.96);
+
+\path[fill=fillColor] (264.35, 73.16) circle (  1.96);
+
+\path[fill=fillColor] (268.16, 73.16) circle (  1.96);
+
+\path[fill=fillColor] (271.97, 73.16) circle (  1.96);
+
+\path[fill=fillColor] (275.79, 73.16) circle (  1.96);
+
+\path[fill=fillColor] (279.60, 73.16) circle (  1.96);
+
+\path[fill=fillColor] (283.42, 73.16) circle (  1.96);
+
+\path[fill=fillColor] (287.23, 73.16) circle (  1.96);
+
+\path[fill=fillColor] (291.05, 73.16) circle (  1.96);
+
+\path[fill=fillColor] (294.86, 73.16) circle (  1.96);
+
+\path[fill=fillColor] (298.68, 73.16) circle (  1.96);
+
+\path[fill=fillColor] (302.49, 73.17) circle (  1.96);
+
+\path[fill=fillColor] (306.31, 73.17) circle (  1.96);
+
+\path[fill=fillColor] (310.12, 73.20) circle (  1.96);
+
+\path[fill=fillColor] (313.94, 73.25) circle (  1.96);
+
+\path[fill=fillColor] (317.75, 73.38) circle (  1.96);
+
+\path[fill=fillColor] (321.56, 73.71) circle (  1.96);
+
+\path[fill=fillColor] (325.38, 74.42) circle (  1.96);
+
+\path[fill=fillColor] (329.19, 76.07) circle (  1.96);
+
+\path[fill=fillColor] (333.01, 78.80) circle (  1.96);
+
+\path[fill=fillColor] (336.82, 82.57) circle (  1.96);
+
+\path[fill=fillColor] (340.64, 87.78) circle (  1.96);
+
+\path[fill=fillColor] (344.45, 94.24) circle (  1.96);
+
+\path[fill=fillColor] (348.27,100.04) circle (  1.96);
+
+\path[fill=fillColor] (352.08,106.25) circle (  1.96);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (253.94, 61.86) -- (259.49, 61.86);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (256.72, 59.08) -- (256.72, 64.63);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.76, 61.00) -- (263.31, 61.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (260.53, 58.23) -- (260.53, 63.78);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.57, 61.00) -- (267.12, 61.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.35, 58.23) -- (264.35, 63.78);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (265.39, 61.00) -- (270.94, 61.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (268.16, 58.23) -- (268.16, 63.78);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (269.20, 61.00) -- (274.75, 61.00);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.97, 58.23) -- (271.97, 63.78);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.01, 61.15) -- (278.56, 61.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.79, 58.38) -- (275.79, 63.93);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (276.83, 61.15) -- (282.38, 61.15);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (279.60, 58.38) -- (279.60, 63.93);
 \definecolor{fillColor}{RGB}{117,112,179}
 
-\path[fill=fillColor] (254.75, 71.20) --
-	(258.68, 71.20) --
-	(258.68, 75.12) --
-	(254.75, 75.12) --
-	cycle;
-
-\path[fill=fillColor] (258.57, 71.20) --
-	(262.49, 71.20) --
-	(262.49, 75.12) --
-	(258.57, 75.12) --
-	cycle;
-
-\path[fill=fillColor] (262.38, 71.20) --
-	(266.31, 71.20) --
-	(266.31, 75.12) --
-	(262.38, 75.12) --
-	cycle;
-
-\path[fill=fillColor] (266.20, 71.20) --
-	(270.12, 71.20) --
-	(270.12, 75.12) --
-	(266.20, 75.12) --
-	cycle;
-
-\path[fill=fillColor] (270.01, 71.20) --
-	(273.94, 71.20) --
-	(273.94, 75.12) --
-	(270.01, 75.12) --
-	cycle;
-
-\path[fill=fillColor] (273.83, 71.20) --
-	(277.75, 71.20) --
-	(277.75, 75.12) --
-	(273.83, 75.12) --
-	cycle;
-
-\path[fill=fillColor] (277.64, 71.20) --
-	(281.57, 71.20) --
-	(281.57, 75.12) --
-	(277.64, 75.12) --
-	cycle;
-
-\path[fill=fillColor] (281.46, 71.20) --
-	(285.38, 71.20) --
-	(285.38, 75.12) --
-	(281.46, 75.12) --
-	cycle;
-
-\path[fill=fillColor] (285.27, 71.20) --
-	(289.20, 71.20) --
-	(289.20, 75.12) --
-	(285.27, 75.12) --
-	cycle;
-
-\path[fill=fillColor] (289.09, 71.20) --
-	(293.01, 71.20) --
-	(293.01, 75.12) --
-	(289.09, 75.12) --
-	cycle;
-
-\path[fill=fillColor] (292.90, 71.20) --
-	(296.82, 71.20) --
-	(296.82, 75.12) --
-	(292.90, 75.12) --
-	cycle;
-
-\path[fill=fillColor] (296.72, 71.20) --
-	(300.64, 71.20) --
-	(300.64, 75.12) --
-	(296.72, 75.12) --
-	cycle;
-
-\path[fill=fillColor] (300.53, 71.21) --
-	(304.45, 71.21) --
-	(304.45, 75.13) --
-	(300.53, 75.13) --
-	cycle;
-
-\path[fill=fillColor] (304.34, 71.21) --
-	(308.27, 71.21) --
-	(308.27, 75.14) --
-	(304.34, 75.14) --
-	cycle;
-
-\path[fill=fillColor] (308.16, 71.24) --
-	(312.08, 71.24) --
-	(312.08, 75.16) --
-	(308.16, 75.16) --
-	cycle;
-
-\path[fill=fillColor] (311.97, 71.29) --
-	(315.90, 71.29) --
-	(315.90, 75.22) --
-	(311.97, 75.22) --
-	cycle;
-
-\path[fill=fillColor] (315.79, 71.42) --
-	(319.71, 71.42) --
-	(319.71, 75.35) --
-	(315.79, 75.35) --
-	cycle;
-
-\path[fill=fillColor] (319.60, 71.75) --
-	(323.53, 71.75) --
-	(323.53, 75.67) --
-	(319.60, 75.67) --
-	cycle;
-
-\path[fill=fillColor] (323.42, 72.46) --
-	(327.34, 72.46) --
-	(327.34, 76.39) --
-	(323.42, 76.39) --
-	cycle;
-
-\path[fill=fillColor] (327.23, 74.10) --
-	(331.16, 74.10) --
-	(331.16, 78.03) --
-	(327.23, 78.03) --
-	cycle;
-
-\path[fill=fillColor] (331.05, 76.84) --
-	(334.97, 76.84) --
-	(334.97, 80.76) --
-	(331.05, 80.76) --
-	cycle;
-
-\path[fill=fillColor] (334.86, 80.61) --
-	(338.79, 80.61) --
-	(338.79, 84.53) --
-	(334.86, 84.53) --
-	cycle;
-
-\path[fill=fillColor] (338.68, 85.82) --
-	(342.60, 85.82) --
-	(342.60, 89.74) --
-	(338.68, 89.74) --
-	cycle;
-
-\path[fill=fillColor] (342.49, 92.28) --
-	(346.41, 92.28) --
-	(346.41, 96.20) --
-	(342.49, 96.20) --
-	cycle;
-
-\path[fill=fillColor] (346.30, 98.07) --
-	(350.23, 98.07) --
-	(350.23,102.00) --
-	(346.30,102.00) --
-	cycle;
-
-\path[fill=fillColor] (350.12,104.29) --
-	(354.04,104.29) --
-	(354.04,108.21) --
-	(350.12,108.21) --
+\path[fill=fillColor] (254.75, 83.46) --
+	(258.68, 83.46) --
+	(258.68, 87.39) --
+	(254.75, 87.39) --
+	cycle;
+
+\path[fill=fillColor] (258.57, 81.76) --
+	(262.49, 81.76) --
+	(262.49, 85.68) --
+	(258.57, 85.68) --
+	cycle;
+
+\path[fill=fillColor] (262.38, 81.92) --
+	(266.31, 81.92) --
+	(266.31, 85.85) --
+	(262.38, 85.85) --
+	cycle;
+
+\path[fill=fillColor] (266.20, 81.73) --
+	(270.12, 81.73) --
+	(270.12, 85.66) --
+	(266.20, 85.66) --
+	cycle;
+
+\path[fill=fillColor] (270.01, 83.97) --
+	(273.94, 83.97) --
+	(273.94, 87.89) --
+	(270.01, 87.89) --
+	cycle;
+
+\path[fill=fillColor] (273.83,106.66) --
+	(277.75,106.66) --
+	(277.75,110.59) --
+	(273.83,110.59) --
 	cycle;
@@
 
-\path[fill=fillColor] (256.72, 64.91) --
-	(259.36, 60.33) --
-	(254.07, 60.33) --
-	cycle;
-
-\path[fill=fillColor] (260.53, 64.05) --
-	(263.17, 59.48) --
-	(257.89, 59.48) --
-	cycle;
-
-\path[fill=fillColor] (264.35, 64.05) --
-	(266.99, 59.48) --
-	(261.70, 59.48) --
-	cycle;
-
-\path[fill=fillColor] (268.16, 64.05) --
-	(270.80, 59.48) --
-	(265.52, 59.48) --
-	cycle;
-
-\path[fill=fillColor] (271.97, 64.05) --
-	(274.62, 59.48) --
-	(269.33, 59.48) --
-	cycle;
-
-\path[fill=fillColor] (275.79, 64.20) --
-	(278.43, 59.63) --
-	(273.15, 59.63) --
-	cycle;
-
-\path[fill=fillColor] (279.60, 64.20) --
-	(282.25, 59.63) --
-	(276.96, 59.63) --
-	cycle;
-\definecolor{fillColor}{RGB}{27,158,119}
-
-\path[fill=fillColor] (256.72, 85.43) circle (  1.96);
-
-\path[fill=fillColor] (260.53, 83.72) circle (  1.96);
-
-\path[fill=fillColor] (264.35, 83.89) circle (  1.96);
-
-\path[fill=fillColor] (268.16, 83.69) circle (  1.96);
-
-\path[fill=fillColor] (271.97, 85.93) circle (  1.96);
-
-\path[fill=fillColor] (275.79,108.62) circle (  1.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (253.94, 72.63) -- (259.49, 72.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (256.72, 69.85) -- (256.72, 75.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (257.76, 72.63) -- (263.31, 72.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (260.53, 69.85) -- (260.53, 75.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.57, 72.63) -- (267.12, 72.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.35, 69.85) -- (264.35, 75.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (265.39, 72.63) -- (270.94, 72.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (268.16, 69.85) -- (268.16, 75.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (269.20, 72.63) -- (274.75, 72.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (271.97, 69.85) -- (271.97, 75.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (273.01, 72.63) -- (278.56, 72.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (275.79, 69.85) -- (275.79, 75.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (276.83, 72.63) -- (282.38, 72.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (279.60, 69.86) -- (279.60, 75.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (280.64, 72.63) -- (286.19, 72.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.42, 69.85) -- (283.42, 75.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (284.46, 72.63) -- (290.01, 72.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (287.23, 69.85) -- (287.23, 75.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (288.27, 72.63) -- (293.82, 72.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (291.05, 69.86) -- (291.05, 75.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (292.09, 72.63) -- (297.64, 72.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (294.86, 69.86) -- (294.86, 75.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (295.90, 72.63) -- (301.45, 72.63);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (298.68, 69.86) -- (298.68, 75.40);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (299.72, 72.64) -- (305.27, 72.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (302.49, 69.86) -- (302.49, 75.41);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (303.53, 72.64) -- (309.08, 72.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (306.31, 69.87) -- (306.31, 75.42);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (307.35, 72.67) -- (312.90, 72.67);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (310.12, 69.90) -- (310.12, 75.45);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (311.16, 72.73) -- (316.71, 72.73);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (313.94, 69.95) -- (313.94, 75.50);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (314.98, 72.87) -- (320.53, 72.87);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (317.75, 70.09) -- (317.75, 75.64);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (318.79, 73.21) -- (324.34, 73.21);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (321.56, 70.44) -- (321.56, 75.99);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (322.60, 73.96) -- (328.15, 73.96);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (325.38, 71.19) -- (325.38, 76.74);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (326.42, 75.58) -- (331.97, 75.58);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (329.19, 72.81) -- (329.19, 78.36);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (330.23, 78.49) -- (335.78, 78.49);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.01, 75.72) -- (333.01, 81.27);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (334.05, 82.32) -- (339.60, 82.32);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (336.82, 79.55) -- (336.82, 85.10);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (337.86, 87.62) -- (343.41, 87.62);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (340.64, 84.84) -- (340.64, 90.39);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (341.68, 94.08) -- (347.23, 94.08);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (344.45, 91.31) -- (344.45, 96.86);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (345.49, 99.98) -- (351.04, 99.98);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (348.27, 97.20) -- (348.27,102.75);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (349.31,106.31) -- (354.86,106.31);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (352.08,103.54) -- (352.08,109.09);
+\path[fill=fillColor] (256.72, 75.68) --
+	(259.36, 71.10) --
+	(254.07, 71.10) --
+	cycle;
+
+\path[fill=fillColor] (260.53, 75.68) --
+	(263.17, 71.10) --
+	(257.89, 71.10) --
+	cycle;
+
+\path[fill=fillColor] (264.35, 75.68) --
+	(266.99, 71.10) --
+	(261.70, 71.10) --
+	cycle;
+
+\path[fill=fillColor] (268.16, 75.68) --
+	(270.80, 71.10) --
+	(265.52, 71.10) --
+	cycle;
+
+\path[fill=fillColor] (271.97, 75.68) --
+	(274.62, 71.10) --
+	(269.33, 71.10) --
+	cycle;
+
+\path[fill=fillColor] (275.79, 75.68) --
+	(278.43, 71.10) --
+	(273.15, 71.10) --
+	cycle;
+
+\path[fill=fillColor] (279.60, 75.68) --
+	(282.25, 71.10) --
+	(276.96, 71.10) --
+	cycle;
+
+\path[fill=fillColor] (283.42, 75.68) --
+	(286.06, 71.10) --
+	(280.78, 71.10) --
+	cycle;
+
+\path[fill=fillColor] (287.23, 75.68) --
+	(289.88, 71.10) --
+	(284.59, 71.10) --
+	cycle;
+
+\path[fill=fillColor] (291.05, 75.68) --
+	(293.69, 71.10) --
+	(288.41, 71.10) --
+	cycle;
+
+\path[fill=fillColor] (294.86, 75.68) --
+	(297.51, 71.10) --
+	(292.22, 71.10) --
+	cycle;
+
+\path[fill=fillColor] (298.68, 75.68) --
+	(301.32, 71.10) --
+	(296.03, 71.10) --
+	cycle;
+
+\path[fill=fillColor] (302.49, 75.69) --
+	(305.13, 71.11) --
+	(299.85, 71.11) --
+	cycle;
+
+\path[fill=fillColor] (306.31, 75.69) --
+	(308.95, 71.12) --
+	(303.66, 71.12) --
+	cycle;
+
+\path[fill=fillColor] (310.12, 75.72) --
+	(312.76, 71.14) --
+	(307.48, 71.14) --
+	cycle;
+
+\path[fill=fillColor] (313.94, 75.78) --
+	(316.58, 71.20) --
+	(311.29, 71.20) --
+	cycle;
+
+\path[fill=fillColor] (317.75, 75.92) --
+	(320.39, 71.34) --
+	(315.11, 71.34) --
+	cycle;
+
+\path[fill=fillColor] (321.56, 76.27) --
+	(324.21, 71.69) --
+	(318.92, 71.69) --
+	cycle;
+
+\path[fill=fillColor] (325.38, 77.01) --
+	(328.02, 72.44) --
+	(322.74, 72.44) --
+	cycle;
+
+\path[fill=fillColor] (329.19, 78.63) --
+	(331.84, 74.06) --
+	(326.55, 74.06) --
+	cycle;
+
+\path[fill=fillColor] (333.01, 81.55) --
+	(335.65, 76.97) --
+	(330.37, 76.97) --
+	cycle;
+
+\path[fill=fillColor] (336.82, 85.37) --
+	(339.47, 80.80) --
+	(334.18, 80.80) --
+	cycle;
+
+\path[fill=fillColor] (340.64, 90.67) --
+	(343.28, 86.09) --
+	(338.00, 86.09) --
+	cycle;
+
+\path[fill=fillColor] (344.45, 97.14) --
+	(347.10, 92.56) --
+	(341.81, 92.56) --
+	cycle;
+
+\path[fill=fillColor] (348.27,103.03) --
+	(350.91, 98.45) --
+	(345.62, 98.45) --
+	cycle;
+
+\path[fill=fillColor] (352.08,109.36) --
+	(354.72,104.79) --
+	(349.44,104.79) --
+	cycle;
 \definecolor{drawColor}{gray}{0.70}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (195.00,130.78) {Friends};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (195.00,130.78) {Friends \& Smokers};
 \end{scope}
@@
 
-\path[fill=fillColor] ( 51.80,  4.50) rectangle (338.20, 27.95);
+\path[fill=fillColor] ( 52.31,  4.50) rectangle (337.68, 27.95);
 \end{scope}
@@
 
-\path[fill=fillColor] ( 60.80,  9.00) rectangle ( 75.25, 23.45);
+\path[fill=fillColor] ( 61.31,  9.00) rectangle ( 75.77, 23.45);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.24, 16.23) -- ( 73.81, 16.23);
+\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.76, 16.23) -- ( 74.32, 16.23);
 \end{scope}
@@
 
-\path[fill=fillColor] ( 68.02, 16.23) circle (  1.96);
+\path[fill=fillColor] ( 68.54, 16.23) circle (  1.96);
 \end{scope}
@@
 
-\path[fill=fillColor] (132.24,  9.00) rectangle (146.69, 23.45);
+\path[fill=fillColor] (129.38,  9.00) rectangle (143.83, 23.45);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (133.68, 16.23) -- (145.25, 16.23);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (130.83, 16.23) -- (142.39, 16.23);
 \end{scope}
@@
 
-\path[fill=fillColor] (139.46, 19.28) --
-	(142.11, 14.70) --
-	(136.82, 14.70) --
+\path[fill=fillColor] (136.61, 19.28) --
+	(139.25, 14.70) --
+	(133.97, 14.70) --
 	cycle;
@@
 
-\path[fill=fillColor] (188.77,  9.00) rectangle (203.22, 23.45);
+\path[fill=fillColor] (209.71,  9.00) rectangle (224.16, 23.45);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (190.22, 16.23) -- (201.78, 16.23);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (211.15, 16.23) -- (222.72, 16.23);
 \end{scope}
@@
 
-\path[fill=fillColor] (194.03, 14.26) --
-	(197.96, 14.26) --
-	(197.96, 18.19) --
-	(194.03, 18.19) --
+\path[fill=fillColor] (214.97, 14.26) --
+	(218.90, 14.26) --
+	(218.90, 18.19) --
+	(214.97, 18.19) --
 	cycle;
@@
 
-\path[fill=fillColor] (257.35,  9.00) rectangle (271.81, 23.45);
+\path[fill=fillColor] (281.15,  9.00) rectangle (295.60, 23.45);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (258.80, 16.23) -- (270.36, 16.23);
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (282.59, 16.23) -- (294.16, 16.23);
 \end{scope}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.81, 16.23) -- (267.35, 16.23);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (264.58, 13.45) -- (264.58, 19.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (285.60, 16.23) -- (291.15, 16.23);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (288.38, 13.45) -- (288.38, 19.00);
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 79.75, 13.75) {\textsc{FastWFOMC}};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 80.27, 13.75) {\textsc{Crane2-BFS}};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (151.19, 13.75) {\textsc{ForcLift}};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (148.33, 13.75) {\textsc{Crane2-Greedy}};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (207.72, 13.75) {\textsc{Gantry-BFS}};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (228.66, 13.75) {\textsc{FastWFOMC}};
 \end{scope}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (276.31, 13.75) {\textsc{Gantry-Greedy}};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (300.10, 13.75) {\textsc{ForcLift}};
 \end{scope}

### 2025-06-05 analysis/analyse.R

@@ -12,8 +12,8 @@ df <- read.csv("../results/processed/results.csv")
 df$compilation.time <- df$compilation.time / 1000
 df$inference.time <- df$inference.time / 1000
 df$time <- df$compilation.time + df$inference.time
-df$algorithm[df$algorithm == "bfs"] <- "\\textsc{Gantry-BFS}"
-df$algorithm[df$algorithm == "greedy"] <- "\\textsc{Gantry-Greedy}"
+df$algorithm[df$algorithm == "bfs"] <- "\\textsc{Crane2-BFS}"
+df$algorithm[df$algorithm == "greedy"] <- "\\textsc{Crane2-Greedy}"
 df$algorithm[df$algorithm == "fastwfomc"] <- "\\textsc{FastWFOMC}"
 df$algorithm[df$algorithm == "forclift"] <- "\\textsc{ForcLift}"
 df$sequence[df$sequence == "bijections"] <- "Bijections"
@@ -21,6 +21,8 @@ df$sequence[df$sequence == "friends"] <- "Friends \\& Smokers"
 df$sequence[df$sequence == "functions"] <- "Functions"
 df <- df[df$domain.size > 1,]
 dark2_colors <- brewer.pal(8, "Dark2")
+
+df %>% group_by(algorithm, sequence) %>% summarize(compilation.time = max(compilation.time))
 
 # Sanity check: differences between max and min counts as a percentage of the
 # min count

### 2025-06-12 doc/talk/talk.tex
Start drafting the talk

--- 2025-06-01 doc/paper/paper.tex
@@
-\documentclass[a4paper,UKenglish,cleveref,autoref,thm-restate]{lipics-v2021}
-\pdfoutput=1
-\bibliographystyle{plainurl}
-
-\title{Towards Practical First-Order Model Counting}
-
-\author{Ananth K. Kidambi}{Indian Institute of Technology Bombay, Mumbai, India}{210051002@iitb.ac.in}{}{}
-\author{Guramrit Singh}{Indian Institute of Technology Bombay, Mumbai, India}{guramrit@iitb.ac.in}{}{}
-\author{Paulius Dilkas}{University of Toronto, Toronto, Canada \and Vector Institute, Toronto, Canada \and \url{https://dilkas.github.io/}}{paulius.dilkas@utoronto.ca}{https://orcid.org/0000-0001-9185-7840}{}
-\author{Kuldeep S. Meel}{University of Toronto, Toronto, Canada \and \url{https://www.cs.toronto.edu/~meel/}}{meel@cs.toronto.edu}{https://orcid.org/0000-0001-9423-5270}{}
-
-\authorrunning{A.\,K. Kidambi, G. Singh, P. Dilkas, and K.\,S. Meel}
-\Copyright{Ananth K. Kidambi, Guramrit Singh, Paulius Dilkas, and Kuldeep S. Meel}
-
-\ccsdesc{Theory of computation~Automated reasoning}
-\ccsdesc{Theory of computation~Logic and verification}
-\ccsdesc{Mathematics of computing~Combinatorics}
-
-\keywords{First-order model counting, knowledge compilation, lifted inference}
-
-\relatedversion{}
-
-\funding{This research was funded in part by the Natural Sciences and
-  Engineering Research Council of Canada (NSERC), funding reference number
-  RGPIN-2024-05956, and the Digital Research Alliance of Canada
-  (\texttt{\href{https://alliancecan.ca/}{alliancecan.ca}}).}
-
-\acknowledgements{The first two authors contributed equally. Part of the
-  research was conducted while all authors were at the National University of
-  Singapore.}
-\nolinenumbers
-
-\EventEditors{Jeremias Berg and Jakob Nordstr\"{o}m}
-\EventNoEds{2}
-\EventLongTitle{28th International Conference on Theory and Applications of Satisfiability Testing (SAT 2025)}
-\EventShortTitle{SAT 2025}
-\EventAcronym{SAT}
-\EventYear{2025}
-\EventDate{August 12--15, 2025}
-\EventLocation{Glasgow, Scotland}
-\EventLogo{}
-\SeriesVolume{341}
-\ArticleNo{5}
-
+\documentclass{beamer}
+\usepackage[utf8]{inputenc}
+\usepackage[UKenglish]{babel}
+\usepackage[UKenglish]{isodate}
+\usepackage{tikz}
 \usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-\usepackage{siunitx}
-\usepackage{tikz}
-\usepackage{microtype}
-\usepackage{mathtools}
 
 \usetikzlibrary{arrows.meta}
+\usetikzlibrary{decorations.pathreplacing}
 \usetikzlibrary{fit}
@@
 \usetikzlibrary{shapes.misc}
-
-\newcommand{\expr}{\mathtt{expr}}
-\newcommand{\Cranetwo}{\textsc{Gantry}}
-\newcommand{\Cranebfs}{\textsc{Gantry-BFS}}
-\newcommand{\Cranegreedy}{\textsc{Gantry-Greedy}}
-\newcommand{\friends}{\emph{Friends \& Smokers}}
-\newcommand{\functions}{\emph{Functions}}
-\newcommand{\bijections}{\emph{Bijections}}
-
-\SetKwProg{Fn}{Function}{:}{}
-\SetKwData{Cache}{Cache}
 
@@
 
-\DeclareMathOperator{\CR}{CR}
-\DeclareMathOperator{\DR}{DR}
-\DeclareMathOperator{\Reff}{Ref}
-\DeclareMathOperator{\Doms}{Doms}
+\newcommand{\expr}{\mathtt{expr}}
+\newcommand{\Cranetwo}{\textsc{Crane2}}
+\newcommand{\Cranebfs}{\textsc{Crane2-BFS}}
+\newcommand{\Cranegreedy}{\textsc{Crane2-Greedy}}
+\newcommand{\friends}{\emph{Friends \& Smokers}}
+\newcommand{\functions}{\emph{Functions}}
+\newcommand{\bijections}{\emph{Bijections}}
 
-\sisetup{group-separator = {,}}
-\newtheorem{assumption}[theorem]{Assumption}
+\beamertemplatenavigationsymbolsempty
+\usetheme{default}
+\usecolortheme{beaver}
 
-\crefalias{enumi}{type}
-\crefname{type}{Type}{Types}
-\creflabelformat{type}{#2\textup{#1}#3}
-\crefalias{clause}{equation}
-\crefname{clause}{clause}{clauses}
-\creflabelformat{clause}{#2\textup{(#1)}#3}
-\crefalias{formula}{equation}
-\crefname{formula}{sentence}{sentences}
-\creflabelformat{formula}{#2\textup{(#1)}#3}
+\author{Ananth K. Kidambi\inst{1} \and Guramrit Singh\inst{1} \and \textbf{Paulius Dilkas}\inst{2,3} \and Kuldeep S. Meel\inst{4,2}}
+\institute{\inst{1} IIT Bombay, India \and \inst{2} University of Toronto, Canada \and \inst{3} Vector Institute, Canada \and \inst{4} Georgia Tech, USA}
 
+\title{Towards Practical First-Order Model Counting}
+\date{SAT 2025}
+
+% TODO: 20 min / 14 slides (presumably)
 \begin{document}
@@
 
-\begin{abstract}
-  First-order model counting (FOMC) is the problem of counting the number of
-  models of a sentence in first-order logic. Since lifted inference techniques
-  rely on reductions to variants of FOMC, the design of scalable methods for
-  FOMC has attracted attention from both theoreticians and practitioners over
-  the past decade. Recently, a new approach based on first-order knowledge
-  compilation was proposed. This approach, called \textsc{Crane}, instead of
-  simply providing the final count, generates definitions of (possibly
-  recursive) functions that can be evaluated with different arguments to compute
-  the model count for any domain size. However, this approach is not fully
-  automated, as it requires manual evaluation of the constructed functions. The
-  primary contribution of this work is a fully automated compilation algorithm,
-  called \Cranetwo{}, which transforms the function definitions into C++ code
-  equipped with arbitrary-precision arithmetic. These additions allow the new
-  FOMC algorithm to scale to domain sizes over \num{500000} times larger than
-  the current state of the art, as demonstrated through experimental results.
-\end{abstract}
-
-\section{Introduction}
-
-\emph{First-order model counting} (FOMC) is the task of determining the number
-of models for a sentence in first-order logic over a specified domain. The
-weighted variant, WFOMC, computes the total weight of these models, linking
-logical reasoning with probabilistic
-frameworks~\cite{DBLP:conf/ijcai/BroeckTMDR11}. It builds upon earlier efforts
-in weighted model counting for propositional
-logic~\cite{DBLP:journals/ai/ChaviraD08} and broader attempts to bridge logic
-and
-probability~\cite{DBLP:journals/ai/Nilsson86,novak2012mathematical,vsaletic2024graded}.
-WFOMC is central to \emph{lifted inference}, which enhances the efficiency of
-probabilistic calculations by exploiting
-symmetries~\cite{DBLP:conf/ecai/Kersting12}. Lifted inference continues to
-advance, with applications extending to constraint satisfaction
-problems~\cite{DBLP:journals/jair/TotisDRK23} and probabilistic answer set
-programming~\cite{DBLP:journals/ijar/AzzoliniR23}. Moreover, WFOMC has proven
-effective at reasoning over probabilistic
-databases~\cite{DBLP:journals/debu/GribkoffSB14} and probabilistic logic
-programs~\cite{DBLP:journals/ijar/RiguzziBZCL17}. FOMC algorithms have also
-facilitated breakthroughs in discovering integer
-sequences~\cite{DBLP:conf/ijcai/SvatosJT0K23} and developing recurrence
-relations for these sequences~\cite{DBLP:conf/kr/DilkasB23}. Recently, these
-algorithms have been extended to perform sampling
-tasks~\cite{DBLP:journals/ai/WangPWK24}.
-
-The complexity of FOMC is generally measured by \emph{data complexity}, with a
-sentence classified as \emph{liftable} if it admits a polynomial-time solution
-relative to the domain size~\cite{DBLP:conf/starai/JaegerB12}. While all
-sentences with up to two variables are known to be
-liftable~\cite{DBLP:conf/nips/Broeck11,DBLP:conf/kr/BroeckMD14}, Beame et
-al.~\cite{DBLP:conf/pods/BeameBGS15} demonstrated that liftability does not
-extend to all sentences, identifying an unliftable sentence with three
-variables. Recent work has extended the liftable fragment with additional
-axioms~\cite{DBLP:conf/aaai/TothK23,DBLP:journals/ai/BremenK23} and counting
-quantifiers~\cite{DBLP:journals/jair/Kuzelka21}, expanding our understanding of
-liftability.
-
-FOMC algorithms are diverse, with approaches ranging from \emph{first-order
-  knowledge compilation} (FOKC) to cell
-enumeration~\cite{DBLP:conf/uai/BremenK21}, local
-search~\cite{DBLP:journals/pvldb/NiuRDS11}, and Monte Carlo
-sampling~\cite{DBLP:journals/cacm/GogateD16}. (See the technical appendix for a
-more detailed comparison of the state-of-the-art FOMC algorithms.) FOKC-based
-algorithms are particularly prominent, transforming sentences into structured
-representations such as circuits or graphs. Even when multiple algorithms can
-solve the same instance, FOKC algorithms are known to find polynomial-time
-solutions where the polynomial has a lower degree than other
-approaches~\cite{DBLP:conf/kr/DilkasB23}. The recently developed ability of a
-FOKC algorithm to formulate solutions in terms of recursive
-functions~\cite{DBLP:conf/kr/DilkasB23} is also noteworthy since the only other
-proposed alternative is to guess recursive
-relations~\cite{DBLP:conf/ilp/BarvinekB0ZK21}. Notable examples of FOKC
-algorithms include \textsc{ForcLift}~\cite{DBLP:conf/ijcai/BroeckTMDR11} and its
-extension \textsc{Crane}~\cite{DBLP:conf/kr/DilkasB23}.
-
-The \textsc{Crane} algorithm marked a significant step forward, expanding the
-range of sentences handled by FOMC algorithms. However, it had notable
-limitations: it required manual evaluation of function definitions to compute
-model counts and introduced recursive functions without proper base cases,
-making it more difficult to use. To address these shortcomings, we present
-\Cranetwo{}, a fully automated FOMC algorithm that overcomes the constraints of
-its predecessor. \Cranetwo{} can handle domain sizes over \num{500000} times
-larger than those of previous algorithms and simplifies the user experience by
-automatically managing base cases and compiling function definitions into
-efficient C++ programs.
-
-The paper is structured as follows. \Cref{sec:preliminaries} covers the
-necessary preliminaries, including notation, terminology, and background
-information about (W)FOMC and FOKC\@. \Cref{sec:main} describes all aspects of
-\Cranetwo{}:
-\begin{itemize}
-  \item its overall structure and interactions with \textsc{Crane},
-  \item how we identify a sufficient set of base cases for a recursive function,
-  \item how we construct the sentence that describes each base case, and
-  \item how we compile function definitions into a C++ program with caching
-        mechanisms that ensure efficiency.
-\end{itemize}
-Then, \cref{sec:experiments} presents our experimental results, demonstrating
-\Cranetwo{}'s performance compared to other FOMC algorithms. Finally,
-\cref{sec:conclusion} concludes the paper by discussing promising avenues for
-future work.
-
-\section{Preliminaries}\label{sec:preliminaries}
-
-We begin this section by describing some notation that we will use throughout
-the paper. Then, in \cref{sec:logic,sec:fomc}, we introduce the basic
-terminology of first-order logic and formally define (W)FOMC\@. \Cref{sec:crane}
-outlines the principles of FOKC, particularly in the context of \textsc{Crane}.
-Finally, in \cref{sec:algebra}, we introduce the algebraic terminology used to
-describe the output of \textsc{Crane}, i.e., functions and equations that define
-them.
-
-\paragraph*{Notation}
-We use $\mathbb{N}_{0}$ to represent the set of non-negative integers. In both
-algebra and logic, we write $S\sigma$ to denote the application of a
-\emph{substitution} $\sigma$ to an expression $S$, where
-$\sigma = [x_{1} \mapsto y_{1}, x_{2} \mapsto y_{2}, \dots, x_{n} \mapsto y_{n}]$
-signifies the replacement of all instances of $x_{i}$ with $y_{i}$ for all
-$i = 1, \dots, n$. Additionally, for any variable $n$ and
-$a, b \in \mathbb{N}_{0}$, let $[a \le n \le b] \coloneqq \begin{cases}
-  1 & \text{if $a \le n \le b$} \\
-  0 & \text{otherwise}
-\end{cases}$.
-
-\subsection{First-Order Logic}\label{sec:logic}
-
-This section reviews the basic concepts of first-order logic used in FOKC
-algorithms. We focus specifically on the format used internally by
-\textsc{ForcLift} and its descendants. See \cref{sec:preprocessing} for a brief
-overview of how \Cranetwo{} transforms an arbitrary sentence in first-order
-logic into this internal format.
-
-A \emph{term} can be either a variable or a constant. An \emph{atom} can be
-either $P(t_{1}, \dots, t_{m})$ (i.e., $P(\mathbf{t})$) for some predicate $P$
-and terms $t_{1}, \dots, t_{m}$, or $x=y$ for some terms $x$ and $y$. The
-\emph{arity} of a predicate is the number of arguments it takes, i.e., $m$ in
-the case of the predicate $P$ mentioned above. We write $P/m$ to denote a
-predicate along with its arity. A \emph{literal} can be either an atom (i.e., a
-\emph{positive} literal) or its negation (i.e., a \emph{negative} literal). An
-atom containing no variables, only constants, is called \emph{ground}. A
-\emph{clause} is of the form $\forall x_{1} \in \Delta_{1}\text{.
-}\forall x_{2} \in \Delta_{2}\dots\text{ }\forall x_{n} \in \Delta_{n}\text{.
-}\phi(x_{1}, x_{2}, \dots, x_{n})$, where $\phi$ is a disjunction of literals
-that contain only the variables $x_{1}, \dots, x_{n}$ (and any constants). We
-say that a clause is a \emph{(positive) unit clause} if there is only one
-literal with a predicate, and it is a positive literal. Finally, a
-\emph{sentence} is a conjunction of clauses. Throughout the paper, we will use
-set-theoretic notation, interpreting a sentence as a set of clauses and a clause
-as a set of literals.
-
-\begin{remark*}
-  Conforming to previous work~\cite{DBLP:conf/ijcai/BroeckTMDR11}, the
-  definition of a clause includes universal quantifiers for all its variables.
-  While it is possible to rewrite the entire sentence with all quantifiers at
-  the front, the format we describe has proven convenient for practical use.
-\end{remark*}
-
-\subsection{First-Order Model Counting}\label{sec:fomc}
-
-In this section, we will formally define FOMC and its weighted variant. Although
-this work focuses on FOMC, computing the FOMC using \Cranetwo{} requires using
-WFOMC for sentences with existential quantifiers. For such sentences,
-preprocessing (described in \cref{sec:preprocessing}) introduces predicates with
-non-unary weights that must be accounted for to compute the correct model count.
-
-\begin{definition}[Structure, model]\label{def:model}
-  Let $\phi$ be a sentence. For each predicate $P/n$ in $\phi$, let
-  ${(\Delta_{i}^{P})}_{i=1}^{n}$ be a list of the corresponding domains. Let
-  $\sigma$ be a map from the domains of $\phi$ to their interpretations as
-  finite sets, ensuring the sets are pairwise disjoint and contain the
-  corresponding constants from $\phi$. A \emph{structure} of $\phi$ is a set $M$
-  of ground literals defined by adding to $M$ either $P(\mathbf{t})$ or
-  $\neg P(\mathbf{t})$ for every predicate $P/n$ in $\phi$ and every $n$-tuple
-  $\mathbf{t} \in \prod_{i=1}^{n} \sigma(\Delta_{i}^{P})$. A structure is a
-  \emph{model} if it makes $\phi$ valid.
-\end{definition}
-
-\begin{example}[Counting bijections]\label{example:bijections}
-  Let us consider the following sentence (previously examined by Dilkas and
-  Belle~\cite{DBLP:conf/kr/DilkasB23}) that defines predicate $P$ as a bijection
-  between two domains $\Gamma$ and $\Delta$:
-  \begin{equation}\label[formula]{eq:bijections}
-    \begin{gathered}
-      (\forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }P(x, y))\land{}\\
-      (\forall y \in \Delta\text{. }\exists x \in \Gamma\text{. }P(x, y))\land{}\\
-      (\forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \Rightarrow y = z)\land{}\\
-      (\forall x, z \in \Gamma\text{. }\forall y \in \Delta\text{. }P(x, y) \land P(z, y) \Rightarrow x = z).
-    \end{gathered}
-  \end{equation}
-  Let $\sigma$ be defined as $\sigma(\Gamma) \coloneqq \{\, 1, 2\,\}$ and
-  $\sigma(\Delta) \coloneqq \{\,a, b\,\}$. \Cref{eq:bijections} has two models:
-  \[
-    \{\, P(1, a), P(2, b), \neg P(1, b), \neg P(2, a) \,\} \qquad \text{and} \qquad \{\, P(1, b), P(2, a), \neg P(1, a), \neg P(2, b) \,\}.
-  \]
-\end{example}
-
-\begin{remark*}
-  The distinctness of domains is significant in two respects. First, in terms of
-  expressiveness, a clause such as $\forall x \in \Delta\text{. }P(x, x)$ is
-  valid if predicate $P$ operates over two copies of the same domain and invalid
-  otherwise. Second, having more distinct domains makes the problem more
-  decomposable for the FOKC algorithm. With distinct domains, the algorithm can
-  make assumptions or deductions about, e.g., the first domain of predicate $P$
-  without worrying how (or if) they apply to the second domain.
-\end{remark*}
-
-\begin{definition}[WFOMC instance]\label{def:instance}
-  A \emph{WFOMC instance} comprises:
-  \begin{itemize}
-    \item a sentence $\phi$,
-    \item two (rational) \emph{weights} $w^{+}(P)$ and $w^{-}(P)$ assigned to
-          each predicate $P$ in $\phi$, and
-    \item $\sigma$ as described in \cref{def:model}.
-  \end{itemize}
-  Unless specified otherwise, we assume all weights are equal to 1.
-\end{definition}
-
-\begin{definition}[WFOMC~\cite{DBLP:conf/ijcai/BroeckTMDR11}]
-  Given a WFOMC instance $(\phi, w^{+}, w^{-}, \sigma)$ as in
-  \cref{def:instance}, the \emph{(symmetric) weighted first-order model count}
-  (WFOMC) of $\phi$ is
-  \begin{equation}\label{eq:wfomc}
-    \sum_{M \models \phi} \prod_{P(\mathbf{t}) \in M} w^{+}(P) \prod_{\neg P(\mathbf{t}) \in M} w^{-}(P),
-  \end{equation}
-  where the sum is over all models of $\phi$.
-\end{definition}
-
-\subsection{Crane and First-Order Knowledge Compilation}\label{sec:crane}
-
-As our work builds on \textsc{Crane}, in this section, we will briefly outline
-the steps \textsc{Crane} goes through to compile a sentence into a set of
-function definitions. We divide the inner workings of the algorithm into two
-stages: preprocessing and compilation.
-
-\subsubsection{Preprocessing}\label{sec:preprocessing}
-
-This stage transforms an arbitrary sentence into the format described in
-\cref{sec:logic}, primarily by eliminating existential quantifiers. For example,
-the first conjunct of \cref{eq:bijections}, i.e.,
-\begin{equation}\label[formula]{eq:skolemizationinitial}
-  \forall x \in \Gamma\text{. }\exists y \in \Delta\text{. } P(x, y)
-\end{equation}
-is transformed into
-\begin{equation}\label[formula]{eq:skolemization}
-  \begin{aligned}
-    (\forall x \in \Gamma\text{. } &Z(x))\land{}\\
-    (\forall x \in \Gamma\text{. } \forall y \in \Delta\text{. } &Z(x) \lor \neg P(x, y))\land{}\\
-    (\forall x \in \Gamma\text{. } &S(x) \lor Z(x))\land{}\\
-    (\forall x \in \Gamma\text{. } \forall y \in \Delta\text{. } &S(x) \lor \neg P(x, y)),
-  \end{aligned}
-\end{equation}
-where $Z/1$ and $S/1$ are two new predicates with $w^{-}(S) = -1$. One can
-verify that the WFOMC of \cref{eq:skolemizationinitial,eq:skolemization} is the
-same.
-
-\subsubsection{Compilation}\label{sec:compilation}
-
-After preprocessing, \textsc{Crane} compiles the sentence into the triple
-$(\mathcal{E}, \mathcal{F}, \mathcal{D})$, where $\mathcal{E}$ is the set of
-equations, and $\mathcal{F}$ and $\mathcal{D}$ are auxiliary maps. $\mathcal{F}$
-maps function names to sentences. $\mathcal{D}$ maps function names and argument
-indices to domains. $\mathcal{E}$ can contain any number of functions, one of
-which (which we will always denote as $f$) represents the solution to the FOMC
-problem. Computing the FOMC for specific domain sizes involves invoking $f$ with
-those sizes as inputs. $\mathcal{D}$ records this correspondence between
-function arguments and domains.
-
-\begin{example}\label{example:solution}
-  \textsc{Crane} compiles \cref{eq:bijections} for bijection counting into
-  \begin{align*}
-    \mathcal{E} &= \left\{\,\begin{aligned}f(m, n) &= \sum_{l=0}^{n} \binom{n}{l}{(-1)}^{n-l}g(l, m),\\ g(l, m) &= \sum_{k=0}^{m}[0 \le k \le 1]\binom{m}{k}g(l-1, m-k)\end{aligned}\,\right\};\\
-    \mathcal{D} &= \{\, (f, 1) \mapsto \Gamma, (f, 2) \mapsto \Delta, (g, 1) \mapsto \Delta^{\top}, (g, 2) \mapsto \Gamma \,\},
-  \end{align*}
-  where $\Delta^{\top}$ is a newly introduced domain. (We omit the definition of
-  $\mathcal{F}$ as the sentences can become quite verbose.) To compute the
-  number of bijections between two sets of cardinality 3, one would evaluate
-  $f(3, 3)$; however, the definition of $g$ is incomplete: $g$ is a recursive
-  function presented without any base cases. $\mathcal{D}$ encodes that in
-  $f(m, n)$, $m$ and $n$ represent $|\Gamma|$ and $|\Delta|$, respectively.
-  Similarly, in $g(l, m)$, $l$ represents $|\Delta^{\top}|$, and $m$ represents
-  $|\Gamma|$.
-\end{example}
-
-Compilation is performed primarily by applying \emph{(compilation) rules} to
-sentences. \textsc{Crane} has two modes depending on the selection process for
-compilation rules when multiple alternatives are available. The first option is
-to use greedy search: there is a list of rules, and the first applicable rule is
-the one that gets used, disregarding all the others. The second option is to use
-a combination of greedy and \emph{breadth-first search} (BFS). In this approach,
-we classify each compilation rule as greedy or non-greedy. Greedy rules are
-applied as soon as possible at any stage of the compilation process, while BFS
-is executed over all applicable non-greedy rules, identifying the solution that
-necessitates the smallest number of non-greedy rules.
-
-\subsection{Algebra}\label{sec:algebra}
-
-In this paper, we use both logical and algebraic constructs. While the rest of
-\cref{sec:preliminaries} focused on the former, this section describes the
-latter. We write $\expr{}$ for an arbitrary algebraic expression. In the context
-of algebra, a \emph{constant} is a non-negative integer. Likewise, a
-\emph{variable} can either be a parameter of a function or a variable introduced
-through summation, such as $i$ in the expression $\sum_{i=1}^{n} \expr$. A
-\emph{function call} is $f(x_{1}, \dots, x_{n})$ (or $f(\mathbf{x})$ for short),
-where $f$ is an $n$-ary function, and each $x_{i}$ is an algebraic expression
-consisting of variables and constants. A (function) \emph{signature} is a
-function call that contains only variables. Given two function calls,
-$f(\mathbf{x})$ and $f(\mathbf{y})$, we say that $f(\mathbf{y})$ \emph{matches}
-$f(\mathbf{x})$ if $x_{i} = y_{i}$ whenever $x_{i}, y_{i} \in \mathbb{N}_{0}$.
-An \emph{equation} is $f(\mathbf{x}) = \expr{}$, where $f(\mathbf{x})$ is a
-function call.
-
-\begin{definition}[Base case]\label{def:basecase}
-  Let $f(\mathbf{x})$ be a function call where each $x_{i}$ is either a constant
-  or a variable. Then the function call $f(\mathbf{y})$ is a \emph{base case} of
-  $f(\mathbf{x})$ if $f(\mathbf{y}) = f(\mathbf{x})\sigma$, where $\sigma$ is a
-  substitution that replaces one or more \emph{variable} $x_{i}$'s with a
-  constant while leaving constants unchanged.
-\end{definition}
-
-\begin{example}
-  In the equation $f(m, n) = f(m-1, n) + nf(m-1, n-1)$, the only constant is
-  $1$, and the variables are $m$ and $n$. The equation contains three function
-  calls: one on the left-hand side (LHS) and two on the right-hand side (RHS).
-  The function call on the LHS is a signature. Function calls such as $f(4, n)$,
-  $f(m, 0)$, and $f(8, 1)$ are all considered base cases of $f(m, n)$ (only some
-  of which are useful).
-\end{example}
-
-\section{Technical Contributions}\label{sec:main}
-
-\begin{figure*}[t]
+\begin{frame}{Knowledge Compilation Workflow}
   \centering
   \begin{tikzpicture}
-    \node[anchor=west] at (-1, 0) (formula) {$\phi$};
+    % Top row
+    \node[anchor=west] at (-0.5, 0) (formula) {$\phi$};
     \node[draw,rounded rectangle] at (3, 0) (compilewithbasecases) {\CompileWithBaseCases};
-    \node[draw,rounded rectangle] at (9, 0) (compilation) {Compile to C++};
+    \node[draw,rounded rectangle] at (8, 0) (compilation) {Compile to C++};
 
-    \node[draw,rounded rectangle,dashed] at (9, -3) (cpp) {C++ code};
+    % Bottom row
+    \node[draw,rounded rectangle,dashed] at (8, -3) (cpp) {C++ code};
     \node[anchor=west] at (-1, -3) (sizes) {Domain sizes};
-    \node at (12, -3) (count) {Answer};
+    \node at (8, -4) (count) {Model count};
 
-    \node[draw,rounded rectangle] at (3, -2) (findbasecases) {\FindBaseCases};
-    \node[draw,rounded rectangle,left = 0.1cm of findbasecases] (crane) {\Compile};
-    \node[draw,rounded rectangle,right = 0.1cm of findbasecases] (propagate) {\Propagate};
-    \node[draw,rounded rectangle,right = 0.1cm of propagate] (simplify) {\Simplify};
+    % Modules
+    \node[draw,rounded rectangle,anchor=north west] at (1.2, -1) (crane) {\Compile};
+    \node[draw,rounded rectangle,right=0.1cm of crane] (findbasecases) {\FindBaseCases};
+    \node[draw,rounded rectangle,anchor=north west] at (1.2, -1.6) (propagate) {\Propagate};
+    \node[draw,rounded rectangle,right=0.1cm of propagate] (simplify) {\Simplify};
 
+    % Bounding box and its name
     \node[draw,fit={(compilewithbasecases) (compilation) (crane) (findbasecases) (propagate)},inner ysep=7pt,yshift=5pt] {};
-    \node at (0.7, 0.5) {\Cranetwo};
+    \node at (1.5, 0.5) {\Cranetwo};
 
+    % Brace and its arrow
+    \node[fit=(crane)(findbasecases)(propagate)(simplify)] (uses) {};
+    \draw[decorate,decoration={brace}] (uses.north west) -- (uses.north east) node[midway] (brace) {};
+    \draw[-Latex,dashed] (compilewithbasecases) -- node[midway,left] {uses} (brace);
+
+    % All other arrows
     \draw[-Latex] (formula) -- (compilewithbasecases);
@@
     \draw[-Latex] (cpp) -- (count);
-
-    \draw[-Latex,dashed] (compilewithbasecases) -- node[midway,left] {uses} (crane);
-    \draw[-Latex,dashed] (compilewithbasecases) -- node[midway,left] {uses} (findbasecases);
-    \draw[-Latex,dashed] (compilewithbasecases) -- node[midway,left] {uses} (propagate);
-    \draw[-Latex,dashed] (compilewithbasecases) -- node[midway,right] {uses} (simplify);
-  \end{tikzpicture}
-  \caption[]{Using \Cranetwo{} to compute the model count of a sentence $\phi$.
-    First, \Cranetwo{} compiles $\phi$ into a set of equations, which form the
-    basis for creating a C++ program. Executing the program with different
-    command line arguments calculates the model count of $\phi$ for various
-    domain sizes. To accomplish this, the \CompileWithBaseCases procedure
-    employs \textsc{Crane}, algebraic simplification techniques (denoted as
-    \Simplify), and two other auxiliary procedures. }\label{fig:overview}
-\end{figure*}
-
-\Cref{fig:overview} provides an overview of \Cranetwo{}'s workflow. We will
-briefly describe and motivate each procedure before going into more detail in
-the corresponding subsection.
-
-\CompileWithBaseCases (see \cref{sec:completing}), the core procedure of
-\Cranetwo{}, is responsible for completing the function definitions produced by
-\textsc{Crane} with the necessary base cases. To do so, it may recursively call
-itself (and \textsc{Crane}) on other sentences. We prove that the number of such
-recursive calls is upper bound by the number of domains.
-
-\cref{sec:completing} also describes the \Simplify procedure for algebraic
-simplification. It is crucial for simplifying, e.g., a sum of $n$ terms, only
-some of which are non-zero. More generally, the equations returned by
-\textsc{Crane} often benefit from easily detectable algebraic simplifications
-such as $0 \cdot \text{anything} = 0$ and $\text{anything}^{0} = 1$.
-
-\FindBaseCases (described in \cref{sec:identifying}) inspects a set of equations
-to identify a sufficient set of base cases for a given set of equations. We
-prove that the returned set of base cases ensures that the evaluation of the
-resulting function definitions will never get stuck in an infinite loop.
-
-\Cref{sec:propagating} introduces the \Propagate procedure, which takes a
-sentence $\phi$, a domain $\Delta$, and $n \in \mathbb{N}_{0}$. It returns
-$\phi$ transformed under the assumption that $|\Delta| = n$, with $n$ new
-constants added and all variables quantified over $\Delta$ eliminated. For
-example, when computing a base case such as $f(0, y)$, \Propagate will
-significantly simplify $\phi$ with the assumption that the domain associated
-with the first parameter of $f$ (i.e., $\mathcal{D}(f, 1)$) is empty.
-\CompileWithBaseCases{\Propagate{$\phi$, $\mathcal{D}(f, 1)$, $0$}} will then
-return the equations for the base case $f(0, y)$.
-
-\Cref{sec:smoothing} describes a new \emph{smoothing} procedure that ensures
-\Propagate preserves the correct model count. Smoothing is a well-known
-technique in knowledge compilation algorithms for propositional model
-counting~\cite{darwiche2001tractable}. Although FOMC algorithms have used
-smoothing before~\cite{DBLP:conf/ijcai/BroeckTMDR11}, our setting requires a
-novel approach.
-
-With the help of other procedures outlined above, \CompileWithBaseCases returns
-a set of equations that fully cover the base cases of all recursive functions.
-While these equations can be intriguing and valuable in their own right, users
-of FOMC algorithms typically expect a numerical answer. Thus, \cref{sec:cpp}
-describes how \Cranetwo{} compiles these equations into a C++ program that one
-can execute with different command-line arguments to compute the model count for
-various combinations of domain sizes.
-
-\subsection{Completing the Definitions of Functions}\label{sec:completing}
-
-\begin{algorithm}[t]
-  \caption{\protect\CompileWithBaseCases{$\phi$}}\label{alg:compilewithbasecases}
-  \KwIn{sentence $\phi$}
-  \KwOut{set $\mathcal{E}$ of equations}
-  $(\mathcal{E}, \mathcal{F}, \mathcal{D}) \gets \Compile{$\phi$}$\;
-  $\mathcal{E} \gets \Simplify{$\mathcal{E}$}$\;\label{line:second}
-  \ForEach{base case $f(\mathbf{x}) \in \FindBaseCases{$\mathcal{E}$}$}{\label{line:loopy}
-    $\psi \gets \mathcal{F}(f)$\;
-    \lForEach{index $i$ such that $x_{i} \in \mathbb{N}_{0}$}{$\psi \gets \Propagate{$\psi$, $\mathcal{D}(f, i)$, $x_i$}$}\label{line:propagate}
-    $\mathcal{E} \gets \mathcal{E} \cup \CompileWithBaseCases{$\psi$}$\;\label{line:final}
-  }
-\end{algorithm}
-
-\Cref{alg:compilewithbasecases} presents our overall approach for compiling a
-sentence into equations that include the necessary base cases. First, we use
-\textsc{Crane} to compile the sentence into three components: $\mathcal{E}$,
-$\mathcal{F}$, and $\mathcal{D}$ (as described in \cref{sec:compilation}). After
-some algebraic simplifications (described below), the algorithm passes
-$\mathcal{E}$ to the \FindBaseCases procedure (see \cref{sec:identifying}). For
-each base case $f(\mathbf{x})$, we retrieve the sentence $\mathcal{F}(f)$
-associated with the function name $f$ and simplify it using the \Propagate
-procedure (explained in detail in \cref{sec:propagating}). We do this by
-iterating over all indices of $\mathbf{x}$, where $x_{i}$ is a constant, and
-using \Propagate to simplify $\psi$ by assuming that domain $\mathcal{D}(f, i)$
-has size $x_{i}$. Finally, on \autoref{line:final}, \CompileWithBaseCases
-recurses on these simplified sentences and adds the resulting base case
-equations to $\mathcal{E}$.
-
-\paragraph*{Simplify}
-The main responsibility of the \Simplify procedure is to handle the algebraic
-pattern $\sum_{m=0}^{n}[a \le m \le b] f(m)$. Here, $n$ is a variable, $a$ and
-$b$ are constants, and $f$ is an expression that may depend on $m$. \Simplify
-transforms this pattern into $f(a) + f(a+1) + \cdots + f(\min\{\, n, b \,\})$.
-
-\begin{example}\label{example:bijectionstwo}
-  {\par\sloppy
-  We return to the bijection-counting problem from \cref{example:bijections} and
-  its initial solution described in \cref{example:solution}. \Simplify
-  transforms
-  \[
-    g(l, m) = \sum_{k=0}^{m}[0 \le k \le 1]\binom{m}{k}g(l-1, m-k)
-  \]
-  into
-  \[
-    g(l, m) = g(l-1, m) + mg(l-1, m-1).
-  \]
-  Then \FindBaseCases identifies two base cases: $g(0, m)$ and $g(l, 0)$. In
-  both cases, \CompileWithBaseCases recurses on the sentence $\mathcal{F}(g)$
-  simplified by assuming that one of the domains is empty. In the first case, we
-  recurse on the sentence $\forall x \in \Gamma\text{. }S(x) \lor \neg S(x)$,
-  where $S$ is a predicate introduced by preprocessing with weights
-  $w^{+}(S) = 1$ and $w^{-}(S) = -1$. Hence, we obtain the base case
-  $g(0, m) = 0^{m}$. In the case of $g(l, 0)$, \Propagate{$\psi$, $\Gamma$, $0$}
-  returns an empty sentence, resulting in $g(l, 0) = 1$. While these base cases
-  overlap when $l = m = 0$, they remain consistent since $0^{0} = 1$.
-  \par}
-\end{example}
-
-Generally, let $\phi$ be a sentence with two domains $\Gamma$ and $\Delta$, and
-let $n, m \in \mathbb{N}_{0}$. Then the FOMC of \Propagate{$\phi$, $\Delta$,
-  $n$}, assuming $|\Gamma| = m$, is the same as the FOMC of \Propagate{$\phi$,
-  $\Gamma$, $m$}, assuming $|\Delta| = n$.
-
-Although \CompileWithBaseCases starts with a call to \textsc{Crane}, the
-proposed algorithm is not merely a post-processing step for FOKC because
-\cref{alg:compilewithbasecases} is recursive and can issue additional calls to
-\textsc{Crane} on various derived sentences. We conclude this section by
-bounding the recursion depth of the \CompileWithBaseCases procedure, thereby
-also proving that the algorithm terminates.
-
-\begin{theorem}
-  Let $\phi$ be a sentence with $n$ domains. The maximum recursion depth of
-  \CompileWithBaseCases{$\phi$} is then $n$.
-\end{theorem}
-
-The proof of this theorem relies on two observations regarding the algorithms
-presented in \cref{sec:identifying,sec:propagating}.
-
-\begin{observation}\label{observation1}
-  Each base case returned by \FindBaseCases contains at least one constant (in
-  line with \cref{def:basecase}).
-\end{observation}
-
-\begin{observation}\label{observation2}
-  For any sentence $\phi$, domain $\Delta$, and $n \in \mathbb{N}_{0}$,
-  \Propagate{$\phi$, $\Delta$, $n$} returns a sentence with no variables
-  quantified over $\Delta$.
-\end{observation}
-
-\begin{proof}
-  We proceed by induction on $n$. If $n=0$, then $\phi$ is essentially a
-  propositional formula, and \textsc{Crane} compiles it into an equation of the
-  form $f = \expr$ with no `function calls'. Suppose that---for all sentences
-  with at most $n$ domains---\CompileWithBaseCases terminates with a recursion
-  depth of at most $n$. Let $\phi$ be a sentence with $n+1$ domains. By
-  \cref{observation1}, each base case on \autoref{line:loopy} of
-  \cref{alg:compilewithbasecases} has at least one constant. Therefore, by
-  \cref{observation2}, after \autoref{line:propagate}, the sentence $\psi$ has
-  at most $n$ domains. Thus, \autoref{line:final} terminates with a recursion
-  depth of at most $n$ by the inductive hypothesis, completing the inductive
-  proof.
-\end{proof}
-
-\subsection{Identifying a Sufficient Set of Base Cases}\label{sec:identifying}
-
-\begin{algorithm}[t]
-  \caption{\protect\FindBaseCases{$\mathcal{E}$}}\label{alg:findbasecases}
-  \KwIn{set $\mathcal{E}$ of equations}
-  \KwOut{set $\mathcal{B}$ of base cases}
-
-  $\mathcal{B} \gets \emptyset$\;
-  \ForEach{function call $f(\mathbf{y})$ on the RHS of an equation in $\mathcal{E}$}{
-    $\mathbf{x} \gets \text{the parameters of $f$ in its definition}$\;
-    \ForEach{$y_{i} \in \mathbf{y}$} {
-      \lIf{$y_{i} \in \mathbb{N}_{0}$}{$\mathcal{B} \gets \mathcal{B} \cup \{\, f(\mathbf{x})[x_{i} \mapsto y_{i}] \,\}$}\label{line:constant}
-      \ElseIf{$y_{i} = x_{i} - c_{i}$ for some $c_{i} \in \mathbb{N}_{0}$}{
-        \lFor{$j \gets 0$ \KwTo $c_{i} - 1$}{$\mathcal{B} \gets \mathcal{B} \cup \{\, f(\mathbf{x})[x_{i} \mapsto j] \,\}$}\label{line:nonconstant}
-      }
-    }
-  }
-\end{algorithm}
-
-\Cref{alg:findbasecases} summarises the implementation of \FindBaseCases. It
-considers two types of arguments when a function $f$ calls itself recursively:
-constants and arguments of the form $x_{i} - c_{i}$. When the argument is a
-constant $c_{i}$, \autoref{line:constant} adds a base case with $c_{i}$ to the
-set of all base cases $\mathcal{B}$. In the second case,
-\autoref{line:nonconstant} adds a base case to $\mathcal{B}$ for each constant
-from $0$ to (but not including) $c_{i}$.
-
-\begin{example}
-  Consider the recursive function $g$ from \cref{example:solution}.
-  \FindBaseCases iterates over two function calls: $g(l-1, m)$ and
-  $g(l-1, m-1)$. The former produces the base case $g(0, m)$, while the latter
-  produces both $g(0, m)$ and $g(l, 0)$.
-\end{example}
-
-In the rest of this section, we will show that the base cases identified by
-\FindBaseCases are sufficient for the algorithm to terminate.\footnote{Note that
-  characterising the fine-grained complexity of the solutions found by
-  \Cranetwo{} or other FOMC algorithms is an emerging area of research. These
-  questions have been partially addressed in previous
-  work~\cite{DBLP:conf/kr/DilkasB23,DBLP:conf/kr/TothK24} and are unrelated to
-  the goals of this section.} Let $\mathcal{E}$ denote the equations returned by
-\CompileWithBaseCases.
-
-\begin{theorem}\label{thm:halting}
-  Given an $n$-ary function $f$ in $\mathcal{E}$ and
-  $\mathbf{x} \in \mathbb{N}_{0}^{n}$, the evaluation of $f(\mathbf{x})$
-  terminates.
-\end{theorem}
-
-We prove \cref{thm:halting} using double induction. First, we apply induction to
-the number of functions in $\mathcal{E}$. Then, we use induction on the arity of
-the `last' function in $\mathcal{E}$ according to a topological ordering. Before
-proving \cref{thm:halting}, we make a few observations about this and
-previous~\cite{DBLP:conf/kr/DilkasB23,DBLP:conf/ijcai/BroeckTMDR11} work.
-
-\begin{observation}\label{assumption1}
-  For each function $f$, there is precisely one equation $e \in \mathcal{E}$
-  with $f(\mathbf{x})$ on the LHS where all $x_{i}$'s are variables (i.e., $e$
-  is not a base case). We refer to $e$ as the \emph{definition} of $f$.
-\end{observation}
-
-\begin{observation}\label{assumption2}
-  There is a \emph{topological ordering} ${(f_{i})}_{i}$ of all functions in
-  $\mathcal{E}$ such that equations in $\mathcal{E}$ with $f_{i}$ on the LHS do
-  not contain function calls to $f_{j}$ with $j > i$.
-\end{observation}
-
-\Cref{assumption2} prevents mutual recursion and other cyclic scenarios.
-
-\begin{observation}\label{assumption3}
-  For each equation $(f(\mathbf{x}) = \expr) \in \mathcal{E}$, the evaluation
-  of $\expr$ terminates when provided with the values of all relevant function
-  calls.
-\end{observation}
-
-\begin{corollary}\label{fact}
-  If $f$ is a non-recursive function with no function calls on the RHS of its
-  definition, then the evaluation of any function call $f(\mathbf{x})$
-  terminates.
-\end{corollary}
-
-\begin{observation}\label{fact2}
-  For each equation $(f(\mathbf{x}) = \expr{}) \in \mathcal{E}$, if $\mathbf{x}$
-  contains only constants, then $\expr{}$ cannot include any function calls to
-  $f$.
-\end{observation}
-
-Additionally, we introduce an assumption about the structure of recursion.
-
-\begin{assumption}\label{assumption4}
-  For each equation $(f(\mathbf{x}) = \expr) \in \mathcal{E}$, every recursive
-  function call $f(\mathbf{y}) \in \expr$ satisfies the following:
-  \begin{itemize}
-    \item each $y_{i}$ is either $x_{i} - c_{i}$ or $c_{i}$ for some constant
-          $c_{i}$ and
-    \item there exists $i$ such that $y_{i} = x_{i} - c_{i}$ for some
-          $c_{i} > 0$.
-  \end{itemize}
-\end{assumption}
-
-Finally, we assume a particular order of evaluation for function calls using the
-equations in $\mathcal{E}$; specifically, base cases precede the recursive
-definition.
-
-\begin{assumption}
-  When multiple equations in $\mathcal{E}$ match a function call
-  $f(\mathbf{x})$, preference is given to the equation with the most constants
-  on its LHS.
-\end{assumption}
-
-With the observations and assumptions mentioned above, we are ready to prove
-\cref{thm:halting}. For readability, we divide the proof into several lemmas of
-increasing generality.
-
-\begin{lemma}\label{lemma:oneunary}
-  Assume that $\mathcal{E}$ consists of just \emph{one unary} function called
-  $f$. Then the evaluation of $f(x)$ terminates for any $x \in \mathbb{N}_{0}$.
-\end{lemma}
-\begin{proof}
-  If $f(x)$ matches a base case, then its evaluation terminates by
-  \cref{fact,fact2}. If $f$ is not recursive, the evaluation of $f(x)$ also
-  terminates by \cref{fact}.
-
-  Otherwise, let $f(y)$ be an arbitrary function call on the RHS of the
-  definition of $f(x)$. If $y$ is a constant, then there is a base case for
-  $f(y)$. Otherwise, let $y = x - c$ for some $c > 0$. Then there exists
-  $k \in \mathbb{N}_{0}$ such that $0 \le x - kc \le c-1$. So, after $k$
-  iterations, the sequence of function calls $f(x), f(x-c), f(x-2c),\dots$ will
-  match the base case $f(x \mod c)$.
-\end{proof}
-
-\begin{lemma}\label{lemma:onefunction}
-  Generalising \cref{lemma:oneunary}, let $\mathcal{E}$ be a set of equations
-  for \emph{one} $n$-ary function $f$ for some $n \ge 1$. The evaluation of
-  $f(\mathbf{x})$ terminates for any $\mathbf{x} \in \mathbb{N}_{0}^{n}$.
-\end{lemma}
-\begin{proof}
-  If $f$ is non-recursive, the evaluation of $f(\mathbf{x})$ terminates by
-  previous arguments. We proceed by induction on $n$, with the base case of
-  $n=1$ handled by \cref{lemma:oneunary}. Assume that $n > 1$. Any base case of
-  $f$ can be seen as a function of arity $n-1$ since one of the parameters is
-  constant. Thus, the evaluation of any base case terminates by the inductive
-  hypothesis. It remains to show that the evaluation of the recursive equation
-  for $f$ terminates, but this follows from \cref{assumption3}.
-\end{proof}
-
-\begin{proof}[Proof of \cref{thm:halting}]
-  We proceed by induction on the number of functions $n$. The base case of $n=1$
-  is handled by \cref{lemma:onefunction}. Let ${(f_{i})}_{i=1}^{n}$ be some
-  topological ordering of these $n > 1$ functions. If $f = f_{j}$ for $j < n$,
-  then the evaluation of $f(\mathbf{x})$ terminates by the inductive hypothesis
-  since $f_{j}$ cannot call $f_{n}$ by \cref{assumption2}. Using the inductive
-  hypothesis that all function calls to $f_{j}$ (with $j < n$) terminate, the
-  proof proceeds similarly to the proof of \cref{lemma:onefunction}.
-\end{proof}
-
-\subsection{Propagating Domain Size Assumptions}\label{sec:propagating}
-
-\begin{algorithm}[t]
-  \caption{\protect\Propagate{$\phi$, $\Delta$, $n$}}\label{alg:propagate}
-  \KwIn{sentence $\phi$, domain $\Delta$, $n \in \mathbb{N}_{0}$}
-  \KwOut{sentence $\phi'$}
-  $\phi' \gets \emptyset$\;
-  \uIf{$n = 0$}{
-    \ForEach{clause $C \in \phi$}{
-      \lIf{$\Delta \not\in \Doms(C)$}{$\phi' \gets \phi' \cup \{\, C \,\}$}
-      \Else{
-        $C' \gets \{\, l \in C \mid \Delta \not\in \Doms(l) \,\}$\;
-        \If{$C' \ne \emptyset$}{\label{line:presmoothing}
-          $l \gets \text{an arbitrary literal in } C'$\;\label{line:smoothing1}
-          $\phi' \gets \phi' \cup \{\, C' \cup \{\, \neg l \,\} \,\} $\;\label{line:smoothing2}
-        }
-      }
-    }
-  }
-  \Else{
-    $D \gets \text{a set of $n$ new constants in $\Delta$}$\;
-    \ForEach{clause $C \in \phi$}{
-      ${(x_{i})}_{i=1}^{m} \gets \text{the variables in $C$ with domain $\Delta$}$\;
-      \lIf{$m = 0$}{$\phi' \gets \phi' \cup \{\, C \,\}$}
-      \lElse{$\phi' \gets \phi' \cup \{\, C[x_{1} \mapsto c_{1}, \dots, x_{m} \mapsto c_{m}] \mid {(c_{i})}_{i=1}^{m} \in D^{m} \,\}$}
-    }
-  }
-\end{algorithm}
-
-\Cref{alg:propagate}, called \Propagate, modifies the sentence $\phi$ based on
-the assumption that $|\Delta| = n$. When $n=0$, some clauses become vacuously
-satisfied and can be removed. When $n > 0$, partial grounding replaces all
-variables with domain $\Delta$ with constants. (None of the sentences examined
-in this work had $n > 1$.) \Cref{alg:propagate} handles these two cases
-separately. For a literal or clause $C$, we write the set of corresponding
-domains as $\Doms(C)$. In the case of $n = 0$, there are three types of clauses
-to consider:
-\begin{enumerate}
-  \item those that do not mention $\Delta$,\label[type]{type1}
-  \item those in which every literal contains variables quantified over
-  $\Delta$ and\label[type]{type2}
-  \item those with some literals containing such variables and some
-        without.\label[type]{type3}
-\end{enumerate}
-We transfer clauses of \cref{type1} to the new sentence $\phi'$ without any
-changes. For clauses of \cref{type2}, $C'$ is empty, so these clauses are
-filtered out. As for clauses of \cref{type3},
-lines~\ref{line:presmoothing}--\ref{line:smoothing2} perform a new kind of
-smoothing, the explanation of which we defer to \cref{sec:smoothing}.
-
-In the case of $n>0$, $n$ new constants are introduced. Let $C$ be an arbitrary
-clause in $\phi$, and let $m \in \mathbb{N}_{0}$ be the number of variables in
-$C$ quantified over $\Delta$. If $m=0$, $C$ is added directly to $\phi'$.
-Otherwise, a clause is added to $\phi'$ for every possible combination of
-replacing the $m$ variables in $C$ with the $n$ new constants.
-
-\begin{example}
-  Let $C \coloneqq \forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{.
-  } \neg P(x, y) \lor \neg P(x, z) \lor y=z$. Then
-  $\Doms(C) = \Doms(\neg P(x, y)) = \Doms(\neg P(x, z)) = \{\, \Gamma, \Delta \,\}$,
-  and $\Doms(y=z) = \{\, \Delta \,\}$. A call to \Propagate{$\{\, C \,\}$,
-    $\Delta$, $3$} would result in the following sentence with nine clauses:
-  \begin{align*}
-    (\forall x \in \Gamma\text{. }\neg P(x, c_{1}) \lor& \neg P(x, c_{1}) \lor c_{1}=c_{1})\land{}\\
-    (\forall x \in \Gamma\text{. }\neg P(x, c_{1}) \lor& \neg P(x, c_{2}) \lor c_{1}=c_{2})\land{}\\
-    \vdots&\\
-    (\forall x \in \Gamma\text{. }\neg P(x, c_{3}) \lor& \neg P(x, c_{3}) \lor c_{3}=c_{3}).
-  \end{align*}
-  Here, $c_{1}$, $c_{2}$, and $c_{3}$ are the new constants.
-\end{example}
-
-\subsection{Smoothing the Base Cases}\label{sec:smoothing}
-
-Smoothing modifies a circuit to reintroduce eliminated atoms, ensuring the
-correct model count~\cite{darwiche2001tractable,DBLP:conf/ijcai/BroeckTMDR11}.
-This section describes a similar process performed on
-lines~\ref{line:presmoothing}--\ref{line:smoothing2} of \cref{alg:propagate}.
-Line~\ref{line:presmoothing} checks if smoothing is necessary, and
-lines~\ref{line:smoothing1} and~\ref{line:smoothing2} execute it. If the
-condition on \autoref{line:presmoothing} is not satisfied, the clause is not
-smoothed but omitted.
-
-Suppose \CompileWithBaseCases calls \Propagate with arguments
-$(\phi, \Delta, 0)$, i.e., we are simplifying the sentence $\phi$ by assuming
-that the domain $\Delta$ is empty. Informally, if there is a predicate $P$ in
-$\phi$ unrelated to $\Delta$, smoothing preserves all occurrences of $P$, even
-if all clauses with $P$ become vacuously satisfied.
-
-\begin{example}\label{example:basecasesmoothing}
-  Let $\phi$ be
-  \begin{align}
-    (\forall x \in \Delta\text{. }\forall y, z \in \Gamma&\text{. }Q(x) \lor P(y, z))\land{}\label[clause]{eq:example1}\\
-    (\forall y, z \in \Gamma'&\text{. }P(y, z))\label[clause]{eq:example2},
-  \end{align}
-  where $\Gamma' \subseteq \Gamma$ is a domain introduced by a compilation rule.
-  Note that $P$, as a relation, is a subset of $\Gamma \times \Gamma$.
-
-  Now, let us reason manually about the model count of $\phi$ when
-  $\Delta = \emptyset$. Predicate $Q$ can only take one value, $Q = \emptyset$.
-  The value of $P$ is fixed over $\Gamma' \times \Gamma'$ by \cref{eq:example2},
-  but it can vary freely over
-  $(\Gamma \times \Gamma) \setminus (\Gamma' \times \Gamma')$ since
-  \cref{eq:example1} is vacuously satisfied by all structures. Therefore, the
-  correct FOMC should be $2^{|\Gamma|^2 - |\Gamma'|^2}$. However, without
-  \autoref{line:smoothing2}, \Propagate would simplify $\phi$ to
-  $\forall y, z \in \Gamma'\text{. }P(y, z)$. In this case, $P$ is a subset of
-  $\Gamma' \times \Gamma'$. This simplified sentence has only one model:
-  $\{\, P(y, z) \mid y, z \in \Gamma' \,\}$. By including
-  \autoref{line:smoothing2}, \Propagate transforms $\phi$ to
-  \[
-    (\forall y, z \in \Gamma\text{. }P(y, z) \lor \neg P(y, z)) \land (\forall y, z \in \Gamma'\text{. }P(y, z)),
-  \]
-  which retains the correct model count.
-\end{example}
-
-It is worth mentioning that the choice of $l$ on \autoref{line:smoothing1} of
-\cref{alg:propagate} is inconsequential because any choice achieves the same
-goal: constructing a tautological clause that retains the literals in $C'$.
-
-\subsection{Generating C++ Code}\label{sec:cpp}
-
-In this section, we will describe the final step of \Cranetwo{} as outlined in
-\cref{fig:overview}, i.e., translating the set of equations $\mathcal{E}$ into
-C++ code. Recall that this step is crucial for the usability of the algorithm;
-otherwise, function definitions would remain purely mathematical, with no
-convenient way to compute the model count for particular domain sizes. Once a
-C++ program is produced, it can be executed with different command-line
-arguments to determine the model count of the sentence for various domain sizes.
-
-\begin{algorithm}[t]
-  \caption{A sketch of the C++ program for the equations in
-    \cref{example:solution}, particularly highlighting the recursive definition
-    of the function $g$.}\label{alg:cpp}
-  initialise $\Cache_{g(0, m)}$, $\Cache_{g(l, 0)}$, $\Cache_{g}$, and
-  $\Cache_{f}$\; \DontPrintSemicolon \textbf{Function} $g_{0,m}(m)$\textbf{:}
-  \dots\; \textbf{Function} $g_{l,0}(l)$\textbf{:} \dots\; \PrintSemicolon
-  \Fn{$g(l, m)$}{
-    \lIf{$(l, m) \in \Cache_{g}$}{\Return{$\Cache_{g}(l, m)$}}\label{line:cache}
-    \lIf{$l = 0$}{\Return{$g_{0,m}(m)$}}\label{line:basecaseone}
-    \lIf{$m = 0$}{\Return{$g_{l,0}(l)$}}\label{line:basecasetwo}
-    $r \gets g(l-1, m) + mg(l-1,m-1)$\; $\Cache_{g}(l, m) \gets r$\;
-    \Return{$r$}\; } \DontPrintSemicolon \textbf{Function} $f(m, n)$\textbf{:}
-  \dots\; \PrintSemicolon \Fn{\Main}{ $(m, n) \gets \Input{}$\;
-    \Return{$f(m, n)$}\; }
-\end{algorithm}
-
-See \cref{alg:cpp} for the typical structure of a generated C++ program. Each
-equation in $\mathcal{E}$ turns into a C++ function with a separate cache for
-memoisation. Hence, \cref{alg:cpp} has a function and a cache for
-$f(\cdot, \cdot)$, $g(\cdot, \cdot)$, $g(\cdot, 0)$, and $g(0, \cdot)$. The
-implementation of an equation consists of three parts. First (on
-\autoref{line:cache}), we check if the arguments already exist in the
-corresponding cache. If they do, we return the cached value. Second (on
-lines~\ref{line:basecaseone} and~\ref{line:basecasetwo}), we check if the
-arguments match any of the base cases (as defined in \cref{sec:algebra}). If so,
-we redirect the arguments to the C++ function for that base case. Finally, if
-none of the above cases applies, we evaluate the arguments based on the
-expression on the RHS of the equation, store the result in the cache, and return
-it.
-
-\section{Experimental Evaluation}\label{sec:experiments}
-
-Our empirical evaluation sought to compare the runtime performance of
-{\Cranetwo} with the current state of the art, namely
-\textsc{FastWFOMC}\footnote{\url{https://github.com/jan-toth/FastWFOMC.jl}}~\cite{DBLP:conf/kr/TothK24,DBLP:conf/uai/BremenK21}
-and \textsc{ForcLift}\footnote{\url{https://github.com/UCLA-StarAI/Forclift}}.
-Our experiments involved two versions of \Cranetwo{}: \Cranegreedy{} and
-\Cranebfs{}. Like its predecessor (see \cref{sec:compilation}), \Cranetwo{} has
-two modes for applying compilation rules to sentences: one that uses a greedy
-search algorithm similar to \textsc{ForcLift} and another that combines greedy
-and BFS\@.
-
-The experiments used an Intel Skylake \SI{2.4}{\giga\hertz} CPU with
-\SI{188}{\gibi\byte} of memory and CentOS~7. We used the Intel C++ Compiler
-2020u4 for C++ programs, Julia~1.10.4 for \textsc{FastWFOMC}, and the Java
-Virtual Machine 1.8.0\_201 for \textsc{ForcLift} and \Cranetwo{}. Although
-implemented in different languages, \Cranetwo{} and \textsc{FastWFOMC} use the
-same GNU Multiple Precision Arithmetic Library for arbitrary-precision
-arithmetic.
-
-We ran each algorithm on each benchmark using domains of size
-$2^{1}, 2^{2}, 2^{3}$, and so on until an algorithm failed to handle a domain
-size due to a timeout (of one hour) or out-of-memory or out-of-precision errors.
-While we separately measured compilation and inference time, we primarily focus
-on total runtime, dominated by the latter. We verified the accuracy of the
-numerical answers using the corresponding integer sequences in the On-Line
-Encyclopedia of Integer Sequences~\cite{oeis}.
-
-\subsection{Benchmarks}
-
-We compare these algorithms using three benchmarks from previous work. The first
-benchmark is the bijection-counting problem from \cref{example:bijections}. The
-second benchmark is a variant of the well-known \friends{} Markov logic
-network~\cite{DBLP:conf/aaai/SinglaD08,DBLP:conf/uai/BroeckCD12}, which takes
-the form of
-\[
-  (\forall x,y \in \Delta\text{.
-  } S(x) \land F(x, y) \Rightarrow S(y)) \land (\forall x \in \Delta\text{.
-  }S(x) \Rightarrow C(x)).
-\]
-In this sentence, we have three predicates, $S$, $F$, and $C$, that denote
-smoking, friendship, and cancer, respectively. The first clause states that
-friends of smokers are also smokers, and the second clause asserts that smoking
-causes cancer. Common additions to this sentence include making the friendship
-relation symmetric and assigning probabilities to each clause. Finally, we
-include the function-counting problem~\cite{DBLP:conf/kr/DilkasB23}
-\begin{equation}\label[formula]{eq:functions}
-  (\forall x \in \Gamma\text{. }\exists y \in \Delta\text{.
-  }P(x, y)) \land (\forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{.
-  }P(x, y) \land P(x, z) \Rightarrow y = z)
-\end{equation}
-as our third benchmark. Here, predicate $P$ represents a function from $\Gamma$
-to $\Delta$. The first clause asserts that each $x$ must have at least one
-corresponding $y$, while the second clause ensures the uniqueness of such a $y$.
-
-\begin{remark*}
-  We formulate the \bijections{} and \functions{} benchmarks using two domains,
-  $\Gamma$ and $\Delta$, as this formulation is known to help FOKC algorithms
-  find efficient solutions~\cite{DBLP:conf/kr/DilkasB23}. To compare \Cranetwo{}
-  and \textsc{ForcLift} with \textsc{FastWFOMC}, which has no support for
-  multiple domains, we set $|\Gamma| = |\Delta|$.
-\end{remark*}
-
-The three benchmarks cover a wide range of possibilities. The \friends{}
-benchmark uses multiple predicates and only two variables without employing any
-constructs specific to only one of the (W)FOMC algorithms. The \functions{}
-benchmark, on the other hand, can still be handled by all the algorithms, but
-its formulation relies on algorithm-specific constructs. Namely, for
-\textsc{ForcLift} and \Cranetwo{}, the sentence is written using three
-variables. Since \textsc{FastWFOMC} supports at most two variables, we rewrite
-the \cref{eq:functions} with two variables and a \emph{cardinality constraint}
-(see the technical appendix for details about translating the benchmarks to
-other first-order logics). Lastly, the \bijections{} benchmark is an example of
-a sentence that \textsc{FastWFOMC} can handle but \textsc{ForcLift} cannot.
-
-\subsection{Results}
-
-\begin{figure*}[t]
-  \centering
-  \includegraphics{plot.pdf}
-  \caption{The runtime of the algorithms as a function of domain size. Note that
-    both axes are on a logarithmic scale.}\label{fig:plot}
-\end{figure*}
-
-\Cref{fig:plot} presents a summary of the experimental results. Only
-\textsc{FastWFOMC} and \Cranebfs{} could handle the bijection-counting problem.
-For this benchmark, the largest domain sizes these algorithms could accommodate
-were \num{64} and \num{4096}, respectively. On the other two benchmarks,
-\textsc{ForcLift} had the lowest runtime. However, since it can only handle
-model counts smaller than $2^{31}$, it only scales up to domain sizes of
-\num{16} and \num{128} for \friends{} and \functions{}, respectively.
-\textsc{FastWFOMC} outperformed \textsc{ForcLift} in the case of \friends{}, but
-not \functions{}, as it could handle domains of size \num{1024} and \num{64},
-respectively. Furthermore, both \Cranebfs{} and \Cranegreedy{} performed
-similarly on both benchmarks. Similarly to the \bijections{} benchmark,
-\Cranetwo{} significantly outperformed the other two algorithms, scaling up to
-domains of size \num{8192} and \num{67108864}, respectively.
-
-One might notice that the runtime of \textsc{FastWFOMC} and \textsc{ForcLift} is
-slightly higher for the smallest domain size. This peculiarity is the
-consequence of \emph{just-in-time} (JIT) compilation. As \Cranetwo{} is only run
-once per benchmark, we include the JIT compilation time in its overall runtime
-across all domain sizes. Additionally, while the compilation time of
-\textsc{ForcLift} is generally lower compared to \Cranetwo{}, neither
-significantly affects the overall runtime. Specifically, \textsc{ForcLift}
-compilation typically takes around \SI{0.5}{\second}, while \Cranetwo{}
-compilation takes around \SI{2.3}{\second}.
-
-Based on our experiments, which algorithm should one use in practice? If
-\textsc{ForcLift} can handle the sentence and the domain sizes are reasonably
-small, it is likely the fastest algorithm. In other situations, \Cranetwo{} will
-likely be significantly more efficient than \textsc{FastWFOMC} regardless of
-domain size, provided both algorithms can handle the sentence.
-
-\section{Conclusion and Future Work}\label{sec:conclusion}
-
-In this work, we have presented a scalable, automated FOKC-based approach to
-FOMC\@. Our algorithm involves completing the definitions of recursive functions
-and subsequently translating all function definitions into C++ code. Empirical
-results demonstrate that \Cranetwo{} can scale to larger domain sizes than
-\textsc{FastWFOMC} while supporting a wider range of sentences than
-\textsc{ForcLift}. The ability to efficiently handle large domain sizes is
-particularly crucial in the weighted setting, as illustrated by the \friends{}
-example, where the model captures complex social networks with probabilistic
-relationships. Without this scalability, these models would have limited
-practical value.
-
-Future directions for research include conducting a comprehensive experimental
-comparison of FOMC algorithms to better understand their comparative performance
-across various sentences. The capabilities of \Cranetwo{} could also be
-characterised theoretically, for example, by proving completeness for logic
-fragments liftable by other
-algorithms~\cite{DBLP:journals/jair/Kuzelka21,DBLP:conf/aaai/TothK23,DBLP:journals/ai/BremenK23}.
-Additionally, the efficiency of FOMC algorithms can be further analysed using
-fine-grained complexity, which would provide more detailed insights into the
-computational demands of different sentences.
-
-\bibliography{paper}
+  \end{tikzpicture} % TODO: maybe add colours?
+\end{frame}
 

### 2025-06-13 doc/talk/bijections.tex
Add experimental results

% Created by tikzDevice version 0.12.6 on 2025-06-13 10:38:09
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (307.15,216.81);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (307.15,216.81);
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 29.55, 66.00) --
	(302.65, 66.00);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 29.55,118.22) --
	(302.65,118.22);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 29.55,170.44) --
	(302.65,170.44);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 53.24, 57.56) --
	( 53.24,212.31);

\path[draw=drawColor,line width= 0.2pt,line join=round] (120.96, 57.56) --
	(120.96,212.31);

\path[draw=drawColor,line width= 0.2pt,line join=round] (188.67, 57.56) --
	(188.67,212.31);

\path[draw=drawColor,line width= 0.2pt,line join=round] (256.38, 57.56) --
	(256.38,212.31);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 29.55, 92.11) --
	(302.65, 92.11);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 29.55,144.33) --
	(302.65,144.33);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 29.55,196.55) --
	(302.65,196.55);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 87.10, 57.56) --
	( 87.10,212.31);

\path[draw=drawColor,line width= 0.5pt,line join=round] (154.81, 57.56) --
	(154.81,212.31);

\path[draw=drawColor,line width= 0.5pt,line join=round] (222.52, 57.56) --
	(222.52,212.31);

\path[draw=drawColor,line width= 0.5pt,line join=round] (290.23, 57.56) --
	(290.23,212.31);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.96, 64.59) --
	( 64.53, 64.59) --
	( 87.10, 64.59) --
	(109.67, 64.59) --
	(132.24, 64.59) --
	(154.81, 64.60) --
	(177.38, 64.62) --
	(199.95, 64.73) --
	(222.52, 65.13) --
	(245.09, 66.75) --
	(267.66, 73.60) --
	(290.23, 93.28);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] ( 41.96,107.13) --
	( 64.53, 79.15) --
	( 87.10, 79.15) --
	(109.67, 79.64) --
	(132.24, 96.07) --
	(154.81,205.28);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] ( 41.96, 64.59) circle (  1.96);

\path[fill=fillColor] ( 64.53, 64.59) circle (  1.96);

\path[fill=fillColor] ( 87.10, 64.59) circle (  1.96);

\path[fill=fillColor] (109.67, 64.59) circle (  1.96);

\path[fill=fillColor] (132.24, 64.59) circle (  1.96);

\path[fill=fillColor] (154.81, 64.60) circle (  1.96);

\path[fill=fillColor] (177.38, 64.62) circle (  1.96);

\path[fill=fillColor] (199.95, 64.73) circle (  1.96);

\path[fill=fillColor] (222.52, 65.13) circle (  1.96);

\path[fill=fillColor] (245.09, 66.75) circle (  1.96);

\path[fill=fillColor] (267.66, 73.60) circle (  1.96);

\path[fill=fillColor] (290.23, 93.28) circle (  1.96);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] ( 40.00,105.17) --
	( 43.92,105.17) --
	( 43.92,109.10) --
	( 40.00,109.10) --
	cycle;

\path[fill=fillColor] ( 62.57, 77.18) --
	( 66.49, 77.18) --
	( 66.49, 81.11) --
	( 62.57, 81.11) --
	cycle;

\path[fill=fillColor] ( 85.14, 77.18) --
	( 89.06, 77.18) --
	( 89.06, 81.11) --
	( 85.14, 81.11) --
	cycle;

\path[fill=fillColor] (107.71, 77.68) --
	(111.63, 77.68) --
	(111.63, 81.60) --
	(107.71, 81.60) --
	cycle;

\path[fill=fillColor] (130.28, 94.10) --
	(134.20, 94.10) --
	(134.20, 98.03) --
	(130.28, 98.03) --
	cycle;

\path[fill=fillColor] (152.85,203.31) --
	(156.77,203.31) --
	(156.77,207.24) --
	(152.85,207.24) --
	cycle;
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.96, 57.56) -- ( 41.96, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 64.53, 57.56) -- ( 64.53, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 87.10, 57.56) -- ( 87.10, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (109.67, 57.56) -- (109.67, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (132.24, 57.56) -- (132.24, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (154.81, 57.56) -- (154.81, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (177.38, 57.56) -- (177.38, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (199.95, 57.56) -- (199.95, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (222.52, 57.56) -- (222.52, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (245.09, 57.56) -- (245.09, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (267.66, 57.56) -- (267.66, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (290.23, 57.56) -- (290.23, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55, 66.00) -- ( 35.24, 66.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55, 92.11) -- ( 35.24, 92.11);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55,118.22) -- ( 35.24,118.22);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55,144.33) -- ( 35.24,144.33);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55,170.44) -- ( 35.24,170.44);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55,196.55) -- ( 35.24,196.55);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 25.50, 89.63) {16};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 25.50,141.85) {64};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 25.50,194.07) {256};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 27.30, 92.11) --
	( 29.55, 92.11);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 27.30,144.33) --
	( 29.55,144.33);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 27.30,196.55) --
	( 29.55,196.55);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 87.10, 55.31) --
	( 87.10, 57.56);

\path[draw=drawColor,line width= 0.5pt,line join=round] (154.81, 55.31) --
	(154.81, 57.56);

\path[draw=drawColor,line width= 0.5pt,line join=round] (222.52, 55.31) --
	(222.52, 57.56);

\path[draw=drawColor,line width= 0.5pt,line join=round] (290.23, 55.31) --
	(290.23, 57.56);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 87.10, 48.55) {$2^{3}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (154.81, 48.55) {$2^{6}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (222.52, 48.55) {$2^{9}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (290.23, 48.55) {$2^{12}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (166.10, 38.70) {Domain size};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 10.70,134.94) {Total runtime (s)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 91.84,  4.50) rectangle (240.35, 27.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] (100.84,  9.00) rectangle (115.30, 23.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (102.29, 16.23) -- (113.85, 16.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] (108.07, 16.23) circle (  1.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] (168.91,  9.00) rectangle (183.36, 23.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (170.36, 16.23) -- (181.92, 16.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] (174.17, 14.26) --
	(178.10, 14.26) --
	(178.10, 18.19) --
	(174.17, 18.19) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (119.80, 13.75) {\textsc{Crane2-BFS}};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (187.86, 13.75) {\textsc{FastWFOMC}};
\end{scope}
\end{tikzpicture}

\end{document}

### 2025-06-13 doc/talk/friends.tex
Add experimental results

% Created by tikzDevice version 0.12.6 on 2025-06-13 10:42:02
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (307.15,216.81);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (307.15,216.81);
\end{scope}
\begin{scope}
\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] ( 33.14, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14, 71.38) --
	(302.65, 71.38);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14,105.92) --
	(302.65,105.92);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14,140.45) --
	(302.65,140.45);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14,174.99) --
	(302.65,174.99);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 33.14,209.53) --
	(302.65,209.53);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 55.60, 57.56) --
	( 55.60,212.31);

\path[draw=drawColor,line width= 0.2pt,line join=round] (116.85, 57.56) --
	(116.85,212.31);

\path[draw=drawColor,line width= 0.2pt,line join=round] (178.10, 57.56) --
	(178.10,212.31);

\path[draw=drawColor,line width= 0.2pt,line join=round] (239.36, 57.56) --
	(239.36,212.31);

\path[draw=drawColor,line width= 0.2pt,line join=round] (300.61, 57.56) --
	(300.61,212.31);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 33.14, 88.65) --
	(302.65, 88.65);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 33.14,123.18) --
	(302.65,123.18);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 33.14,157.72) --
	(302.65,157.72);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 33.14,192.26) --
	(302.65,192.26);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 86.23, 57.56) --
	( 86.23,212.31);

\path[draw=drawColor,line width= 0.5pt,line join=round] (147.48, 57.56) --
	(147.48,212.31);

\path[draw=drawColor,line width= 0.5pt,line join=round] (208.73, 57.56) --
	(208.73,212.31);

\path[draw=drawColor,line width= 0.5pt,line join=round] (269.98, 57.56) --
	(269.98,212.31);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 45.39, 90.51) --
	( 65.81, 90.50) --
	( 86.23, 90.50) --
	(106.65, 90.50) --
	(127.06, 90.50) --
	(147.48, 90.50) --
	(167.90, 90.51) --
	(188.31, 90.59) --
	(208.73, 91.56) --
	(229.15,101.10) --
	(249.56,129.63) --
	(269.98,167.15) --
	(290.40,205.28);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 45.39, 90.23) --
	( 65.81, 90.22) --
	( 86.23, 90.22) --
	(106.65, 90.22) --
	(127.06, 90.22) --
	(147.48, 90.22) --
	(167.90, 90.23) --
	(188.31, 90.31) --
	(208.73, 91.30) --
	(229.15,100.97) --
	(249.56,129.66) --
	(269.98,167.14) --
	(290.40,205.28);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 45.39,118.59) --
	( 65.81,117.07) --
	( 86.23,116.78) --
	(106.65,116.86) --
	(127.06,117.36) --
	(147.48,117.53) --
	(167.90,117.77) --
	(188.31,121.87) --
	(208.73,137.98) --
	(229.15,179.16);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 45.39, 69.46) --
	( 65.81, 64.59) --
	( 86.23, 64.59) --
	(106.65, 64.59);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] ( 43.43,116.62) --
	( 47.36,116.62) --
	( 47.36,120.55) --
	( 43.43,120.55) --
	cycle;

\path[fill=fillColor] ( 63.85,115.10) --
	( 67.77,115.10) --
	( 67.77,119.03) --
	( 63.85,119.03) --
	cycle;

\path[fill=fillColor] ( 84.27,114.82) --
	( 88.19,114.82) --
	( 88.19,118.74) --
	( 84.27,118.74) --
	cycle;

\path[fill=fillColor] (104.68,114.89) --
	(108.61,114.89) --
	(108.61,118.82) --
	(104.68,118.82) --
	cycle;

\path[fill=fillColor] (125.10,115.40) --
	(129.02,115.40) --
	(129.02,119.33) --
	(125.10,119.33) --
	cycle;

\path[fill=fillColor] (145.52,115.56) --
	(149.44,115.56) --
	(149.44,119.49) --
	(145.52,119.49) --
	cycle;

\path[fill=fillColor] (165.93,115.81) --
	(169.86,115.81) --
	(169.86,119.73) --
	(165.93,119.73) --
	cycle;

\path[fill=fillColor] (186.35,119.91) --
	(190.28,119.91) --
	(190.28,123.83) --
	(186.35,123.83) --
	cycle;

\path[fill=fillColor] (206.77,136.02) --
	(210.69,136.02) --
	(210.69,139.94) --
	(206.77,139.94) --
	cycle;

\path[fill=fillColor] (227.18,177.20) --
	(231.11,177.20) --
	(231.11,181.13) --
	(227.18,181.13) --
	cycle;
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor] ( 45.39, 93.28) --
	( 48.04, 88.70) --
	( 42.75, 88.70) --
	cycle;

\path[fill=fillColor] ( 65.81, 93.27) --
	( 68.45, 88.70) --
	( 63.17, 88.70) --
	cycle;

\path[fill=fillColor] ( 86.23, 93.27) --
	( 88.87, 88.70) --
	( 83.59, 88.70) --
	cycle;

\path[fill=fillColor] (106.65, 93.27) --
	(109.29, 88.70) --
	(104.00, 88.70) --
	cycle;

\path[fill=fillColor] (127.06, 93.27) --
	(129.70, 88.70) --
	(124.42, 88.70) --
	cycle;

\path[fill=fillColor] (147.48, 93.27) --
	(150.12, 88.70) --
	(144.84, 88.70) --
	cycle;

\path[fill=fillColor] (167.90, 93.28) --
	(170.54, 88.70) --
	(165.25, 88.70) --
	cycle;

\path[fill=fillColor] (188.31, 93.36) --
	(190.96, 88.79) --
	(185.67, 88.79) --
	cycle;

\path[fill=fillColor] (208.73, 94.35) --
	(211.37, 89.77) --
	(206.09, 89.77) --
	cycle;

\path[fill=fillColor] (229.15,104.02) --
	(231.79, 99.44) --
	(226.50, 99.44) --
	cycle;

\path[fill=fillColor] (249.56,132.72) --
	(252.21,128.14) --
	(246.92,128.14) --
	cycle;

\path[fill=fillColor] (269.98,170.20) --
	(272.62,165.62) --
	(267.34,165.62) --
	cycle;

\path[fill=fillColor] (290.40,208.33) --
	(293.04,203.75) --
	(287.75,203.75) --
	cycle;

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 42.62, 69.46) -- ( 48.17, 69.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 45.39, 66.69) -- ( 45.39, 72.24);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 63.04, 64.59) -- ( 68.59, 64.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 65.81, 61.82) -- ( 65.81, 67.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.45, 64.59) -- ( 89.00, 64.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 86.23, 61.82) -- ( 86.23, 67.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (103.87, 64.59) -- (109.42, 64.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (106.65, 61.82) -- (106.65, 67.37);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] ( 45.39, 90.51) circle (  1.96);

\path[fill=fillColor] ( 65.81, 90.50) circle (  1.96);

\path[fill=fillColor] ( 86.23, 90.50) circle (  1.96);

\path[fill=fillColor] (106.65, 90.50) circle (  1.96);

\path[fill=fillColor] (127.06, 90.50) circle (  1.96);

\path[fill=fillColor] (147.48, 90.50) circle (  1.96);

\path[fill=fillColor] (167.90, 90.51) circle (  1.96);

\path[fill=fillColor] (188.31, 90.59) circle (  1.96);

\path[fill=fillColor] (208.73, 91.56) circle (  1.96);

\path[fill=fillColor] (229.15,101.10) circle (  1.96);

\path[fill=fillColor] (249.56,129.63) circle (  1.96);

\path[fill=fillColor] (269.98,167.15) circle (  1.96);

\path[fill=fillColor] (290.40,205.28) circle (  1.96);
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 45.39, 57.56) -- ( 45.39, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 65.81, 57.56) -- ( 65.81, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 86.23, 57.56) -- ( 86.23, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (106.65, 57.56) -- (106.65, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (127.06, 57.56) -- (127.06, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (147.48, 57.56) -- (147.48, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (167.90, 57.56) -- (167.90, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (188.31, 57.56) -- (188.31, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (208.73, 57.56) -- (208.73, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (229.15, 57.56) -- (229.15, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (249.56, 57.56) -- (249.56, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (269.98, 57.56) -- (269.98, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (290.40, 57.56) -- (290.40, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 65.62) -- ( 38.84, 65.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 77.13) -- ( 38.84, 77.13);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14, 88.65) -- ( 38.84, 88.65);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,100.16) -- ( 38.84,100.16);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,111.67) -- ( 38.84,111.67);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,123.18) -- ( 38.84,123.18);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,134.70) -- ( 38.84,134.70);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,146.21) -- ( 38.84,146.21);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,157.72) -- ( 38.84,157.72);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,169.23) -- ( 38.84,169.23);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,180.75) -- ( 38.84,180.75);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,192.26) -- ( 38.84,192.26);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,203.77) -- ( 38.84,203.77);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 29.09, 86.17) {2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 29.09,120.71) {16};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 29.09,155.24) {128};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 29.09,189.78) {1024};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 30.89, 88.65) --
	( 33.14, 88.65);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 30.89,123.18) --
	( 33.14,123.18);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 30.89,157.72) --
	( 33.14,157.72);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 30.89,192.26) --
	( 33.14,192.26);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 86.23, 55.31) --
	( 86.23, 57.56);

\path[draw=drawColor,line width= 0.5pt,line join=round] (147.48, 55.31) --
	(147.48, 57.56);

\path[draw=drawColor,line width= 0.5pt,line join=round] (208.73, 55.31) --
	(208.73, 57.56);

\path[draw=drawColor,line width= 0.5pt,line join=round] (269.98, 55.31) --
	(269.98, 57.56);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 86.23, 48.55) {$2^{3}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (147.48, 48.55) {$2^{6}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (208.73, 48.55) {$2^{9}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (269.98, 48.55) {$2^{12}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (167.90, 38.70) {Domain size};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 10.70,134.94) {Total runtime (s)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 25.21,  4.50) rectangle (310.58, 27.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] ( 34.21,  9.00) rectangle ( 48.67, 23.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.66, 16.23) -- ( 47.22, 16.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] ( 41.44, 16.23) circle (  1.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] (102.28,  9.00) rectangle (116.73, 23.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (103.72, 16.23) -- (115.29, 16.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor] (109.51, 19.28) --
	(112.15, 14.70) --
	(106.86, 14.70) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] (182.61,  9.00) rectangle (197.06, 23.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (184.05, 16.23) -- (195.62, 16.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] (187.87, 14.26) --
	(191.80, 14.26) --
	(191.80, 18.19) --
	(187.87, 18.19) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] (254.05,  9.00) rectangle (268.50, 23.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (255.49, 16.23) -- (267.06, 16.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (258.50, 16.23) -- (264.05, 16.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (261.27, 13.45) -- (261.27, 19.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 53.17, 13.75) {\textsc{Crane2-BFS}};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (121.23, 13.75) {\textsc{Crane2-Greedy}};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (201.56, 13.75) {\textsc{FastWFOMC}};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (273.00, 13.75) {\textsc{ForcLift}};
\end{scope}
\end{tikzpicture}

\end{document}

### 2025-06-13 doc/talk/functions.tex
Add experimental results

% Created by tikzDevice version 0.12.6 on 2025-06-13 10:38:23
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}
\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (307.15,216.81);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (307.15,216.81);
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 29.55, 72.61) --
	(302.65, 72.61);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 29.55,118.05) --
	(302.65,118.05);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 29.55,163.49) --
	(302.65,163.49);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 29.55,208.93) --
	(302.65,208.93);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 32.03, 57.56) --
	( 32.03,212.31);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 46.92, 57.56) --
	( 46.92,212.31);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 76.72, 57.56) --
	( 76.72,212.31);

\path[draw=drawColor,line width= 0.2pt,line join=round] (106.51, 57.56) --
	(106.51,212.31);

\path[draw=drawColor,line width= 0.2pt,line join=round] (136.30, 57.56) --
	(136.30,212.31);

\path[draw=drawColor,line width= 0.2pt,line join=round] (166.10, 57.56) --
	(166.10,212.31);

\path[draw=drawColor,line width= 0.2pt,line join=round] (195.89, 57.56) --
	(195.89,212.31);

\path[draw=drawColor,line width= 0.2pt,line join=round] (225.68, 57.56) --
	(225.68,212.31);

\path[draw=drawColor,line width= 0.2pt,line join=round] (255.48, 57.56) --
	(255.48,212.31);

\path[draw=drawColor,line width= 0.2pt,line join=round] (285.27, 57.56) --
	(285.27,212.31);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 29.55, 95.33) --
	(302.65, 95.33);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 29.55,140.77) --
	(302.65,140.77);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 29.55,186.21) --
	(302.65,186.21);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 61.82, 57.56) --
	( 61.82,212.31);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 91.61, 57.56) --
	( 91.61,212.31);

\path[draw=drawColor,line width= 0.5pt,line join=round] (121.41, 57.56) --
	(121.41,212.31);

\path[draw=drawColor,line width= 0.5pt,line join=round] (151.20, 57.56) --
	(151.20,212.31);

\path[draw=drawColor,line width= 0.5pt,line join=round] (180.99, 57.56) --
	(180.99,212.31);

\path[draw=drawColor,line width= 0.5pt,line join=round] (210.79, 57.56) --
	(210.79,212.31);

\path[draw=drawColor,line width= 0.5pt,line join=round] (240.58, 57.56) --
	(240.58,212.31);

\path[draw=drawColor,line width= 0.5pt,line join=round] (270.37, 57.56) --
	(270.37,212.31);

\path[draw=drawColor,line width= 0.5pt,line join=round] (300.16, 57.56) --
	(300.16,212.31);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 41.96,100.51) --
	( 51.89,100.51) --
	( 61.82,100.51) --
	( 71.75,100.51) --
	( 81.68,100.51) --
	( 91.61,100.52) --
	(101.55,100.51) --
	(111.48,100.51) --
	(121.41,100.51) --
	(131.34,100.52) --
	(141.27,100.52) --
	(151.20,100.52) --
	(161.13,100.54) --
	(171.06,100.55) --
	(180.99,100.64) --
	(190.92,100.79) --
	(200.85,101.17) --
	(210.79,102.14) --
	(220.72,104.25) --
	(230.65,109.09) --
	(240.58,117.17) --
	(250.51,128.32) --
	(260.44,143.70) --
	(270.37,162.78) --
	(280.30,179.90) --
	(290.23,198.27);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 41.96, 98.94) --
	( 51.89, 98.94) --
	( 61.82, 98.94) --
	( 71.75, 98.94) --
	( 81.68, 98.94) --
	( 91.61, 98.94) --
	(101.55, 98.95) --
	(111.48, 98.94) --
	(121.41, 98.94) --
	(131.34, 98.95) --
	(141.27, 98.95) --
	(151.20, 98.95) --
	(161.13, 98.96) --
	(171.06, 98.98) --
	(180.99, 99.07) --
	(190.92, 99.24) --
	(200.85, 99.65) --
	(210.79,100.67) --
	(220.72,102.88) --
	(230.65,107.66) --
	(240.58,116.27) --
	(250.51,127.58) --
	(260.44,143.23) --
	(270.37,162.33) --
	(280.30,179.73) --
	(290.23,198.45);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 41.96,136.75) --
	( 51.89,131.71) --
	( 61.82,132.20) --
	( 71.75,131.63) --
	( 81.68,138.24) --
	( 91.61,205.28);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] ( 41.96, 67.12) --
	( 51.89, 64.59) --
	( 61.82, 64.59) --
	( 71.75, 64.59) --
	( 81.68, 64.59) --
	( 91.61, 65.04) --
	(101.55, 65.04);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] ( 41.96,100.51) circle (  1.96);

\path[fill=fillColor] ( 51.89,100.51) circle (  1.96);

\path[fill=fillColor] ( 61.82,100.51) circle (  1.96);

\path[fill=fillColor] ( 71.75,100.51) circle (  1.96);

\path[fill=fillColor] ( 81.68,100.51) circle (  1.96);

\path[fill=fillColor] ( 91.61,100.52) circle (  1.96);

\path[fill=fillColor] (101.55,100.51) circle (  1.96);

\path[fill=fillColor] (111.48,100.51) circle (  1.96);

\path[fill=fillColor] (121.41,100.51) circle (  1.96);

\path[fill=fillColor] (131.34,100.52) circle (  1.96);

\path[fill=fillColor] (141.27,100.52) circle (  1.96);

\path[fill=fillColor] (151.20,100.52) circle (  1.96);

\path[fill=fillColor] (161.13,100.54) circle (  1.96);

\path[fill=fillColor] (171.06,100.55) circle (  1.96);

\path[fill=fillColor] (180.99,100.64) circle (  1.96);

\path[fill=fillColor] (190.92,100.79) circle (  1.96);

\path[fill=fillColor] (200.85,101.17) circle (  1.96);

\path[fill=fillColor] (210.79,102.14) circle (  1.96);

\path[fill=fillColor] (220.72,104.25) circle (  1.96);

\path[fill=fillColor] (230.65,109.09) circle (  1.96);

\path[fill=fillColor] (240.58,117.17) circle (  1.96);

\path[fill=fillColor] (250.51,128.32) circle (  1.96);

\path[fill=fillColor] (260.44,143.70) circle (  1.96);

\path[fill=fillColor] (270.37,162.78) circle (  1.96);

\path[fill=fillColor] (280.30,179.90) circle (  1.96);

\path[fill=fillColor] (290.23,198.27) circle (  1.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 39.18, 67.12) -- ( 44.73, 67.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 41.96, 64.34) -- ( 41.96, 69.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.12, 64.59) -- ( 54.66, 64.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 51.89, 61.82) -- ( 51.89, 67.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 59.05, 64.59) -- ( 64.60, 64.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 61.82, 61.82) -- ( 61.82, 67.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.98, 64.59) -- ( 74.53, 64.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 71.75, 61.82) -- ( 71.75, 67.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 78.91, 64.59) -- ( 84.46, 64.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 81.68, 61.82) -- ( 81.68, 67.37);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 88.84, 65.04) -- ( 94.39, 65.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 91.61, 62.26) -- ( 91.61, 67.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 98.77, 65.04) -- (104.32, 65.04);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (101.55, 62.26) -- (101.55, 67.81);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] ( 40.00,134.78) --
	( 43.92,134.78) --
	( 43.92,138.71) --
	( 40.00,138.71) --
	cycle;

\path[fill=fillColor] ( 49.93,129.75) --
	( 53.85,129.75) --
	( 53.85,133.67) --
	( 49.93,133.67) --
	cycle;

\path[fill=fillColor] ( 59.86,130.24) --
	( 63.78,130.24) --
	( 63.78,134.16) --
	( 59.86,134.16) --
	cycle;

\path[fill=fillColor] ( 69.79,129.67) --
	( 73.71,129.67) --
	( 73.71,133.59) --
	( 69.79,133.59) --
	cycle;

\path[fill=fillColor] ( 79.72,136.28) --
	( 83.65,136.28) --
	( 83.65,140.20) --
	( 79.72,140.20) --
	cycle;

\path[fill=fillColor] ( 89.65,203.31) --
	( 93.58,203.31) --
	( 93.58,207.24) --
	( 89.65,207.24) --
	cycle;
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor] ( 41.96,101.99) --
	( 44.60, 97.41) --
	( 39.32, 97.41) --
	cycle;

\path[fill=fillColor] ( 51.89,101.99) --
	( 54.53, 97.41) --
	( 49.25, 97.41) --
	cycle;

\path[fill=fillColor] ( 61.82,101.99) --
	( 64.46, 97.41) --
	( 59.18, 97.41) --
	cycle;

\path[fill=fillColor] ( 71.75,101.99) --
	( 74.39, 97.41) --
	( 69.11, 97.41) --
	cycle;

\path[fill=fillColor] ( 81.68,101.99) --
	( 84.33, 97.41) --
	( 79.04, 97.41) --
	cycle;

\path[fill=fillColor] ( 91.61,101.99) --
	( 94.26, 97.41) --
	( 88.97, 97.41) --
	cycle;

\path[fill=fillColor] (101.55,102.00) --
	(104.19, 97.42) --
	( 98.90, 97.42) --
	cycle;

\path[fill=fillColor] (111.48,101.99) --
	(114.12, 97.41) --
	(108.83, 97.41) --
	cycle;

\path[fill=fillColor] (121.41,101.99) --
	(124.05, 97.41) --
	(118.76, 97.41) --
	cycle;

\path[fill=fillColor] (131.34,102.00) --
	(133.98, 97.42) --
	(128.70, 97.42) --
	cycle;

\path[fill=fillColor] (141.27,102.00) --
	(143.91, 97.42) --
	(138.63, 97.42) --
	cycle;

\path[fill=fillColor] (151.20,102.00) --
	(153.84, 97.42) --
	(148.56, 97.42) --
	cycle;

\path[fill=fillColor] (161.13,102.02) --
	(163.77, 97.44) --
	(158.49, 97.44) --
	cycle;

\path[fill=fillColor] (171.06,102.03) --
	(173.70, 97.46) --
	(168.42, 97.46) --
	cycle;

\path[fill=fillColor] (180.99,102.12) --
	(183.64, 97.54) --
	(178.35, 97.54) --
	cycle;

\path[fill=fillColor] (190.92,102.29) --
	(193.57, 97.71) --
	(188.28, 97.71) --
	cycle;

\path[fill=fillColor] (200.85,102.70) --
	(203.50, 98.12) --
	(198.21, 98.12) --
	cycle;

\path[fill=fillColor] (210.79,103.72) --
	(213.43, 99.15) --
	(208.14, 99.15) --
	cycle;

\path[fill=fillColor] (220.72,105.94) --
	(223.36,101.36) --
	(218.07,101.36) --
	cycle;

\path[fill=fillColor] (230.65,110.72) --
	(233.29,106.14) --
	(228.01,106.14) --
	cycle;

\path[fill=fillColor] (240.58,119.32) --
	(243.22,114.75) --
	(237.94,114.75) --
	cycle;

\path[fill=fillColor] (250.51,130.63) --
	(253.15,126.06) --
	(247.87,126.06) --
	cycle;

\path[fill=fillColor] (260.44,146.28) --
	(263.08,141.70) --
	(257.80,141.70) --
	cycle;

\path[fill=fillColor] (270.37,165.38) --
	(273.01,160.80) --
	(267.73,160.80) --
	cycle;

\path[fill=fillColor] (280.30,182.78) --
	(282.95,178.21) --
	(277.66,178.21) --
	cycle;

\path[fill=fillColor] (290.23,201.50) --
	(292.88,196.92) --
	(287.59,196.92) --
	cycle;
\definecolor{drawColor}{gray}{0.70}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 32.03, 57.56) -- ( 32.03, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 41.96, 57.56) -- ( 41.96, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 51.89, 57.56) -- ( 51.89, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 61.82, 57.56) -- ( 61.82, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 71.75, 57.56) -- ( 71.75, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 81.68, 57.56) -- ( 81.68, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 91.61, 57.56) -- ( 91.61, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (101.55, 57.56) -- (101.55, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (111.48, 57.56) -- (111.48, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (121.41, 57.56) -- (121.41, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (131.34, 57.56) -- (131.34, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (141.27, 57.56) -- (141.27, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (151.20, 57.56) -- (151.20, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (161.13, 57.56) -- (161.13, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (171.06, 57.56) -- (171.06, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (180.99, 57.56) -- (180.99, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (190.92, 57.56) -- (190.92, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (200.85, 57.56) -- (200.85, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (210.79, 57.56) -- (210.79, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (220.72, 57.56) -- (220.72, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (230.65, 57.56) -- (230.65, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (240.58, 57.56) -- (240.58, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (250.51, 57.56) -- (250.51, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (260.44, 57.56) -- (260.44, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (270.37, 57.56) -- (270.37, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (280.30, 57.56) -- (280.30, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (290.23, 57.56) -- (290.23, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (300.16, 57.56) -- (300.16, 63.25);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55, 65.04) -- ( 35.24, 65.04);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55, 80.18) -- ( 35.24, 80.18);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55, 95.33) -- ( 35.24, 95.33);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55,110.48) -- ( 35.24,110.48);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55,125.62) -- ( 35.24,125.62);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55,140.77) -- ( 35.24,140.77);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55,155.92) -- ( 35.24,155.92);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55,171.06) -- ( 35.24,171.06);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55,186.21) -- ( 35.24,186.21);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55,201.36) -- ( 35.24,201.36);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 25.50, 92.85) {2};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 25.50,138.29) {16};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 25.50,183.73) {128};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 27.30, 95.33) --
	( 29.55, 95.33);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 27.30,140.77) --
	( 29.55,140.77);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 27.30,186.21) --
	( 29.55,186.21);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 61.82, 55.31) --
	( 61.82, 57.56);

\path[draw=drawColor,line width= 0.5pt,line join=round] ( 91.61, 55.31) --
	( 91.61, 57.56);

\path[draw=drawColor,line width= 0.5pt,line join=round] (121.41, 55.31) --
	(121.41, 57.56);

\path[draw=drawColor,line width= 0.5pt,line join=round] (151.20, 55.31) --
	(151.20, 57.56);

\path[draw=drawColor,line width= 0.5pt,line join=round] (180.99, 55.31) --
	(180.99, 57.56);

\path[draw=drawColor,line width= 0.5pt,line join=round] (210.79, 55.31) --
	(210.79, 57.56);

\path[draw=drawColor,line width= 0.5pt,line join=round] (240.58, 55.31) --
	(240.58, 57.56);

\path[draw=drawColor,line width= 0.5pt,line join=round] (270.37, 55.31) --
	(270.37, 57.56);

\path[draw=drawColor,line width= 0.5pt,line join=round] (300.16, 55.31) --
	(300.16, 57.56);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{gray}{0.30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 61.82, 48.55) {$2^{3}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 91.61, 48.55) {$2^{6}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (121.41, 48.55) {$2^{9}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (151.20, 48.55) {$2^{12}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (180.99, 48.55) {$2^{15}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (210.79, 48.55) {$2^{18}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (240.58, 48.55) {$2^{21}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (270.37, 48.55) {$2^{24}$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.72] at (300.16, 48.55) {$2^{27}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (166.10, 38.70) {Domain size};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at ( 10.70,134.94) {Total runtime (s)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 23.41,  4.50) rectangle (308.78, 27.95);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] ( 32.41,  9.00) rectangle ( 46.87, 23.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{27,158,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 33.86, 16.23) -- ( 45.42, 16.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{fillColor}{RGB}{27,158,119}

\path[fill=fillColor] ( 39.64, 16.23) circle (  1.96);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] (100.48,  9.00) rectangle (114.93, 23.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.93, 16.23) -- (113.49, 16.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{fillColor}{RGB}{217,95,2}

\path[fill=fillColor] (107.71, 19.28) --
	(110.35, 14.70) --
	(105.06, 14.70) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] (180.81,  9.00) rectangle (195.26, 23.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (182.25, 16.23) -- (193.82, 16.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{fillColor}{RGB}{117,112,179}

\path[fill=fillColor] (186.07, 14.26) --
	(190.00, 14.26) --
	(190.00, 18.19) --
	(186.07, 18.19) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] (252.25,  9.00) rectangle (266.70, 23.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (253.69, 16.23) -- (265.26, 16.23);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (256.70, 16.23) -- (262.25, 16.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (259.48, 13.45) -- (259.48, 19.00);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at ( 51.37, 13.75) {\textsc{Crane2-BFS}};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (119.43, 13.75) {\textsc{Crane2-Greedy}};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (199.76, 13.75) {\textsc{FastWFOMC}};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (271.20, 13.75) {\textsc{ForcLift}};
\end{scope}
\end{tikzpicture}

\end{document}

### 2025-06-13 analysis/analyse.R

@@ -22,7 +22,8 @@ df$sequence[df$sequence == "functions"] <- "Functions"
 df <- df[df$domain.size > 1,]
 dark2_colors <- brewer.pal(8, "Dark2")
 
-df %>% group_by(algorithm, sequence) %>% summarize(compilation.time = max(compilation.time))
+# df %>% group_by(algorithm, sequence) %>%
+#   summarize(compilation.time = max(compilation.time))
 
 # Sanity check: differences between max and min counts as a percentage of the
 # min count
@@ -50,7 +51,7 @@ ggplot(df, aes(domain.size, time, color = algorithm, linetype = algorithm,
   facet_wrap(vars(sequence))
 dev.off()
 
-tikz(file = "../../misc/talks-and-notes/monthly_talk/bijections.tex",
+tikz(file = "../doc/talk/bijections.tex",
      width = 4.25, height = 3, standAlone = TRUE)
 ggplot(df[df$sequence == "Bijections",],
        aes(domain.size, time, color = algorithm, linetype = algorithm,
@@ -71,9 +72,9 @@ ggplot(df[df$sequence == "Bijections",],
   scale_shape_manual(values = c(16, 15))
 dev.off()
 
-tikz(file = "../../misc/talks-and-notes/monthly_talk/friends.tex",
+tikz(file = "../doc/talk/friends.tex",
      width = 4.25, height = 3, standAlone = TRUE)
-ggplot(df[df$sequence == "Friends",],
+ggplot(df[df$sequence == "Friends \\& Smokers",],
        aes(domain.size, time, color = algorithm, linetype = algorithm,
            shape = algorithm)) +
   geom_line() +
@@ -90,7 +91,7 @@ ggplot(df[df$sequence == "Friends",],
   scale_color_brewer(palette = "Dark2")
 dev.off()
 
-tikz(file = "../../misc/talks-and-notes/monthly_talk/functions.tex",
+tikz(file = "../doc/talk/functions.tex",
      width = 4.25, height = 3, standAlone = TRUE)
 ggplot(df[df$sequence == "Functions",],
        aes(domain.size, time, color = algorithm, linetype = algorithm,

### 2025-06-14 doc/talk/bijections.tex
Better plots

@@
-% Created by tikzDevice version 0.12.6 on 2025-06-13 10:38:09
+% Created by tikzDevice version 0.12.6 on 2025-06-14 12:11:57
 % !TEX encoding = UTF-8 Unicode
@@
 \path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
-\definecolor{fillColor}{gray}{0.92}
+\definecolor{fillColor}{RGB}{255,255,255}
 
 \path[fill=fillColor] ( 29.55, 57.56) rectangle (302.65,212.31);
-\definecolor{drawColor}{RGB}{255,255,255}
+\definecolor{drawColor}{gray}{0.92}
 
@@
 \path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55,196.55) -- ( 35.24,196.55);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (154.81,156.33) -- (290.23,156.33);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (170.46,165.36) --
+	(154.81,156.33) --
+	(170.46,147.29);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,147.29) --
+	(290.23,156.33) --
+	(274.59,165.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (154.81,156.33) -- (290.23,156.33);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (170.46,165.36) --
+	(154.81,156.33) --
+	(170.46,147.29);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,147.29) --
+	(290.23,156.33) --
+	(274.59,165.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (154.81,156.33) -- (290.23,156.33);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (170.46,165.36) --
+	(154.81,156.33) --
+	(170.46,147.29);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,147.29) --
+	(290.23,156.33) --
+	(274.59,165.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (154.81,156.33) -- (290.23,156.33);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (170.46,165.36) --
+	(154.81,156.33) --
+	(170.46,147.29);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,147.29) --
+	(290.23,156.33) --
+	(274.59,165.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (154.81,156.33) -- (290.23,156.33);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (170.46,165.36) --
+	(154.81,156.33) --
+	(170.46,147.29);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,147.29) --
+	(290.23,156.33) --
+	(274.59,165.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (154.81,156.33) -- (290.23,156.33);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (170.46,165.36) --
+	(154.81,156.33) --
+	(170.46,147.29);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,147.29) --
+	(290.23,156.33) --
+	(274.59,165.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (154.81,156.33) -- (290.23,156.33);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (170.46,165.36) --
+	(154.81,156.33) --
+	(170.46,147.29);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,147.29) --
+	(290.23,156.33) --
+	(274.59,165.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (154.81,156.33) -- (290.23,156.33);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (170.46,165.36) --
+	(154.81,156.33) --
+	(170.46,147.29);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,147.29) --
+	(290.23,156.33) --
+	(274.59,165.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (154.81,156.33) -- (290.23,156.33);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (170.46,165.36) --
+	(154.81,156.33) --
+	(170.46,147.29);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,147.29) --
+	(290.23,156.33) --
+	(274.59,165.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (154.81,156.33) -- (290.23,156.33);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (170.46,165.36) --
+	(154.81,156.33) --
+	(170.46,147.29);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,147.29) --
+	(290.23,156.33) --
+	(274.59,165.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (154.81,156.33) -- (290.23,156.33);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (170.46,165.36) --
+	(154.81,156.33) --
+	(170.46,147.29);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,147.29) --
+	(290.23,156.33) --
+	(274.59,165.36);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (154.81,156.33) -- (290.23,156.33);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (170.46,165.36) --
+	(154.81,156.33) --
+	(170.46,147.29);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,147.29) --
+	(290.23,156.33) --
+	(274.59,165.36);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (154.81,156.33) -- (290.23,156.33);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (170.46,165.36) --
+	(154.81,156.33) --
+	(170.46,147.29);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (274.59,147.29) --
+	(290.23,156.33) --
+	(274.59,165.36);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (154.81,156.33) -- (290.23,156.33);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (170.46,165.36) --
+	(154.81,156.33) --
+	(170.46,147.29);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (274.59,147.29) --
+	(290.23,156.33) --
+	(274.59,165.36);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (154.81,156.33) -- (290.23,156.33);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (170.46,165.36) --
+	(154.81,156.33) --
+	(170.46,147.29);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (274.59,147.29) --
+	(290.23,156.33) --
+	(274.59,165.36);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (154.81,156.33) -- (290.23,156.33);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (170.46,165.36) --
+	(154.81,156.33) --
+	(170.46,147.29);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (274.59,147.29) --
+	(290.23,156.33) --
+	(274.59,165.36);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (154.81,156.33) -- (290.23,156.33);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (170.46,165.36) --
+	(154.81,156.33) --
+	(170.46,147.29);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (274.59,147.29) --
+	(290.23,156.33) --
+	(274.59,165.36);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (154.81,156.33) -- (290.23,156.33);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (170.46,165.36) --
+	(154.81,156.33) --
+	(170.46,147.29);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 7pt off 3pt ,line join=round] (274.59,147.29) --
+	(290.23,156.33) --
+	(274.59,165.36);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
+	(233.67,149.20) --
+	(233.59,149.20) --
+	(233.91,149.21) --
+	(234.22,149.28) --
+	(234.52,149.39) --
+	(234.80,149.55) --
+	(235.05,149.76) --
+	(235.26,150.00) --
+	(235.43,150.27) --
+	(235.56,150.56) --
+	(235.63,150.87) --
+	(235.66,151.19) --
+	(235.66,151.19) --
+	(235.66,161.46) --
+	(235.66,161.46) --
+	(235.63,161.78) --
+	(235.56,162.09) --
+	(235.43,162.38) --
+	(235.26,162.66) --
+	(235.05,162.90) --
+	(234.80,163.10) --
+	(234.52,163.26) --
+	(234.22,163.37) --
+	(233.91,163.44) --
+	(233.67,163.45) --
+	(211.38,163.45) --
+	(211.62,163.44) --
+	(211.30,163.45) --
+	(210.98,163.41) --
+	(210.67,163.32) --
+	(210.38,163.19) --
+	(210.12,163.00) --
+	(209.89,162.78) --
+	(209.69,162.52) --
+	(209.54,162.24) --
+	(209.44,161.94) --
+	(209.39,161.62) --
+	(209.38,161.46) --
+	(209.38,151.19) --
+	(209.39,151.36) --
+	(209.39,151.03) --
+	(209.44,150.72) --
+	(209.54,150.41) --
+	(209.69,150.13) --
+	(209.89,149.87) --
+	(210.12,149.65) --
+	(210.38,149.47) --
+	(210.67,149.33) --
+	(210.98,149.24) --
+	(211.30,149.20) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
+	(233.67,149.20) --
+	(233.59,149.20) --
+	(233.91,149.21) --
+	(234.22,149.28) --
+	(234.52,149.39) --
+	(234.80,149.55) --
+	(235.05,149.76) --
+	(235.26,150.00) --
+	(235.43,150.27) --
+	(235.56,150.56) --
+	(235.63,150.87) --
+	(235.66,151.19) --
+	(235.66,151.19) --
+	(235.66,161.46) --
+	(235.66,161.46) --
+	(235.63,161.78) --
+	(235.56,162.09) --
+	(235.43,162.38) --
+	(235.26,162.66) --
+	(235.05,162.90) --
+	(234.80,163.10) --
+	(234.52,163.26) --
+	(234.22,163.37) --
+	(233.91,163.44) --
+	(233.67,163.45) --
+	(211.38,163.45) --
+	(211.62,163.44) --
+	(211.30,163.45) --
+	(210.98,163.41) --
+	(210.67,163.32) --
+	(210.38,163.19) --
+	(210.12,163.00) --
+	(209.89,162.78) --
+	(209.69,162.52) --
+	(209.54,162.24) --
+	(209.44,161.94) --
+	(209.39,161.62) --
+	(209.38,161.46) --
+	(209.38,151.19) --
+	(209.39,151.36) --
+	(209.39,151.03) --
+	(209.44,150.72) --
+	(209.54,150.41) --
+	(209.69,150.13) --
+	(209.89,149.87) --
+	(210.12,149.65) --
+	(210.38,149.47) --
+	(210.67,149.33) --
+	(210.98,149.24) --
+	(211.30,149.20) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
+	(233.67,149.20) --
+	(233.59,149.20) --
+	(233.91,149.21) --
+	(234.22,149.28) --
+	(234.52,149.39) --
+	(234.80,149.55) --
+	(235.05,149.76) --
+	(235.26,150.00) --
+	(235.43,150.27) --
+	(235.56,150.56) --
+	(235.63,150.87) --
+	(235.66,151.19) --
+	(235.66,151.19) --
+	(235.66,161.46) --
+	(235.66,161.46) --
+	(235.63,161.78) --
+	(235.56,162.09) --
+	(235.43,162.38) --
+	(235.26,162.66) --
+	(235.05,162.90) --
+	(234.80,163.10) --
+	(234.52,163.26) --
+	(234.22,163.37) --
+	(233.91,163.44) --
+	(233.67,163.45) --
+	(211.38,163.45) --
+	(211.62,163.44) --
+	(211.30,163.45) --
+	(210.98,163.41) --
+	(210.67,163.32) --
+	(210.38,163.19) --
+	(210.12,163.00) --
+	(209.89,162.78) --
+	(209.69,162.52) --
+	(209.54,162.24) --
+	(209.44,161.94) --
+	(209.39,161.62) --
+	(209.38,161.46) --
+	(209.38,151.19) --
+	(209.39,151.36) --
+	(209.39,151.03) --
+	(209.44,150.72) --
+	(209.54,150.41) --
+	(209.69,150.13) --
+	(209.89,149.87) --
+	(210.12,149.65) --
+	(210.38,149.47) --
+	(210.67,149.33) --
+	(210.98,149.24) --
+	(211.30,149.20) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
+	(233.67,149.20) --
+	(233.59,149.20) --
+	(233.91,149.21) --
+	(234.22,149.28) --
+	(234.52,149.39) --
+	(234.80,149.55) --
+	(235.05,149.76) --
+	(235.26,150.00) --
+	(235.43,150.27) --
+	(235.56,150.56) --
+	(235.63,150.87) --
+	(235.66,151.19) --
+	(235.66,151.19) --
+	(235.66,161.46) --
+	(235.66,161.46) --
+	(235.63,161.78) --
+	(235.56,162.09) --
+	(235.43,162.38) --
+	(235.26,162.66) --
+	(235.05,162.90) --
+	(234.80,163.10) --
+	(234.52,163.26) --
+	(234.22,163.37) --
+	(233.91,163.44) --
+	(233.67,163.45) --
+	(211.38,163.45) --
+	(211.62,163.44) --
+	(211.30,163.45) --
+	(210.98,163.41) --
+	(210.67,163.32) --
+	(210.38,163.19) --
+	(210.12,163.00) --
+	(209.89,162.78) --
+	(209.69,162.52) --
+	(209.54,162.24) --
+	(209.44,161.94) --
+	(209.39,161.62) --
+	(209.38,161.46) --
+	(209.38,151.19) --
+	(209.39,151.36) --
+	(209.39,151.03) --
+	(209.44,150.72) --
+	(209.54,150.41) --
+	(209.69,150.13) --
+	(209.89,149.87) --
+	(210.12,149.65) --
+	(210.38,149.47) --
+	(210.67,149.33) --
+	(210.98,149.24) --
+	(211.30,149.20) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
+	(233.67,149.20) --
+	(233.59,149.20) --
+	(233.91,149.21) --
+	(234.22,149.28) --
+	(234.52,149.39) --
+	(234.80,149.55) --
+	(235.05,149.76) --
+	(235.26,150.00) --
+	(235.43,150.27) --
+	(235.56,150.56) --
+	(235.63,150.87) --
+	(235.66,151.19) --
+	(235.66,151.19) --
+	(235.66,161.46) --
+	(235.66,161.46) --
+	(235.63,161.78) --
+	(235.56,162.09) --
+	(235.43,162.38) --
+	(235.26,162.66) --
+	(235.05,162.90) --
+	(234.80,163.10) --
+	(234.52,163.26) --
+	(234.22,163.37) --
+	(233.91,163.44) --
+	(233.67,163.45) --
+	(211.38,163.45) --
+	(211.62,163.44) --
+	(211.30,163.45) --
+	(210.98,163.41) --
+	(210.67,163.32) --
+	(210.38,163.19) --
+	(210.12,163.00) --
+	(209.89,162.78) --
+	(209.69,162.52) --
+	(209.54,162.24) --
+	(209.44,161.94) --
+	(209.39,161.62) --
+	(209.38,161.46) --
+	(209.38,151.19) --
+	(209.39,151.36) --
+	(209.39,151.03) --
+	(209.44,150.72) --
+	(209.54,150.41) --
+	(209.69,150.13) --
+	(209.89,149.87) --
+	(210.12,149.65) --
+	(210.38,149.47) --
+	(210.67,149.33) --
+	(210.98,149.24) --
+	(211.30,149.20) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
+	(233.67,149.20) --
+	(233.59,149.20) --
+	(233.91,149.21) --
+	(234.22,149.28) --
+	(234.52,149.39) --
+	(234.80,149.55) --
+	(235.05,149.76) --
+	(235.26,150.00) --
+	(235.43,150.27) --
+	(235.56,150.56) --
+	(235.63,150.87) --
+	(235.66,151.19) --
+	(235.66,151.19) --
+	(235.66,161.46) --
+	(235.66,161.46) --
+	(235.63,161.78) --
+	(235.56,162.09) --
+	(235.43,162.38) --
+	(235.26,162.66) --
+	(235.05,162.90) --
+	(234.80,163.10) --
+	(234.52,163.26) --
+	(234.22,163.37) --
+	(233.91,163.44) --
+	(233.67,163.45) --
+	(211.38,163.45) --
+	(211.62,163.44) --
+	(211.30,163.45) --
+	(210.98,163.41) --
+	(210.67,163.32) --
+	(210.38,163.19) --
+	(210.12,163.00) --
+	(209.89,162.78) --
+	(209.69,162.52) --
+	(209.54,162.24) --
+	(209.44,161.94) --
+	(209.39,161.62) --
+	(209.38,161.46) --
+	(209.38,151.19) --
+	(209.39,151.36) --
+	(209.39,151.03) --
+	(209.44,150.72) --
+	(209.54,150.41) --
+	(209.69,150.13) --
+	(209.89,149.87) --
+	(210.12,149.65) --
+	(210.38,149.47) --
+	(210.67,149.33) --
+	(210.98,149.24) --
+	(211.30,149.20) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
+	(233.67,149.20) --
+	(233.59,149.20) --
+	(233.91,149.21) --
+	(234.22,149.28) --
+	(234.52,149.39) --
+	(234.80,149.55) --
+	(235.05,149.76) --
+	(235.26,150.00) --
+	(235.43,150.27) --
+	(235.56,150.56) --
+	(235.63,150.87) --
+	(235.66,151.19) --
+	(235.66,151.19) --
+	(235.66,161.46) --
+	(235.66,161.46) --
+	(235.63,161.78) --
+	(235.56,162.09) --
+	(235.43,162.38) --
+	(235.26,162.66) --
+	(235.05,162.90) --
+	(234.80,163.10) --
+	(234.52,163.26) --
+	(234.22,163.37) --
+	(233.91,163.44) --
+	(233.67,163.45) --
+	(211.38,163.45) --
+	(211.62,163.44) --
+	(211.30,163.45) --
+	(210.98,163.41) --
+	(210.67,163.32) --
+	(210.38,163.19) --
+	(210.12,163.00) --
+	(209.89,162.78) --
+	(209.69,162.52) --
+	(209.54,162.24) --
+	(209.44,161.94) --
+	(209.39,161.62) --
+	(209.38,161.46) --
+	(209.38,151.19) --
+	(209.39,151.36) --
+	(209.39,151.03) --
+	(209.44,150.72) --
+	(209.54,150.41) --
+	(209.69,150.13) --
+	(209.89,149.87) --
+	(210.12,149.65) --
+	(210.38,149.47) --
+	(210.67,149.33) --
+	(210.98,149.24) --
+	(211.30,149.20) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
+	(233.67,149.20) --
+	(233.59,149.20) --
+	(233.91,149.21) --
+	(234.22,149.28) --
+	(234.52,149.39) --
+	(234.80,149.55) --
+	(235.05,149.76) --
+	(235.26,150.00) --
+	(235.43,150.27) --
+	(235.56,150.56) --
+	(235.63,150.87) --
+	(235.66,151.19) --
+	(235.66,151.19) --
+	(235.66,161.46) --
+	(235.66,161.46) --
+	(235.63,161.78) --
+	(235.56,162.09) --
+	(235.43,162.38) --
+	(235.26,162.66) --
+	(235.05,162.90) --
+	(234.80,163.10) --
+	(234.52,163.26) --
+	(234.22,163.37) --
+	(233.91,163.44) --
+	(233.67,163.45) --
+	(211.38,163.45) --
+	(211.62,163.44) --
+	(211.30,163.45) --
+	(210.98,163.41) --
+	(210.67,163.32) --
+	(210.38,163.19) --
+	(210.12,163.00) --
+	(209.89,162.78) --
+	(209.69,162.52) --
+	(209.54,162.24) --
+	(209.44,161.94) --
+	(209.39,161.62) --
+	(209.38,161.46) --
+	(209.38,151.19) --
+	(209.39,151.36) --
+	(209.39,151.03) --
+	(209.44,150.72) --
+	(209.54,150.41) --
+	(209.69,150.13) --
+	(209.89,149.87) --
+	(210.12,149.65) --
+	(210.38,149.47) --
+	(210.67,149.33) --
+	(210.98,149.24) --
+	(211.30,149.20) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
+	(233.67,149.20) --
+	(233.59,149.20) --
+	(233.91,149.21) --
+	(234.22,149.28) --
+	(234.52,149.39) --
+	(234.80,149.55) --
+	(235.05,149.76) --
+	(235.26,150.00) --
+	(235.43,150.27) --
+	(235.56,150.56) --
+	(235.63,150.87) --
+	(235.66,151.19) --
+	(235.66,151.19) --
+	(235.66,161.46) --
+	(235.66,161.46) --
+	(235.63,161.78) --
+	(235.56,162.09) --
+	(235.43,162.38) --
+	(235.26,162.66) --
+	(235.05,162.90) --
+	(234.80,163.10) --
+	(234.52,163.26) --
+	(234.22,163.37) --
+	(233.91,163.44) --
+	(233.67,163.45) --
+	(211.38,163.45) --
+	(211.62,163.44) --
+	(211.30,163.45) --
+	(210.98,163.41) --
+	(210.67,163.32) --
+	(210.38,163.19) --
+	(210.12,163.00) --
+	(209.89,162.78) --
+	(209.69,162.52) --
+	(209.54,162.24) --
+	(209.44,161.94) --
+	(209.39,161.62) --
+	(209.38,161.46) --
+	(209.38,151.19) --
+	(209.39,151.36) --
+	(209.39,151.03) --
+	(209.44,150.72) --
+	(209.54,150.41) --
+	(209.69,150.13) --
+	(209.89,149.87) --
+	(210.12,149.65) --
+	(210.38,149.47) --
+	(210.67,149.33) --
+	(210.98,149.24) --
+	(211.30,149.20) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
+	(233.67,149.20) --
+	(233.59,149.20) --
+	(233.91,149.21) --
+	(234.22,149.28) --
+	(234.52,149.39) --
+	(234.80,149.55) --
+	(235.05,149.76) --
+	(235.26,150.00) --
+	(235.43,150.27) --
+	(235.56,150.56) --
+	(235.63,150.87) --
+	(235.66,151.19) --
+	(235.66,151.19) --
+	(235.66,161.46) --
+	(235.66,161.46) --
+	(235.63,161.78) --
+	(235.56,162.09) --
+	(235.43,162.38) --
+	(235.26,162.66) --
+	(235.05,162.90) --
+	(234.80,163.10) --
+	(234.52,163.26) --
+	(234.22,163.37) --
+	(233.91,163.44) --
+	(233.67,163.45) --
+	(211.38,163.45) --
+	(211.62,163.44) --
+	(211.30,163.45) --
+	(210.98,163.41) --
+	(210.67,163.32) --
+	(210.38,163.19) --
+	(210.12,163.00) --
+	(209.89,162.78) --
+	(209.69,162.52) --
+	(209.54,162.24) --
+	(209.44,161.94) --
+	(209.39,161.62) --
+	(209.38,161.46) --
+	(209.38,151.19) --
+	(209.39,151.36) --
+	(209.39,151.03) --
+	(209.44,150.72) --
+	(209.54,150.41) --
+	(209.69,150.13) --
+	(209.89,149.87) --
+	(210.12,149.65) --
+	(210.38,149.47) --
+	(210.67,149.33) --
+	(210.98,149.24) --
+	(211.30,149.20) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
+	(233.67,149.20) --
+	(233.59,149.20) --
+	(233.91,149.21) --
+	(234.22,149.28) --
+	(234.52,149.39) --
+	(234.80,149.55) --
+	(235.05,149.76) --
+	(235.26,150.00) --
+	(235.43,150.27) --
+	(235.56,150.56) --
+	(235.63,150.87) --
+	(235.66,151.19) --
+	(235.66,151.19) --
+	(235.66,161.46) --
+	(235.66,161.46) --
+	(235.63,161.78) --
+	(235.56,162.09) --
+	(235.43,162.38) --
+	(235.26,162.66) --
+	(235.05,162.90) --
+	(234.80,163.10) --
+	(234.52,163.26) --
+	(234.22,163.37) --
+	(233.91,163.44) --
+	(233.67,163.45) --
+	(211.38,163.45) --
+	(211.62,163.44) --
+	(211.30,163.45) --
+	(210.98,163.41) --
+	(210.67,163.32) --
+	(210.38,163.19) --
+	(210.12,163.00) --
+	(209.89,162.78) --
+	(209.69,162.52) --
+	(209.54,162.24) --
+	(209.44,161.94) --
+	(209.39,161.62) --
+	(209.38,161.46) --
+	(209.38,151.19) --
+	(209.39,151.36) --
+	(209.39,151.03) --
+	(209.44,150.72) --
+	(209.54,150.41) --
+	(209.69,150.13) --
+	(209.89,149.87) --
+	(210.12,149.65) --
+	(210.38,149.47) --
+	(210.67,149.33) --
+	(210.98,149.24) --
+	(211.30,149.20) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
+	(233.67,149.20) --
+	(233.59,149.20) --
+	(233.91,149.21) --
+	(234.22,149.28) --
+	(234.52,149.39) --
+	(234.80,149.55) --
+	(235.05,149.76) --
+	(235.26,150.00) --
+	(235.43,150.27) --
+	(235.56,150.56) --
+	(235.63,150.87) --
+	(235.66,151.19) --
+	(235.66,151.19) --
+	(235.66,161.46) --
+	(235.66,161.46) --
+	(235.63,161.78) --
+	(235.56,162.09) --
+	(235.43,162.38) --
+	(235.26,162.66) --
+	(235.05,162.90) --
+	(234.80,163.10) --
+	(234.52,163.26) --
+	(234.22,163.37) --
+	(233.91,163.44) --
+	(233.67,163.45) --
+	(211.38,163.45) --
+	(211.62,163.44) --
+	(211.30,163.45) --
+	(210.98,163.41) --
+	(210.67,163.32) --
+	(210.38,163.19) --
+	(210.12,163.00) --
+	(209.89,162.78) --
+	(209.69,162.52) --
+	(209.54,162.24) --
+	(209.44,161.94) --
+	(209.39,161.62) --
+	(209.38,161.46) --
+	(209.38,151.19) --
+	(209.39,151.36) --
+	(209.39,151.03) --
+	(209.44,150.72) --
+	(209.54,150.41) --
+	(209.69,150.13) --
+	(209.89,149.87) --
+	(210.12,149.65) --
+	(210.38,149.47) --
+	(210.67,149.33) --
+	(210.98,149.24) --
+	(211.30,149.20) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
+	(233.67,149.20) --
+	(233.59,149.20) --
+	(233.91,149.21) --
+	(234.22,149.28) --
+	(234.52,149.39) --
+	(234.80,149.55) --
+	(235.05,149.76) --
+	(235.26,150.00) --
+	(235.43,150.27) --
+	(235.56,150.56) --
+	(235.63,150.87) --
+	(235.66,151.19) --
+	(235.66,151.19) --
+	(235.66,161.46) --
+	(235.66,161.46) --
+	(235.63,161.78) --
+	(235.56,162.09) --
+	(235.43,162.38) --
+	(235.26,162.66) --
+	(235.05,162.90) --
+	(234.80,163.10) --
+	(234.52,163.26) --
+	(234.22,163.37) --
+	(233.91,163.44) --
+	(233.67,163.45) --
+	(211.38,163.45) --
+	(211.62,163.44) --
+	(211.30,163.45) --
+	(210.98,163.41) --
+	(210.67,163.32) --
+	(210.38,163.19) --
+	(210.12,163.00) --
+	(209.89,162.78) --
+	(209.69,162.52) --
+	(209.54,162.24) --
+	(209.44,161.94) --
+	(209.39,161.62) --
+	(209.38,161.46) --
+	(209.38,151.19) --
+	(209.39,151.36) --
+	(209.39,151.03) --
+	(209.44,150.72) --
+	(209.54,150.41) --
+	(209.69,150.13) --
+	(209.89,149.87) --
+	(210.12,149.65) --
+	(210.38,149.47) --
+	(210.67,149.33) --
+	(210.98,149.24) --
+	(211.30,149.20) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
+	(233.67,149.20) --
+	(233.59,149.20) --
+	(233.91,149.21) --
+	(234.22,149.28) --
+	(234.52,149.39) --
+	(234.80,149.55) --
+	(235.05,149.76) --
+	(235.26,150.00) --
+	(235.43,150.27) --
+	(235.56,150.56) --
+	(235.63,150.87) --
+	(235.66,151.19) --
+	(235.66,151.19) --
+	(235.66,161.46) --
+	(235.66,161.46) --
+	(235.63,161.78) --
+	(235.56,162.09) --
+	(235.43,162.38) --
+	(235.26,162.66) --
+	(235.05,162.90) --
+	(234.80,163.10) --
+	(234.52,163.26) --
+	(234.22,163.37) --
+	(233.91,163.44) --
+	(233.67,163.45) --
+	(211.38,163.45) --
+	(211.62,163.44) --
+	(211.30,163.45) --
+	(210.98,163.41) --
+	(210.67,163.32) --
+	(210.38,163.19) --
+	(210.12,163.00) --
+	(209.89,162.78) --
+	(209.69,162.52) --
+	(209.54,162.24) --
+	(209.44,161.94) --
+	(209.39,161.62) --
+	(209.38,161.46) --
+	(209.38,151.19) --
+	(209.39,151.36) --
+	(209.39,151.03) --
+	(209.44,150.72) --
+	(209.54,150.41) --
+	(209.69,150.13) --
+	(209.89,149.87) --
+	(210.12,149.65) --
+	(210.38,149.47) --
+	(210.67,149.33) --
+	(210.98,149.24) --
+	(211.30,149.20) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
+	(233.67,149.20) --
+	(233.59,149.20) --
+	(233.91,149.21) --
+	(234.22,149.28) --
+	(234.52,149.39) --
+	(234.80,149.55) --
+	(235.05,149.76) --
+	(235.26,150.00) --
+	(235.43,150.27) --
+	(235.56,150.56) --
+	(235.63,150.87) --
+	(235.66,151.19) --
+	(235.66,151.19) --
+	(235.66,161.46) --
+	(235.66,161.46) --
+	(235.63,161.78) --
+	(235.56,162.09) --
+	(235.43,162.38) --
+	(235.26,162.66) --
+	(235.05,162.90) --
+	(234.80,163.10) --
+	(234.52,163.26) --
+	(234.22,163.37) --
+	(233.91,163.44) --
+	(233.67,163.45) --
+	(211.38,163.45) --
+	(211.62,163.44) --
+	(211.30,163.45) --
+	(210.98,163.41) --
+	(210.67,163.32) --
+	(210.38,163.19) --
+	(210.12,163.00) --
+	(209.89,162.78) --
+	(209.69,162.52) --
+	(209.54,162.24) --
+	(209.44,161.94) --
+	(209.39,161.62) --
+	(209.38,161.46) --
+	(209.38,151.19) --
+	(209.39,151.36) --
+	(209.39,151.03) --
+	(209.44,150.72) --
+	(209.54,150.41) --
+	(209.69,150.13) --
+	(209.89,149.87) --
+	(210.12,149.65) --
+	(210.38,149.47) --
+	(210.67,149.33) --
+	(210.98,149.24) --
+	(211.30,149.20) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
+	(233.67,149.20) --
+	(233.59,149.20) --
+	(233.91,149.21) --
+	(234.22,149.28) --
+	(234.52,149.39) --
+	(234.80,149.55) --
+	(235.05,149.76) --
+	(235.26,150.00) --
+	(235.43,150.27) --
+	(235.56,150.56) --
+	(235.63,150.87) --
+	(235.66,151.19) --
+	(235.66,151.19) --
+	(235.66,161.46) --
+	(235.66,161.46) --
+	(235.63,161.78) --
+	(235.56,162.09) --
+	(235.43,162.38) --
+	(235.26,162.66) --
+	(235.05,162.90) --
+	(234.80,163.10) --
+	(234.52,163.26) --
+	(234.22,163.37) --
+	(233.91,163.44) --
+	(233.67,163.45) --
+	(211.38,163.45) --
+	(211.62,163.44) --
+	(211.30,163.45) --
+	(210.98,163.41) --
+	(210.67,163.32) --
+	(210.38,163.19) --
+	(210.12,163.00) --
+	(209.89,162.78) --
+	(209.69,162.52) --
+	(209.54,162.24) --
+	(209.44,161.94) --
+	(209.39,161.62) --
+	(209.38,161.46) --
+	(209.38,151.19) --
+	(209.39,151.36) --
+	(209.39,151.03) --
+	(209.44,150.72) --
+	(209.54,150.41) --
+	(209.69,150.13) --
+	(209.89,149.87) --
+	(210.12,149.65) --
+	(210.38,149.47) --
+	(210.67,149.33) --
+	(210.98,149.24) --
+	(211.30,149.20) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
+	(233.67,149.20) --
+	(233.59,149.20) --
+	(233.91,149.21) --
+	(234.22,149.28) --
+	(234.52,149.39) --
+	(234.80,149.55) --
+	(235.05,149.76) --
+	(235.26,150.00) --
+	(235.43,150.27) --
+	(235.56,150.56) --
+	(235.63,150.87) --
+	(235.66,151.19) --
+	(235.66,151.19) --
+	(235.66,161.46) --
+	(235.66,161.46) --
+	(235.63,161.78) --
+	(235.56,162.09) --
+	(235.43,162.38) --
+	(235.26,162.66) --
+	(235.05,162.90) --
+	(234.80,163.10) --
+	(234.52,163.26) --
+	(234.22,163.37) --
+	(233.91,163.44) --
+	(233.67,163.45) --
+	(211.38,163.45) --
+	(211.62,163.44) --
+	(211.30,163.45) --
+	(210.98,163.41) --
+	(210.67,163.32) --
+	(210.38,163.19) --
+	(210.12,163.00) --
+	(209.89,162.78) --
+	(209.69,162.52) --
+	(209.54,162.24) --
+	(209.44,161.94) --
+	(209.39,161.62) --
+	(209.38,161.46) --
+	(209.38,151.19) --
+	(209.39,151.36) --
+	(209.39,151.03) --
+	(209.44,150.72) --
+	(209.54,150.41) --
+	(209.69,150.13) --
+	(209.89,149.87) --
+	(210.12,149.65) --
+	(210.38,149.47) --
+	(210.67,149.33) --
+	(210.98,149.24) --
+	(211.30,149.20) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (211.38,149.20) --
+	(233.67,149.20) --
+	(233.59,149.20) --
+	(233.91,149.21) --
+	(234.22,149.28) --
+	(234.52,149.39) --
+	(234.80,149.55) --
+	(235.05,149.76) --
+	(235.26,150.00) --
+	(235.43,150.27) --
+	(235.56,150.56) --
+	(235.63,150.87) --
+	(235.66,151.19) --
+	(235.66,151.19) --
+	(235.66,161.46) --
+	(235.66,161.46) --
+	(235.63,161.78) --
+	(235.56,162.09) --
+	(235.43,162.38) --
+	(235.26,162.66) --
+	(235.05,162.90) --
+	(234.80,163.10) --
+	(234.52,163.26) --
+	(234.22,163.37) --
+	(233.91,163.44) --
+	(233.67,163.45) --
+	(211.38,163.45) --
+	(211.62,163.44) --
+	(211.30,163.45) --
+	(210.98,163.41) --
+	(210.67,163.32) --
+	(210.38,163.19) --
+	(210.12,163.00) --
+	(209.89,162.78) --
+	(209.69,162.52) --
+	(209.54,162.24) --
+	(209.44,161.94) --
+	(209.39,161.62) --
+	(209.38,161.46) --
+	(209.38,151.19) --
+	(209.39,151.36) --
+	(209.39,151.03) --
+	(209.44,150.72) --
+	(209.54,150.41) --
+	(209.69,150.13) --
+	(209.89,149.87) --
+	(210.12,149.65) --
+	(210.38,149.47) --
+	(210.67,149.33) --
+	(210.98,149.24) --
+	(211.30,149.20) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (222.52,152.52) {$64 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round] ( 29.55, 57.56) rectangle (302.65,212.31);
 \end{scope}
@@
 \path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
-\definecolor{fillColor}{gray}{0.92}
+\definecolor{fillColor}{RGB}{255,255,255}
 

### 2025-06-14 doc/talk/friends.tex
Better plots

@@
-% Created by tikzDevice version 0.12.6 on 2025-06-13 10:42:02
+% Created by tikzDevice version 0.12.6 on 2025-06-14 12:06:26
 % !TEX encoding = UTF-8 Unicode
@@
 \path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
-\definecolor{fillColor}{gray}{0.92}
+\definecolor{fillColor}{RGB}{255,255,255}
 
 \path[fill=fillColor] ( 33.14, 57.56) rectangle (302.65,212.31);
-\definecolor{drawColor}{RGB}{255,255,255}
+\definecolor{drawColor}{gray}{0.92}
 
@@
 \path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 33.14,203.77) -- ( 38.84,203.77);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (229.15,201.57) -- (290.40,201.57);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (244.79,210.61) --
+	(229.15,201.57) --
+	(244.79,192.54);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.75,192.54) --
+	(290.40,201.57) --
+	(274.75,210.61);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (251.39,194.45) --
+	(268.15,194.45) --
+	(268.07,194.45) --
+	(268.39,194.46) --
+	(268.71,194.53) --
+	(269.01,194.64) --
+	(269.29,194.80) --
+	(269.53,195.00) --
+	(269.75,195.24) --
+	(269.92,195.51) --
+	(270.04,195.81) --
+	(270.12,196.12) --
+	(270.15,196.44) --
+	(270.15,196.44) --
+	(270.15,206.70) --
+	(270.15,206.70) --
+	(270.12,207.02) --
+	(270.04,207.34) --
+	(269.92,207.63) --
+	(269.75,207.90) --
+	(269.53,208.14) --
+	(269.29,208.35) --
+	(269.01,208.51) --
+	(268.71,208.62) --
+	(268.39,208.68) --
+	(268.15,208.70) --
+	(251.39,208.70) --
+	(251.63,208.68) --
+	(251.31,208.70) --
+	(250.99,208.66) --
+	(250.68,208.57) --
+	(250.39,208.43) --
+	(250.12,208.25) --
+	(249.89,208.03) --
+	(249.70,207.77) --
+	(249.55,207.49) --
+	(249.45,207.18) --
+	(249.40,206.86) --
+	(249.39,206.70) --
+	(249.39,196.44) --
+	(249.40,196.60) --
+	(249.40,196.28) --
+	(249.45,195.96) --
+	(249.55,195.66) --
+	(249.70,195.37) --
+	(249.89,195.12) --
+	(250.12,194.90) --
+	(250.39,194.71) --
+	(250.68,194.58) --
+	(250.99,194.49) --
+	(251.31,194.45) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (259.77,197.77) {$8 \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 33.14, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round] ( 33.14, 57.56) rectangle (302.65,212.31);
 \end{scope}

### 2025-06-14 doc/talk/functions.tex
Better plots

@@
-% Created by tikzDevice version 0.12.6 on 2025-06-13 10:38:23
+% Created by tikzDevice version 0.12.6 on 2025-06-14 12:29:26
 % !TEX encoding = UTF-8 Unicode
@@
 \setlength\PreviewBorder{0pt}
-\begin{document}
+
+\usepackage{siunitx}
+\usepackage{siunitx}
+\sisetup{group-separator = {,}}\begin{document}
 
@@
 \path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55,201.36) -- ( 35.24,201.36);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
+	(101.55,198.27) --
+	(117.19,189.23);
+
+\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
+	(290.23,198.27) --
+	(274.59,207.30);
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+\definecolor{fillColor}{RGB}{255,255,255}
+
+\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
+	(225.43,191.14) --
+	(225.35,191.14) --
+	(225.67,191.16) --
+	(225.99,191.22) --
+	(226.29,191.33) --
+	(226.57,191.49) --
+	(226.81,191.70) --
+	(227.03,191.94) --
+	(227.20,192.21) --
+	(227.32,192.50) --
+	(227.40,192.82) --
+	(227.43,193.14) --
+	(227.43,193.14) --
+	(227.43,203.40) --
+	(227.43,203.40) --
+	(227.40,203.72) --
+	(227.32,204.03) --
+	(227.20,204.33) --
+	(227.03,204.60) --
+	(226.81,204.84) --
+	(226.57,205.04) --
+	(226.29,205.20) --
+	(225.99,205.32) --
+	(225.67,205.38) --
+	(225.43,205.39) --
+	(166.35,205.39) --
+	(166.59,205.38) --
+	(166.27,205.39) --
+	(165.95,205.35) --
+	(165.64,205.26) --
+	(165.35,205.13) --
+	(165.08,204.94) --
+	(164.85,204.72) --
+	(164.66,204.47) --
+	(164.51,204.18) --
+	(164.41,203.88) --
+	(164.36,203.56) --
+	(164.35,203.40) --
+	(164.35,193.14) --
+	(164.36,193.30) --
+	(164.36,192.98) --
+	(164.41,192.66) --
+	(164.51,192.35) --
+	(164.66,192.07) --
+	(164.85,191.81) --
+	(165.08,191.59) --
+	(165.35,191.41) --
+	(165.64,191.27) --
+	(165.95,191.18) --
+	(166.27,191.14) --
+	cycle;
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{RGB}{169,169,169}
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
+\end{scope}
+\begin{scope}
+\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
+\definecolor{drawColor}{gray}{0.20}
+
+\path[draw=drawColor,line width= 0.5pt,line join=round,line cap=round] ( 29.55, 57.56) rectangle (302.65,212.31);
 \end{scope}

### 2025-06-14 analysis/analyse.R

@@ -4,9 +4,13 @@ library(tikzDevice)
 library(ggpubr)
 library(RColorBrewer)
 
-#df <- read.csv("../results/processed/results_with_counts.csv")
-#df$count <- NULL
-#write.csv(df, "../results/processed/results.csv")
+options(tikzLatexPackages = c(getOption("tikzLatexPackages"),
+                              "\\usepackage{siunitx}",
+                              "\\sisetup{group-separator = {,}}"))
+
+# df <- read.csv("../results/processed/results_with_counts.csv")
+# df$count <- NULL
+# write.csv(df, "../results/processed/results.csv")
 
 df <- read.csv("../results/processed/results.csv")
 df$compilation.time <- df$compilation.time / 1000
@@ -65,11 +69,16 @@ ggplot(df[df$sequence == "Bijections",],
   ylab("Total runtime (s)") +
   xlab("Domain size") +
   labs(color = "", linetype = "", shape = "") +
-  theme_grey(base_size = 9) +
+  theme_bw(base_size = 9) +
   theme(legend.position = "bottom") +
   scale_color_manual(values = c(dark2_colors[1], dark2_colors[3])) +
   scale_linetype_manual(values = c(1, 5)) +
-  scale_shape_manual(values = c(16, 15))
+  scale_shape_manual(values = c(16, 15)) +
+  geom_segment(aes(x = 64, xend = 4096, y = 88, yend = 88),
+               colour = "darkgray", arrow = arrow(ends = "both"),
+               show.legend = FALSE) +
+  geom_label(aes(label = str_wrap("$64 \\times$"), x = 512, y = 88),
+             colour = "darkgray")
 dev.off()
 
 tikz(file = "../doc/talk/friends.tex",
@@ -86,9 +95,14 @@ ggplot(df[df$sequence == "Friends \\& Smokers",],
   ylab("Total runtime (s)") +
   xlab("Domain size") +
   labs(color = "", linetype = "", shape = "") +
-  theme_grey(base_size = 9) +
+  theme_bw(base_size = 9) +
   theme(legend.position = "bottom") +
-  scale_color_brewer(palette = "Dark2")
+  scale_color_brewer(palette = "Dark2") +
+  geom_segment(aes(x = 1024, xend = 8192, y = 1794, yend = 1794),
+               colour = "darkgray", arrow = arrow(ends = "both"),
+               show.legend = FALSE) +
[…]

### 2025-06-18 doc/talk/talk.tex
Add experimental results
Better plots
More slides

@@
 \usepackage[linesnumbered,ruled,vlined]{algorithm2e}
+\usepackage{complexity}
+\usepackage{fontawesome}
 
 \usetikzlibrary{arrows.meta}
+\usetikzlibrary{backgrounds}
 \usetikzlibrary{decorations.pathreplacing}
@@
 
+\begin{frame}{First-Order Model Counting: The Motivation}
+  \begin{exampleblock}{Example Setting}
+    \begin{itemize}
+      \item Let \structure{$\Delta$} be a set of cardinality \structure{$n$}
+      \item Suppose we want to count all \structure{$P \subseteq \Delta^{2}$}
+            that are:
+            \begin{itemize}
+              \item functions,
+              \item bijections,
+              \item partial orders,
+              \item symmetric,
+              \item transitive,
+              \item etc.
+            \end{itemize}
+    \end{itemize}
+  \end{exampleblock}
+  \pause
+  \begin{itemize}
+    \item[\faThumbsODown] Propositional model counting (\structure{$\#\SAT$}) is
+          \alert{$\#\P$-complete}
+    \item[\faThumbsOUp] But many of these counting problems have
+          \alert{efficient solutions}
+    \item And we can find them using \alert{first-order model counting}
+          \begin{itemize}
+            \item i.e., reasoning about sets, subsets, and arbitrary elements
+                  without \alert{grounding} them
+          \end{itemize}
+  \end{itemize}
+\end{frame}
+
+% TODO:
+% 1) define FOMC: any number of domains, any number of predicates of any arity
+% 2) introduce WFOMC algorithms
+% 3) Introduce Greedy vs BFS?
+\begin{frame}{First-Order Model Counting}
+\end{frame}
+
+\begin{frame}{The Problem with \textsc{Crane}}
+  \begin{block}{A Solution Produced for the Bijection-Counting Problem}
+  \begin{align*}
+    f(m, n) &= \sum_{l=0}^{n} \binom{n}{l}{(-1)}^{n-l}g(l, m),\\
+    g(l, m) &= g(l-1, m) + mg(l-1, m-1)
+  \end{align*}
+  \end{block}
+  \pause
+  \begin{alertblock}{Issues}
+    \begin{description}
+      \item[Completeness:] what are the base cases of \structure{$g$}?
+      \item[Usability:] how do I compute, e.g., \structure{$f(7, 7)$}?
+    \end{description}
+  \end{alertblock}
+\end{frame}
+% NOTE: after some simplifications
+% NOTE: the first but not the best: it can also find a linear-time solution
+
 \begin{frame}{Knowledge Compilation Workflow}
@@
     % Bounding box and its name
-    \node[draw,fit={(compilewithbasecases) (compilation) (crane) (findbasecases) (propagate)},inner ysep=7pt,yshift=5pt] {};
+    \begin{scope}[on background layer]
+      \node[draw,fit={(compilewithbasecases) (compilation) (crane) (findbasecases) (propagate)},inner ysep=7pt,yshift=5pt,fill=gray!10] {};
+    \end{scope}
     \node at (1.5, 0.5) {\Cranetwo};
@@
     \draw[-Latex] (cpp) -- (count);
-  \end{tikzpicture} % TODO: maybe add colours?
+  \end{tikzpicture}
+\end{frame}
+
+% TODO: 4 more slides explaining the solution (maybe including the theorems)
+
+\begin{frame}{}
+\end{frame}
+
+\begin{frame}{Benchmarks}
+  \begin{itemize}
+    \item Friends \& Smokers
+          \[
+          (\forall x,y \in \Delta\text{.
+          } S(x) \land F(x, y) \to S(y)) \land (\forall x \in \Delta\text{.
+          }S(x) \to C(x))
+          \]
+          \pause
+    \item Functions
+          \begin{gather*}
+            (\forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }P(x, y)) \land{}\\
+            (\forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \to y = z)
+          \end{gather*}
+          \pause
+    \item Bijections
+          \begin{gather*}
+            (\forall x \in \Gamma\text{. }\exists y \in \Delta\text{. }P(x, y))\land{}\\
+            (\forall y \in \Delta\text{. }\exists x \in \Gamma\text{. }P(x, y))\land{}\\
+            (\forall x \in \Gamma\text{. }\forall y, z \in \Delta\text{. }P(x, y) \land P(x, z) \to y = z)\land{}\\
+            (\forall x, z \in \Gamma\text{. }\forall y \in \Delta\text{. }P(x, y) \land P(z, y) \to x = z)
+          \end{gather*}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}{Friends \& Smokers}
+  \centering
+  \includegraphics{friends.pdf}
+\end{frame}
+
+\begin{frame}{Bijections}
+  \centering
+  \includegraphics{bijections.pdf}
+\end{frame}
+
+\begin{frame}{Functions}
+  \centering
+  \includegraphics{functions.pdf}
+\end{frame}
+
+\begin{frame}{Summary}
+  TODO: and future work
 \end{frame}

### 2025-07-03 doc/talk/talk.tex
Explaining the workflow

@@
 \usetikzlibrary{backgrounds}
+\usetikzlibrary{cd}
 \usetikzlibrary{decorations.pathreplacing}
@@
 \beamertemplatenavigationsymbolsempty
+\setbeamertemplate{footline}[frame number]
 \usetheme{default}
@@
 
-\begin{frame}{First-Order Model Counting: The Motivation}
+\begin{frame}{Motivation}
   \begin{exampleblock}{Example Setting}
@@
       \item Suppose we want to count all \structure{$P \subseteq \Delta^{2}$}
-            that are:
+            (as a function of \structure{$n$}) that are:
             \begin{itemize}
@@
 
-% TODO:
-% 1) define FOMC: any number of domains, any number of predicates of any arity
+% TODO: (maybe later, once I know more)
+% 1) define FOMC: any number of domains, any number of predicates of any arity (do I need to define weights?)
 % 2) introduce WFOMC algorithms
@@
 % TODO: 4 more slides explaining the solution (maybe including the theorems)
+% 0. Preprocess
+% 1. Use Crane to compile into functions
+% 2. Simplify
+% 3. FindBaseCases TODO
+% 4. For each base case
+% 4.1. For each constant (TODO?)
+% 4.1.1. Propagate TODO
+% 5. Compile to C++
 
-\begin{frame}{}
+\begin{frame}{Knowledge Compilation Workflow (1/2)}
+  \begin{enumerate}
+    \item Use \textsc{Crane} to compile \structure{$\phi$} into a set of
+          equations \structure{$\mathcal{E}$}
+    \item Simplify them, e.g.,
+          \[
+            g(l, m) = \sum_{k=0}^{m}[0 \le k \le 1]\binom{m}{k}g(l-1, m-k)
+          \]
+          becomes
+          \[
+            g(l, m) = g(l-1, m) + mg(l-1, m-1)
+          \]
+    \item Identify a sufficient set of base cases
+          \begin{itemize}
+            \item e.g., \structure{$\{\, g(0, m), g(l, 0) \,\}$}
+          \end{itemize}
+  \end{enumerate}
+\end{frame}
+
+% TODO:
+% 2) maybe space out
+% 3) add labels for each step
+% 4) add question marks that then change to 0^m and 1
+% 5) make arrows gray
+% 6) make the last line (except C++ code) appear last
+% 8) mark which steps will be explained in more detail
+\begin{frame}[fragile]{Knowledge Compilation Workflow (2/2)}
+  \centering For each base case:
+
+  \begin{tikzcd}
+    g(0, m) \arrow[d] & \phantom{-} \arrow[d, phantom] & g(l, 0) \arrow[d] \\
+    \forall x \in \Gamma\text{. }S(x) \lor \neg S(x) \arrow[d] & \phantom{-} & \top \arrow[d] \\
+    g(0, m) = 0^m \arrow[rd] & & g(l, 0) = 1 \arrow[ld] \\
+    & \mathcal{E} \arrow[d] & \\
+    \text{Domain sizes} \arrow[r] & \text{C++ code} \arrow[r] & \text{Model count}
+  \end{tikzcd}
 \end{frame}

### 2025-07-05 doc/talk/talk.tex
Finish explaining the workflow

@@
 \usepackage{fontawesome}
+\usepackage{dashbox}
 
@@
 \usetikzlibrary{shapes.misc}
+
+\tikzset{
+    invisible/.style={opacity=0},
+    visible on/.style={alt={#1{}{invisible}}},
+    alt/.code args={<#1>#2#3}{%
+      \alt<#1>{\pgfkeysalso{#2}}{\pgfkeysalso{#3}}%
+  }
+}
 
@@
 
-\begin{frame}{Knowledge Compilation Workflow}
-  \centering
-  \begin{tikzpicture}
-    % Top row
-    \node[anchor=west] at (-0.5, 0) (formula) {$\phi$};
-    \node[draw,rounded rectangle] at (3, 0) (compilewithbasecases) {\CompileWithBaseCases};
-    \node[draw,rounded rectangle] at (8, 0) (compilation) {Compile to C++};
+% \begin{frame}{Knowledge Compilation Workflow}
+%   \centering
+%   \begin{tikzpicture}
+%     % Top row
+%     \node[anchor=west] at (-0.5, 0) (formula) {$\phi$};
+%     \node[draw,rounded rectangle] at (3, 0) (compilewithbasecases) {\CompileWithBaseCases};
+%     \node[draw,rounded rectangle] at (8, 0) (compilation) {Compile to C++};
 
-    % Bottom row
-    \node[draw,rounded rectangle,dashed] at (8, -3) (cpp) {C++ code};
-    \node[anchor=west] at (-1, -3) (sizes) {Domain sizes};
-    \node at (8, -4) (count) {Model count};
+%     % Bottom row
+%     \node[draw,rounded rectangle,dashed] at (8, -3) (cpp) {C++ code};
+%     \node[anchor=west] at (-1, -3) (sizes) {Domain sizes};
+%     \node at (8, -4) (count) {Model count};
 
-    % Modules
-    \node[draw,rounded rectangle,anchor=north west] at (1.2, -1) (crane) {\Compile};
-    \node[draw,rounded rectangle,right=0.1cm of crane] (findbasecases) {\FindBaseCases};
-    \node[draw,rounded rectangle,anchor=north west] at (1.2, -1.6) (propagate) {\Propagate};
-    \node[draw,rounded rectangle,right=0.1cm of propagate] (simplify) {\Simplify};
+%     % Modules
+%     \node[draw,rounded rectangle,anchor=north west] at (1.2, -1) (crane) {\Compile};
+%     \node[draw,rounded rectangle,right=0.1cm of crane] (findbasecases) {\FindBaseCases};
+%     \node[draw,rounded rectangle,anchor=north west] at (1.2, -1.6) (propagate) {\Propagate};
+%     \node[draw,rounded rectangle,right=0.1cm of propagate] (simplify) {\Simplify};
 
-    % Bounding box and its name
-    \begin{scope}[on background layer]
-      \node[draw,fit={(compilewithbasecases) (compilation) (crane) (findbasecases) (propagate)},inner ysep=7pt,yshift=5pt,fill=gray!10] {};
-    \end{scope}
-    \node at (1.5, 0.5) {\Cranetwo};
+%     % Bounding box and its name
+%     \begin{scope}[on background layer]
+%       \node[draw,fit={(compilewithbasecases) (compilation) (crane) (findbasecases) (propagate)},inner ysep=7pt,yshift=5pt,fill=gray!10] {};
+%     \end{scope}
+%     \node at (1.5, 0.5) {\Cranetwo};
 
-    % Brace and its arrow
-    \node[fit=(crane)(findbasecases)(propagate)(simplify)] (uses) {};
-    \draw[decorate,decoration={brace}] (uses.north west) -- (uses.north east) node[midway] (brace) {};
-    \draw[-Latex,dashed] (compilewithbasecases) -- node[midway,left] {uses} (brace);
+%     % Brace and its arrow
+%     \node[fit=(crane)(findbasecases)(propagate)(simplify)] (uses) {};
+%     \draw[decorate,decoration={brace}] (uses.north west) -- (uses.north east) node[midway] (brace) {};
+%     \draw[-Latex,dashed] (compilewithbasecases) -- node[midway,left] {uses} (brace);
 
-    % All other arrows
-    \draw[-Latex] (formula) -- (compilewithbasecases);
-    \draw[-Latex] (compilewithbasecases) -- node[above] {$\mathcal{E}$} (compilation);
-    \draw[-Latex] (compilation) -- (cpp);
-    \draw[-Latex] (sizes) -- (cpp);
-    \draw[-Latex] (cpp) -- (count);
-  \end{tikzpicture}
-\end{frame}
+%     % All other arrows
+%     \draw[-Latex] (formula) -- (compilewithbasecases);
+%     \draw[-Latex] (compilewithbasecases) -- node[above] {$\mathcal{E}$} (compilation);
+%     \draw[-Latex] (compilation) -- (cpp);
+%     \draw[-Latex] (sizes) -- (cpp);
+%     \draw[-Latex] (cpp) -- (count);
+%   \end{tikzpicture}
+% \end{frame}
 
-% TODO: 4 more slides explaining the solution (maybe including the theorems)
+% TODO: 5 slides explaining the solution (maybe including the theorems)
 % 0. Preprocess
@@
 
+% TODO: (here and on the next slide) mark which steps will be explained in more detail
 \begin{frame}{Knowledge Compilation Workflow (1/2)}
@@
     \item Use \textsc{Crane} to compile \structure{$\phi$} into a set of
-          equations \structure{$\mathcal{E}$}
+          equations \structure{$\mathcal{E}$} \pause
     \item Simplify them, e.g.,
@@
             g(l, m) = g(l-1, m) + mg(l-1, m-1)
-          \]
+          \] \pause
     \item Identify a sufficient set of base cases
@@
 
-% TODO:
-% 2) maybe space out
-% 3) add labels for each step
-% 4) add question marks that then change to 0^m and 1
-% 5) make arrows gray
-% 6) make the last line (except C++ code) appear last
-% 8) mark which steps will be explained in more detail
 \begin{frame}[fragile]{Knowledge Compilation Workflow (2/2)}
-  \centering For each base case:
+  \centering \structure{4.} For each base case:
 
   \begin{tikzcd}
-    g(0, m) \arrow[d] & \phantom{-} \arrow[d, phantom] & g(l, 0) \arrow[d] \\
-    \forall x \in \Gamma\text{. }S(x) \lor \neg S(x) \arrow[d] & \phantom{-} & \top \arrow[d] \\
-    g(0, m) = 0^m \arrow[rd] & & g(l, 0) = 1 \arrow[ld] \\
-    & \mathcal{E} \arrow[d] & \\
-    \text{Domain sizes} \arrow[r] & \text{C++ code} \arrow[r] & \text{Model count}
+    g(0, m) \arrow[d, gray, visible on=<2->] & \phantom{-} \arrow[d, phantom, visible on=<2->, "\text{\structure{4.1.} Construct the corr.\ sentence}"] & g(l, 0) \arrow[d, gray, visible on=<2->] \\
+    |[visible on=<2->]| \forall x \in \Gamma\text{.
+}S(x) \lor \neg S(x) \arrow[d, gray, visible on=<3->] & \phantom{-} \arrow[d, phantom, visible on=<3->, "\text{\structure{4.2.} Recurse}"] & |[visible on=<2->]| \top \arrow[d, gray, visible on=<3->] \\
+    |[visible on=<3->]| g(0, m) = \alt<4->{0^m}{\text{???}} \arrow[rd, gray, visible on=<5->] & |[visible on=<5->]| \text{\structure{4.3.} Add to }\structure{\mathcal{E}} & |[visible on=<3->]| g(l, 0) = \alt<4->{1}{???} \arrow[ld, gray, visible on=<5->] \\
+    & |[visible on=<5->]| \mathcal{E} \arrow[d, gray, visible on=<6->, "\text{\color{black}{\structure{5.} Compile to C++}}"] & \\
+    |[visible on=<7->]| \text{Domain sizes} \arrow[r, gray, visible on=<7->] & |[visible on=<6->]| \text{\dbox{C++ code}} \arrow[r, gray, visible on=<7->] & |[visible on=<7->]| \text{Model count}
   \end{tikzcd}

### 2025-07-06 doc/talk/talk.tex
More slides

@@
 
-% TODO: 5 slides explaining the solution (maybe including the theorems)
-% 0. Preprocess
-% 1. Use Crane to compile into functions
-% 2. Simplify
-% 3. FindBaseCases TODO
-% 4. For each base case
-% 4.1. For each constant (TODO?)
-% 4.1.1. Propagate TODO
-% 5. Compile to C++
-
-% TODO: (here and on the next slide) mark which steps will be explained in more detail
 \begin{frame}{Knowledge Compilation Workflow (1/2)}
@@
           \] \pause
-    \item Identify a sufficient set of base cases
+    \item[3. ($\Rightarrow$)] Identify a sufficient set of base cases
           \begin{itemize}
@@
 \end{frame}
+% NOTE: explain what the arrow means
 
@@
   \begin{tikzcd}
-    g(0, m) \arrow[d, gray, visible on=<2->] & \phantom{-} \arrow[d, phantom, visible on=<2->, "\text{\structure{4.1.} Construct the corr.\ sentence}"] & g(l, 0) \arrow[d, gray, visible on=<2->] \\
+    g(0, m) \arrow[d, gray, visible on=<2->] & \phantom{-} \arrow[d, phantom, visible on=<2->, "\text{\structure{4.1.
+($\Rightarrow$)} Construct the corr.\ sentence}"] & g(l, 0) \arrow[d, gray, visible on=<2->] \\
     |[visible on=<2->]| \forall x \in \Gamma\text{.
@@
   \end{tikzcd}
+\end{frame}
+
+\begin{frame}[fragile]{Finding (a Sufficient Set of) Base Cases}
+  \begin{block}{Outline}
+    \begin{enumerate}
+      \item For every function call:
+            \begin{enumerate}
+              \item For every argument of the form
+                    \structure{$\textit{var} - \textit{const}$}:
+                    \begin{enumerate}
+                      \item Replace the signature parameter with
+                            \structure{$0$}, \structure{$1$}, \dots,
+                            \structure{$\textit{const} - 1$}
+                    \end{enumerate}
+              \item For every argument of the form \structure{$\textit{const}$}:
+                    \begin{enumerate}
+                      \item Replace the corresponding signature parameter with
+                            \structure{$\textit{const}$}
+                    \end{enumerate}
+            \end{enumerate}
+    \end{enumerate}
+  \end{block}
+  \begin{example}
+    The signature of \structure{$g$} is \structure{$g(l, m)$}.
+
+    \centering
+    \begin{tikzcd}
+      \text{Function calls:} & g(l-1, m) \arrow[d] & g(l-1, m-1) \arrow[ld] \arrow[d] \\
+      \text{Base cases:} & g(0, m) & g(l, 0)
+    \end{tikzcd}
+  \end{example}
+\end{frame}
+
+\begin{frame}{Theoretical Results}
+  \begin{theorem}
+    The maximum \alert{recursion depth} of the compilation algorithm is upper
+    bounded by the \alert{number of domains}.
+  \end{theorem}
+  \pause
+  \begin{proof}[Proof (hint).]
+    Each recursive call eliminates a domain.
+  \end{proof}
+  \pause
+  \begin{theorem}
+    The \alert{evaluation} of a recursive function always \alert{terminates}.
+  \end{theorem}
+  \pause
+  \begin{proof}[Proof (hints).]
+    \begin{itemize}
+      \item There exists a \alert{topological ordering} of functions
+      \item All function calls follow the \alert{structure} from the previous
+            slide
+      \item Some common-sense assumptions about the \alert{evaluation order} and
+            previous work
+    \end{itemize}
+  \end{proof}
+\end{frame}
+
+% TODO: propagate + maybe smoothing
+\begin{frame}{From a Base Case to a Sentence}
+  \begin{block}{Preliminaries}
+    \begin{itemize}
+      \item \textsc{Crane} associates each function \structure{$f$} with a
+            sentence \structure{$\phi$} such that
+            \structure{$\textsc{Crane}(\phi)$} produces the definition of
+            \structure{$f$}
+      \item There is a bijection between the parameters of \structure{$f$} and
+            the domains of \structure{$\phi$}
+    \end{itemize}
+  \end{block}
 \end{frame}

### 2025-07-07 doc/talk/talk.tex
Finish explaining the algorithm

@@
 \documentclass{beamer}
+\usepackage[T1]{fontenc}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{dashbox}
+\usepackage[style=authoryear]{biblatex}
+
+\addbibresource{talk.bib}
 
@@
 ($\Rightarrow$)} Construct the corr.\ sentence}"] & g(l, 0) \arrow[d, gray, visible on=<2->] \\
-    |[visible on=<2->]| \forall x \in \Gamma\text{.
-}S(x) \lor \neg S(x) \arrow[d, gray, visible on=<3->] & \phantom{-} \arrow[d, phantom, visible on=<3->, "\text{\structure{4.2.} Recurse}"] & |[visible on=<2->]| \top \arrow[d, gray, visible on=<3->] \\
+    |[visible on=<2->]| \forall y \in \Delta\text{.
+}S(y) \lor \neg S(y) \arrow[d, gray, visible on=<3->] & \phantom{-} \arrow[d, phantom, visible on=<3->, "\text{\structure{4.2.} Recurse}"] & |[visible on=<2->]| \top \arrow[d, gray, visible on=<3->] \\
     |[visible on=<3->]| g(0, m) = \alt<4->{0^m}{\text{???}} \arrow[rd, gray, visible on=<5->] & |[visible on=<5->]| \text{\structure{4.3.} Add to }\structure{\mathcal{E}} & |[visible on=<3->]| g(l, 0) = \alt<4->{1}{???} \arrow[ld, gray, visible on=<5->] \\
@@
     \begin{enumerate}
-      \item For every function call:
+      \item For every \alert{function call}:
             \begin{enumerate}
-              \item For every argument of the form
+              \item For every \alert{argument} of the form
                     \structure{$\textit{var} - \textit{const}$}:
                     \begin{enumerate}
-                      \item Replace the signature parameter with
+                      \item Replace the \alert{signature parameter} with
                             \structure{$0$}, \structure{$1$}, \dots,
@@
                     \end{enumerate}
-              \item For every argument of the form \structure{$\textit{const}$}:
+              \item For every \alert{argument} of the form
+                    \structure{$\textit{const}$}:
                     \begin{enumerate}
@@
   \begin{example}
-    The signature of \structure{$g$} is \structure{$g(l, m)$}.
+    The \alert{signature} of \structure{$g$} is \structure{$g(l, m)$}.
 
@@
 
-% TODO: propagate + maybe smoothing
-\begin{frame}{From a Base Case to a Sentence}
-  \begin{block}{Preliminaries}
+\begin{frame}[fragile]{From a Base Case to a Sentence}
+  \begin{block}{From Previous Work~\color{gray}{\parencite{DBLP:conf/kr/DilkasB23}}}
     \begin{itemize}
@@
   \end{block}
+  \begin{example}
+    \begin{itemize}
+      \item Base case: \structure{$g(\stackrel{\mbox{\color{black}{\tiny\onslide<2->{\ensuremath{\Gamma}}}}}{\stackrel{\mbox{\color{black}{\tiny\onslide<2->{\ensuremath{\updownarrow}}}}}{0}}, \stackrel{\mbox{\color{black}{\tiny\onslide<2->{\ensuremath{\Delta}}}}}{\stackrel{\mbox{\color{black}{\tiny\onslide<2->{\ensuremath{\updownarrow}}}}}{m}})$}
+      \item<3-> \alert{Part} of the sentence of \structure{$g$}:
+            \begin{equation}\label{eq}
+              \forall x \in \Gamma\text{. }\forall y \in \Delta\text{. }S(y) \lor \neg P(x, y)
+            \end{equation}
+      \item<4-> \structure{$g(0, \dots)$} means we need to simplify \eqref{eq}
+            by assuming \structure{$|\Gamma| = 0$}
+      \item<5-> Result: \structure{$\forall y \in \Delta\text{.
+            }S(y) \lor \neg S(y)$} \qquad (\alert{Smoothing})
+    \end{itemize}
+  \end{example}
 \end{frame}

### 2025-07-09 doc/talk/talk.tex
Explain Crane

@@
 \usepackage[style=authoryear]{biblatex}
+\usepackage{mathtools}
 
@@
 
-% TODO: (maybe later, once I know more)
-% 1) define FOMC: any number of domains, any number of predicates of any arity (do I need to define weights?)
-% 2) introduce WFOMC algorithms
-% 3) Introduce Greedy vs BFS?
-\begin{frame}{First-Order Model Counting}
+\begin{frame}{More Formally: What Is the Input?}
+  \[
+    \forall x \in \alert<2>{\Gamma}\text{. }\forall y, z \in \alert<2>{\Delta}\text{. }P(x, y) \land P(x, z) \Rightarrow \alert<4>{y=z}
+  \]
+  \begin{block}{\mbox{\alert<2>{Many-Sorted} \alert<3>{Function-Free}
+        First-Order Logic with \alert<4>{Equality}}}
+  \begin{itemize}
+    \item<5-> Any number of variables and constants
+    % \item<5-> All variables are bound (by \alert{$\exists$} or
+    %       \alert{$\forall$})
+    \item<6-> \alert{$\exists$} and \alert{$\forall$} quantifiers can be nested
+          arbitrarily deeply
+    \item<6-> All domains are finite
+          \begin{itemize}
+            \item Solutions are functions that take domain sizes as input
+          \end{itemize}
+    % \item<6-> Predicates can have any arity
+  \end{itemize}
+  \end{block}
+  \onslide<7->{
+    \begin{block}{First-Order Model Counting (FOMC)}
+      \begin{itemize}
+        \item Each predicate acts like a \alert{subset}
+        \begin{itemize}
+          \item of a domain or
+          \item of a Cartesian product of domains
+        \end{itemize}
+        \item Goal: count \alert{combinations of subsets} that satisfy the
+              sentence
+      \end{itemize}
+    \end{block}
+  }
 \end{frame}
 
-\begin{frame}{The Problem with \textsc{Crane}}
-  \begin{block}{A Solution Produced for the Bijection-Counting Problem}
+\begin{frame}{Previous Work:
+    \textsc{Crane}~\color{gray}{\parencite{DBLP:conf/kr/DilkasB23}}}
+  \begin{itemize}
+    \item A knowledge compilation approach:
+          \begin{itemize}
+            \item \alert{Sentences} $\to$ labelled \alert{digraphs} $\to$
+                  function-defining \alert{equations}
+          \end{itemize}
+    \item Capable of constructing recursive solutions
+  \end{itemize}
+  \pause
+  \begin{exampleblock}{An Example Solution for Counting Bijections}
     \begin{align*}
@@
     \end{align*}
-  \end{block}
+  \end{exampleblock}
   \pause
@@
 \end{frame}
-% NOTE: after some simplifications
 % NOTE: the first but not the best: it can also find a linear-time solution
+% NOTE: this slide formulates the problem tackled by this work
 

### 2025-07-11 doc/talk/talk.tex
First complete draft of the SAT talk
Clarity improvements

@@
 \usepackage{mathtools}
+\usepackage{siunitx}
+\usepackage{libertinus}
 
@@
 \newcommand{\bijections}{\emph{Bijections}}
+
+\sisetup{group-separator = {,}}
 
@@
 \begin{frame}{More Formally: What Is the Input?}
+  \begin{exampleblock}{Example Input Sentence}
     \[
-    \forall x \in \alert<2>{\Gamma}\text{. }\forall y, z \in \alert<2>{\Delta}\text{. }P(x, y) \land P(x, z) \Rightarrow \alert<4>{y=z}
+      \forall x \in \alert<2>{\Gamma}\text{.
+      }\forall y, z \in \alert<2>{\Delta}\text{.
+      }P(x, y) \land P(x, z) \Rightarrow \alert<4>{y=z}
     \]
+  \end{exampleblock}
   \begin{block}{\mbox{\alert<2>{Many-Sorted} \alert<3>{Function-Free}
@@
         \begin{itemize}
-          \item of a domain or
-          \item of a Cartesian product of domains
+          \item of a domain or product of domains
         \end{itemize}
@@
     \item Capable of constructing recursive solutions
+    \item Two variants: \alert{greedy} search and \alert{breadth-first search}
+          (BFS)
   \end{itemize}
@@
   \pause
-  \begin{alertblock}{Issues}
+  \begin{alertblock}{Issues We Are Going to Address}
     \begin{description}
-      \item[Completeness:] what are the base cases of \structure{$g$}?
+      \item[Completeness:] recursive functions (like \structure{$g$}) have
+            \alert{no base cases}
       \item[Usability:] how do I compute, e.g., \structure{$f(7, 7)$}?
@@
 
-\begin{frame}{Knowledge Compilation Workflow (1/2)}
+\begin{frame}{Workflow (1/2)}
   \begin{enumerate}
@@
 
-\begin{frame}[fragile]{Knowledge Compilation Workflow (2/2)}
+\begin{frame}[fragile]{Workflow (2/2)}
   \centering \structure{4.} For each base case:
@@
 
-\begin{frame}{Theoretical Results}
+\begin{frame}{Theoretical Guarantees}
   \begin{theorem}
@@
 
-\begin{frame}{Summary}
-  TODO: and future work
+\begin{frame}{Summary \& Future Work}
+  \begin{block}{Contributions}
+    \begin{description}
+      \item[Completeness:] recursive solutions now come with \alert{base cases}
+      \item[Usability:] compilation to C++ programs
+      \item[Scalability] compared to other FOMC algorithms
+            \begin{itemize}
+              \item \numrange{8}{500000} times higher domain sizes
+            \end{itemize}
+    \end{description}
+  \end{block}
+  \pause
+  \begin{block}{Future Work}
+    \begin{itemize}
+      \item Support for weighted counting (trivial)
+      \item Experiments on a large set of benchmarks
+      \item Completeness for fragments of first-order logic
+      \item Fine-grained complexity
+    \end{itemize}
+  \end{block}
+  % \vspace{0.5em} \small
+  % \begin{itemize}
+  %   \item Implementation:
+  %         \href{https://github.com/dilkas/crane}{\texttt{github.com/dilkas/crane}}
+  %   \item Experimental setup:
+  %         \href{https://github.com/dilkas/sat25-ksdm}{\texttt{github.com/dilkas/sat25-ksdm}}
+  % \end{itemize}
 \end{frame}

### 2025-08-02 doc/talk/talk.tex
One more slide
Ditto

@@
 \usepackage{tikz}
-\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
+\usepackage[vlined]{algorithm2e}
 \usepackage{complexity}
@@
 \usepackage{libertinus}
+\usepackage{csquotes}
 
@@
 
+\SetKwProg{Fn}{Function}{:}{}
+\SetKwData{Cache}{Cache}
 \SetKwFunction{CompileWithBaseCases}{CompileWithBaseCases}
@@
 
+\begin{frame}{Exact Algorithms for FOMC}
+  \begin{block}{Predecessors of This Work}
+    \begin{itemize}
+      \item
+            \alert{\textsc{ForcLift}}~\textcolor{gray}{\parencite{DBLP:conf/ijcai/BroeckTMDR11}}
+            \begin{itemize}
+              \item knowledge compilation to \alert{FO d-DNNF}
+            \end{itemize}
+      \item \alert{\textsc{Crane}}~\textcolor{gray}{\parencite{DBLP:conf/kr/DilkasB23}}
+            \begin{itemize}
+              \item knowledge compilation to $\text{FO
+                    d-DNNF} + \alert{\text{directed cycles}}$
+              \item extends \alert{\textsc{ForcLift}} with support for:
+                    \begin{itemize}
+                      \item more input sentences and
+                      \item recursive solutions
+                    \end{itemize}
+            \end{itemize}
+    \end{itemize}
+  \end{block}
+  \pause
+  \begin{block}{Other Approaches}
+    \begin{itemize}
+      \item \alert{L2C}~\textcolor{gray}{\parencite{DBLP:conf/kr/KazemiP16}}
+            \begin{itemize}
+              \item knowledge compilation to \alert{C++} code
+            \end{itemize}
+      \item
+            \alert{Alchemy}~\textcolor{gray}{\parencite{DBLP:journals/cacm/GogateD16}}
+            \begin{itemize}
+              \item \alert{DPLL}-style search
+            \end{itemize}
+      \item
+            \alert{FastWFOMC}~\textcolor{gray}{\parencite{DBLP:conf/uai/BremenK21}}
+            \begin{itemize}
+              \item based on \alert{cell enumeration}
+              % \item with extensions for \alert{additional axioms}, ordered domains, etc.
+            \end{itemize}
+    \end{itemize}
+  \end{block}
+\end{frame}
+
 \begin{frame}{Previous Work:
-    \textsc{Crane}~\color{gray}{\parencite{DBLP:conf/kr/DilkasB23}}}
+    \textsc{Crane}~\textcolor{gray}{\parencite{DBLP:conf/kr/DilkasB23}}}
   \begin{itemize}
@@
           \end{itemize}
-    \item Capable of constructing recursive solutions
+    % \item Capable of constructing recursive solutions
     \item Two variants: \alert{greedy} search and \alert{breadth-first search}
@@
 
-% \begin{frame}{Knowledge Compilation Workflow}
-%   \centering
-%   \begin{tikzpicture}
-%     % Top row
-%     \node[anchor=west] at (-0.5, 0) (formula) {$\phi$};
-%     \node[draw,rounded rectangle] at (3, 0) (compilewithbasecases) {\CompileWithBaseCases};
-%     \node[draw,rounded rectangle] at (8, 0) (compilation) {Compile to C++};
-
-%     % Bottom row
-%     \node[draw,rounded rectangle,dashed] at (8, -3) (cpp) {C++ code};
-%     \node[anchor=west] at (-1, -3) (sizes) {Domain sizes};
-%     \node at (8, -4) (count) {Model count};
-
-%     % Modules
-%     \node[draw,rounded rectangle,anchor=north west] at (1.2, -1) (crane) {\Compile};
-%     \node[draw,rounded rectangle,right=0.1cm of crane] (findbasecases) {\FindBaseCases};
-%     \node[draw,rounded rectangle,anchor=north west] at (1.2, -1.6) (propagate) {\Propagate};
-%     \node[draw,rounded rectangle,right=0.1cm of propagate] (simplify) {\Simplify};
-
-%     % Bounding box and its name
-%     \begin{scope}[on background layer]
-%       \node[draw,fit={(compilewithbasecases) (compilation) (crane) (findbasecases) (propagate)},inner ysep=7pt,yshift=5pt,fill=gray!10] {};
-%     \end{scope}
-%     \node at (1.5, 0.5) {\Cranetwo};
-
-%     % Brace and its arrow
-%     \node[fit=(crane)(findbasecases)(propagate)(simplify)] (uses) {};
-%     \draw[decorate,decoration={brace}] (uses.north west) -- (uses.north east) node[midway] (brace) {};
-%     \draw[-Latex,dashed] (compilewithbasecases) -- node[midway,left] {uses} (brace);
-
-%     % All other arrows
-%     \draw[-Latex] (formula) -- (compilewithbasecases);
-%     \draw[-Latex] (compilewithbasecases) -- node[above] {$\mathcal{E}$} (compilation);
-%     \draw[-Latex] (compilation) -- (cpp);
-%     \draw[-Latex] (sizes) -- (cpp);
-%     \draw[-Latex] (cpp) -- (count);
-%   \end{tikzpicture}
-% \end{frame}
-
-\begin{frame}{Workflow (1/2)}
+\begin{frame}{The Workflow of \textsc{Crane2} (1/2)}
   \begin{enumerate}
-    \item Use \textsc{Crane} to compile \structure{$\phi$} into a set of
+    \item Use \alert{\textsc{Crane}} to compile \structure{$\phi$} into a set of
           equations \structure{$\mathcal{E}$} \pause
@@
 
-\begin{frame}[fragile]{Workflow (2/2)}
+\begin{frame}[fragile]{The Workflow of \textsc{Crane2} (2/2)}
   \centering \structure{4.} For each base case:
@@
     |[visible on=<3->]| g(0, m) = \alt<4->{0^m}{\text{???}} \arrow[rd, gray, visible on=<5->] & |[visible on=<5->]| \text{\structure{4.3.} Add to }\structure{\mathcal{E}} & |[visible on=<3->]| g(l, 0) = \alt<4->{1}{???} \arrow[ld, gray, visible on=<5->] \\
-    & |[visible on=<5->]| \mathcal{E} \arrow[d, gray, visible on=<6->, "\text{\color{black}{\structure{5.} Compile to C++}}"] & \\
+    & |[visible on=<5->]| \mathcal{E} \arrow[d, gray, visible on=<6->, "\text{\textcolor{black}{\structure{5. ($\Rightarrow$)} Compile to C++}}"] & \\
     |[visible on=<7->]| \text{Domain sizes} \arrow[r, gray, visible on=<7->] & |[visible on=<6->]| \text{\dbox{C++ code}} \arrow[r, gray, visible on=<7->] & |[visible on=<7->]| \text{Model count}
@@
 \begin{frame}[fragile]{From a Base Case to a Sentence}
-  \begin{block}{From Previous Work~\color{gray}{\parencite{DBLP:conf/kr/DilkasB23}}}
+  \begin{block}{From Previous
+      Work~\textcolor{gray}{\parencite{DBLP:conf/kr/DilkasB23}}}
     \begin{itemize}
-      \item \textsc{Crane} associates each function \structure{$f$} with a
+      \item \alert{\textsc{Crane}} associates each function \structure{$f$} with a
             sentence \structure{$\phi$} such that
@@
     \begin{itemize}
-      \item Base case: \structure{$g(\stackrel{\mbox{\color{black}{\tiny\onslide<2->{\ensuremath{\Gamma}}}}}{\stackrel{\mbox{\color{black}{\tiny\onslide<2->{\ensuremath{\updownarrow}}}}}{0}}, \stackrel{\mbox{\color{black}{\tiny\onslide<2->{\ensuremath{\Delta}}}}}{\stackrel{\mbox{\color{black}{\tiny\onslide<2->{\ensuremath{\updownarrow}}}}}{m}})$}
+      \item Base case: \structure{$g(\stackrel{\mbox{\textcolor{black}{\tiny\onslide<2->{\ensuremath{\Gamma}}}}}{\stackrel{\mbox{\textcolor{black}{\tiny\onslide<2->{\ensuremath{\updownarrow}}}}}{0}}, \stackrel{\mbox{\textcolor{black}{\tiny\onslide<2->{\ensuremath{\Delta}}}}}{\stackrel{\mbox{\textcolor{black}{\tiny\onslide<2->{\ensuremath{\updownarrow}}}}}{m}})$}
       \item<3-> \alert{Part} of the sentence of \structure{$g$}:
@@
   \end{example}
+\end{frame}
+
+\begin{frame}{An Outline of the Resulting C++ Program}
+  \begin{algorithm}[H]
+    initialise $\Cache_{\alert{g(0, m)}}$, $\Cache_{\alert{g(l, 0)}}$, $\Cache_{\alert{g}}$, and $\Cache_{\alert{f}}$\; \DontPrintSemicolon\pause
+    \textbf{Function} $\alert{g_{0,m}(m)}$\textbf{:} \dots\;
+    \textbf{Function} $\alert{g_{l,0}(l)}$\textbf{:} \dots\; \PrintSemicolon\pause
+    \Fn{$\alert{g(l, m)}$}{
+      \lIf{$(l, m) \in \Cache_{\alert{g}}$}{\Return{$\Cache_{\alert{g}}(l, m)$}}\label{line:cache}
+      \lIf{$l = 0$}{\Return{$\alert{g_{0,m}(m)}$}}\label{line:basecaseone}
+      \lIf{$m = 0$}{\Return{$\alert{g_{l,0}(l)}$}}\label{line:basecasetwo}
+      $r \gets \alert{g(l-1, m)} + m\alert{g(l-1,m-1)}$\;
+      $\Cache_{\alert{g}}(l, m) \gets r$\;
+      \Return{$r$}\;
+    } \DontPrintSemicolon
+    \textbf{Function} $\alert{f(m, n)}$\textbf{:} \dots\; \PrintSemicolon
+    \Fn{\alert{\Main}}{
+      $(m, n) \gets \Input{}$\;
+      \Return{$\alert{f(m, n)}$}\;
+    }
+  \end{algorithm}
 \end{frame}

### 2025-08-07 doc/talk/talk.tex
Minor changes

@@
 
-% TODO: 20 min / 14 slides (presumably)
 \begin{document}
@@
     \begin{itemize}
-      \item Let \structure{$\Delta$} be a set of cardinality \structure{$n$}
+      \item Let \structure{$\Delta$} be a set of cardinality
+            \structure{$n \in \mathbb{N}_0$}
       \item Suppose we want to count all \structure{$P \subseteq \Delta^{2}$}
@@
     \item<5-> Any number of variables and constants
-    % \item<5-> All variables are bound (by \alert{$\exists$} or
-    %       \alert{$\forall$})
-    \item<6-> \alert{$\exists$} and \alert{$\forall$} quantifiers can be nested
-          arbitrarily deeply
-    \item<6-> All domains are finite
+    \item<5-> \structure{$\exists$} and \structure{$\forall$} quantifiers can be
+          nested arbitrarily deeply
+    \item<5-> All domains are finite
           \begin{itemize}
@@
           \end{itemize}
-    % \item<6-> Predicates can have any arity
+    \item<5-> Of course, not all valid inputs have tractable solutions
   \end{itemize}
   \end{block}
-  \onslide<7->{
+  \onslide<6->{
     \begin{block}{First-Order Model Counting (FOMC)}
@@
   \begin{enumerate}
-    \item Use \alert{\textsc{Crane}} to compile \structure{$\phi$} into a set of
-          equations \structure{$\mathcal{E}$} \pause
+    \item Use \alert{\textsc{Crane}} to compile sentence \structure{$\phi$} into
+          a set of equations \structure{$\mathcal{E}$} \pause
     \item Simplify them, e.g.,
@@
             \structure{$f$}
-      \item There is a bijection between the parameters of \structure{$f$} and
-            the domains of \structure{$\phi$}
+      \item There is a bijection between the parameters of the \alert{main
+            function} \structure{$f$} and the \alert{domains} of the
+            \alert{input sentence} \structure{$\phi$}
     \end{itemize}
@@
       \item<5-> Result: \structure{$\forall y \in \Delta\text{.
-            }S(y) \lor \neg S(y)$} \qquad (\alert{Smoothing})
+            }S(y) \lor \neg S(y)$}\hfill(\alert{Smoothing})
     \end{itemize}

### 2025-08-08 doc/talk/talk.tex
Ditto

@@
   \begin{itemize}
-    \item[\faThumbsODown] Propositional model counting (\structure{$\#\SAT$}) is
+    \item[\faThumbsODown] Propositional model counting (\alert{$\#\SAT$}) is
           \alert{$\#\P$-complete}
@@
           \begin{itemize}
-            \item Solutions are functions that take domain sizes as input
+            \item Solutions are functions that take domain sizes as inputs
           \end{itemize}
@@
         \begin{itemize}
-          \item of a domain or product of domains
+          \item of a domain or a Cartesian product of domains
         \end{itemize}
@@
   \pause
-  \begin{block}{Other Approaches}
+  \begin{block}{Some Other Approaches}
     \begin{itemize}
@@
           \end{itemize}
-    % \item Capable of constructing recursive solutions
-    \item Two variants: \alert{greedy} search and \alert{breadth-first search}
+    \item Two variants: \alert{greedy} search and \alert{breadth-first} search
           (BFS)
@@
           \] \pause
-    \item[3. ($\Rightarrow$)] Identify a sufficient set of base cases
+    \item[3. ($\Rightarrow$)] Identify a \alert{sufficient set of base cases} of
+          all recursive functions
           \begin{itemize}
@@
             \structure{$f$}
-      \item There is a bijection between the parameters of the \alert{main
-            function} \structure{$f$} and the \alert{domains} of the
-            \alert{input sentence} \structure{$\phi$}
+      \item And there is a bijection between the \alert{parameters} of
+            \structure{$f$} and the \alert{domains} of \structure{$\phi$}
     \end{itemize}
@@
 
-\begin{frame}{An Outline of the Resulting C++ Program}
+\begin{frame}{The Structure of the Resulting C++ Program}
   \begin{algorithm}[H]
